### 2021-08-26 scripts/FINAL PROCESSING/Analysis/Final analysis.Rmd
data

---
title: "The Role of Theory of Mind and Interoception in Deception and Psychopathy "
subtitle: "Statistical Analysis"
output:
  html_document:
    theme: journal
    footer: LIE questionnaire validation
    highlight: pygments
    toc: yes
    toc_depth: 4
    toc_float: yes
    df_print: kable
    code_folding: hide
  word_document: default
  pdf_document:
    toc: yes
    toc_depth: '4'
editor_options: 
  chunk_output_type: console
---

Final Year Project by Low Jia Rong (U1730052L)

# Packages and Setup

## Libraries
```{r setup, include=TRUE, warning = FALSE, message = FALSE}
setwd("~/Dropbox/FYP_Jia Rong/R Processing/FINAL PROCESSING/Analysis")
library(tidyverse)
library(lme4)
library(ggplot2)
library(glmmTMB)
library(correlation)
library(sjPlot)
#library(easystats)

library(report)
library(correlation)
library(parameters)
library(see)

descriptive_statistics <- function(df, begins_with){
  df %>% 
    select(dplyr::starts_with(begins_with)) %>% 
    report() %>% 
    as.data.frame() %>% 
    select(-one_of(c("n_Obs", "Median", "MAD", "n_Missing"))) %>% 
    print()

  plot(df %>% 
    select(dplyr::starts_with(begins_with)) %>% 
    bayestestR::estimate_density(method = "KernSmooth") %>% 
    plot() + 
      xlab("Score") + ylab("Frequency") +
    see::theme_modern())
}

```

## Read data
```{r read_data, include=TRUE, warning = FALSE, message = FALSE}
Behav <- read.csv('BehaviouraldataNEW.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1)] %>% 
  rename(participant = ID,
         truthfulness = condition) %>% 
  mutate(ConditionSP = rep(c("social","polygraph"), each = 40, times = 30))

Behav[stringr::str_detect(names(Behav), "subresp")] <- effectsize::change_scale(Behav[stringr::str_detect(names(Behav), "subresp")], from = c(0, 1), to = c(10, -10))

Phy <- read.csv('DT_04.csv', stringsAsFactors = FALSE, header = TRUE) [-c(1),] %>% 
  rename(participant = Participant.number,) %>% 
  mutate(Trial = rep(1:80, each = 4, times = 30))

data <- merge(Behav, Phy, by = c("participant" ,"Trial"), all = TRUE) %>% 
  arrange(participant,Trial) %>% 
  mutate(participant = as.factor(participant),
         ConditionSP = as.factor(ConditionSP))

Demo <- read.csv('demo_30.csv', stringsAsFactors = FALSE, header = TRUE)[-c(2,3,4:6,9,11,12,18)]

```

```{r , include=FALSE, warning = FALSE, message = FALSE}
## Cleaning data
data <- data %>% 
  filter(Inclusion != "0")

```

# Descriptive Statistics
## Participants Demographics Information
Summary of participants Gender, Age, and Handedness
```{r , include=TRUE, warning = FALSE, message = FALSE}

#General Descriptive Stats
report(Demo)
display(Demo)

#Gender
Gender <- Demo %>% 
  group_by(Gender) %>% 
  summarize(n = n(),
            Ratio = n() / nrow(Demo))
report(Demo$Gender)

as.data.frame(table(Demo$Gender)) %>%
  ggplot(aes(x="", y =Freq, fill = reorder(Var1, -Freq))) +
  geom_bar(width = 1, stat = "identity") +
  labs(fill = "Gender") +
  coord_polar("y", start = 0, direction = -1) +
  scale_fill_brewer(palette="Blues") +
  theme_void() +
  theme(legend.text = element_text(size = 12)) +
  theme(legend.title = element_text(face = "bold", size = 20))

#Age
Age <- Demo [-c(1),] %>% 
  summarise(mean(Age),sd(Age))
report(Demo$Age)

as.data.frame(table(Demo$Age)) %>%
  ggplot(aes(x="", y =Freq, fill = reorder(Var1, -Freq))) +
  geom_bar(width = 1, stat = "identity") +
  labs(fill = "Age") +
  coord_polar("y", start = 0, direction = 1) +
  scale_fill_brewer(palette="Oranges", breaks=c("18","19","20","21","22","24","25")) +
  theme_void() +
  theme(legend.text = element_text(size = 15)) +
  theme(legend.title = element_text(face = "bold", size = 20))

#Handedness
Handedness <- Demo %>% 
  group_by(handedness) %>% 
  summarize(n = n(),
            Ratio = n() / nrow(Demo))
report(Demo$handedness)

as.data.frame(table(Demo$handedness)) %>%
  ggplot(aes(x="", y =Freq, fill = reorder(Var1, Freq))) +
  geom_bar(width = 1, stat = "identity") +
  labs(fill = "Handedness") +
  coord_polar("y", start = 0, direction = -1) +
  scale_fill_brewer(palette="greens") +
  theme_void() +
  theme(legend.text = element_text(size = 12)) +
  theme(legend.title = element_text(face = "bold", size = 20))

#Ethnicity
as.data.frame(table(Demo$Ethnicity)) %>%
  ggplot(aes(x="", y =Freq, fill = reorder(Var1, -Freq))) +
  geom_bar(width = 1, stat = "identity") +
  labs(fill = "Ethnicity") +
  coord_polar("y", start = 0, direction = -1) +
  scale_fill_brewer(palette="Pastel1") +
  theme_void() +
  theme(legend.text = element_text(size = 12)) +
  theme(legend.title = element_text(face = "bold", size = 20))

#Religion
as.data.frame(table(Demo$Religion)) %>%
  ggplot(aes(x="", y =Freq, fill = reorder(Var1, -Freq))) +
  geom_bar(width = 1, stat = "identity") +
  labs(fill = "Religion") +
  coord_polar("y", start = 0, direction = -1) +
  scale_fill_brewer(palette="Set2") +
  theme_void() +
  theme(legend.text = element_text(size = 12)) +
  theme(legend.title = element_text(face = "bold", size = 20))

#Nationality
as.data.frame(table(Demo$Nationality)) %>%
  ggplot(aes(x="", y =Freq, fill = reorder(Var1, -Freq))) +
  geom_bar(width = 1, stat = "identity") +
  labs(fill = "Nationality") +
  coord_polar("y", start = 0, direction = -1) +
  scale_fill_brewer(palette="Set2") +
  theme_void() +
  theme(legend.text = element_text(size = 12)) +
  theme(legend.title = element_text(face = "bold", size = 20))

```

## Tasks Descriptive Statistics
Summary of Questionnaires and  Behavioural Tasks Data
```{r , include=TRUE, warning = FALSE, message = FALSE}

des_stat <- data %>% 
group_by(participant) %>% 
  summarise_all(mean) %>% 
  mutate(yoni_new = yoni_affective + yoni_cognitive) %>% 
  select(-ends_with("Total"),
          -ends_with("TotalAvg"))

#Questionnaires
descriptive_statistics(des_stat, "BES_")          #Basic Empathy/ToM
descriptive_statistics(des_stat, "MAIA")          #Interoceptive Awareness
descriptive_statistics(des_stat, "SRP3_")         #Psychopathic Traits

#Behavioural Tasks
descriptive_statistics(des_stat, "HCT") +
  facet_wrap(~Parameter, scales="free")           #Heartbeat Counting Task (Interoception)
descriptive_statistics(des_stat, "yoni_")         #Yoni Task (ToM)

#Deception Task Subjective Response Data
df_sub <- Behav %>% 
  filter(truthfulness == "LIE") %>% 
  group_by(participant, ConditionSP) %>% 
  summarise_all(mean) %>% 
  select(1,2,9) %>% 
  pivot_wider(names_from = ConditionSP, values_from = subresp) %>% 
  rename(sub_poly = polygraph,
         sub_soc = social) %>% 
  mutate(participant = as.factor(participant)) %>% 
  mutate(sub_total = (sub_poly + sub_soc)/2) %>% 
  ungroup(participant)

descriptive_statistics(df_sub, "sub_")          #Subjective Response

```

## Participants Individual Summary Results for Behavioural Tasks (Deception, HCT & Yoni Task)
```{r , include=TRUE, warning = FALSE, message = FALSE}

df_descriptive <- data %>% 
  filter(truthfulness != "TRUTH") %>% 
  group_by(participant, ConditionSP) %>% 
  summarise_all(mean)

df_descriptive <- df_descriptive %>% 
  select(c(1,2,9,36:42)) %>% 
  pivot_wider(names_from = ConditionSP, values_from = subresp) %>% 
  rename(PolyCon_subresp = polygraph,
         SociCon_subresp = social)
display(df_descriptive)

```

```{r , include=FALSE, warning = FALSE, message = FALSE}

## Plot of Average Subjective Response of Lies for Each Participant (REMOVE)
plot_desriptive <- data %>% 
  filter(truthfulness != "TRUTH") %>% 
  group_by(participant, ConditionSP) %>% 
  summarise_all(mean) %>% 
  select(c(1,2,9)) %>% 
  filter(participant != "3",
         participant != "15",
         participant != "19",
         participant != "23")

pd <- position_dodge(0.1)
plot_desriptive %>% 
  mutate(participant = as.factor(participant)) %>% 
  ggplot(aes(x = ConditionSP, y = subresp, color = participant, group=participant)) +
  geom_point(position = pd) +
  geom_line(position = pd) +
  xlab("Condition") + ylab("Subjective Response")+
  ggtitle("Plot of Average Subjective Responses for Lies")  + 
  see::theme_modern() +
  theme(plot.title = element_text(size=12))

```

## Summary of Tasks
average and SD of each task
```{r , include=TRUE, warning = FALSE, message = FALSE}
Task_summary <- data.frame(
  Mean = sapply(df_descriptive[2:ncol(df_descriptive)], mean, na.rm = TRUE),
  SD = sapply(df_descriptive[2:ncol(df_descriptive)], sd, na.rm = TRUE)
)
print(Task_summary)

```

# Correlation Matrix of all Variables
```{r , include=TRUE, warning = FALSE, message = FALSE}

df_correlation <- data %>% 
  filter(truthfulness != "TRUTH") %>% 
  filter(Condition == "R") %>% 
  select(c(1,8,50,55:90)) %>% 
  mutate(participant = as.factor(participant),
         ConditionSP = as.factor(ConditionSP))

Corr_Matrix <- correlation::correlation(
  select(df_correlation,
         participant, 
         ConditionSP, 
         subresp, 
         starts_with("ECG"), 
         starts_with("RSP"),
         starts_with("EDA")),
  multilevel = F, p_adjust = "none")

dplyr::filter(Corr_Matrix, Parameter1 == "subresp") %>% 
  arrange(desc(abs(r)))

```

# Hypothesis Analysis
## Subjective Response Comparison
Linear Mixed Model Regression

### Hypothesis 1A: Predicted Values of Subjective Response by Yoni Task
```{r , include=TRUE, warning = FALSE, message = FALSE}

df <- data %>% 
  mutate(participant = as.factor(participant),
         ConditionSP = as.factor(ConditionSP)) %>% 
  filter(truthfulness == "LIE") %>% 
  filter(Inclusion2 != "0") %>% 
  filter(participant != "3",
         participant != "15",
         participant != "19",
         participant != "23") %>% 
  filter(Condition == "Q") %>% 
  mutate(yoni_new = yoni_affective + yoni_cognitive) 
df$ConditionSP <- relevel(df$ConditionSP, ref = "social")

# TOM Hypothesis 1A: SUBRESP -> YONI
model_sub1 <- lme4::lmer(subresp ~ ConditionSP * yoni_new + (1|participant), data = df)  #explorative
parameters::parameters(model_sub1)
plot_model(model_sub1, type = "pred", terms = c("yoni_new", "ConditionSP"), axis.title = c("Yoni Task", "Subjective Response"), title = "Predicted Values of Subjective Response by Yoni Task", legend.title = "Condition") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_sub1)

```

### Hypothesis 1A: Predicted Values of Subjective Response by BES Questionnaire
```{r , include=TRUE, warning = FALSE, message = FALSE}
# TOM Hypothesis 1A: SUBRESP -> YONI/BES
model_sub2 <- lme4::lmer(subresp ~ ConditionSP * BES_Total + (1|participant), data = df)
parameters::parameters(model_sub2)
plot_model(model_sub2, type = "pred", terms = c("BES_Total", "ConditionSP"), axis.title = c("BES Questionnaire", "Subjective Response"), title = "Predicted Values of Subjective Response by BES Questionnaire", legend.title = "Condition") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_sub2)
```

### Hypothesis 1C: Predicted Values of Subjective Response by SRP3
```{r , include=TRUE, warning = FALSE, message = FALSE}
#TOM Hypothesis 1C: SUBRESP -> SRP3
model_sub3 <- lme4::lmer(subresp ~ ConditionSP * SRP3_Total + (1|participant), data = df)
parameters::parameters(model_sub3)
plot_model(model_sub3, type = "pred", terms = c("SRP3_Total", "ConditionSP"), axis.title = c("SRP3 Inventory", "Subjective Response"), title = "Predicted Values of Subjective Response by SRP3 Inventory", legend.title = "Condition") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_sub3)
```

### Hypothesis 2A: Predicted Values of Subjective Response by HCT Accuracy
```{r , include=TRUE, warning = FALSE, message = FALSE}
df$ConditionSP <- relevel(df$ConditionSP, ref = "polygraph")

#Interoception Hypothesis 2A: SUBRESP -> HCT
model_sub4 <- lme4::lmer(subresp ~ ConditionSP * HCT_Accuracy + (1|participant), data = df)
parameters::parameters(model_sub4)
plot_model(model_sub4, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"), axis.title = c("HCT Accuracy", "Subjective Response"), title = "Predicted Values of Subjective Response by HCT Accuracy", legend.title = "Condition") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_sub4)
```

### Hypothesis 2A: Predicted Values of Subjective Response by MAIA2
```{r , include=TRUE, warning = FALSE, message = FALSE}
#Interoception Hypothesis 2A: SUBRESP -> MAIA2
model_sub5 <- lme4::lmer(subresp ~ ConditionSP * MAIA_Total + (1|participant), data = df)
parameters::parameters(model_sub5)
plot_model(model_sub5, type = "pred", terms = c("MAIA_Total", "ConditionSP"), axis.title = c("MAIA2", "Subjective Response"), title = "Predicted Values of Subjective Response by MAIA2", legend.title = "Condition") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_sub5)
```

### Hypothesis 2C: Predicted Values of Subjective Response by Primary SRP3 Subfactor
```{r , include=TRUE, warning = FALSE, message = FALSE}
#Interoception Hypothesis 2C: SUBRESP -> SRP3_PRI
model_sub6 <- lme4::lmer(subresp ~ ConditionSP * SRP3_PRI + (1|participant), data = df)
parameters::parameters(model_sub6)
plot_model(model_sub6, type = "pred", terms = c("SRP3_PRI", "ConditionSP"), axis.title = c("SRP3 (PRI) Inventory", "Subjective Response"), title = "Predicted Values of Subjective Response by SRP3 (PRI)", legend.title = "Condition") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_sub6)

```

## ECG Physio scores comparison
Linear Mixed Model Regression

### Hypothesis 1A: Predicted Values of Heartrate Acceleration by Yoni Task
```{r , include=TRUE, warning = FALSE, message = FALSE}

df2 <- data %>% 
  mutate(participant = as.factor(participant),
         ConditionSP = as.factor(ConditionSP)) %>% 
  filter(truthfulness == "LIE") %>% 
  filter(Inclusion2 != "0") %>%
#  filter(participant != "22") %>% 
#  filter(participant != "23") %>%         
  filter(participant != "30") %>% 
  filter(participant != "15") %>% 
  filter(Condition == "Q") %>% 
  mutate(yoni_new = yoni_affective + yoni_cognitive) 
df2$ConditionSP <- relevel(df2$ConditionSP, ref = "social")

#ECG_RATE_MAX
#TOM Hypothesis 1A: ECG_Rate_Max -> YONI
model_ecg1 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * yoni_new + (1|participant), data = df2)  #explorative
parameters::parameters(model_ecg1)
plot_model(model_ecg1, type = "pred", terms = c("yoni_new", "ConditionSP"), axis.title = c("Yoni Task", "Heartrate Acceleration"), title = "Predicted Values of Heartrate Acceleration by Yoni Task ", legend.title = "Condition") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_ecg1)
```

### Hypothesis 1A: Predicted Values of Heartrate Acceleration by BES Questionniare
```{r , include=TRUE, warning = FALSE, message = FALSE}
#TOM Hypothesis 1A: ECG_Rate_Max -> BES
model_ecg2 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * BES_Total + (1|participant), data = df2)
parameters::parameters(model_ecg2)
plot_model(model_ecg2, type = "pred", terms = c("BES_Total", "ConditionSP"), axis.title = c("BES Questionnaire", "Heartrate Acceleration"), title = "Predicted Values of Heartrate Acceleration by BES Questionnaire", legend.title = "Condition") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_ecg2)
```

### Hypothesis 1C: Predicted Values of Heartrate Acceleration by SRP3
```{r , include=TRUE, warning = FALSE, message = FALSE}
#TOM Hypothesis 1C: ECG_Rate_Max -> SRP3
model_ecg3 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * SRP3_Total + (1|participant), data = df2)
parameters::parameters(model_ecg3)
plot_model(model_ecg3, type = "pred", terms = c("SRP3_Total", "ConditionSP"), axis.title = c("SRP3 Inventory", "Heartrate Acceleration"), title = "Predicted Values of Heartrate Acceleration by SRP3 Inventory", legend.title = "Condition") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_ecg3)
```

### Hypothesis 2A: Predicted Values of Heartrate Acceleration by HCT Accuracy
```{r , include=TRUE, warning = FALSE, message = FALSE}
df2$ConditionSP <- relevel(df2$ConditionSP, ref = "social")

#Interoception Hypothesis 2A: ECG_Rate_Max -> HCT
model_ecg4 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * HCT_Accuracy + (1|participant), data = df2)
parameters::parameters(model_ecg4)
plot_model(model_ecg4, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"), axis.title = c("HCT Accuracy", "Heartrate Acceleration"), title = "Predicted Values of Heartrate Acceleration by HCT Accuracy", legend.title = "Condition") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_ecg4)
```

### Hypothesis 2A: Predicted Values of Heartrate Acceleration by MAIA2
```{r , include=TRUE, warning = FALSE, message = FALSE}
#Interoception Hypothesis 2A: ECG_Rate_Max -> MAIA2
model_ecg5 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * MAIA_Total + (1|participant), data = df2)
parameters::parameters(model_ecg5)
plot_model(model_ecg5, type = "pred", terms = c("MAIA_Total", "ConditionSP"), axis.title = c("MAIA2", "Heartrate Acceleration"), title = "Predicted Values of Heartrate Acceleration by MAIA2", legend.title = "Condition") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_ecg5)
```

### Hypothesis 2C: Predicted Values of Heartrate Acceleration by Primary SRP3 Subfactor
```{r , include=TRUE, warning = FALSE, message = FALSE}
#Interoception Hypothesis 2C: ECG_Rate_Max -> SRP3_PRI
model_ecg6 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * SRP3_PRI + (1|participant), data = df2)
parameters::parameters(model_ecg6)
plot_model(model_ecg6, type = "pred", terms = c("SRP3_PRI", "ConditionSP"), axis.title = c("SRP3 (PRI) Inventory", "Heartrate Acceleration"), title = "Predicted Values of Heartrate Acceleration by SRP3 (PRI) ", legend.title = "Condition") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_ecg6)
```

## Correalation Analysis
### Hypothesis 1B: Correlation Between ToM and Psychopathy
```{r , include=TRUE, warning = FALSE, message = FALSE}
df5 <- data %>% 
  mutate(yoni_new = yoni_affective + yoni_cognitive) %>% 
group_by(participant) %>% 
  summarise_all(mean)

#Hypothesis 1b
##Yoni Task (1b)
model_H1 <- lm(yoni_affective ~  SRP3_Total, data = df5)
parameters::parameters(model_H1)
plot_model(model_H1, type = "pred", terms = c("SRP3_Total"), axis.title = c("SRP3 Inventory", "Yoni Task (Affective)"), title = "Relationship Between Yoni Task (Affective) and SRP3") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_H1)

correlation::correlation(select(df5,
         yoni_affective,
         SRP3_Total), method = "pearson")

##Basic Empathy Scale (1b)
model_H1a <- lm(BES_Affective ~  SRP3_Total, data = df5)
parameters::parameters(model_H1a)
plot_model(model_H1a, type = "pred", terms = ("SRP3_Total"),  axis.title = c("SRP3 Inventory", "BES (Affective)"), title = "Relationship Between BES (Affective) Score and SRP3") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_H1a)

correlation::correlation(select(df5,
         BES_Affective,
         SRP3_Total), method = "pearson")

```

### Hypothesis 2B: Correlation Between Interoception and Primary Psychopathy
```{r , include=TRUE, warning = FALSE, message = FALSE}
#Hypothesis 2b
##Heartbeat Counting Task(2b)
model_H2 <- lm(HCT_Accuracy ~  SRP3_PRI, data = df5)
parameters::parameters(model_H2)
plot_model(model_H2, type = "pred", terms = ("SRP3_PRI"), axis.title = c("SRP3 (PRI) Inventory", "HCT Accuracy"), title = "Relationship Between HCT Accuracy and SRP3 (PRI)") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_H2)

correlation::correlation(select(df5,
         HCT_Accuracy,
         SRP3_PRI), method = "pearson")

##MAIA2 (2b)
model_H2a <- lm(MAIA_Total ~  SRP3_PRI, data = df5)
parameters::parameters(model_H2)
plot_model(model_H2, type = "pred", terms = ("SRP3_PRI"), axis.title = c("SRP3 (PRI) Inventory", "MAIA2"), title = "Relationship Between MAIA2 and SRP3 (PRI)") + theme_sjplot(base_size = 10, base_family = "Times New Roman")
report(model_H2a)

correlation::correlation(select(df5,
         MAIA_Total,
         SRP3_PRI), method = "pearson")
```

### Correlation Between Yoni Task and Basic Empathy Scale
```{r , include=TRUE, warning = FALSE, message = FALSE}
#Correlation between Yoni Task and BES Scale
correlation::correlation(select(df5,
         yoni_new,
         BES_Total), method = "pearson")

correlation::correlation(select(df5,
         yoni_affective,
         BES_Affective), method = "pearson")
```

### 2021-08-26 scripts/FINAL PROCESSING/Analysis/analysis.Rmd
data

---
title: "Analysis"
output:
  word_document: default
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

# Libraries
```{r setup, include=TRUE, warning = FALSE, message = FALSE}
setwd("~/Dropbox/FYP_Jia Rong/R Processing/FINAL PROCESSING/Analysis")
library(tidyverse)
library(lme4)
library(ggplot2)
library(glmmTMB)
library(correlation)
library(sjPlot)
library(easystats)
library(report)
#library(ggpubr)

descriptive_statistics <- function(df, begins_with){
  df %>% 
    select(dplyr::starts_with(begins_with)) %>% 
    report() %>% 
    as.data.frame() %>% 
    select(-one_of(c("n_Obs", "Median", "MAD", "n_Missing"))) %>% 
    print()

  plot(df %>% 
    select(dplyr::starts_with(begins_with)) %>% 
    bayestestR::estimate_density(method = "KernSmooth") %>% 
    plot() + 
      xlab("Score") + ylab("Frequency") +
    see::theme_modern())
}

```

# Read data

```{r read_data, include=TRUE, warning = FALSE, message = FALSE}
Behav <- read.csv('BehaviouraldataNEW.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1)] %>% 
  rename(participant = ID,
         truthfulness = condition) %>% 
  mutate(ConditionSP = rep(c("social","polygraph"), each = 40, times = 30))

Behav[stringr::str_detect(names(Behav), "subresp")] <- effectsize::change_scale(Behav[stringr::str_detect(names(Behav), "subresp")], from = c(0, 1), to = c(10, -10))

Phy <- read.csv('DT.csv', stringsAsFactors = FALSE, header = TRUE) [-c(1),] %>% 
  rename(participant = Participant.number,) %>% 
  mutate(Trial = rep(1:80, each = 4, times = 30))

Phy2 <- read.csv('DT_04.csv', stringsAsFactors = FALSE, header = TRUE) [-c(1),] %>% 
  rename(participant = Participant.number,) %>% 
  mutate(Trial = rep(1:80, each = 4, times = 30))

Phy3 <- read.csv('DT_03.csv', stringsAsFactors = FALSE, header = TRUE) [-c(1),] %>% 
  rename(participant = Participant.number,) %>% 
  mutate(Trial = rep(1:80, each = 4, times = 30))

data <- merge(Behav, Phy2, by = c("participant" ,"Trial"), all = TRUE) %>% 
  arrange(participant,Trial) %>% 
  mutate(participant = as.factor(participant),
         ConditionSP = as.factor(ConditionSP))

Demo <- read.csv('demo_30.csv', stringsAsFactors = FALSE, header = TRUE)[-c(2,3,4:6,9,11,12,18)]

```

# Cleaning data

```{r cleandata, include=TRUE, warning = FALSE, message = FALSE}
data <- data %>% 
  filter(Inclusion != "0")

```

# Descriptive Statistics

## Participants Demographics Information
Summary of participants Gender, Age, and handedness
```{r , include=TRUE, warning = FALSE, message = FALSE}

#General Descriptive Stats
report(Demo)
report_participants(Demo)

Gender <- Demo %>% 
  group_by(Gender) %>% 
  summarize(n = n(),
            Ratio = n() / nrow(Demo))

Age <- Demo [-c(1),] %>% 
  summarise(mean(Age),sd(Age))
report(Demo$Age)

Handedness <- Demo %>% 
  group_by(handedness) %>% 
  summarize(n = n(),
            Ratio = n() / nrow(Demo))
report(Demo$handedness)

#Gender
as.data.frame(table(Demo$Gender)) %>%
  ggplot(aes(x="", y =Freq, fill = reorder(Var1, -Freq))) +
  geom_bar(width = 1, stat = "identity") +
  labs(fill = "Gender") +
  coord_polar("y", start = 0, direction = -1) +
  scale_fill_brewer(palette="Blues") +
  theme_void() +
  theme(legend.text = element_text(size = 12)) +
  theme(legend.title = element_text(face = "bold", size = 20))

#Age
as.data.frame(table(Demo$Age)) %>%
  ggplot(aes(x="", y =Freq, fill = reorder(Var1, -Freq))) +
  geom_bar(width = 1, stat = "identity") +
  labs(fill = "Age") +
  coord_polar("y", start = 0, direction = 1) +
  scale_fill_brewer(palette="Oranges", breaks=c("18","19","20","21","22","24","25")) +
  theme_void() +
  theme(legend.text = element_text(size = 15)) +
  theme(legend.title = element_text(face = "bold", size = 20))

#Handedness
as.data.frame(table(Demo$handedness)) %>%
  ggplot(aes(x="", y =Freq, fill = reorder(Var1, Freq))) +
  geom_bar(width = 1, stat = "identity") +
  labs(fill = "Handedness") +
  coord_polar("y", start = 0, direction = -1) +
  scale_fill_brewer(palette="greens") +
  theme_void() +
  theme(legend.text = element_text(size = 12)) +
  theme(legend.title = element_text(face = "bold", size = 20))

#Ethnicity
as.data.frame(table(Demo$Ethnicity)) %>%
  ggplot(aes(x="", y =Freq, fill = reorder(Var1, -Freq))) +
  geom_bar(width = 1, stat = "identity") +
  labs(fill = "Ethnicity") +
  coord_polar("y", start = 0, direction = -1) +
  scale_fill_brewer(palette="Pastel1") +
  theme_void() +
  theme(legend.text = element_text(size = 12)) +
  theme(legend.title = element_text(face = "bold", size = 20))

#Religion
as.data.frame(table(Demo$Religion)) %>%
  ggplot(aes(x="", y =Freq, fill = reorder(Var1, -Freq))) +
  geom_bar(width = 1, stat = "identity") +
  labs(fill = "Religion") +
  coord_polar("y", start = 0, direction = -1) +
  scale_fill_brewer(palette="Set2") +
  theme_void() +
  theme(legend.text = element_text(size = 12)) +
  theme(legend.title = element_text(face = "bold", size = 20))

#Nationality
as.data.frame(table(Demo$Nationality)) %>%
  ggplot(aes(x="", y =Freq, fill = reorder(Var1, -Freq))) +
  geom_bar(width = 1, stat = "identity") +
  labs(fill = "Nationality") +
  coord_polar("y", start = 0, direction = -1) +
  scale_fill_brewer(palette="Set2") +
  theme_void() +
  theme(legend.text = element_text(size = 12)) +
  theme(legend.title = element_text(face = "bold", size = 20))

des_stat <- data %>% 
group_by(participant) %>% 
  summarise_all(mean) %>% 
  mutate(yoni_new = yoni_affective + yoni_cognitive) %>% 
  select(-ends_with("Total"),
          -ends_with("TotalAvg"))

descriptive_statistics(des_stat, "BES_")          #Basic Empathy/ToM
descriptive_statistics(des_stat, "Lie_")          #Deceptive Tendency
descriptive_statistics(des_stat, "MAIA")          #Interoceptive Awareness
descriptive_statistics(des_stat, "SRP3_")         #Psychopathic Traits
descriptive_statistics(des_stat, "HCT") +
  facet_wrap(~Parameter, scales="free")         #Heartbeat Counting Task (Interoception)
descriptive_statistics(des_stat, "yoni_")         #Yoni Task (ToM)

df_sub <- Behav %>% 
  filter(truthfulness == "LIE") %>% 
  group_by(participant, ConditionSP) %>% 
  summarise_all(mean) %>% 
  select(1,2,9) %>% 
  pivot_wider(names_from = ConditionSP, values_from = subresp) %>% 
  rename(sub_poly = polygraph,
         sub_soc = social) %>% 
  mutate(participant = as.factor(participant)) %>% 
  mutate(sub_total = (sub_poly + sub_soc)/2) %>% 
  ungroup(participant)

descriptive_statistics(df_sub, "sub_")

```

The final sample included 30 participants (Mean age = 21.1, SD = 2.1, range: [18, 25]; 63.3% females).

## Participants Individual Summary Results for Behavioural Tasks (Deception, HCT & Yoni Task)
```{r , include=TRUE, warning = FALSE, message = FALSE}

df_descriptive <- data %>% 
  filter(truthfulness != "TRUTH") %>% 
  group_by(participant, ConditionSP) %>% 
  summarise_all(mean)

df_descriptive <- df_descriptive %>% 
  select(c(1,2,9,36:42)) %>% 
  pivot_wider(names_from = ConditionSP, values_from = subresp) %>% 
  rename(PolyCon_subresp = polygraph,
         SociCon_subresp = social)

```

##Plot of Average Subjective Response of Lies for Each Participant
```{r , include=TRUE, warning = FALSE, message = FALSE}

plot_desriptive <- data %>% 
  filter(truthfulness != "TRUTH") %>% 
  group_by(participant, ConditionSP) %>% 
  summarise_all(mean) %>% 
  select(c(1,2,9)) %>% 
  filter(participant != "3",
         participant != "15",
         participant != "19",
         participant != "23")

pd <- position_dodge(0.1)
plot_desriptive %>% 
  mutate(participant = as.factor(participant)) %>% 
  ggplot(aes(x = ConditionSP, y = subresp, color = participant, group=participant)) +
  geom_point(position = pd) +
  geom_line(position = pd) +
  xlab("Condition") + ylab("Subjective Response")+
  ggtitle("Plot of Average Subjective Responses for Lies")  + 
  see::theme_modern() +
  theme(plot.title = element_text(size=12))

```

## Summary of Tasks
average and SD of each task
```{r , include=TRUE, warning = FALSE, message = FALSE}
Summary_of_task <- data.frame(
  Mean = sapply(df_descriptive[2:ncol(df_descriptive)], mean, na.rm = TRUE),
  SD = sapply(df_descriptive[2:ncol(df_descriptive)], sd, na.rm = TRUE)
)

```

# Analysis

##Inferential (TO REMOVE)
Plot of various average Physio scores in 2 conditions
```{r , include=TRUE, warning = FALSE, message = FALSE}

Corr <- data %>% 
  filter(truthfulness != "TRUTH") %>% 
  filter(Condition == "R") %>% 
  group_by(participant, ConditionSP) %>% 
  summarise_all(mean) %>% 
  select(c(1,2,9,58,72,80))

#Plot of Average Physio Response of lies in 2 conditions
##ECG_Rate_Mean
pd <- position_dodge(0.1)
Corr %>% 
  mutate(participant = as.factor(participant)) %>% 
  ggplot(aes(x = ConditionSP, y = ECG_Rate_Mean, color = participant, group=participant)) +
  geom_point(position = pd) +
  geom_line(position = pd) +
  xlab("Condition") + ylab("Subjective Response")+
  ggtitle("Plot of ECG Rate Mean for Lies")  + 
  see::theme_modern() +
  theme(plot.title = element_text(size=12))

##RSP_Rate_Mean
Corr %>% 
  mutate(participant = as.factor(participant)) %>% 
  ggplot(aes(x = ConditionSP, y = RSP_Rate_Mean, color = participant, group=participant)) +
  geom_point(position = pd) +
  geom_line(position = pd) +
  xlab("Condition") + ylab("Subjective Response")+
  ggtitle("Plot of RSP Rate Mean for Lies")  + 
  see::theme_modern() +
  theme(plot.title = element_text(size=12))

##RSP_Amplitude_Mean
Corr %>% 
  mutate(participant = as.factor(participant)) %>% 
  ggplot(aes(x = ConditionSP, y = RSP_Amplitude_Mean, color = participant, group=participant)) +
  geom_point(position = pd) +
  geom_line(position = pd) +
  xlab("Condition") + ylab("Subjective Response")+
  ggtitle("Plot of RSP Amplitude Mean for Lies")  + 
  see::theme_modern() +
  theme(plot.title = element_text(size=12))

#Correlation of Average subjective response vs Physio + Scatterplots
#http://www.sthda.com/english/wiki/correlation-test-between-two-variables-in-r

```

#Correlation Matrix of all Variables
```{r , include=TRUE, warning = FALSE, message = FALSE}

df_correlation <- data %>% 
  filter(truthfulness != "TRUTH") %>% 
  filter(Condition == "R") %>% 
  select(c(1,8,50,55:90)) %>% 
  mutate(participant = as.factor(participant),
         ConditionSP = as.factor(ConditionSP))

Corr_Matrix <- correlation::correlation(
  select(df_correlation,
         participant, 
         ConditionSP, 
         subresp, 
         starts_with("ECG"), 
         starts_with("RSP"),
         starts_with("EDA")),
  multilevel = F, p_adjust = "none")

dplyr::filter(Corr_Matrix, Parameter1 == "subresp") %>% 
  arrange(desc(abs(r)))

```

#Hypothesis Nested Regression Analysis
##Subjective Response Comparison
```{r , include=TRUE, warning = FALSE, message = FALSE}

df <- data %>% 
  mutate(participant = as.factor(participant),
         ConditionSP = as.factor(ConditionSP)) %>% 
  filter(truthfulness == "LIE") %>% 
  filter(Inclusion2 != "0") %>% 
  filter(participant != "3",
         participant != "15",
         participant != "19",
         participant != "23") %>% 
  filter(Condition == "Q") %>% 
  mutate(yoni_new = yoni_affective + yoni_cognitive)

df$ConditionSP <- relevel(df$ConditionSP, ref = "social")

#TOM Hypothesis 1A: SUBRESP -> YONI/BES
model_sub1 <- lme4::lmer(subresp ~ ConditionSP * yoni_total + (1|participant), data = df)
parameters::parameters(model_sub1)
plot_model(model_sub1, type = "pred", terms = c("yoni_total", "ConditionSP"), axis.title = c("Yoni Task", "Subjective Response"), title = "Predicted Values of Subjective Response by Yoni Task", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_sub1)

+ font_size(title = 15, axis_title.x = 15, axis_title.y = 15) + legend_style(inside = TRUE, pos = "top right")

model_sub2 <- lme4::lmer(subresp ~ ConditionSP * yoni_new + (1|participant), data = df)  #explorative
parameters::parameters(model_sub2)
plot_model(model_sub2, type = "pred", terms = c("yoni_new", "ConditionSP"), axis.title = c("Yoni Task", "Subjective Response"), title = "Predicted Values of Subjective Response by Yoni Task", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")report(model_sub2)

model_sub3 <- lme4::lmer(subresp ~ ConditionSP * BES_Total + (1|participant), data = df)
parameters::parameters(model_sub3)
plot_model(model_sub3, type = "pred", terms = c("BES_Total", "ConditionSP"), axis.title = c("BES Questionnaire", "Subjective Response"), title = "Predicted Values of Subjective Response by BES Questionnaire", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_sub3)

model_sub4 <- lme4::lmer(subresp ~ (ConditionSP * yoni_total) + BES_Total + (1|participant), data = df)  #explorative
parameters::parameters(model_sub4)
plot_model(model_sub4, type = "pred", terms = c("yoni_total", "ConditionSP", "BES_Total"))

#TOM Hypothesis 1C: SUBRESP -> SRP3
model_sub5 <- lme4::lmer(subresp ~ ConditionSP * SRP3_Total + (1|participant), data = df)
parameters::parameters(model_sub5)
plot_model(model_sub5, type = "pred", terms = c("SRP3_Total", "ConditionSP"), axis.title = c("SRP3 Inventory", "Subjective Response"), title = "Predicted Values of Subjective Response by SRP3 Inventory", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_sub5)

model_sub6 <- lme4::lmer(subresp ~ ConditionSP * SRP3_ELS + (1|participant), data = df)  #explorative
parameters::parameters(model_sub6)
plot_model(model_sub6, type = "pred", terms = c("SRP3_ELS", "ConditionSP"), axis.title = c("SRP3 (Erratic Life Style)", "Subjective Response"), title = "Predicted Values of Subjective Response by SRP3 - ELS", legend.title = "Condition")

#Interoception Hypothesis 2A: SUBRESP -> HCT/MAIA
model_sub7 <- lme4::lmer(subresp ~ ConditionSP * HCT_Accuracy + (1|participant), data = df)
parameters::parameters(model_sub7)
plot_model(model_sub7, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"), axis.title = c("HCT Accuracy (%)", "Subjective Response"), title = "Predicted Values of Subjective Response by HCT Accuracy", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_sub7)

model_sub8 <- lme4::lmer(subresp ~ ConditionSP * MAIA_Total + (1|participant), data = df)
parameters::parameters(model_sub8)
plot_model(model_sub8, type = "pred", terms = c("MAIA_Total", "ConditionSP"), axis.title = c("MAIA2", "Subjective Response"), title = "Predicted Values of Subjective Response by MAIA2", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_sub8)

model_sub9 <- lme4::lmer(subresp ~ (ConditionSP * HCT_Accuracy) + HCT_Confidence + MAIA_Total + (1|participant), data = df)                                                                                       #explorative
parameters::parameters(model_sub9)
plot_model(model_sub9, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"))

#Interoception Hypothesis 2C: SUBRESP -> SRP3_PRI
model_sub10 <- lme4::lmer(subresp ~ ConditionSP * SRP3_PRI + (1|participant), data = df)
parameters::parameters(model_sub10)
plot_model(model_sub10, type = "pred", terms = c("SRP3_PRI", "ConditionSP"), axis.title = c("SRP3 (PRI) Inventory", "Subjective Response"), title = "Predicted Values of Subjective Response by SRP3 (PRI)", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_sub10)

```

##ECG Physio scores comparison
```{r , include=TRUE, warning = FALSE, message = FALSE}

df2 <- data %>% 
  mutate(participant = as.factor(participant),
         ConditionSP = as.factor(ConditionSP)) %>% 
  filter(truthfulness == "LIE") %>% 
  filter(Inclusion2 != "0") %>%
#  filter(participant != "22") %>% 
#  filter(participant != "23") %>%         
  filter(participant != "30") %>% 
  filter(participant != "15") %>% 
  filter(Condition == "Q") %>% 
  mutate(yoni_new = yoni_affective + yoni_cognitive)

df2$ConditionSP <- relevel(df2$ConditionSP, ref = "social")

good combo: remove 30 and 15 / dont remove 12 / use "Q"

#ECG_RATE_MAX
#TOM Hypothesis 1A: ECG_Rate_Max -> YONI/BES
model_ecg1 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * yoni_total + (1|participant), data = df2)
parameters::parameters(model_ecg1)
plot_model(model_ecg1, type = "pred", terms = c("yoni_total", "ConditionSP"), axis.title = c("Yoni Task", " Heartrate Acceleration"), title = "Predicted Values of Heartrate Acceleration by Yoni Task", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_ecg1)

model_ecg2 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * yoni_new + (1|participant), data = df2)  #explorative
parameters::parameters(model_ecg2)
plot_model(model_ecg2, type = "pred", terms = c("yoni_new", "ConditionSP"), axis.title = c("Yoni Task", "Heartrate Acceleration (beats/min)"), title = "Predicted Values of Heartrate Acceleration by Yoni Task ", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_ecg2)

model_ecg3 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * BES_Total + (1|participant), data = df2)
parameters::parameters(model_ecg3)
plot_model(model_ecg3, type = "pred", terms = c("BES_Total", "ConditionSP"), axis.title = c("BES Questionnaire", "Heartrate Acceleration (beats/min)"), title = "Predicted Values of Heartrate Acceleration by BES Questionnaire", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_ecg3)

model_ecg4 <- lme4::lmer(ECG_Rate_Max ~ (ConditionSP * yoni_total) + BES_Total + (1|participant), data = df2)
parameters::parameters(model_ecg4)
plot_model(model_ecg4, type = "pred", terms = c("yoni_total", "ConditionSP", "BES_Total"))

#TOM Hypothesis 1C: ECG_Rate_Max -> SRP3
model_ecg5 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * SRP3_Total + (1|participant), data = df2)
parameters::parameters(model_ecg5)
plot_model(model_ecg5, type = "pred", terms = c("SRP3_Total", "ConditionSP"), axis.title = c("SRP3 Inventory", "Heartrate Acceleration (beats/min)"), title = "Predicted Values of Heartrate Acceleration by SRP3 Inventory", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_ecg5)

model_ecg6 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * SRP3_ELS + (1|participant), data = df2)  #explorative
parameters::parameters(model_ecg6)
plot_model(model_ecg6, type = "pred", terms = c("SRP3_ELS", "ConditionSP"), axis.title = c("SRP3 (Erratic Life Style)", "Heartrate Acceleration"), title = "Predicted Values of Heartrate Acceleration by SRP3 - ELS", legend.title = "Condition")

df2$ConditionSP <- relevel(df2$ConditionSP, ref = "polygraph")

#Interoception Hypothesis 2A: ECG_Rate_Max -> HCT/MAIA
model_ecg7 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * HCT_Accuracy + (1|participant), data = df2)
parameters::parameters(model_ecg7)
plot_model(model_ecg7, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"), axis.title = c("HCT Accuracy (%)", "Heartrate Acceleration (beats/min)"), title = "Predicted Values of Heartrate Acceleration by HCT Accuracy", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_ecg7)

model_ecg8 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * MAIA_Total + (1|participant), data = df2)
parameters::parameters(model_ecg8)
plot_model(model_ecg8, type = "pred", terms = c("MAIA_Total", "ConditionSP"), axis.title = c("MAIA2", "Heartrate Acceleration (beats/min)"), title = "Predicted Values of Heartrate Acceleration by MAIA2", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_ecg8)

model_ecg9 <- lme4::lmer(ECG_Rate_Max ~ (ConditionSP * HCT_Accuracy) + HCT_Confidence + MAIA_Total + (1|participant), data = df2)
parameters::parameters(model_ecg9)
plot_model(model_ecg9, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"))

#Interoception Hypothesis 2C: ECG_Rate_Max -> SRP3_PRI
model_ecg10 <- lme4::lmer(ECG_Rate_Max ~ ConditionSP * SRP3_PRI + (1|participant), data = df2)
parameters::parameters(model_ecg10)
plot_model(model_ecg10, type = "pred", terms = c("SRP3_PRI", "ConditionSP"), axis.title = c("SRP3 (PRI) Inventory", "Heartrate Acceleration (beats/min)"), title = "Predicted Values of Heartrate Acceleration by SRP3 (PRI) ", legend.title = "Condition") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_ecg10)

#ONLY CA was showing good results

#ECG_RATE_MIN
#TOM Hypothesis 1A: ECG_Rate_Min -> YONI/BES
model_ecg1a <- lme4::lmer(ECG_Rate_Min ~ ConditionSP * yoni_total + (1|participant), data = df2)
parameters::parameters(model_ecg1a)
plot_model(model_ecg1a, type = "pred", terms = c("yoni_total", "ConditionSP"))

model_ecg2a <- lme4::lmer(ECG_Rate_Min ~ ConditionSP * yoni_affective + (1|participant), data = df2)  #explorative
parameters::parameters(model_ecg2a)
plot_model(model_ecg2a, type = "pred", terms = c("yoni_affective", "ConditionSP"))

model_ecg3a <- lme4::lmer(ECG_Rate_Min ~ ConditionSP * BES_Total + (1|participant), data = df2)
parameters::parameters(model_ecg3a)
plot_model(model_ecg3a, type = "pred", terms = c("BES_Total", "ConditionSP"))

model_ecg4a <- lme4::lmer(ECG_Rate_Min ~ (ConditionSP * yoni_total) + BES_Total + (1|participant), data = df2)
parameters::parameters(model_ecg4a)
plot_model(model_ecg4a, type = "pred", terms = c("yoni_total", "ConditionSP", "BES_Total"))

#TOM Hypothesis 1C: ECG_Rate_Min -> SRP3
model_ecg5a <- lme4::lmer(ECG_Rate_Min ~ ConditionSP * SRP3_Total + (1|participant), data = df2)
parameters::parameters(model_ecg5a)
plot_model(model_ecg5a, type = "pred", terms = c("SRP3_Total", "ConditionSP"))

model_ecg6a <- lme4::lmer(ECG_Rate_Min ~ ConditionSP * SRP3_ELS + (1|participant), data = df2)  #explorative
parameters::parameters(model_ecg6a)
plot_model(model_ecg6a, type = "pred", terms = c("SRP3_ELS", "ConditionSP"))

#Interoception Hypothesis 2A: ECG_Rate_Min -> HCT/MAIA
model_ecg7a <- lme4::lmer(ECG_Rate_Min ~ ConditionSP * HCT_Accuracy + (1|participant), data = df2)
parameters::parameters(model_ecg7a)
plot_model(model_ecg7a, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"))

model_ecg8a <- lme4::lmer(ECG_Rate_Min ~ ConditionSP * MAIA_Total + (1|participant), data = df2)
parameters::parameters(model_ecg8a)
plot_model(model_ecg8, type = "pred", terms = c("MAIA_Total", "ConditionSP"))

model_ecg9a <- lme4::lmer(ECG_Rate_Min ~ (ConditionSP * HCT_Accuracy) + HCT_Confidence + MAIA_Total + (1|participant), data = df2)
parameters::parameters(model_ecg9a)
plot_model(model_ecg9, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"))

#Interoception Hypothesis 2C: ECG_Rate_Min -> SRP3_PRI
model_ecg10a <- lme4::lmer(ECG_Rate_Min ~ ConditionSP * SRP3_PRI + (1|participant), data = df2)
parameters::parameters(model_ecg10a)
plot_model(model_ecg10a, type = "pred", terms = c("SRP3_PRI", "ConditionSP"))

```

##RESPIRATION PHYSIO ANALYSIS
```{r , include=TRUE, warning = FALSE, message = FALSE}

df3 <- data %>% 
  mutate(participant = as.factor(participant),
         ConditionSP = as.factor(ConditionSP)) %>% 
  filter(truthfulness == "LIE") %>% 
  filter(Inclusion2 != "0") %>% 
  filter(participant != "22") %>% 
    filter(Condition == "Q")
#  filter(participant != "23") %>% 
  # filter(participant != "30") %>% 
  # filter(#participant != "12",            #try keep 15
  #        participant != "15") %>%

#RSP_Amplitude_Max
#TOM Hypothesis 1A: RSP_Amplitude_Max -> YONI/BES
model_rsp1 <- lme4::lmer(RSP_Amplitude_Max ~ ConditionSP * yoni_total + (1|participant), data = df3)
parameters::parameters(model_rsp1)
plot_model(model_rsp1, type = "pred", terms = c("yoni_total", "ConditionSP"))

model_rsp2 <- lme4::lmer(RSP_Amplitude_Max ~ ConditionSP * yoni_affective + (1|participant), data = df3)  #explorative
parameters::parameters(model_rsp2)
plot_model(model_rsp2, type = "pred", terms = c("yoni_affective", "ConditionSP"))

model_rsp3 <- lme4::lmer(RSP_Amplitude_Max ~ ConditionSP * BES_Total + (1|participant), data = df3)
parameters::parameters(model_rsp3)
plot_model(model_rsp3, type = "pred", terms = c("BES_Total", "ConditionSP"))

model_rsp4 <- lme4::lmer(RSP_Amplitude_Max ~ (ConditionSP * yoni_total) + BES_Total + (1|participant), data = df3)
parameters::parameters(model_rsp4)
plot_model(model_rsp4, type = "pred", terms = c("yoni_total", "ConditionSP", "BES_Total"))

#TOM Hypothesis 1C: RSP_Amplitude_Max -> SRP3
model_rsp5 <- lme4::lmer(RSP_Amplitude_Max ~ ConditionSP * SRP3_Total + (1|participant), data = df3)
parameters::parameters(model_rsp5)
plot_model(model_rsp5, type = "pred", terms = c("SRP3_Total", "ConditionSP"))

model_rsp6 <- lme4::lmer(RSP_Amplitude_Max ~ ConditionSP * SRP3_ELS + (1|participant), data = df3)  #explorative
parameters::parameters(model_rsp6)
plot_model(model_rsp6, type = "pred", terms = c("SRP3_ELS", "ConditionSP"))

#Interoception Hypothesis 2A: RSP_Amplitude_Max -> HCT/MAIA
model_rsp7 <- lme4::lmer(RSP_Amplitude_Max ~ ConditionSP * HCT_Accuracy + (1|participant), data = df3)
parameters::parameters(model_rsp7)
plot_model(model_rsp7, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"))

model_rsp8 <- lme4::lmer(RSP_Amplitude_Max ~ ConditionSP * MAIA_Total + (1|participant), data = df3)
parameters::parameters(model_rsp8)
plot_model(model_rsp8, type = "pred", terms = c("MAIA_Total", "ConditionSP"))

model_rsp9 <- lme4::lmer(RSP_Amplitude_Max ~ (ConditionSP * HCT_Accuracy) + HCT_Confidence + MAIA_Total + (1|participant), data = df3)
parameters::parameters(model_rsp9)
plot_model(model_rsp9, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"))

#Interoception Hypothesis 2C: RSP_Amplitude_Max -> SRP3_PRI
model_rsp10 <- lme4::lmer(RSP_Amplitude_Max ~ ConditionSP * SRP3_PRI + (1|participant), data = df3)
parameters::parameters(model_rsp10)
plot_model(model_rsp10, type = "pred", terms = c("SRP3_PRI", "ConditionSP"))

```

##EDA_SCR
```{r , include=TRUE, warning = FALSE, message = FALSE}

  df4 <- data %>% 
  mutate(participant = as.factor(participant),
         ConditionSP = as.factor(ConditionSP)) %>% 
  filter(truthfulness == "LIE") %>% 
  filter(Inclusion2 != "0") %>% 
  filter(participant != "22") %>% 
  filter(participant != "4",
         participant != "5",
         participant != "10",
         participant != "12",
         participant != "16",
         participant != "23",
         participant != "27",
         participant != "29") %>% 
  filter(Condition == "C")

#  filter(participant != "23") %>% 
#  filter(participant != "30") %>%

#TOM Hypothesis 1A: EDA_SCR -> YONI/BES
model_eda1 <- lme4::lmer(EDA_SCR ~ ConditionSP * yoni_total + (1|participant), data = df4)
parameters::parameters(model_eda1)
plot_model(model_eda1, type = "pred", terms = c("yoni_total", "ConditionSP"))

model_eda2 <- lme4::lmer(EDA_SCR ~ ConditionSP * yoni_affective + (1|participant), data = df4)  #explorative
parameters::parameters(model_eda2)
plot_model(model_eda2, type = "pred", terms = c("yoni_affective", "ConditionSP"))

model_eda3 <- lme4::lmer(EDA_SCR ~ ConditionSP * BES_Total + (1|participant), data = df4)
parameters::parameters(model_eda3)
plot_model(model_eda3, type = "pred", terms = c("BES_Total", "ConditionSP"))

model_eda4 <- lme4::lmer(EDA_SCR ~ (ConditionSP * yoni_total) + BES_Total + (1|participant), data = df4)
parameters::parameters(model_eda4)
plot_model(model_eda4, type = "pred", terms = c("yoni_total", "ConditionSP", "BES_Total"))

#TOM Hypothesis 1C: EDA_SCR -> SRP3
model_eda5 <- lme4::lmer(EDA_SCR ~ ConditionSP * SRP3_Total + (1|participant), data = df4)
parameters::parameters(model_eda5)
plot_model(model_eda5, type = "pred", terms = c("SRP3_Total", "ConditionSP"))

model_eda6 <- lme4::lmer(EDA_SCR ~ ConditionSP * SRP3_ELS + (1|participant), data = df4)  #explorative
parameters::parameters(model_eda6)
plot_model(model_eda6, type = "pred", terms = c("SRP3_ELS", "ConditionSP"))

#Interoception Hypothesis 2A: EDA_SCR -> HCT/MAIA
model_eda7 <- lme4::lmer(EDA_SCR ~ ConditionSP * HCT_Accuracy + (1|participant), data = df4)
parameters::parameters(model_eda7)
plot_model(model_eda7, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"))

model_eda8 <- lme4::lmer(EDA_SCR ~ ConditionSP * MAIA_Total + (1|participant), data = df4)
parameters::parameters(model_eda8)
plot_model(model_eda8, type = "pred", terms = c("MAIA_Total", "ConditionSP"))

model_eda9 <- lme4::lmer(EDA_SCR ~ (ConditionSP * HCT_Accuracy) + HCT_Confidence + MAIA_Total + (1|participant), data = df4)
parameters::parameters(model_eda9)
plot_model(model_eda9, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"))

#Interoception Hypothesis 2C: EDA_SCR -> SRP3_PRI
model_eda10 <- lme4::lmer(EDA_SCR ~ ConditionSP * SRP3_PRI + (1|participant), data = df4)
parameters::parameters(model_eda10)
plot_model(model_eda10, type = "pred", terms = c("SRP3_PRI", "ConditionSP"))

```

## Correalation Analysis
```{r , include=TRUE, warning = FALSE, message = FALSE}

df5 <- data %>% 
  mutate(yoni_new = yoni_affective + yoni_cognitive) %>% 
group_by(participant) %>% 
  summarise_all(mean)

model_H1 <- lm(yoni_affective ~  SRP3_Total, data = df5)
parameters::parameters(model_H1)
plot_model(model_H1, type = "pred", terms = c("SRP3_Total"), axis.title = c("SRP3 Inventory", "Yoni Task (Affective)"), title = "Relationship Between Yoni Task (Affective) and SRP3") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_H1)

correlation::correlation(select(df5,
         yoni_affective,
         SRP3_Total), method = "pearson")

model_H1a <- lm(BES_Affective ~  SRP3_Total, data = df5)
parameters::parameters(model_H1a)
plot_model(model_H1a, type = "pred",  axis.title = c("SRP3 Inventory", "BES (Affective)"), title = "Relationship Between BES (Affective) Score and SRP3") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_H1a)

correlation::correlation(select(df5,
         BES_Affective,
         SRP3_Total), method = "pearson")

model_H2 <- lm(HCT_Accuracy ~  SRP3_PRI, data = df5)
parameters::parameters(model_H2)
plot_model(model_H2, type = "pred", axis.title = c("SRP3 (PRI) Inventory", "HCT Accuracy"), title = "Relationship Between HCT Accuracy and SRP3 (PRI)") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_H2)

correlation::correlation(select(df5,
         HCT_Accuracy,
         SRP3_PRI), method = "pearson")

model_H2a <- lm(MAIA_Total ~  SRP3_PRI, data = df5)
parameters::parameters(model_H2)
plot_model(model_H2, type = "pred", axis.title = c("SRP3 (PRI) Inventory", "MAIA2"), title = "Relationship Between MAIA2 and SRP3 (PRI)") + theme_sjplot(base_size = 25, base_family = "Times New Roman")
report(model_H2a)

correlation::correlation(select(df5,
         MAIA_Total,
         SRP3_PRI), method = "pearson")

correlation::correlation(select(df5,
         yoni_new,
         BES_Total), method = "pearson")

correlation::correlation(select(df5,
         yoni_affective,
         BES_Affective), method = "pearson")

correlation::correlation(select(df5,
         HCT_Accuracy,
         MAIA_Total), method = "pearson")
```

An interaction is present when the effects of one IV on DV change at the different levels of the second IV.
the +ve effect of the HCT_Accuracy on the subjective response varies on the different level of the ConditionSP. The rate of change of HCT_Accuracy on the subjective response in the polygraph condition is larger than the rate of change of HCT_Accuracy on the subjective response in the social condition.

Interaction EXPLANATION
- ConditionSP - differences between social and poly condition when HCTACCuracy is 0
- HCTAccuracy (poly condition as 0) - only in polygraph condition, there is a positive effect of HCT_Accuracy on sub resp but not significant
- interaction - participants who have a better HCTAccur (interoceptive ability) have better confidence on their lies in the poly condition compared to social condition

# Other Analysis
```{r , include=TRUE, warning = FALSE, message = FALSE}

```

### 2021-08-26 scripts/Demogaphics/Demo Code.R

@@ -1,0 +1,295 @@
+#### HP3804 EFA in RStudio =====================================  (stats generated factors)
+# install the following 4 packages before you can run the commands below:
+#foreign is for reading spss
+#psych is for efa
+#gpa rotation is for factor rotation
+#hmisc is for some factor analysis
+install.packages("foreign")
+install.packages("psych")
+install.packages("GPArotation")
+install.packages("Hmisc")
+install.packages("tidyverse")
+install.packages("ggplot2")
+install.packages("bayestestR")
+install.packages("see")
+install.packages("stringr")
+
+# Load required packages
+library(foreign)
+library(psych)
+library(GPArotation)
+library(Hmisc)
+library(tidyverse)
+library(ggplot2)
+library(bayestestR)
+library(see)
+library(stringr)
+
+# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
+setwd("  ")
+setwd("~/Desktop/R Testing")
+
+
+
+#**********YONI TASK Code Processing************************************
+# read SPSS fa_eg.sav
+# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
+setwd("~/Dropbox/FYP_Jia Rong/R Processing/Demogaphics")
+library(tidyverse)
+library(stringr)
+
+
+
+mydata <- read.csv('demo.csv', stringsAsFactors = FALSE)[-c(1:2), -c(1:17, 30, 32, 34,36)] 
+
+mydata <- mydata %>% 
+  rename(Name = Q2,
+         ID = Q3,
+         Matric = Q4,
+         HP = Q5,
+         Email = Q6,
+         Gender = Q7,
+         Age = Q8,
+         Birthday = Q9,
+         handedness = Q10,
+         School = Q11,
+         Course = Q12,
+         Polyjc = Q13,
+         Ethnicity = Q14,
+         Religion = Q15,
+         Nationality = Q16,
+         RaisedinSG = Q17,
+         LivedinSG = Q18) %>% 
+  mutate(ID = as.numeric(ID)) %>% 
+  arrange(ID)
+
+write.csv(mydata, file = "demo_30.csv")
+
[…]

### 2021-08-26 scripts/FINAL PROCESSING/Analysis/Analysis Code.R

@@ -1,0 +1,88 @@
+#### HP3804 EFA in RStudio =====================================  (stats generated factors)
+# install the following 4 packages before you can run the commands below:
+#foreign is for reading spss
+#psych is for efa
+#gpa rotation is for factor rotation
+#hmisc is for some factor analysis
+install.packages("foreign")
+install.packages("psych")
+install.packages("GPArotation")
+install.packages("Hmisc")
+install.packages("tidyverse")
+install.packages("ggplot2")
+install.packages("bayestestR")
+install.packages("see")
+install.packages("psycho")
+install.packages("lme4")
+install.packages("rstatix")
+install.packages("glmer")
+
+# Load required packages
+library(foreign)
+library(psych)
+library(GPArotation)
+library(Hmisc)
+library(tidyverse)
+library(ggplot2)
+library(bayestestR)
+library(see)
+
+# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
+setwd("  ")
+setwd("~/Desktop/R Testing")
+
+
+
+#**********YONI TASK Code Processing************************************
+# read SPSS fa_eg.sav
+# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
+setwd("~/Dropbox/FYP_Jia Rong/R Processing/FINAL PROCESSING")
+library(tidyverse)
+library(lme4)
+#library(rstatix)
+
+#LOAD DATA
+Behav <- read.csv('Behaviouraldata.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1)] %>% 
+  rename(participant = ID) %>% 
+  mutate(Trial = rep(1:80, 30))
+
+Phy <- read.csv('DT.csv', stringsAsFactors = FALSE, header = TRUE) [-c(1),] %>% 
+  rename(participant = Participant.number) %>% 
+  mutate(Trial = rep(1:80, each = 4, times = 30))
+
+#Phy <- Phy[!(Phy$Participant == 1 & Phy$Label == 3),]
+
+data <- merge(Behav, Phy, by = c("participant" ,"Trial"), all = TRUE) %>% 
+  arrange(participant,Trial)
+
+#REMOVE ERROR TRIALS IN PARTICIPANTS
+
+
[…]

### 2021-08-26 scripts/FINAL PROCESSING/Analysis/Old Codes.R

@@ -1,0 +1,608 @@
+
+#Regression models
+##Subjective Response Comparison
+df <- data %>% 
+  mutate(participant = as.factor(participant),
+         ConditionSP = as.factor(ConditionSP)) %>% 
+  filter(truthfulness == "LIE") %>% 
+  filter(participant != "3",
+         participant != "15",
+         participant != "19",
+         participant != "23")
+
+#report(model)
+#summary(model)
+
+#subresp = ConditionSP(X1) + Yoni_Task(X2) + HCT_Accuracy(X3) (3-way interaction)
+model_sub1 <- lme4::lmer(subresp ~ ConditionSP * yoni_total * HCT_Accuracy + (1|participant), data = df)
+parameters::parameters(model_sub1)
+plot_model(model_sub1, type = "pred", terms = c("HCT_Accuracy", "yoni_total", "ConditionSP"))
+
+#subresp = ConditionSP(X1) + Yoni_Task(X2) + HCT_Accuracy(X3) (3-way interaction)
+model_sub2 <- lme4::lmer(subresp ~ ConditionSP * (yoni_total + HCT_Accuracy) + (1|participant), data = df)
+parameters::parameters(model_sub2)
+plot_model(model_sub2, type = "pred", terms = c("yoni_total", "HCT_Accuracy", "ConditionSP"))
+
+#Interoception (HCT)
+#subresp = ConditionSP(X1) + HCT_Accuracy(X2) (Interaction)
+model_sub3 <- lme4::lmer(subresp ~ ConditionSP * HCT_Accuracy + (1|participant), data = df)
+parameters::parameters(model_sub3)
+plot_model(model_sub3, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"))
+
+model_sub4 <- lme4::lmer(subresp ~ ConditionSP * MAIA_Total + (1|participant), data = df)
+parameters::parameters(model_sub4)
+plot_model(model_sub4, type = "pred", terms = c("MAIA_Total", "ConditionSP"))
+
+model_sub5 <- lme4::lmer(subresp ~ (ConditionSP * HCT_Accuracy) + HCT_Confidence + HCT_Awareness + MAIA_Total + (1|participant), data = df)
+parameters::parameters(model_sub5)
+plot_model(model_sub5, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"))
+
[…]

### 2021-08-26 scripts/FINAL PROCESSING/FInal Code.R

@@ -1,0 +1,333 @@
+#### HP3804 EFA in RStudio =====================================  (stats generated factors)
+# install the following 4 packages before you can run the commands below:
+#foreign is for reading spss
+#psych is for efa
+#gpa rotation is for factor rotation
+#hmisc is for some factor analysis
+install.packages("foreign")
+install.packages("psych")
+install.packages("GPArotation")
+install.packages("Hmisc")
+install.packages("tidyverse")
+install.packages("ggplot2")
+install.packages("bayestestR")
+install.packages("see")
+install.packages("psycho")
+install.packages("lme4")
+install.packages("rstatix")
+install.packages("glmer")
+
+# Load required packages
+library(foreign)
+library(psych)
+library(GPArotation)
+library(Hmisc)
+library(tidyverse)
+library(ggplot2)
+library(bayestestR)
+library(see)
+
+# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
+setwd("  ")
+setwd("~/Desktop/R Testing")
+
+
+
+#**********YONI TASK Code Processing************************************
+# read SPSS fa_eg.sav
+# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
+setwd("~/Dropbox/FYP_Jia Rong/R Processing/FINAL PROCESSING")
+library(tidyverse)
+library(lme4)
+library(rstatix)
+
+BES <- read.csv('BES_30processed.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1)]
+LIE <- read.csv('lieprofiler_30.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1,2)]
+MAIA <- read.csv('MAIA2_30processed.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1,2)]
+SRP3 <- read.csv('SRP3_30processed.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1,2)]
+YONI <- read.csv('yonitask_30processed.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1,2)]
+HCT <- read.csv('HCTdata.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1,2)]
[…]

### 2021-08-26 scripts/Yoni task processing in R/Yoni task Response Code.R

@@ -1,0 +1,217 @@
+#### HP3804 EFA in RStudio =====================================  (stats generated factors)
+# install the following 4 packages before you can run the commands below:
+#foreign is for reading spss
+#psych is for efa
+#gpa rotation is for factor rotation
+#hmisc is for some factor analysis
+install.packages("foreign")
+install.packages("psych")
+install.packages("GPArotation")
+install.packages("Hmisc")
+install.packages("tidyverse")
+install.packages("ggplot2")
+install.packages("bayestestR")
+install.packages("see")
+
+# Load required packages
+library(foreign)
+library(psych)
+library(GPArotation)
+library(Hmisc)
+library(tidyverse)
+library(ggplot2)
+library(bayestestR)
+library(see)
+
+# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
+setwd("  ")
+setwd("~/Desktop/R Testing")
+
+
+
+#**********YONI TASK Code Processing************************************
+# read SPSS fa_eg.sav
+# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
+setwd("~/Dropbox/FYP_Jia Rong/R Processing/Yoni task processing in R")
+library(tidyverse)
+
+mydata <- data.frame()
+for (participant in list.files("../../data/")) {
+  df_sub <- read.csv(paste0("../../data/", participant, "/yoni/", participant, "_untitled.csv"))[-c(1:3,28,61, 104), -c(4,5, 7:38, 42:47 )]
+    mydata <- rbind(mydata, df_sub)
+}
+
+results <- mydata %>% 
+  rename(response = mouse_2.clicked_name,
+         responsetime = mouse_2.time) %>% 
+  mutate(answer = ifelse(correct == response, 1, 0))
+
+total_score <- results %>% 
+  group_by(participant, condition) %>% 
+  summarise(total = sum(answer)) %>% 
+  pivot_wider(names_from = condition, values_from = total) %>% 
+  mutate(yoni_total = affect+cognitive+physical) %>% 
+  rename(yoni_affective = affect,
[…]

### 2021-08-26 scripts/heartbeat task processing in R/HCT Code.R

@@ -1,0 +1,342 @@
+#### HP3804 EFA in RStudio =====================================  (stats generated factors)
+# install the following 4 packages before you can run the commands below:
+#foreign is for reading spss
+#psych is for efa
+#gpa rotation is for factor rotation
+#hmisc is for some factor analysis
+install.packages("foreign")
+install.packages("psych")
+install.packages("GPArotation")
+install.packages("Hmisc")
+install.packages("tidyverse")
+install.packages("ggplot2")
+install.packages("bayestestR")
+install.packages("see")
+install.packages("stringr")
+
+# Load required packages
+library(foreign)
+library(psych)
+library(GPArotation)
+library(Hmisc)
+library(tidyverse)
+library(ggplot2)
+library(bayestestR)
+library(see)
+library(stringr)
+
+# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
+setwd("  ")
+setwd("~/Desktop/R Testing")
+
+
+
+#**********YONI TASK Code Processing************************************
+# read SPSS fa_eg.sav
+# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
+setwd("~/Dropbox/FYP_Jia Rong/R Processing/heartbeat task processing in R")
+library(tidyverse)
+library(stringr)
+
+
+
+mydata <- data.frame()
+for (participant in list.files("../../data/")) {
+  df_sub <- read.csv(paste0("../../data/", participant, "/heartbeat/", participant, "_heartbeat.csv"))[-c(6:9), -c(1, 3:8, 12:31, 33:38)]  
+    mydata <- rbind(mydata, df_sub)
+}
+
+
+mydata <- mydata %>% 
+rename(hbcount = heartbeatresponse.text,
+       confidence = confidenceslider.response,
+       confidenceRT = confidenceslider.rt)
+      # guess = key_guess.keys,
+      # guessRT = key_guess.rt,
+      # noguess = key_noguess.keys,
+     #  noguessRT = key_noguess.rt,
+     #  onebreath = key_noguess_perturbed.keys,
[…]

### 2021-09-01 scripts/claudia/data processing.Rmd
data extraction
for yoni, bes, hct and maia2

```{r load packages}
library(tidyverse)
```

```{r tom obj yoni}
rm(list=ls())
cat("\014")

mydata <- data.frame()
for (participant in list.files("../../data/data_experimental")) {
  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/yoni/", participant, "_untitled.csv"))[-c(1:3,28,61,104), -c(4,5,7:38,42:47)]
  mydata <- rbind(mydata, df_sub)
}

data <- mydata %>% 
  rename(response = mouse_2.clicked_name,
         responsetime = mouse_2.time) %>% 
  mutate(answer = ifelse(correct == response, 1, 0))

results <- data %>%
  group_by(participant, condition) %>%
  summarise(total = sum(answer)) %>%
  pivot_wider(names_from = condition, values_from = total) %>%
  mutate(yoni_total = affect+cognitive+physical) %>%
  rename(yoni_affective = affect,
         yoni_cognitive = cognitive,
         yoni_physical = physical,
         ID = participant)

write.csv(data, file = "yonitask_extracted.csv", row.names=FALSE)
write.csv(results, file = "yonitask_processed.csv", row.names=FALSE)
```

```{r tom subj bes}
rm(list=ls())
cat("\014")

mydata <- read.csv("../../data/data_questionnaire/BES.csv", stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]

results <- mydata %>% 
  rename(Q1 = Q3_1,
       Q2 = Q3_2,
       Q3 = Q3_3,
       Q4 = Q3_4,
       Q5 = Q3_5,
       Q6 = Q3_6,
       Q7 = Q3_7,
       Q8 = Q3_8,
       Q9 = Q3_9,
       Q10 = Q3_10,
       Q11 = Q3_11,
       Q12 = Q3_12,
       Q13 = Q3_13,
       Q14 = Q3_14,
       Q15 = Q3_15,
       Q16 = Q3_16,
       Q17 = Q3_17,
       Q18 = Q3_18,
       Q19 = Q3_19,
       Q20 = Q3_20,
       ID = Q2) %>%

  mutate(Q1 = recode(Q1, "1" = "5", "2" = "4", "4" = "2", "5" = "1"),
    Q6 = recode(Q6, "1" = "5", "2" = "4", "4" = "2", "5" = "1"),
    Q7 = recode(Q7, "1" = "5", "2" = "4", "4" = "2", "5" = "1"),
    Q8 = recode(Q8, "1" = "5", "2" = "4", "4" = "2", "5" = "1"),
    Q13 = recode(Q13, "1" = "5", "2" = "4", "4" = "2", "5" = "1"),
    Q18 = recode(Q18, "1" = "5", "2" = "4", "4" = "2", "5" = "1"),
    Q19 = recode(Q19, "1" = "5", "2" = "4", "4" = "2", "5" = "1"),
    Q20 = recode(Q20, "1" = "5", "2" = "4", "4" = "2", "5" = "1")) %>%

  mutate(Q1 = as.numeric(Q1), Q2 = as.numeric(Q2), Q3 = as.numeric(Q3), Q4 = as.numeric(Q4), 
         Q5 = as.numeric(Q5), Q6 = as.numeric(Q6), Q7 = as.numeric(Q7), Q8 = as.numeric(Q8), 
         Q9 = as.numeric(Q9), Q10 = as.numeric(Q10), Q11 = as.numeric(Q11), Q12 = as.numeric(Q12), 
         Q13 = as.numeric(Q13), Q14 = as.numeric(Q14), Q15 = as.numeric(Q15), Q16 = as.numeric(Q16),
         Q17 = as.numeric(Q17), Q18 = as.numeric(Q18), Q19 = as.numeric(Q19), Q20 = as.numeric(Q20)) %>%

  mutate(BES_Cognitive = Q3+Q6+Q9+Q10+Q12+Q14+Q16+Q19+Q20) %>% 
  mutate(BES_Affective = Q1+Q2+Q4+Q5+Q7+Q8+Q11+Q13+Q15+Q17+Q18) %>% 
  mutate(BES_Total = BES_Cognitive+BES_Affective) %>%

  arrange(ID)

write.csv(results, file = "BES_processed.csv", row.names=FALSE)
```

```{r int obj heartbeat}
rm(list=ls())
cat("\014")

mydata <- data.frame()
for (participant in list.files("../../data/data_experimental")) {
  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/heartbeat/", participant, "_heartbeat.csv"))[-c(6:9), -c(1, 3:8, 12:31, 33:38)]  
  mydata <- rbind(mydata, df_sub)
}

data <- mydata %>% 
  rename(hbcount_reported = heartbeatresponse.text,
       HCT_confidence = confidenceslider.response,
       HCT_confidenceRT = confidenceslider.rt,
       ID = participant) %>%

  select(ID, everything()) %>% #move ID column to front

  mutate(hbcount_reported = str_remove_all(hbcount_reported, "Enter Number")) %>% 
  mutate(hbcount_reported = as.numeric(hbcount_reported)) %>% 
  mutate(HCT_confidence = str_replace_all(HCT_confidence, "None", "0")) %>% 
  mutate(HCT_confidenceRT = str_replace_all(HCT_confidenceRT, "None", "0")) %>% 
  mutate(HCT_confidence = as.numeric(HCT_confidence)) %>%

  arrange(ID, time)

HCT <- read.csv("../heartbeat/HCT.csv", stringsAsFactors = FALSE)[-c(2,8:10)] %>% 
  rename(participant = Participant.number) %>%
  pivot_longer(!participant, names_to = "task", values_to = "hbcount_real")
data <- cbind(data, HCT)

data <- data %>% 
  select(-c(participant, task)) %>% 
  mutate(numerator = hbcount_real - hbcount_reported) %>% 
  mutate(numerator = abs(numerator)) %>% 
  mutate(denominator = (hbcount_real + hbcount_reported)/2) %>% 
  mutate(HCT_accuracy = 1 - numerator/denominator)

df_awareness <- data.frame()
for(participant in unique(data$ID)) {
  conf <- data[data$ID == participant, "HCT_confidence"]
  acc <- data[data$ID == participant, "HCT_accuracy"]
  awa <- cor(conf, acc, use = "pairwise.complete.obs")
  df_awareness <- rbind(df_awareness,
                       data.frame(ID = participant,
                                  HCT_awareness = awa))
}

data <- merge(data, df_awareness, by = "ID")
results <- data %>% 
  select(c(ID, HCT_confidence, HCT_accuracy, HCT_awareness)) %>% 
  group_by(ID) %>%
  summarise_all(mean, na.rm = TRUE)

write.csv(data, file = "HCT_extracted.csv", row.names=FALSE)
write.csv(results, file = "HCT_processed.csv", row.names=FALSE)
```

```{r int subj maia2}
rm(list=ls())
cat("\014")

mydata <- read.csv('../../data/data_questionnaire/MAIA2.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]

results <- mydata %>% 
  rename(Q1 = Q3_1,
       Q2 = Q3_2,
       Q3 = Q3_3,
       Q4 = Q3_4,
       Q5 = Q3_5,
       Q6 = Q3_6,
       Q7 = Q3_7,
       Q8 = Q3_8,
       Q9 = Q3_9,
       Q10 = Q3_10,
       Q11 = Q3_11,
       Q12 = Q3_12,
       Q13 = Q3_13,
       Q14 = Q3_14,
       Q15 = Q3_15,
       Q16 = Q3_16,
       Q17 = Q3_17,
       Q18 = Q3_18,
       Q19 = Q3_19,
       Q20 = Q3_20,
       Q21 = Q4_1,
       Q22 = Q4_2,
       Q23 = Q4_3,
       Q24 = Q4_4,
       Q25 = Q4_5,
       Q26 = Q4_6,
       Q27 = Q4_7,
       Q28 = Q4_8,
       Q29 = Q4_9,
       Q30 = Q4_10,
       Q31 = Q4_11,
       Q32 = Q4_12,
       Q33 = Q4_13,
       Q34 = Q4_14,
       Q35 = Q4_15,
       Q36 = Q4_16,
       Q37 = Q4_17,
       ID = Q2) %>%

  mutate(Q5 = recode(Q5, "0" = "5", "1" = "4", "2" = "3", "3" = "2", "4" = "1", "5" = "0"),
    Q6 = recode(Q6, "0" = "5", "1" = "4", "2" = "3", "3" = "2", "4" = "1", "5" = "0"),
    Q7 = recode(Q7, "0" = "5", "1" = "4", "2" = "3", "3" = "2", "4" = "1", "5" = "0"),
    Q8 = recode(Q8, "0" = "5", "1" = "4", "2" = "3", "3" = "2", "4" = "1", "5" = "0"),
    Q9 = recode(Q9, "0" = "5", "1" = "4", "2" = "3", "3" = "2", "4" = "1", "5" = "0"),
    Q10 = recode(Q10, "0" = "5", "1" = "4", "2" = "3", "3" = "2", "4" = "1", "5" = "0"),
    Q11 = recode(Q11, "0" = "5", "1" = "4", "2" = "3", "3" = "2", "4" = "1", "5" = "0"),
    Q12 = recode(Q12, "0" = "5", "1" = "4", "2" = "3", "3" = "2", "4" = "1", "5" = "0"),
    Q15 = recode(Q15, "0" = "5", "1" = "4", "2" = "3", "3" = "2", "4" = "1", "5" = "0")) %>%

  mutate(Q1 = as.numeric(Q1), Q2 = as.numeric(Q2), Q3 = as.numeric(Q3), Q4 = as.numeric(Q4),
         Q5 = as.numeric(Q5), Q6 = as.numeric(Q6), Q7 = as.numeric(Q7), Q8 = as.numeric(Q8),
         Q9 = as.numeric(Q9), Q10 = as.numeric(Q10), Q11 = as.numeric(Q11), Q12 = as.numeric(Q12),
         Q13 = as.numeric(Q13), Q14 = as.numeric(Q14), Q15 = as.numeric(Q15), Q16 = as.numeric(Q16),
         Q17 = as.numeric(Q17), Q18 = as.numeric(Q18), Q19 = as.numeric(Q19), Q20 = as.numeric(Q20),
         Q21 = as.numeric(Q21), Q22 = as.numeric(Q22), Q23 = as.numeric(Q23), Q24 = as.numeric(Q24),
         Q25 = as.numeric(Q25), Q26 = as.numeric(Q26), Q27 = as.numeric(Q27), Q28 = as.numeric(Q28),
         Q29 = as.numeric(Q29), Q30 = as.numeric(Q30), Q31 = as.numeric(Q31), Q32 = as.numeric(Q32),
         Q33 = as.numeric(Q33), Q34 = as.numeric(Q34), Q35 = as.numeric(Q35), Q36 = as.numeric(Q36),
         Q37 = as.numeric(Q37)) %>%

  mutate(MAIA1 = (Q1+Q2+Q3+Q4)/4, MAIA2 = (Q5+Q6+Q7+Q8+Q9+Q10)/6, MAIA3 = (Q11+Q12+Q13+Q14+Q15)/5, MAIA4 = (Q16+Q17+Q18+Q19+Q20+Q21+Q22)/7,
        MAIA5 = (Q23+Q24+Q25+Q26+Q27)/5, MAIA6 = (Q28+Q29+Q30+Q31)/4, MAIA7 = (Q32+Q33+Q34)/3, MAIA8 = (Q35+Q36+Q37)/3) %>% 
  mutate(MAIA_Total = (MAIA1+MAIA2+MAIA3+MAIA4+MAIA5+MAIA6+MAIA7+MAIA8)/8) %>%

  arrange(ID)

write.csv(results, file = "MAIA2_processed.csv", row.names=FALSE)
```

### 2021-09-10 1_descriptive.Rmd
started on descriptive

---
output: html_document
editor_options: 
  chunk_output_type: console
---

## Part 1

Here's a cool plot:

```{r 1_plot_scatter_basic, warning=FALSE, message=FALSE, fig.heiht=figheight, fig.width=figwidth, dpi=150}
ggplot(df, aes(x=V1, y=V2, color=Participant)) + 
  geom_point() +
  see::theme_modern()
```

## Part 2

That's another great plot:

```{r 1_plot_density, warning=FALSE, message=FALSE, fig.heiht=figheight, fig.width=figwidth, dpi=150}
plot(bayestestR::estimate_density(df[c("V1", "V2")])) +
  see::theme_blackboard()
```

## Part 3

```{r}
ggplot(df, aes(yoni_total)) + geom_histogram()
ggplot(df, aes(BES_total)) + geom_histogram()
ggplot(df, aes(yoni_total, BES_total)) + geom_point()
ggplot(df, aes(HCT_accuracy)) + geom_histogram()
ggplot(df, aes(MAIA_total)) + geom_histogram()
ggplot(df, aes(HCT_accuracy, MAIA_total)) + geom_point()
```

### 2021-09-10 index.Rmd
started on descriptive

---
title: '**Results Template**'
subtitle: A Subtitle
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: yes
    toc_depth: 3
    toc_float: yes
    number_sections: no
    df_print: kable
    code_folding: hide
    code_download: yes
  word_document:
    reference_docx: utils/Template_Word.docx
    highlight: pygments
    toc: no
    toc_depth: 3
    df_print: kable
    number_sections: yes
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '2'
    latex_engine: xelatex
editor_options:
  chunk_output_type: console
bibliography: utils/bibliography.bib
csl: utils/apa.csl
---

<!-- 
!!!! IMPORTANT: run `source("utils/render.R")` to publish instead of clicking on 'Knit'
-->

```{r setup, warning=FALSE, message=TRUE, include=FALSE}
# Set up the environment (or use local alternative `source("utils/config.R")`)
source("https://raw.githubusercontent.com/RealityBending/TemplateResults/main/utils/config.R")

fast <- FALSE  # Make this false to skip the chunks
```

# Introduction

```{r badges, echo=FALSE, message=TRUE, warning=FALSE, results='asis'}
# This chunk is a bit complex so don't worry about it: it's made to add badges to the HTML versions
# NOTE: You have to replace the links accordingly to have working "buttons" on the HTML versions
if (!knitr::is_latex_output() && knitr::is_html_output()) {
  cat("![Build](https://github.com/RealityBending/TemplateResults/workflows/Build/badge.svg)
      [![Website](https://img.shields.io/badge/repo-Readme-2196F3)](https://github.com/RealityBending/TemplateResults)
      [![Website](https://img.shields.io/badge/visit-website-E91E63)](https://realitybending.github.io/TemplateResults/)
      [![Website](https://img.shields.io/badge/download-.docx-FF5722)](https://github.com/RealityBending/TemplateResults/raw/main/word_and_pdf/SupplementaryMaterials.docx)
      [![Website](https://img.shields.io/badge/see-.pdf-FF9800)](https://github.com/RealityBending/TemplateResults/blob/main/word_and_pdf/SupplementaryMaterials.pdf)")
}
```

This is a template for a data analysis folder that can be easily exported as a [**webpage**](https://realitybending.github.io/TemplateResults/) or as **Supplementary Materials** (e.g., as a [**Word document**](https://github.com/RealityBending/TemplateResults/raw/main/word_and_pdf/SupplementaryMaterials.docx) or a [**PDF**](https://github.com/RealityBending/TemplateResults/blob/main/word_and_pdf/SupplementaryMaterials.pdf)).

How does it look like? Just like this! The README page of this repository, alongside the [webpage](https://realitybending.github.io/TemplateResults/) and the word and PDF documents, were all created from the [index.Rmd](https://github.com/RealityBending/TemplateResults/blob/main/index.Rmd) file.

This means you can easily **share your data analysis**, either by attaching the *PDF* or *Word* file to the publication (as **Supplementary Materials**), or by directly providing the URL of your GitHub repository: the readers can then enjoy your awesome open-access work in a convenient and transparent way.

## Features

- [x] Automatically generates different types of document:
  - [**README page**](https://github.com/RealityBending/TemplateResults/blob/main/README.md)
  - [**Published website**](https://realitybending.github.io/TemplateResults/)
  - [**Word document**](https://github.com/RealityBending/TemplateResults/raw/main/word_and_pdf/SupplementaryMaterials.docx)
  - [**PDF document**](https://github.com/RealityBending/TemplateResults/blob/main/word_and_pdf/SupplementaryMaterials.pdf)
- [x] APA citations
- [x] Automatic citations and [reference list](https://github.com/RealityBending/TemplateResults#package-references) for all packages
- [x] Tidy organisation (separate files for independent analyses)
- [x] Great default configuration
- [x] And more!

```{r demo_gif, echo=FALSE, message=TRUE, warning=FALSE}
# Let's include a demo GIF (this doesn't work in PDF documents)
if (!knitr::is_latex_output()) {
  knitr::include_graphics("figures/demo.gif")
}
```

## Installation

- **What is this?**

This repository is a template to set up a reproducible, convenient and shareable workflow for your data analysis. It consists of several [*Rmarkdown*](https://rmarkdown.rstudio.com/lesson-1.html) files (`.Rmd`), that allow you to have R code and text (markdown) in the same document. Importantly, these files can be transformed into other documents formats.

- **How to use this template?**

Download it ([**click here to download**](https://github.com/RealityBending/TemplateResults/archive/main.zip)), unzip it and edit.
Alternatively, you click on the [**Use this template**](https://github.com/RealityBending/TemplateResults/generate) button at the top of this screen to create a GitHub repository with all the content copied (then you just need to clone the repo to your local machine).

The main files you need to edit are the `.Rmd` files, that you can open with some editor (e.g., [Rstudio](https://rstudio.com/)), and edit the text and the R chunks of code.

- **How to upload it to a website?**

If your repo is not already connected to GitHub, then create a new repository and upload all the content (so that it looks like this repo). Then, go to settings of the repo and enable **GitHub pages** (i.e., that gives you a webpage from an html stored on GitHub), and select the `docs/` folder as the location of the webpage. Indeed, rendering (knitting) the files will generate an "index.html" file in the `/docs/` folder, which is used as the website. You can see an example at [https://realitybending.github.io/TemplateResults/](https://realitybending.github.io/TemplateResults/).

- **To knit or not to knit**

In this repo, with have set up a [GitHub action](https://github.com/RealityBending/TemplateResults/blob/main/.github/workflows/website.yml) that generates all the output files everytime someone commit to the repository. This means that the final documents here are always "up-to-date" with the *Rmds* (as shown by the green badge). That said, you can remove this GitHub action (just remove the `.github/workflows/website.yml` file) if you prefer to generate the documents manually only.

- **But I don't want do upload all my data**

In that case, you'll need to 1) deactivate (i.e., remove the action file) the automatic rendering by GitHub (as no data will be stored on GitHub) and 2) mark the **data** folder as "to be ignored" (so that it won't be uploaded). This can be done by adding `/data/` to the [**.gitignore**](https://github.com/RealityBending/TemplateResults/blob/main/.gitignore) file (that you can open with a notepad). This means that you can still store the data here locally, and generate the documents accordingly, but the data folder will be ignored by git and never uploaded to GitHub. This way, you can still have a cool website, an open-access script, but the data is safe with you. The only down side is that you have to build it manually (cannot use GitHub actions).

- **How to add references?**

References have to be added in `bib` format in the [*utils/bibliography.bib*](https://github.com/RealityBending/TemplateResults/blob/main/utils/bibliography.bib) file, and further referenced in the text like this `[@ludecke2019insight]` [@ludecke2019insight].

- **I don't like the Word (.docx) theme**

The theme for the word document is defined in the [**Template_Word.docx](https://github.com/RealityBending/TemplateResults/tree/main/utils) file, in the `/utils/` folder. You need to edit the "styles" (not just the content, but the style itself) to your preference.

- **I have Python code**

Thanks to R's possibilities when it comes to integration with Python, it's super easy to enable it in your pipeline. Just uncomment the [Python installation line](https://github.com/RealityBending/TemplateResults/blob/main/utils/config.R#L24) in the `utils/config.R` file and you're ready to go!

- **It doesn't work / I have questions / I have ideas**

Just [**open an issue**](https://github.com/RealityBending/TemplateResults/issues) and we'll be happy to assist ☺

## Structure

Most files that you'll need to create / edit will be written in [**rmarkdown**](https://rmarkdown.rstudio.com/lesson-1.html), which consists of a mix of markdown text and R chunks of code.

The main file is named [**index.Rmd**](https://github.com/RealityBending/TemplateResults/blob/main/index.Rmd). However, to avoid having overly long files, the different (and independent) analyses parts are actually split in other documents. For instance, in this template example, the descriptive statistics section is in the [**1_descriptive.Rmd**](https://github.com/RealityBending/TemplateResults/blob/main/1_descriptive.Rmd) file. As you can [see in the index file](https://github.com/RealityBending/TemplateResults/blob/690f7947da0fc8ac85eaf6fb87fafeaa46fb3c50/index.Rmd#L89-L90), this file is then integrated as a child document (i.e., it is merged). This makes it very convenient to have a clear structure with well-organized files, that are put together only when merged.

## Render and Publish

Importantly, in order to render all the files, do not Knit this document by pressing the 'Knit' button. If you do, it will create an output file (for instance `index.html`) in the root folder, alongside `index.Rmd`. This is **not what we want**, as we want to keep the output files tidy in separate folders (for instance, the html version should be in the `/docs/` folder, as this is where the website will look for).

There an R script, [utils/render.R](https://github.com/RealityBending/TemplateResults/blob/main/utils/render.R), that contains the lines to render everything in its correct location. So, when you have the "index.Rmd" file opened (and your working directory is at its root), simply run **`source("utils/render.R")`** in the console (or the relevant lines in that file). This will run the rendering file and create all the files.

## Contribution

Do not hesitate to improve this template by updating, documenting, or expanding it!

# Packages & Data

## Packages

This document was prepared on `r format(Sys.Date())`.

```{r warning=FALSE, message=TRUE, results='asis'}
library(bayestestR)
library(parameters)
library(performance)
library(report)
library(see)
library(ggplot2)

summary(report::report(sessionInfo()))
```

## Data

```{r warning=FALSE, message=TRUE, results='asis'}
df <- read.csv("data/data_combined.csv")

cat(paste("The data consists of",
          report::report_participants(df,
                                      participants = "ID",
                                      sex = "Gender",
                                      age = "Age")))
```

Note that the chunks generating figures in the code below have some arguments specified in their header, such as `fig.width` and `fig.height`, which controls the figure size. These were filled with an eponym argument defined in [`utils/config.R`](https://github.com/RealityBending/TemplateResults/blob/main/utils/config.R#L26-L27). We also set the resolution, i.e., `dpi`, to a low value so that the resulting file is lighter. But **don't forget to crank this value up** (to 300-600) to get nice-looking results.

# Descriptive Stats {.tabset}

Notice the `{.tabset}` tag after the section name. This will show the subsections as different tabs (in the [html version](https://realitybending.github.io/TemplateResults/#Descriptive_Stats) only, because the other formats are static).

```{r child=if (fast == FALSE) '1_descriptive.Rmd'}
```

# Inferential Stats

```{r child=if (fast == FALSE) '2_inferential.Rmd'}
```

# Full Code

The full script of executive code contained in this document is reproduced here.

```{r full_code, ref.label=knitr::all_labels(), eval=FALSE}
```

# Package References

```{r warning=FALSE, message=FALSE, results='asis'}
report::cite_packages(sessionInfo())
```

# References

### 2021-09-10 scripts/claudia/data processing.Rmd
started on descriptive

@@
 library(tidyverse)
+```
+
+```{r demo}
+rm(list=ls())
+cat("\014")
+
+mydata <- read.csv('../../data/data_questionnaire/Demographics.csv', stringsAsFactors = FALSE)[-c(1:2), -c(1:17, 30, 32, 34, 36)]
+
+mydata <- mydata %>% 
+  rename(Name = Q2,
+         ID = Q3,
+         Matric = Q4,
+         HP = Q5,
+         Email = Q6,
+         Gender = Q7,
+         Age = Q8,
+         Birthday = Q9,
+         handedness = Q10,
+         School = Q11,
+         Course = Q12,
+         Polyjc = Q13,
+         Ethnicity = Q14,
+         Religion = Q15,
+         Nationality = Q16,
+         RaisedinSG = Q17,
+         LivedinSG = Q18) %>% 
+  mutate(ID = as.numeric(ID)) %>% 
+  arrange(ID)
+
+write.csv(mydata, file = "demo.csv", row.names = FALSE)
 ```
@@
 
-write.csv(data, file = "yonitask_extracted.csv", row.names=FALSE)
-write.csv(results, file = "yonitask_processed.csv", row.names=FALSE)
+write.csv(data, file = "yoni_extracted.csv", row.names=FALSE)
+write.csv(results, file = "yoni_processed.csv", row.names=FALSE)
 ```
@@
 
-  mutate(BES_Cognitive = Q3+Q6+Q9+Q10+Q12+Q14+Q16+Q19+Q20) %>% 
-  mutate(BES_Affective = Q1+Q2+Q4+Q5+Q7+Q8+Q11+Q13+Q15+Q17+Q18) %>% 
-  mutate(BES_Total = BES_Cognitive+BES_Affective) %>%
+  mutate(BES_cognitive = Q3+Q6+Q9+Q10+Q12+Q14+Q16+Q19+Q20) %>% 
+  mutate(BES_affective = Q1+Q2+Q4+Q5+Q7+Q8+Q11+Q13+Q15+Q17+Q18) %>% 
+  mutate(BES_total = BES_cognitive+BES_affective) %>%
 
@@
   summarise_all(mean, na.rm = TRUE)
+
+parttwo <- data.frame()
+for (participant in list.files("../../data/data_experimental")) {
+  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/heartbeat/", participant, "_heartbeat.csv"))[-c(1:5, 9), -c(1:13, 16:19, 22:25, 28:31, 33:38)]  
+  parttwo <- rbind(parttwo, df_sub)
+}
+
+parttwo <- parttwo %>% 
+  rename(guess = key_guess.keys,
+         guessRT = key_guess.rt,
+         noguess = key_noguess.keys,
+         noguessRT = key_noguess.rt,
+         onebreath = key_noguess_perturbed.keys,
+         onebreathRT = key_noguess_perturbed.rt,
+         ID = participant) %>% 
+  group_by(ID) %>% 
+  summarise_all(funs(trimws(paste(., collapse = ''))))
+
+parttwo <- parttwo %>% 
+  mutate(HCT_guess = str_count(parttwo$guess, "space")) %>% 
+  mutate(HCT_noguess = str_count(parttwo$noguess, "space")) %>% 
+  mutate(HCT_onebreath = str_count(parttwo$onebreath, "space")) %>% 
+  select(c(ID, HCT_guess, HCT_noguess, HCT_onebreath))
+
+results <- left_join(results, parttwo)
 
@@
         MAIA5 = (Q23+Q24+Q25+Q26+Q27)/5, MAIA6 = (Q28+Q29+Q30+Q31)/4, MAIA7 = (Q32+Q33+Q34)/3, MAIA8 = (Q35+Q36+Q37)/3) %>% 
-  mutate(MAIA_Total = (MAIA1+MAIA2+MAIA3+MAIA4+MAIA5+MAIA6+MAIA7+MAIA8)/8) %>%
+  mutate(MAIA_total = (MAIA1+MAIA2+MAIA3+MAIA4+MAIA5+MAIA6+MAIA7+MAIA8)/8) %>%
 
@@
 ```
+
+```{r deception}
+
+```
+
+```{r merge all}
+data_combined <- read.csv("demo.csv") %>% 
+  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG)) %>% 
+  left_join(read.csv("yoni_processed.csv")) %>% 
+  left_join(read.csv("BES_processed.csv")) %>% 
+  select(-c(contains("Q"))) %>% 
+  left_join(read.csv("HCT_processed.csv")) %>% 
+  left_join(read.csv("MAIA2_processed.csv")) %>% 
+  select(-c(contains("Q")))
+
+write.csv(data_combined, file = "../../data/data_combined.csv", row.names = FALSE)
+```

### 2021-09-16 scripts/claudia/data processing.Rmd
data extraction
deception task

@@
 
-```{r deception}
+```{r deception subj}
+rm(list=ls())
+cat("\014")
 
+mydata <- data.frame()
+for (participant in list.files("../../data/data_experimental")) {
+  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), -c(5:34, 37:46, 48:54)]  
+  mydata <- rbind(mydata, df_sub)
+}
+
+data <- mydata %>% 
+  rename(item = V1,
+       style = V2,
+       condition = V3,
+       question = V4,
+       subresp = V35,
+       RT = V36,
+       ID = V47) %>%
+
+  mutate(subresp = str_replace_all(subresp, "None", "0")) %>% 
+  mutate(RT = str_replace_all(RT, "None", "0")) %>% 
+  mutate(subresp = as.numeric(subresp)) %>% 
+  mutate(RT = as.numeric(RT)) %>% 
+  mutate(condition = as.factor(condition)) %>% 
+  mutate(ID = as.numeric(ID))
+
+results <- data %>% 
+  group_by(ID, condition, style) %>% 
+  summarise(DT_SubjAvg = mean(subresp), DT_RTAvg = mean(RT)) %>% 
+  group_by(ID, condition) %>% 
+  mutate(DT_TotalAvg = mean(DT_SubjAvg), TotalRT = mean(DT_RTAvg)) %>% 
+  rename(DT_condition = condition,
+         DT_style = style)
+
+write.csv(data, file = "deceptiontask_extracted.csv", row.names=FALSE)
+write.csv(results, file = "deceptiontask_processed.csv", row.names=FALSE)
 ```
@@
   left_join(read.csv("MAIA2_processed.csv")) %>% 
-  select(-c(contains("Q")))
+  select(-c(contains("Q"))) %>% 
+  right_join(read.csv("deceptiontask_processed.csv"))
 

### 2021-09-16 scripts/claudia/data processing.Rmd
deception task
data combined to include 80 trials, trial number, condition, inclusion

--- 2021-09-10 scripts/claudia/data processing.Rmd
@@
+```{r clear everything}
+rm(list=ls())
+cat("\014")
+```
+
 ```{r load packages}
@@
          Birthday = Q9,
-         handedness = Q10,
+         Handedness = Q10,
          School = Q11,
@@
   rename(response = mouse_2.clicked_name,
-         responsetime = mouse_2.time) %>% 
-  mutate(answer = ifelse(correct == response, 1, 0))
+         responseRT = mouse_2.time,
+         ID = participant) %>% 
+  mutate(answer = ifelse(correct == response, 1, 0)) %>% 
+  select(ID, everything()) #move ID column to front
 
 results <- data %>%
-  group_by(participant, condition) %>%
+  group_by(ID, condition) %>%
   summarise(total = sum(answer)) %>%
@@
          yoni_cognitive = cognitive,
-         yoni_physical = physical,
-         ID = participant)
+         yoni_physical = physical)
 
@@
   mutate(hbcount_reported = as.numeric(hbcount_reported)) %>% 
-  mutate(HCT_confidence = str_replace_all(HCT_confidence, "None", "0")) %>% 
-  mutate(HCT_confidenceRT = str_replace_all(HCT_confidenceRT, "None", "0")) %>% 
   mutate(HCT_confidence = as.numeric(HCT_confidence)) %>%
@@
 
-```{r deception}
+```{r deception subj}
+rm(list=ls())
+cat("\014")
 
+mydata <- data.frame()
+for (participant in list.files("../../data/data_experimental")) {
+  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), -c(5:34, 37:46, 48:54)] %>% 
+    mutate(DT_trial = c(1:80)) %>% 
+    mutate(DT_condition = c(rep("Social", 40), rep("Polygraph", 40)))
+  mydata <- rbind(mydata, df_sub)
+}
+
+inclusion <- read.csv("../final_processing/Errors.csv") %>%
+  rename(ID = ï..participant,
+         DT_trial = Trial,
+         inclusion = Inclusion,
+         inclusion2 = Inclusion2)
+
+data <- mydata %>% 
+  rename(DT_item = V1,
+       DT_style = V2,
+       DT_instruction = V3,
+       DT_question = V4,
+       DT_confidence = V35,
+       DT_confidenceRT = V36,
+       ID = V47) %>%
+
+  mutate(DT_confidence = as.numeric(DT_confidence)) %>% 
+  mutate(DT_confidenceRT = as.numeric(DT_confidenceRT)) %>% 
+  mutate(DT_instruction = as.factor(DT_instruction)) %>% 
+  mutate(ID = as.numeric(ID)) %>% 
+  left_join(inclusion) %>%
+
+  select(ID, DT_trial, DT_condition, inclusion, inclusion2, everything()) #move columns to front
+
+results <- data %>% 
+  group_by(ID, DT_instruction, DT_style) %>% 
+  summarise(DT_confidence_avg = mean(DT_confidence), DT_confidenceRT_avg = mean(DT_confidenceRT))
+
+write.csv(data, file = "deceptiontask_extracted.csv", row.names=FALSE)
+write.csv(results, file = "deceptiontask_processed.csv", row.names=FALSE)
 ```
 
-```{r merge all}
-data_combined <- read.csv("demo.csv") %>% 
-  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG)) %>% 
+```{r combine data}
+data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
   left_join(read.csv("yoni_processed.csv")) %>% 
@@
   left_join(read.csv("MAIA2_processed.csv")) %>% 
-  select(-c(contains("Q")))
+  select(-c(contains("Q"))) %>% 
+  left_join(read.csv("demo.csv")) %>% 
+  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG))
 

### 2021-09-27 1_descriptive.Rmd
lmer and descriptive (dt)

@@
 
-```{r}
+```{r independent var}
 ggplot(df, aes(yoni_total)) + geom_histogram()
@@
 ```
+
+```{r dependent var}
+ggplot(df, aes(instruction, DT_confidence)) + geom_boxplot()
+ggplot(df, aes(instruction, DT_confidenceRT)) + geom_boxplot()
+ggplot(df, aes(condition, DT_confidence)) + geom_boxplot()
+ggplot(df, aes(condition, DT_confidenceRT)) + geom_boxplot()
+```
+
+```{r}
+df.social <- df %>% filter(condition == 'Social')
+ggplot(df.social, aes(yoni_total, DT_confidence_avg)) + geom_point()
+ggplot(df.social, aes(BES_total, DT_confidence_avg)) + geom_point()
+
+df.polyg <- df %>% filter(condition == 'Polygraph')
+ggplot(df.polyg, aes(HCT_accuracy, DT_confidence_avg)) + geom_point()
+ggplot(df.polyg, aes(MAIA_total, DT_confidence_avg)) + geom_point()
+```

### 2021-09-27 2_inferential.Rmd
lmer and descriptive (dt)

---
output: html_document
editor_options: 
  chunk_output_type: console
---

Here is another analysis that is contained in a separate file. Let's check-out this linear regression model (note that, in the code chunk parameters, I multiplied `figheight` by 2 to have a taller plot):

```{r 2_plot_model, warning=FALSE, message=FALSE, fig.heiht=figheight * 2, fig.width=figwidth, dpi=150}
model <- lm(Petal.Length ~ Sepal.Length, data=iris)
performance::check_model(model)
```

```{r}
y.var <- c('DT_confidence', 'DT_confidence', 'DT_confidenceRT')
x.var <- c('DT_confidenceRT', 'condition*instruction', 'condition*instruction')

for (i in seq_along(y.var)){
  for (j in seq_along(x.var)){
    if (i==j){
      model <- lmer(paste(y.var[i],' ~', x.var[j],' + (1|ID) + (1|item) + (1|trial)'), df)
      print(report(model))
      print(parameters(model, effects = "fixed"))
      if (grepl('\\*', x.var[j]) == TRUE){
        p <- interactions::cat_plot(model, pred = instruction, modx = condition)
      }
      else{
        viz_data <- estimate_relation(model)
        p <- ggplot(data = viz_data, aes(x = DT_confidenceRT, y = Predicted)) +
          geom_line() +
          geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3) +
          geom_point(data = df, aes(x = DT_confidenceRT, y = DT_confidence, color = ID))
      }
      print(p)
    }
  }
}
```

```{r}
model <- lmer(DT_confidence ~ DT_confidenceRT + (1|ID) + (1|item) + (1|trial), df)
report(model)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model)
p <- ggplot(data = viz_data, aes(x = DT_confidenceRT, y = Predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3) +
  geom_point(data = df, aes(x = DT_confidenceRT, y = DT_confidence, color = ID))
p
#R2 does not account for random effects
#weirdly significant given the plot
#what's the include_random thing (6.5 vs 6.7)
```

```{r}
model <- lmer(DT_confidence ~ condition*instruction + (1|ID) + (1|item) + (1|trial), df)
report(model)
parameters(model, effects = "fixed")
interactions::cat_plot(model, pred = instruction, modx = condition)
#R2 does not account for random effects
#interaction is significant
```

```{r}
model <- lmer(DT_confidenceRT ~ condition*instruction + (1|ID) + (1|item) + (1|trial), df)
#actually this is not the reaction time? it's the reaction time to the question of how confident
```

### 2021-09-27 index.Rmd
lmer and descriptive (dt)

@@
 library(ggplot2)
+library(lme4)
+library(modelbased)
 

### 2021-09-27 scripts/claudia/data processing.Rmd
lmer and descriptive (dt)

@@
   df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), -c(5:34, 37:46, 48:54)] %>% 
-    mutate(DT_trial = c(1:80)) %>% 
-    mutate(DT_condition = c(rep("Social", 40), rep("Polygraph", 40)))
+    mutate(trial = c(1:80)) %>% 
+    mutate(condition = c(rep("Social", 40), rep("Polygraph", 40)))
   mydata <- rbind(mydata, df_sub)
@@
   rename(ID = ï..participant,
-         DT_trial = Trial,
+         trial = Trial,
          inclusion = Inclusion,
@@
 data <- mydata %>% 
-  rename(DT_item = V1,
-       DT_style = V2,
-       DT_instruction = V3,
-       DT_question = V4,
+  rename(item = V1,
+       style = V2,
+       instruction = V3,
+       question = V4,
        DT_confidence = V35,
@@
   mutate(DT_confidenceRT = as.numeric(DT_confidenceRT)) %>% 
-  mutate(DT_instruction = as.factor(DT_instruction)) %>% 
+  mutate(instruction = as.factor(instruction)) %>% 
   mutate(ID = as.numeric(ID)) %>% 
@@
 
-  select(ID, DT_trial, DT_condition, inclusion, inclusion2, everything()) #move columns to front
+  select(ID, trial, condition, inclusion, inclusion2, everything()) #move columns to front
 
 results <- data %>% 
-  group_by(ID, DT_instruction, DT_style) %>% 
+  group_by(ID, instruction, style) %>% 
   summarise(DT_confidence_avg = mean(DT_confidence), DT_confidenceRT_avg = mean(DT_confidenceRT))
@@
 data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
+  left_join(read.csv("deceptiontask_processed.csv")) %>% 
   left_join(read.csv("yoni_processed.csv")) %>% 

### 2021-09-28 1_descriptive.Rmd
dt rt

--- 2021-09-10 1_descriptive.Rmd
@@
 ```
+
+```{r dependent var}
+ggplot(df, aes(instruction, DT_RT)) + geom_boxplot()
+ggplot(df, aes(instruction, DT_confidence)) + geom_boxplot()
+ggplot(df, aes(condition, DT_RT)) + geom_boxplot()
+ggplot(df, aes(condition, DT_confidence)) + geom_boxplot()
+```
+
+```{r}
+df %>% 
+  group_by(ID, condition, instruction) %>% 
+  summarise(confidence = mean(DT_confidence, na.rm = TRUE),
+            yoni_total = mean(yoni_total, na.rm = TRUE)) %>% #create a new df for plot
+  ggplot(aes(x = yoni_total, y = confidence, colour = instruction)) +
+  geom_point() +
+  geom_smooth(method = "lm") + 
+  facet_wrap(~condition)
+```

### 2021-09-28 2_inferential.Rmd
dt rt

@@
 ```{r}
-model <- lmer(DT_confidence ~ condition*instruction + (1|ID) + (1|item) + (1|trial), df)
+model <- lmer(DT_confidence ~ condition*instruction + (1|ID) + (1|item), df)
 report(model)
@@
 interactions::cat_plot(model, pred = instruction, modx = condition)
+means <- modelbased::estimate_means(model, at = c("condition", "instruction"))
+means
+contrasts <- modelbased::estimate_contrasts(model, contrast = c("condition", "instruction"))
+ggplot(means, aes(x = instruction, y = Mean, colour = condition)) + 
+  geom_line(aes(group = condition)) +
+  geom_pointrange(aes(ymin = CI_low, ymax= CI_high))
 #R2 does not account for random effects
 #interaction is significant
+performance::performance(model)
 ```

### 2021-09-28 index.Rmd
dt rt

--- 2021-09-10 index.Rmd
@@
 library(see)
-library(ggplot2)
+library(tidyverse)
+library(lme4)
+library(modelbased)
 

### 2021-09-28 scripts/claudia/data processing.Rmd
dt rt

@@
 for (participant in list.files("../../data/data_experimental")) {
-  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), -c(5:34, 37:46, 48:54)] %>% 
+  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), c(1:4, 29, 31, 35, 36, 43, 45, 47)] %>% 
     mutate(trial = c(1:80)) %>% 
@@
        question = V4,
+       social_start = V29,
+       social_stop = V31,
        DT_confidence = V35,
        DT_confidenceRT = V36,
+       polyg_start = V43,
+       polyg_stop = V45,
        ID = V47) %>%
@@
   mutate(DT_confidence = as.numeric(DT_confidence)) %>% 
-  mutate(DT_confidenceRT = as.numeric(DT_confidenceRT)) %>% 
   mutate(instruction = as.factor(instruction)) %>% 
+  mutate(social_start = as.numeric(social_start)) %>% 
+  mutate(social_stop = as.numeric(social_stop)) %>% 
+  mutate(polyg_start = as.numeric(polyg_start)) %>% 
+  mutate(polyg_stop = as.numeric(polyg_stop)) %>% 
   mutate(ID = as.numeric(ID)) %>%
+  mutate(DT_RT = ifelse(condition == "Social", social_stop - social_start,
+         ifelse(condition == "Polygraph", polyg_stop - polyg_start, NA))) %>%
+
   left_join(inclusion) %>%
-
   select(ID, trial, condition, inclusion, inclusion2, everything()) #move columns to front
@@
   group_by(ID, instruction, style) %>%
-  summarise(DT_confidence_avg = mean(DT_confidence), DT_confidenceRT_avg = mean(DT_confidenceRT))
+  summarise(DT_RT_avg = mean(DT_RT, na.rm = TRUE),
+            DT_confidence_avg = mean(DT_confidence, na.rm = TRUE))
 
@@
 data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
-  left_join(read.csv("deceptiontask_processed.csv")) %>% 
+  select(-c(contains("start")|contains("stop"))) %>% 
   left_join(read.csv("yoni_processed.csv")) %>% 

### 2021-10-07 1_descriptive.Rmd
descriptive and interaction models
condition*instruction
style*instruction

--- 2021-09-10 1_descriptive.Rmd
@@
 ```{r}
-ggplot(df, aes(yoni_total)) + geom_histogram()
-ggplot(df, aes(BES_total)) + geom_histogram()
-ggplot(df, aes(yoni_total, BES_total)) + geom_point()
-ggplot(df, aes(HCT_accuracy)) + geom_histogram()
-ggplot(df, aes(MAIA_total)) + geom_histogram()
-ggplot(df, aes(HCT_accuracy, MAIA_total)) + geom_point()
+df.plot <- df %>% 
+  group_by(ID, condition, instruction) %>% 
+  summarise(confidence = mean(DT_confidence, na.rm = TRUE),
+            RT = mean(DT_RT, na.rm = TRUE),
+            yoni_total = mean(yoni_total, na.rm = TRUE),
+            BES_total = mean(BES_total, na.rm = TRUE),
+            HCT_accuracy = mean(HCT_accuracy, na.rm = TRUE),
+            MAIA_total = mean(MAIA_total, na.rm = TRUE))
 ```
+
+```{r independent var}
+ggplot(df.plot, aes(yoni_total)) + geom_histogram()
+ggplot(df.plot, aes(BES_total)) + geom_histogram()
+ggplot(df.plot, aes(yoni_total, BES_total)) + geom_point()
+ggplot(df.plot, aes(HCT_accuracy)) + geom_histogram()
+ggplot(df.plot, aes(MAIA_total)) + geom_histogram()
+ggplot(df.plot, aes(HCT_accuracy, MAIA_total)) + geom_point()
+```
+
+```{r dependent var}
+ggplot(df, aes(DT_confidence)) + geom_density()
+ggplot(df, aes(DT_RT)) + geom_density()
+
+ggplot(df, aes(instruction, DT_confidence)) + geom_boxplot()
+# much higher confidence in truth
+ggplot(df, aes(instruction, DT_RT)) + geom_boxplot()
+# no diff in reaction time in truth or lie
+
+ggplot(df, aes(condition, DT_confidence)) + geom_boxplot()
+ggplot(df, aes(condition, DT_RT)) + geom_boxplot()
+# not much diff for diff conditions
+
+ggplot(df, aes(DT_RT, DT_confidence)) + geom_point()
+# RT and confidence don't seem to have a correlation
+```
+
+```{r both}
+# is there a way to loop this
+ggplot(df.plot, aes(x = yoni_total, y = confidence, colour = instruction)) +
+  geom_point() +
+  geom_smooth(method = "lm") + 
+  facet_wrap(~condition)
+
+ggplot(df.plot, aes(x = BES_total, y = confidence, colour = instruction)) +
+  geom_point() +
+  geom_smooth(method = "lm") + 
+  facet_wrap(~condition)
+# both yoni and BES do not seem to have effect in social condition, higher yoni/BES increases confidence in truth and decreases confidences in lie
+
+ggplot(df.plot, aes(x = HCT_accuracy, y = confidence, colour = instruction)) +
+  geom_point() +
+  geom_smooth(method = "lm") + 
+  facet_wrap(~condition)
+# same effect in both social and polygraph, higher HCT accuracy decreases confidence in truth and increases confidence in lie
+
+ggplot(df.plot, aes(x = MAIA_total, y = confidence, colour = instruction)) +
+  geom_point() +
+  geom_smooth(method = "lm") + 
+  facet_wrap(~condition)
+# same effect for lie in both social and polygraph, higher MAIA increases confidence
+# higher MAIA increases confidence in lie for social and not polygraph
+
+# interesting that the social tests are more correlated with polygraph and vice versa
+```

### 2021-10-07 2_inferential.Rmd
descriptive and interaction models
condition*instruction
style*instruction

--- 2021-09-27 2_inferential.Rmd
@@
 
-```{r}
-y.var <- c('DT_confidence', 'DT_confidence', 'DT_confidenceRT')
-x.var <- c('DT_confidenceRT', 'condition*instruction', 'condition*instruction')
+```{r loop archive}
+y.var <- c('DT_confidence', 'DT_confidence', 'DT_RT')
+x.var <- c('DT_RT', 'condition*instruction', 'condition*instruction')
 
@@
         viz_data <- estimate_relation(model)
-        p <- ggplot(data = viz_data, aes(x = DT_confidenceRT, y = Predicted)) +
+        p <- ggplot(data = viz_data, aes(x = DT_RT, y = Predicted)) +
           geom_line() +
           geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3) +
-          geom_point(data = df, aes(x = DT_confidenceRT, y = DT_confidence, color = ID))
+          geom_point(data = df, aes(x = DT_RT, y = DT_confidence, color = ID))
       }
@@
 
-```{r}
-model <- lmer(DT_confidence ~ DT_confidenceRT + (1|ID) + (1|item) + (1|trial), df)
-report(model)
+```{r confidence and RT}
+model <- lmer(DT_confidence ~ DT_RT + (1|ID) + (1|item), df) # removed trial
 parameters(model, effects = "fixed")
 viz_data <- estimate_relation(model)
-p <- ggplot(data = viz_data, aes(x = DT_confidenceRT, y = Predicted)) +
+p <- ggplot(data = viz_data, aes(x = DT_RT, y = Predicted)) +
   geom_line() +
   geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3) +
-  geom_point(data = df, aes(x = DT_confidenceRT, y = DT_confidence, color = ID))
+  geom_point(data = df, aes(x = DT_RT, y = DT_confidence, color = ID))
 p
-#R2 does not account for random effects
-#weirdly significant given the plot
-#what's the include_random thing (6.5 vs 6.7)
+# there's still a singular fit?
+# weirdly significant given the plot
+# what's the include_random thing (6.5 vs 6.7)
+```
+
+```{r condition*instruction}
+y.var <- c('DT_confidence', 'DT_RT')
+
+for (i in seq_along(y.var)){
+  model <- lmer(paste(y.var[i],' ~ condition*instruction + (1|ID) + (1|item)'), df)
+  print(parameters(model, effects = "fixed"))
+  means <- modelbased::estimate_means(model, at = c("condition", "instruction"))
+  contrasts <- modelbased::estimate_contrasts(model, contrast = c("condition", "instruction"))
+  p <- ggplot(means, aes(x = instruction, y = Mean, colour = condition)) + 
+    geom_line(aes(group = condition)) +
+    geom_pointrange(aes(ymin = CI_low, ymax= CI_high))
+  print(p)
+}
+# what's the better way to loop
+# significant interaction for confidence: in truth, polygraph increases confidence but no diff in lie
+# non-significant interaction for RT
+```
+
+```{r style*instruction}
+y.var <- c('DT_confidence', 'DT_RT')
+
+for (i in seq_along(y.var)){
+  model <- lmer(paste(y.var[i],' ~ style*instruction + (1|ID) + (1|item)'), df)
+  print(parameters(model, effects = "fixed"))
+  means <- modelbased::estimate_means(model, at = c("style", "instruction"))
+  contrasts <- modelbased::estimate_contrasts(model, contrast = c("style", "instruction"))
+  p <- ggplot(means, aes(x = instruction, y = Mean, colour = style)) + 
+    geom_line(aes(group = style)) +
+    geom_pointrange(aes(ymin = CI_low, ymax= CI_high))
+  print(p)
+}
+# non-significant interaction for both (large CI)
 ```
@@
 ```{r}
-model <- lmer(DT_confidence ~ condition*instruction + (1|ID) + (1|item) + (1|trial), df)
+model <- lmer(DT_confidence ~ condition*instruction + (1|ID) + (1|item), df)
 report(model)
 parameters(model, effects = "fixed")
-interactions::cat_plot(model, pred = instruction, modx = condition)
-#R2 does not account for random effects
-#interaction is significant
+means <- modelbased::estimate_means(model, at = c("condition", "instruction"))
+contrasts <- modelbased::estimate_contrasts(model, contrast = c("condition", "instruction"))
+ggplot(means, aes(x = instruction, y = Mean, colour = condition)) + 
+  geom_line(aes(group = condition)) +
+  geom_pointrange(aes(ymin = CI_low, ymax= CI_high))
+performance::performance(model)
 ```
-
-```{r}
-model <- lmer(DT_confidenceRT ~ condition*instruction + (1|ID) + (1|item) + (1|trial), df)
-#actually this is not the reaction time? it's the reaction time to the question of how confident
-```

### 2021-10-07 index.Rmd
descriptive and interaction models
condition*instruction
style*instruction

--- 2021-09-10 index.Rmd
@@
 ```{r warning=FALSE, message=TRUE, results='asis'}
+library(tidyverse)
+library(lme4)
+library(report)
+library(parameters)
+library(modelbased)
+library(performance)
 library(bayestestR)
-library(parameters)
-library(performance)
-library(report)
 library(see)
-library(ggplot2)
 

### 2021-10-21 1_descriptive.Rmd
knit, questionnaire, lie scale (partial)

--- 2021-09-28 1_descriptive.Rmd
@@
 
-## Part 1
-
-Here's a cool plot:
-
-```{r 1_plot_scatter_basic, warning=FALSE, message=FALSE, fig.heiht=figheight, fig.width=figwidth, dpi=150}
-ggplot(df, aes(x=V1, y=V2, color=Participant)) + 
-  geom_point() +
-  see::theme_modern()
+```{r message=FALSE}
+df.plot <- df %>% 
+  group_by(ID, condition, instruction) %>% 
+  summarise(DT_confidence = mean(DT_confidence, na.rm = TRUE),
+            DT_RT = mean(DT_RT, na.rm = TRUE),
+            yoni_total = mean(yoni_total, na.rm = TRUE),
+            BES_total = mean(BES_total, na.rm = TRUE),
+            HCT_accuracy = mean(HCT_accuracy, na.rm = TRUE),
+            MAIA_total = mean(MAIA_total, na.rm = TRUE))
 ```
 
-## Part 2
-
-That's another great plot:
-
-```{r 1_plot_density, warning=FALSE, message=FALSE, fig.heiht=figheight, fig.width=figwidth, dpi=150}
-plot(bayestestR::estimate_density(df[c("V1", "V2")])) +
-  see::theme_blackboard()
+## Questionnaires
+```{r message=FALSE}
+p <- ggplot(df.plot, aes(yoni_total)) + geom_histogram()
+q <- ggplot(df.plot, aes(BES_total)) + geom_histogram()
+r <- ggplot(df.plot, aes(yoni_total, BES_total)) + geom_point()
+s <- ggplot(df.plot, aes(HCT_accuracy)) + geom_histogram()
+t <- ggplot(df.plot, aes(MAIA_total)) + geom_histogram()
+u <- ggplot(df.plot, aes(HCT_accuracy, MAIA_total)) + geom_point()
+(p + q + r)/(s + t + u) 
 ```
 
-## Part 3
+## Deception Task
+much higher confidence in truth
+no diff in reaction time in truth or lie
+not much diff for diff conditions
+```{r warning=FALSE}
+p <- ggplot(df, aes(DT_confidence)) + geom_density()
+q <- ggplot(df, aes(DT_RT)) + geom_density()
 
-```{r independent var}
-ggplot(df, aes(yoni_total)) + geom_histogram()
-ggplot(df, aes(BES_total)) + geom_histogram()
-ggplot(df, aes(yoni_total, BES_total)) + geom_point()
-ggplot(df, aes(HCT_accuracy)) + geom_histogram()
-ggplot(df, aes(MAIA_total)) + geom_histogram()
-ggplot(df, aes(HCT_accuracy, MAIA_total)) + geom_point()
+r <- ggplot(df, aes(instruction, DT_confidence, fill = condition)) + geom_boxplot()
+s <- ggplot(df, aes(instruction, DT_RT, fill = condition)) + geom_boxplot()
+
+(p + q)/(r + s)
 ```
 
-```{r dependent var}
-ggplot(df, aes(instruction, DT_RT)) + geom_boxplot()
-ggplot(df, aes(instruction, DT_confidence)) + geom_boxplot()
-ggplot(df, aes(condition, DT_RT)) + geom_boxplot()
-ggplot(df, aes(condition, DT_confidence)) + geom_boxplot()
+## Questionnaire and Deception Task
+interesting that the social tests are more correlated with polygraph and vice versa
+
+### Yoni and BES
+both yoni and BES do not seem to have effect in social condition, higher yoni/BES increases confidence in truth and decreases confidences in lie
+```{r message=FALSE, warning=FALSE}
+p <- ggplot(df.plot, aes(x = yoni_total, y = DT_confidence, colour = instruction)) +
+  geom_point() +
+  geom_smooth(method = "lm") + 
+  facet_wrap(~condition)
+
+q <- ggplot(df.plot, aes(x = BES_total, y = DT_confidence, colour = instruction)) +
+  geom_point() +
+  geom_smooth(method = "lm") + 
+  facet_wrap(~condition)
+
+p + q
 ```
 
-```{r}
-df %>% 
-  group_by(ID, condition, instruction) %>% 
-  summarise(confidence = mean(DT_confidence, na.rm = TRUE),
-            yoni_total = mean(yoni_total, na.rm = TRUE)) %>% #create a new df for plot
-  ggplot(aes(x = yoni_total, y = confidence, colour = instruction)) +
+### HCT
+same effect in both social and polygraph, higher HCT accuracy decreases confidence in truth and increases confidence in lie
+```{r message=FALSE, warning=FALSE}
+ggplot(df.plot, aes(x = HCT_accuracy, y = DT_confidence, colour = instruction)) +
   geom_point() +
@@
 ```
+
+### MAIA
+same effect for lie in both social and polygraph, higher MAIA increases confidence
+higher MAIA increases confidence in lie for social and not polygraph
+```{r message=FALSE, warning=FALSE}
+ggplot(df.plot, aes(x = MAIA_total, y = DT_confidence, colour = instruction)) +
+  geom_point() +
+  geom_smooth(method = "lm") + 
+  facet_wrap(~condition)
+```

### 2021-10-21 2_inferential.Rmd
knit, questionnaire, lie scale (partial)

--- 2021-09-27 2_inferential.Rmd
@@
 
-Here is another analysis that is contained in a separate file.
-Let's check-out this linear regression model (note that, in the code chunk parameters, I multiplied `figheight` by 2 to have a taller plot):
+## The effect of confidence on RT
+Confidence has a significant impact on RT.
+```{r warning=FALSE}
+model <- glmmTMB(DT_confidence ~ DT_RT + (1|ID) + (1|item), data = df) # removed trial
+parameters(model, effects = "fixed")
+viz_data <- estimate_relation(model)
+ggplot(data = viz_data, aes(x = DT_RT, y = Predicted)) +
+  geom_point(data = df, aes(x = DT_RT, y = DT_confidence, color = ID), show.legend = FALSE) +
+  geom_line() +
+  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
 
-```{r 2_plot_model, warning=FALSE, message=FALSE, fig.heiht=figheight * 2, fig.width=figwidth, dpi=150}
-model <- lm(Petal.Length ~ Sepal.Length, data=iris)
-performance::check_model(model)
+# what's the include_random thing (6.5 vs 6.7)
 ```
 
+## Interaction of condition and instruction
+### Confidence
+There is a significant interaction of condition and instruction on confidence.
+The increase in confidence from lie to truth is more in polygraph than social.
 ```{r}
-y.var <- c('DT_confidence', 'DT_confidence', 'DT_confidenceRT')
-x.var <- c('DT_confidenceRT', 'condition*instruction', 'condition*instruction')
-
-for (i in seq_along(y.var)){
-  for (j in seq_along(x.var)){
-    if (i==j){
-      model <- lmer(paste(y.var[i],' ~', x.var[j],' + (1|ID) + (1|item) + (1|trial)'), df)
-      print(report(model))
-      print(parameters(model, effects = "fixed"))
-      if (grepl('\\*', x.var[j]) == TRUE){
-        p <- interactions::cat_plot(model, pred = instruction, modx = condition)
-      }
-      else{
-        viz_data <- estimate_relation(model)
-        p <- ggplot(data = viz_data, aes(x = DT_confidenceRT, y = Predicted)) +
-          geom_line() +
-          geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3) +
-          geom_point(data = df, aes(x = DT_confidenceRT, y = DT_confidence, color = ID))
-      }
-      print(p)
-    }
-  }
-}
+model <- glmmTMB(DT_confidence ~ condition*instruction + (1|ID) + (1|item), data = df)
+parameters(model, effects = "fixed")
+means <- modelbased::estimate_means(model, at = c("condition", "instruction"))
+contrasts <- modelbased::estimate_contrasts(model, contrast = c("condition", "instruction"))
+ggplot(means, aes(x = instruction, y = Mean, colour = condition)) + 
+  geom_line(aes(group = condition)) +
+  geom_pointrange(aes(ymin = CI_low, ymax= CI_high))
 ```
 
+### Reaction time
+There is no significant interaction of condition and instruction on RT.
 ```{r}
-model <- lmer(DT_confidence ~ DT_confidenceRT + (1|ID) + (1|item) + (1|trial), df)
-report(model)
+model <- glmmTMB(DT_RT ~ condition*instruction + (1|ID) + (1|item), data = df)
 parameters(model, effects = "fixed")
-viz_data <- estimate_relation(model)
-p <- ggplot(data = viz_data, aes(x = DT_confidenceRT, y = Predicted)) +
-  geom_line() +
-  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3) +
-  geom_point(data = df, aes(x = DT_confidenceRT, y = DT_confidence, color = ID))
-p
-#R2 does not account for random effects
-#weirdly significant given the plot
-#what's the include_random thing (6.5 vs 6.7)
+means <- modelbased::estimate_means(model, at = c("condition", "instruction"))
+ggplot(means, aes(x = instruction, y = Mean, colour = condition)) + 
+  geom_line(aes(group = condition)) +
+  geom_pointrange(aes(ymin = CI_low, ymax= CI_high))
 ```
 
+## Interaction of style and instruction
+### Confidence
+There is no significant interaction of style and instruction on confidence.
 ```{r}
-model <- lmer(DT_confidence ~ condition*instruction + (1|ID) + (1|item) + (1|trial), df)
-report(model)
+model <- glmmTMB(DT_confidence ~ style*instruction + (1|ID) + (1|item), data = df)
 parameters(model, effects = "fixed")
-interactions::cat_plot(model, pred = instruction, modx = condition)
-#R2 does not account for random effects
-#interaction is significant
+means <- modelbased::estimate_means(model, at = c("style", "instruction"))
+ggplot(means, aes(x = instruction, y = Mean, colour = style)) + 
+  geom_line(aes(group = style)) +
+  geom_pointrange(aes(ymin = CI_low, ymax= CI_high))
 ```
 
+### Reaction time
+There is no significant interaction of style and instruction on RT.
 ```{r}
-model <- lmer(DT_confidenceRT ~ condition*instruction + (1|ID) + (1|item) + (1|trial), df)
-#actually this is not the reaction time? it's the reaction time to the question of how confident
+model <- glmmTMB(DT_RT ~ style*instruction + (1|ID) + (1|item), data = df)
+parameters(model, effects = "fixed")
+means <- modelbased::estimate_means(model, at = c("style", "instruction"))
+ggplot(means, aes(x = instruction, y = Mean, colour = style)) + 
+  geom_line(aes(group = style)) +
+  geom_pointrange(aes(ymin = CI_low, ymax= CI_high))
 ```

### 2021-10-21 3_inferential_questionnaire.Rmd
knit, questionnaire, lie scale (partial)

---
output: html_document
editor_options: 
  chunk_output_type: console
---
## The effect of TOM ability on confidence and RT
### Yoni task
no correlation of yoni score with confidence
```{r}
model <- glmmTMB(DT_confidence ~ yoni_total + DT_RT + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "yoni_total")
ggplot(data = viz_data, aes(x = yoni_total, y = Predicted)) +
  geom_point(data = df.plot, aes(x = yoni_total, y = DT_confidence, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

no correlation of yoni score with RT
```{r}
model <- glmmTMB(DT_RT ~ yoni_total + DT_confidence + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "yoni_total")
ggplot(data = viz_data, aes(x = yoni_total, y = Predicted)) +
  geom_point(data = df.plot, aes(x = yoni_total, y = DT_RT, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

### BES
no correlation of BES score with confidence
```{r}
model <- glmmTMB(DT_confidence ~ BES_total + DT_RT + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "BES_total")
ggplot(data = viz_data, aes(x = BES_total, y = Predicted)) +
  geom_point(data = df.plot, aes(x = BES_total, y = DT_confidence, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

no correlation of BES score with RT
```{r}
model <- glmmTMB(DT_RT ~ BES_total + DT_confidence + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "BES_total")
ggplot(data = viz_data, aes(x = BES_total, y = Predicted)) +
  geom_point(data = df.plot, aes(x = BES_total, y = DT_RT, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

## The effect of interoceptive ability on confidence and RT
### HCT
no correlation of HCT accuracy with confidence
```{r}
model <- glmmTMB(DT_confidence ~ HCT_accuracy + DT_RT + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "HCT_accuracy")
ggplot(data = viz_data, aes(x = HCT_accuracy, y = Predicted)) +
  geom_point(data = df.plot, aes(x = HCT_accuracy, y = DT_confidence, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

no correlation of HCT accuracy with RT
```{r}
model <- glmmTMB(DT_RT ~ HCT_accuracy + DT_confidence + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "HCT_accuracy")
ggplot(data = viz_data, aes(x = HCT_accuracy, y = Predicted)) +
  geom_point(data = df.plot, aes(x = HCT_accuracy, y = DT_RT, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

### MAIA
the higher the MAIA the higher the confidence (p=0.048)
```{r}
model <- glmmTMB(DT_confidence ~ MAIA_total + DT_RT + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "MAIA_total")
ggplot(data = viz_data, aes(x = MAIA_total, y = Predicted)) +
  geom_point(data = df.plot, aes(x = MAIA_total, y = DT_confidence, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

the higher the MAIA the lower the RT (p=0.035)
```{r}
model <- glmmTMB(DT_RT ~ MAIA_total + DT_confidence + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "MAIA_total")
ggplot(data = viz_data, aes(x = MAIA_total, y = Predicted)) +
  geom_point(data = df.plot, aes(x = MAIA_total, y = DT_RT, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

```{r test}
model <- glmmTMB(DT_confidence ~ MAIA_total + DT_RT + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "MAIA_total")
ggplot(data = viz_data, aes(x = MAIA_total, y = Predicted)) +
  geom_boxplot(data = df, aes(x = MAIA_total, y = DT_confidence, color = ID), show.legend = FALSE) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

## idea for within
independent variable: 
each participant is assigned a percentile for yoni/bes/hct/maia
objective-objective and subjective-subjective to obtain difference in TOM-int ability

dependent variable:
average of DT_confidence in social - polygraph
hmm

hypothesis: 
the higher the difference in TOM-int, the higher the social-polygraph confidence
(though this does not seem to be the case in descriptive)

### 2021-10-21 index.Rmd
knit, questionnaire, lie scale (partial)

--- 2021-09-27 index.Rmd
@@
 
-This is a template for a data analysis folder that can be easily exported as a [**webpage**](https://realitybending.github.io/TemplateResults/) or as **Supplementary Materials** (e.g., as a [**Word document**](https://github.com/RealityBending/TemplateResults/raw/main/word_and_pdf/SupplementaryMaterials.docx) or a [**PDF**](https://github.com/RealityBending/TemplateResults/blob/main/word_and_pdf/SupplementaryMaterials.pdf)).
-
-How does it look like?
-Just like this!
-The README page of this repository, alongside the [webpage](https://realitybending.github.io/TemplateResults/) and the word and PDF documents, were all created from the [index.Rmd](https://github.com/RealityBending/TemplateResults/blob/main/index.Rmd) file.
-
-This means you can easily **share your data analysis**, either by attaching the *PDF* or *Word* file to the publication (as **Supplementary Materials**), or by directly providing the URL of your GitHub repository: the readers can then enjoy your awesome open-access work in a convenient and transparent way.
-
-## Features
-
-- [x] Automatically generates different types of document:
-  - [**README page**](https://github.com/RealityBending/TemplateResults/blob/main/README.md)
-  - [**Published website**](https://realitybending.github.io/TemplateResults/)
-  - [**Word document**](https://github.com/RealityBending/TemplateResults/raw/main/word_and_pdf/SupplementaryMaterials.docx)
-  - [**PDF document**](https://github.com/RealityBending/TemplateResults/blob/main/word_and_pdf/SupplementaryMaterials.pdf)
-- [x] APA citations
-- [x] Automatic citations and [reference list](https://github.com/RealityBending/TemplateResults#package-references) for all packages
-- [x] Tidy organisation (separate files for independent analyses)
-- [x] Great default configuration
-- [x] And more!
-
-```{r demo_gif, echo=FALSE, message=TRUE, warning=FALSE}
-# Let's include a demo GIF (this doesn't work in PDF documents)
-if (!knitr::is_latex_output()) {
-  knitr::include_graphics("figures/demo.gif")
-}
-```
-
-## Installation
-
-- **What is this?**
-
-This repository is a template to set up a reproducible, convenient and shareable workflow for your data analysis.
-It consists of several [*Rmarkdown*](https://rmarkdown.rstudio.com/lesson-1.html) files (`.Rmd`), that allow you to have R code and text (markdown) in the same document.
-Importantly, these files can be transformed into other documents formats.
-
-- **How to use this template?**
-
-Download it ([**click here to download**](https://github.com/RealityBending/TemplateResults/archive/main.zip)), unzip it and edit.
-Alternatively, you click on the [**Use this template**](https://github.com/RealityBending/TemplateResults/generate) button at the top of this screen to create a GitHub repository with all the content copied (then you just need to clone the repo to your local machine).
-
-The main files you need to edit are the `.Rmd` files, that you can open with some editor (e.g., [Rstudio](https://rstudio.com/)), and edit the text and the R chunks of code.
-
-- **How to upload it to a website?**
-
-If your repo is not already connected to GitHub, then create a new repository and upload all the content (so that it looks like this repo).
-Then, go to settings of the repo and enable **GitHub pages** (i.e., that gives you a webpage from an html stored on GitHub), and select the `docs/` folder as the location of the webpage.
-Indeed, rendering (knitting) the files will generate an "index.html" file in the `/docs/` folder, which is used as the website.
-You can see an example at [https://realitybending.github.io/TemplateResults/](https://realitybending.github.io/TemplateResults/).
-
-- **To knit or not to knit**
-
-In this repo, with have set up a [GitHub action](https://github.com/RealityBending/TemplateResults/blob/main/.github/workflows/website.yml) that generates all the output files everytime someone commit to the repository.
-This means that the final documents here are always "up-to-date" with the *Rmds* (as shown by the green badge).
-That said, you can remove this GitHub action (just remove the `.github/workflows/website.yml` file) if you prefer to generate the documents manually only.
-
-- **But I don't want do upload all my data**
-
-In that case, you'll need to 1) deactivate (i.e., remove the action file) the automatic rendering by GitHub (as no data will be stored on GitHub) and 2) mark the **data** folder as "to be ignored" (so that it won't be uploaded).
-This can be done by adding `/data/` to the [**.gitignore**](https://github.com/RealityBending/TemplateResults/blob/main/.gitignore) file (that you can open with a notepad).
-This means that you can still store the data here locally, and generate the documents accordingly, but the data folder will be ignored by git and never uploaded to GitHub.
-This way, you can still have a cool website, an open-access script, but the data is safe with you.
-The only down side is that you have to build it manually (cannot use GitHub actions).
-
-- **How to add references?**
-
-References have to be added in `bib` format in the [*utils/bibliography.bib*](https://github.com/RealityBending/TemplateResults/blob/main/utils/bibliography.bib) file, and further referenced in the text like this `[@ludecke2019insight]` [@ludecke2019insight].
-
-- **I don't like the Word (.docx) theme**
-
-The theme for the word document is defined in the [**Template_Word.docx](https://github.com/RealityBending/TemplateResults/tree/main/utils) file, in the `/utils/` folder.
-You need to edit the "styles" (not just the content, but the style itself) to your preference.
-
-- **I have Python code**
-
-Thanks to R's possibilities when it comes to integration with Python, it's super easy to enable it in your pipeline.
-Just uncomment the [Python installation line](https://github.com/RealityBending/TemplateResults/blob/main/utils/config.R#L24) in the `utils/config.R` file and you're ready to go!
-
-- **It doesn't work / I have questions / I have ideas**
-
-Just [**open an issue**](https://github.com/RealityBending/TemplateResults/issues) and we'll be happy to assist ☺
-
-## Structure
-
-Most files that you'll need to create / edit will be written in [**rmarkdown**](https://rmarkdown.rstudio.com/lesson-1.html), which consists of a mix of markdown text and R chunks of code.
-
-The main file is named [**index.Rmd**](https://github.com/RealityBending/TemplateResults/blob/main/index.Rmd).
-However, to avoid having overly long files, the different (and independent) analyses parts are actually split in other documents.
-For instance, in this template example, the descriptive statistics section is in the [**1_descriptive.Rmd**](https://github.com/RealityBending/TemplateResults/blob/main/1_descriptive.Rmd) file.
-As you can [see in the index file](https://github.com/RealityBending/TemplateResults/blob/690f7947da0fc8ac85eaf6fb87fafeaa46fb3c50/index.Rmd#L89-L90), this file is then integrated as a child document (i.e., it is merged).
-This makes it very convenient to have a clear structure with well-organized files, that are put together only when merged.
-
-## Render and Publish
-
-Importantly, in order to render all the files, do not Knit this document by pressing the 'Knit' button.
-If you do, it will create an output file (for instance `index.html`) in the root folder, alongside `index.Rmd`.
-This is **not what we want**, as we want to keep the output files tidy in separate folders (for instance, the html version should be in the `/docs/` folder, as this is where the website will look for).
-
-There an R script, [utils/render.R](https://github.com/RealityBending/TemplateResults/blob/main/utils/render.R), that contains the lines to render everything in its correct location.
-So, when you have the "index.Rmd" file opened (and your working directory is at its root), simply run **`source("utils/render.R")`** in the console (or the relevant lines in that file).
-This will run the rendering file and create all the files.
-
-## Contribution
-
-Do not hesitate to improve this template by updating, documenting, or expanding it!
-
 # Packages & Data
@@
 ```{r warning=FALSE, message=TRUE, results='asis'}
+library(tidyverse)
+library(patchwork)
+library(glmmTMB)
+library(report)
+library(parameters)
+library(modelbased)
+library(performance)
 library(bayestestR)
-library(parameters)
-library(performance)
-library(report)
 library(see)
-library(ggplot2)
-library(lme4)
-library(modelbased)
 
@@
 ```{r warning=FALSE, message=TRUE, results='asis'}
-df <- read.csv("data/data_combined.csv")
+df <- read.csv("data/data_combined.csv") %>% 
+  mutate(ID = as.factor(ID),
+         condition = as.factor(condition),
+         item = as.factor(item),
+         style = as.factor(style),
+         instruction = as.factor(instruction))
 
@@
 
-# Inferential Stats
+# Inferential Stats {.tabset}
 

### 2021-10-21 scripts/claudia/data processing.Rmd
knit, questionnaire, lie scale (partial)

@@
 
-  mutate(BES_cognitive = Q3+Q6+Q9+Q10+Q12+Q14+Q16+Q19+Q20) %>% 
-  mutate(BES_affective = Q1+Q2+Q4+Q5+Q7+Q8+Q11+Q13+Q15+Q17+Q18) %>% 
-  mutate(BES_total = BES_cognitive+BES_affective) %>%
+  mutate(BES_cognitive = Q3+Q6+Q9+Q10+Q12+Q14+Q16+Q19+Q20, 
+         BES_affective = Q1+Q2+Q4+Q5+Q7+Q8+Q11+Q13+Q15+Q17+Q18,
+         BES_total = BES_cognitive+BES_affective) %>%
 
@@
   mutate(hbcount_reported = str_remove_all(hbcount_reported, "Enter Number")) %>% 
-  mutate(hbcount_reported = as.numeric(hbcount_reported)) %>% 
-  mutate(HCT_confidence = as.numeric(HCT_confidence)) %>%
+  mutate(hbcount_reported = as.numeric(hbcount_reported),
+         HCT_confidence = as.numeric(HCT_confidence)) %>%
 
@@
 parttwo <- parttwo %>% 
-  mutate(HCT_guess = str_count(parttwo$guess, "space")) %>% 
-  mutate(HCT_noguess = str_count(parttwo$noguess, "space")) %>% 
-  mutate(HCT_onebreath = str_count(parttwo$onebreath, "space")) %>% 
+  mutate(HCT_guess = str_count(parttwo$guess, "space"),
+         HCT_noguess = str_count(parttwo$noguess, "space"),
+         HCT_onebreath = str_count(parttwo$onebreath, "space")) %>% 
   select(c(ID, HCT_guess, HCT_noguess, HCT_onebreath))
@@
 
+```{r lie scale}
+rm(list=ls())
+cat("\014")
+
+mydata <- read.csv('../../data/data_questionnaire/Lie Scale.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]
+
+results <- mydata %>% 
+  rename(Q1 = Q1_4,
+       Q2 = Q2_4,
+       Q3 = Q3_4,
+       Q4 = Q4_4,
+       Q5 = Q5_4,
+       Q6 = Q6_4,
+       Q7 = Q7_4,
+       Q8 = Q8_4,
+       Q9 = Q9_4,
+       Q10 = Q10_1,
+       Q11 = Q11_1,
+       Q12 = Q12_4,
+       Q13 = Q13_4,
+       Q14 = Q14_4,
+       Q15 = Q15_4,
+       Q16 = Q16_4,
+       Q17 = Q17,
+       Q18 = Q18) %>%
+
+  mutate(Q1 = as.numeric(Q1), Q2 = as.numeric(Q2), Q3 = as.numeric(Q3), Q4 = as.numeric(Q4),
+         Q5 = as.numeric(Q5), Q6 = as.numeric(Q6), Q7 = as.numeric(Q7), Q8 = as.numeric(Q8),
+         Q9 = as.numeric(Q9), Q10 = as.numeric(Q10), Q11 = as.numeric(Q11), Q12 = as.numeric(Q12),
+         Q13 = as.numeric(Q13), Q14 = as.numeric(Q14), Q15 = as.numeric(Q15), Q16 = as.numeric(Q16),
+         Q17 = as.numeric(Q17), Q18 = as.numeric(Q18)) %>%
+
+  arrange(ID)
+
+# write.csv(results, file = "Lie Scale_processed.csv", row.names=FALSE)
+```
+
 ```{r deception subj}
@@
   df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), c(1:4, 29, 31, 35, 36, 43, 45, 47)] %>% 
-    mutate(trial = c(1:80)) %>% 
-    mutate(condition = c(rep("Social", 40), rep("Polygraph", 40)))
+    mutate(trial = c(1:80),
+           condition = c(rep("Social", 40), rep("Polygraph", 40)))
   mydata <- rbind(mydata, df_sub)
@@
 
-  mutate(DT_confidence = as.numeric(DT_confidence)) %>% 
-  mutate(instruction = as.factor(instruction)) %>% 
-  mutate(social_start = as.numeric(social_start)) %>% 
-  mutate(social_stop = as.numeric(social_stop)) %>% 
-  mutate(polyg_start = as.numeric(polyg_start)) %>% 
-  mutate(polyg_stop = as.numeric(polyg_stop)) %>% 
-  mutate(ID = as.numeric(ID)) %>%
+  mutate(DT_confidence = as.numeric(DT_confidence),
+         social_start = as.numeric(social_start),
+         social_stop = as.numeric(social_stop),
+         polyg_start = as.numeric(polyg_start),
+         polyg_stop = as.numeric(polyg_stop),
+         ID = as.numeric(ID)) %>%
   mutate(DT_RT = ifelse(condition == "Social", social_stop - social_start,
@@
   left_join(inclusion) %>%
-  select(ID, trial, condition, inclusion, inclusion2, everything()) #move columns to front
+  select(ID, trial, condition, inclusion, inclusion2, everything()) # move columns to front
 

### 2021-10-21 3_inferential_questionnaire.Rmd
update lie and maia

@@
 ---
+```{r}
+plot_effect <- function(model, var) {
+  viz_data <- estimate_relation(model, at = c("condition", var, "instruction"))
+  ggplot(data = viz_data, aes_string(x = var, y = "Predicted")) +
+    geom_point(data = df.plot, aes_string(y = "DT_confidence", color = "condition"), show.legend = FALSE) +
+    geom_line(aes_string(color = "condition")) +
+    geom_ribbon(aes_string(ymin = "CI_low", ymax = "CI_high", fill = "condition"), alpha = 0.3) + 
+    facet_wrap(~instruction)
+}
+plot_effect(model, "MAIA_total")
+```
+
 ## The effect of TOM ability on confidence and RT
 ### Yoni task
-no correlation of yoni score with confidence
 ```{r}
-model <- glmmTMB(DT_confidence ~ yoni_total + DT_RT + (1|ID) + (1|item), data = df)
+model <- glmmTMB(DT_confidence ~ instruction/(condition*yoni_total) + (1|ID) + (1|item), data = df)
 parameters(model, effects = "fixed")
-viz_data <- estimate_relation(model, at = "yoni_total")
+viz_data <- estimate_relation(model, at = c("condition", "yoni_total", "instruction"))
 ggplot(data = viz_data, aes(x = yoni_total, y = Predicted)) +
-  geom_point(data = df.plot, aes(x = yoni_total, y = DT_confidence, color = ID), show.legend = FALSE) +
-  geom_line() +
-  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
+  geom_point(data = df.plot, aes(y = DT_confidence, color = condition), show.legend = FALSE) +
+  geom_line(aes(color = condition)) +
+  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = condition), alpha = 0.3) + 
+  facet_wrap(~instruction)
 ```
-
-no correlation of yoni score with RT
-```{r}
-model <- glmmTMB(DT_RT ~ yoni_total + DT_confidence + (1|ID) + (1|item), data = df)
-parameters(model, effects = "fixed")
-viz_data <- estimate_relation(model, at = "yoni_total")
-ggplot(data = viz_data, aes(x = yoni_total, y = Predicted)) +
-  geom_point(data = df.plot, aes(x = yoni_total, y = DT_RT, color = ID), show.legend = FALSE) +
-  geom_line() +
-  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
-```
+the higher someone scores in yoni, the bigger the difference in lie and truth
 
 ### BES
-no correlation of BES score with confidence
 ```{r}
-model <- glmmTMB(DT_confidence ~ BES_total + DT_RT + (1|ID) + (1|item), data = df)
+model <- glmmTMB(DT_confidence ~ instruction/(condition*BES_total) + (1|ID) + (1|item), data = df)
 parameters(model, effects = "fixed")
-viz_data <- estimate_relation(model, at = "BES_total")
+viz_data <- estimate_relation(model, at = c("condition", "BES_total", "instruction"))
 ggplot(data = viz_data, aes(x = BES_total, y = Predicted)) +
-  geom_point(data = df.plot, aes(x = BES_total, y = DT_confidence, color = ID), show.legend = FALSE) +
-  geom_line() +
-  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
-```
-
-no correlation of BES score with RT
-```{r}
-model <- glmmTMB(DT_RT ~ BES_total + DT_confidence + (1|ID) + (1|item), data = df)
-parameters(model, effects = "fixed")
-viz_data <- estimate_relation(model, at = "BES_total")
-ggplot(data = viz_data, aes(x = BES_total, y = Predicted)) +
-  geom_point(data = df.plot, aes(x = BES_total, y = DT_RT, color = ID), show.legend = FALSE) +
-  geom_line() +
-  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
+  geom_point(data = df.plot, aes(y = DT_confidence, color = condition), show.legend = FALSE) +
+  geom_line(aes(color = condition)) +
+  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = condition), alpha = 0.3) + 
+  facet_wrap(~instruction)
 ```
@@
 ### HCT
-no correlation of HCT accuracy with confidence
 ```{r}
-model <- glmmTMB(DT_confidence ~ HCT_accuracy + DT_RT + (1|ID) + (1|item), data = df)
+model <- glmmTMB(DT_confidence ~ instruction/(condition*HCT_accuracy) + (1|ID) + (1|item), data = df)
 parameters(model, effects = "fixed")
-viz_data <- estimate_relation(model, at = "HCT_accuracy")
+viz_data <- estimate_relation(model, at = c("condition", "HCT_accuracy", "instruction"))
 ggplot(data = viz_data, aes(x = HCT_accuracy, y = Predicted)) +
-  geom_point(data = df.plot, aes(x = HCT_accuracy, y = DT_confidence, color = ID), show.legend = FALSE) +
-  geom_line() +
-  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
-```
-
-no correlation of HCT accuracy with RT
-```{r}
-model <- glmmTMB(DT_RT ~ HCT_accuracy + DT_confidence + (1|ID) + (1|item), data = df)
-parameters(model, effects = "fixed")
-viz_data <- estimate_relation(model, at = "HCT_accuracy")
-ggplot(data = viz_data, aes(x = HCT_accuracy, y = Predicted)) +
-  geom_point(data = df.plot, aes(x = HCT_accuracy, y = DT_RT, color = ID), show.legend = FALSE) +
-  geom_line() +
-  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
+  geom_point(data = df.plot, aes(y = DT_confidence, color = condition), show.legend = FALSE) +
+  geom_line(aes(color = condition)) +
+  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = condition), alpha = 0.3) + 
+  facet_wrap(~instruction)
 ```
@@
 ### MAIA
-the higher the MAIA the higher the confidence (p=0.048)
 ```{r}
-model <- glmmTMB(DT_confidence ~ MAIA_total + DT_RT + (1|ID) + (1|item), data = df)
+model <- glmmTMB(DT_confidence ~ instruction/(condition*MAIA_total) + (1|ID) + (1|item), data = df)
 parameters(model, effects = "fixed")
-viz_data <- estimate_relation(model, at = "MAIA_total")
-ggplot(data = viz_data, aes(x = MAIA_total, y = Predicted)) +
-  geom_point(data = df.plot, aes(x = MAIA_total, y = DT_confidence, color = ID), show.legend = FALSE) +
-  geom_line() +
-  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
+parameters(emmeans::emtrends(model, ~instruction, var = "MAIA_total")) # main effect only significant for lie, averages (properly) over condition -> similar to instruction/MAIA_total but takes into account condition
 ```
-
-the higher the MAIA the lower the RT (p=0.035)
-```{r}
-model <- glmmTMB(DT_RT ~ MAIA_total + DT_confidence + (1|ID) + (1|item), data = df)
-parameters(model, effects = "fixed")
-viz_data <- estimate_relation(model, at = "MAIA_total")
-ggplot(data = viz_data, aes(x = MAIA_total, y = Predicted)) +
-  geom_point(data = df.plot, aes(x = MAIA_total, y = DT_RT, color = ID), show.legend = FALSE) +
-  geom_line() +
-  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
-```
-
-```{r test}
-model <- glmmTMB(DT_confidence ~ MAIA_total + DT_RT + (1|ID) + (1|item), data = df)
-parameters(model, effects = "fixed")
-viz_data <- estimate_relation(model, at = "MAIA_total")
-ggplot(data = viz_data, aes(x = MAIA_total, y = Predicted)) +
-  geom_boxplot(data = df, aes(x = MAIA_total, y = DT_confidence, color = ID), show.legend = FALSE) + 
-  geom_line() +
-  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
-```
-
-## idea for within
-independent variable: 
-each participant is assigned a percentile for yoni/bes/hct/maia
-objective-objective and subjective-subjective to obtain difference in TOM-int ability
-
-dependent variable:
-average of DT_confidence in social - polygraph
-hmm
-
-hypothesis: 
-the higher the difference in TOM-int, the higher the social-polygraph confidence
-(though this does not seem to be the case in descriptive)

### 2021-10-21 scripts/claudia/data processing.Rmd
update lie and maia

@@
   mutate(MAIA_total = (MAIA1+MAIA2+MAIA3+MAIA4+MAIA5+MAIA6+MAIA7+MAIA8)/8) %>%
+  rename(MAIA_noticing = MAIA1,
+         MAIA_not_distracting = MAIA2,
+         MAIA_not_worrying = MAIA3,
+         MAIA_attention_regulation = MAIA4,
+         MAIA_emotional_awareness = MAIA5,
+         MAIA_self_regulation = MAIA6,
+         MAIA_body_listening = MAIA7,
+         MAIA_trusting = MAIA8) %>%
 
@@
 
+  mutate(lie_ability = (Q4+Q5+Q6+Q7)/4, 
+         lie_frequency = (Q1+Q2+Q3+Q8)/4, 
+         lie_negativity = (Q9+Q11+Q13+Q16)/4, 
+         lie_contextuality = (Q10+Q12+Q14+Q15)/4) %>%
+
   arrange(ID)
 
-# write.csv(results, file = "Lie Scale_processed.csv", row.names=FALSE)
+write.csv(results, file = "liescale_processed.csv", row.names=FALSE)
 ```

### 2021-11-03 1_descriptive.Rmd
added functions, more iv
other HCT measures, lie scale

@@
             BES_total = mean(BES_total, na.rm = TRUE),
+            HCT_confidence = mean(HCT_confidence, na.rm = TRUE),
             HCT_accuracy = mean(HCT_accuracy, na.rm = TRUE),
-            MAIA_total = mean(MAIA_total, na.rm = TRUE))
+            HCT_awareness = mean(HCT_awareness, na.rm = TRUE),
+            MAIA_total = mean(MAIA_total, na.rm = TRUE),
+            lie_ability = mean(lie_ability, na.rm = TRUE),
+            lie_frequency = mean(lie_frequency, na.rm = TRUE),
+            lie_negativity = mean(lie_negativity, na.rm = TRUE),
+            lie_contextuality = mean(lie_contextuality, na.rm = TRUE))
 ```

### 2021-11-03 2_inferential_expt.Rmd
added functions, more iv
other HCT measures, lie scale

---
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r}
plot_expt <- function(model, var){
  means <- estimate_means(model, at = c(var, "instruction"))
  ggplot(means, aes_string(x = "instruction", y = "Mean", colour = var)) + 
    geom_line(aes_string(group = var)) +
    geom_pointrange(aes(ymin = CI_low, ymax= CI_high))
}
```

## The effect of confidence on RT
Confidence has a significant impact on RT. Increased confidence decreases RT.
```{r warning=FALSE}
model <- glmmTMB(DT_confidence ~ DT_RT + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model)
ggplot(data = viz_data, aes(x = DT_RT, y = Predicted)) +
  geom_point(data = df, aes(x = DT_RT, y = DT_confidence, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

## Confidence
### Interaction of condition and instruction
There is a significant interaction of condition and instruction on confidence.
The increase in confidence from lie to truth is more in polygraph than social.
```{r}
model <- glmmTMB(DT_confidence ~ condition*instruction + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_expt(model, "condition")
```

### Interaction of style and instruction
There is no significant interaction of style and instruction on confidence.
```{r}
model <- glmmTMB(DT_confidence ~ style*instruction + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_expt(model, "style")
```

## Reaction time
### Interaction of condition and instruction
There is no significant interaction of condition and instruction on RT.
```{r}
model <- glmmTMB(DT_RT ~ condition*instruction + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_expt(model, "condition")
```

### Interaction of style and instruction
There is no significant interaction of style and instruction on RT.
Indirect style significantly increases RT.
```{r}
model <- glmmTMB(DT_RT ~ style*instruction + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_expt(model, "style")
```

### 2021-11-03 3_inferential_behv.Rmd
added functions, more iv
other HCT measures, lie scale

---
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r}
plot_behv <- function(model, varx, vary) {
  viz_data <- estimate_relation(model, at = c("condition", varx, "instruction"))
  ggplot(data = viz_data, aes_string(x = varx, y = "Predicted")) +
    geom_point(data = df.plot, aes_string(y = vary, color = "condition"), show.legend = FALSE) +
    geom_line(aes(color = condition)) +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = condition), alpha = 0.3) + 
    facet_wrap(~instruction)
}
```

## Summary
```{r}
summary <- data.frame("yoni", "decrease (trend)", "social", "increase (ns)", "ns")
names(summary) <- c("measure", "conf main effect (lie)", "conf interact", "RT main effect (lie)", "RT interact")
summary <- summary %>% 
  rbind(c("BES", "decrease (ns)", "social (trend)", "decrease (ns)", "polygraph")) %>% 
  rbind(c("HCT confidence", "increase", "polygraph", "decrease", "ns")) %>% 
  rbind(c("HCT accuracy", "increase", "polygraph", "decrease (ns)", "ns")) %>% 
  rbind(c("HCT awareness", "decrease", "social", "increase", "polygraph")) %>% 
  rbind(c("MAIA", "increase", "ns", "decrease", "social"))
summary
```

## TOM ability
### Yoni task
When instructed to lie, the decrease in confidence in participants with higher yoni score is less in social than polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_confidence ~ instruction/(condition*yoni_total) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "yoni_total", "DT_confidence")
```

When instructed to lie, participants with higher yoni score show no significant difference in RT between social and polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_RT ~ instruction/(condition*yoni_total) + style + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "yoni_total", "DT_RT")
```

### BES
When instructed to lie, the decrease in confidence in participants with higher BES score has a trend towards being less in social than polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_confidence ~ instruction/(condition*BES_total) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "BES_total", "DT_confidence")
```

When instructed to lie, the decrease in RT in participants with higher BES score is more in social than polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_RT ~ instruction/(condition*BES_total) + style + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "BES_total", "DT_RT")
```

## Interoceptive ability
### HCT confidence
When instructed to lie, the increase in confidence in participants with higher HCT confidence is more in polygraph than social condition.
```{r warning=FALSE}
model <- glmmTMB(DT_confidence ~ instruction/(condition*HCT_confidence) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "HCT_confidence", "DT_confidence")
```

When instructed to lie, participants with higher HCT confidence show no significant difference in RT between social and polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_RT ~ instruction/(condition*HCT_confidence) + style + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "HCT_confidence", "DT_RT")
```

### HCT accuracy
When instructed to lie, the increase in confidence in participants with higher HCT accuracy is more in polygraph than social condition.
```{r warning=FALSE}
model <- glmmTMB(DT_confidence ~ instruction/(condition*HCT_accuracy) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "HCT_accuracy", "DT_confidence")
```

When instructed to lie, participants with higher HCT accuracy show no significant difference in RT between social and polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_RT ~ instruction/(condition*HCT_accuracy) + style + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "HCT_accuracy", "DT_RT")
```

### HCT awareness
When instructed to lie, participants with higher HCT awareness have higher confidence in social than polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_confidence ~ instruction/(condition*HCT_awareness) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "HCT_awareness", "DT_confidence")
```

When instructed to lie, the increase in RT in participants with higher HCT awareness is less in social than polygraph condition. (Strange considering confidence increases)
```{r warning=FALSE}
model <- glmmTMB(DT_RT ~ instruction/(condition*HCT_awareness) + style + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "HCT_awareness", "DT_RT")
```

### MAIA
When instructed to lie, participants with higher MAIA score show no significant difference in confidence between social and polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_confidence ~ instruction/(condition*MAIA_total) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "MAIA_total", "DT_confidence")
```

When instructed to lie, the decrease in RT in participants with higher MAIA score is more in polygraph than social condition.
```{r warning=FALSE}
model <- glmmTMB(DT_RT ~ instruction/(condition*MAIA_total) + style + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "MAIA_total", "DT_RT")
```

## Lie scale
### Lie ability
Higher lie ability increases confidence more in lie than truth.
When instructed to lie, participants with higher lie ability show no significant difference in confidence between social and polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_confidence ~ instruction/(condition*lie_ability) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "lie_ability", "DT_confidence")
```

When instructed to lie, participants with higher lie ability show no significant difference in RT between social and polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_RT ~ instruction/(condition*lie_ability) + style + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "lie_ability", "DT_RT")
```

### Lie frequency
When instructed to lie, participants with higher lie frequency show no significant difference in confidence between social and polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_confidence ~ instruction/(condition*lie_frequency) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "lie_frequency", "DT_confidence")
```

Participants with higher lie frequency show significant increase in RT for both lie and truth.
When instructed to lie, the increase in RT in participants with higher lie frequency is more in polygraph than social condition.
```{r warning=FALSE}
model <- glmmTMB(DT_RT ~ instruction/(condition*lie_frequency) + style + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "lie_frequency", "DT_RT")
```

### Lie negativity
When instructed to lie, participants with higher perception of lie negativity show no significant difference in confidence between social and polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_confidence ~ instruction/(condition*lie_negativity) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "lie_negativity", "DT_confidence")
```

Participants with higher perception of lie negativity show significant decrease in RT for both lie and truth.
When instructed to lie, the decrease in RT in participants with higher perception of lie negativity is more in polygraph than social condition.
```{r warning=FALSE}
model <- glmmTMB(DT_RT ~ instruction/(condition*lie_negativity) + style + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "lie_negativity", "DT_RT")
```

### Lie contextuality
When instructed to lie, participants with higher lie contextuality show no significant difference in confidence between social and polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_confidence ~ instruction/(condition*lie_contextuality) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "lie_contextuality", "DT_confidence")
```

When instructed to lie, the decrease in RT in participants with higher lie contextuality is more in social than polygraph condition.
```{r warning=FALSE}
model <- glmmTMB(DT_RT ~ instruction/(condition*lie_contextuality) + style + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
plot_behv(model, "lie_contextuality", "DT_RT")
```

### 2021-11-03 index.Rmd
added functions, more iv
other HCT measures, lie scale

@@
 library(performance)
-library(bayestestR)
-library(see)
+# library(bayestestR)
+# library(see)
 
@@
 ```{r warning=FALSE, message=TRUE, results='asis'}
+setwd("C:/Users/user/Desktop/Sputnik/2019-23/DeceptionInteroTom")
 df <- read.csv("data/data_combined.csv") %>% 
@@
 
-Notice the `{.tabset}` tag after the section name.
-This will show the subsections as different tabs (in the [html version](https://realitybending.github.io/TemplateResults/#Descriptive_Stats) only, because the other formats are static).
-
 ```{r child=if (fast == FALSE) '1_descriptive.Rmd'}
@@
 
-# Inferential Stats {.tabset}
+# Inferential Stats (Experimental) {.tabset}
 
-```{r child=if (fast == FALSE) '2_inferential.Rmd'}
+```{r child=if (fast == FALSE) '2_inferential_expt.Rmd'}
+```
+
+# Inferential Stats (Behavioural) {.tabset}
+
+Effect on confidence and RT
+
+```{r child=if (fast == FALSE) '3_inferential_behv.Rmd'}
 ```

### 2021-11-03 scripts/claudia/data processing.Rmd
added functions, more iv
other HCT measures, lie scale

@@
 ```{r combine data}
+qn <- paste0("Q", 1:40)
 data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
@@
   left_join(read.csv("BES_processed.csv")) %>% 
-  select(-c(contains("Q"))) %>% 
+  select(-c(contains(paste0("Q", 0:9)))) %>%
   left_join(read.csv("HCT_processed.csv")) %>% 
   left_join(read.csv("MAIA2_processed.csv")) %>% 
-  select(-c(contains("Q"))) %>% 
+  select(-c(contains(paste0("Q", 0:9)))) %>%
+  left_join(read.csv("liescale_processed.csv")) %>% 
+  select(-c(contains(paste0("Q", 0:9)))) %>%
   left_join(read.csv("demo.csv")) %>% 

### 2021-11-10 scripts/claudia/HCT_Part2.py
format hct part 2 data

@@ -1,0 +1,63 @@
+import os
+
+import matplotlib.pyplot as plt
+import neurokit2 as nk
+import numpy as np
+import pandas as pd
+
+### Get psychopy data files
+directory = os.getcwd()
+list_participants = os.listdir(directory + "/../../data/data_experimental")
+
+### Utilities
+
+def extract_taps(key, rt, started, task="Guess"):
+    """keys: column name corresponding to when "space" is entered
+    rt: column name corresponding to the cumulative time points when space is entered
+    started: onset of trial wrt beginning of experiment
+    """
+    taps_n = len(data[key].dropna().iloc[0].split(','))
+    taps = np.arange(1, taps_n + 1)
+
+    start_task_time = data[started].dropna().iloc[0]
+    tap_times = pd.DataFrame(data[rt].dropna())
+    tap_times = np.array([start_task_time + float(i) for i in tap_times[rt].iloc[0].replace('[', '').replace(']', '').split(',')])
+
+    df = pd.DataFrame([taps, tap_times]).T
+    df.columns = ['Tap_Number', 'Tap_Times']
+    df['Condition'] = task
+
+    return df
+
+df_all = pd.DataFrame()
+### Loop through participants and extract data
+for i, participant in enumerate(list_participants):
+    data = pd.read_csv(directory + "/../../data/data_experimental/" + participant + "/heartbeat/" + participant + "_heartbeat.csv")
+
+    data = data[["key_guess.keys", "key_guess.rt", "key_guess.started", # guessing condition
+                 "key_noguess.keys", "key_noguess.rt", "key_noguess.started", # no guessing condition
+                 "key_noguess_perturbed.keys", "key_noguess_perturbed.rt", "key_noguess_perturbed.started"]] # perturbed condition
+
+    # Format data from three conditions
+    if 'None' in np.array(data['key_guess.keys']):
+        df_guess = pd.DataFrame([])
+    else:
+        df_guess = extract_taps("key_guess.keys", "key_guess.rt", "key_guess.started", task="Guess")
+
+    if 'None' in np.array(data['key_noguess.keys']):
+        df_noguess = pd.DataFrame([])
+    else:
+        df_noguess = extract_taps("key_noguess.keys", "key_noguess.rt", "key_noguess.started", task="NoGuess")
+
+    if 'None' in np.array(data['key_noguess_perturbed.keys']):
[…]

### 2021-11-11 scripts/claudia/HCT_Part2.py
HBC part 1 and 2 scripts
heartbeat_tracking to be updated

@@ -1,63 +1,0 @@
-import os
-
-import matplotlib.pyplot as plt
-import neurokit2 as nk
-import numpy as np
-import pandas as pd
-
-### Get psychopy data files
-directory = os.getcwd()
-list_participants = os.listdir(directory + "/../../data/data_experimental")
-
-### Utilities
-
-def extract_taps(key, rt, started, task="Guess"):
-    """keys: column name corresponding to when "space" is entered
-    rt: column name corresponding to the cumulative time points when space is entered
-    started: onset of trial wrt beginning of experiment
-    """
-    taps_n = len(data[key].dropna().iloc[0].split(','))
-    taps = np.arange(1, taps_n + 1)
-
-    start_task_time = data[started].dropna().iloc[0]
-    tap_times = pd.DataFrame(data[rt].dropna())
-    tap_times = np.array([start_task_time + float(i) for i in tap_times[rt].iloc[0].replace('[', '').replace(']', '').split(',')])
-
-    df = pd.DataFrame([taps, tap_times]).T
-    df.columns = ['Tap_Number', 'Tap_Times']
-    df['Condition'] = task
-
-    return df
-
-df_all = pd.DataFrame()
-### Loop through participants and extract data
-for i, participant in enumerate(list_participants):
-    data = pd.read_csv(directory + "/../../data/data_experimental/" + participant + "/heartbeat/" + participant + "_heartbeat.csv")
-
-    data = data[["key_guess.keys", "key_guess.rt", "key_guess.started", # guessing condition
-                 "key_noguess.keys", "key_noguess.rt", "key_noguess.started", # no guessing condition
-                 "key_noguess_perturbed.keys", "key_noguess_perturbed.rt", "key_noguess_perturbed.started"]] # perturbed condition
-
-    # Format data from three conditions
-    if 'None' in np.array(data['key_guess.keys']):
-        df_guess = pd.DataFrame([])
-    else:
-        df_guess = extract_taps("key_guess.keys", "key_guess.rt", "key_guess.started", task="Guess")
-
-    if 'None' in np.array(data['key_noguess.keys']):
-        df_noguess = pd.DataFrame([])
-    else:
-        df_noguess = extract_taps("key_noguess.keys", "key_noguess.rt", "key_noguess.started", task="NoGuess")
-
-    if 'None' in np.array(data['key_noguess_perturbed.keys']):
[…]

### 2021-11-11 scripts/claudia/heartbeat_counting.py

@@ -1,0 +1,35 @@
+# Load dependencies
+import os
+
+import matplotlib.pyplot as plt
+import neurokit2 as nk
+import numpy as np
+import pandas as pd
+
+# Set working directory
+directory = os.getcwd()
+list_participants = os.listdir(directory + "/../../data/data_experimental")
+participant = '001'
+subdir = directory + "/../../data/data_experimental/" + participant + "/heartbeat/"
+
+# Load data
+filename = [i for i in os.listdir(subdir) if i.endswith('.txt')][0]
+bio, sampling_rate = nk.read_bitalino(subdir + "/" + filename)
+
+# Clean ecg signal
+ecg_cleaned = nk.ecg_clean(bio["ECGBIT"], sampling_rate=sampling_rate)
+
+# Epoching
+events = nk.events_find(bio["LUX"], event_conditions=['start', 'stop'] * 8)
+event_conditions = np.array(['start', 'stop'] * 8)
+events_start = np.array(events["onset"])[event_conditions == 'start']
+events_duration = np.array(events["onset"])[event_conditions == 'stop'] - events_start
+
+peaks_total = np.repeat(np.nan, len(events_start[:5]))
+for i, start in enumerate(events_start[:5]):
+    epoch = ecg_cleaned[start:start+events_duration[i]]
+    peaks, info = nk.ecg_peaks(epoch, sampling_rate=sampling_rate)
+    peaks_total[i] = len(info["ECG_R_Peaks"])
+    print(peaks_total)
+
+# Get behavioural data

### 2021-11-11 scripts/claudia/heartbeat_tracking.py

@@ -1,0 +1,124 @@
+# Load dependencies
+import os
+
+import matplotlib.pyplot as plt
+import neurokit2 as nk
+import numpy as np
+import pandas as pd
+from opensignalsreader import OpenSignalsReader
+
+### Get psychopy data files ---------------------------------------------------
+directory = os.getcwd()
+list_participants = os.listdir(directory + "/../../data/data_experimental")
+
+### Utilities -----------------------------------------------------------------
+def extract_taps(data, key, rt, started, task="Guess"):
+    """keys: column name corresponding to when "space" is entered
+    rt: column name corresponding to the cumulative time points when space is entered
+    started: onset of trial wrt beginning of experiment
+    task: can be "Guess", "NoGuess", or "NoGuess_Perturbed"
+    """
+    if 'None' in np.array(data[key]):
+        return pd.DataFrame([])  # return empty if no taps
+    else:
+        taps_n = len(data[key].dropna().iloc[0].split(','))
+        taps = np.arange(1, taps_n + 1)
+
+        # '.started' corresponds to timing of last tap of the condition
+        last_tap_time = data[started].dropna().iloc[0]
+
+        # get cumulative time points of taps
+        tap_times = pd.DataFrame(data[rt].dropna())
+        tap_times = np.array([float(i) for i in tap_times[rt].iloc[0].replace('[', '').replace(']', '').split(',')])
+        lapsed = last_tap_time - tap_times[-1]
+        tap_times = np.array([i + lapsed for i in tap_times])
+
+        # Tidy df
+        df = pd.DataFrame([taps, tap_times]).T
+        df.columns = ['Tap_Number', 'Tap_Times']
+        df['Condition'] = task
+        return df
+
+def align_taps(df, epochs, sampling_rate):
+    # Align ecg to taps
+    tap_times = np.array(df['Tap_Times'] * sampling_rate)
+    taps = nk.find_closest(tap_times, np.array(epochs.index))
+    epochs["Tap"] = 0
+    for i in taps:
+        epochs.loc[i, "Tap"] = 1
+
+    # Condition column
+    epochs["Condition"] = np.unique(df['Condition'])[0]
+
+    return epochs
+
+
+### Loop through participants and extract data --------------------------------
+df_psychopy = pd.DataFrame()
[…]

### 2021-11-11 1_Measures.Rmd
Revise analysis script

---
output: html_document
editor_options: 
  chunk_output_type: console
---

## Theory of Mind / Empathy

### Yoni Task

```{r message=FALSE}
df %>% 
  group_by(Participant) %>% 
  select(starts_with("YONI_")) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_longer(-Participant, values_to = "Scores") |> 
  mutate(name = paste0(str_replace(name, "_", " ("), ")")) |> 
  ggplot(aes(x = Scores, fill = name)) +
  geom_density() +
  scale_fill_manual(values = c("YONI (Affective)" = "Purple",
                                 "YONI (Cognitive)" = "Blue",
                                 "YONI (Physical)" = "Green",
                                 "YONI (Total)"= "DarkBlue"),
                      guide = "none") +
  facet_wrap(~name, scales = "free")
```

### BES Questionnaire

```{r message=FALSE}
df %>% 
  group_by(Participant) %>% 
  select(starts_with("BES_")) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_longer(-Participant, values_to = "Scores") |> 
  mutate(name = paste0(str_replace(name, "_", " ("), ")")) |> 
  ggplot(aes(x = Scores, fill = name)) +
  geom_density() +
  scale_fill_manual(values = c("BES (Affective)" = "Purple",
                               "BES (Cognitive)" = "Blue",
                               "BES (Total)"= "DarkBlue"),
                      guide = "none") +
  facet_wrap(~name, scales = "free")
```

## Interoception

### Heartbeat Counting Task (HCT)

```{r message=FALSE}
df %>% 
  group_by(Participant) %>% 
  select(starts_with("HCT_")) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_longer(-Participant, values_to = "Scores") |> 
  mutate(name = paste0(str_replace(name, "_", " ("), ")")) |> 
  ggplot(aes(x = Scores, fill = name)) +
  geom_density() +
  scale_fill_manual(values = c("HCT (Accuracy)" = "Red",
                               "HCT (Awareness)" = "Orange",
                               "HCT (Confidence)"= "DarkOrange"),
                      guide = "none") +
  facet_wrap(~name, scales = "free")
```

### MAIA

```{r message=FALSE}
df %>% 
  group_by(Participant) %>% 
  select(starts_with("MAIA_")) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_longer(-Participant, values_to = "Scores") |> 
  mutate(name = paste0(str_replace(name, "_", " ("), ")")) |> 
  ggplot(aes(x = Scores, fill = name)) +
  geom_density() +
  scale_fill_brewer(palette = "Reds", guide = "none") +
  facet_wrap(~name, scales = "free")
```

## Deception

### LIE Scale

```{r message=FALSE}
df %>% 
  group_by(Participant) %>% 
  select(starts_with("LIE_")) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_longer(-Participant, values_to = "Scores") |> 
  mutate(name = paste0(str_replace(name, "_", " ("), ")")) |> 
  ggplot(aes(x = Scores, fill = name)) +
  geom_density() +
  scale_fill_manual(values = c("LIE (Ability)" = "#2196F3",
                               "LIE (Frequency)" = "#4CAF50",
                               "LIE (Contextuality)"= "#FF9800",
                               "LIE (Negativity)"= "#E91E63"),
                    guide = "none") +
  facet_wrap(~name, scales = "free")
```

### Deception Task

#### Summary Table

```{r warning=FALSE}

df |> 
  group_by(Participant, Answer) |> 
  summarise(Confidence = paste(insight::format_value(mean(Confidence, na.rm = TRUE)),
                               " +- ",
                               insight::format_value(sd(Confidence, na.rm = TRUE))),
            RT = paste(insight::format_value(mean(RT, na.rm = TRUE)),
                       " +- ",
                       insight::format_value(sd(RT, na.rm = TRUE)))) |> 
  arrange(Participant) |> 
  knitr::kable()
```

#### Outliers

```{r warning=FALSE}
df <- df |> 
  dplyr::filter(Participant != "S9",  # Extreme answers
                !Participant %in% c("S3", "S15", "S19", "S23"))  # No data
```

#### Distributions

```{r warning=FALSE}
p1 <- df |> 
  dplyr::filter(!Participant %in% c("S29")) |>
  ggplot(aes(x = Confidence, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  see::theme_modern() +
  scale_x_continuous(labels = scales::percent, expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p2 <- df |> 
  dplyr::filter(!Participant %in% c("S29")) |> 
  ggplot(aes(x = RT, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p1 / p2
```

### 2021-11-11 2_ManipulationChecks.Rmd
Revise analysis script

---
output: html_document
editor_options: 
  chunk_output_type: console
---

## Correlation {.tabset}

```{r message=FALSE, warning=FALSE}
dfsub <- df |> 
  select(Participant, 
         starts_with("YONI_"), 
         starts_with("BES_"),
         starts_with("HCT_"),
         starts_with("MAIA_"),
         starts_with("LIE_")) |> 
  group_by(Participant) |> 
  summarise_all(mean)
```

### Theory of Mind / Empathy

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("YONI_")),
                 select(dfsub, starts_with("BES_")), 
                 p_adjust = "none")

summary(r) |> 
  plot()
```

### Interoception

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("MAIA_")),
                 select(dfsub, starts_with("HCT_")), 
                 p_adjust = "none")

summary(r) |> 
  plot()
```

### ToM and Interoception

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with(c("MAIA_", "HCT_"))),
                 select(dfsub, starts_with(c("YONI_", "BES_"))), 
                 p_adjust = "none")

summary(r) |> 
  plot()
```

## Phrasing {.tabset}

- Main effect of phrasing on RT only. Indirect questions lead to slower answers.

### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer * Phrasing + (1|Participant) + (1|Item), data = df)

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
estimate_means(model, at = c("Answer", "Phrasing")) |> 
  plot(show_data = "none") 
```

### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer * Phrasing + (1|Participant) + (1|Item), data = df)

parameters::parameters(model)
```

```{r message=FALSE, warning=FALSE}
estimate_means(model, at = c("Answer", "Phrasing")) |> 
  plot(show_data = "none") 
```

## Lies and RT

- The faster they answer, the more confident they are in their lies.

```{r message=FALSE, warning=FALSE}
# Adjustments for beta models
df$Confidence[df$Confidence == 1] <- 0.99999
df$Confidence[df$Confidence == 0] <- 0.00001

model <- glmmTMB(Confidence ~ RT * Answer + Phrasing + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("RT", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```

## Effect of Condition

### Confidence

- Significant interaction between the condition and the answer: the effect of answer (being more confident in truths than in lies) is lower in the social condition.
- Effect mostly driven by the social condition that increases the confidence in lies. 
- In other words: harder to lie in the polygraph condition: less obvious feedback cues?

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer * Condition + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
estimate_means(model, at = c("Condition", "Answer")) |> 
  plot(show_data = "none") 
```

### RT

- Significant main effect of the condition: people are slower in the polygraph condition.
- Consistent with the "less intuitive cues".

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer * Condition + (1|Participant) + (1|Item), 
                 data = df)

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
estimate_means(model, at = c("Condition", "Answer")) |> 
  plot(show_data = "none") 
```

### 2021-11-11 3_ToM.Rmd
Revise analysis script

---
output: html_document
editor_options: 
  chunk_output_type: console
---

## Yoni Task {.tabset}

- When instructed to lie, the decrease in confidence in participants with higher yoni score is less in social than polygraph condition.

### Correlation with LIE Scale

```{r message=FALSE, warning=FALSE}
get_correlation <- function(var = "YONI_", var2 = "LIE_") {
  r <- correlation(select(dfsub, starts_with(var2)),
                 select(dfsub, starts_with(var)), 
                 p_adjust = "none") |> 
  mutate(Parameter1 = paste0(str_replace(Parameter1, "_", " ("), ")"),
         Parameter2 = paste0(str_replace(Parameter2, "_", " ("), ")"))

  p <- summary(r) |> 
    plot() +
    theme_minimal()
  list(r = r, plot = p)
}

r <- get_correlation(var = "YONI_")
r$plot
```

### Total Score

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Total) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

get_parameters <- function(model) {
  # Parameters
  params <- parameters::parameters(model, effects = "fixed") 
  # Marginal effects
  at <- c("Answer", "Condition")
  trend <- insight::find_predictors(model)$conditional
  trend <- trend[!trend %in% at]
  marg <- modelbased::estimate_slopes(model, trend = trend, at = at)
  # Output
  list(params = params, marginal_effects = marg)
}

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect <- function(model, var = "YONI_Total", outcome = "Confidence") {
  data <- df |> 
    group_by(Participant, Answer, Condition) |> 
    summarise({{var}} := mean(.data[[var]], na.rm = TRUE),
              SD = sd(.data[[outcome]], na.rm = TRUE),
              {{outcome}} := mean(.data[[outcome]], na.rm = TRUE),
              CI_low = .data[[outcome]] - SD / 2,
              CI_high = .data[[outcome]] + SD / 2)

  dodge_width <- 0.02 * diff(range(data[[var]]))
  ylab <- ifelse(outcome == "RT", "Reaction Time (s)", "Confidence")

  link_data <- estimate_relation(model, at = c("Condition", var, "Answer"), length = 30)
  ggplot(link_data, aes_string(x = var, y = "Predicted")) +
    geom_pointrange(data = data, aes_string(y = outcome, color = "Condition", ymin = "CI_low", ymax = "CI_high"), position = position_dodge(width = dodge_width)) +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.33) + 
    geom_line(aes(color = Condition)) +
    labs(y = ylab, x = paste0(stringr::str_replace(var, "_", " ("), ")")) +
    scale_color_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) +
    scale_fill_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) +
    facet_wrap(~Answer) 
}

plot_effect(model, var = "YONI_Total", outcome = "Confidence")
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * YONI_Total) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "YONI_Total", outcome = "RT")
```

## BES {.tabset}

### Total Score

#### LIE Scale

```{r message=FALSE, warning=FALSE}
r <- get_correlation(var = "BES_")
r$plot
```

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * BES_Total) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "BES_Total", outcome = "Confidence")
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * BES_Total) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "BES_Total", outcome = "RT")
```

### 2021-11-11 4_Intero.Rmd
Revise analysis script

---
output: html_document
editor_options: 
  chunk_output_type: console
---

## Heartbeat Counting {.tabset}

### Correlation with LIE Scale

```{r message=FALSE, warning=FALSE}
r <- get_correlation(var = "HCT_")
r$plot

# plot(correlation::cor_test(dfsub, "HCT_Accuracy", "LIE_Ability"))
```

### Accuracy

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * HCT_Accuracy) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "HCT_Accuracy", outcome = "Confidence")
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * HCT_Accuracy) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "HCT_Accuracy", outcome = "RT")
```

### Interoceptive Confidence

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * HCT_Confidence) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "HCT_Confidence", outcome = "Confidence")
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * HCT_Confidence) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "HCT_Confidence", outcome = "RT")
```

### Interoceptive Awareness

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * HCT_Awareness) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "HCT_Awareness", outcome = "Confidence")
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * HCT_Awareness) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "HCT_Awareness", outcome = "RT")
```

## MAIA {.tabset}

### Correlation with LIE Scale

```{r message=FALSE, warning=FALSE}
r <- get_correlation(var = "MAIA_")
r$plot +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```

### Total Score

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_Total) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "MAIA_Total", outcome = "Confidence")
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * MAIA_Total) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "MAIA_Total", outcome = "RT")
```

### Noticing

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_Noticing) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "MAIA_Noticing", outcome = "Confidence")
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * MAIA_Noticing) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "MAIA_Noticing", outcome = "RT")
```

### Not Distracting

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_NotDistracting) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "MAIA_NotDistracting", outcome = "Confidence")
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * MAIA_NotDistracting) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "MAIA_NotDistracting", outcome = "RT")
```

### 2021-11-11 index.Rmd
Revise analysis script

@@
 ---
-title: '**Results Template**'
+title: '**The Place of Interoception and Theory of Mind in Deception**'
 subtitle: A Subtitle
@@
 source("https://raw.githubusercontent.com/RealityBending/TemplateResults/main/utils/config.R")  
-
-fast <- FALSE  # Make this false to skip the chunks
+options(dplyr.summarise.inform = FALSE) 
+knitr::opts_chunk$set(echo = TRUE)
+library(ggplot2)
+theme_set(see::theme_modern())
 ```
@@
 
+<!-- Title ideas:-->
+<!-- Theory of Body and Others -->
+
 # Packages & Data
@@
 library(parameters)
+library(correlation)
 library(modelbased)
 library(performance)
-# library(bayestestR)
-# library(see)
+library(see)
 
@@
 ```{r warning=FALSE, message=TRUE, results='asis'}
-setwd("C:/Users/user/Desktop/Sputnik/2019-23/DeceptionInteroTom")
+# setwd("C:/Users/user/Desktop/Sputnik/2019-23/DeceptionInteroTom")
+
 df <- read.csv("data/data_combined.csv") %>% 
-  mutate(ID = as.factor(ID),
+  mutate(ID = as.factor(paste0("S", ID)),
          condition = as.factor(condition),
@@
          style = as.factor(style),
-         instruction = as.factor(instruction))
+         instruction = as.factor(instruction)) |> 
+  #TODO: This renaming should be done at the preprocessing stage
+  rename("Participant" = "ID",
+         "Condition" = "condition",
+         "Item" = "item",
+         "Phrasing" = "style",
+         "Answer" = "instruction",
+         "YONI_Total" = "yoni_total",
+         "YONI_Affective" = "yoni_affective",
+         "YONI_Cognitive" = "yoni_cognitive",
+         "YONI_Physical" = "yoni_physical",
+         "BES_Total" = "BES_total",
+         "BES_Cognitive" = "BES_cognitive",
+         "BES_Affective" = "BES_affective",
+         "HCT_Confidence" = "HCT_confidence",
+         "HCT_Accuracy" = "HCT_accuracy",
+         "HCT_Awareness" = "HCT_awareness",
+         "MAIA_Total" = "MAIA_total",
+         "MAIA_AttentionRegulation" = "MAIA_attention_regulation",
+         "MAIA_BodyListening" = "MAIA_body_listening",
+         "MAIA_EmotionalAwareness" = "MAIA_emotional_awareness",
+         "MAIA_NotDistracting" = "MAIA_not_distracting",
+         "MAIA_NotWorrying" = "MAIA_not_worrying",
+         "MAIA_Noticing" = "MAIA_noticing",
+         "MAIA_SelfRegulation" = "MAIA_self_regulation",
+         "MAIA_Trusting" = "MAIA_trusting",
+         "LIE_Ability" = "lie_ability",
+         "LIE_Frequency" = "lie_frequency",
+         "LIE_Negativity" = "lie_negativity",
+         "LIE_Contextuality" = "lie_contextuality",
+         "Confidence" = "DT_confidence",
+         "RT" = "DT_RT") |> 
+  mutate(Answer = fct_recode(Answer, Lie = "LIE", Truth = "TRUTH")) |> 
+  select(-HCT_guess, -HCT_noguess, -HCT_onebreath)
 
@@
           report::report_participants(df,
-                                      participants = "ID",
+                                      participants = "Participant",
                                       sex = "Gender",
@@
 
-Note that the chunks generating figures in the code below have some arguments specified in their header, such as `fig.width` and `fig.height`, which controls the figure size.
-These were filled with an eponym argument defined in [`utils/config.R`](https://github.com/RealityBending/TemplateResults/blob/main/utils/config.R#L26-L27).
-We also set the resolution, i.e., `dpi`, to a low value so that the resulting file is lighter.
-But **don't forget to crank this value up** (to 300-600) to get nice-looking results.
+# Measures {.tabset}
 
-# Descriptive Stats {.tabset}
-
-```{r child=if (fast == FALSE) '1_descriptive.Rmd'}
+```{r child='1_Measures.Rmd'}
 ```
 
-# Inferential Stats (Experimental) {.tabset}
+<!-- # Manipulation Checks -->
 
-```{r child=if (fast == FALSE) '2_inferential_expt.Rmd'}
-```
+<!-- ```{r child='2_ManipulationChecks.Rmd'} -->
+<!-- ``` -->
 
-# Inferential Stats (Behavioural) {.tabset}
+<!-- # Theory of Mind / Empathy -->
 
-Effect on confidence and RT
+<!-- ```{r child='3_ToM.Rmd'} -->
+<!-- ``` -->
 
-```{r child=if (fast == FALSE) '3_inferential_behv.Rmd'}
-```
+<!-- # Interoception -->
+
+<!-- ```{r child='4_Intero.Rmd'} -->
+<!-- ``` -->
 

### 2021-11-11 scripts/claudia/heartbeat_tracking.py
heartbeat tracking script

@@ -5,120 +5,135 @@ import matplotlib.pyplot as plt
 import neurokit2 as nk
 import numpy as np
 import pandas as pd
-from opensignalsreader import OpenSignalsReader
+pd.options.mode.chained_assignment = None  # default='warn'
 
 ### Get psychopy data files ---------------------------------------------------
 directory = os.getcwd()
 list_participants = os.listdir(directory + "/../../data/data_experimental")
 
 ### Utilities -----------------------------------------------------------------
-def extract_taps(data, key, rt, started, task="Guess"):
+def extract_taps(data, key, rt):
     """keys: column name corresponding to when "space" is entered
     rt: column name corresponding to the cumulative time points when space is entered
-    started: onset of trial wrt beginning of experiment
-    task: can be "Guess", "NoGuess", or "NoGuess_Perturbed"
     """
     if 'None' in np.array(data[key]):
-        return pd.DataFrame([])  # return empty if no taps
+        return np.array([])  # return empty if no taps
     else:
-        taps_n = len(data[key].dropna().iloc[0].split(','))
-        taps = np.arange(1, taps_n + 1)
-
-        # '.started' corresponds to timing of last tap of the condition
-        last_tap_time = data[started].dropna().iloc[0]
-
         # get cumulative time points of taps
         tap_times = pd.DataFrame(data[rt].dropna())
         tap_times = np.array([float(i) for i in tap_times[rt].iloc[0].replace('[', '').replace(']', '').split(',')])
-        lapsed = last_tap_time - tap_times[-1]
-        tap_times = np.array([i + lapsed for i in tap_times])
 
-        # Tidy df
-        df = pd.DataFrame([taps, tap_times]).T
-        df.columns = ['Tap_Number', 'Tap_Times']
-        df['Condition'] = task
-        return df
+        return tap_times
 
-def align_taps(df, epochs, sampling_rate):
+def align_taps(ecg, start, stop, sampling_rate, taps, task="Guess"):
+    """ecg: ecg signal
+    start: onset time of the task
+    stop: end time of the task
+    taps: array of tap timings obtained from `extract_taps()`
+    task: name of the task condition (appended to final dataframe)
+    """
+
+    # Process ecg signal
[…]

### 2021-11-11 scripts/claudia/heartbeat_tracking.py
processed hct pt2

@@ -136,4 +136,5 @@ for i, participant in enumerate(list_participants):
     
     df_all = pd.concat([df_all, df])  # combine all participants
 
-df_all.to_csv("HCT_Part2.csv", na_rep="NA", index=False)
+# df_all.to_csv("HCT_Part2.csv", na_rep="NA", index=False)  too big file
+nk.write_csv(df_all, "Heartbeat_Tracking", parts=5)  # split into subsets of csvs

### 2021-11-11 scripts/claudia/heartbeat_counting.py
real heartbeat data

@@ -9,27 +9,29 @@ import pandas as pd
 # Set working directory
 directory = os.getcwd()
 list_participants = os.listdir(directory + "/../../data/data_experimental")
-participant = '001'
-subdir = directory + "/../../data/data_experimental/" + participant + "/heartbeat/"
-
+HCT_real = {"time": np.array([20, 25, 30, 35, 40])}
+for participant in list_participants:
+    subdir = directory + "/../../data/data_experimental/" + participant + "/heartbeat/"
+    
 # Load data
-filename = [i for i in os.listdir(subdir) if i.endswith('.txt')][0]
-bio, sampling_rate = nk.read_bitalino(subdir + "/" + filename)
-
+    filename = [i for i in os.listdir(subdir) if i.endswith('.txt')][0]
+    bio, sampling_rate = nk.read_bitalino(subdir + "/" + filename)
+    
 # Clean ecg signal
-ecg_cleaned = nk.ecg_clean(bio["ECGBIT"], sampling_rate=sampling_rate)
-
+    ecg_cleaned = nk.ecg_clean(bio["ECGBIT"], sampling_rate=sampling_rate)
+    
 # Epoching
-events = nk.events_find(bio["LUX"], event_conditions=['start', 'stop'] * 8)
-event_conditions = np.array(['start', 'stop'] * 8)
-events_start = np.array(events["onset"])[event_conditions == 'start']
-events_duration = np.array(events["onset"])[event_conditions == 'stop'] - events_start
-
-peaks_total = np.repeat(np.nan, len(events_start[:5]))
-for i, start in enumerate(events_start[:5]):
-    epoch = ecg_cleaned[start:start+events_duration[i]]
-    peaks, info = nk.ecg_peaks(epoch, sampling_rate=sampling_rate)
-    peaks_total[i] = len(info["ECG_R_Peaks"])
-    print(peaks_total)
-
-# Get behavioural data
+    events = nk.events_find(bio["LUX"], duration_min = 3, event_conditions=['start', 'stop'] * 8)
+    event_conditions = np.array(['start', 'stop'] * 8)
+    events_start = np.array(events["onset"])[event_conditions == 'start']
+    events_duration = np.array(events["onset"])[event_conditions == 'stop'] - events_start
+    
+    peaks_total = np.repeat(np.nan, len(events_start[:5]))
+    for i, start in enumerate(events_start[:5]):
[…]

### 2021-11-11 3_ToM.Rmd
update script

@@
 - When instructed to lie, the decrease in confidence in participants with higher yoni score is less in social than polygraph condition.
-
-### Correlation with LIE Scale
-
-```{r message=FALSE, warning=FALSE}
-get_correlation <- function(var = "YONI_", var2 = "LIE_") {
-  r <- correlation(select(dfsub, starts_with(var2)),
-                 select(dfsub, starts_with(var)), 
-                 p_adjust = "none") |> 
-  mutate(Parameter1 = paste0(str_replace(Parameter1, "_", " ("), ")"),
-         Parameter2 = paste0(str_replace(Parameter2, "_", " ("), ")"))
-
-  p <- summary(r) |> 
-    plot() +
-    theme_minimal()
-  list(r = r, plot = p)
-}
-
-r <- get_correlation(var = "YONI_")
-r$plot
-```
 
@@
 
-plot_effect(model, var = "YONI_Total", outcome = "Confidence")
+p_conf_yoni_total <- plot_effect(model, var = "YONI_Total", outcome = "Confidence")
+# p_conf_yoni_total
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "YONI_Total", outcome = "RT")
+p_rt_yoni_total <- plot_effect(model, var = "YONI_Total", outcome = "RT")
+# p_rt_yoni_total
+```
+
+### Cognitive Theory of Mind
+
+#### Confidence
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Cognitive) + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_conf_yoni_cognitive <- plot_effect(model, var = "YONI_Cognitive", outcome = "Confidence")
+# p_conf_yoni_cognitive
+```
+
+#### RT
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(RT ~ Answer / (Condition * YONI_Cognitive) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_rt_yoni_cognitive <- plot_effect(model, var = "YONI_Cognitive", outcome = "RT")
+# p_rt_yoni_cognitive
+```
+
+### Affective Theory of Mind
+
+#### Confidence
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Affective) + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_conf_yoni_affective <- plot_effect(model, var = "YONI_Affective", outcome = "Confidence")
+# p_conf_yoni_affective
+```
+
+#### RT
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(RT ~ Answer / (Condition * YONI_Affective) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_rt_yoni_affective <- plot_effect(model, var = "YONI_Affective", outcome = "RT")
+# p_rt_yoni_affective
+```
+
+### Physical Theory of Mind
+
+#### Confidence
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Physical) + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_conf_yoni_physical <- plot_effect(model, var = "YONI_Physical", outcome = "Confidence")
+# p_conf_yoni_physical
+```
+
+#### RT
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(RT ~ Answer / (Condition * YONI_Physical) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_rt_yoni_physical <- plot_effect(model, var = "YONI_Physical", outcome = "RT")
+# p_rt_yoni_physical
+```
+
+### Correlation with LIE Scale
+
+```{r message=FALSE, warning=FALSE}
+get_correlation <- function(var = "YONI_", var2 = "LIE_") {
+  r <- correlation(select(dfsub, starts_with(var2)),
+                 select(dfsub, starts_with(var)), 
+                 p_adjust = "none") |> 
+  mutate(Parameter1 = paste0(str_replace(Parameter1, "_", " ("), ")"),
+         Parameter2 = paste0(str_replace(Parameter2, "_", " ("), ")"))
+
+  p <- summary(r) |> 
+    plot() +
+    theme_minimal()
+  list(r = r, plot = p)
+}
+
+r <- get_correlation(var = "YONI_")
+r$plot
+```
+
+### Summary
+
+```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
+p_conf_yoni_total / 
+  p_conf_yoni_cognitive / 
+  p_conf_yoni_affective / 
+  p_conf_yoni_physical +
+  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))
+
+p_rt_yoni_total / 
+  p_rt_yoni_cognitive / 
+  p_rt_yoni_affective / 
+  p_rt_yoni_physical +
+  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))
 ```
@@
 ### Total Score
-
-#### LIE Scale
-
-```{r message=FALSE, warning=FALSE}
-r <- get_correlation(var = "BES_")
-r$plot
-```
 
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "BES_Total", outcome = "Confidence")
+p_conf_bes_total <- plot_effect(model, var = "BES_Total", outcome = "Confidence")
+# p_conf_bes_total
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "BES_Total", outcome = "RT")
+p_rt_bes_total <- plot_effect(model, var = "BES_Total", outcome = "RT")
+# p_rt_bes_total
 ```
+
+### Cognitive Empathy
+
+#### Confidence
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ Answer / (Condition * BES_Cognitive) + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_conf_bes_cognitive <- plot_effect(model, var = "BES_Cognitive", outcome = "Confidence")
+# p_conf_bes_cognitive
+```
+
+#### RT
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(RT ~ Answer / (Condition * BES_Cognitive) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_rt_bes_cognitive <- plot_effect(model, var = "BES_Cognitive", outcome = "RT")
+# p_rt_bes_cognitive
+```
+
+### Affective Empathy
+
+#### Confidence
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ Answer / (Condition * BES_Affective) + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_conf_bes_affective <- plot_effect(model, var = "BES_Affective", outcome = "Confidence")
+# p_conf_bes_affective
+```
+
+#### RT
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(RT ~ Answer / (Condition * BES_Affective) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_rt_bes_affective <- plot_effect(model, var = "BES_Affective", outcome = "RT")
+# p_rt_bes_affective
+```
+
+### Correlation with LIE Scale
+
+```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
+r <- get_correlation(var = "BES_")
+r$plot
+```
+
+### Summary
+
+```{r message=FALSE, warning=FALSE}
+p_conf_bes_total / 
+  p_conf_bes_cognitive / 
+  p_conf_bes_affective +
+  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))
+
+p_rt_bes_total / 
+  p_rt_bes_cognitive / 
+  p_rt_bes_affective +
+  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))
+```

### 2021-11-11 4_Intero.Rmd
update script

@@
 ## Heartbeat Counting {.tabset}
-
-### Correlation with LIE Scale
-
-```{r message=FALSE, warning=FALSE}
-r <- get_correlation(var = "HCT_")
-r$plot
-
-# plot(correlation::cor_test(dfsub, "HCT_Accuracy", "LIE_Ability"))
-```
 
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "HCT_Accuracy", outcome = "Confidence")
+p_conf_hct_accuracy <- plot_effect(model, var = "HCT_Accuracy", outcome = "Confidence")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "HCT_Accuracy", outcome = "RT")
+p_rt_hct_accuracy <- plot_effect(model, var = "HCT_Accuracy", outcome = "RT")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "HCT_Confidence", outcome = "Confidence")
+p_conf_hct_confidence <- plot_effect(model, var = "HCT_Confidence", outcome = "Confidence")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "HCT_Confidence", outcome = "RT")
+p_rt_hct_confidence <- plot_effect(model, var = "HCT_Confidence", outcome = "RT")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "HCT_Awareness", outcome = "Confidence")
+p_conf_hct_awareness <- plot_effect(model, var = "HCT_Awareness", outcome = "Confidence")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "HCT_Awareness", outcome = "RT")
+p_rt_hct_awareness <- plot_effect(model, var = "HCT_Awareness", outcome = "RT")
 ```
-
-## MAIA {.tabset}
 
@@
 ```{r message=FALSE, warning=FALSE}
-r <- get_correlation(var = "MAIA_")
-r$plot +
-  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
+r <- get_correlation(var = "HCT_")
+r$plot
+
+# plot(correlation::cor_test(dfsub, "HCT_Accuracy", "LIE_Ability"))
 ```
+
+### Summary
+
+```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
+p_conf_hct_accuracy / 
+  p_conf_hct_confidence / 
+  p_conf_hct_awareness +
+  patchwork::plot_annotation(title = "Interoception", theme = theme(plot.title = element_text(hjust = 0.5)))
+
+p_rt_hct_accuracy / 
+  p_rt_hct_confidence / 
+  p_rt_hct_awareness +
+  patchwork::plot_annotation(title = "Interoception", theme = theme(plot.title = element_text(hjust = 0.5)))
+```
+
+## MAIA {.tabset}
 
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "MAIA_Total", outcome = "Confidence")
+p_conf_maia_total <- plot_effect(model, var = "MAIA_Total", outcome = "Confidence")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "MAIA_Total", outcome = "RT")
+p_rt_maia_total <- plot_effect(model, var = "MAIA_Total", outcome = "RT")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "MAIA_Noticing", outcome = "Confidence")
+p_conf_maia_noticing <- plot_effect(model, var = "MAIA_Noticing", outcome = "Confidence")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "MAIA_Noticing", outcome = "RT")
+p_rt_maia_noticing <- plot_effect(model, var = "MAIA_Noticing", outcome = "RT")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "MAIA_NotDistracting", outcome = "Confidence")
+p_conf_maia_notdistracting <- plot_effect(model, var = "MAIA_NotDistracting", outcome = "Confidence")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect(model, var = "MAIA_NotDistracting", outcome = "RT")
+p_rt_maia_notdistracting <- plot_effect(model, var = "MAIA_NotDistracting", outcome = "RT")
 ```
+
+### Body Listening
+
+#### Confidence
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_BodyListening) + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_conf_maia_bodylistening <- plot_effect(model, var = "MAIA_BodyListening", outcome = "Confidence")
+```
+
+#### RT
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(RT ~ Answer / (Condition * MAIA_BodyListening) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_rt_maia_bodylistening <- plot_effect(model, var = "MAIA_BodyListening", outcome = "RT")
+```
+
+### Correlation with LIE Scale
+
+```{r message=FALSE, warning=FALSE}
+r <- get_correlation(var = "MAIA_")
+r$plot +
+  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
+```
+
+### Summary
+
+```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
+p_conf_maia_total / 
+  p_conf_maia_noticing / 
+  p_conf_maia_notdistracting / 
+  p_conf_maia_bodylistening +
+  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))
+
+p_rt_maia_total / 
+  p_rt_maia_noticing / 
+  p_rt_maia_notdistracting / 
+  p_rt_maia_bodylistening +
+  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))
+```

### 2021-11-11 index.Rmd
update script

@@
     number_sections: no
-    df_print: kable
+    df_print: default
     code_folding: hide
@@
 
-<!-- # Manipulation Checks -->
+# Manipulation Checks
 
-<!-- ```{r child='2_ManipulationChecks.Rmd'} -->
-<!-- ``` -->
+```{r child='2_ManipulationChecks.Rmd'}
+```
 
-<!-- # Theory of Mind / Empathy -->
+# Theory of Mind / Empathy
 
-<!-- ```{r child='3_ToM.Rmd'} -->
-<!-- ``` -->
+```{r child='3_ToM.Rmd'}
+```
 
-<!-- # Interoception -->
+# Interoception
 
-<!-- ```{r child='4_Intero.Rmd'} -->
-<!-- ``` -->
+```{r child='4_Intero.Rmd'}
+```
 

### 2021-11-11 scripts/claudia/data processing.Rmd

@@
 
-  select(ID, everything()) %>% #move ID column to front
+  select(ID, everything()) %>% # move ID column to front
 
@@
 
-HCT <- read.csv("../heartbeat/HCT.csv", stringsAsFactors = FALSE)[-c(2,8:10)] %>% 
-  rename(participant = Participant.number) %>%
-  pivot_longer(!participant, names_to = "task", values_to = "hbcount_real")
+HCT <- read.csv("HCT_real.csv") %>% 
+  pivot_longer(!task, names_to = "participant", values_to = "hbcount_real") %>%
+  arrange(participant)
 data <- cbind(data, HCT)

### 2021-11-11 3_ToM.Rmd
add significance stars to plots

@@
 ```{r message=FALSE, warning=FALSE}
-plot_effect <- function(model, var = "YONI_Total", outcome = "Confidence") {
+plot_effect <- function(model, results, var = "YONI_Total", outcome = "Confidence") {
   data <- df |> 
@@
 
-  dodge_width <- 0.02 * diff(range(data[[var]]))
-  ylab <- ifelse(outcome == "RT", "Reaction Time (s)", "Confidence")
+  link_data <- estimate_relation(model, at = c("Condition", var, "Answer"), length = 30)
+  range_x <- diff(range(data[[var]]))
 
-  link_data <- estimate_relation(model, at = c("Condition", var, "Answer"), length = 30)
-  ggplot(link_data, aes_string(x = var, y = "Predicted")) +
-    geom_pointrange(data = data, aes_string(y = outcome, color = "Condition", ymin = "CI_low", ymax = "CI_high"), position = position_dodge(width = dodge_width)) +
+  annot <- results$marginal_effects  
+  annot$Label <- insight::format_p(annot$p, stars_only = TRUE)
+  annot$x <- mean(range(data[[var]]))
+  annot$x <- ifelse(annot$Condition == "Polygraph", 
+                    annot$x - 0.05 * range_x, 
+                    annot$x + 0.05 * range_x)
+  annot$y <- max(data[[outcome]]) - 0.01 * diff(range(data[[outcome]]))
+
+  p <- ggplot(link_data, aes_string(x = var, y = "Predicted")) +
+    geom_pointrange(data = data, 
+                    aes_string(y = outcome, 
+                               color = "Condition", 
+                               ymin = "CI_low", 
+                               ymax = "CI_high"), 
+                    position = position_dodge(width = 0.02 * range_x)) +
     geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.33) + 
     geom_line(aes(color = Condition)) +
-    labs(y = ylab, x = paste0(stringr::str_replace(var, "_", " ("), ")")) +
+    geom_text(data=annot, aes(x = x, y = y, label = Label, color = Condition), 
+              size = 8, show.legend = FALSE) +
+    labs(y = ifelse(outcome == "RT", "Reaction Time (s)", "Confidence"), 
+         x = paste0(stringr::str_replace(var, "_", " ("), ")")) +
     scale_color_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) +
@@
     facet_wrap(~Answer)
+
+  # Narrow y range
+  if(outcome == "Confidence") {
+    p <- p +
+      coord_cartesian(ylim = c(0, 1)) +
+      scale_y_continuous(expand=expansion(c(0, 0))) 
+  }
+  p
 }
 
-p_conf_yoni_total <- plot_effect(model, var = "YONI_Total", outcome = "Confidence")
+p_conf_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "Confidence")
 # p_conf_yoni_total
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_yoni_total <- plot_effect(model, var = "YONI_Total", outcome = "RT")
+p_rt_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "RT")
 # p_rt_yoni_total
@@
 ```{r message=FALSE, warning=FALSE}
-p_conf_yoni_cognitive <- plot_effect(model, var = "YONI_Cognitive", outcome = "Confidence")
+p_conf_yoni_cognitive <- plot_effect(model, results, var = "YONI_Cognitive", outcome = "Confidence")
 # p_conf_yoni_cognitive
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_yoni_cognitive <- plot_effect(model, var = "YONI_Cognitive", outcome = "RT")
+p_rt_yoni_cognitive <- plot_effect(model, results, var = "YONI_Cognitive", outcome = "RT")
 # p_rt_yoni_cognitive
@@
 ```{r message=FALSE, warning=FALSE}
-p_conf_yoni_affective <- plot_effect(model, var = "YONI_Affective", outcome = "Confidence")
+p_conf_yoni_affective <- plot_effect(model, results, var = "YONI_Affective", outcome = "Confidence")
 # p_conf_yoni_affective
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_yoni_affective <- plot_effect(model, var = "YONI_Affective", outcome = "RT")
+p_rt_yoni_affective <- plot_effect(model, results, var = "YONI_Affective", outcome = "RT")
 # p_rt_yoni_affective
@@
 ```{r message=FALSE, warning=FALSE}
-p_conf_yoni_physical <- plot_effect(model, var = "YONI_Physical", outcome = "Confidence")
+p_conf_yoni_physical <- plot_effect(model, results, var = "YONI_Physical", outcome = "Confidence")
 # p_conf_yoni_physical
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_yoni_physical <- plot_effect(model, var = "YONI_Physical", outcome = "RT")
+p_rt_yoni_physical <- plot_effect(model, results, var = "YONI_Physical", outcome = "RT")
 # p_rt_yoni_physical
@@
 ```{r message=FALSE, warning=FALSE}
-p_conf_bes_total <- plot_effect(model, var = "BES_Total", outcome = "Confidence")
+p_conf_bes_total <- plot_effect(model, results, var = "BES_Total", outcome = "Confidence")
 # p_conf_bes_total
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_bes_total <- plot_effect(model, var = "BES_Total", outcome = "RT")
+p_rt_bes_total <- plot_effect(model, results, var = "BES_Total", outcome = "RT")
 # p_rt_bes_total
@@
 ```{r message=FALSE, warning=FALSE}
-p_conf_bes_cognitive <- plot_effect(model, var = "BES_Cognitive", outcome = "Confidence")
+p_conf_bes_cognitive <- plot_effect(model, results, var = "BES_Cognitive", outcome = "Confidence")
 # p_conf_bes_cognitive
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_bes_cognitive <- plot_effect(model, var = "BES_Cognitive", outcome = "RT")
+p_rt_bes_cognitive <- plot_effect(model, results, var = "BES_Cognitive", outcome = "RT")
 # p_rt_bes_cognitive
@@
 ```{r message=FALSE, warning=FALSE}
-p_conf_bes_affective <- plot_effect(model, var = "BES_Affective", outcome = "Confidence")
+p_conf_bes_affective <- plot_effect(model, results, var = "BES_Affective", outcome = "Confidence")
 # p_conf_bes_affective
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_bes_affective <- plot_effect(model, var = "BES_Affective", outcome = "RT")
+p_rt_bes_affective <- plot_effect(model, results, var = "BES_Affective", outcome = "RT")
 # p_rt_bes_affective
@@
 
-```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
+```{r message=FALSE, warning=FALSE}
 r <- get_correlation(var = "BES_")
@@
 
-```{r message=FALSE, warning=FALSE}
+```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
 p_conf_bes_total / 

### 2021-11-11 4_Intero.Rmd
add significance stars to plots

@@
 ```{r message=FALSE, warning=FALSE}
-p_conf_hct_accuracy <- plot_effect(model, var = "HCT_Accuracy", outcome = "Confidence")
+p_conf_hct_accuracy <- plot_effect(model, results, var = "HCT_Accuracy", outcome = "Confidence")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_hct_accuracy <- plot_effect(model, var = "HCT_Accuracy", outcome = "RT")
+p_rt_hct_accuracy <- plot_effect(model, results, var = "HCT_Accuracy", outcome = "RT")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p_conf_hct_confidence <- plot_effect(model, var = "HCT_Confidence", outcome = "Confidence")
+p_conf_hct_confidence <- plot_effect(model, results, var = "HCT_Confidence", outcome = "Confidence")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_hct_confidence <- plot_effect(model, var = "HCT_Confidence", outcome = "RT")
+p_rt_hct_confidence <- plot_effect(model, results, var = "HCT_Confidence", outcome = "RT")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p_conf_hct_awareness <- plot_effect(model, var = "HCT_Awareness", outcome = "Confidence")
+p_conf_hct_awareness <- plot_effect(model, results, var = "HCT_Awareness", outcome = "Confidence")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_hct_awareness <- plot_effect(model, var = "HCT_Awareness", outcome = "RT")
+p_rt_hct_awareness <- plot_effect(model, results, var = "HCT_Awareness", outcome = "RT")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p_conf_maia_total <- plot_effect(model, var = "MAIA_Total", outcome = "Confidence")
+p_conf_maia_total <- plot_effect(model, results, var = "MAIA_Total", outcome = "Confidence")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_maia_total <- plot_effect(model, var = "MAIA_Total", outcome = "RT")
+p_rt_maia_total <- plot_effect(model, results, var = "MAIA_Total", outcome = "RT")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p_conf_maia_noticing <- plot_effect(model, var = "MAIA_Noticing", outcome = "Confidence")
+p_conf_maia_noticing <- plot_effect(model, results, var = "MAIA_Noticing", outcome = "Confidence")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_maia_noticing <- plot_effect(model, var = "MAIA_Noticing", outcome = "RT")
+p_rt_maia_noticing <- plot_effect(model, results, var = "MAIA_Noticing", outcome = "RT")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p_conf_maia_notdistracting <- plot_effect(model, var = "MAIA_NotDistracting", outcome = "Confidence")
+p_conf_maia_notdistracting <- plot_effect(model, results, var = "MAIA_NotDistracting", outcome = "Confidence")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_maia_notdistracting <- plot_effect(model, var = "MAIA_NotDistracting", outcome = "RT")
+p_rt_maia_notdistracting <- plot_effect(model, results, var = "MAIA_NotDistracting", outcome = "RT")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p_conf_maia_bodylistening <- plot_effect(model, var = "MAIA_BodyListening", outcome = "Confidence")
+p_conf_maia_bodylistening <- plot_effect(model, results, var = "MAIA_BodyListening", outcome = "Confidence")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p_rt_maia_bodylistening <- plot_effect(model, var = "MAIA_BodyListening", outcome = "RT")
+p_rt_maia_bodylistening <- plot_effect(model, results, var = "MAIA_BodyListening", outcome = "RT")
 ```

### 2021-11-19 scripts/claudia/heartbeat_tracking.py
comment on ppts with empty conditions

@@ -65,7 +65,7 @@ for i, participant in enumerate(list_participants):
 #     print(f"{participant} : {n_events} events detected\n======================")
 #     # participants 010: 1 extra
 #     # participants 012, 023: 3 extra
-
+    
     # Directory of where heartbeat data is stored
     subdir = directory + "/../../data/data_experimental/" + participant + "/heartbeat/"
 
@@ -94,15 +94,24 @@ for i, participant in enumerate(list_participants):
     start_noguess_perturbed, stop_noguess_perturbed = events_all['onset'][14], events_all['onset'][15]
 
     # Get time to closest Rpeaks
-    if participant == '009':  # no taps for guess and no guess conditions
+    if participant == '009':
         df = get_time_to_rpeak(bio["ECGBIT"], start_noguess_perturbed, stop_noguess_perturbed,
                                sampling_rate, taps_noguess_perturbed, task="NoGuess_Perturbed")
-    elif participant == '027':  # no taps for noguess_perturbed condition
+    elif participant == '027':
         time_guess = get_time_to_rpeak(bio["ECGBIT"], start_guess, stop_guess, sampling_rate, taps_guess,
                                        task="Guess")
         time_noguess = get_time_to_rpeak(bio["ECGBIT"], start_noguess, stop_noguess, sampling_rate, taps_noguess,
                                          task="NoGuess")
         df = pd.concat([time_guess, time_noguess])
+    elif participant in ['010', '028']:
+        time_guess = get_time_to_rpeak(bio["ECGBIT"], start_guess, stop_guess, sampling_rate, taps_guess,
+                                       task="Guess")
+        time_noguess_perturbed = get_time_to_rpeak(bio["ECGBIT"], start_noguess_perturbed, stop_noguess_perturbed,
+                                                   sampling_rate, taps_noguess_perturbed, task="NoGuess_Perturbed")
+        df = pd.concat([time_guess, time_noguess_perturbed])
+    elif participant == '013':
+        df = get_time_to_rpeak(bio["ECGBIT"], start_guess, stop_guess, sampling_rate, taps_guess,
+                               task="Guess")
     else:
         time_guess = get_time_to_rpeak(bio["ECGBIT"], start_guess, stop_guess, sampling_rate, taps_guess,
                                        task="Guess")
@@ -111,6 +120,12 @@ for i, participant in enumerate(list_participants):
         time_noguess_perturbed = get_time_to_rpeak(bio["ECGBIT"], start_noguess_perturbed, stop_noguess_perturbed,
[…]

### 2021-11-19 scripts/claudia/deception_task.py
fix and rerun dece physio script

@@ -5,41 +5,45 @@ import numpy as np
 import pandas as pd
 
 # Set working directory
-directory = os.getcwd()
-list_participants = os.listdir(directory + "/data/data_experimental")
-list_participants.remove("022")  # only have 133 events
+list_participants = os.listdir("../../data/data_experimental")
 df = pd.DataFrame()
-for participant in list_participants[21:]:
+for participant in list_participants:
     print(participant)
     if participant == "022":
-        data = pd.DataFrame({"ID" : participant,
-                             "condition" : ["Social"] * 40 + ["Polygraph"] * 40,
-                             "trial" : np.arange(1, 81),
-                             "ECG_Rate_MeanRaw" : np.repeat(np.nan, 80),
-                             "ECG_Rate_Mean" : np.repeat(np.nan, 80)})
+        data = pd.DataFrame(
+            {
+                "ID": "22",
+                "trial": np.arange(1, 81),
+                "condition": ["Social"] * 40 + ["Polygraph"] * 40,
+                "ECG_Rate_MeanRaw": np.repeat(np.nan, 80),
+                "ECG_Rate_Mean": np.repeat(np.nan, 80),
+            }
+        )
     else:
-        subdir = directory + "/data/data_experimental/" + participant + "/deception/"
-    # Load data
-        filename = [i for i in os.listdir(subdir) if i.endswith('.txt')][0]
+        subdir = "../../data/data_experimental/" + participant + "/deception/"
+        # Load data
+        filename = [i for i in os.listdir(subdir) if i.endswith(".txt")][0]
         bio, sampling_rate = nk.read_bitalino(subdir + "/" + filename)
-    # Clean ecg signal
+        # Clean ecg signal
         signal, _ = nk.ecg_process(bio["ECGBIT"], sampling_rate=sampling_rate)
-    # Epoching
+        # Epoching
         events = nk.events_find(bio["LUX"], duration_min=3)
         index = np.arange(1, len(events["onset"]) + 1, 4)
-        epochs = nk.epochs_create(signal, events["onset"][index], epochs_end = 2, sampling_rate=sampling_rate)
+        epochs = nk.epochs_create(
+            signal, events["onset"][index], epochs_end=2, sampling_rate=sampling_rate
+        )
[…]

### 2021-11-22 1_Measures.Rmd
update

@@
 
+### Heartbeat Tracking Task (HTT)
+
+```{r message=FALSE}
+htt_data <- read.csv("scripts/claudia/HCT_Tracking.csv") |> 
+  mutate(Participant = paste0("S", as.character(ID)),
+         Condition = fct_recode(Condition, "NoGuessPerturbed" = "NoGuess_Perturbed")) |> 
+  rename(Distance = Time_to_Rpeak)
+
+htt_data |>
+  ggplot(aes(x = Distance, fill = Condition)) +
+  geom_histogram(binwidth = 0.05, alpha = 0.5, position="identity") +
+  geom_vline(xintercept = 0, linetype = "dashed") +
+  facet_wrap(~ID) +
+  see::theme_modern()
+
+# model <- rstanarm::stan_lmer(Distance ~ Condition + (1 + Condition | ID), data = hct_data, refresh=0, chains = 2)
+# model <- glmmTMB::glmmTMB(Distance ~ Condition + (1 | ID), data = hct_data)
+
+htt_scores <- htt_data |> 
+  group_by(Participant, Condition) |> 
+  summarise(HTT_Mean = mean(Distance),
+            HTT_n = n()) |> 
+  ungroup() |> 
+  complete(Participant, Condition, fill = list(HTT_Mean = NA, HTT_n = 0)) |> 
+  tidyr::pivot_wider(names_from = "Condition", values_from = c("HTT_Mean", "HTT_n"))
+
+df <- merge(df, htt_scores, by = "Participant")
+```
+
 ### MAIA
@@
 
+#### Physiological Processing
+
+```{r warning=FALSE}
+df_physio <- read.csv("data/data_physio_DeceptionTask.csv") |> 
+  tidyr::pivot_longer(starts_with("X"), names_to = "Time", values_to = "HeartRate") |> 
+  mutate(Time = as.numeric(str_remove(Time, "X"))-500,
+         group = paste0(ID, condition, instruction),
+         condition = fct_recode(condition, "Interrogation" = "Social"),
+         instruction = fct_relevel(instruction, "TRUTH")) |> 
+  group_by(condition, instruction, Time) |> 
+  summarise(HeartRate = mean(HeartRate)) |> 
+  ungroup()
+
+df_physio |> 
+  ggplot(aes(x = Time, y = HeartRate)) +
+  geom_rect(aes(xmin=1500, xmax=2500, ymin=-65, ymax=90), alpha=0.1, fill = "green") +
+  geom_line(aes(color = condition, linetype = instruction), size=1) +
+  geom_vline(aes(xintercept=0), linetype = "dotted") +
+  labs(y = "Average Heart Rate (bpm)", x = "Time (ms)") +
+  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
+  theme(legend.position = "top", legend.title=element_blank())
+```
+
 #### Summary Table
@@
 ```{r warning=FALSE}
-
 df |> 
@@
 df <- df |> 
+  # Remove participants
   dplyr::filter(Participant != "S9",  # Extreme answers
-                !Participant %in% c("S3", "S15", "S19", "S23"))  # No data
+                !Participant %in% c("S3", "S15", "S19", "S23")) |>  # No data
+  group_by(Participant) |> 
+  mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore_robust", threshold = qnorm(0.999))),
+         Outliers_Physio = as.logical(performance::check_outliers(ECG_Rate_Mean_2.5s, method = "zscore_robust", threshold = qnorm(0.999))))
+  ungroup()
+```
+
+```{r warning=FALSE}
+df |> 
+  group_by(Participant) |> 
+  summarise(Physio = sum(Outliers_RT) / n(),
+            RT = sum(Outliers_Physio) / n()) |> 
+  tidyr::pivot_longer(-Participant, names_to = "Outlier_Type") |> 
+  ggplot(aes(x=Participant, y = value, fill = Outlier_Type)) +
+  geom_bar(stat = "identity") + 
+  scale_y_continuous(labels = scales::percent) + 
+  labs(y = "Percentage of trials") +
+  ggtitle("Number of Trial Dropped Per Participant")
+
+df$RT[df$Outliers_RT] <- NA
+df$ECG_Rate_Mean_2.5s[df$Outliers_Physio] <- NA
 ```
@@
 
-```{r warning=FALSE}
+```{r warning=FALSE, fig.height=figheight*2}
 p1 <- df |> 
-  dplyr::filter(!Participant %in% c("S29")) |>
   ggplot(aes(x = Confidence, fill = Participant)) +
@@
   see::scale_fill_material_d(palette = "rainbow", guide = "none") +
-  see::theme_modern() +
   scale_x_continuous(labels = scales::percent, expand=expansion(c(0, .05))) +
@@
 p2 <- df |> 
-  dplyr::filter(!Participant %in% c("S29")) |> 
   ggplot(aes(x = RT, fill = Participant)) +
@@
   facet_wrap(~Answer)
-p1 / p2
+p3 <- df |> 
+  ggplot(aes(x = ECG_Rate_Mean_2_3s, fill = Participant)) +
+  geom_density(alpha = 0.1) +
+  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
+  scale_x_continuous(expand=expansion(c(0, .05))) +
+  scale_y_continuous(expand=expansion(c(0, .05))) +
+  facet_wrap(~Answer)
+p1 / p2 / p3
 ```

### 2021-11-22 2_ManipulationChecks.Rmd
update

@@
          starts_with("HCT_"),
+         starts_with("HTT_"),
          starts_with("MAIA_"),
@@
 ```{r message=FALSE, warning=FALSE}
+r <- correlation(select(dfsub, starts_with("HTT_")),
+                 select(dfsub, starts_with("HCT_")), 
+                 p_adjust = "none")
+
+summary(r) |> 
+  plot()
+```
+
+```{r message=FALSE, warning=FALSE}
 r <- correlation(select(dfsub, starts_with("MAIA_")),
-                 select(dfsub, starts_with("HCT_")), 
+                 select(dfsub, starts_with("HCT_"), starts_with("HTT_")), 
                  p_adjust = "none")
@@
 
+### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(ECG_Rate_MeanRaw ~ Answer * Phrasing + (1|Participant) + (1|Item), data = df)
+
+parameters::parameters(model)
+```
+
+```{r message=FALSE, warning=FALSE}
+estimate_means(model, at = c("Answer", "Phrasing")) |> 
+  plot(show_data = "none") 
+```
+
 ## Lies and RT
@@
 estimate_relation(model, at = c("RT", "Answer")) |> 
+  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
+```
+
+## Lies and Heart Rate
+
+- The faster they answer, the more confident they are in their lies.
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(ECG_Rate_Mean ~ Confidence * Answer + (1|Participant) + (1|Item), 
+                 data = df)
+
+parameters::parameters(model, effects = "fixed")
+```
+
+```{r message=FALSE, warning=FALSE}
+estimate_relation(model, at = c("Confidence", "Answer")) |> 
   plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
@@
 ```
+
+### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+# ECG_Rate_Mean_2.5s
+names(select(df, starts_with("ECG_")))
+model <- glmmTMB(ECG_Rate_Mean_1.5_2.5s ~ Answer * Condition + (1|Participant) + (1|Item), 
+                 data = dplyr::filter(df, abs(ECG_Rate_Mean_1.5_2.5s) < 10))
+
+parameters::parameters(model, effects = "fixed")
+
+modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
+modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
+```
+
+```{r message=FALSE, warning=FALSE}
+estimate_means(model, at = c("Condition", "Answer")) |> 
+  plot(show_data = "none") 
+```

### 2021-11-22 index.Rmd
update

@@
 
-df <- read.csv("data/data_combined.csv") %>% 
+df <- read.csv("data/data_combined_wPhysio.csv") %>% 
   mutate(ID = as.factor(paste0("S", ID)),

### 2021-11-22 preprocessing/physio_DeceptionTask.py

@@ -1,0 +1,81 @@
+import os
+
+import neurokit2 as nk
+import numpy as np
+import pandas as pd
+
+# Set working directory
+list_participants = os.listdir("../data/data_experimental")
+df = pd.DataFrame()
+df_signal = pd.DataFrame()
+for participant in list_participants:
+    print(participant)
+    if participant == "022":
+        data = pd.DataFrame(
+            {
+                "ID": "22",
+                "trial": np.arange(1, 81),
+                "condition": ["Social"] * 40 + ["Polygraph"] * 40,
+                "ECG_Rate_MeanRaw": np.repeat(np.nan, 80),
+                "ECG_Rate_Mean": np.repeat(np.nan, 80),
+            }
+        )
+    else:
+        subdir = "../data/data_experimental/" + participant + "/deception/"
+        # Load data
+        filename = [i for i in os.listdir(subdir) if i.endswith(".txt")][0]
+        bio, sampling_rate = nk.read_bitalino(subdir + "/" + filename)
+        # Clean ecg signal
+        signal, _ = nk.ecg_process(bio["ECGBIT"], sampling_rate=sampling_rate)
+        # Initialize data
+        data = pd.DataFrame(
+            {
+                "condition": ["Social"] * 40 + ["Polygraph"] * 40,
+                "trial": np.arange(1, 81),
+                "ID": [participant.lstrip("0")] * 80,
+            }
+        )
+        # Epoching
+        events = nk.events_find(bio["LUX"], duration_min=3)
+        index = np.arange(1, len(events["onset"]) + 1, 4)
+        for window in [3.5, 3, 2.5, 2]:
+            epochs = nk.epochs_create(
+                signal,
+                events["onset"][index],
+                epochs_start=-0.5,
+                epochs_end=window,
+                sampling_rate=sampling_rate,
+            )
+            if window == 3.5:  # Store rate signal for the longest epoch
+                rate_signal = pd.DataFrame([epochs[i]["ECG_Rate"].values for i in epochs.keys()])
+                data[f"ECG_Rate_MeanRaw_2_3s"] = rate_signal.loc[:, 2500:3500].mean(axis=1)
[…]

### 2021-11-22 scripts/claudia/deception_task.py

@@ -1,49 +1,0 @@
-import os
-
-import neurokit2 as nk
-import numpy as np
-import pandas as pd
-
-# Set working directory
-list_participants = os.listdir("../../data/data_experimental")
-df = pd.DataFrame()
-for participant in list_participants:
-    print(participant)
-    if participant == "022":
-        data = pd.DataFrame(
-            {
-                "ID": "22",
-                "trial": np.arange(1, 81),
-                "condition": ["Social"] * 40 + ["Polygraph"] * 40,
-                "ECG_Rate_MeanRaw": np.repeat(np.nan, 80),
-                "ECG_Rate_Mean": np.repeat(np.nan, 80),
-            }
-        )
-    else:
-        subdir = "../../data/data_experimental/" + participant + "/deception/"
-        # Load data
-        filename = [i for i in os.listdir(subdir) if i.endswith(".txt")][0]
-        bio, sampling_rate = nk.read_bitalino(subdir + "/" + filename)
-        # Clean ecg signal
-        signal, _ = nk.ecg_process(bio["ECGBIT"], sampling_rate=sampling_rate)
-        # Epoching
-        events = nk.events_find(bio["LUX"], duration_min=3)
-        index = np.arange(1, len(events["onset"]) + 1, 4)
-        epochs = nk.epochs_create(
-            signal, events["onset"][index], epochs_end=2, sampling_rate=sampling_rate
-        )
-        data = nk.ecg_analyze(epochs, sampling_rate=sampling_rate)
-        data["ECG_Rate_MeanRaw"] = data["ECG_Rate_Mean"] + data["ECG_Rate_Baseline"]
-        data["condition"] = ["Social"] * 40 + ["Polygraph"] * 40
-        data["trial"] = np.arange(1, len(data) + 1)
-        data["ID"] = participant.lstrip("0")
-        data = data[["ID", "trial", "condition", "ECG_Rate_MeanRaw", "ECG_Rate_Mean"]]
-    # Concat
-    df = pd.concat([df, data], axis=0)
-
-
-data_beh = pd.read_csv("../../data/data_combined.csv")
-data_beh["ID"] = data_beh["ID"].astype(str)
-data_all = pd.merge(df, data_beh)
-assert len(data_beh) == len(data_all)
-data_all.to_csv("../../data/data_combined_wPhysio.csv", index=False)

### 2021-11-23 1_Measures.Rmd
update

@@
 df_physio <- read.csv("data/data_physio_DeceptionTask.csv") |> 
+  dplyr::filter(ID != 30) |> 
   tidyr::pivot_longer(starts_with("X"), names_to = "Time", values_to = "HeartRate") |> 
@@
   ggplot(aes(x = Time, y = HeartRate)) +
-  geom_rect(aes(xmin=1500, xmax=2500, ymin=-65, ymax=90), alpha=0.1, fill = "green") +
+  annotate("rect", xmin=1500, xmax=2500, ymin=-Inf, ymax=Inf, alpha=0.1, fill = "green") +
   geom_line(aes(color = condition, linetype = instruction), size=1) +
@@
 
+##### Participants
+
+```{r warning=FALSE}
+df |> 
+  select(Participant, Confidence, RT, HeartRate) |> 
+  tidyr::pivot_longer(-Participant) |> 
+  ggplot(aes(x=Participant, y=value)) +
+  geom_violin(aes(fill=name), color="white", alpha=0.5) +
+  geom_jitter(aes(color=name), width = 0.25, height=0, shape="+", size=2) +
+  facet_wrap(~name, scales="free", nrow=3) +
+  guides(fill="none", color="none")
+
+df$Confidence[df$Participant %in% c("S9", "S29")] <- NA # Extreme responses
+sum(is.na(df$Confidence)) / nrow(df) * 100
+df$HeartRate[df$Participant == "S30"] <- NA # Extreme values
+sum(is.na(df$HeartRate)) / nrow(df) * 100
+df$RT[df$Participant == "S13"] <- NA # Slower than the others
+df$RT[df$RT > 8.25] <- NA # Extreme RT values 
+sum(is.na(df$RT)) / nrow(df) * 100
+```
+
+##### Observations
+
 ```{r warning=FALSE}
@@
   # Remove participants
-  dplyr::filter(Participant != "S9",  # Extreme answers
-                !Participant %in% c("S3", "S15", "S19", "S23")) |>  # No data
   group_by(Participant) |> 
-  mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore_robust", threshold = qnorm(0.999))),
-         Outliers_Physio = as.logical(performance::check_outliers(ECG_Rate_Mean_2.5s, method = "zscore_robust", threshold = qnorm(0.999))))
+  mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore", threshold = qnorm(0.9999))),
+         Outliers_Physio = as.logical(performance::check_outliers(HeartRate, method = "zscore", threshold = qnorm(0.9999)))) |> 
   ungroup()
@@
 df$RT[df$Outliers_RT] <- NA
-df$ECG_Rate_Mean_2.5s[df$Outliers_Physio] <- NA
+df$HeartRate[df$Outliers_Physio] <- NA
 ```
@@
 p3 <- df |> 
-  ggplot(aes(x = ECG_Rate_Mean_2_3s, fill = Participant)) +
+  ggplot(aes(x = HeartRate, fill = Participant)) +
   geom_density(alpha = 0.1) +

### 2021-11-23 2_ManipulationChecks.Rmd
update

@@
 
-## Correlation {.tabset}
+## Inter-Measures Correlation {.tabset}
 
@@
 
-## Phrasing {.tabset}
+### Deception Task and LIE Scale
+
+```{r message=FALSE, warning=FALSE}
+r <- df |> 
+  select(Participant, Answer, Confidence, RT, HeartRate) |> 
+  group_by(Participant, Answer) |> 
+  summarise_all(mean, na.rm=TRUE) |> 
+  tidyr::pivot_wider(names_from = "Answer", values_from = c("Confidence", "RT", "HeartRate")) |> 
+  ungroup() |> 
+  select(-Participant) |> 
+  correlation(select(dfsub, starts_with("LIE_")), p_adjust = "none")
+
+summary(r) |> 
+  plot()
+```
+
+### Confidence and RT
+
+- When lying, the faster they answer, the more confident they are.
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ RT * Answer + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
+
+parameters::parameters(model, effects = "fixed")
+```
+
+```{r message=FALSE, warning=FALSE}
+modelbased::estimate_slopes(model, trend = "RT", at = "Answer")
+```
+
+```{r message=FALSE, warning=FALSE}
+estimate_relation(model, at = c("RT", "Answer")) |> 
+  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
+```
+
+### Confidence and Heart Rate
+
+- More confidence in truths is associated with higher heart rate.
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ HeartRate * Answer + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family()) # warning can be ignored
+
+parameters::parameters(model, effects = "fixed")
+```
+
+```{r message=FALSE, warning=FALSE}
+modelbased::estimate_slopes(model, trend = "HeartRate", at = "Answer")
+```
+
+```{r message=FALSE, warning=FALSE}
+estimate_relation(model, at = c("HeartRate", "Answer")) |> 
+  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
+```
+
+### RT and Heart Rate
+
+- No relationship.
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(RT ~ HeartRate * Answer + (1|Participant) + (1|Item), 
+                 data = df)
+
+parameters::parameters(model, effects = "fixed")
+```
+
+```{r message=FALSE, warning=FALSE}
+estimate_relation(model, at = c("HeartRate", "Answer")) |> 
+  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
+```
+
+## Effect of Phrasing {.tabset}
 
@@
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer * Phrasing + (1|Participant) + (1|Item), data = df)
+model <- glmmTMB(RT ~ Answer * Phrasing + (1|Participant), data = df)
 
@@
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer * Phrasing + (1|Participant) + (1|Item), data = df)
+model <- glmmTMB(Confidence ~ Answer * Phrasing + (1|Participant), data = df)
 
@@
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(ECG_Rate_MeanRaw ~ Answer * Phrasing + (1|Participant) + (1|Item), data = df)
+model <- glmmTMB(HeartRate ~ Answer * Phrasing + (1|Participant), data = df)
 
@@
 
-## Lies and RT
+## Effect of Condition
 
-- The faster they answer, the more confident they are in their lies.
+### Confidence
+
+- Significant interaction between the condition and the answer: the effect of answer (being more confident in truths than in lies) is lower in the social condition.
+- Effect mostly driven by lower lie confidence in the polygraph condition: less obvious feedback cues?
 
 ```{r message=FALSE, warning=FALSE}
-# Adjustments for beta models
-df$Confidence[df$Confidence == 1] <- 0.99999
-df$Confidence[df$Confidence == 0] <- 0.00001
-
-model <- glmmTMB(Confidence ~ RT * Answer + Phrasing + (1|Participant) + (1|Item), 
+model <- glmmTMB(Confidence ~ Answer * Condition + (1|Participant) + (1|Item), 
                  data = df, family = beta_family())
@@
 ```{r message=FALSE, warning=FALSE}
-estimate_relation(model, at = c("RT", "Answer")) |> 
-  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
-```
-
-## Lies and Heart Rate
-
-- The faster they answer, the more confident they are in their lies.
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(ECG_Rate_Mean ~ Confidence * Answer + (1|Participant) + (1|Item), 
-                 data = df)
-
-parameters::parameters(model, effects = "fixed")
-```
-
-```{r message=FALSE, warning=FALSE}
-estimate_relation(model, at = c("Confidence", "Answer")) |> 
-  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
-```
-
-## Effect of Condition
-
-### Confidence
-
-- Significant interaction between the condition and the answer: the effect of answer (being more confident in truths than in lies) is lower in the social condition.
-- Effect mostly driven by the social condition that increases the confidence in lies. 
-- In other words: harder to lie in the polygraph condition: less obvious feedback cues?
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer * Condition + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-parameters::parameters(model, effects = "fixed")
+modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
+modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
 ```
@@
 
+- Higher heart rate in lies vs. truths, and higher heart rate in social condition vs. polygraph.
+- No interaction.
+
 ```{r message=FALSE, warning=FALSE}
-# ECG_Rate_Mean_2.5s
-names(select(df, starts_with("ECG_")))
-model <- glmmTMB(ECG_Rate_Mean_1.5_2.5s ~ Answer * Condition + (1|Participant) + (1|Item), 
-                 data = dplyr::filter(df, abs(ECG_Rate_Mean_1.5_2.5s) < 10))
+model <- glmmTMB(HeartRate ~ Answer * Condition + (1|Participant) + (1|Item), 
+                 data = df)
 
 parameters::parameters(model, effects = "fixed")
+```
 
+```{r message=FALSE, warning=FALSE}
 modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")

### 2021-11-23 3_ToM.Rmd
update

@@
               size = 8, show.legend = FALSE) +
-    labs(y = ifelse(outcome == "RT", "Reaction Time (s)", "Confidence"), 
+    labs(y = ifelse(outcome == "RT", "Reaction Time (s)", ifelse(outcome == "HeartRate", "Heart Rate (bpm)", "Confidence")), 
          x = paste0(stringr::str_replace(var, "_", " ("), ")")) +
@@
 # p_rt_yoni_total
+```
+
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Total) + (1|Participant), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "HeartRate")
+# p_hr_yoni_total
 ```
@@
 
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Cognitive) + (1|Participant), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_yoni_cognitive <- plot_effect(model, results, var = "YONI_Cognitive", outcome = "HeartRate")
+# p_hr_yoni_cognitive
+```
+
 ### Affective Theory of Mind
@@
 # p_rt_yoni_affective
+```
+
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Affective) + (1|Participant), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_yoni_affective <- plot_effect(model, results, var = "YONI_Affective", outcome = "HeartRate")
+# p_hr_yoni_affective
 ```
@@
 
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Physical) + (1|Participant), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_yoni_physical <- plot_effect(model, results, var = "YONI_Physical", outcome = "HeartRate")
+# p_hr_yoni_physical
+```
+
 ### Correlation with LIE Scale
@@
   p_rt_yoni_physical +
+  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))
+
+p_hr_yoni_total / 
+  p_hr_yoni_cognitive / 
+  p_hr_yoni_affective / 
+  p_hr_yoni_physical +
   patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))
@@
 
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * BES_Total) + (1|Participant), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_bes_total <- plot_effect(model, results, var = "BES_Total", outcome = "HeartRate")
+# p_hr_bes_total
+```
+
 ### Cognitive Empathy
@@
 # p_rt_bes_cognitive
+```
+
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * BES_Cognitive) + (1|Participant), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_bes_cognitive <- plot_effect(model, results, var = "BES_Cognitive", outcome = "HeartRate")
+# p_hr_bes_cognitive
 ```
@@
 
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * BES_Affective) + (1|Participant), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_bes_affective <- plot_effect(model, results, var = "BES_Affective", outcome = "HeartRate")
+# p_hr_bes_affective
+```
+
 ### Correlation with LIE Scale
@@
   patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))
+
+p_hr_bes_total / 
+  p_hr_bes_cognitive / 
+  p_hr_bes_affective +
+  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))
 ```

### 2021-11-23 4_Intero.Rmd
update

@@
 
-### Accuracy
+### Interoceptive Accuracy
 
@@
 p_rt_hct_accuracy <- plot_effect(model, results, var = "HCT_Accuracy", outcome = "RT")
+```
+
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * HCT_Accuracy) + (1|Participant), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_hct_accuracy <- plot_effect(model, results, var = "HCT_Accuracy", outcome = "HeartRate")
 ```
@@
 
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * HCT_Confidence) + (1|Participant), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_hct_confidence <- plot_effect(model, results, var = "HCT_Confidence", outcome = "HeartRate")
+```
+
 ### Interoceptive Awareness
@@
 
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * HCT_Awareness) + (1|Participant), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_hct_awareness <- plot_effect(model, results, var = "HCT_Awareness", outcome = "HeartRate")
+```
+
 ### Correlation with LIE Scale
@@
   p_conf_hct_awareness +
-  patchwork::plot_annotation(title = "Interoception", theme = theme(plot.title = element_text(hjust = 0.5)))
+  patchwork::plot_annotation(title = "Heartbeat Counting Task", theme = theme(plot.title = element_text(hjust = 0.5)))
 
@@
   p_rt_hct_awareness +
-  patchwork::plot_annotation(title = "Interoception", theme = theme(plot.title = element_text(hjust = 0.5)))
+  patchwork::plot_annotation(title = "Heartbeat Counting Task", theme = theme(plot.title = element_text(hjust = 0.5)))
+
+p_hr_hct_accuracy / 
+  p_hr_hct_confidence / 
+  p_hr_hct_awareness +
+  patchwork::plot_annotation(title = "Heartbeat Counting Task", theme = theme(plot.title = element_text(hjust = 0.5)))
 ```
+
+## Heartbeat Tracking {.tabset}
 
@@
 
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_Total) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_maia_total <- plot_effect(model, results, var = "MAIA_Total", outcome = "HeartRate")
+```
+
 ### Noticing
@@
 p_rt_maia_noticing <- plot_effect(model, results, var = "MAIA_Noticing", outcome = "RT")
+```
+
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_Noticing) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_maia_noticing <- plot_effect(model, results, var = "MAIA_Noticing", outcome = "HeartRate")
 ```
@@
 
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_NotDistracting) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_maia_notdistracting <- plot_effect(model, results, var = "MAIA_NotDistracting", outcome = "HeartRate")
+```
+
 ### Body Listening
@@
 
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_BodyListening) + (1|Participant), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_maia_bodylistening <- plot_effect(model, results, var = "MAIA_BodyListening", outcome = "HeartRate")
+```
+
+### Trusting
+
+#### Confidence
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_Trusting) + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_conf_maia_trusting <- plot_effect(model, results, var = "MAIA_Trusting", outcome = "Confidence")
+```
+
+#### RT
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(RT ~ Answer / (Condition * MAIA_Trusting) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_rt_maia_trusting <- plot_effect(model, results, var = "MAIA_Trusting", outcome = "RT")
+```
+
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_Trusting) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_maia_trusting <- plot_effect(model, results, var = "MAIA_Trusting", outcome = "HeartRate")
+```
+
+### Not Worrying
+
+#### Confidence
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_NotWorrying) + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_conf_maia_notworrying <- plot_effect(model, results, var = "MAIA_NotWorrying", outcome = "Confidence")
+```
+
+#### RT
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(RT ~ Answer / (Condition * MAIA_NotWorrying) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_rt_maia_notworrying <- plot_effect(model, results, var = "MAIA_NotWorrying", outcome = "RT")
+```
+
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_NotWorrying) + (1|Participant), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_maia_notworrying <- plot_effect(model, results, var = "MAIA_NotWorrying", outcome = "HeartRate")
+```
+
+### Emotional Awareness
+
+#### Confidence
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_EmotionalAwareness) + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_conf_maia_emotionalawareness <- plot_effect(model, results, var = "MAIA_EmotionalAwareness", outcome = "Confidence")
+```
+
+#### RT
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(RT ~ Answer / (Condition * MAIA_EmotionalAwareness) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_rt_maia_emotionalawareness <- plot_effect(model, results, var = "MAIA_EmotionalAwareness", outcome = "RT")
+```
+
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_EmotionalAwareness) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_maia_emotionalawareness <- plot_effect(model, results, var = "MAIA_EmotionalAwareness", outcome = "HeartRate")
+```
+
+### Attention Regulation
+
+#### Confidence
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_AttentionRegulation) + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_conf_maia_attentionregulation <- plot_effect(model, results, var = "MAIA_AttentionRegulation", outcome = "Confidence")
+```
+
+#### RT
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(RT ~ Answer / (Condition * MAIA_AttentionRegulation) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_rt_maia_attentionregulation <- plot_effect(model, results, var = "MAIA_AttentionRegulation", outcome = "RT")
+```
+
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_AttentionRegulation) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_maia_attentionregulation <- plot_effect(model, results, var = "MAIA_AttentionRegulation", outcome = "HeartRate")
+```
+
+### Self Regulation
+
+#### Confidence
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_SelfRegulation) + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_conf_maia_selfregulation <- plot_effect(model, results, var = "MAIA_SelfRegulation", outcome = "Confidence")
+```
+
+#### RT
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(RT ~ Answer / (Condition * MAIA_SelfRegulation) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_rt_maia_selfregulation <- plot_effect(model, results, var = "MAIA_SelfRegulation", outcome = "RT")
+```
+
+#### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_SelfRegulation) + (1|Participant) + (1|Item), 
+                 data = df)
+
+results <- get_parameters(model)
+results$params
+results$marginal_effects
+```
+
+```{r message=FALSE, warning=FALSE}
+p_hr_maia_selfregulation <- plot_effect(model, results, var = "MAIA_SelfRegulation", outcome = "HeartRate")
+```
+
 ### Correlation with LIE Scale
@@
 
-```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
+```{r message=FALSE, warning=FALSE, fig.height=figheight*4, fig.width=figwidth*1.5}
 p_conf_maia_total / 
@@
   p_conf_maia_notdistracting / 
-  p_conf_maia_bodylistening +
+  p_conf_maia_bodylistening /
+  p_conf_maia_trusting / 
+  p_conf_maia_notworrying / 
+  p_conf_maia_emotionalawareness / 
+  p_conf_maia_attentionregulation / 
+  p_conf_maia_selfregulation +
   patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))
@@
   p_rt_maia_notdistracting / 
-  p_rt_maia_bodylistening +
+  p_rt_maia_bodylistening /
+  p_rt_maia_trusting / 
+  p_rt_maia_notworrying / 
+  p_rt_maia_emotionalawareness / 
+  p_rt_maia_attentionregulation / 
+  p_rt_maia_selfregulation +
+  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))
+
+p_hr_maia_total / 
+  p_hr_maia_noticing / 
+  p_hr_maia_notdistracting / 
+  p_hr_maia_bodylistening /
+  p_hr_maia_trusting / 
+  p_hr_maia_notworrying / 
+  p_hr_maia_emotionalawareness / 
+  p_hr_maia_attentionregulation / 
+  p_hr_maia_selfregulation +
   patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))

### 2021-11-23 index.Rmd
update

--- 2021-11-11 index.Rmd
@@
          "Confidence" = "DT_confidence",
-         "RT" = "DT_RT") |> 
+         "RT" = "DT_RT",
+         "HeartRate" = "ECG_Rate_MeanRaw_1.5_2.5s") |> 
   mutate(Answer = fct_recode(Answer, Lie = "LIE", Truth = "TRUTH")) |> 
-  select(-HCT_guess, -HCT_noguess, -HCT_onebreath)
+  select(-HCT_guess, -HCT_noguess, -HCT_onebreath) |> 
+  dplyr::filter(!Participant %in% c("S3", "S15", "S19", "S23"))  # No data
+
+# Adjustments for beta models
+df$Confidence[df$Confidence == 1] <- 0.99999
+df$Confidence[df$Confidence == 0] <- 0.00001
 

### 2021-11-23 preprocessing/physio_DeceptionTask.py

@@ -38,29 +38,43 @@ for participant in list_participants:
         # Epoching
         events = nk.events_find(bio["LUX"], duration_min=3)
         index = np.arange(1, len(events["onset"]) + 1, 4)
-        for window in [3.5, 3, 2.5, 2]:
-            epochs = nk.epochs_create(
-                signal,
-                events["onset"][index],
-                epochs_start=-0.5,
-                epochs_end=window,
-                sampling_rate=sampling_rate,
-            )
-            if window == 3.5:  # Store rate signal for the longest epoch
-                rate_signal = pd.DataFrame([epochs[i]["ECG_Rate"].values for i in epochs.keys()])
-                data[f"ECG_Rate_MeanRaw_2_3s"] = rate_signal.loc[:, 2500:3500].mean(axis=1)
-                data[f"ECG_Rate_Mean_2_3s"] = data[f"ECG_Rate_MeanRaw_2_3s"] - rate_signal[500]
-                data[f"ECG_Rate_MeanRaw_1.5_2.5s"] = rate_signal.loc[:, 2000:3000].mean(axis=1)
-                data[f"ECG_Rate_Mean_1.5_2.5s"] = (
-                    data[f"ECG_Rate_MeanRaw_1.5_2.5s"] - rate_signal[500]
-                )
-                data[f"ECG_Rate_MeanRaw_1.5_3s"] = rate_signal.loc[:, 2000:3500].mean(axis=1)
-                data[f"ECG_Rate_Mean_1.5_3s"] = data[f"ECG_Rate_MeanRaw_1.5_3s"] - rate_signal[500]
-                rate_signal = pd.concat([data, rate_signal], axis=1)
-                df_signal = pd.concat([df_signal, rate_signal], axis=0)
-            temp = nk.ecg_analyze(epochs, sampling_rate=sampling_rate).reset_index(drop=True)
-            data[f"ECG_Rate_MeanRaw_{window}s"] = temp["ECG_Rate_Mean"] + temp["ECG_Rate_Baseline"]
-            data[f"ECG_Rate_Mean_{window}s"] = temp["ECG_Rate_Mean"]
+        epochs = nk.epochs_create(
+            signal,
+            events["onset"][index],
+            epochs_start=-0.5,
+            epochs_end=3.5,
+            sampling_rate=sampling_rate,
[…]

### 2021-11-23 paper/manuscript_v0.Rmd
initiate paper template

---
title: '**Fractal and Entropic Characteristics of EEG during Resting State**'
shorttitle        : "Resting-state EEG Complexity"
author:
  - name          : "Dominique Makowski"
    affiliation   : " 1, *"
    address       : "HSS 04-18, 48 Nanyang Avenue, Singapore"
    email         : "dmakowski@ntu.edu.sg"
  - name          : "Zen J. Lau"
    affiliation   : " 1"
  - name          : "Tam Pham"
    affiliation   : " 1"
  - name          : "S.H. Annabel Chen"
    affiliation   : " 1, 2, 3, 4"
    corresponding : yes    # Define only one corresponding author
    address       : "HSS 04-19, 48 Nanyang Avenue, Singapore"
    email         : "annabelchen@ntu.edu.sg"
affiliation:
  - id            : "1"
    institution   : "School of Social Sciences, Nanyang Technological University, Singapore"
  - id            : "2"
    institution   : "Centre for Research and Development in Learning, Nanyang Technological University, Singapore"
  - id            : "3"
    institution   : "Lee Kong Chian School of Medicine, Nanyang Technological University, Singapore"
  - id            : "4"
    institution   : "National Institute of Education, Nanyang Technological University, Singapore"
abstract: |
output:
  papaja::apa6_word:
    keep_tex: yes
  pdf_document: default
  papaja::apa6_pdf:
    keep_tex: yes
keywords: "EEG, Complexity, Entropy, Fractal Dimension, Resting State"
wordcount: ''
bibliography: ["references.bib"]
floatsintext: yes
figsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
header-includes:
- \usepackage[labelfont=bf, font={color=gray,small}]{caption}
- \usepackage{float}
- \usepackage[document]{ragged2e}
csl: utils/apa.csl
---

\justify

```{r r_setup, include = FALSE, warning=FALSE, message=FALSE}
library("papaja")
library("kableExtra")
options(knitr.kable.NA = 'None')
```

```{=html}
<!-- 
Journals:
Neuroscience Letters https://www.journals.elsevier.com/neuroscience-letters
Biological Psychology https://www.journals.elsevier.com/biological-psychology
Psychophysiology https://onlinelibrary.wiley.com/journal/14698986
Cognitive Neurodynamics https://www.springer.com/journal/11571
Neuroscience & Biobehavioral Reviews https://www.journals.elsevier.com/neuroscience-and-biobehavioral-reviews
-->
```
<!-- Resting state -->

<!-- # Defining Complexity -->

Complexity science is an umbrella term encompassing the study and characterization of "complex" systems - systems consisting of multiple interdependent components that operate and interact at different levels [@fernandez2013complexity]. Such complex systems typically exhibit "chaotic" behaviour. Rather than referring to a state of disorder or confusion, a chaotic system is characterized by unpredictability and irregularities, often the result of a multitude of nonlinear interactions [@faure2001there]. As such, small changes in the system can lead to exponential changes (a property popularized as the 'butterfly effect'). For instance, the Earth's atmosphere at any point in time and space is the result of a (virtually infinite) number of variables (e.g., temperature, particle composition, cloud density, etc.) interacting together, rendering any long-term projections challenging. Nevertheless, the overarching idea of complexity science is not necessarily to establish methods for making exact predictions, but rather to provide some insights into the characterization of the long-term trajectory of a given complex system [@faure2001there]. These principles have its roots in a branch of mathematics called *chaos theory* [see @thietart1995chaos, for an overview], which has led several disciplines (e.g., environmental science, meteorology, biology) to adopt the framework of complex dynamical systems [@burggren2005assessing; @kiel1996chaos].

The application of complexity science to nonlinear systems, referred to as "nonlinear dynamics", is an emerging approach gaining traction in the study of human physiology and pathology [@ehlers1995chaos]. The theoretical conceptualization of the human physiological system as complex is warranted given that it is made up of multiple constituent subsystems (be it anatomical components or physiological processes) that are constantly interacting between themselves at different levels (i.e., from molecules to organs), as well as with the external environment to maintain homeostasis [@faure2001there]. The underlying assumptions are that physiological systems are inherently complex [@golbeter1996biochemical], and that pathological states [or 'dynamical diseases', see @mackey1977oscillation] can be characterized by disrupted or abnormal dynamic processes. One of the seminal works that contributed to this perspective was @lipsitz1992loss, who demonstrated that aging and disease are associated with a generalized loss of physiological complexity due to functional and/or structural alteration in the underlying organization of the physiological system [see @vaillancourt2002changing for a schematic illustration of this idea].

<!-- talk about eeg resting state analysis using complexity vs other traditional methods-->

<!-- resting state + personality -->

-   Resting state brain activity as a novel way to identify neurobiological correlates of personality traits
-   Modulatory effects of trait feature affects brain activity permanently (vs experimentally dependent for modulatory effects of a state condition)

# Methods

## Participants

Data from 80 participants was collected from two separate samples. Specifically, 45 participants from Singapore and 35 participants from France were recruited via posters, flyers, and online social media platforms. For the Singapore sample, participants were reimbursed 60 Singapore Dollars upon study completion, which included acquisition of resting-state EEG data and other tasks as part of a larger study. [**Describe French sample**]. One participant from the Singapore sample was excluded due to technical problems in the study setup and [**any exclusions from french sample here**]. The final sample included [...] participants ($N_{Singapore}$ = 44, $N_{France}$ = ...; Mean age = ..., SD = ..., range = [..., ...]; ...% females) The study was approved by the Institutional Review Board (Reference Number: IRB-2018-10-029) of Nanyang Technological University (NTU) in Singapore and by the [**Review board of French sample**]. Inclusion criteria included absence of current or history of neurological, psychiatric, or cardiovascular disorders.

## Procedure

### Singapore sample

Prior to EEG data acquisition, participants first provided their written informed consent and completed an online questionnaire on demographic information and personality measures. 128-channel EEG was then measured (sampling rate: 4000Hz) from participants for 8 minutes during eyes-closed rest. Participants were instructed to relax and stay still, to refrain from thinking about anything in particular, and to stay awake for the entire duration of the recording. All assessments were conducted at the same experimental location, in an air-conditioned (22 degrees celsius), dark, sound-attenuated room. EEG signals were recorded using Deymed's Truscan EEG system in accordance with the international 10-05 system, with most impedances around 15-20k$\Omega$ and all impedences kept below 50k$\Omega$. For maximal precision, a photosensor attached to the screen marked event timings (i.e., the start and end) of the resting session. After the resting condition, participants answered some questions pertaining to sensations and thoughts that they experienced during the resting state.

<!-- describe French set up??-->

## Measures

### Personality

Personality traits were assessed using the 24-item Mini-IPIP6 based on the HEXACO Personality Model [@ashtonlee2009hexaco; @Sibley_2011]. Sub-scores were computed for the 6 dimensions of personality, namely *Extraversion* (engagement in social behaviors), *Openness* (being open-minded such as displaying imagination and curiosity), *Agreeableness* (being cooperative and tolerant of others), *Conscientiousness* (being diligent, meticulous and organized), *Neuroticism* (the tendency to experience a persisting negative emotionality), and *Honesty-Humility* (being honest, sincere, and fair during social exchanges).

### Resting-State Cognition

Resting-state cognition was assessed using a brief questionnaire consisting of 6 items on a visual analogue scale, where participants were told to rate the percentage of time spent in 6 different states, namely, *Drowsiness* (feelings of drowsiness), *Absorption External* (the extent to which thoughts were directed towards external stimuli i.e., sounds, voices etc.), *Absorption Internal* (the extent to which thoughts were directed internally i.e., imagination, recalling of past events etc.), *Absorption Body* (the extent to which thoughts were directed bodily sensations and changes), *Mind Wandering* (free flowing of thoughts), and *Mind Focus* (the extent to which a particular thought or sensation was the prime focus). The protocol, including the task instructions, execution of the resting session, as well as the post-rest questionnaire, is open-access and available at [\*https://github.com/neuropsychology/RestingState\*\*](https://github.com/neuropsychology/RestingState).

## EEG Complexity Measures

## Data Analysis

For each participant, complexity indices were computed at each electrode for the following frequency bands: gamma (30 - 80 Hz), beta (13 - 30 Hz), alpha (8 - 13 Hz), theta (4 - 8 Hz), and delta (1 - 4 Hz). [**Were these values z-scored?**].

A factor analysis using a varimax rotation was conducted to identify the groupings of electrodes. [**Describe more**]. The final groupings resulted in 5 distinct factors, namely *frontal*, *left*, *right*, *central*, and *posterior*, corresponding to the regions of the brain.

# Results

# Discussion

-   Limitations: lack of validated ASRQ measure

# Funding

The authors did not receive support from any organization for the submitted work.

# Author Contributions

<!-- D.M. conceived the study. Z.J.L. and T.P. coordinated the study and drafted the manuscript. D.M. and S.H.A.C. performed a critical review of the manuscript. All authors have read and agreed to the published version of the manuscript. -->

# Conflict of Interest Statement

The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.

# Acknowledgements

\newpage

# References

```{r create_r-references}
r_refs(file = "references.bib")
```

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs}
:::

\endgroup

### 2021-11-24 3_ToM.Rmd
add stars

@@
                     annot$x + 0.05 * range_x)
-  annot$y <- max(data[[outcome]]) - 0.01 * diff(range(data[[outcome]]))
+  annot$y <- max(data[[outcome]], na.rm=TRUE) - 0.01 * diff(range(data[[outcome]], na.rm=TRUE))
 
@@
 p_conf_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "Confidence")
-# p_conf_yoni_total
 ```

### 2021-11-24 4_Intero.Rmd
add stars

@@
   p_conf_maia_bodylistening /
-  p_conf_maia_trusting / 
+  p_conf_maia_trusting +
+  patchwork::plot_annotation(title = "Interoception (MAIA) 1/2", theme = theme(plot.title = element_text(hjust = 0.5)))
+
 p_conf_maia_notworrying / 
@@
   p_conf_maia_selfregulation +
-  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))
+  patchwork::plot_annotation(title = "Interoception (MAIA) 2/2", theme = theme(plot.title = element_text(hjust = 0.5)))
 
@@
   p_rt_maia_bodylistening /
-  p_rt_maia_trusting / 
-  p_rt_maia_notworrying / 
+  p_rt_maia_trusting +
+  patchwork::plot_annotation(title = "Interoception (MAIA) 1/2", theme = theme(plot.title = element_text(hjust = 0.5)))
+
+  p_rt_maia_notworrying + 
   p_rt_maia_emotionalawareness / 
@@
   p_rt_maia_selfregulation +
-  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))
+  patchwork::plot_annotation(title = "Interoception (MAIA) 2/2", theme = theme(plot.title = element_text(hjust = 0.5)))
 
@@
   p_hr_maia_bodylistening /
-  p_hr_maia_trusting / 
-  p_hr_maia_notworrying / 
+  p_hr_maia_trusting +
+  patchwork::plot_annotation(title = "Interoception (MAIA) 1/2", theme = theme(plot.title = element_text(hjust = 0.5)))
+
+p_hr_maia_notworrying + 
   p_hr_maia_emotionalawareness / 
@@
   p_hr_maia_selfregulation +
-  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))
+  patchwork::plot_annotation(title = "Interoception (MAIA) 2/2", theme = theme(plot.title = element_text(hjust = 0.5)))
 ```

### 2021-11-24 4_Intero.Rmd
fix images

@@
 
-  p_rt_maia_notworrying + 
+  p_rt_maia_notworrying / 
   p_rt_maia_emotionalawareness / 
@@
 
-p_hr_maia_notworrying + 
+p_hr_maia_notworrying / 
   p_hr_maia_emotionalawareness / 

### 2021-12-07 index.Rmd
tidy up
move files to preprocessing, rename scripts folder, rename variables in data processing

--- 2021-11-11 index.Rmd
@@
 
-df <- read.csv("data/data_combined.csv") %>% 
+df <- read.csv("data/data_combined_wPhysio.csv") %>% 
   mutate(ID = as.factor(paste0("S", ID)),
-         condition = as.factor(condition),
-         item = as.factor(item),
-         style = as.factor(style),
-         instruction = as.factor(instruction)) |> 
-  #TODO: This renaming should be done at the preprocessing stage
-  rename("Participant" = "ID",
-         "Condition" = "condition",
-         "Item" = "item",
-         "Phrasing" = "style",
-         "Answer" = "instruction",
-         "YONI_Total" = "yoni_total",
-         "YONI_Affective" = "yoni_affective",
-         "YONI_Cognitive" = "yoni_cognitive",
-         "YONI_Physical" = "yoni_physical",
-         "BES_Total" = "BES_total",
-         "BES_Cognitive" = "BES_cognitive",
-         "BES_Affective" = "BES_affective",
-         "HCT_Confidence" = "HCT_confidence",
-         "HCT_Accuracy" = "HCT_accuracy",
-         "HCT_Awareness" = "HCT_awareness",
-         "MAIA_Total" = "MAIA_total",
-         "MAIA_AttentionRegulation" = "MAIA_attention_regulation",
-         "MAIA_BodyListening" = "MAIA_body_listening",
-         "MAIA_EmotionalAwareness" = "MAIA_emotional_awareness",
-         "MAIA_NotDistracting" = "MAIA_not_distracting",
-         "MAIA_NotWorrying" = "MAIA_not_worrying",
-         "MAIA_Noticing" = "MAIA_noticing",
-         "MAIA_SelfRegulation" = "MAIA_self_regulation",
-         "MAIA_Trusting" = "MAIA_trusting",
-         "LIE_Ability" = "lie_ability",
-         "LIE_Frequency" = "lie_frequency",
-         "LIE_Negativity" = "lie_negativity",
-         "LIE_Contextuality" = "lie_contextuality",
-         "Confidence" = "DT_confidence",
-         "RT" = "DT_RT") |> 
-  mutate(Answer = fct_recode(Answer, Lie = "LIE", Truth = "TRUTH")) |> 
-  select(-HCT_guess, -HCT_noguess, -HCT_onebreath)
+         Condition = as.factor(Condition),
+         Item = as.factor(Item),
+         Phrasing = as.factor(Phrasing),
+         Answer = as.factor(Answer)) |> 
+  rename("HeartRate" = "ECG_Rate_MeanRaw_1.5_2.5s") |> 
+  dplyr::filter(!Participant %in% c("S3", "S15", "S19", "S23"))  # No data
+
+# Adjustments for beta models
+df$Confidence[df$Confidence == 1] <- 0.99999
+df$Confidence[df$Confidence == 0] <- 0.00001
 

### 2021-12-07 preprocessing/data processing.Rmd
tidy up
move files to preprocessing, rename scripts folder, rename variables in data processing

--- 2021-11-11 scripts/claudia/data processing.Rmd
@@
 
-mydata <- read.csv('../../data/data_questionnaire/Demographics.csv', stringsAsFactors = FALSE)[-c(1:2), -c(1:17, 30, 32, 34, 36)]
+mydata <- read.csv('../data/data_questionnaire/Demographics.csv', stringsAsFactors = FALSE)[-c(1:2), -c(1:17, 30, 32, 34, 36)]
 
@@
 mydata <- data.frame()
-for (participant in list.files("../../data/data_experimental")) {
-  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/yoni/", participant, "_untitled.csv"))[-c(1:3,28,61,104), -c(4,5,7:38,42:47)]
+for (participant in list.files("../data/data_experimental")) {
+  df_sub <- read.csv(paste0("../data/data_experimental/", participant, "/yoni/", participant, "_untitled.csv"))[-c(1:3,28,61,104), -c(4,5,7:38,42:47)]
   mydata <- rbind(mydata, df_sub)
@@
   pivot_wider(names_from = condition, values_from = total) %>%
-  mutate(yoni_total = affect+cognitive+physical) %>%
-  rename(yoni_affective = affect,
-         yoni_cognitive = cognitive,
-         yoni_physical = physical)
+  mutate(YONI_Total = affect+cognitive+physical) %>%
+  rename(YONI_Affective = affect,
+         YONI_Cognitive = cognitive,
+         YONI_Physical = physical)
 
@@
 
-mydata <- read.csv("../../data/data_questionnaire/BES.csv", stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]
+mydata <- read.csv("../data/data_questionnaire/BES.csv", stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]
 
@@
 
-  mutate(BES_cognitive = Q3+Q6+Q9+Q10+Q12+Q14+Q16+Q19+Q20, 
-         BES_affective = Q1+Q2+Q4+Q5+Q7+Q8+Q11+Q13+Q15+Q17+Q18,
-         BES_total = BES_cognitive+BES_affective) %>%
+  mutate(BES_Cognitive = Q3+Q6+Q9+Q10+Q12+Q14+Q16+Q19+Q20, 
+         BES_Affective = Q1+Q2+Q4+Q5+Q7+Q8+Q11+Q13+Q15+Q17+Q18,
+         BES_Total = BES_Cognitive+BES_Affective) %>%
 
@@
 mydata <- data.frame()
-for (participant in list.files("../../data/data_experimental")) {
-  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/heartbeat/", participant, "_heartbeat.csv"))[-c(6:9), -c(1, 3:8, 12:31, 33:38)]  
+for (participant in list.files("../data/data_experimental")) {
+  df_sub <- read.csv(paste0("../data/data_experimental/", participant, "/heartbeat/", participant, "_heartbeat.csv"))[-c(6:9), -c(1, 3:8, 12:31, 33:38)]  
   mydata <- rbind(mydata, df_sub)
@@
   rename(hbcount_reported = heartbeatresponse.text,
-       HCT_confidence = confidenceslider.response,
-       HCT_confidenceRT = confidenceslider.rt,
+       HCT_Confidence = confidenceslider.response,
+       HCT_ConfidenceRT = confidenceslider.rt,
        ID = participant) %>%
@@
   mutate(hbcount_reported = as.numeric(hbcount_reported),
-         HCT_confidence = as.numeric(HCT_confidence)) %>%
+         HCT_Confidence = as.numeric(HCT_Confidence)) %>%
 
@@
   mutate(denominator = (hbcount_real + hbcount_reported)/2) %>% 
-  mutate(HCT_accuracy = 1 - numerator/denominator)
+  mutate(HCT_Accuracy = 1 - numerator/denominator)
 
@@
 for(participant in unique(data$ID)) {
-  conf <- data[data$ID == participant, "HCT_confidence"]
-  acc <- data[data$ID == participant, "HCT_accuracy"]
+  conf <- data[data$ID == participant, "HCT_Confidence"]
+  acc <- data[data$ID == participant, "HCT_Accuracy"]
   awa <- cor(conf, acc, use = "pairwise.complete.obs")
@@
                        data.frame(ID = participant,
-                                  HCT_awareness = awa))
+                                  HCT_Awareness = awa))
 }
@@
 results <- data %>% 
-  select(c(ID, HCT_confidence, HCT_accuracy, HCT_awareness)) %>% 
+  select(c(ID, HCT_Confidence, HCT_Accuracy, HCT_Awareness)) %>% 
   group_by(ID) %>%
@@
 
-parttwo <- data.frame()
-for (participant in list.files("../../data/data_experimental")) {
-  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/heartbeat/", participant, "_heartbeat.csv"))[-c(1:5, 9), -c(1:13, 16:19, 22:25, 28:31, 33:38)]  
-  parttwo <- rbind(parttwo, df_sub)
-}
-
-parttwo <- parttwo %>% 
-  rename(guess = key_guess.keys,
-         guessRT = key_guess.rt,
-         noguess = key_noguess.keys,
-         noguessRT = key_noguess.rt,
-         onebreath = key_noguess_perturbed.keys,
-         onebreathRT = key_noguess_perturbed.rt,
-         ID = participant) %>% 
-  group_by(ID) %>% 
-  summarise_all(funs(trimws(paste(., collapse = ''))))
-
-parttwo <- parttwo %>% 
-  mutate(HCT_guess = str_count(parttwo$guess, "space"),
-         HCT_noguess = str_count(parttwo$noguess, "space"),
-         HCT_onebreath = str_count(parttwo$onebreath, "space")) %>% 
-  select(c(ID, HCT_guess, HCT_noguess, HCT_onebreath))
-
-results <- left_join(results, parttwo)
+# parttwo <- data.frame()
+# for (participant in list.files("../data/data_experimental")) {
+#   df_sub <- read.csv(paste0("../data/data_experimental/", participant, "/heartbeat/", participant, "_heartbeat.csv"))[-c(1:5, 9), -c(1:13, 16:19, 22:25, 28:31, 33:38)]  
+#   parttwo <- rbind(parttwo, df_sub)
+# }
+#   
+# parttwo <- parttwo %>% 
+#   rename(guess = key_guess.keys,
+#          guessRT = key_guess.rt,
+#          noguess = key_noguess.keys,
+#          noguessRT = key_noguess.rt,
+#          onebreath = key_noguess_perturbed.keys,
+#          onebreathRT = key_noguess_perturbed.rt,
+#          ID = participant) %>% 
+#   group_by(ID) %>% 
+#   summarise_all(funs(trimws(paste(., collapse = ''))))
+# 
+# parttwo <- parttwo %>% 
+#   mutate(HCT_guess = str_count(parttwo$guess, "space"),
+#          HCT_noguess = str_count(parttwo$noguess, "space"),
+#          HCT_onebreath = str_count(parttwo$onebreath, "space")) %>% 
+#   select(c(ID, HCT_guess, HCT_noguess, HCT_onebreath))
+# 
+# results <- left_join(results, parttwo)
 
@@
 
-mydata <- read.csv('../../data/data_questionnaire/MAIA2.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]
+mydata <- read.csv('../data/data_questionnaire/MAIA2.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]
 
@@
         MAIA5 = (Q23+Q24+Q25+Q26+Q27)/5, MAIA6 = (Q28+Q29+Q30+Q31)/4, MAIA7 = (Q32+Q33+Q34)/3, MAIA8 = (Q35+Q36+Q37)/3) %>% 
-  mutate(MAIA_total = (MAIA1+MAIA2+MAIA3+MAIA4+MAIA5+MAIA6+MAIA7+MAIA8)/8) %>%
-  rename(MAIA_noticing = MAIA1,
-         MAIA_not_distracting = MAIA2,
-         MAIA_not_worrying = MAIA3,
-         MAIA_attention_regulation = MAIA4,
-         MAIA_emotional_awareness = MAIA5,
-         MAIA_self_regulation = MAIA6,
-         MAIA_body_listening = MAIA7,
-         MAIA_trusting = MAIA8) %>%
+  mutate(MAIA_Total = (MAIA1+MAIA2+MAIA3+MAIA4+MAIA5+MAIA6+MAIA7+MAIA8)/8) %>%
+  rename(MAIA_Noticing = MAIA1,
+         MAIA_NotDistracting = MAIA2,
+         MAIA_NotWorrying = MAIA3,
+         MAIA_AttentionRegulation = MAIA4,
+         MAIA_EmotionalAwareness = MAIA5,
+         MAIA_SelfRegulation = MAIA6,
+         MAIA_BodyListening = MAIA7,
+         MAIA_Trusting = MAIA8) %>%
 
@@
 
-mydata <- read.csv('../../data/data_questionnaire/Lie Scale.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]
+mydata <- read.csv('../data/data_questionnaire/Lie Scale.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]
 
@@
 
-  mutate(lie_ability = (Q4+Q5+Q6+Q7)/4, 
-         lie_frequency = (Q1+Q2+Q3+Q8)/4, 
-         lie_negativity = (Q9+Q11+Q13+Q16)/4, 
-         lie_contextuality = (Q10+Q12+Q14+Q15)/4) %>%
+  mutate(LIE_Ability = (Q4+Q5+Q6+Q7)/4, 
+         LIE_Frequency = (Q1+Q2+Q3+Q8)/4, 
+         LIE_Negativity = (Q9+Q11+Q13+Q16)/4, 
+         LIE_Contextuality = (Q10+Q12+Q14+Q15)/4) %>%
 
@@
 
-write.csv(results, file = "liescale_processed.csv", row.names=FALSE)
+write.csv(results, file = "lie_processed.csv", row.names=FALSE)
 ```
@@
 mydata <- data.frame()
-for (participant in list.files("../../data/data_experimental")) {
-  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), c(1:4, 29, 31, 35, 36, 43, 45, 47)] %>% 
-    mutate(trial = c(1:80),
-           condition = c(rep("Social", 40), rep("Polygraph", 40)))
+for (participant in list.files("../data/data_experimental")) {
+  df_sub <- read.csv(paste0("../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), c(1:4, 29, 31, 35, 36, 43, 45, 47)] %>% 
+    mutate(Trial = c(1:80),
+           Condition = c(rep("Social", 40), rep("Polygraph", 40)))
   mydata <- rbind(mydata, df_sub)
@@
 
-inclusion <- read.csv("../final_processing/Errors.csv") %>%
-  rename(ID = ï..participant,
-         trial = Trial,
-         inclusion = Inclusion,
-         inclusion2 = Inclusion2)
-
 data <- mydata %>% 
-  rename(item = V1,
-       style = V2,
-       instruction = V3,
-       question = V4,
+  rename(Item = V1,
+       Phrasing = V2,
+       Answer = V3,
+       Question = V4,
        social_start = V29,
        social_stop = V31,
-       DT_confidence = V35,
-       DT_confidenceRT = V36,
+       Confidence = V35,
+       ConfidenceRT = V36,
        polyg_start = V43,
@@
 
-  mutate(DT_confidence = as.numeric(DT_confidence),
+  mutate(Confidence = as.numeric(Confidence),
          social_start = as.numeric(social_start),
@@
          ID = as.numeric(ID)) %>%
-  mutate(DT_RT = ifelse(condition == "Social", social_stop - social_start,
-         ifelse(condition == "Polygraph", polyg_stop - polyg_start, NA))) %>%
+  mutate(RT = ifelse(Condition == "Social", social_stop - social_start,
+         ifelse(Condition == "Polygraph", polyg_stop - polyg_start, NA))) %>%
 
-  left_join(inclusion) %>%
-  select(ID, trial, condition, inclusion, inclusion2, everything()) # move columns to front
-
-results <- data %>%
-  group_by(ID, instruction, style) %>%
-  summarise(DT_RT_avg = mean(DT_RT, na.rm = TRUE),
-            DT_confidence_avg = mean(DT_confidence, na.rm = TRUE))
+  select(ID, Trial, Condition, everything()) # move columns to front
 
 write.csv(data, file = "deceptiontask_extracted.csv", row.names=FALSE)
-write.csv(results, file = "deceptiontask_processed.csv", row.names=FALSE)
 ```
@@
   select(-c(contains(paste0("Q", 0:9)))) %>%
-  left_join(read.csv("liescale_processed.csv")) %>% 
+  left_join(read.csv("lie_processed.csv")) %>% 
   select(-c(contains(paste0("Q", 0:9)))) %>%
   left_join(read.csv("demo.csv")) %>% 
-  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG))
+  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG)) %>% 
+  rename(Participant = ID) %>% 
+  mutate(Answer = fct_recode(Answer, Lie = "LIE", Truth = "TRUTH"))
 
-write.csv(data_combined, file = "../../data/data_combined.csv", row.names = FALSE)
+write.csv(data_combined, file = "../data/data_combined.csv", row.names = FALSE)
 ```

### 2021-12-07 preprocessing/heartbeat_counting.py

@@ -8,16 +8,20 @@ import pandas as pd
 
 # Set working directory
 directory = os.getcwd()
-list_participants = os.listdir(directory + "/../../data/data_experimental")
-HCT_real = {"time": np.array([20, 25, 30, 35, 40])}
+list_participants = os.listdir(directory + "/../data/data_experimental")
+HCT_real = {"task": np.array([20, 25, 30, 35, 40])}
 for participant in list_participants:
-    subdir = directory + "/../../data/data_experimental/" + participant + "/heartbeat/"
+    subdir = directory + "/../data/data_experimental/" + participant + "/heartbeat/"
 
 # Load data
     filename = [i for i in os.listdir(subdir) if i.endswith('.txt')][0]
     bio, sampling_rate = nk.read_bitalino(subdir + "/" + filename)
 
-
+# Clean ecg signal
+    ecg_cleaned = nk.ecg_clean(bio["ECGBIT"], sampling_rate=sampling_rate)
+    
+# Epoching
+    events = nk.events_find(bio["LUX"], duration_min = 3, event_conditions=['start', 'stop'] * 8)
     event_conditions = np.array(['start', 'stop'] * 8)
     events_start = np.array(events["onset"])[event_conditions == 'start']
     events_duration = np.array(events["onset"])[event_conditions == 'stop'] - events_start

### 2021-12-07 preprocessing/heartbeat_tracking.py

@@ -10,7 +10,7 @@ pd.options.mode.chained_assignment = None  # default='warn'
 
 ### Get psychopy data files ---------------------------------------------------
 directory = os.getcwd()
-list_participants = os.listdir(directory + "/../../data/data_experimental")
+list_participants = os.listdir(directory + "/../data/data_experimental")
 
 ### Utilities -----------------------------------------------------------------
 def extract_taps(data, key, rt):
@@ -58,7 +58,7 @@ df_all = pd.DataFrame([])
 
 for i, participant in enumerate(list_participants):
 #     # Check number of photosensor events per participant (16 expected)
-#     subdir = directory + "/../../data/data_experimental/" + participant + "/heartbeat/"
+#     subdir = directory + "/../data/data_experimental/" + participant + "/heartbeat/"
 #     filename = [i for i in os.listdir(subdir) if i.endswith('.txt')][0]
 #     bio, sampling_rate = nk.read_bitalino(subdir + "/" + filename)
 #     n_events = len(nk.events_find(bio["LUX"])['onset'])
@@ -67,7 +67,7 @@ for i, participant in enumerate(list_participants):
 #     # participants 012, 023: 3 extra
     
     # Directory of where heartbeat data is stored
-    subdir = directory + "/../../data/data_experimental/" + participant + "/heartbeat/"
+    subdir = directory + "/../data/data_experimental/" + participant + "/heartbeat/"
 
     # Get psychopy data
     print(f"Reading psychopy data for participant: {participant}\n======================")
@@ -130,4 +130,4 @@ for i, participant in enumerate(list_participants):
     df['ID'] = i + 1  # append participant number
     df_all = pd.concat([df_all, df])  # combine all participants
 
-df_all.to_csv("HCT_Tracking.csv", na_rep="NA", index=False)
+df_all.to_csv("HCT_tracking.csv", na_rep="NA", index=False)

### 2021-12-07 1_Measures.Rmd
move data merging to data processing file
HTT (originally in measures) and physio (original in python)

@@
 ```{r message=FALSE}
-htt_data <- read.csv("scripts/claudia/HCT_Tracking.csv") |> 
-  mutate(Participant = paste0("S", as.character(ID)),
-         Condition = fct_recode(Condition, "NoGuessPerturbed" = "NoGuess_Perturbed")) |> 
+htt_data <- read.csv("preprocessing/HTT_extracted.csv") |> 
+  mutate(Condition = fct_recode(Condition, "NoGuessPerturbed" = "NoGuess_Perturbed")) |> 
   rename(Distance = Time_to_Rpeak)
@@
   see::theme_modern() 
-
-# model <- rstanarm::stan_lmer(Distance ~ Condition + (1 + Condition | ID), data = hct_data, refresh=0, chains = 2)
-# model <- glmmTMB::glmmTMB(Distance ~ Condition + (1 | ID), data = hct_data)
-
-htt_scores <- htt_data |> 
-  group_by(Participant, Condition) |> 
-  summarise(HTT_Mean = mean(Distance),
-            HTT_n = n()) |> 
-  ungroup() |> 
-  complete(Participant, Condition, fill = list(HTT_Mean = NA, HTT_n = 0)) |> 
-  tidyr::pivot_wider(names_from = "Condition", values_from = c("HTT_Mean", "HTT_n"))
-
-df <- merge(df, htt_scores, by = "Participant")
 ```

### 2021-12-07 index.Rmd
move data merging to data processing file
HTT (originally in measures) and physio (original in python)

@@
 ```{r warning=FALSE, message=TRUE, results='asis'}
-# setwd("C:/Users/user/Desktop/Sputnik/2019-23/DeceptionInteroTom")
-
-df <- read.csv("data/data_combined_wPhysio.csv") %>% 
-  mutate(ID = as.factor(paste0("S", ID)),
+df <- read.csv("data/data_combined.csv") %>% 
+  mutate(Participant = as.factor(paste0("S", Participant)),
          Condition = as.factor(Condition),
@@
          Answer = as.factor(Answer)) |> 
-  rename("HeartRate" = "ECG_Rate_MeanRaw_1.5_2.5s") |> 
   dplyr::filter(!Participant %in% c("S3", "S15", "S19", "S23"))  # No data

### 2021-12-07 preprocessing/data processing.Rmd
move data merging to data processing file
HTT (originally in measures) and physio (original in python)

@@
 
+```{r int obj htt}
+rm(list=ls())
+cat("\014")
+
+mydata <- read.csv("HTT_extracted.csv") %>% 
+  mutate(Condition = fct_recode(Condition, "NoGuessPerturbed" = "NoGuess_Perturbed")) %>% 
+  rename(Distance = Time_to_Rpeak)
+
+results <- mydata %>% 
+  group_by(ID, Condition) %>% 
+  summarise(HTT_Mean = mean(Distance),
+            HTT_n = n()) %>%  
+  ungroup() %>% 
+  complete(ID, Condition, fill = list(HTT_Mean = NA, HTT_n = 0)) %>% 
+  tidyr::pivot_wider(names_from = "Condition", values_from = c("HTT_Mean", "HTT_n"))
+
+write.csv(results, file = "HTT_processed.csv", row.names=FALSE)
+```
+
 ```{r int subj maia2}
@@
   df_sub <- read.csv(paste0("../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), c(1:4, 29, 31, 35, 36, 43, 45, 47)] %>% 
-    mutate(Trial = c(1:80),
-           Condition = c(rep("Social", 40), rep("Polygraph", 40)))
+    mutate(trial = c(1:80),
+           condition = c(rep("Social", 40), rep("Polygraph", 40)))
   mydata <- rbind(mydata, df_sub)
@@
          ID = as.numeric(ID)) %>%
-  mutate(RT = ifelse(Condition == "Social", social_stop - social_start,
-         ifelse(Condition == "Polygraph", polyg_stop - polyg_start, NA))) %>%
+  mutate(RT = ifelse(condition == "Social", social_stop - social_start,
+         ifelse(condition == "Polygraph", polyg_stop - polyg_start, NA))) %>%
 
-  select(ID, Trial, Condition, everything()) # move columns to front
+  select(ID, trial, condition, everything()) # move columns to front
 
@@
   select(-c(contains("start")|contains("stop"))) %>% 
+  left_join(read.csv("deceptiontask_physio_processed.csv")) %>% 
   left_join(read.csv("yoni_processed.csv")) %>% 
@@
   left_join(read.csv("HCT_processed.csv")) %>% 
+  left_join(read.csv("HTT_processed.csv")) %>% 
   left_join(read.csv("MAIA2_processed.csv")) %>% 
@@
   select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG)) %>% 
-  rename(Participant = ID) %>% 
+  rename(Participant = ID,
+         Trial = trial,
+         Condition = condition,
+         HeartRate = ECG_Rate_MeanRaw_1.5_2.5s) %>%
   mutate(Answer = fct_recode(Answer, Lie = "LIE", Truth = "TRUTH"))

### 2021-12-07 preprocessing/heartbeat_tracking.py

@@ -130,4 +130,4 @@ for i, participant in enumerate(list_participants):
     df['ID'] = i + 1  # append participant number
     df_all = pd.concat([df_all, df])  # combine all participants
 
-df_all.to_csv("HCT_tracking.csv", na_rep="NA", index=False)
+df_all.to_csv("HTT_extracted.csv", na_rep="NA", index=False)

### 2021-12-07 preprocessing/physio_DeceptionTask.py

@@ -80,16 +80,14 @@ for participant in list_participants:
     df = pd.concat([df, data], axis=0)
 
 # Load behavioural
-data_beh = pd.read_csv("../data/data_combined.csv")
+data_beh = pd.read_csv("deceptiontask_extracted.csv")
 data_beh["ID"] = data_beh["ID"].astype(str)
 
-# Merge features
-data_all = pd.merge(df, data_beh)
-assert len(data_beh) == len(data_all)
-data_all.to_csv("../data/data_combined_wPhysio.csv", index=False)
+# Export data
+df.to_csv("deceptiontask_physio_processed.csv", index=False)
 
 # Merge signals
 df_signal = pd.merge(df_signal, data_beh)
-df_signal.groupby(["ID", "condition", "instruction"])[np.arange(4000)].mean().to_csv(
-    "../data/data_physio_DeceptionTask.csv"
+df_signal.groupby(["ID", "condition", "Answer"])[np.arange(4000)].mean().to_csv(
+    "deceptiontask_physio_extracted.csv"
 )

### 2021-12-12 1_Measures.Rmd
minor edits
change social to interrogation

@@
 ```{r warning=FALSE}
-df_physio <- read.csv("data/data_physio_DeceptionTask.csv") |> 
+df_physio <- read.csv("preprocessing/deceptiontask_physio_extracted.csv") |> 
   dplyr::filter(ID != 30) |> 
@@
   mutate(Time = as.numeric(str_remove(Time, "X"))-500,
-         group = paste0(ID, condition, instruction),
-         condition = fct_recode(condition, "Interrogation" = "Social"),
-         instruction = fct_relevel(instruction, "TRUTH")) |> 
-  group_by(condition, instruction, Time) |> 
+         group = paste0(ID, condition, Answer),
+         instruction = fct_relevel(Answer, "TRUTH")) |> 
+  group_by(condition, Answer, Time) |> 
   summarise(HeartRate = mean(HeartRate)) |> 
@@
   annotate("rect", xmin=1500, xmax=2500, ymin=-Inf, ymax=Inf, alpha=0.1, fill = "green") +
-  geom_line(aes(color = condition, linetype = instruction), size=1) +
+  geom_line(aes(color = condition, linetype = Answer), size=1) +
   geom_vline(aes(xintercept=0), linetype = "dotted") +
@@
 df$Confidence[df$Participant %in% c("S9", "S29")] <- NA # Extreme responses
-sum(is.na(df$Confidence)) / nrow(df) * 100
 df$HeartRate[df$Participant == "S30"] <- NA # Extreme values
-sum(is.na(df$HeartRate)) / nrow(df) * 100
 df$RT[df$Participant == "S13"] <- NA # Slower than the others
 df$RT[df$RT > 8.25] <- NA # Extreme RT values 
-sum(is.na(df$RT)) / nrow(df) * 100
 ```
+
+- Percentage of Confidence data removed: `r sum(is.na(df$Confidence)) / nrow(df) * 100`
+- Percentage of RT data removed: `r sum(is.na(df$RT)) / nrow(df) * 100`
+- Percentage of Heart Rate data removed: `r sum(is.na(df$HeartRate)) / nrow(df) * 100`
 
@@
 df <- df |> 
-  # Remove participants
+  # Remove outlier trials
   group_by(Participant) |> 

### 2021-12-12 2_ManipulationChecks.Rmd
minor edits
change social to interrogation

@@
 ```{r message=FALSE, warning=FALSE}
-r <- correlation(select(dfsub, starts_with("HTT_")),
-                 select(dfsub, starts_with("HCT_")), 
-                 p_adjust = "none")
-
-summary(r) |> 
-  plot()
+# Leave out HTT
+# r <- correlation(select(dfsub, starts_with("HTT_")),
+#                  select(dfsub, starts_with("HCT_")), 
+#                  p_adjust = "none")
+# 
+# summary(r) |> 
+#   plot()
 ```
@@
 r <- correlation(select(dfsub, starts_with("MAIA_")),
-                 select(dfsub, starts_with("HCT_"), starts_with("HTT_")), 
+                 select(dfsub, starts_with("HCT_")), 
+                        #starts_with("HTT_")), 
                  p_adjust = "none")
@@
 summary(r) |> 
-  plot()
+  plot() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer * Phrasing + (1|Participant), data = df)
+model <- glmmTMB(RT ~ Answer * Phrasing + (1|Participant) + (1|Item), 
+                 data = df)
 
@@
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer * Phrasing + (1|Participant), data = df)
+model <- glmmTMB(Confidence ~ Answer * Phrasing + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
 
-parameters::parameters(model)
+parameters::parameters(model, effects = "fixed")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer * Phrasing + (1|Participant), data = df)
+model <- glmmTMB(HeartRate ~ Answer * Phrasing + (1|Participant) + (1|Item), 
+                 data = df)
 
-parameters::parameters(model)
+parameters::parameters(model, effects = "fixed")
 ```
@@
 
-## Effect of Condition
+## Effect of Condition {.tabset}
 
@@
 
-- Significant interaction between the condition and the answer: the effect of answer (being more confident in truths than in lies) is lower in the social condition.
+- Significant interaction between the condition and the answer: the effect of answer (being more confident in truths than in lies) is lower in the interrogation condition.
 - Effect mostly driven by lower lie confidence in the polygraph condition: less obvious feedback cues?
@@
 ```{r message=FALSE, warning=FALSE}
+modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
+modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
+```
+
+```{r message=FALSE, warning=FALSE}
 estimate_means(model, at = c("Condition", "Answer")) |> 
@@
 
-- Higher heart rate in lies vs. truths, and higher heart rate in social condition vs. polygraph.
+- Higher heart rate in lies vs. truths, and higher heart rate in interrogation condition vs. polygraph.
 - No interaction.

### 2021-12-12 3_ToM.Rmd
minor edits
change social to interrogation

@@
 
-- When instructed to lie, the decrease in confidence in participants with higher yoni score is less in social than polygraph condition.
+- When instructed to lie, the decrease in confidence in participants with higher yoni score is less in interrogation than polygraph condition.
 
@@
          x = paste0(stringr::str_replace(var, "_", " ("), ")")) +
-    scale_color_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) +
-    scale_fill_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) + 
+    scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
+    scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) + 
     facet_wrap(~Answer)
@@
 p_conf_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "Confidence")
+# p_conf_yoni_total
 ```

### 2021-12-12 index.Rmd
minor edits
change social to interrogation

@@
 ---
-title: '**The Place of Interoception and Theory of Mind in Deception**'
+title: '**The Role of Interoception and Theory of Mind in Deception**'
 subtitle: A Subtitle
@@
 df <- read.csv("data/data_combined.csv") %>% 
-  mutate(Participant = as.factor(paste0("S", Participant)),
+  mutate(Participant = factor(paste0("S", Participant), levels = paste0("S", 1:30)),
          Condition = as.factor(Condition),

### 2021-12-12 preprocessing/data processing.Rmd
minor edits
change social to interrogation

@@
     mutate(trial = c(1:80),
-           condition = c(rep("Social", 40), rep("Polygraph", 40)))
+           condition = c(rep("Interrogation", 40), rep("Polygraph", 40)))
   mydata <- rbind(mydata, df_sub)
@@
        Question = V4,
-       social_start = V29,
-       social_stop = V31,
+       interro_start = V29,
+       interro_stop = V31,
        Confidence = V35,
@@
   mutate(Confidence = as.numeric(Confidence),
-         social_start = as.numeric(social_start),
-         social_stop = as.numeric(social_stop),
+         interro_start = as.numeric(interro_start),
+         interro_stop = as.numeric(interro_stop),
          polyg_start = as.numeric(polyg_start),
@@
          ID = as.numeric(ID)) %>%
-  mutate(RT = ifelse(condition == "Social", social_stop - social_start,
+  mutate(RT = ifelse(condition == "Interrogation", interro_stop - interro_start,
          ifelse(condition == "Polygraph", polyg_stop - polyg_start, NA))) %>%

### 2021-12-12 preprocessing/physio_DeceptionTask.py

@@ -15,7 +15,7 @@ for participant in list_participants:
             {
                 "ID": "22",
                 "trial": np.arange(1, 81),
-                "condition": ["Social"] * 40 + ["Polygraph"] * 40,
+                "condition": ["Interrogation"] * 40 + ["Polygraph"] * 40,
                 "ECG_Rate_MeanRaw": np.repeat(np.nan, 80),
                 "ECG_Rate_Mean": np.repeat(np.nan, 80),
             }
@@ -30,7 +30,7 @@ for participant in list_participants:
         # Initialize data
         data = pd.DataFrame(
             {
-                "condition": ["Social"] * 40 + ["Polygraph"] * 40,
+                "condition": ["Interrogation"] * 40 + ["Polygraph"] * 40,
                 "trial": np.arange(1, 81),
                 "ID": [participant.lstrip("0")] * 80,
             }

### 2021-12-18 1_Measures.Rmd
added interpretations

@@
 
-- Percentage of Confidence data removed: `r sum(is.na(df$Confidence)) / nrow(df) * 100`
-- Percentage of RT data removed: `r sum(is.na(df$RT)) / nrow(df) * 100`
-- Percentage of Heart Rate data removed: `r sum(is.na(df$HeartRate)) / nrow(df) * 100`
+Percentage of Confidence data removed: `r sum(is.na(df$Confidence)) / nrow(df) * 100` %  
+Percentage of RT data removed: `r sum(is.na(df$RT)) / nrow(df) * 100` %  
+Percentage of Heart Rate data removed: `r sum(is.na(df$HeartRate)) / nrow(df) * 100` %
 

### 2021-12-18 3_ToM.Rmd
added interpretations

@@
 
-- When instructed to lie, the decrease in confidence in participants with higher yoni score is less in interrogation than polygraph condition.
+- Confidence: effect in total, cognitive and physical.
+- RT: effect in cognitive only.
+- Heart rate: no effect.
 
@@
 #### Confidence
+
+- Higher Yoni score associated with decreased lie confidence and increased truth confidence in polygraph condition only.
+- Significant interactions.
+- Driven by cognitive and physical domains.
+- Polygraph condition is harder: participants with better TOM became less confident in absence of another person from which to obtain feedback cues?
+- Plateau effect in interrogation condition, where individual differences do not matter as much?
 
@@
 #### RT
+
+- Effect only in cognitive domain: higher score associated with slower lie reaction time in polygraph condition and faster truth reaction time in interrogation condition.
+- No significant interaction.
 
@@
 
+- Confidence: effect in all.
+- RT: no effect.
+- Heart rate: effect in all.
+
 ### Total Score
@@
 #### Confidence
+
+- Higher BES score associated with decreased lie confidence and increased truth confidence in polygraph condition only.
+- Same as Yoni.
+- Significant interaction in lie only.
+- Effect in lie driven by both cognitive and affective domains, effect in truth driven by affective domain only.
 
@@
 #### Heart Rate
+
+- Higher BES score associated with increased lie and truth confidence in both conditions, with larger effect in interrogation condition.
+- Compared to no effect at all in Yoni.
+- Significant interactions.
+- More empathetic person will experience more physiological arousals.
+- Effect in interrogation is driven by both domains, effect in polygraph is driven by cognitive domain only.
 

### 2021-12-18 4_Intero.Rmd
minor edits
change social to interrogation
added interpretations

@@
 
+- Confidence: effect in all.
+- RT: effect in confidence only.
+- Heart rate: effect in accuracy and awareness.
+
 ### Interoceptive Accuracy
@@
 #### Confidence
+
+- Higher HCT accuracy score associated with increased lie confidence and decreased truth confidence in polygraph condition only.
+- Significant interaction in truth only.
 
@@
 
+- Higher HCT accuracy score associated with decreased lie heart rate in interrogation condition only.
+- Significant interaction.
+- Generally, larger effect in interrogation condition for heart rate?
+- Plateau effect in polygraph condition for heart rate?
+
 ```{r message=FALSE, warning=FALSE}
@@
 
+- Higher HCT confidence score associated with increased lie confidence and decreased truth confidence in both conditions, with larger effect in polygraph condition.
+- But no significant interaction.
+
 ```{r message=FALSE, warning=FALSE}
@@
 #### RT
+
+- Higher HCT confidence score associated with faster lie reaction time in polygraph condition and faster truth reaction time in both conditions.
+- No significant interaction.
 
@@
 
+- Higher HCT awareness score associated with decreased lie confidence in polygraph condition only.
+- Significant interaction.
+
 ```{r message=FALSE, warning=FALSE}
@@
 #### Heart Rate
+
+- Higher HCT awareness score associated with decreased lie heart rate in interrogation condition only.
+- Significant interaction.
 
@@
 
+- Confidence: effect in total, noticing, not distracting, body listening, not worrying, attention regulation and self regulation.
+- RT: effect in total, noticing, body listening, attention regulation and self regulation.
+- Heart rate: effect in trusting and emotional awareness only.
+
 ### Total Score
@@
 #### Confidence
+
+- Higher MAIA score associated with increased lie confidence in both conditions with a larger effect in polygraph condition, and decreased truth confidence in polygraph condition only.
+- Significant interactions.
+- Effect in lie driven by all domains except trusting and emotional awareness, effect in truth driven by noticing, attention regulation and self regulation domains.
 
@@
 #### RT
+- Higher MAIA score associated with faster truth reaction time in polygraph condition only.
+- Significant interaction.
+- Driven by body listening, attention regulation and self regulation domains.
+- Faster lie reaction time in polygraph condition for noticing, body listening and attention regulation domains.
 
@@
 #### Heart Rate
+
+- Effect only in trusting and emotional awareness domains: higher score associated with increased lie heart rate in interrogation for both, increased truth heart rate in interrogation for emotional awareness only.
+- No significant interactions.
 

### 2022-06-13 paper/manuscript_v0.Rmd
Update manuscript_v0.Rmd

@@
 ---
-title: '**Fractal and Entropic Characteristics of EEG during Resting State**'
-shorttitle        : "Resting-state EEG Complexity"
+title: '**TITLE**'
+shorttitle        : "TITLE"
 author:
@@
     keep_tex: yes
-keywords: "EEG, Complexity, Entropy, Fractal Dimension, Resting State"
+keywords: ""
 wordcount: ''
@@
 
+```{=tex}
 \endgroup
+```

### 2022-06-13 paper/manuscript_v0.Rmd
Update manuscript_v0.Rmd

@@
 ---
-title: '**TITLE**'
+title: '**The Role of Interoception and Theory of Mind in Deception**'
 shorttitle        : "TITLE"
@@
 ```
-<!-- Resting state -->
-
-<!-- # Defining Complexity -->
-
-Complexity science is an umbrella term encompassing the study and characterization of "complex" systems - systems consisting of multiple interdependent components that operate and interact at different levels [@fernandez2013complexity].
-Such complex systems typically exhibit "chaotic" behaviour.
-Rather than referring to a state of disorder or confusion, a chaotic system is characterized by unpredictability and irregularities, often the result of a multitude of nonlinear interactions [@faure2001there].
-As such, small changes in the system can lead to exponential changes (a property popularized as the 'butterfly effect').
-For instance, the Earth's atmosphere at any point in time and space is the result of a (virtually infinite) number of variables (e.g., temperature, particle composition, cloud density, etc.) interacting together, rendering any long-term projections challenging.
-Nevertheless, the overarching idea of complexity science is not necessarily to establish methods for making exact predictions, but rather to provide some insights into the characterization of the long-term trajectory of a given complex system [@faure2001there].
-These principles have its roots in a branch of mathematics called *chaos theory* [see @thietart1995chaos, for an overview], which has led several disciplines (e.g., environmental science, meteorology, biology) to adopt the framework of complex dynamical systems [@burggren2005assessing; @kiel1996chaos].
-
-The application of complexity science to nonlinear systems, referred to as "nonlinear dynamics", is an emerging approach gaining traction in the study of human physiology and pathology [@ehlers1995chaos].
-The theoretical conceptualization of the human physiological system as complex is warranted given that it is made up of multiple constituent subsystems (be it anatomical components or physiological processes) that are constantly interacting between themselves at different levels (i.e., from molecules to organs), as well as with the external environment to maintain homeostasis [@faure2001there].
-The underlying assumptions are that physiological systems are inherently complex [@golbeter1996biochemical], and that pathological states [or 'dynamical diseases', see @mackey1977oscillation] can be characterized by disrupted or abnormal dynamic processes.
-One of the seminal works that contributed to this perspective was @lipsitz1992loss, who demonstrated that aging and disease are associated with a generalized loss of physiological complexity due to functional and/or structural alteration in the underlying organization of the physiological system [see @vaillancourt2002changing for a schematic illustration of this idea].
-
-<!-- talk about eeg resting state analysis using complexity vs other traditional methods-->
-
-<!-- resting state + personality -->
-
--   Resting state brain activity as a novel way to identify neurobiological correlates of personality traits
--   Modulatory effects of trait feature affects brain activity permanently (vs experimentally dependent for modulatory effects of a state condition)
+# Introduction
 
@@
 
-Data from 80 participants was collected from two separate samples.
-Specifically, 45 participants from Singapore and 35 participants from France were recruited via posters, flyers, and online social media platforms.
-For the Singapore sample, participants were reimbursed 60 Singapore Dollars upon study completion, which included acquisition of resting-state EEG data and other tasks as part of a larger study.
-[**Describe French sample**].
-One participant from the Singapore sample was excluded due to technical problems in the study setup and [**any exclusions from french sample here**].
-The final sample included [...] participants ($N_{Singapore}$ = 44, $N_{France}$ = ...; Mean age = ..., SD = ..., range = [..., ...]; ...% females) The study was approved by the Institutional Review Board (Reference Number: IRB-2018-10-029) of Nanyang Technological University (NTU) in Singapore and by the [**Review board of French sample**].
-Inclusion criteria included absence of current or history of neurological, psychiatric, or cardiovascular disorders.
-
 ## Procedure
 
-### Singapore sample
-
-Prior to EEG data acquisition, participants first provided their written informed consent and completed an online questionnaire on demographic information and personality measures.
-128-channel EEG was then measured (sampling rate: 4000Hz) from participants for 8 minutes during eyes-closed rest.
-Participants were instructed to relax and stay still, to refrain from thinking about anything in particular, and to stay awake for the entire duration of the recording.
-All assessments were conducted at the same experimental location, in an air-conditioned (22 degrees celsius), dark, sound-attenuated room.
-EEG signals were recorded using Deymed's Truscan EEG system in accordance with the international 10-05 system, with most impedances around 15-20k$\Omega$ and all impedences kept below 50k$\Omega$.
-For maximal precision, a photosensor attached to the screen marked event timings (i.e., the start and end) of the resting session.
-After the resting condition, participants answered some questions pertaining to sensations and thoughts that they experienced during the resting state.
-
-<!-- describe French set up??-->
+###
 
@@
 
-### Personality
-
-Personality traits were assessed using the 24-item Mini-IPIP6 based on the HEXACO Personality Model [@ashtonlee2009hexaco; @Sibley_2011].
-Sub-scores were computed for the 6 dimensions of personality, namely *Extraversion* (engagement in social behaviors), *Openness* (being open-minded such as displaying imagination and curiosity), *Agreeableness* (being cooperative and tolerant of others), *Conscientiousness* (being diligent, meticulous and organized), *Neuroticism* (the tendency to experience a persisting negative emotionality), and *Honesty-Humility* (being honest, sincere, and fair during social exchanges).
-
-### Resting-State Cognition
-
-Resting-state cognition was assessed using a brief questionnaire consisting of 6 items on a visual analogue scale, where participants were told to rate the percentage of time spent in 6 different states, namely, *Drowsiness* (feelings of drowsiness), *Absorption External* (the extent to which thoughts were directed towards external stimuli i.e., sounds, voices etc.), *Absorption Internal* (the extent to which thoughts were directed internally i.e., imagination, recalling of past events etc.), *Absorption Body* (the extent to which thoughts were directed bodily sensations and changes), *Mind Wandering* (free flowing of thoughts), and *Mind Focus* (the extent to which a particular thought or sensation was the prime focus).
-The protocol, including the task instructions, execution of the resting session, as well as the post-rest questionnaire, is open-access and available at [\*https://github.com/neuropsychology/RestingState\*\*](https://github.com/neuropsychology/RestingState).
+###
 
@@
 
-For each participant, complexity indices were computed at each electrode for the following frequency bands: gamma (30 - 80 Hz), beta (13 - 30 Hz), alpha (8 - 13 Hz), theta (4 - 8 Hz), and delta (1 - 4 Hz).
-[**Were these values z-scored?**].
-
-A factor analysis using a varimax rotation was conducted to identify the groupings of electrodes.
-[**Describe more**].
-The final groupings resulted in 5 distinct factors, namely *frontal*, *left*, *right*, *central*, and *posterior*, corresponding to the regions of the brain.
-
 # Results
@@
 
--   Limitations: lack of validated ASRQ measure
-
 # Funding
-
-The authors did not receive support from any organization for the submitted work.
 
@@
 
-<!-- D.M.
-conceived the study.
-Z.J.L.
-and T.P.
-coordinated the study and drafted the manuscript.
-D.M.
-and S.H.A.C.
-performed a critical review of the manuscript.
-All authors have read and agreed to the published version of the manuscript.
--->
-
 # Conflict of Interest Statement
-
-The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
 

### 2022-08-19 paper/manuscript_v0.Rmd
manuscript update

@@
 
+Much of the current research investigating the process and mechanisms involved in lying has considered capabilities such as Theory of Mind, the ability to understand and make inferences about other people's mental states and predict their behaviours [@el2017deception; @lee2021lying] .
+This ability is highly relevant in the context of deception, as the liar in question may utilize their inferences about the mental states of the other to predict whether the individual accepted as true the invalid information that they have presented to them [@stewart2019deception].
+However, there is a growing link between other cognitive and physiological mechanisms that may play a role in both deception detection, and fabricating successful lies.
+This includes the interplay of mechanisms underlying increased abilities in emotional intelligence, which has been associated with increased accuracy when detecting deception [@ainley2016bodily; @stewart2019deception].
+
+@wielgopolan2021can examined how greater awareness of one's own emotions and the emotional states of others may enhance the ability ability to accurately detect deception.
+Their research found a positive correlation between emotional awareness and the 'success' of a lie, suggesting that that individuals better at recognizing their own emotional state may be better at manipulating the cues that they output [@wielgopolan2021can].
+
+Interoception is the awareness and ability to monitor the sensations and state of one's internal organs, and is closely tied to emotional and cognitive processes [@garfinkel2015knowing].
+@ohira2020predictive suggests that from a predictive coding perspective, awareness of bodily signals and rapid interpretation and learning from these interoceptive signals plays a key role in the ability to regulate one's physical state.
+
+-expand on ohira's model
+
+This may partially explain why mindfulness practitioners tend to have greater interoceptive awareness and greater ability to regulate stress and associated physiological indicators [@ardi2021effects; @mcmahon2021mindful].
+
+Some research has examined how higher interoceptive accuracy, measured through heart beat detection, has been associated with vasoconstriction when faced with a liar, indicating that interoception may aid in discriminating high stakes emotional lies and truths [@gunderson2021body].
+It is clear that interoception may indicate on an implicit level that one is being lied to, however, there is limited research investigating how interoception may work the other way around, in favour of a liar, as @wielgopolan2021can's work appears to suggest.
+
+The findings by @vabba2022interoceptive indicate that high cardiac interoceptive participants were more likely to be dishonest and to tell higher egoistic lies.
+Meanwhile, @megias2019emotionally used EEG and heart rate to find that interoceptive awareness facilitated regulation of arousal during cognitive reappraisal.
+There is limited research examining whether individuals with high interoceptive accuracy may be more confident in managing physiological tells associated with emotions like guilt or anxiety that the lie may be discovered through suppression or reappraisal [@fustos2013embodiment; @megias2019emotionally].
+
+Since fluctuations in key physiological indicators as a means to determine whether the individual is lying is a key principle behind the polygraph test and other lie detection techniques, this paucity strengthens the need for more research examining the relationship between interoception and deception, and theory of mind, and the role it plays in moral behavior and deception.
+However, while there is a clear link established between interoception and deception playing a role in lie detection, limited research has been conducted examining this phenomena on its head.
+The act of lying is often accompanied by physiological responses such as increased heart rate, increased respiration and sweating.
+This research attempts to isolate the effects of theory of mind and interoception, and examine how they interact with deception.
+Of particular interest is how liars might utilize their interoceptive ability to self regulate in towards a more successful deception, and how this ability may compare or interact with other mechanisms at play such as theory of mind.
+
+-   more theory of mind
+
 # Methods
+
+## Study Design
 
@@
 
-## Procedure
+*26* participants (65.4% Females, M~*age*~ = 20.9, *SD* = 2.0) were
 
-###
+recruited VIA HOW
+
+for HUAT
+
+-exclusion criteria
+
+This research was approved by the Institutional Review Board (Reference Number: IRB-) of Nanyang Technological University (NTU).
+
+volunteered for [duration of study] for [compensation provided].
 
@@
 
-###
+### Theory of Mind and Empathy
 
-## EEG Complexity Measures
+Since Theory of Mind and empathy are closely related, *The Basic Empathy Scale (BES)* [@jolliffe2006development] was used as a subjective measure for theory of mind.
+*BES* uses a Likert scale to rate statements such as, "I can usually work out when people are cheerful".
+We also implemented the *Yoni Task,* which assesses the ability to judge mental states based on verbal cues, eye gaze and facial expression [@shamay2007dissociable].
+
+### Interoceptive Ability
+
+To measure interoception, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart], where participants count their heart beats without taking their pulse, as well as provide a confidence rating for their estimate.
+At the same time their true heart rate is recorded and the scores are compared to determine the individual's accuracy.
+They also completed the *MAIA questionnaire* [@mehling2012multidimensional], where they rated statements such as "I can use my breath to reduce tension" on a Likert scale.
+
+Heartbeat Tracking Task (HTT)
+
+### Deception
+
+LIE Scale ????
+
+#### Deception Task
+
+Participants were randomly allocated(??) between two conditions where they underwent 40 trials of a directed lying task.
+During the task, participants would be instructed to lie for 20 of the trials to questions such as, "What secondary school did you go to?".
+Prior to beginning the experiment, researchers collected the answers via questionnaire.
+In each condition, participants received false feedback through different mediums according to the condition that they were assigned, intended to examine the relationship between theory of mind or interoception and the dependent variables (see fig.
+X?).
+Participants were randomized between two conditions which we titled the Interrogation Condition and the Polygraph Condition.
+
+In the Interrogation condition, participants were instructed that following their lie, a live examiner over video feed would appear briefly to judge whether they were truthful or not.
+In actuality, the video of the examiner shown was pre-recorded and the same for all participants.
+We hypothesized that participants would will rely on theory of mind abilities to predict whether their lie to the examiner was successfully accepted as true.
+
+The Polygraph Condition followed the same routine, however instead of a recieving feedback from an interrogator, following the lie, a video of physiological signals was shown.
+We hypothesized when made acutely aware of such signals through false feedback, that participants would rely on interoceptive abilities to be more mindful or intentional about modulating the signals that may give them away.
+The physiological signals in this condition are also false feedback, and pre-recorded and identical for all participants.
+
+During each trial, the time it took for participants to answer is recorded, and their heart rates are measured using an electrocardiogram.
+Following the trial, participants gave a confidence rating for how successful they believe their lie or truth was.
+
+We hypothesize that participants with greater theory of mind ability will show higher lie confidence, shorter reaction time, and lower physiological arousal in the interrogation condition, while participants in the polygraph condition will demonstrate lower lie confidence, lower reaction time and higher physiological arousal during the polygraph prediction.
+(??)
+
+During the interrogation condition, participants were exposed to video feedback of an examiner following each question.
+They were informed that the examiner was live and monitoring their physiological signals remotely to determine the honesty of their answers, however this was false, and the same sequence of videos was show to each participant.
+
+### Demographic Information
+
+The demographic information we collected was age, ethnicity, nationality, dominant hand (for application of EDA electrodes, education level (determined by highest qualification received, or in the midst of achieving), religion and duration lived in Singapore.
+
+## Procedure
+
+Each subject was briefed on the experimental procedure and study aims and signed an informed consent document prior to the study commencing.
+
+questionnaire to obtain truthful answers to directed lying task,
+
+when were the measures like yoni etc taken?
+
+sound attenuated room
+
+Physio recording devices (equipment by huat and who)
+
+Where/how did they provide their answer during directed lying task
+
+Deception task
+
+During the experiment, all participants were connected to an electrocardiogram to monitor their heart would be asked a question, [HOW WAS ANSWER GIVEN?] and then connected for 10 seconds to the condition-unique stimulus.
+Following the exposure to the stimulus, they would be asked to rate their confidence on a sliding scale before repeating the trial 40 times.
+
+Debriefing was provided following the study.
 
@@
 
+We adopted a linear mixed-effect model where
+
+From the deception task, there were three dependent variables: confidence, reaction time and heart rate.
+For each dependent variable, we investigated its relationship with theory of mind and interoception abilities as measured by the tests on the previous slide.
+Participant and the specific question asked were added in as random effects, as they are not independent factors.
+For example, certain participants may be more confident in lying unrelated to their theory of mind or interoception abilities, or certain questions may have a longer reaction time
+
+To further build on the model, trials for lies and truths were separated using an embedded model and the interaction between the dependent variable and condition was probed.
+This reveals instances where the effect is greater in one condition, for example in this case, (mouseover) a higher total yoni score is correlated with decreased lie confidence, but only in the polygraph condition.
+
+INSERT VERY FANCY STATISTICS
+
+### Data Pre-Processing and Analyses
+
+??????????????????
+
 # Results
 
+INSERT VERY FANCY, VERY PRETTY GRAPHS
+
+Implicit relationship between dependent variables. Inter-Measure Correlation:
+
+-   (confident and reaction time) When lying, the faster they answer, the more confident they are.
+
+-   less confident in lies than truths (expected) Condition interaction, greater effect in polygraph (relying on interoception) likely less intuitive feedback cues??
+Slower in polygraph makes sense if less intuitive
+
+-   (HR and RT) no relationship
+
+TOM correlated with trials in polygraph (interoception), not expected(!) because expected it to correlate with Interrogation
+
+higher HCT accuracy and MAIA positively correlated with lie confidence in polygraph condition
+
+No effect for reaction time
+
+BES positively correlated with HR,
+
+HCT accuracy negatively correlated with HR
+
 # Discussion
+
+This study aimed to examine the relationship between theory of mind and interoception on lie confidence, reaction time and physiological arousal during deception.
+While there is an extensive literature examining the role of theory of mind abilities in deception, this research contributes new insights into how interoceptive abilities....
+
+It is interesting to note that the theory of mind measures are correlated with trials in the polygraph condition, when we expected it to be correlated with the interrogation condition instead.
+Higher HCT accuracy and MAIA scores are positively correlated with lie confidence in the polygraph condition, as expected.
+There was no significant effect for reaction time.
+BES is positively correlated with heart rate, even though we expected that better theory of mind ability would lead to lower physiological arousal.
+On the other hand, HCT accuracy is negatively correlated with heart rate, but only in the interrogation condition, even though we expected this for the polygraph condition.
+I will be going through these results in more detail, starting with confidence.
+
+### Interoception
+
+less confident in lies than truths (expected) Condition interaction, greater effect in polygraph (relying on interoception) likely less intuitive feedback cues??
+Slower in polygraph makes sense if less intuitive
+
+We found that greater interoceptive abilities were associated with greater lie confidence, and lower truth confidence, with a larger effect in the polygraph condition which was intended to test interoceptive abilities.
+Out of the 8 domains tested in MAIA, the interaction is significant for *noticing, body listening* and *attention regulation*.
+MAIA, HCT accuracy and confidence show the same effect.
+
+However, the effect of HCT awareness is more similar to that of theory of mind, where a higher score is associated with decreased lie confidence only in the polygraph condition.
+HCT awareness is the correlation between HCT accuracy and confidence.
+A low level of awareness could mean they accurately counted their heartbeats but were not confident, or vice versa where they were inaccurate at counting their heartbeats but were confident.
+Since awareness could mean two very different things, this data may not be very reliable.
+
+Generally, we found a negative correlation between measures of interoception and the Yoni Task, except for HCT awareness. (not significant)
+
+This is consistent with measures of interoception having an opposite effect to that of theory of mind except HCT awareness.
+The generally positive correlation of interoception with BES cognitive is opposite from the rest, but this agrees with the earlier results where the effect of BES cognitive is weaker.
+
+There is a strong correlation between MAIA and HCT confidence which is consistent with MAIA and HCT confidence showing the same effect.
+However, this also means that MAIA was only able to measure the confidence aspect of interoception.
+
+scores show a larger effect on confidence in the polygraph condition.
+
+-   could be polygraph condition more difficult less intuitive feedback cues
+
+-   better at interoception would be more confident in their lies, as we expected.
+
+-   On the other hand, those with better theory of mind become less confident in the absence of another person from which to obtain feedback cues.
+
+-   interrogation condition, may be a plateau effect where individual differences have a lesser effect
+
+### Theory of Mind
+
+TOM correlated with trials in polygraph (interoception), not expected(!) because expected it to correlate with Interrogation
+
+The greater Theory of Mind abilities, the lower participants lie confidence, and the higher their truth confidence in the polygraph (interoceptive) condition.
+The effect in the Yoni Task is driven by the cognitive and physical domains.
+For BES, the effect is only driven by the affective domain,
+
+This can also be seen in the correlation matrix where yoni is generally positively correlated with BES, even though none of the correlations are significant.
+The domains of the yoni task are also less correlated with the cognitive domain of BES, which is consistent with the smaller effect of BES cognitive in the previous slide.
+
+### Heart Rate
+
+For interoception, HCT accuracy is negatively correlated with heart rate, only in the interrogation condition.
+While it is expected that those with greater interoceptive ability would be better at percieving and regulating physiological arousal, we expected to see this result in the polygraph condition which emphasizes interoceptive abilities.
+
+-   relationship of BES scores with heart rate is also more prominent in the interrogation condition - in general scores show larger effect on heart rate in interrogation? emotional intelligence etc
+-   (confidence and HR) high in truths is associated with higher heart rate.
+Expected.
+Also slightly higher in interrogation than polygraph, since presence of another person can cause heightened physiological arousal @hazem2017know.
+Direct gaze increase bodily self awareness and physiological arousal
+
+A higher BES score correlated with a higher heart rate for both lies and truths in both conditions, with a larger effect in the interrogation condition.
+
+The effect in the polygraph condition is driven only by the cognitive domain of BES, while that in the interrogation condition is driven by both domains.
+
+\- more empathetic person will experience more physiological arousal (especially) when telling a lie.
+
+It is consistent with our hypothesis that this effect will be more pronounced in the interrogation condition.
+
+Yoni Task has no association with heart rate, implying that heart rate may be related to empathy only and not theory of mind.
+
+## Limitations and Future Research
+
+Potential limitations worth noting in this research is that the interrogation and polygraph conditions may not bring out Theory of Mind and interoceptive abilities to the greatest degree.
+This must be considered as a potential limitation since the participants were still connected to the ECG in the interrogation condition, which may amplify their interoceptive awareness beyond what they may normally experience during a real-world act of deception.
+Furthermore, as aforementioned, it is possible that there could be an interplay between Theory of Mind and interoception.
+More research is needed to investigate this relationship in the context of deception.
 

### 2022-08-23 paper/manuscript_v0.Rmd
Update manuscript_v0.Rmd
update manuscript

@@
 
-## Study Design
+The plan for this study was preregistered (OSF???????). The raw data and analysis script can be found at (GITHUB?????).
+
+##
 
@@
 Since Theory of Mind and empathy are closely related, *The Basic Empathy Scale (BES)* [@jolliffe2006development] was used as a subjective measure for theory of mind.
-*BES* uses a Likert scale to rate statements such as, "I can usually work out when people are cheerful".
+*BES* uses a 40-item Likert scale to rate statements such as, "I can usually work out when people are cheerful" from 1-5.
 We also implemented the *Yoni Task,* which assesses the ability to judge mental states based on verbal cues, eye gaze and facial expression [@shamay2007dissociable].
@@
 At the same time their true heart rate is recorded and the scores are compared to determine the individual's accuracy.
-They also completed the *MAIA questionnaire* [@mehling2012multidimensional], where they rated statements such as "I can use my breath to reduce tension" on a Likert scale.
+They also completed the *MAIA questionnaire* [@mehling2012multidimensional], where they rated 32 statements such as "I can use my breath to reduce tension" on a 1-5 Likert scale.
 
-Heartbeat Tracking Task (HTT)
+Additionally, we implemented the Heartbeat Tracking Task (HTT), in which participants  - tap one
 
@@
 
-LIE Scale ????
+We used the *LIE Scale*, which is a 44-item questionnaire examining deception as a dispositional trait, and measures the participant propensity towards lie frequency, ability, contextuality and negativity [@makowski2021structure].
+(!CHECK!)
 
@@
 
-The Polygraph Condition followed the same routine, however instead of a recieving feedback from an interrogator, following the lie, a video of physiological signals was shown.
+The Polygraph Condition followed the same routine, however instead of a receiving feedback from an interrogator, following the lie, a video of physiological signals was shown.
 We hypothesized when made acutely aware of such signals through false feedback, that participants would rely on interoceptive abilities to be more mindful or intentional about modulating the signals that may give them away.

### 2022-08-31 paper/manuscript_v0.Rmd
editing manuscript

--- 2022-08-19 paper/manuscript_v0.Rmd
@@
 
-Much of the current research investigating the process and mechanisms involved in lying has considered capabilities such as Theory of Mind, the ability to understand and make inferences about other people's mental states and predict their behaviours [@el2017deception; @lee2021lying] .
+# Methods
+
+## Study Design
+
+Much of the current research investigating the process and mechanisms involved in lying has considered capabilities such as Theory of Mind, the ability to understand and make inferences about other people's mental states and predict their behaviours [@el2017deception; @lee2021lying].
 This ability is highly relevant in the context of deception, as the liar in question may utilize their inferences about the mental states of the other to predict whether the individual accepted as true the invalid information that they have presented to them [@stewart2019deception].
-However, there is a growing link between other cognitive and physiological mechanisms that may play a role in both deception detection, and fabricating successful lies.
-This includes the interplay of mechanisms underlying increased abilities in emotional intelligence, which has been associated with increased accuracy when detecting deception [@ainley2016bodily; @stewart2019deception].
+However, there is a growing link between other cognitive and physiological mechanisms that may play a role in both deception detection, and fabricating successful lies
 
-@wielgopolan2021can examined how greater awareness of one's own emotions and the emotional states of others may enhance the ability ability to accurately detect deception.
-Their research found a positive correlation between emotional awareness and the 'success' of a lie, suggesting that that individuals better at recognizing their own emotional state may be better at manipulating the cues that they output [@wielgopolan2021can].
+Interoceptive awareness (IA) is the ability to monitor, interpret, integrate and regulate the sensations and state of one's internal organs, and is closely tied to emotional and cognitive processes [@garfinkel2015knowing, @chen2021emerging].
+Greater IA is associated with greater self-regulation [@weiss2014interaction], especially in mindfulness practitioners who tend to have greater interoceptive awareness and greater ability to regulate stress and associated physiological indicators [@ardi2021effects; @mcmahon2021mindful].
 
-Interoception is the awareness and ability to monitor the sensations and state of one's internal organs, and is closely tied to emotional and cognitive processes [@garfinkel2015knowing].
-@ohira2020predictive suggests that from a predictive coding perspective, awareness of bodily signals and rapid interpretation and learning from these interoceptive signals plays a key role in the ability to regulate one's physical state.
-
--expand on ohira's model
-
-This may partially explain why mindfulness practitioners tend to have greater interoceptive awareness and greater ability to regulate stress and associated physiological indicators [@ardi2021effects; @mcmahon2021mindful].
-
-Some research has examined how higher interoceptive accuracy, measured through heart beat detection, has been associated with vasoconstriction when faced with a liar, indicating that interoception may aid in discriminating high stakes emotional lies and truths [@gunderson2021body].
-It is clear that interoception may indicate on an implicit level that one is being lied to, however, there is limited research investigating how interoception may work the other way around, in favour of a liar, as @wielgopolan2021can's work appears to suggest.
-
+Some research has examined how higher interoceptive accuracy, measured through heart beat detection, has been associated with vasoconstriction when faced with a liar, indicating that IA may aid in discriminating high stakes emotional lies and truths [@gunderson2021body].
+It is clear that interoception may indicate on an implicit level that one is being lied to, however, there is limited research investigating how interoception may work the other way around, in favour of a liar in regulating their own physiological state that may betray their deception.
 The findings by @vabba2022interoceptive indicate that high cardiac interoceptive participants were more likely to be dishonest and to tell higher egoistic lies.
 Meanwhile, @megias2019emotionally used EEG and heart rate to find that interoceptive awareness facilitated regulation of arousal during cognitive reappraisal.
-There is limited research examining whether individuals with high interoceptive accuracy may be more confident in managing physiological tells associated with emotions like guilt or anxiety that the lie may be discovered through suppression or reappraisal [@fustos2013embodiment; @megias2019emotionally].
+There is limited research examining whether individuals with high interoceptive accuracy may be more confident in managing physiological tells associated with emotions like guilt or anxiety that the lie may be discovered through suppression or reappraisal [@fustos2013embodiment, @megias2019emotionally].
 
@@
 
--   more theory of mind
-
-# Methods
-
-## Study Design
+We hypothesize that participantswith greater theory of mind ability will show higher lie confidence, shorter reaction time, and lower physiological arousal in the interrogation condition, while participants in the polygraph condition will demonstrate lower lie confidence, lower reaction time and higher physiological arousal during the polygraph prediction.
+(??)
 
@@
 
-Heartbeat Tracking Task (HTT)
+Heartbeat Tracking Task (HTT) - tap one
 
@@
 
-LIE Scale ????
+LIE Scale ???? - doms scale structure of deception
 
@@
 Following the trial, participants gave a confidence rating for how successful they believe their lie or truth was.
-
-We hypothesize that participants with greater theory of mind ability will show higher lie confidence, shorter reaction time, and lower physiological arousal in the interrogation condition, while participants in the polygraph condition will demonstrate lower lie confidence, lower reaction time and higher physiological arousal during the polygraph prediction.
-(??)
 
@@
 
+@durlik2014enhanced interoceptive awareness positively correlated with negative affect, anxiety, etc before public speaking etc (fear of negative eval + mood) heart beat detection more accurate during anxiety
+
 A higher BES score correlated with a higher heart rate for both lies and truths in both conditions, with a larger effect in the interrogation condition.

### 2022-08-31 paper/manuscript_v0.Rmd

@@
 At the same time their true heart rate is recorded and the scores are compared to determine the individual's accuracy.
-They also completed the *MAIA questionnaire* [@mehling2012multidimensional], where they rated statements such as "I can use my breath to reduce tension" on a Likert scale.
+They also completed the *MAIA questionnaire* [@mehling2012multidimensional], where they rated 32 statements such as "I can use my breath to reduce tension" on a 1-5 Likert scale.
 
-Heartbeat Tracking Task (HTT) - tap one
+Additionally, we implemented the Heartbeat Tracking Task (HTT), in which participants  - tap one
 
@@
 
-LIE Scale ???? - doms scale structure of deception
+We used the *LIE Scale*, which is a 44-item questionnaire examining deception as a dispositional trait, and measures the participant propensity towards lie frequency, ability, contextuality and negativity [@makowski2021structure].
+(!CHECK!)
 

### 2022-08-31 paper/manuscript_v0.Rmd
update manuscript

@@
 # Introduction
+
+Much of the current research investigating the process and mechanisms involved in lying has considered capabilities such as Theory of Mind, the ability to understand and make inferences about other people's mental states and predict their behaviours [@el2017deception; @lee2021lying].
+This ability is highly relevant in the context of deception, as the liar in question may utilize their inferences about the mental states of the other to predict whether the individual accepted as true the invalid information that they have presented to them [@stewart2019deception].
+However, there is a growing link between other cognitive and physiological mechanisms that may play a role in both deception detection, and fabricating successful lies
+
+Interoceptive awareness (IA) is the ability to monitor, interpret, integrate and regulate the sensations and state of one's internal organs, and is closely tied to emotional and cognitive processes [@garfinkel2015knowing, \@wen].
+Greater is IA associated with greater self-regulation [Weiss et al,], especially mindfulness practitioners who tend to have greater interoceptive awareness and greater ability to regulate stress and associated physiological indicators [@ardi2021effects; @mcmahon2021mindful].
+
+Some research has examined how higher interoceptive accuracy, measured through heart beat detection, has been associated with vasoconstriction when faced with a liar, indicating that IA may aid in discriminating high stakes emotional lies and truths [@gunderson2021body].
+It is clear that interoception may indicate on an implicit level that one is being lied to, however, there is limited research investigating how interoception may work the other way around, in favour of a liar in regulating their own physiological state that may betray their deception.
+The findings by @vabba2022interoceptive indicate that high cardiac interoceptive participants were more likely to be dishonest and to tell higher egoistic lies.
+Meanwhile, @megias2019emotionally used EEG and heart rate to find that interoceptive awareness facilitated regulation of arousal during cognitive reappraisal.
+There is limited research examining whether individuals with high interoceptive accuracy may be more confident in managing physiological tells associated with emotions like guilt or anxiety that the lie may be discovered through suppression or reappraisal [@fustos2013embodiment; @megias2019emotionally].
+
+Since fluctuations in key physiological indicators as a means to determine whether the individual is lying is a key principle behind the polygraph test and other lie detection techniques, this paucity strengthens the need for more research examining the relationship between interoception and deception, and theory of mind, and the role it plays in moral behavior and deception.
+However, while there is a clear link established between interoception and deception playing a role in lie detection, limited research has been conducted examining this phenomena on its head.
+The act of lying is often accompanied by physiological responses such as increased heart rate, increased respiration and sweating.
+This research attempts to isolate the effects of theory of mind and interoception, and examine how they interact with deception.
+Of particular interest is how liars might utilize their interoceptive ability to self regulate in towards a more successful deception, and how this ability may compare or interact with other mechanisms at play such as theory of mind.
+We hypothesize that participants with greater theory of mind ability will show higher lie confidence, shorter reaction time, and lower physiological arousal in the interrogation condition, while participants in the polygraph condition will demonstrate lower lie confidence, lower reaction time and higher physiological arousal during the polygraph prediction.
+(??)
 

### 2022-08-31 paper/manuscript_v0.Rmd
update

@@
 
-Interoceptive awareness (IA) is the ability to monitor, interpret, integrate and regulate the sensations and state of one's internal organs, and is closely tied to emotional and cognitive processes [@garfinkel2015knowing, \@wen].
-Greater is IA associated with greater self-regulation [Weiss et al,], especially mindfulness practitioners who tend to have greater interoceptive awareness and greater ability to regulate stress and associated physiological indicators [@ardi2021effects; @mcmahon2021mindful].
+Interoceptive awareness (IA) is the ability to monitor, interpret, integrate and regulate the sensations and state of one's internal organs, and is closely tied to emotional and cognitive processes [@garfinkel2015knowing, @chen2021emerging].
+Greater is IA associated with greater self-regulation [@weiss2014interaction], especially mindfulness practitioners who tend to have greater interoceptive awareness and greater ability to regulate stress and associated physiological indicators [@ardi2021effects; @mcmahon2021mindful].
 
@@
 
-Since fluctuations in key physiological indicators as a means to determine whether the individual is lying is a key principle behind the polygraph test and other lie detection techniques, this paucity strengthens the need for more research examining the relationship between interoception and deception, and theory of mind, and the role it plays in moral behavior and deception.
-However, while there is a clear link established between interoception and deception playing a role in lie detection, limited research has been conducted examining this phenomena on its head.
 The act of lying is often accompanied by physiological responses such as increased heart rate, increased respiration and sweating.
+Since fluctuations in key physiological indicators as a means to determine whether the individual is lying is a key principle behind the polygraph test and other lie detection techniques, there is a need for more research examining the relationship between IA, theory of mind, and deception.
 This research attempts to isolate the effects of theory of mind and interoception, and examine how they interact with deception.
@@
 The plan for this study was preregistered (OSF???????). The raw data and analysis script can be found at (GITHUB?????).
-
-##
-
-Much of the current research investigating the process and mechanisms involved in lying has considered capabilities such as Theory of Mind, the ability to understand and make inferences about other people's mental states and predict their behaviours [@el2017deception; @lee2021lying].
-This ability is highly relevant in the context of deception, as the liar in question may utilize their inferences about the mental states of the other to predict whether the individual accepted as true the invalid information that they have presented to them [@stewart2019deception].
-However, there is a growing link between other cognitive and physiological mechanisms that may play a role in both deception detection, and fabricating successful lies
-
-Interoceptive awareness (IA) is the ability to monitor, interpret, integrate and regulate the sensations and state of one's internal organs, and is closely tied to emotional and cognitive processes [@garfinkel2015knowing, @chen2021emerging].
-Greater IA is associated with greater self-regulation [@weiss2014interaction], especially in mindfulness practitioners who tend to have greater interoceptive awareness and greater ability to regulate stress and associated physiological indicators [@ardi2021effects; @mcmahon2021mindful].
-
-Some research has examined how higher interoceptive accuracy, measured through heart beat detection, has been associated with vasoconstriction when faced with a liar, indicating that IA may aid in discriminating high stakes emotional lies and truths [@gunderson2021body].
-It is clear that interoception may indicate on an implicit level that one is being lied to, however, there is limited research investigating how interoception may work the other way around, in favour of a liar in regulating their own physiological state that may betray their deception.
-The findings by @vabba2022interoceptive indicate that high cardiac interoceptive participants were more likely to be dishonest and to tell higher egoistic lies.
-Meanwhile, @megias2019emotionally used EEG and heart rate to find that interoceptive awareness facilitated regulation of arousal during cognitive reappraisal.
-There is limited research examining whether individuals with high interoceptive accuracy may be more confident in managing physiological tells associated with emotions like guilt or anxiety that the lie may be discovered through suppression or reappraisal [@fustos2013embodiment, @megias2019emotionally].
-
-Since fluctuations in key physiological indicators as a means to determine whether the individual is lying is a key principle behind the polygraph test and other lie detection techniques, this paucity strengthens the need for more research examining the relationship between interoception and deception, and theory of mind, and the role it plays in moral behavior and deception.
-However, while there is a clear link established between interoception and deception playing a role in lie detection, limited research has been conducted examining this phenomena on its head.
-The act of lying is often accompanied by physiological responses such as increased heart rate, increased respiration and sweating.
-This research attempts to isolate the effects of theory of mind and interoception, and examine how they interact with deception.
-Of particular interest is how liars might utilize their interoceptive ability to self regulate in towards a more successful deception, and how this ability may compare or interact with other mechanisms at play such as theory of mind.
-
-We hypothesize that participantswith greater theory of mind ability will show higher lie confidence, shorter reaction time, and lower physiological arousal in the interrogation condition, while participants in the polygraph condition will demonstrate lower lie confidence, lower reaction time and higher physiological arousal during the polygraph prediction.
-(??)
 

### 2022-09-19 paper/manuscript_v0.Rmd
update refs
manuscript update/polish

@@
 
-Much of the current research investigating the process and mechanisms involved in lying has considered capabilities such as Theory of Mind, the ability to understand and make inferences about other people's mental states and predict their behaviours [@el2017deception; @lee2021lying].
-This ability is highly relevant in the context of deception, as the liar in question may utilize their inferences about the mental states of the other to predict whether the individual accepted as true the invalid information that they have presented to them [@stewart2019deception].
+<!-- Little intro-->
+
+The fabrication and delivery of false information is a sophisticated, and cognitively taxing activity [@abe2007deceiving; @leal2008time ], resulting in physiological arousal [@eskritt2021did] which may require effortful self-regulation to conceal[@krokoszinski2016emotion].
+
+<!-- ToM-->
+
+Much of the current research investigating the process and mechanisms involved in lying has considered capabilities such as Theory of Mind (ToM), the ability to understand and make inferences about other people's mental states and predict their behaviours [@el2017deception; @lee2021lying].
+ToM is a critical component of deception, since the liar in question must be able to use their inferences to predict whether the individual accepted as true the false information presented to them [@stewart2019deception].
+Children begin using deception during the same period of development in which executive function and ToM develops [@sai2021theory], and children trained in ToM saw an increase in lying behaviour [@ding2015theory].
 However, there is a growing link between other cognitive and physiological mechanisms that may play a role in both deception detection, and fabricating successful lies
 
-Interoceptive awareness (IA) is the ability to monitor, interpret, integrate and regulate the sensations and state of one's internal organs, and is closely tied to emotional and cognitive processes [@garfinkel2015knowing, @chen2021emerging].
+<!-- Intero in deception research-->
+
+Interoceptive awareness (IA) is the ability to monitor, interpret, integrate, and regulate the sensations and state of one's internal organs, and is closely tied to emotional and cognitive processes [@chen2021emerging; @garfinkel2015knowing].
 Greater is IA associated with greater self-regulation [@weiss2014interaction], especially mindfulness practitioners who tend to have greater interoceptive awareness and greater ability to regulate stress and associated physiological indicators [@ardi2021effects; @mcmahon2021mindful].
 
+The growing literature examining the relationship between interoception and deception is rapidly growing area of inquiry.
 Some research has examined how higher interoceptive accuracy, measured through heart beat detection, has been associated with vasoconstriction when faced with a liar, indicating that IA may aid in discriminating high stakes emotional lies and truths [@gunderson2021body].
-It is clear that interoception may indicate on an implicit level that one is being lied to, however, there is limited research investigating how interoception may work the other way around, in favour of a liar in regulating their own physiological state that may betray their deception.
-The findings by @vabba2022interoceptive indicate that high cardiac interoceptive participants were more likely to be dishonest and to tell higher egoistic lies.
-Meanwhile, @megias2019emotionally used EEG and heart rate to find that interoceptive awareness facilitated regulation of arousal during cognitive reappraisal.
+It is clear that interoception may indicate on an implicit level that one is being lied to [@ten2019different; @van2014registered], however, there is limited research investigating how interoception may work the other way around, in favour of a liar in regulating their own physiological state that may betray their deception.
+
+Attending to interoceptive cues has been associated with greater willingness to engage in cheating [@williams2016valjean], risk-taking behaviours [@ditto2006visceral; @lenggenhager2013listening].
+The findings by @vabba2022interoceptive indicate that high cardiac interoceptive participants were more likely to be dishonest, and to tell higher egoistic lies.
 There is limited research examining whether individuals with high interoceptive accuracy may be more confident in managing physiological tells associated with emotions like guilt or anxiety that the lie may be discovered through suppression or reappraisal [@fustos2013embodiment; @megias2019emotionally].
+
+<!-- Hypothesis -->
 
@@
 We hypothesize that participants with greater theory of mind ability will show higher lie confidence, shorter reaction time, and lower physiological arousal in the interrogation condition, while participants in the polygraph condition will demonstrate lower lie confidence, lower reaction time and higher physiological arousal during the polygraph prediction.
-(??)
 
@@
 
-The plan for this study was preregistered (OSF???????). The raw data and analysis script can be found at (GITHUB?????).
+The plan for this study was preregistered (OSF?). The raw data and analysis script can be found at (GITHUB?).
 
@@
 We used the *LIE Scale*, which is a 44-item questionnaire examining deception as a dispositional trait, and measures the participant propensity towards lie frequency, ability, contextuality and negativity [@makowski2021structure].
-(!CHECK!)
 
@@
 
-The demographic information we collected was age, ethnicity, nationality, dominant hand (for application of EDA electrodes, education level (determined by highest qualification received, or in the midst of achieving), religion and duration lived in Singapore.
+The demographic information we collected was age, ethnicity, nationality, dominant hand (for application of EDA electrodes), education level (determined by highest qualification received, or in the midst of achieving), religion and duration lived in Singapore.
 
@@
 
-We adopted a linear mixed-effect model where
+The data analysis was carried out using R.... [CITE STUFF]. The full reproducible analysis script is available [INSERT LINK].
+
+We implimented a linear mixed-effect model where
 
@@
 To further build on the model, trials for lies and truths were separated using an embedded model and the interaction between the dependent variable and condition was probed.
-This reveals instances where the effect is greater in one condition, for example in this case, (mouseover) a higher total yoni score is correlated with decreased lie confidence, but only in the polygraph condition.
-
-INSERT VERY FANCY STATISTICS
+This reveals instances where the effect is greater in one condition, for example a higher total Yoni Task score is correlated with decreased lie confidence, but only in the polygraph condition.
 
 ### Data Pre-Processing and Analyses
-
-??????????????????
 
@@
 
-This study aimed to examine the relationship between theory of mind and interoception on lie confidence, reaction time and physiological arousal during deception.
-While there is an extensive literature examining the role of theory of mind abilities in deception, this research contributes new insights into how interoceptive abilities....
+This study aimed to examine the relationship between Theory of Mind and interoception on lie confidence, reaction time and physiological arousal during deception.
+This was achieved through a directed lying task in which participants were randomized between two two conditions of false feedback where they were intended to rely on either interoceptive or ToM abilities.
+Across both conditions, the scores show a larger effect on confidence in the polygraph condition, which was both expected and unexpected.
+This may be due to the polygraph condition may be harder due to the less intuitive feedback cues.
+Those better at interoception or perceiving their internal signals would hence be more confident in their lies, as we expected.
+On the other hand, those with better theory of mind become less confident in the absence of another person from which to obtain feedback cues.
 
-It is interesting to note that the theory of mind measures are correlated with trials in the polygraph condition, when we expected it to be correlated with the interrogation condition instead.
-Higher HCT accuracy and MAIA scores are positively correlated with lie confidence in the polygraph condition, as expected.
-There was no significant effect for reaction time.
-BES is positively correlated with heart rate, even though we expected that better theory of mind ability would lead to lower physiological arousal.
-On the other hand, HCT accuracy is negatively correlated with heart rate, but only in the interrogation condition, even though we expected this for the polygraph condition.
-I will be going through these results in more detail, starting with confidence.
+There was no significant relationship between reaction time and heart rate, however lie confidence is negatively correlated with reaction time, which is expected.
+Generally, participants were less confident in lies than truth, however is effect was greater in the polygraph condition, which is possibly due to less intuitive feedback cues.
+This effect carries over into reaction time, where participants were also slower to respond in the polygraph condition, which is consistent with less intuitive cues.
 
-### Interoception
+To our knowledge, this is the first study that has found a significant correlation between interoceptive awareness and lie confidence.
+Both interoceptive measures, HCT and MAIA, were strongly correlated.
+Participants with greater IA, also had greater lie confidence and lower truth confidence in the polygraph condition.
+The three sub-scales of MAIA which had a significant interaction were *Noticing, Body Listening* and *Attention Regulation*.
+Since participants were made aware of their cardiac activation through false feedback, we anticipated that those with greater accuracy would demonstrate greater lie confidence.
+Since research has shown deception is more likely when individuals judge a lower risk of confrontation or being caught [@sip2012if; @sip2013pinocchio], these results may offer support to the literature that implicates IA with immoral behaviour.
+Thus our research may be in support of the findings from @vabba2022interoceptive, where IA was found to be a significant moderator in participant's propensity toward deception and high egoist lies.
+Similar findings have also linked increased bodily awareness was linked to a greater likelihood of engaging in immoral behavior such as cheating [@williams2016valjean], and risk-taking behaviours [@ditto2006visceral; @lenggenhager2013listening].
+However, more research is required to examine this potential link.
 
-less confident in lies than truths (expected) Condition interaction, greater effect in polygraph (relying on interoception) likely less intuitive feedback cues??
-Slower in polygraph makes sense if less intuitive
+A greater HCT score was associated with decreased lie confidence in the polygraph condition.
+Since HCT awareness is understood to be the correlation between HCT accuracy and HCT confidence, there are two potential explanations for this.
+First, a low level of awareness could mean that the participant accurately counted their heartbeats, but were not confidence; or vice versa, where they were inaccurate counting but expressed high confidence.
+The dual interpretations of this data may indicate its lack of reliability.
+More research is needed to understand the relationship between lie confidence, interoception and potential implications on lying behaviour.
 
-We found that greater interoceptive abilities were associated with greater lie confidence, and lower truth confidence, with a larger effect in the polygraph condition which was intended to test interoceptive abilities.
-Out of the 8 domains tested in MAIA, the interaction is significant for *noticing, body listening* and *attention regulation*.
-MAIA, HCT accuracy and confidence show the same effect.
+HCT accuracy is negatively correlated with heart rate, but only in the interrogation condition.
+While it is expected that those with greater interoceptive ability would be better at perceiving and regulating physiological arousal [@megias2019emotionally], we expected to see this result in the polygraph condition which emphasizes interoceptive abilities.
+A potential explanation for this is that the presence of another person, whom they believe is observing them is understood to increase an individual's interoceptive accuracy [@hazem2017know; @isomura2020direct], which may in turn, cause the participant to attempt to regulate their cardiac response.
 
-However, the effect of HCT awareness is more similar to that of theory of mind, where a higher score is associated with decreased lie confidence only in the polygraph condition.
-HCT awareness is the correlation between HCT accuracy and confidence.
-A low level of awareness could mean they accurately counted their heartbeats but were not confident, or vice versa where they were inaccurate at counting their heartbeats but were confident.
-Since awareness could mean two very different things, this data may not be very reliable.
+Greater ToM abilities negatively correlated with lie confidence, and saw an increase in truth confidence, but only in the polygraph condition.
+In the Yoni Task, this effect is driven by the cognitive and physical domains.
+BES saw the effect driven by both the cognitive and affective domain for lie confidence, meanwhile, truth confidence is only driven by the affective domain.
 
-Generally, we found a negative correlation between measures of interoception and the Yoni Task, except for HCT awareness. (not significant)
-
-This is consistent with measures of interoception having an opposite effect to that of theory of mind except HCT awareness.
-The generally positive correlation of interoception with BES cognitive is opposite from the rest, but this agrees with the earlier results where the effect of BES cognitive is weaker.
-
-There is a strong correlation between MAIA and HCT confidence which is consistent with MAIA and HCT confidence showing the same effect.
-However, this also means that MAIA was only able to measure the confidence aspect of interoception.
-
-scores show a larger effect on confidence in the polygraph condition.
-
--   could be polygraph condition more difficult less intuitive feedback cues
-
--   better at interoception would be more confident in their lies, as we expected.
-
--   On the other hand, those with better theory of mind become less confident in the absence of another person from which to obtain feedback cues.
-
--   interrogation condition, may be a plateau effect where individual differences have a lesser effect
-
-### Theory of Mind
-
-TOM correlated with trials in polygraph (interoception), not expected(!) because expected it to correlate with Interrogation
-
-The greater Theory of Mind abilities, the lower participants lie confidence, and the higher their truth confidence in the polygraph (interoceptive) condition.
-The effect in the Yoni Task is driven by the cognitive and physical domains.
-For BES, the effect is only driven by the affective domain,
-
-This can also be seen in the correlation matrix where yoni is generally positively correlated with BES, even though none of the correlations are significant.
-The domains of the yoni task are also less correlated with the cognitive domain of BES, which is consistent with the smaller effect of BES cognitive in the previous slide.
-
-### Heart Rate
-
-For interoception, HCT accuracy is negatively correlated with heart rate, only in the interrogation condition.
-While it is expected that those with greater interoceptive ability would be better at percieving and regulating physiological arousal, we expected to see this result in the polygraph condition which emphasizes interoceptive abilities.
-
--   relationship of BES scores with heart rate is also more prominent in the interrogation condition - in general scores show larger effect on heart rate in interrogation? emotional intelligence etc
--   (confidence and HR) high in truths is associated with higher heart rate.
-Expected.
-Also slightly higher in interrogation than polygraph, since presence of another person can cause heightened physiological arousal @hazem2017know.
-Direct gaze increase bodily self awareness and physiological arousal
-
-@durlik2014enhanced interoceptive awareness positively correlated with negative affect, anxiety, etc before public speaking etc (fear of negative eval + mood) heart beat detection more accurate during anxiety
-
-A higher BES score correlated with a higher heart rate for both lies and truths in both conditions, with a larger effect in the interrogation condition.
-
-The effect in the polygraph condition is driven only by the cognitive domain of BES, while that in the interrogation condition is driven by both domains.
-
-\- more empathetic person will experience more physiological arousal (especially) when telling a lie.
-
-It is consistent with our hypothesis that this effect will be more pronounced in the interrogation condition.
-
-Yoni Task has no association with heart rate, implying that heart rate may be related to empathy only and not theory of mind.
+We anticipated that ToM measures would negatively correlate with physiological arousal, however while the Yoni Task had no association with heart rate, we found that BES scores were positively correlated with heart rate for both lies and truths, with a larger effect in the interrogation condition.
+Although initially unexpected, this finding is makes sense when interpreted in line with past research which finds a close positive correlation between empathy and increased cardiac response [@jauniaux2020emotion; @lischke2018inter].
+The lack of correlation between heart rate and the Yoni task, indicates that the elevated cardiac response may be due exclusively to empathy, and attributable to ToM.
 
@@
 This must be considered as a potential limitation since the participants were still connected to the ECG in the interrogation condition, which may amplify their interoceptive awareness beyond what they may normally experience during a real-world act of deception.
-Furthermore, as aforementioned, it is possible that there could be an interplay between Theory of Mind and interoception.
+Furthermore, it is possible that there could be an interplay between Theory of Mind and interoception.
 More research is needed to investigate this relationship in the context of deception.

### 2022-10-04 1_Measures.Rmd
update

@@
 
+## Outcomes
+
+```{r message=FALSE}
+p1 <- estimate_density(df$Confidence, at=df$Participant, method = "kernSmooth") |> 
+  ggplot(aes(x=x, y=y)) +
+  geom_line(aes(color = Group)) + 
+  scale_x_continuous(labels = scales::percent, expand = c(0, 0)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  labs(x = "Confidence", y = "") +
+  scale_colour_flat_d(guide="none")
+
+p2 <- estimate_density(df$RT, at=df$Participant, method = "kernSmooth") |> 
+  ggplot(aes(x=x, y=y)) +
+  geom_line(aes(color = Group)) +
+  scale_x_continuous(expand = c(0, 0)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  labs(x = "RT (s)", y = "") +
+  scale_colour_viridis_d(guide="none")
+
+p3 <- estimate_density(filter(df, !is.na(HeartRate)), select="HeartRate", at="Participant", method = "kernSmooth") |> 
+  ggplot(aes(x=x, y=y)) +
+  geom_line(aes(color = Participant)) +
+  scale_x_continuous(expand = c(0, 0)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  labs(x = "Heart Rate (bpm)", y = "") +
+  scale_colour_pizza_d(guide="none")
+
+p1 / p2 / p3 + plot_annotation(title = "Distribution of each participant")
+```
 ## Theory of Mind / Empathy
@@
   guides(fill="none", color="none")
-
-df$Confidence[df$Participant %in% c("S9", "S29")] <- NA # Extreme responses
-df$HeartRate[df$Participant == "S30"] <- NA # Extreme values
-df$RT[df$Participant == "S13"] <- NA # Slower than the others
-df$RT[df$RT > 8.25] <- NA # Extreme RT values 
 ```
 
-Percentage of Confidence data removed: `r sum(is.na(df$Confidence)) / nrow(df) * 100` %  
-Percentage of RT data removed: `r sum(is.na(df$RT)) / nrow(df) * 100` %  
-Percentage of Heart Rate data removed: `r sum(is.na(df$HeartRate)) / nrow(df) * 100` %
-
 ##### Observations
-
-```{r warning=FALSE}
-df <- df |> 
-  # Remove outlier trials
-  group_by(Participant) |> 
-  mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore", threshold = qnorm(0.9999))),
-         Outliers_Physio = as.logical(performance::check_outliers(HeartRate, method = "zscore", threshold = qnorm(0.9999)))) |> 
-  ungroup()
-```
 
@@
 ```
+
+## Inter-Measures Correlation {.tabset}
+
+```{r message=FALSE, warning=FALSE}
+dfsub <- df |> 
+  select(Participant, 
+         starts_with("YONI_"), 
+         starts_with("BES_"),
+         starts_with("HCT_"),
+         starts_with("HTT_"),
+         starts_with("MAIA_"),
+         starts_with("LIE_")) |> 
+  group_by(Participant) |> 
+  summarise_all(mean)
+```
+
+### Theory of Mind / Empathy
+
+```{r message=FALSE, warning=FALSE}
+r <- correlation(select(dfsub, starts_with("YONI_")),
+                 select(dfsub, starts_with("BES_")), 
+                 p_adjust = "none")
+
+summary(r) |> 
+  plot() 
+```
+
+### Interoception
+
+```{r message=FALSE, warning=FALSE}
+# Leave out HTT
+# r <- correlation(select(dfsub, starts_with("HTT_")),
+#                  select(dfsub, starts_with("HCT_")), 
+#                  p_adjust = "none")
+# 
+# summary(r) |> 
+#   plot()
+```
+
+```{r message=FALSE, warning=FALSE}
+r <- correlation(select(dfsub, starts_with("MAIA_")),
+                 select(dfsub, starts_with("HCT_")), 
+                        #starts_with("HTT_")), 
+                 p_adjust = "none")
+
+summary(r) |> 
+  plot()
+```
+
+### ToM and Interoception
+
+```{r message=FALSE, warning=FALSE}
+r <- correlation(select(dfsub, starts_with(c("MAIA_", "HCT_"))),
+                 select(dfsub, starts_with(c("YONI_", "BES_"))), 
+                 p_adjust = "none")
+
+summary(r) |> 
+  plot() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
+```
+
+### Deception Task and LIE Scale
+
+```{r message=FALSE, warning=FALSE}
+r <- df |> 
+  select(Participant, Answer, Confidence, RT, HeartRate) |> 
+  group_by(Participant, Answer) |> 
+  summarise_all(mean, na.rm=TRUE) |> 
+  tidyr::pivot_wider(names_from = "Answer", values_from = c("Confidence", "RT", "HeartRate")) |> 
+  ungroup() |> 
+  select(-Participant) |> 
+  correlation(select(dfsub, starts_with("LIE_")), p_adjust = "none")
+
+summary(r) |> 
+  plot()
+```
+
+### Confidence and RT
+
+- When lying, the faster they answer, the more confident they are.
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ RT * Answer + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family())
+
+parameters::parameters(model, effects = "fixed")
+```
+
+```{r message=FALSE, warning=FALSE}
+modelbased::estimate_slopes(model, trend = "RT", at = "Answer")
+```
+
+```{r message=FALSE, warning=FALSE}
+estimate_relation(model, at = c("RT", "Answer")) |> 
+  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
+```
+
+### Confidence and Heart Rate
+
+- More confidence in truths is associated with higher heart rate.
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(Confidence ~ HeartRate * Answer + (1|Participant) + (1|Item), 
+                 data = df, family = beta_family()) # warning can be ignored
+
+parameters::parameters(model, effects = "fixed")
+```
+
+```{r message=FALSE, warning=FALSE}
+modelbased::estimate_slopes(model, trend = "HeartRate", at = "Answer")
+```
+
+```{r message=FALSE, warning=FALSE}
+estimate_relation(model, at = c("HeartRate", "Answer")) |> 
+  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
+```
+
+### RT and Heart Rate
+
+- No relationship.
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB(RT ~ HeartRate * Answer + (1|Participant) + (1|Item), 
+                 data = df)
+
+parameters::parameters(model, effects = "fixed")
+```
+
+```{r message=FALSE, warning=FALSE}
+estimate_relation(model, at = c("HeartRate", "Answer")) |> 
+  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
+```

### 2022-10-04 2_ManipulationChecks.Rmd
added interpretations
update

@@
 ---
-
-## Inter-Measures Correlation {.tabset}
-
-```{r message=FALSE, warning=FALSE}
-dfsub <- df |> 
-  select(Participant, 
-         starts_with("YONI_"), 
-         starts_with("BES_"),
-         starts_with("HCT_"),
-         starts_with("HTT_"),
-         starts_with("MAIA_"),
-         starts_with("LIE_")) |> 
-  group_by(Participant) |> 
-  summarise_all(mean)
-```
-
-### Theory of Mind / Empathy
-
-```{r message=FALSE, warning=FALSE}
-r <- correlation(select(dfsub, starts_with("YONI_")),
-                 select(dfsub, starts_with("BES_")), 
-                 p_adjust = "none")
-
-summary(r) |> 
-  plot() 
-```
-
-### Interoception
-
-```{r message=FALSE, warning=FALSE}
-# Leave out HTT
-# r <- correlation(select(dfsub, starts_with("HTT_")),
-#                  select(dfsub, starts_with("HCT_")), 
-#                  p_adjust = "none")
-# 
-# summary(r) |> 
-#   plot()
-```
-
-```{r message=FALSE, warning=FALSE}
-r <- correlation(select(dfsub, starts_with("MAIA_")),
-                 select(dfsub, starts_with("HCT_")), 
-                        #starts_with("HTT_")), 
-                 p_adjust = "none")
-
-summary(r) |> 
-  plot()
-```
-
-### ToM and Interoception
-
-```{r message=FALSE, warning=FALSE}
-r <- correlation(select(dfsub, starts_with(c("MAIA_", "HCT_"))),
-                 select(dfsub, starts_with(c("YONI_", "BES_"))), 
-                 p_adjust = "none")
-
-summary(r) |> 
-  plot() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-```
-
-### Deception Task and LIE Scale
-
-```{r message=FALSE, warning=FALSE}
-r <- df |> 
-  select(Participant, Answer, Confidence, RT, HeartRate) |> 
-  group_by(Participant, Answer) |> 
-  summarise_all(mean, na.rm=TRUE) |> 
-  tidyr::pivot_wider(names_from = "Answer", values_from = c("Confidence", "RT", "HeartRate")) |> 
-  ungroup() |> 
-  select(-Participant) |> 
-  correlation(select(dfsub, starts_with("LIE_")), p_adjust = "none")
-
-summary(r) |> 
-  plot()
-```
-
-### Confidence and RT
-
-- When lying, the faster they answer, the more confident they are.
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ RT * Answer + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-parameters::parameters(model, effects = "fixed")
-```
-
-```{r message=FALSE, warning=FALSE}
-modelbased::estimate_slopes(model, trend = "RT", at = "Answer")
-```
-
-```{r message=FALSE, warning=FALSE}
-estimate_relation(model, at = c("RT", "Answer")) |> 
-  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
-```
-
-### Confidence and Heart Rate
-
-- More confidence in truths is associated with higher heart rate.
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ HeartRate * Answer + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family()) # warning can be ignored
-
-parameters::parameters(model, effects = "fixed")
-```
-
-```{r message=FALSE, warning=FALSE}
-modelbased::estimate_slopes(model, trend = "HeartRate", at = "Answer")
-```
-
-```{r message=FALSE, warning=FALSE}
-estimate_relation(model, at = c("HeartRate", "Answer")) |> 
-  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
-```
-
-### RT and Heart Rate
-
-- No relationship.
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ HeartRate * Answer + (1|Participant) + (1|Item), 
-                 data = df)
-
-parameters::parameters(model, effects = "fixed")
-```
-
-```{r message=FALSE, warning=FALSE}
-estimate_relation(model, at = c("HeartRate", "Answer")) |> 
-  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
-```
-
-## Effect of Phrasing {.tabset}
-
-- Main effect of phrasing on RT only. Indirect questions lead to slower answers.
-
-### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer * Phrasing + (1|Participant) + (1|Item), 
-                 data = df)
-
-parameters::parameters(model, effects = "fixed")
-```
-
-```{r message=FALSE, warning=FALSE}
-estimate_means(model, at = c("Answer", "Phrasing")) |> 
-  plot(show_data = "none") 
-```
-
-### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer * Phrasing + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-parameters::parameters(model, effects = "fixed")
-```
-
-```{r message=FALSE, warning=FALSE}
-estimate_means(model, at = c("Answer", "Phrasing")) |> 
-  plot(show_data = "none") 
-```
-
-### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer * Phrasing + (1|Participant) + (1|Item), 
-                 data = df)
-
-parameters::parameters(model, effects = "fixed")
-```
-
-```{r message=FALSE, warning=FALSE}
-estimate_means(model, at = c("Answer", "Phrasing")) |> 
-  plot(show_data = "none") 
-```
 
@@
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer * Condition + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
+# Prior: plot(seq(-5, 5, length.out=100), dstudent_t(seq(-5, 5, length.out=100), 1, 0, 1), "l")
 
-parameters::parameters(model, effects = "fixed")
+model <- brms::brm(Confidence ~ Answer * Condition + (1|Participant) + (1|Item), 
+                   data = df, family = "beta", seed=3, refresh=0,
+                   prior = set_prior("student_t(1, 0, 1)", class = "b"))
+
+show_parameters(model)
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer * Condition + (1|Participant) + (1|Item), 
-                 data = df)
+# Prior: plot(seq(-10, 10, length.out=100), dstudent_t(seq(-10, 10, length.out=100), 1, 0, 3), "l")
 
-parameters::parameters(model, effects = "fixed")
+model <- brms::brm(RT ~ Answer * Condition + (1|Participant) + (1|Item),
+                   data = df, seed=3, refresh=0,
+                   prior = set_prior("student_t(1, 0, 3)", class = "b"))
+
+show_parameters(model)
 ```
@@
 
-- Higher heart rate in lies vs. truths, and higher heart rate in interrogation condition vs. polygraph.
+- Higher heart rate in lies vs. truths.
+- Higher heart rate in interrogation condition vs. polygraph: presence of another person causes heightened physiological arousals.
 - No interaction.
@@
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer * Condition + (1|Participant) + (1|Item), 
-                 data = df)
+# Prior: plot(seq(-30, 30, length.out=100), dstudent_t(seq(-30,30, length.out=100), 1, 0, 8), "l")
+model <- brms::brm(HeartRate ~ Answer * Condition + (1|Participant) + (1|Item),
+                   data = df, seed=3, refresh=0,
+                   prior = set_prior("student_t(1, 0, 8)", class = "b"))
 
-parameters::parameters(model, effects = "fixed")
+show_parameters(model)
 ```
@@
 ```
+
+## Effect of Phrasing {.tabset}
+
+- Main effect of phrasing on RT only. Indirect questions lead to slower answers.
+
+### Confidence
+
+```{r message=FALSE, warning=FALSE}
+# Prior: plot(seq(-2, 2, length.out=100), dstudent_t(seq(-2, 2, length.out=100), 1, 0, 1), "l")
+
+model <- brms::brm(Confidence ~ Answer * Phrasing + (1|Participant) + (1|Item), 
+                   data = df, family = "beta", seed=3, refresh=0,
+                   prior = set_prior("student_t(1, 0, 1)", class = "b"))
+
+show_parameters(model)
+```
+
+```{r message=FALSE, warning=FALSE}
+estimate_means(model, at = c("Answer", "Phrasing")) |> 
+  plot(show_data = "none") 
+```
+
+### RT
+
+```{r message=FALSE, warning=FALSE}
+# Prior: plot(seq(-10, 10, length.out=100), dstudent_t(seq(-10, 10, length.out=100), 1, 0, 3), "l")
+
+model <- brms::brm(RT ~ Answer * Phrasing + (1|Participant) + (1|Item),
+                   data = df, seed=3, refresh=0,
+                   prior = set_prior("student_t(1, 0, 3)", class = "b"))
+
+show_parameters(model)
+```
+
+```{r message=FALSE, warning=FALSE}
+estimate_means(model, at = c("Answer", "Phrasing")) |> 
+  plot(show_data = "none") 
+```
+
+### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+# Prior: plot(seq(-50, 50, length.out=100), dstudent_t(seq(-50, 50, length.out=100), 1, 0, 8), "l")
+model <- brms::brm(HeartRate ~ Answer * Phrasing + (1|Participant) + (1|Item),
+                   data = df, seed=3, refresh=0,
+                   prior = set_prior("student_t(1, 0, 8)", class = "b"))
+
+show_parameters(model)
+```
+
+```{r message=FALSE, warning=FALSE}
+estimate_means(model, at = c("Answer", "Phrasing")) |> 
+  plot(show_data = "none") 
+```

### 2022-10-04 3_ToM.Rmd
update

--- 2021-11-24 3_ToM.Rmd
@@
 
-- When instructed to lie, the decrease in confidence in participants with higher yoni score is less in social than polygraph condition.
+- Confidence: effect in total, cognitive and physical.
+- RT: effect in cognitive only.
+- Heart rate: no effect.
 
-### Total Score
-
-#### Confidence
+### Confidence
 
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Total) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
+results <- data.frame()
+for (var in c("YONI_Total", "YONI_Cognitive", "YONI_Affective", "YONI_Physical")) {
+  model <- glmmTMB(as.formula(paste0("Confidence ~ Answer / (Condition / ", 
+                                     var, 
+                                     ") + (1|Participant) + (1|Item)")), 
+                   data = df, 
+                   family = beta_family())
 
-get_parameters <- function(model) {
-  # Parameters
-  params <- parameters::parameters(model, effects = "fixed") 
-  # Marginal effects
-  at <- c("Answer", "Condition")
-  trend <- insight::find_predictors(model)$conditional
-  trend <- trend[!trend %in% at]
-  marg <- modelbased::estimate_slopes(model, trend = trend, at = at)
-  # Output
-  list(params = params, marginal_effects = marg)
+  results <- parameters::parameters(model, effects = "fixed", keep=var) |> 
+    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |> 
+    separate(Parameter, sep=":", into = c("Answer", "Condition", "Variable")) |> 
+    data_relocate(select="Variable", before=1) |> 
+    rbind(results)
 }
 
-results <- get_parameters(model)
-results$params
-results$marginal_effects
+display(results, stars=TRUE)
 ```
 
+### RT
+
 ```{r message=FALSE, warning=FALSE}
-plot_effect <- function(model, results, var = "YONI_Total", outcome = "Confidence") {
-  data <- df |> 
-    group_by(Participant, Answer, Condition) |> 
-    summarise({{var}} := mean(.data[[var]], na.rm = TRUE),
-              SD = sd(.data[[outcome]], na.rm = TRUE),
-              {{outcome}} := mean(.data[[outcome]], na.rm = TRUE),
-              CI_low = .data[[outcome]] - SD / 2,
-              CI_high = .data[[outcome]] + SD / 2)
+results <- data.frame()
+for (var in c("YONI_Total", "YONI_Cognitive", "YONI_Affective", "YONI_Physical")) {
+  model <- glmmTMB(as.formula(paste0("RT ~ Answer / (Condition / ", 
+                                     var, 
+                                     ") + (1|Participant) + (1|Item)")), 
+                   data = df)
 
-  link_data <- estimate_relation(model, at = c("Condition", var, "Answer"), length = 30)
-  range_x <- diff(range(data[[var]]))
-
-  annot <- results$marginal_effects  
-  annot$Label <- insight::format_p(annot$p, stars_only = TRUE)
-  annot$x <- mean(range(data[[var]]))
-  annot$x <- ifelse(annot$Condition == "Polygraph", 
-                    annot$x - 0.05 * range_x, 
-                    annot$x + 0.05 * range_x)
-  annot$y <- max(data[[outcome]], na.rm=TRUE) - 0.01 * diff(range(data[[outcome]], na.rm=TRUE))
-
-  p <- ggplot(link_data, aes_string(x = var, y = "Predicted")) +
-    geom_pointrange(data = data, 
-                    aes_string(y = outcome, 
-                               color = "Condition", 
-                               ymin = "CI_low", 
-                               ymax = "CI_high"), 
-                    position = position_dodge(width = 0.02 * range_x)) +
-    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.33) + 
-    geom_line(aes(color = Condition)) +
-    geom_text(data=annot, aes(x = x, y = y, label = Label, color = Condition), 
-              size = 8, show.legend = FALSE) +
-    labs(y = ifelse(outcome == "RT", "Reaction Time (s)", ifelse(outcome == "HeartRate", "Heart Rate (bpm)", "Confidence")), 
-         x = paste0(stringr::str_replace(var, "_", " ("), ")")) +
-    scale_color_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) +
-    scale_fill_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) + 
-    facet_wrap(~Answer)
-
-  # Narrow y range
-  if(outcome == "Confidence") {
-    p <- p +
-      coord_cartesian(ylim = c(0, 1)) +
-      scale_y_continuous(expand=expansion(c(0, 0))) 
-  }
-  p
+  results <- parameters::parameters(model, effects = "fixed", keep=var) |> 
+    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |> 
+    separate(Parameter, sep=":", into = c("Answer", "Condition", "Variable")) |> 
+    data_relocate(select="Variable", before=1) |> 
+    rbind(results)
 }
 
-p_conf_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "Confidence")
+display(results, stars=TRUE)
 ```
 
-#### RT
+### Heart Rate
 
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * YONI_Total) + (1|Participant) + (1|Item), 
+results <- data.frame()
+for (var in c("YONI_Total", "YONI_Cognitive", "YONI_Affective", "YONI_Physical")) {
+  model <- glmmTMB(as.formula(paste0("HeartRate ~ Answer / (Condition / ", 
+                                     var, 
+                                     ") + (1|Participant) + (1|Item)")), 
                    data = df)
 
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
+  results <- parameters::parameters(model, effects = "fixed", keep=var) |> 
+    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |> 
+    separate(Parameter, sep=":", into = c("Answer", "Condition", "Variable")) |> 
+    data_relocate(select="Variable", before=1) |> 
+    rbind(results)
+}
 
-```{r message=FALSE, warning=FALSE}
-p_rt_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "RT")
-# p_rt_yoni_total
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Total) + (1|Participant), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "HeartRate")
-# p_hr_yoni_total
-```
-
-### Cognitive Theory of Mind
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Cognitive) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_yoni_cognitive <- plot_effect(model, results, var = "YONI_Cognitive", outcome = "Confidence")
-# p_conf_yoni_cognitive
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * YONI_Cognitive) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_yoni_cognitive <- plot_effect(model, results, var = "YONI_Cognitive", outcome = "RT")
-# p_rt_yoni_cognitive
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Cognitive) + (1|Participant), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_yoni_cognitive <- plot_effect(model, results, var = "YONI_Cognitive", outcome = "HeartRate")
-# p_hr_yoni_cognitive
-```
-
-### Affective Theory of Mind
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Affective) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_yoni_affective <- plot_effect(model, results, var = "YONI_Affective", outcome = "Confidence")
-# p_conf_yoni_affective
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * YONI_Affective) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_yoni_affective <- plot_effect(model, results, var = "YONI_Affective", outcome = "RT")
-# p_rt_yoni_affective
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Affective) + (1|Participant), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_yoni_affective <- plot_effect(model, results, var = "YONI_Affective", outcome = "HeartRate")
-# p_hr_yoni_affective
-```
-
-### Physical Theory of Mind
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Physical) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_yoni_physical <- plot_effect(model, results, var = "YONI_Physical", outcome = "Confidence")
-# p_conf_yoni_physical
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * YONI_Physical) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_yoni_physical <- plot_effect(model, results, var = "YONI_Physical", outcome = "RT")
-# p_rt_yoni_physical
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Physical) + (1|Participant), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_yoni_physical <- plot_effect(model, results, var = "YONI_Physical", outcome = "HeartRate")
-# p_hr_yoni_physical
+display(results, stars=TRUE)
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-get_correlation <- function(var = "YONI_", var2 = "LIE_") {
-  r <- correlation(select(dfsub, starts_with(var2)),
-                 select(dfsub, starts_with(var)), 
-                 p_adjust = "none") |> 
-  mutate(Parameter1 = paste0(str_replace(Parameter1, "_", " ("), ")"),
-         Parameter2 = paste0(str_replace(Parameter2, "_", " ("), ")"))
+dfsub <- df |> 
+  select(Participant, 
+         starts_with("LIE_"), 
+         starts_with("YONI_")) |> 
+  group_by(Participant) |> 
+  summarise_all(mean)
 
-  p <- summary(r) |> 
-    plot() +
-    theme_minimal()
-  list(r = r, plot = p)
-}
-
-r <- get_correlation(var = "YONI_")
-r$plot
-```
-
-### Summary
-
-```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
-p_conf_yoni_total / 
-  p_conf_yoni_cognitive / 
-  p_conf_yoni_affective / 
-  p_conf_yoni_physical +
-  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))
-
-p_rt_yoni_total / 
-  p_rt_yoni_cognitive / 
-  p_rt_yoni_affective / 
-  p_rt_yoni_physical +
-  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))
-
-p_hr_yoni_total / 
-  p_hr_yoni_cognitive / 
-  p_hr_yoni_affective / 
-  p_hr_yoni_physical +
-  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))
+correlation(select(dfsub, starts_with("LIE_")), select(dfsub, starts_with("YONI_")), p_adjust = "none")
 ```
@@
 
-### Total Score
+- Confidence: effect in all.
+- RT: no effect.
+- Heart rate: effect in all.
 
-#### Confidence
+### Confidence
 
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * BES_Total) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
+results <- data.frame()
+for (var in c("BES_Total", "BES_Cognitive", "BES_Affective")) {
+  model <- glmmTMB(as.formula(paste0("Confidence ~ Answer / (Condition / ", 
+                                     var, 
+                                     ") + (1|Participant) + (1|Item)")), 
+                   data = df, 
+                   family = beta_family())
 
-results <- get_parameters(model)
-results$params
-results$marginal_effects
+  results <- parameters::parameters(model, effects = "fixed", keep=var) |> 
+    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |> 
+    separate(Parameter, sep=":", into = c("Answer", "Condition", "Variable")) |> 
+    data_relocate(select="Variable", before=1) |> 
+    rbind(results)
+}
+
+display(results, stars=TRUE)
 ```
 
+### RT
+
 ```{r message=FALSE, warning=FALSE}
-p_conf_bes_total <- plot_effect(model, results, var = "BES_Total", outcome = "Confidence")
-# p_conf_bes_total
+results <- data.frame()
+for (var in c("BES_Total", "BES_Cognitive", "BES_Affective")) {
+  model <- glmmTMB(as.formula(paste0("RT ~ Answer / (Condition / ", 
+                                     var, 
+                                     ") + (1|Participant) + (1|Item)")), 
+                   data = df)
+
+  results <- parameters::parameters(model, effects = "fixed", keep=var) |> 
+    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |> 
+    separate(Parameter, sep=":", into = c("Answer", "Condition", "Variable")) |> 
+    data_relocate(select="Variable", before=1) |> 
+    rbind(results)
+}
+
+display(results, stars=TRUE)
 ```
 
-#### RT
+### Heart Rate
 
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * BES_Total) + (1|Participant) + (1|Item), 
+results <- data.frame()
+for (var in c("BES_Total", "BES_Cognitive", "BES_Affective")) {
+  model <- glmmTMB(as.formula(paste0("HeartRate ~ Answer / (Condition / ", 
+                                     var, 
+                                     ") + (1|Participant) + (1|Item)")), 
                    data = df)
 
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
+  results <- parameters::parameters(model, effects = "fixed", keep=var) |> 
+    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |> 
+    separate(Parameter, sep=":", into = c("Answer", "Condition", "Variable")) |> 
+    data_relocate(select="Variable", before=1) |> 
+    rbind(results)
+}
 
-```{r message=FALSE, warning=FALSE}
-p_rt_bes_total <- plot_effect(model, results, var = "BES_Total", outcome = "RT")
-# p_rt_bes_total
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * BES_Total) + (1|Participant), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_bes_total <- plot_effect(model, results, var = "BES_Total", outcome = "HeartRate")
-# p_hr_bes_total
-```
-
-### Cognitive Empathy
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * BES_Cognitive) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_bes_cognitive <- plot_effect(model, results, var = "BES_Cognitive", outcome = "Confidence")
-# p_conf_bes_cognitive
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * BES_Cognitive) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_bes_cognitive <- plot_effect(model, results, var = "BES_Cognitive", outcome = "RT")
-# p_rt_bes_cognitive
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * BES_Cognitive) + (1|Participant), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_bes_cognitive <- plot_effect(model, results, var = "BES_Cognitive", outcome = "HeartRate")
-# p_hr_bes_cognitive
-```
-
-### Affective Empathy
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * BES_Affective) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_bes_affective <- plot_effect(model, results, var = "BES_Affective", outcome = "Confidence")
-# p_conf_bes_affective
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * BES_Affective) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_bes_affective <- plot_effect(model, results, var = "BES_Affective", outcome = "RT")
-# p_rt_bes_affective
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * BES_Affective) + (1|Participant), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_bes_affective <- plot_effect(model, results, var = "BES_Affective", outcome = "HeartRate")
-# p_hr_bes_affective
+display(results, stars=TRUE)
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-r <- get_correlation(var = "BES_")
-r$plot
+dfsub <- df |> 
+  select(Participant, 
+         starts_with("LIE_"), 
+         starts_with("BES_")) |> 
+  group_by(Participant) |> 
+  summarise_all(mean)
+
+correlation(select(dfsub, starts_with("LIE_")), select(dfsub, starts_with("BES_")), p_adjust = "none")
 ```
-
-### Summary
-
-```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
-p_conf_bes_total / 
-  p_conf_bes_cognitive / 
-  p_conf_bes_affective +
-  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))
-
-p_rt_bes_total / 
-  p_rt_bes_cognitive / 
-  p_rt_bes_affective +
-  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))
-
-p_hr_bes_total / 
-  p_hr_bes_cognitive / 
-  p_hr_bes_affective +
-  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))
-```

### 2022-10-04 4_Intero.Rmd
update

--- 2021-11-24 4_Intero.Rmd
@@
 
-### Interoceptive Accuracy
+- Confidence: effect in all.
+- RT: effect in confidence only.
+- Heart rate: effect in accuracy and awareness.
 
-#### Confidence
+### Confidence
 
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * HCT_Accuracy) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
+results <- data.frame()
+for (var in c("HCT_Accuracy", "HCT_Confidence", "HCT_Awareness")) {
+  model <- glmmTMB(as.formula(paste0(
+    "Confidence ~ Answer / (Condition / ",
+    var,
+    ") + (1|Participant) + (1|Item)"
+  )),
+  data = df,
+  family = beta_family()
+  )
 
-results <- get_parameters(model)
-results$params
-results$marginal_effects
+  results <- parameters::parameters(model, effects = "fixed", keep = var) |>
+    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |>
+    separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+    data_relocate(select = "Variable", before = 1) |>
+    rbind(results)
+}
+
+display(results, stars = TRUE)
 ```
 
+### RT
+
 ```{r message=FALSE, warning=FALSE}
-p_conf_hct_accuracy <- plot_effect(model, results, var = "HCT_Accuracy", outcome = "Confidence")
+results <- data.frame()
+for (var in c("HCT_Accuracy", "HCT_Confidence", "HCT_Awareness")) {
+  model <- glmmTMB(as.formula(paste0(
+    "RT ~ Answer / (Condition / ",
+    var,
+    ") + (1|Participant) + (1|Item)"
+  )),
+  data = df
+  )
+
+  results <- parameters::parameters(model, effects = "fixed", keep = var) |>
+    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |>
+    separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+    data_relocate(select = "Variable", before = 1) |>
+    rbind(results)
+}
+
+display(results, stars = TRUE)
 ```
 
-#### RT
+### Heart Rate
 
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * HCT_Accuracy) + (1|Participant) + (1|Item), 
-                 data = df)
+results <- data.frame()
+for (var in c("HCT_Accuracy", "HCT_Confidence", "HCT_Awareness")) {
+  model <- glmmTMB(as.formula(paste0(
+    "HeartRate ~ Answer / (Condition / ",
+    var,
+    ") + (1|Participant) + (1|Item)"
+  )),
+  data = df
+  )
 
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
+  results <- parameters::parameters(model, effects = "fixed", keep = var) |>
+    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |>
+    separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+    data_relocate(select = "Variable", before = 1) |>
+    rbind(results)
+}
 
-```{r message=FALSE, warning=FALSE}
-p_rt_hct_accuracy <- plot_effect(model, results, var = "HCT_Accuracy", outcome = "RT")
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * HCT_Accuracy) + (1|Participant), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_hct_accuracy <- plot_effect(model, results, var = "HCT_Accuracy", outcome = "HeartRate")
-```
-
-### Interoceptive Confidence
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * HCT_Confidence) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_hct_confidence <- plot_effect(model, results, var = "HCT_Confidence", outcome = "Confidence")
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * HCT_Confidence) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_hct_confidence <- plot_effect(model, results, var = "HCT_Confidence", outcome = "RT")
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * HCT_Confidence) + (1|Participant), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_hct_confidence <- plot_effect(model, results, var = "HCT_Confidence", outcome = "HeartRate")
-```
-
-### Interoceptive Awareness
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * HCT_Awareness) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_hct_awareness <- plot_effect(model, results, var = "HCT_Awareness", outcome = "Confidence")
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * HCT_Awareness) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_hct_awareness <- plot_effect(model, results, var = "HCT_Awareness", outcome = "RT")
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * HCT_Awareness) + (1|Participant), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_hct_awareness <- plot_effect(model, results, var = "HCT_Awareness", outcome = "HeartRate")
+display(results, stars = TRUE)
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-r <- get_correlation(var = "HCT_")
-r$plot
+dfsub <- df |>
+  select(
+    Participant,
+    starts_with("LIE_"),
+    starts_with("HCT_")
+  ) |>
+  group_by(Participant) |>
+  summarise_all(mean)
 
-# plot(correlation::cor_test(dfsub, "HCT_Accuracy", "LIE_Ability"))
+correlation(select(dfsub, starts_with("LIE_")), select(dfsub, starts_with("HCT_")), p_adjust = "none")
 ```
-
-### Summary
-
-```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
-p_conf_hct_accuracy / 
-  p_conf_hct_confidence / 
-  p_conf_hct_awareness +
-  patchwork::plot_annotation(title = "Heartbeat Counting Task", theme = theme(plot.title = element_text(hjust = 0.5)))
-
-p_rt_hct_accuracy / 
-  p_rt_hct_confidence / 
-  p_rt_hct_awareness +
-  patchwork::plot_annotation(title = "Heartbeat Counting Task", theme = theme(plot.title = element_text(hjust = 0.5)))
-
-p_hr_hct_accuracy / 
-  p_hr_hct_confidence / 
-  p_hr_hct_awareness +
-  patchwork::plot_annotation(title = "Heartbeat Counting Task", theme = theme(plot.title = element_text(hjust = 0.5)))
-```
-
-## Heartbeat Tracking {.tabset}
 
@@
 
-### Total Score
+- Confidence: effect in total, noticing, not distracting, body listening, not worrying, attention regulation and self regulation.
+- RT: effect in total, noticing, body listening, attention regulation and self regulation.
+- Heart rate: effect in trusting and emotional awareness only.
 
-#### Confidence
+### Confidence
 
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_Total) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
+results <- data.frame()
+for (var in c(
+  "MAIA_Noticing", "MAIA_NotDistracting", "MAIA_NotWorrying",
+  "MAIA_AttentionRegulation", "MAIA_EmotionalAwareness", "MAIA_SelfRegulation",
+  "MAIA_BodyListening", "MAIA_Trusting", "MAIA_Total"
+)) {
+  model <- glmmTMB(as.formula(paste0(
+    "Confidence ~ Answer / (Condition / ",
+    var,
+    ") + (1|Participant) + (1|Item)"
+  )),
+  data = df,
+  family = beta_family()
+  )
 
-results <- get_parameters(model)
-results$params
-results$marginal_effects
+  results <- parameters::parameters(model, effects = "fixed", keep = var) |>
+    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |>
+    separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+    data_relocate(select = "Variable", before = 1) |>
+    rbind(results)
+}
+
+display(results, stars = TRUE)
 ```
 
+### RT
+
 ```{r message=FALSE, warning=FALSE}
-p_conf_maia_total <- plot_effect(model, results, var = "MAIA_Total", outcome = "Confidence")
+results <- data.frame()
+for (var in c(
+  "MAIA_Noticing", "MAIA_NotDistracting", "MAIA_NotWorrying",
+  "MAIA_AttentionRegulation", "MAIA_EmotionalAwareness", "MAIA_SelfRegulation",
+  "MAIA_BodyListening", "MAIA_Trusting", "MAIA_Total"
+)) {
+  model <- glmmTMB(as.formula(paste0(
+    "RT ~ Answer / (Condition / ",
+    var,
+    ") + (1|Participant) + (1|Item)"
+  )),
+  data = df
+  )
+
+  results <- parameters::parameters(model, effects = "fixed", keep = var) |>
+    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |>
+    separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+    data_relocate(select = "Variable", before = 1) |>
+    rbind(results)
+}
+
+display(results, stars = TRUE)
 ```
 
-#### RT
+### Heart Rate
 
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * MAIA_Total) + (1|Participant) + (1|Item), 
-                 data = df)
+results <- data.frame()
+for (var in c(
+  "MAIA_Noticing", "MAIA_NotDistracting", "MAIA_NotWorrying",
+  "MAIA_AttentionRegulation", "MAIA_EmotionalAwareness", "MAIA_SelfRegulation",
+  "MAIA_BodyListening", "MAIA_Trusting", "MAIA_Total"
+)) {
+  model <- glmmTMB(as.formula(paste0(
+    "HeartRate ~ Answer / (Condition / ",
+    var,
+    ") + (1|Participant) + (1|Item)"
+  )),
+  data = df
+  )
 
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
+  results <- parameters::parameters(model, effects = "fixed", keep = var) |>
+    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |>
+    separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+    data_relocate(select = "Variable", before = 1) |>
+    rbind(results)
+}
 
-```{r message=FALSE, warning=FALSE}
-p_rt_maia_total <- plot_effect(model, results, var = "MAIA_Total", outcome = "RT")
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_Total) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_maia_total <- plot_effect(model, results, var = "MAIA_Total", outcome = "HeartRate")
-```
-
-### Noticing
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_Noticing) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_maia_noticing <- plot_effect(model, results, var = "MAIA_Noticing", outcome = "Confidence")
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * MAIA_Noticing) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_maia_noticing <- plot_effect(model, results, var = "MAIA_Noticing", outcome = "RT")
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_Noticing) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_maia_noticing <- plot_effect(model, results, var = "MAIA_Noticing", outcome = "HeartRate")
-```
-
-### Not Distracting
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_NotDistracting) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_maia_notdistracting <- plot_effect(model, results, var = "MAIA_NotDistracting", outcome = "Confidence")
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * MAIA_NotDistracting) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_maia_notdistracting <- plot_effect(model, results, var = "MAIA_NotDistracting", outcome = "RT")
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_NotDistracting) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_maia_notdistracting <- plot_effect(model, results, var = "MAIA_NotDistracting", outcome = "HeartRate")
-```
-
-### Body Listening
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_BodyListening) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_maia_bodylistening <- plot_effect(model, results, var = "MAIA_BodyListening", outcome = "Confidence")
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * MAIA_BodyListening) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_maia_bodylistening <- plot_effect(model, results, var = "MAIA_BodyListening", outcome = "RT")
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_BodyListening) + (1|Participant), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_maia_bodylistening <- plot_effect(model, results, var = "MAIA_BodyListening", outcome = "HeartRate")
-```
-
-### Trusting
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_Trusting) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_maia_trusting <- plot_effect(model, results, var = "MAIA_Trusting", outcome = "Confidence")
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * MAIA_Trusting) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_maia_trusting <- plot_effect(model, results, var = "MAIA_Trusting", outcome = "RT")
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_Trusting) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_maia_trusting <- plot_effect(model, results, var = "MAIA_Trusting", outcome = "HeartRate")
-```
-
-### Not Worrying
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_NotWorrying) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_maia_notworrying <- plot_effect(model, results, var = "MAIA_NotWorrying", outcome = "Confidence")
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * MAIA_NotWorrying) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_maia_notworrying <- plot_effect(model, results, var = "MAIA_NotWorrying", outcome = "RT")
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_NotWorrying) + (1|Participant), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_maia_notworrying <- plot_effect(model, results, var = "MAIA_NotWorrying", outcome = "HeartRate")
-```
-
-### Emotional Awareness
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_EmotionalAwareness) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_maia_emotionalawareness <- plot_effect(model, results, var = "MAIA_EmotionalAwareness", outcome = "Confidence")
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * MAIA_EmotionalAwareness) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_maia_emotionalawareness <- plot_effect(model, results, var = "MAIA_EmotionalAwareness", outcome = "RT")
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_EmotionalAwareness) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_maia_emotionalawareness <- plot_effect(model, results, var = "MAIA_EmotionalAwareness", outcome = "HeartRate")
-```
-
-### Attention Regulation
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_AttentionRegulation) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_maia_attentionregulation <- plot_effect(model, results, var = "MAIA_AttentionRegulation", outcome = "Confidence")
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * MAIA_AttentionRegulation) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_maia_attentionregulation <- plot_effect(model, results, var = "MAIA_AttentionRegulation", outcome = "RT")
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_AttentionRegulation) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_maia_attentionregulation <- plot_effect(model, results, var = "MAIA_AttentionRegulation", outcome = "HeartRate")
-```
-
-### Self Regulation
-
-#### Confidence
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_SelfRegulation) + (1|Participant) + (1|Item), 
-                 data = df, family = beta_family())
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_conf_maia_selfregulation <- plot_effect(model, results, var = "MAIA_SelfRegulation", outcome = "Confidence")
-```
-
-#### RT
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(RT ~ Answer / (Condition * MAIA_SelfRegulation) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_rt_maia_selfregulation <- plot_effect(model, results, var = "MAIA_SelfRegulation", outcome = "RT")
-```
-
-#### Heart Rate
-
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_SelfRegulation) + (1|Participant) + (1|Item), 
-                 data = df)
-
-results <- get_parameters(model)
-results$params
-results$marginal_effects
-```
-
-```{r message=FALSE, warning=FALSE}
-p_hr_maia_selfregulation <- plot_effect(model, results, var = "MAIA_SelfRegulation", outcome = "HeartRate")
+display(results, stars = TRUE)
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-r <- get_correlation(var = "MAIA_")
-r$plot +
-  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
+dfsub <- df |>
+  select(
+    Participant,
+    starts_with("LIE_"),
+    starts_with("MAIA_")
+  ) |>
+  group_by(Participant) |>
+  summarise_all(mean)
+
+correlation(select(dfsub, starts_with("LIE_")), select(dfsub, starts_with("MAIA_")), p_adjust = "none")
 ```
-
-### Summary
-
-```{r message=FALSE, warning=FALSE, fig.height=figheight*4, fig.width=figwidth*1.5}
-p_conf_maia_total / 
-  p_conf_maia_noticing / 
-  p_conf_maia_notdistracting / 
-  p_conf_maia_bodylistening /
-  p_conf_maia_trusting +
-  patchwork::plot_annotation(title = "Interoception (MAIA) 1/2", theme = theme(plot.title = element_text(hjust = 0.5)))
-
-p_conf_maia_notworrying / 
-  p_conf_maia_emotionalawareness / 
-  p_conf_maia_attentionregulation / 
-  p_conf_maia_selfregulation +
-  patchwork::plot_annotation(title = "Interoception (MAIA) 2/2", theme = theme(plot.title = element_text(hjust = 0.5)))
-
-p_rt_maia_total /
-  p_rt_maia_noticing / 
-  p_rt_maia_notdistracting / 
-  p_rt_maia_bodylistening /
-  p_rt_maia_trusting +
-  patchwork::plot_annotation(title = "Interoception (MAIA) 1/2", theme = theme(plot.title = element_text(hjust = 0.5)))
-
-  p_rt_maia_notworrying / 
-  p_rt_maia_emotionalawareness / 
-  p_rt_maia_attentionregulation / 
-  p_rt_maia_selfregulation +
-  patchwork::plot_annotation(title = "Interoception (MAIA) 2/2", theme = theme(plot.title = element_text(hjust = 0.5)))
-
-p_hr_maia_total / 
-  p_hr_maia_noticing / 
-  p_hr_maia_notdistracting / 
-  p_hr_maia_bodylistening /
-  p_hr_maia_trusting +
-  patchwork::plot_annotation(title = "Interoception (MAIA) 1/2", theme = theme(plot.title = element_text(hjust = 0.5)))
-
-p_hr_maia_notworrying / 
-  p_hr_maia_emotionalawareness / 
-  p_hr_maia_attentionregulation / 
-  p_hr_maia_selfregulation +
-  patchwork::plot_annotation(title = "Interoception (MAIA) 2/2", theme = theme(plot.title = element_text(hjust = 0.5)))
-```

### 2022-10-04 index.Rmd
added interpretations
update

@@
 title: '**The Role of Interoception and Theory of Mind in Deception**'
-subtitle: A Subtitle
+author: "Dominique Makowski et al."
+date: "`r Sys.Date()`"
 output:
   html_document:
-    theme: cerulean
-    highlight: pygments
+    theme: paper
     toc: yes
     toc_depth: 3
-    toc_float: yes
-    number_sections: no
     df_print: default
@@
     code_download: yes
-  word_document:
-    reference_docx: utils/Template_Word.docx
-    highlight: pygments
-    toc: no
-    toc_depth: 3
-    df_print: kable
-    number_sections: yes
-  rmarkdown::html_vignette:
-    toc: yes
-    toc_depth: 3
-  pdf_document:
-    toc: yes
-    toc_depth: '2'
-    latex_engine: xelatex
 editor_options:
   chunk_output_type: console
-bibliography: utils/bibliography.bib
-csl: utils/apa.csl
 ---
@@
 source("https://raw.githubusercontent.com/RealityBending/TemplateResults/main/utils/config.R")
-options(dplyr.summarise.inform = FALSE) 
+
+options(
+  digits = 3,
+  mc.cores = 4,
+  brms.algorithm = "sampling",
+  brms.backend = "cmdstanr",
+  dplyr.summarise.inform = FALSE
+)
+
 knitr::opts_chunk$set(echo = TRUE)
+
 library(ggplot2)
@@
 ```
-
-# Introduction
-
-```{r badges, echo=FALSE, message=TRUE, warning=FALSE, results='asis'}
-# This chunk is a bit complex so don't worry about it: it's made to add badges to the HTML versions
-# NOTE: You have to replace the links accordingly to have working "buttons" on the HTML versions
-if (!knitr::is_latex_output() && knitr::is_html_output()) {
-  cat("![Build](https://github.com/RealityBending/TemplateResults/workflows/Build/badge.svg)
-      [![Website](https://img.shields.io/badge/repo-Readme-2196F3)](https://github.com/RealityBending/TemplateResults)
-      [![Website](https://img.shields.io/badge/visit-website-E91E63)](https://realitybending.github.io/TemplateResults/)
-      [![Website](https://img.shields.io/badge/download-.docx-FF5722)](https://github.com/RealityBending/TemplateResults/raw/main/word_and_pdf/SupplementaryMaterials.docx)
-      [![Website](https://img.shields.io/badge/see-.pdf-FF9800)](https://github.com/RealityBending/TemplateResults/blob/main/word_and_pdf/SupplementaryMaterials.pdf)")
-}
-```
-
-<!-- Title ideas:-->
-<!-- Theory of Body and Others -->
-
-# Packages & Data
-
-## Packages
-
-This document was prepared on `r format(Sys.Date())`.
 
@@
 library(glmmTMB)
-library(report)
-library(parameters)
-library(correlation)
-library(modelbased)
-library(performance)
-library(see)
+library(brms)
+library(easystats)
 
+show_parameters <- function(model) {
+  p <- parameters::parameters(model, effects = "fixed", component="conditional", test=c("pd")) |>
+    data_relocate("pd", after=-1)
+  display(p, stars=TRUE)
+}
+```
+
+```{r warning=FALSE, message=TRUE, results='asis'}
 summary(report::report(sessionInfo()))
 ```
-
-## Data
 
@@
   dplyr::filter(!Participant %in% c("S3", "S15", "S19", "S23"))  # No data
+
+# Outliers
+df$HeartRate[df$Participant == "S30"] <- NA # Extreme values
+# df$Confidence[df$Participant %in% c("S9", "S29")] <- NA # Extreme responses
+df$RT[df$Participant == "S13"] <- NA # Slower than the others
+
+# Remove outlier trials
+df <- df |>
+  group_by(Participant) |>
+  mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore", threshold = qnorm(0.99999))),
+         Outliers_Physio = as.logical(performance::check_outliers(HeartRate, method = "zscore", threshold = qnorm(0.99999)))) |>
+  ungroup()
 
@@
 
+Percentage of Confidence data removed: `r sum(is.na(df$Confidence)) / nrow(df) * 100` %  
+Percentage of RT data removed: `r sum(is.na(df$RT)) / nrow(df) * 100` %  
+Percentage of Heart Rate data removed: `r sum(is.na(df$HeartRate)) / nrow(df) * 100` %
+
 # Measures {.tabset}
@@
 ```{r child='1_Measures.Rmd'}
+```
+
+# Dimension Reduction
+
+## Theory of Mind
+
+```{r message=FALSE, warning=FALSE}
+dfsub <- df |> 
+  select(Participant, 
+         starts_with("YONI_"), 
+         starts_with("BES_")) |> 
+  select(-ends_with("Total")) |> 
+  group_by(Participant) |> 
+  summarise_all(mean) |> 
+  select(-Participant)
+
+parameters::n_factors(dfsub)
+efa <- parameters::factor_analysis(dfsub, n=1, sort=TRUE, rotation = "oblimin")
+efa
+
+df <- cbind(df, predict(efa, newdata=df, names="ToM"))
+```
+
+## Interoception
+
+```{r message=FALSE, warning=FALSE}
+dfsub <- df |> 
+  select(Participant, 
+         starts_with("HCT_"), 
+         starts_with("MAIA_")) |> 
+  select(-ends_with("Total")) |> 
+  group_by(Participant) |> 
+  summarise_all(mean) |> 
+  select(-Participant)
+
+parameters::n_components(dfsub)
+efa <- parameters::factor_analysis(dfsub, n=4, sort=TRUE, rotation = "oblimin")
+efa
+df <- cbind(df, predict(efa, newdata=df, names=c("Intero_Meta", "Intero_Listening", "Intero_Focus", "Intero_Regulation")))
 ```
@@
 
+## Theory of Mind Score {.tabset}
+
+### Confidence
+
+```{r message=FALSE, warning=FALSE}
+results <- list()
+for (var in c("ToM")) {
+  model <- brms::brm(as.formula(paste0("Confidence ~ Answer / (Condition / ",
+                                     var,
+                                     ") + (1|Participant) + (1|Item)")),
+                   data = df, family = "beta", refresh=0, seed=3, iter=4000,
+                   prior = set_prior("student_t(1, 0, 1)", class = "b"))
+
+  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
+      as.data.frame() |> 
+      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+      mutate(
+        Answer = str_remove(Answer, "b_Answer"),
+        Condition = str_remove(Condition, "Condition")
+      )
+}
+
+display(format_table(results$ToM, stars = TRUE))
+```
+
+### RT
+
+```{r message=FALSE, warning=FALSE}
+results <- list()
+for (var in c("ToM")) {
+  model <- brms::brm(as.formula(paste0("RT ~ Answer / (Condition / ",
+                                     var,
+                                     ") + (1|Participant) + (1|Item)")),
+                   data = df, refresh=0, seed=3, iter=4000,
+                   prior = set_prior("student_t(1, 0, 3)", class = "b"))
+
+  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
+      as.data.frame() |> 
+      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+      mutate(
+        Answer = str_remove(Answer, "b_Answer"),
+        Condition = str_remove(Condition, "Condition")
+      )
+}
+
+display(format_table(results$ToM, stars = TRUE))
+```
+
+### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+results <- list()
+for (var in c("ToM")) {
+  model <- brms::brm(as.formula(paste0("HeartRate ~ Answer / (Condition / ",
+                                     var,
+                                     ") + (1|Participant) + (1|Item)")),
+                   data = df, refresh=0, seed=3, iter=4000,
+                   prior = set_prior("student_t(1, 0, 8)", class = "b"))
+
+  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
+      as.data.frame() |> 
+      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+      mutate(
+        Answer = str_remove(Answer, "b_Answer"),
+        Condition = str_remove(Condition, "Condition")
+      )
+}
+
+display(format_table(results$ToM, stars = TRUE))
+```
+
+### Correlation with LIE Scale
+
+```{r message=FALSE, warning=FALSE}
+dfsub <- df |>
+  select(Participant,
+         starts_with("LIE_"),
+         starts_with("ToM")) |>
+  group_by(Participant) |>
+  summarise_all(mean)
+
+correlation(select(dfsub, starts_with("LIE_")), select(dfsub, starts_with("ToM")), bayesian=TRUE)
+```
+
 ```{r child='3_ToM.Rmd'}
@@
 
+## Interoception Scores {.tabset}
+
+### Confidence
+
+```{r message=FALSE, warning=FALSE}
+results <- list()
+for (var in c("Intero_Meta", "Intero_Listening", "Intero_Focus", "Intero_Regulation")) {
+  model <- brms::brm(as.formula(paste0(
+    "Confidence ~ Answer / (Condition / ",
+    var,
+    ") + (1|Participant) + (1|Item)"
+  )),
+  data = df, family = "beta", refresh = 0, seed=3, iter = 4000,
+  prior = set_prior("student_t(1, 0, 1)", class = "b")
+  )
+
+  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
+      as.data.frame() |> 
+      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+      mutate(
+        Answer = str_remove(Answer, "b_Answer"),
+        Condition = str_remove(Condition, "Condition")
+      )
+}
+
+display(format_table(results$Intero_Meta, stars = TRUE))
+display(format_table(results$Intero_Listening, stars = TRUE))
+display(format_table(results$Intero_Focus, stars = TRUE))
+display(format_table(results$Intero_Regulation, stars = TRUE))
+```
+
+### RT
+
+```{r message=FALSE, warning=FALSE}
+results <- list()
+for (var in c("Intero_Meta", "Intero_Listening", "Intero_Focus", "Intero_Regulation")) {
+  model <- brms::brm(as.formula(paste0(
+    "RT ~ Answer / (Condition / ",
+    var,
+    ") + (1|Participant) + (1|Item)"
+  )),
+  data = df, refresh = 0, seed=3, iter = 4000,
+  prior = set_prior("student_t(1, 0, 3)", class = "b")
+  )
+
+  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
+      as.data.frame() |> 
+      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+      mutate(
+        Answer = str_remove(Answer, "b_Answer"),
+        Condition = str_remove(Condition, "Condition")
+      )
+}
+
+display(format_table(results$Intero_Meta, stars = TRUE))
+display(format_table(results$Intero_Listening, stars = TRUE))
+display(format_table(results$Intero_Focus, stars = TRUE))
+display(format_table(results$Intero_Regulation, stars = TRUE))
+```
+
+### Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+results <- list()
+for (var in c("Intero_Meta", "Intero_Listening", "Intero_Focus", "Intero_Regulation")) {
+  model <- brms::brm(as.formula(paste0(
+    "HeartRate ~ Answer / (Condition / ",
+    var,
+    ") + (1|Participant) + (1|Item)"
+  )),
+  data = df, refresh = 0, seed=3, iter = 4000,
+  prior = set_prior("student_t(1, 0, 8)", class = "b")
+  )
+
+  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
+      as.data.frame() |> 
+      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+      mutate(
+        Answer = str_remove(Answer, "b_Answer"),
+        Condition = str_remove(Condition, "Condition")
+      )
+}
+
+display(format_table(results$Intero_Meta, stars = TRUE))
+display(format_table(results$Intero_Listening, stars = TRUE))
+display(format_table(results$Intero_Focus, stars = TRUE))
+display(format_table(results$Intero_Regulation, stars = TRUE))
+```
+
+### Correlation with LIE Scale
+
+```{r message=FALSE, warning=FALSE}
+dfsub <- df |>
+  select(
+    Participant,
+    starts_with("LIE_"),
+    starts_with("Intero_")
+  ) |>
+  group_by(Participant) |>
+  summarise_all(mean)
+
+correlation(select(dfsub, starts_with("LIE_")), select(dfsub, starts_with("Intero_")), bayesian = TRUE)
+```
+
 ```{r child='4_Intero.Rmd'}
@@
 
-# Full Code
+# Figure
 
-The full script of executive code contained in this document is reproduced here.
+```{r warning=FALSE, message=FALSE, eval=FALSE}
+data <- df |>
+  group_by(Participant, Answer, Condition) |> 
+  select(Confidence, RT, HeartRate, ToM, Intero_Regulation, Intero_Focus, Intero_Meta, Intero_Listening) |> 
+  summarise_all(.funs = list(Mean = function(x) mean(x, na.rm = TRUE), 
+                             low = function(x) (mean(x, na.rm=TRUE) - sd(x, na.rm=TRUE) / 2),
+                             high = function(x) (mean(x, na.rm=TRUE) + sd(x, na.rm=TRUE) / 2))) |> 
+  mutate(ToM_Mean = ifelse(Condition == "Polygraph", ToM_Mean-0.01, ToM_Mean+0.01),
+         Intero_Regulation_Mean = ifelse(Condition == "Polygraph", Intero_Regulation_Mean-0.01, Intero_Regulation_Mean+0.01),
+         Intero_Focus_Mean = ifelse(Condition == "Polygraph", Intero_Focus_Mean-0.01, Intero_Focus_Mean+0.01),
+         Intero_Meta_Mean = ifelse(Condition == "Polygraph", Intero_Meta_Mean-0.01, Intero_Meta_Mean+0.01),
+         Intero_Listening_Mean = ifelse(Condition == "Polygraph", Intero_Listening_Mean-0.01, Intero_Listening_Mean+0.01))
 
-```{r full_code, ref.label=knitr::all_labels(), eval=FALSE}
+model <- glmmTMB(Confidence ~ Answer / Condition / ToM + (1|Participant) + (1|Item), 
+                 data = df, 
+                 family = beta_family())
+
+model <- brms::brm(Confidence ~ Answer / Condition / ToM + (1|Participant) + (1|Item), 
+                   data = df, family = "beta", seed=3, refresh=0,
+                   prior = set_prior("student_t(1, 0, 1)", class = "b"))
+
+link_data <- estimate_relation(model, at = c("Condition", "Answer", "ToM"), length = 30)
+
+p1 <- ggplot(link_data, aes(x = ToM, y = Predicted)) +
+  geom_segment(data = data,
+                  aes(x = ToM_Mean,
+                      xend = ToM_Mean,
+                      y = Confidence_low,
+                      yend = Confidence_high,
+                      color = Condition),
+                  alpha=1/3) +
+  geom_point2(data = data,
+                  aes(x = ToM_Mean,
+                      y = Confidence_Mean,
+                      color = Condition),
+              size=2) +
+  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
+  geom_line(aes(color = Condition), size=1) +
+  geom_text(data=data.frame(ToM = -0.3, Predicted = 0.45, Condition = "Polygraph", Answer = "Lie"),
+            label = "***",
+            color = "#FF5722",
+            size = 10, show.legend = FALSE, fontface = "bold") +
+  labs(y = "Confidence",
+       x = "Theory of Mind") +
+  scale_y_continuous(labels = scales::percent) + 
+  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
+  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
+  facet_wrap(~Answer) +
+  theme_modern(axis.title.space = 10) +
+  theme(strip.text = element_text(size = 10),
+        strip.background = element_rect(fill = c("grey"), color = "white"))
+p1
+
+model <- brms::brm(Confidence ~ Answer / Condition / Intero_Meta + (1|Participant) + (1|Item), 
+                   data = df, family = "beta", seed=3, refresh=0,
+                   prior = set_prior("student_t(1, 0, 1)", class = "b"))
+
+link_data <- estimate_relation(model, at = c("Condition", "Answer", "Intero_Meta"), length = 30)
+
+p2 <- ggplot(link_data, aes(x = Intero_Meta, y = Predicted)) +
+  geom_segment(data = data,
+                  aes(x = Intero_Meta_Mean,
+                      xend = Intero_Meta_Mean,
+                      y = Confidence_low,
+                      yend = Confidence_high,
+                      color = Condition),
+                  alpha=1/3) +
+  geom_point2(data = data,
+                  aes(x = Intero_Meta_Mean,
+                      y = Confidence_Mean,
+                      color = Condition),
+              size=2) +
+  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
+  geom_line(aes(color = Condition), size=1) +
+  geom_text(data=data.frame(Intero_Meta = -0.15, Predicted = 0.25, Condition = "Polygraph", Answer = "Lie"),
+            label = "***",
+            color = "#FF5722",
+            size = 10, show.legend = FALSE, fontface = "bold") +
+  labs(y = "Confidence",
+       x = expression(Interoception["  (.97 MAIA Attention regulation, .63 MAIA Self-regulation, .60 MAIA Emotional Awareness)"])) +
+  scale_y_continuous(labels = scales::percent) + 
+  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
+  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
+  facet_wrap(~Answer) +
+  theme_modern(axis.title.space = 10) +
+  theme(strip.text = element_text(size = 10),
+        strip.background = element_rect(fill = c("grey"), color = "white"))
+p2
+
+model <- brms::brm(Confidence ~ Answer / Condition / Intero_Listening + (1|Participant) + (1|Item), 
+                   data = df, family = "beta", seed=3, refresh=0,
+                   prior = set_prior("student_t(1, 0, 1)", class = "b"))
+link_data <- estimate_relation(model, at = c("Condition", "Answer", "Intero_Listening"), length = 30)
+
+p3 <- ggplot(link_data, aes(x = Intero_Listening, y = Predicted)) +
+  geom_segment(data = data,
+                  aes(x = Intero_Listening_Mean,
+                      xend = Intero_Listening_Mean,
+                      y = Confidence_low,
+                      yend = Confidence_high,
+                      color = Condition),
+                  alpha=1/3) +
+  geom_point2(data = data,
+                  aes(x = Intero_Listening_Mean,
+                      y = Confidence_Mean,
+                      color = Condition),
+              size=2) +
+  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
+  geom_line(aes(color = Condition), size=1) +
+  geom_text(data=data.frame(Intero_Listening = 0.2, Predicted = 0.45, Condition = "Polygraph", Answer = "Lie"),
+            label = "***",
+            color = "#FF5722",
+            size = 10, show.legend = FALSE, fontface = "bold") +
+  labs(y = "Confidence",
+       x = expression(Interoception["  (.92 MAIA Body listening, -.60 HCT Awareness, .53 HCT Trusting)"])) +
+  scale_y_continuous(labels = scales::percent) + 
+  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
+  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
+  facet_wrap(~Answer) +
+  theme_modern(axis.title.space = 10) +
+  theme(strip.text = element_text(size = 10),
+        strip.background = element_rect(fill = c("grey"), color = "white"))
+
+p3
+
+model <- brms::brm(Confidence ~ Answer / Condition / Intero_Focus + (1|Participant) + (1|Item), 
+                   data = df, family = "beta", seed=3, refresh=0,
+                   prior = set_prior("student_t(1, 0, 1)", class = "b"))
+link_data <- estimate_relation(model, at = c("Condition", "Answer", "Intero_Focus"), length = 30)
+
+p4 <- ggplot(link_data, aes(x = Intero_Focus, y = Predicted)) +
+  geom_segment(data = data,
+                  aes(x = Intero_Focus_Mean,
+                      xend = Intero_Focus_Mean,
+                      y = Confidence_low,
+                      yend = Confidence_high,
+                      color = Condition),
+                  alpha=1/3) +
+  geom_point2(data = data,
+                  aes(x = Intero_Focus_Mean,
+                      y = Confidence_Mean,
+                      color = Condition),
+              size=2) +
+  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
+  geom_line(aes(color = Condition), size=1) +
+  geom_text(data=data.frame(Intero_Focus = -0.2,
+                            Predicted = c(0.55, 0.75),
+                            Condition = c("Polygraph", "Interrogation"),
+                            Answer = c("Truth", "Truth")),
+            label = c("*", "*"),
+            color = c("#2196F3", "#FF5722"),
+            size = 10, show.legend = FALSE, fontface = "bold") +
+  labs(y = "Confidence",
+       x = expression(Interoception["  (.87 MAIA Not-distracting, -.40 MAIA Emotional Awareness, .33 HCT Accuracy)"])) +
+  scale_y_continuous(labels = scales::percent) + 
+  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
+  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
+  facet_wrap(~Answer) +
+  theme_modern(axis.title.space = 10) +
+  theme(strip.text = element_text(size = 10),
+        strip.background = element_rect(fill = c("grey"), color = "white"))
+p4
+
+model <- brms::brm(Confidence ~ Answer / Condition / Intero_Regulation + (1|Participant) + (1|Item), 
+                   data = df, family = "beta", seed=3, refresh=0,
+                   prior = set_prior("student_t(1, 0, 1)", class = "b"))
+
+link_data <- estimate_relation(model, at = c("Condition", "Answer", "Intero_Regulation"), length = 30)
+
+p5 <- ggplot(link_data, aes(x = Intero_Regulation, y = Predicted)) +
+  geom_segment(data = data,
+                  aes(x = Intero_Regulation_Mean,
+                      xend = Intero_Regulation_Mean,
+                      y = Confidence_low,
+                      yend = Confidence_high,
+                      color = Condition),
+                  alpha=1/3) +
+  geom_point2(data = data,
+                  aes(x = Intero_Regulation_Mean,
+                      y = Confidence_Mean,
+                      color = Condition),
+              size=2) +
+  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
+  geom_line(aes(color = Condition), size=1) +
+  geom_text(data=data.frame(Intero_Regulation = -0.15, 
+                            Predicted = c(0.25, 0.45, 0.75),
+                            Condition = c("Polygraph", "Interrogation", "Polygraph"), 
+                            Answer = c("Lie", "Lie", "Truth")),
+            label = c("***", "*", "*"),
+            color = c("#FF5722", "#2196F3", "#FF5722"),
+            size = 10, show.legend = FALSE, fontface = "bold") +
+  labs(y = "Confidence",
+       x = expression(Interoception["  (.71 MAIA Not-worrying, .61 HCT Accuracy, .40 MAIA Trusting)"])) +
+  scale_y_continuous(labels = scales::percent) + 
+  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
+  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
+  facet_wrap(~Answer) +
+  theme_modern(axis.title.space = 10) +
+  theme(strip.text = element_text(size = 10),
+        strip.background = element_rect(fill = c("grey"), color = "white")) 
+p5
+
+p <- (p1 / p2 / p3 / p4 / p5) + plot_layout(guides = "collect") + plot_annotation(title = "Interindividual correlates of the confidence\nthat one tells a convincing lie", theme = list(plot.title = element_text(face = "bold", hjust = 0.5)))
+p
+ggsave("figures/Figure1.png", width=12, height=15)
 ```
 
-# Package References
+# References
 
@@
 ```
-
-# References

### 2022-10-04 old/final_processing/Analysis/analysis.tex
update

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\title{Analysis}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\hypertarget{libraries}{%
\section{Libraries}\label{libraries}}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{setwd}\NormalTok{(}\StringTok{"~/Dropbox/FYP_Jia Rong/R Processing/FINAL PROCESSING/Analysis"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(tidyverse)}
\KeywordTok{library}\NormalTok{(lme4)}
\KeywordTok{library}\NormalTok{(ggplot2)}
\KeywordTok{library}\NormalTok{(glmmTMB)}
\KeywordTok{library}\NormalTok{(correlation)}
\KeywordTok{library}\NormalTok{(sjPlot)}
\KeywordTok{library}\NormalTok{(easystats)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # Attaching packages
## ✔ insight     0.13.1.1   ✔ bayestestR  0.8.3.1 
## ✔ performance 0.7.0.1    ✔ parameters  0.12.0.1
## ✔ see         0.6.2      ✔ effectsize  0.4.4   
## ✔ modelbased  0.5.9      ✔ report      0.2.0   
## 
## Warnings or errors in CRAN checks for package(s) 'insight', 'bayestestR', 'parameters', 'effectsize', 'modelbased', 'correlation'.
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#library(ggpubr)}

\NormalTok{descriptive_statistics <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(df, begins_with)\{}
\NormalTok{  df }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{select}\NormalTok{(dplyr}\OperatorTok{::}\KeywordTok{starts_with}\NormalTok{(begins_with)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{report}\NormalTok{() }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{as.data.frame}\NormalTok{() }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\KeywordTok{one_of}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"n_Obs"}\NormalTok{, }\StringTok{"Median"}\NormalTok{, }\StringTok{"MAD"}\NormalTok{, }\StringTok{"n_Missing"}\NormalTok{))) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{print}\NormalTok{()}

  \KeywordTok{plot}\NormalTok{(df }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{select}\NormalTok{(dplyr}\OperatorTok{::}\KeywordTok{starts_with}\NormalTok{(begins_with)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\NormalTok{bayestestR}\OperatorTok{::}\KeywordTok{estimate_density}\NormalTok{(}\DataTypeTok{method =} \StringTok{"KernSmooth"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{plot}\NormalTok{() }\OperatorTok{+}\StringTok{ }
\StringTok{    }\NormalTok{see}\OperatorTok{::}\KeywordTok{theme_modern}\NormalTok{())}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{read-data}{%
\section{Read data}\label{read-data}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Behav <-}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{'BehaviouraldataNEW.csv'}\NormalTok{, }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{header =} \OtherTok{TRUE}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{)] }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{participant =}\NormalTok{ ID,}
         \DataTypeTok{truthfulness =}\NormalTok{ condition) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ConditionSP =} \KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"social"}\NormalTok{,}\StringTok{"polygraph"}\NormalTok{), }\DataTypeTok{each =} \DecValTok{40}\NormalTok{, }\DataTypeTok{times =} \DecValTok{30}\NormalTok{))}

\NormalTok{Behav[stringr}\OperatorTok{::}\KeywordTok{str_detect}\NormalTok{(}\KeywordTok{names}\NormalTok{(Behav), }\StringTok{"subresp"}\NormalTok{)] <-}\StringTok{ }\NormalTok{effectsize}\OperatorTok{::}\KeywordTok{change_scale}\NormalTok{(Behav[stringr}\OperatorTok{::}\KeywordTok{str_detect}\NormalTok{(}\KeywordTok{names}\NormalTok{(Behav), }\StringTok{"subresp"}\NormalTok{)], }\DataTypeTok{from =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{), }\DataTypeTok{to =} \KeywordTok{c}\NormalTok{(}\DecValTok{10}\NormalTok{, }\DecValTok{-10}\NormalTok{))}

\NormalTok{Phy <-}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{'DT.csv'}\NormalTok{, }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{header =} \OtherTok{TRUE}\NormalTok{) [}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{),] }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{participant =}\NormalTok{ Participant.number,) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Trial =} \KeywordTok{rep}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{80}\NormalTok{, }\DataTypeTok{each =} \DecValTok{4}\NormalTok{, }\DataTypeTok{times =} \DecValTok{30}\NormalTok{)) }

\CommentTok{#Phy <- Phy[!(Phy$Participant == 1 & Phy$Label == 3),]}

\NormalTok{data <-}\StringTok{ }\KeywordTok{merge}\NormalTok{(Behav, Phy, }\DataTypeTok{by =} \KeywordTok{c}\NormalTok{(}\StringTok{"participant"}\NormalTok{ ,}\StringTok{"Trial"}\NormalTok{), }\DataTypeTok{all =} \OtherTok{TRUE}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{arrange}\NormalTok{(participant,Trial) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{participant =} \KeywordTok{as.factor}\NormalTok{(participant),}
         \DataTypeTok{ConditionSP =} \KeywordTok{as.factor}\NormalTok{(ConditionSP))}

\NormalTok{Demo <-}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{'demo_30.csv'}\NormalTok{, }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{header =} \OtherTok{TRUE}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{2}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{4}\OperatorTok{:}\DecValTok{6}\NormalTok{,}\DecValTok{9}\NormalTok{,}\DecValTok{11}\NormalTok{,}\DecValTok{12}\NormalTok{,}\DecValTok{18}\NormalTok{)]}
\end{Highlighting}
\end{Shaded}

\hypertarget{cleaning-data}{%
\section{Cleaning data}\label{cleaning-data}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{data <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(Inclusion }\OperatorTok{!=}\StringTok{ "0"}\NormalTok{)}
\CommentTok{#  filter(Inclusion2 != "0")}
\CommentTok{# filter(participant != "22", "30")}
\end{Highlighting}
\end{Shaded}

\hypertarget{descriptive-statistics}{%
\section{Descriptive Statistics}\label{descriptive-statistics}}

\hypertarget{participants-demographics-information}{%
\subsection{Participants Demographics
Information}\label{participants-demographics-information}}

Summary of participants Gender, Age, and handedness

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#General Descriptive Stats}
\KeywordTok{report}\NormalTok{(Demo)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## The data contains 30 observations of the following variables:
##   - X: n = 30, Mean = 15.50, SD = 8.80, Median = 15.50, MAD = 11.12, range: [1, 30], Skewness = 0.00, Kurtosis = -1.20, 0 missing
##   - Gender: 2 entries, such as Female (n = 19); Male (n = 11); NA (0 missing)
##   - Age: n = 30, Mean = 21.10, SD = 2.09, Median = 20.50, MAD = 2.22, range: [18, 25], Skewness = 0.73, Kurtosis = -0.67, 0 missing
##   - handedness: 2 entries, such as Right handed (n = 28); Left handed (n = 2); NA (0 missing)
##   - Polyjc: 5 entries, such as Junior College (n = 18); Polytechnic (n = 9); Equivalent of Junior College in India (n = 1) and 2 others (0 missing)
##   - Ethnicity: 6 entries, such as Chinese (n = 25); Burmese (n = 1); Caucasian (n = 1) and 3 others (0 missing)
##   - Religion: 7 entries, such as Buddhism (n = 10); Not religious (n = 9); Christianity (n = 7) and 4 others (0 missing)
##   - Nationality: 5 entries, such as Singaporean (n = 25); China (n = 2); Indian (n = 1) and 2 others (0 missing)
##   - RaisedinSG: 2 entries, such as Yes (n = 21); No (n = 9); NA (0 missing)
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{report_participants}\NormalTok{(Demo)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] "30 participants (Mean age = 21.1, SD = 2.1, range: [18, 25]; 63.3% females)"
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Gender <-}\StringTok{ }\NormalTok{Demo }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{group_by}\NormalTok{(Gender) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{summarize}\NormalTok{(}\DataTypeTok{n =} \KeywordTok{n}\NormalTok{(),}
            \DataTypeTok{Ratio =} \KeywordTok{n}\NormalTok{() }\OperatorTok{/}\StringTok{ }\KeywordTok{nrow}\NormalTok{(Demo))}

\NormalTok{Age <-}\StringTok{ }\NormalTok{Demo [}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{),] }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{summarise}\NormalTok{(}\KeywordTok{mean}\NormalTok{(Age),}\KeywordTok{sd}\NormalTok{(Age))}
\KeywordTok{report}\NormalTok{(Demo}\OperatorTok{$}\NormalTok{Age)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## x: n = 30, Mean = 21.10, SD = 2.09, Median = 20.50, MAD = 2.22, range: [18, 25], Skewness = 0.73, Kurtosis = -0.67, 0 missing
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Handedness <-}\StringTok{ }\NormalTok{Demo }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{group_by}\NormalTok{(handedness) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{summarize}\NormalTok{(}\DataTypeTok{n =} \KeywordTok{n}\NormalTok{(),}
            \DataTypeTok{Ratio =} \KeywordTok{n}\NormalTok{() }\OperatorTok{/}\StringTok{ }\KeywordTok{nrow}\NormalTok{(Demo))}
\KeywordTok{report}\NormalTok{(Demo}\OperatorTok{$}\NormalTok{handedness)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## x: 2 entries, such as Right handed (n = 28); Left handed (n = 2); NA (0 missing)
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Gender}
\KeywordTok{as.data.frame}\NormalTok{(}\KeywordTok{table}\NormalTok{(Demo}\OperatorTok{$}\NormalTok{Gender)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\StringTok{""}\NormalTok{, }\DataTypeTok{y =}\NormalTok{Freq, }\DataTypeTok{fill =} \KeywordTok{reorder}\NormalTok{(Var1, }\OperatorTok{-}\NormalTok{Freq))) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_bar}\NormalTok{(}\DataTypeTok{width =} \DecValTok{1}\NormalTok{, }\DataTypeTok{stat =} \StringTok{"identity"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{fill =} \StringTok{"Gender"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{coord_polar}\NormalTok{(}\StringTok{"y"}\NormalTok{, }\DataTypeTok{start =} \DecValTok{0}\NormalTok{, }\DataTypeTok{direction =} \DecValTok{-1}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_fill_brewer}\NormalTok{(}\DataTypeTok{palette=}\StringTok{"Blues"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_void}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{12}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{face =} \StringTok{"bold"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{20}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-1-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Age}
\KeywordTok{as.data.frame}\NormalTok{(}\KeywordTok{table}\NormalTok{(Demo}\OperatorTok{$}\NormalTok{Age)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\StringTok{""}\NormalTok{, }\DataTypeTok{y =}\NormalTok{Freq, }\DataTypeTok{fill =} \KeywordTok{reorder}\NormalTok{(Var1, }\OperatorTok{-}\NormalTok{Freq))) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_bar}\NormalTok{(}\DataTypeTok{width =} \DecValTok{1}\NormalTok{, }\DataTypeTok{stat =} \StringTok{"identity"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{fill =} \StringTok{"Age"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{coord_polar}\NormalTok{(}\StringTok{"y"}\NormalTok{, }\DataTypeTok{start =} \DecValTok{0}\NormalTok{, }\DataTypeTok{direction =} \DecValTok{1}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_fill_brewer}\NormalTok{(}\DataTypeTok{palette=}\StringTok{"Oranges"}\NormalTok{, }\DataTypeTok{breaks=}\KeywordTok{c}\NormalTok{(}\StringTok{"18"}\NormalTok{,}\StringTok{"19"}\NormalTok{,}\StringTok{"20"}\NormalTok{,}\StringTok{"21"}\NormalTok{,}\StringTok{"22"}\NormalTok{,}\StringTok{"24"}\NormalTok{,}\StringTok{"25"}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_void}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{15}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{face =} \StringTok{"bold"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{20}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-1-2.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Handedness}
\KeywordTok{as.data.frame}\NormalTok{(}\KeywordTok{table}\NormalTok{(Demo}\OperatorTok{$}\NormalTok{handedness)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\StringTok{""}\NormalTok{, }\DataTypeTok{y =}\NormalTok{Freq, }\DataTypeTok{fill =} \KeywordTok{reorder}\NormalTok{(Var1, Freq))) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_bar}\NormalTok{(}\DataTypeTok{width =} \DecValTok{1}\NormalTok{, }\DataTypeTok{stat =} \StringTok{"identity"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{fill =} \StringTok{"Handedness"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{coord_polar}\NormalTok{(}\StringTok{"y"}\NormalTok{, }\DataTypeTok{start =} \DecValTok{0}\NormalTok{, }\DataTypeTok{direction =} \DecValTok{-1}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_fill_brewer}\NormalTok{(}\DataTypeTok{palette=}\StringTok{"greens"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_void}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{12}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{face =} \StringTok{"bold"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{20}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-1-3.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Ethnicity}
\KeywordTok{as.data.frame}\NormalTok{(}\KeywordTok{table}\NormalTok{(Demo}\OperatorTok{$}\NormalTok{Ethnicity)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\StringTok{""}\NormalTok{, }\DataTypeTok{y =}\NormalTok{Freq, }\DataTypeTok{fill =} \KeywordTok{reorder}\NormalTok{(Var1, }\OperatorTok{-}\NormalTok{Freq))) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_bar}\NormalTok{(}\DataTypeTok{width =} \DecValTok{1}\NormalTok{, }\DataTypeTok{stat =} \StringTok{"identity"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{fill =} \StringTok{"Ethnicity"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{coord_polar}\NormalTok{(}\StringTok{"y"}\NormalTok{, }\DataTypeTok{start =} \DecValTok{0}\NormalTok{, }\DataTypeTok{direction =} \DecValTok{-1}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_fill_brewer}\NormalTok{(}\DataTypeTok{palette=}\StringTok{"Pastel1"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_void}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{12}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{face =} \StringTok{"bold"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{20}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-1-4.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Religion}
\KeywordTok{as.data.frame}\NormalTok{(}\KeywordTok{table}\NormalTok{(Demo}\OperatorTok{$}\NormalTok{Religion)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\StringTok{""}\NormalTok{, }\DataTypeTok{y =}\NormalTok{Freq, }\DataTypeTok{fill =} \KeywordTok{reorder}\NormalTok{(Var1, }\OperatorTok{-}\NormalTok{Freq))) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_bar}\NormalTok{(}\DataTypeTok{width =} \DecValTok{1}\NormalTok{, }\DataTypeTok{stat =} \StringTok{"identity"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{fill =} \StringTok{"Religion"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{coord_polar}\NormalTok{(}\StringTok{"y"}\NormalTok{, }\DataTypeTok{start =} \DecValTok{0}\NormalTok{, }\DataTypeTok{direction =} \DecValTok{-1}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_fill_brewer}\NormalTok{(}\DataTypeTok{palette=}\StringTok{"Set2"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_void}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{12}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{face =} \StringTok{"bold"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{20}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-1-5.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Nationality}
\KeywordTok{as.data.frame}\NormalTok{(}\KeywordTok{table}\NormalTok{(Demo}\OperatorTok{$}\NormalTok{Nationality)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\StringTok{""}\NormalTok{, }\DataTypeTok{y =}\NormalTok{Freq, }\DataTypeTok{fill =} \KeywordTok{reorder}\NormalTok{(Var1, }\OperatorTok{-}\NormalTok{Freq))) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_bar}\NormalTok{(}\DataTypeTok{width =} \DecValTok{1}\NormalTok{, }\DataTypeTok{stat =} \StringTok{"identity"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{fill =} \StringTok{"Nationality"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{coord_polar}\NormalTok{(}\StringTok{"y"}\NormalTok{, }\DataTypeTok{start =} \DecValTok{0}\NormalTok{, }\DataTypeTok{direction =} \DecValTok{-1}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_fill_brewer}\NormalTok{(}\DataTypeTok{palette=}\StringTok{"Set2"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_void}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{12}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{face =} \StringTok{"bold"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{20}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-1-6.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{des_stat <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }
\KeywordTok{group_by}\NormalTok{(participant) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{summarise_all}\NormalTok{(mean) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\KeywordTok{ends_with}\NormalTok{(}\StringTok{"Total"}\NormalTok{),}
          \OperatorTok{-}\KeywordTok{ends_with}\NormalTok{(}\StringTok{"TotalAvg"}\NormalTok{))}

\KeywordTok{descriptive_statistics}\NormalTok{(des_stat, }\StringTok{"BES_"}\NormalTok{)          }\CommentTok{#Basic Empathy/ToM}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Variable      |  Mean |   SD |   Min |   Max | Skewness | Kurtosis
## ------------------------------------------------------------------
## BES_Cognitive | 35.40 | 4.28 | 26.00 | 44.00 |    -0.40 |     0.12
## BES_Affective | 38.03 | 7.13 | 25.00 | 53.00 |     0.19 |    -0.50
\end{verbatim}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-1-7.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{descriptive_statistics}\NormalTok{(des_stat, }\StringTok{"Lie_"}\NormalTok{)          }\CommentTok{#Deceptive Tendency}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Variable    |  Mean |   SD |   Min |  Max | Skewness | Kurtosis
## ---------------------------------------------------------------
## Lie_Freq    |  1.18 | 2.08 | -3.04 | 4.30 |    -0.52 |    -0.61
## Lie_Ability | -0.90 | 2.03 | -4.84 | 3.23 |    -0.20 |    -0.25
## Lie_Neg     | -0.43 | 1.36 | -3.51 | 2.43 |    -0.05 |    -0.14
## Lie_Content | -0.77 | 0.90 | -2.16 | 1.41 |     0.60 |    -0.32
\end{verbatim}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-1-8.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{descriptive_statistics}\NormalTok{(des_stat, }\StringTok{"MAIA"}\NormalTok{)          }\CommentTok{#Interoceptive Awareness}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Variable | Mean |   SD |  Min |  Max | Skewness | Kurtosis
## ----------------------------------------------------------
## MAIA1    | 2.98 | 0.70 | 0.75 | 4.25 |    -0.94 |     2.43
## MAIA2    | 1.76 | 0.90 | 0.17 | 3.67 |     0.08 |    -0.12
## MAIA3    | 2.14 | 0.77 | 0.60 | 3.80 |     0.25 |    -0.58
## MAIA4    | 2.72 | 0.91 | 0.71 | 4.14 |    -0.37 |    -0.34
## MAIA5    | 3.33 | 0.77 | 1.40 | 4.80 |    -0.51 |     0.02
## MAIA6    | 2.83 | 0.81 | 1.50 | 4.25 |     0.07 |    -1.33
## MAIA7    | 2.56 | 1.13 | 0.33 | 5.00 |     0.04 |    -0.67
## MAIA8    | 3.36 | 1.06 | 0.33 | 5.00 |    -0.99 |     0.95
\end{verbatim}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-1-9.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{descriptive_statistics}\NormalTok{(des_stat, }\StringTok{"SRP3_"}\NormalTok{)         }\CommentTok{#Psychopathic Traits}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Variable |  Mean |    SD |   Min |    Max | Skewness | Kurtosis
## ---------------------------------------------------------------
## SRP3_IPM | 42.30 |  9.35 | 25.00 |  63.00 |    -0.04 |    -0.25
## SRP3_CA  | 37.87 |  9.62 | 22.00 |  55.00 |     0.21 |    -1.21
## SRP3_ELS | 40.40 |  7.33 | 25.00 |  55.00 |    -0.36 |    -0.14
## SRP3_ASB | 22.50 |  6.61 | 16.00 |  42.00 |     1.46 |     2.10
## SRP3_PRI | 80.17 | 16.73 | 51.00 | 113.00 |    -0.02 |    -0.64
## SRP3_SEC | 62.90 | 11.83 | 42.00 |  90.00 |     0.22 |    -0.16
\end{verbatim}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-1-10.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{descriptive_statistics}\NormalTok{(des_stat, }\StringTok{"HCT"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{facet_wrap}\NormalTok{(}\OperatorTok{~}\NormalTok{Parameter, }\DataTypeTok{scales=}\StringTok{"free"}\NormalTok{)         }\CommentTok{#Heartbeat Counting Task (Interoception)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Variable       | Mean |   SD |   Min |  Max | Skewness | Kurtosis
## -----------------------------------------------------------------
## HCT_Confidence | 0.46 | 0.30 |  0.00 | 0.89 |    -0.16 |    -1.41
## HCT_Accuracy   | 0.93 | 0.06 |  0.76 | 0.99 |    -1.34 |     1.11
## HCT_Awareness  | 0.10 | 0.55 | -0.93 | 0.98 |     0.03 |    -0.75
\end{verbatim}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-1-11.pdf}
\includegraphics{analysis_files/figure-latex/unnamed-chunk-1-12.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{descriptive_statistics}\NormalTok{(des_stat, }\StringTok{"yoni_"}\NormalTok{)         }\CommentTok{#Yoni Task (ToM)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Variable       |  Mean |   SD |   Min |   Max | Skewness | Kurtosis
## -------------------------------------------------------------------
## yoni_affective | 41.83 | 4.07 | 33.00 | 47.00 |    -0.79 |    -0.39
## yoni_cognitive | 31.03 | 3.06 | 24.00 | 36.00 |    -0.50 |     0.04
## yoni_physical  | 12.20 | 2.51 |  4.00 | 14.00 |    -1.85 |     3.11
\end{verbatim}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-1-13.pdf}

The final sample included 30 participants (Mean age = 21.1, SD = 2.1,
range: {[}18, 25{]}; 63.3\% females).

\hypertarget{participants-individual-summary-results-for-behavioural-tasks-deception-hct-yoni-task}{%
\subsection{Participants Individual Summary Results for Behavioural
Tasks (Deception, HCT \& Yoni
Task)}\label{participants-individual-summary-results-for-behavioural-tasks-deception-hct-yoni-task}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df_descriptive <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(truthfulness }\OperatorTok{!=}\StringTok{ "TRUTH"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{group_by}\NormalTok{(participant, ConditionSP) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{summarise_all}\NormalTok{(mean)}

\NormalTok{df_descriptive <-}\StringTok{ }\NormalTok{df_descriptive }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{,}\DecValTok{9}\NormalTok{,}\DecValTok{36}\OperatorTok{:}\DecValTok{42}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{pivot_wider}\NormalTok{(}\DataTypeTok{names_from =}\NormalTok{ ConditionSP, }\DataTypeTok{values_from =}\NormalTok{ subresp) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{PolyCon_subresp =}\NormalTok{ polygraph,}
         \DataTypeTok{SociCon_subresp =}\NormalTok{ social)}
\end{Highlighting}
\end{Shaded}

\#\#Plot of Average Subjective Response of Lies for Each Participant

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{plot_desriptive <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(truthfulness }\OperatorTok{!=}\StringTok{ "TRUTH"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{group_by}\NormalTok{(participant, ConditionSP) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{summarise_all}\NormalTok{(mean) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{,}\DecValTok{9}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(participant }\OperatorTok{!=}\StringTok{ "3"}\NormalTok{,}
\NormalTok{         participant }\OperatorTok{!=}\StringTok{ "15"}\NormalTok{,}
\NormalTok{         participant }\OperatorTok{!=}\StringTok{ "19"}\NormalTok{,}
\NormalTok{         participant }\OperatorTok{!=}\StringTok{ "23"}\NormalTok{)}

\NormalTok{pd <-}\StringTok{ }\KeywordTok{position_dodge}\NormalTok{(}\FloatTok{0.1}\NormalTok{)}
\NormalTok{plot_desriptive }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{participant =} \KeywordTok{as.factor}\NormalTok{(participant)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ ConditionSP, }\DataTypeTok{y =}\NormalTok{ subresp, }\DataTypeTok{color =}\NormalTok{ participant, }\DataTypeTok{group=}\NormalTok{participant)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_point}\NormalTok{(}\DataTypeTok{position =}\NormalTok{ pd) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{position =}\NormalTok{ pd) }\OperatorTok{+}
\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{"Condition"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{ylab}\NormalTok{(}\StringTok{"Subjective Response"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Plot of Average Subjective Responses for Lies"}\NormalTok{)  }\OperatorTok{+}\StringTok{ }
\StringTok{  }\NormalTok{see}\OperatorTok{::}\KeywordTok{theme_modern}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{plot.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{12}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-3-1.pdf}

\hypertarget{summary-of-tasks}{%
\subsection{Summary of Tasks}\label{summary-of-tasks}}

average and SD of each task

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Summary_of_task <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}
  \DataTypeTok{Mean =} \KeywordTok{sapply}\NormalTok{(df_descriptive[}\DecValTok{2}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(df_descriptive)], mean, }\DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{),}
  \DataTypeTok{SD =} \KeywordTok{sapply}\NormalTok{(df_descriptive[}\DecValTok{2}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(df_descriptive)], sd, }\DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{analysis}{%
\section{Analysis}\label{analysis}}

\#\#Inferential (TO REMOVE) Plot of various average Physio scores in 2
conditions

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Corr <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(truthfulness }\OperatorTok{!=}\StringTok{ "TRUTH"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(Condition }\OperatorTok{==}\StringTok{ "R"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{group_by}\NormalTok{(participant, ConditionSP) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{summarise_all}\NormalTok{(mean) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{,}\DecValTok{9}\NormalTok{,}\DecValTok{58}\NormalTok{,}\DecValTok{72}\NormalTok{,}\DecValTok{80}\NormalTok{))}

\CommentTok{#Plot of Average Physio Response of lies in 2 conditions}
\CommentTok{##ECG_Rate_Mean}
\NormalTok{pd <-}\StringTok{ }\KeywordTok{position_dodge}\NormalTok{(}\FloatTok{0.1}\NormalTok{)}
\NormalTok{Corr }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{participant =} \KeywordTok{as.factor}\NormalTok{(participant)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ ConditionSP, }\DataTypeTok{y =}\NormalTok{ ECG_Rate_Mean, }\DataTypeTok{color =}\NormalTok{ participant, }\DataTypeTok{group=}\NormalTok{participant)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_point}\NormalTok{(}\DataTypeTok{position =}\NormalTok{ pd) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{position =}\NormalTok{ pd) }\OperatorTok{+}
\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{"Condition"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{ylab}\NormalTok{(}\StringTok{"Subjective Response"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Plot of ECG Rate Mean for Lies"}\NormalTok{)  }\OperatorTok{+}\StringTok{ }
\StringTok{  }\NormalTok{see}\OperatorTok{::}\KeywordTok{theme_modern}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{plot.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{12}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-5-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{##RSP_Rate_Mean}
\NormalTok{Corr }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{participant =} \KeywordTok{as.factor}\NormalTok{(participant)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ ConditionSP, }\DataTypeTok{y =}\NormalTok{ RSP_Rate_Mean, }\DataTypeTok{color =}\NormalTok{ participant, }\DataTypeTok{group=}\NormalTok{participant)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_point}\NormalTok{(}\DataTypeTok{position =}\NormalTok{ pd) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{position =}\NormalTok{ pd) }\OperatorTok{+}
\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{"Condition"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{ylab}\NormalTok{(}\StringTok{"Subjective Response"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Plot of RSP Rate Mean for Lies"}\NormalTok{)  }\OperatorTok{+}\StringTok{ }
\StringTok{  }\NormalTok{see}\OperatorTok{::}\KeywordTok{theme_modern}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{plot.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{12}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-5-2.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{##RSP_Amplitude_Mean}
\NormalTok{Corr }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{participant =} \KeywordTok{as.factor}\NormalTok{(participant)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ ConditionSP, }\DataTypeTok{y =}\NormalTok{ RSP_Amplitude_Mean, }\DataTypeTok{color =}\NormalTok{ participant, }\DataTypeTok{group=}\NormalTok{participant)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_point}\NormalTok{(}\DataTypeTok{position =}\NormalTok{ pd) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{position =}\NormalTok{ pd) }\OperatorTok{+}
\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{"Condition"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{ylab}\NormalTok{(}\StringTok{"Subjective Response"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Plot of RSP Amplitude Mean for Lies"}\NormalTok{)  }\OperatorTok{+}\StringTok{ }
\StringTok{  }\NormalTok{see}\OperatorTok{::}\KeywordTok{theme_modern}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{plot.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{12}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-5-3.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Correlation of Average subjective response vs Physio + Scatterplots}
\CommentTok{#http://www.sthda.com/english/wiki/correlation-test-between-two-variables-in-r}
\end{Highlighting}
\end{Shaded}

\#Correlation Matrix of all Variables

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df_correlation <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(truthfulness }\OperatorTok{!=}\StringTok{ "TRUTH"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(Condition }\OperatorTok{==}\StringTok{ "R"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{8}\NormalTok{,}\DecValTok{50}\NormalTok{,}\DecValTok{55}\OperatorTok{:}\DecValTok{90}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{participant =} \KeywordTok{as.factor}\NormalTok{(participant),}
         \DataTypeTok{ConditionSP =} \KeywordTok{as.factor}\NormalTok{(ConditionSP))}

\NormalTok{Corr_Matrix <-}\StringTok{ }\NormalTok{correlation}\OperatorTok{::}\KeywordTok{correlation}\NormalTok{(}
  \KeywordTok{select}\NormalTok{(df_correlation,}
\NormalTok{         participant, }
\NormalTok{         ConditionSP, }
\NormalTok{         subresp, }
         \KeywordTok{starts_with}\NormalTok{(}\StringTok{"ECG"}\NormalTok{), }
         \KeywordTok{starts_with}\NormalTok{(}\StringTok{"RSP"}\NormalTok{),}
         \KeywordTok{starts_with}\NormalTok{(}\StringTok{"EDA"}\NormalTok{)),}
  \DataTypeTok{multilevel =}\NormalTok{ F, }\DataTypeTok{p_adjust =} \StringTok{"none"}\NormalTok{) }

\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{filter}\NormalTok{(Corr_Matrix, Parameter1 }\OperatorTok{==}\StringTok{ "subresp"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{arrange}\NormalTok{(}\KeywordTok{desc}\NormalTok{(}\KeywordTok{abs}\NormalTok{(r)))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # Correlation table (pearson-method)
## 
## Parameter1 |                       Parameter2 |         r |         95% CI | t(1173) |         p
## ------------------------------------------------------------------------------------------------
## subresp    |                     ECG_Rate_Max |     -0.17 | [-0.22, -0.11] |   -5.82 | < .001***
## subresp    |                ECG_Rate_Max_Time |     -0.16 | [-0.22, -0.11] |   -5.65 | < .001***
## subresp    |                ECG_Rate_Trend_R2 |     -0.15 | [-0.20, -0.09] |   -5.13 | < .001***
## subresp    |                ECG_Rate_Min_Time |      0.11 | [ 0.05,  0.17] |    3.83 | < .001***
## subresp    |               RSP_Amplitude_Mean |     -0.11 | [-0.17, -0.05] |   -3.79 | < .001***
## subresp    |                RSP_Amplitude_Max |     -0.09 | [-0.15, -0.04] |   -3.18 | 0.002**  
## subresp    |                     ECG_Rate_Min |      0.07 | [ 0.02,  0.13] |    2.57 | 0.010*   
## subresp    |                RSP_Rate_Baseline |     -0.06 | [-0.12, -0.01] |   -2.17 | 0.030*   
## subresp    |      ECG_Phase_Completion_Atrial |      0.05 | [-0.01,  0.11] |    1.77 | 0.077    
## subresp    |                          EDA_SCR |      0.05 | [-0.01,  0.11] |    1.77 | 0.078    
## subresp    |         ECG_Rate_Trend_Quadratic |     -0.04 | [-0.10,  0.01] |   -1.50 | 0.133    
## subresp    |                RSP_Rate_Trend_R2 |     -0.04 | [-0.10,  0.02] |   -1.44 | 0.150    
## subresp    |                RSP_Amplitude_Min |     -0.03 | [-0.09,  0.02] |   -1.19 | 0.232    
## subresp    |            ECG_Phase_Ventricular |     -0.03 | [-0.09,  0.02] |   -1.16 | 0.247    
## subresp    |                     RSP_Rate_Min |      0.03 | [-0.02,  0.09] |    1.14 | 0.256    
## subresp    |            RSP_Rate_Trend_Linear |      0.03 | [-0.03,  0.09] |    0.98 | 0.326    
## subresp    |         RSP_Rate_Trend_Quadratic |     -0.02 | [-0.08,  0.03] |   -0.81 | 0.420    
## subresp    |                    ECG_Rate_Mean |     -0.02 | [-0.08,  0.04] |   -0.74 | 0.460    
## subresp    | ECG_Phase_Completion_Ventricular |     -0.02 | [-0.08,  0.04] |   -0.68 | 0.498    
## subresp    |                    RSP_Rate_Mean |      0.02 | [-0.04,  0.08] |    0.63 | 0.528    
## subresp    |                RSP_Rate_Min_Time |     -0.02 | [-0.07,  0.04] |   -0.57 | 0.572    
## subresp    |                        RSP_Phase |     -0.01 | [-0.07,  0.04] |   -0.51 | 0.611    
## subresp    |             RSP_Phase_Completion |      0.01 | [-0.04,  0.07] |    0.43 | 0.664    
## subresp    |                     RSP_Rate_Max |     -0.01 | [-0.07,  0.05] |   -0.42 | 0.676    
## subresp    |                RSP_Rate_Max_Time |     -0.01 | [-0.07,  0.05] |   -0.40 | 0.687    
## subresp    |                ECG_Rate_Baseline |      0.01 | [-0.05,  0.07] |    0.40 | 0.688    
## subresp    |                 ECG_Quality_Mean |      0.01 | [-0.05,  0.07] |    0.35 | 0.723    
## subresp    |               EDA_Peak_Amplitude | -4.29e-03 | [-0.06,  0.05] |   -0.15 | 0.883    
## subresp    |            ECG_Rate_Trend_Linear |  2.34e-03 | [-0.05,  0.06] |    0.08 | 0.936    
## subresp    |                 ECG_Phase_Atrial |  7.04e-04 | [-0.06,  0.06] |    0.02 | 0.981    
## 
## p-value adjustment method: none
## Observations: 1175
\end{verbatim}

\#Hypothesis Nested Regression Analysis

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Regression models}
\CommentTok{##Subjective Response Comparison}
\NormalTok{df <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{participant =} \KeywordTok{as.factor}\NormalTok{(participant),}
         \DataTypeTok{ConditionSP =} \KeywordTok{as.factor}\NormalTok{(ConditionSP)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(truthfulness }\OperatorTok{==}\StringTok{ "LIE"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(Inclusion2 }\OperatorTok{!=}\StringTok{ "0"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(participant }\OperatorTok{!=}\StringTok{ "3"}\NormalTok{,}
\NormalTok{         participant }\OperatorTok{!=}\StringTok{ "15"}\NormalTok{,}
\NormalTok{         participant }\OperatorTok{!=}\StringTok{ "19"}\NormalTok{,}
\NormalTok{         participant }\OperatorTok{!=}\StringTok{ "23"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(Condition }\OperatorTok{==}\StringTok{ "C"}\NormalTok{) }
  \CommentTok{# mutate(yoni_new = yoni_affective + yoni_cognitive) }

\CommentTok{#TOM Hypothesis 1A: SUBRESP -> YONI/BES}
\NormalTok{model_sub1 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(subresp }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_sub1)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |   SE |          95% CI | t(948) |     p
## -----------------------------------------------------------------------------------------
## (Intercept)                       |       -6.82 | 9.37 | [-25.18, 11.53] |  -0.73 | 0.466
## ConditionSP [social]              |        9.27 | 3.79 | [  1.83, 16.70] |   2.44 | 0.015
## yoni_total                        |        0.10 | 0.11 | [ -0.11,  0.31] |   0.91 | 0.362
## ConditionSP [social] * yoni_total |       -0.11 | 0.04 | [ -0.20, -0.03] |  -2.54 | 0.011
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_sub1, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"Yoni Task"}\NormalTok{, }\StringTok{"Subjective Response"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of Subjective Response by Yoni Task"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_sub2 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(subresp }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_cognitive }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df)  }\CommentTok{#explorative}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_sub2)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                             | Coefficient |   SE |          95% CI | t(948) |      p
## ----------------------------------------------------------------------------------------------
## (Intercept)                           |      -11.70 | 8.39 | [-28.13,  4.74] |  -1.40 | 0.163 
## ConditionSP [social]                  |       12.23 | 3.40 | [  5.57, 18.90] |   3.60 | < .001
## yoni_cognitive                        |        0.43 | 0.27 | [ -0.10,  0.96] |   1.60 | 0.109 
## ConditionSP [social] * yoni_cognitive |       -0.41 | 0.11 | [ -0.62, -0.19] |  -3.70 | < .001
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_sub2, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_cognitive"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"Yoni Task (Affective)"}\NormalTok{, }\StringTok{"Subjective Response"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of Subjective Response by Yoni Task (Affective)"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-2.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_sub3 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(subresp }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{BES_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_sub3)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                        | Coefficient |   SE |          95% CI | t(948) |     p
## ----------------------------------------------------------------------------------------
## (Intercept)                      |       -4.11 | 7.01 | [-17.85,  9.62] |  -0.59 | 0.557
## ConditionSP [social]             |        7.49 | 2.84 | [  1.94, 13.05] |   2.64 | 0.008
## BES_Total                        |        0.08 | 0.10 | [ -0.11,  0.27] |   0.83 | 0.404
## ConditionSP [social] * BES_Total |       -0.11 | 0.04 | [ -0.18, -0.03] |  -2.77 | 0.006
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_sub3, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"BES_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"BES Questionnaire"}\NormalTok{, }\StringTok{"Subjective Response"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of Subjective Response by BES Questionnaire"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-3.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_sub4 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(subresp }\OperatorTok{~}\StringTok{ }\NormalTok{(ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_total) }\OperatorTok{+}\StringTok{ }\NormalTok{BES_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df)  }\CommentTok{#explorative}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_sub4)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |    SE |          95% CI | t(947) |     p
## ------------------------------------------------------------------------------------------
## (Intercept)                       |       -7.47 | 10.51 | [-28.07, 13.14] |  -0.71 | 0.477
## ConditionSP [social]              |        9.26 |  3.79 | [  1.83, 16.70] |   2.44 | 0.015
## yoni_total                        |        0.10 |  0.12 | [ -0.13,  0.32] |   0.81 | 0.416
## BES_Total                         |        0.01 |  0.10 | [ -0.18,  0.21] |   0.15 | 0.883
## ConditionSP [social] * yoni_total |       -0.11 |  0.04 | [ -0.20, -0.03] |  -2.54 | 0.011
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_sub4, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{, }\StringTok{"BES_Total"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-4.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#TOM Hypothesis 1C: SUBRESP -> SRP3}
\NormalTok{model_sub5 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(subresp }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_sub5)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |   SE |         95% CI | t(948) |     p
## ----------------------------------------------------------------------------------------
## (Intercept)                       |       -3.06 | 4.51 | [-11.89, 5.78] |  -0.68 | 0.498
## ConditionSP [social]              |       -0.97 | 1.85 | [ -4.59, 2.64] |  -0.53 | 0.597
## SRP3_Total                        |        0.03 | 0.03 | [ -0.03, 0.10] |   1.07 | 0.286
## ConditionSP [social] * SRP3_Total |    4.74e-03 | 0.01 | [ -0.02, 0.03] |   0.37 | 0.713
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_sub5, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3 Inventory"}\NormalTok{, }\StringTok{"Subjective Response"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of Subjective Response by SRP3 Inventory"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-5.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_sub6 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(subresp }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_ELS }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df)  }\CommentTok{#explorative}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_sub6)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                       | Coefficient |   SE |         95% CI | t(948) |     p
## --------------------------------------------------------------------------------------
## (Intercept)                     |       -1.35 | 4.87 | [-10.88, 8.19] |  -0.28 | 0.782
## ConditionSP [social]            |       -1.16 | 1.96 | [ -4.99, 2.68] |  -0.59 | 0.555
## SRP3_ELS                        |        0.07 | 0.12 | [ -0.16, 0.31] |   0.63 | 0.528
## ConditionSP [social] * SRP3_ELS |        0.02 | 0.05 | [ -0.07, 0.11] |   0.44 | 0.661
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_sub6, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_ELS"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3 (Erratic Life Style)"}\NormalTok{, }\StringTok{"Subjective Response"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of Subjective Response by SRP3 - ELS"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-6.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Interoception Hypothesis 2A: SUBRESP -> HCT/MAIA}
\NormalTok{model_sub7 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(subresp }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{HCT_Accuracy }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_sub7)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                           | Coefficient |    SE |          95% CI | t(948) |     p
## --------------------------------------------------------------------------------------------
## (Intercept)                         |       18.49 | 11.85 | [ -4.74, 41.72] |   1.56 | 0.119
## ConditionSP [social]                |      -12.41 |  4.82 | [-21.87, -2.96] |  -2.57 | 0.010
## HCT_Accuracy                        |      -18.22 | 12.82 | [-43.35,  6.90] |  -1.42 | 0.155
## ConditionSP [social] * HCT_Accuracy |       13.13 |  5.22 | [  2.90, 23.36] |   2.52 | 0.012
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_sub7, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"HCT_Accuracy"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"HCT Accuracy"}\NormalTok{, }\StringTok{"Subjective Response"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of Subjective Response by HCT Accuracy"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-7.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_sub8 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(subresp }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{MAIA_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_sub8)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |   SE |         95% CI | t(948) |     p
## ----------------------------------------------------------------------------------------
## (Intercept)                       |        8.58 | 4.05 | [ 0.64, 16.52] |   2.12 | 0.034
## ConditionSP [social]              |       -3.25 | 1.69 | [-6.55,  0.06] |  -1.93 | 0.054
## MAIA_Total                        |       -0.32 | 0.19 | [-0.69,  0.04] |  -1.74 | 0.082
## ConditionSP [social] * MAIA_Total |        0.14 | 0.08 | [-0.01,  0.29] |   1.78 | 0.075
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_sub8, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"MAIA_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"MAIA2"}\NormalTok{, }\StringTok{"Subjective Response"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of Subjective Response by MAIA2"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-8.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_sub9 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(subresp }\OperatorTok{~}\StringTok{ }\NormalTok{(ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{HCT_Accuracy) }\OperatorTok{+}\StringTok{ }\NormalTok{HCT_Confidence }\OperatorTok{+}\StringTok{ }\NormalTok{MAIA_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df)                                                                                       }\CommentTok{#explorative}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_sub9)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                           | Coefficient |    SE |          95% CI | t(946) |     p
## --------------------------------------------------------------------------------------------
## (Intercept)                         |       21.30 | 12.76 | [ -3.72, 46.31] |   1.67 | 0.095
## ConditionSP [social]                |      -12.39 |  4.82 | [-21.85, -2.94] |  -2.57 | 0.010
## HCT_Accuracy                        |      -16.04 | 13.15 | [-41.82,  9.74] |  -1.22 | 0.223
## HCT_Confidence                      |       -0.53 |  4.63 | [ -9.61,  8.55] |  -0.11 | 0.909
## MAIA_Total                          |       -0.21 |  0.28 | [ -0.75,  0.33] |  -0.77 | 0.441
## ConditionSP [social] * HCT_Accuracy |       13.10 |  5.22 | [  2.87, 23.33] |   2.51 | 0.012
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_sub9, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"HCT_Accuracy"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-9.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Interoception Hypothesis 2C: SUBRESP -> SRP3_PRI}
\NormalTok{model_sub10 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(subresp }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_PRI }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_sub10)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                       | Coefficient |   SE |         95% CI | t(948) |     p
## --------------------------------------------------------------------------------------
## (Intercept)                     |       -3.28 | 3.97 | [-11.05, 4.50] |  -0.83 | 0.409
## ConditionSP [social]            |       -0.55 | 1.64 | [ -3.76, 2.65] |  -0.34 | 0.735
## SRP3_PRI                        |        0.06 | 0.05 | [ -0.03, 0.16] |   1.28 | 0.202
## ConditionSP [social] * SRP3_PRI |    3.15e-03 | 0.02 | [ -0.04, 0.04] |   0.15 | 0.878
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_sub10, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_PRI"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3 (PRI) Inventory"}\NormalTok{, }\StringTok{"Subjective Response"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of Subjective Response by SRP3 (PRI)"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-10.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#ECG Physio scores comparison}
\NormalTok{df2 <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{participant =} \KeywordTok{as.factor}\NormalTok{(participant),}
         \DataTypeTok{ConditionSP =} \KeywordTok{as.factor}\NormalTok{(ConditionSP)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(truthfulness }\OperatorTok{==}\StringTok{ "LIE"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(Inclusion2 }\OperatorTok{!=}\StringTok{ "0"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(participant }\OperatorTok{!=}\StringTok{ "22"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\CommentTok{#  filter(participant != "23") %>%         #try keep 12 and 15}
\StringTok{  }\KeywordTok{filter}\NormalTok{(participant }\OperatorTok{!=}\StringTok{ "30"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{filter}\NormalTok{(Condition }\OperatorTok{==}\StringTok{ "C"}\NormalTok{) }
  \CommentTok{# filter(participant != "12",}
  \CommentTok{#        participant != "15") %>%}

\CommentTok{#ECG_RATE_MAX}
\CommentTok{#TOM Hypothesis 1A: ECG_Rate_Max -> YONI/BES}
\NormalTok{model_ecg1 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg1)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |   SE |         95% CI | t(1017) |     p
## -----------------------------------------------------------------------------------------
## (Intercept)                       |       13.99 | 6.34 | [ 1.56, 26.42] |    2.21 | 0.027
## ConditionSP [social]              |        2.08 | 3.26 | [-4.31,  8.47] |    0.64 | 0.524
## yoni_total                        |       -0.09 | 0.07 | [-0.24,  0.05] |   -1.23 | 0.218
## ConditionSP [social] * yoni_total |   -3.91e-03 | 0.04 | [-0.08,  0.07] |   -0.10 | 0.918
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg1, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"Yoni Task"}\NormalTok{, }\StringTok{"ECG_Rate_Max"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of ECG_Rate_Max by Yoni Task"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-11.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_ecg2 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_affective }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)  }\CommentTok{#explorative}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg2)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                             | Coefficient |   SE |         95% CI | t(1017) |      p
## ----------------------------------------------------------------------------------------------
## (Intercept)                           |       19.40 | 5.72 | [ 8.19, 30.61] |    3.39 | < .001
## ConditionSP [social]                  |        1.98 | 3.10 | [-4.10,  8.06] |    0.64 | 0.523 
## yoni_affective                        |       -0.32 | 0.14 | [-0.58, -0.05] |   -2.32 | 0.021 
## ConditionSP [social] * yoni_affective |   -5.63e-03 | 0.07 | [-0.15,  0.14] |   -0.08 | 0.939
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg2, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_affective"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"Yoni Task (Affective)"}\NormalTok{, }\StringTok{"ECG_Rate_Max"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of ECG_Rate_Max by Yoni Task (Affective)"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-12.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_ecg3 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{BES_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg3)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                        | Coefficient |   SE |        95% CI |   t(1017) |     p
## -----------------------------------------------------------------------------------------
## (Intercept)                      |       -0.03 | 4.90 | [-9.63, 9.56] | -7.06e-03 | 0.994
## ConditionSP [social]             |        2.19 | 2.51 | [-2.73, 7.11] |      0.87 | 0.384
## BES_Total                        |        0.08 | 0.07 | [-0.04, 0.21] |      1.29 | 0.198
## ConditionSP [social] * BES_Total |   -6.03e-03 | 0.03 | [-0.07, 0.06] |     -0.18 | 0.859
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg3, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"BES_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"BES Questionnaire"}\NormalTok{, }\StringTok{"ECG_Rate_Max"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of ECG_Rate_Max by BES Questionnaire"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-13.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_ecg4 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Max }\OperatorTok{~}\StringTok{ }\NormalTok{(ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_total) }\OperatorTok{+}\StringTok{ }\NormalTok{BES_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg4)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |   SE |         95% CI | t(1016) |     p
## -----------------------------------------------------------------------------------------
## (Intercept)                       |        8.17 | 7.40 | [-6.33, 22.66] |    1.10 | 0.269
## ConditionSP [social]              |        2.09 | 3.26 | [-4.30,  8.48] |    0.64 | 0.522
## yoni_total                        |       -0.10 | 0.07 | [-0.25,  0.04] |   -1.39 | 0.164
## BES_Total                         |        0.09 | 0.06 | [-0.03,  0.21] |    1.46 | 0.145
## ConditionSP [social] * yoni_total |   -4.01e-03 | 0.04 | [-0.08,  0.07] |   -0.10 | 0.916
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg4, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{, }\StringTok{"BES_Total"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-14.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#TOM Hypothesis 1C: ECG_Rate_Max -> SRP3}
\NormalTok{model_ecg5 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg5)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |   SE |         95% CI | t(1017) |     p
## -----------------------------------------------------------------------------------------
## (Intercept)                       |        5.76 | 3.55 | [-1.19, 12.71] |    1.62 | 0.105
## ConditionSP [social]              |        2.65 | 1.75 | [-0.78,  6.07] |    1.51 | 0.130
## SRP3_Total                        |    3.20e-03 | 0.02 | [-0.04,  0.05] |    0.13 | 0.896
## ConditionSP [social] * SRP3_Total |   -6.34e-03 | 0.01 | [-0.03,  0.02] |   -0.52 | 0.601
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg5, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3 Inventory"}\NormalTok{, }\StringTok{"ECG_Rate_Max"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of ECG_Rate_Max by SRP3 Inventory"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-15.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_ecg6 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_ELS }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)  }\CommentTok{#explorative}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg6)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                       | Coefficient |   SE |         95% CI | t(1017) |     p
## ---------------------------------------------------------------------------------------
## (Intercept)                     |        4.48 | 3.77 | [-2.91, 11.87] |    1.19 | 0.235
## ConditionSP [social]            |        5.79 | 1.83 | [ 2.21,  9.37] |    3.17 | 0.002
## SRP3_ELS                        |        0.04 | 0.09 | [-0.14,  0.22] |    0.47 | 0.639
## ConditionSP [social] * SRP3_ELS |       -0.10 | 0.04 | [-0.19, -0.01] |   -2.24 | 0.025
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg6, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_ELS"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3 (Erratic Life Style)"}\NormalTok{, }\StringTok{"ECG_Rate_Max"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of ECG_Rate_Max by SRP3 - ELS"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-16.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Interoception Hypothesis 2A: ECG_Rate_Max -> HCT/MAIA}
\NormalTok{model_ecg7 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{HCT_Accuracy }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg7)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                           | Coefficient |   SE |          95% CI | t(1017) |     p
## --------------------------------------------------------------------------------------------
## (Intercept)                         |       11.69 | 9.24 | [ -6.43, 29.80] |    1.26 | 0.206
## ConditionSP [social]                |       -3.51 | 4.57 | [-12.47,  5.45] |   -0.77 | 0.442
## HCT_Accuracy                        |       -5.92 | 9.98 | [-25.48, 13.63] |   -0.59 | 0.553
## ConditionSP [social] * HCT_Accuracy |        5.69 | 4.94 | [ -3.99, 15.37] |    1.15 | 0.249
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg7, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"HCT_Accuracy"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"HCT Accuracy"}\NormalTok{, }\StringTok{"ECG_Rate_Max"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of ECG_Rate_Max by HCT Accuracy"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-17.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_ecg8 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{MAIA_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg8)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |   SE |        95% CI | t(1017) |     p
## ----------------------------------------------------------------------------------------
## (Intercept)                       |       -0.53 | 3.14 | [-6.69, 5.63] |   -0.17 | 0.866
## ConditionSP [social]              |        3.97 | 1.65 | [ 0.73, 7.21] |    2.40 | 0.016
## MAIA_Total                        |        0.32 | 0.15 | [ 0.03, 0.60] |    2.18 | 0.029
## ConditionSP [social] * MAIA_Total |       -0.10 | 0.08 | [-0.25, 0.05] |   -1.37 | 0.171
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg8, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"MAIA_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"MAIA2"}\NormalTok{, }\StringTok{"ECG_Rate_Max"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of ECG_Rate_Max by MAIA2"}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-18.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_ecg9 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Max }\OperatorTok{~}\StringTok{ }\NormalTok{(ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{HCT_Accuracy) }\OperatorTok{+}\StringTok{ }\NormalTok{HCT_Confidence }\OperatorTok{+}\StringTok{ }\NormalTok{MAIA_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg9)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                           | Coefficient |   SE |          95% CI | t(1015) |     p
## --------------------------------------------------------------------------------------------
## (Intercept)                         |        8.62 | 9.21 | [ -9.43, 26.67] |    0.94 | 0.349
## ConditionSP [social]                |       -3.56 | 4.57 | [-12.52,  5.40] |   -0.78 | 0.436
## HCT_Accuracy                        |       -8.46 | 9.74 | [-27.56, 10.64] |   -0.87 | 0.385
## HCT_Confidence                      |        1.21 | 2.42 | [ -3.54,  5.95] |    0.50 | 0.617
## MAIA_Total                          |        0.23 | 0.17 | [ -0.11,  0.57] |    1.32 | 0.188
## ConditionSP [social] * HCT_Accuracy |        5.74 | 4.94 | [ -3.94, 15.42] |    1.16 | 0.245
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg9, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"HCT_Accuracy"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-19.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Interoception Hypothesis 2C: ECG_Rate_Max -> SRP3_PRI}
\NormalTok{model_ecg10 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_CA }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg10)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                      | Coefficient |   SE |         95% CI | t(1017) |     p
## --------------------------------------------------------------------------------------
## (Intercept)                    |        7.53 | 2.57 | [ 2.49, 12.57] |    2.93 | 0.003
## ConditionSP [social]           |        1.84 | 1.28 | [-0.67,  4.34] |    1.44 | 0.151
## SRP3_CA                        |       -0.03 | 0.07 | [-0.16,  0.09] |   -0.53 | 0.599
## ConditionSP [social] * SRP3_CA |   -2.45e-03 | 0.03 | [-0.07,  0.06] |   -0.07 | 0.941
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg10, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_CA"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{), }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3 (PRI) Inventory"}\NormalTok{, }\StringTok{"ECG_Rate_Max"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Predicted Values of ECG_Rate_Max by SRP3 (PRI) "}\NormalTok{, }\DataTypeTok{legend.title =} \StringTok{"Condition"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-20.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#ONLY CA was showing good results}

\CommentTok{#ECG_RATE_MIN}
\CommentTok{#TOM Hypothesis 1A: ECG_Rate_Min -> YONI/BES}
\NormalTok{model_ecg1a <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Min }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg1a)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |   SE |          95% CI | t(1017) |     p
## ------------------------------------------------------------------------------------------
## (Intercept)                       |      -10.13 | 4.34 | [-18.65, -1.61] |   -2.33 | 0.020
## ConditionSP [social]              |       -3.46 | 3.65 | [-10.62,  3.69] |   -0.95 | 0.342
## yoni_total                        |        0.05 | 0.05 | [ -0.05,  0.15] |    1.03 | 0.305
## ConditionSP [social] * yoni_total |        0.05 | 0.04 | [ -0.03,  0.14] |    1.21 | 0.225
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg1a, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-21.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_ecg2a <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Min }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_affective }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)  }\CommentTok{#explorative}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg2a)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                             | Coefficient |   SE |         95% CI | t(1017) |     p
## ---------------------------------------------------------------------------------------------
## (Intercept)                           |       -7.05 | 4.32 | [-15.51, 1.41] |   -1.63 | 0.102
## ConditionSP [social]                  |       -2.06 | 3.47 | [ -8.87, 4.75] |   -0.59 | 0.552
## yoni_affective                        |        0.03 | 0.10 | [ -0.17, 0.23] |    0.32 | 0.751
## ConditionSP [social] * yoni_affective |        0.07 | 0.08 | [ -0.09, 0.23] |    0.87 | 0.384
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg2a, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_affective"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-22.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_ecg3a <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Min }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{BES_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg3a)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                        | Coefficient |   SE |         95% CI | t(1017) |     p
## ----------------------------------------------------------------------------------------
## (Intercept)                      |       -6.57 | 3.50 | [-13.44, 0.29] |   -1.88 | 0.061
## ConditionSP [social]             |        2.26 | 2.81 | [ -3.25, 7.77] |    0.80 | 0.421
## BES_Total                        |        0.01 | 0.05 | [ -0.08, 0.10] |    0.26 | 0.798
## ConditionSP [social] * BES_Total |       -0.02 | 0.04 | [ -0.09, 0.06] |   -0.47 | 0.637
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg3a, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"BES_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-23.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_ecg4a <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Min }\OperatorTok{~}\StringTok{ }\NormalTok{(ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_total) }\OperatorTok{+}\StringTok{ }\NormalTok{BES_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg4a)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |   SE |         95% CI | t(1016) |     p
## -----------------------------------------------------------------------------------------
## (Intercept)                       |       -9.85 | 5.16 | [-19.97, 0.26] |   -1.91 | 0.056
## ConditionSP [social]              |       -3.46 | 3.65 | [-10.61, 3.69] |   -0.95 | 0.343
## yoni_total                        |        0.05 | 0.05 | [ -0.05, 0.15] |    1.02 | 0.309
## BES_Total                         |   -4.45e-03 | 0.04 | [ -0.09, 0.08] |   -0.11 | 0.916
## ConditionSP [social] * yoni_total |        0.05 | 0.04 | [ -0.03, 0.14] |    1.21 | 0.225
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg4a, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{, }\StringTok{"BES_Total"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-24.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#TOM Hypothesis 1C: ECG_Rate_Min -> SRP3}
\NormalTok{model_ecg5a <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Min }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg5a)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |   SE |          95% CI | t(1017) |     p
## ------------------------------------------------------------------------------------------
## (Intercept)                       |       -7.05 | 2.41 | [-11.78, -2.33] |   -2.92 | 0.003
## ConditionSP [social]              |       -1.05 | 1.96 | [ -4.89,  2.78] |   -0.54 | 0.590
## SRP3_Total                        |    9.57e-03 | 0.02 | [ -0.02,  0.04] |    0.57 | 0.566
## ConditionSP [social] * SRP3_Total |        0.01 | 0.01 | [ -0.01,  0.04] |    1.04 | 0.299
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg5a, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-25.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_ecg6a <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Min }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_ELS }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)  }\CommentTok{#explorative}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg6a)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                       | Coefficient |   SE |          95% CI | t(1017) |     p
## ----------------------------------------------------------------------------------------
## (Intercept)                     |       -6.45 | 2.60 | [-11.55, -1.35] |   -2.48 | 0.013
## ConditionSP [social]            |        1.82 | 2.05 | [ -2.20,  5.84] |    0.89 | 0.375
## SRP3_ELS                        |        0.02 | 0.06 | [ -0.11,  0.14] |    0.30 | 0.765
## ConditionSP [social] * SRP3_ELS |       -0.02 | 0.05 | [ -0.12,  0.08] |   -0.43 | 0.666
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg6a, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_ELS"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-26.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Interoception Hypothesis 2A: ECG_Rate_Min -> HCT/MAIA}
\NormalTok{model_ecg7a <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Min }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{HCT_Accuracy }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg7a)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                           | Coefficient |   SE |          95% CI | t(1017) |     p
## --------------------------------------------------------------------------------------------
## (Intercept)                         |      -13.08 | 6.02 | [-24.88, -1.28] |   -2.17 | 0.030
## ConditionSP [social]                |       -6.86 | 5.12 | [-16.89,  3.17] |   -1.34 | 0.180
## HCT_Accuracy                        |        8.00 | 6.50 | [ -4.74, 20.74] |    1.23 | 0.218
## ConditionSP [social] * HCT_Accuracy |        8.45 | 5.53 | [ -2.38, 19.28] |    1.53 | 0.126
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg7a, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"HCT_Accuracy"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-27.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_ecg8a <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Min }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{MAIA_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg8a)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |   SE |         95% CI | t(1017) |     p
## -----------------------------------------------------------------------------------------
## (Intercept)                       |       -5.36 | 2.31 | [-9.89, -0.83] |   -2.32 | 0.020
## ConditionSP [social]              |       -0.06 | 1.85 | [-3.70,  3.57] |   -0.04 | 0.972
## MAIA_Total                        |       -0.02 | 0.11 | [-0.23,  0.19] |   -0.15 | 0.884
## ConditionSP [social] * MAIA_Total |        0.05 | 0.09 | [-0.12,  0.22] |    0.55 | 0.579
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg8, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"MAIA_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-28.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_ecg9a <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Min }\OperatorTok{~}\StringTok{ }\NormalTok{(ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{HCT_Accuracy) }\OperatorTok{+}\StringTok{ }\NormalTok{HCT_Confidence }\OperatorTok{+}\StringTok{ }\NormalTok{MAIA_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg9a)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                           | Coefficient |   SE |          95% CI | t(1015) |     p
## --------------------------------------------------------------------------------------------
## (Intercept)                         |      -14.32 | 5.96 | [-26.02, -2.63] |   -2.40 | 0.016
## ConditionSP [social]                |       -6.80 | 5.12 | [-16.82,  3.23] |   -1.33 | 0.184
## HCT_Accuracy                        |        8.39 | 6.33 | [ -4.02, 20.81] |    1.33 | 0.185
## HCT_Confidence                      |       -3.04 | 1.46 | [ -5.91, -0.18] |   -2.08 | 0.037
## MAIA_Total                          |        0.10 | 0.11 | [ -0.10,  0.31] |    0.99 | 0.322
## ConditionSP [social] * HCT_Accuracy |        8.38 | 5.53 | [ -2.45, 19.21] |    1.52 | 0.129
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg9, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"HCT_Accuracy"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-29.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Interoception Hypothesis 2C: ECG_Rate_Min -> SRP3_PRI}
\NormalTok{model_ecg10a <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(ECG_Rate_Min }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_PRI }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df2)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_ecg10a)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                       | Coefficient |   SE |          95% CI | t(1017) |     p
## ----------------------------------------------------------------------------------------
## (Intercept)                     |       -6.86 | 2.08 | [-10.94, -2.77] |   -3.29 | 0.001
## ConditionSP [social]            |       -0.84 | 1.69 | [ -4.16,  2.48] |   -0.50 | 0.620
## SRP3_PRI                        |        0.01 | 0.03 | [ -0.04,  0.07] |    0.57 | 0.567
## ConditionSP [social] * SRP3_PRI |        0.02 | 0.02 | [ -0.02,  0.06] |    1.08 | 0.282
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_ecg10a, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_PRI"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-30.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#RESPIRATION PHYSIO ANALYSIS}

\NormalTok{df3 <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{participant =} \KeywordTok{as.factor}\NormalTok{(participant),}
         \DataTypeTok{ConditionSP =} \KeywordTok{as.factor}\NormalTok{(ConditionSP)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(truthfulness }\OperatorTok{==}\StringTok{ "LIE"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(Inclusion2 }\OperatorTok{!=}\StringTok{ "0"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(participant }\OperatorTok{!=}\StringTok{ "22"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{filter}\NormalTok{(Condition }\OperatorTok{==}\StringTok{ "C"}\NormalTok{)}
\CommentTok{#  filter(participant != "23") %>% }
  \CommentTok{# filter(participant != "30") %>% }
  \CommentTok{# filter(#participant != "12",            #try keep 15}
  \CommentTok{#        participant != "15") %>% }

\CommentTok{#RSP_Amplitude_Max}
\CommentTok{#TOM Hypothesis 1A: RSP_Amplitude_Max -> YONI/BES}
\NormalTok{model_rsp1 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(RSP_Amplitude_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df3)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_rsp1)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |    SE |            95% CI | t(1054) |     p
## ---------------------------------------------------------------------------------------------
## (Intercept)                       |      175.33 | 91.45 | [  -3.90, 354.57] |    1.92 | 0.055
## ConditionSP [social]              |       30.10 | 69.56 | [-106.23, 166.44] |    0.43 | 0.665
## yoni_total                        |       -0.93 |  1.07 | [  -3.02,   1.17] |   -0.86 | 0.388
## ConditionSP [social] * yoni_total |       -0.59 |  0.82 | [  -2.19,   1.01] |   -0.73 | 0.467
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_rsp1, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-31.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_rsp2 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(RSP_Amplitude_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_affective }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df3)  }\CommentTok{#explorative}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_rsp2)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                             | Coefficient |    SE |            95% CI | t(1054) |     p
## -------------------------------------------------------------------------------------------------
## (Intercept)                           |      196.30 | 87.87 | [  24.07, 368.53] |    2.23 | 0.025
## ConditionSP [social]                  |       -5.99 | 66.43 | [-136.19, 124.21] |   -0.09 | 0.928
## yoni_affective                        |       -2.38 |  2.09 | [  -6.48,   1.71] |   -1.14 | 0.254
## ConditionSP [social] * yoni_affective |       -0.34 |  1.58 | [  -3.44,   2.76] |   -0.22 | 0.829
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_rsp2, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_affective"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-32.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_rsp3 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(RSP_Amplitude_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{BES_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df3)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_rsp3)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                        | Coefficient |    SE |            95% CI | t(1054) |     p
## --------------------------------------------------------------------------------------------
## (Intercept)                      |      145.27 | 71.70 | [   4.74, 285.80] |    2.03 | 0.043
## ConditionSP [social]             |       -2.13 | 53.75 | [-107.48, 103.22] |   -0.04 | 0.968
## BES_Total                        |       -0.66 |  0.97 | [  -2.55,   1.23] |   -0.68 | 0.494
## ConditionSP [social] * BES_Total |       -0.25 |  0.72 | [  -1.67,   1.17] |   -0.34 | 0.734
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_rsp3, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"BES_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-33.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_rsp4 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(RSP_Amplitude_Max }\OperatorTok{~}\StringTok{ }\NormalTok{(ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_total) }\OperatorTok{+}\StringTok{ }\NormalTok{BES_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df3)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_rsp4)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |     SE |            95% CI | t(1053) |     p
## ----------------------------------------------------------------------------------------------
## (Intercept)                       |      219.28 | 108.36 | [   6.90, 431.67] |    2.02 | 0.043
## ConditionSP [social]              |       29.97 |  69.56 | [-106.37, 166.31] |    0.43 | 0.667
## yoni_total                        |       -0.85 |   1.08 | [  -2.97,   1.27] |   -0.79 | 0.432
## BES_Total                         |       -0.68 |   0.89 | [  -2.43,   1.06] |   -0.77 | 0.443
## ConditionSP [social] * yoni_total |       -0.59 |   0.82 | [  -2.19,   1.01] |   -0.73 | 0.468
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_rsp4, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{, }\StringTok{"BES_Total"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-34.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#TOM Hypothesis 1C: RSP_Amplitude_Max -> SRP3}
\NormalTok{model_rsp5 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(RSP_Amplitude_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df3)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_rsp5)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |    SE |            95% CI | t(1054) |     p
## ---------------------------------------------------------------------------------------------
## (Intercept)                       |      116.70 | 49.56 | [  19.56, 213.84] |    2.35 | 0.019
## ConditionSP [social]              |      -39.62 | 36.48 | [-111.11,  31.88] |   -1.09 | 0.277
## SRP3_Total                        |       -0.14 |  0.34 | [  -0.82,   0.53] |   -0.41 | 0.680
## ConditionSP [social] * SRP3_Total |        0.14 |  0.25 | [  -0.36,   0.64] |    0.54 | 0.591
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_rsp5, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-35.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_rsp6 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(RSP_Amplitude_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_ELS }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df3)  }\CommentTok{#explorative}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_rsp6)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                       | Coefficient |    SE |           95% CI | t(1054) |     p
## ------------------------------------------------------------------------------------------
## (Intercept)                     |       97.36 | 49.30 | [  0.72, 193.99] |    1.97 | 0.048
## ConditionSP [social]            |       29.61 | 36.10 | [-41.14, 100.36] |    0.82 | 0.412
## SRP3_ELS                        |       -0.02 |  1.21 | [ -2.39,   2.36] |   -0.01 | 0.989
## ConditionSP [social] * SRP3_ELS |       -1.25 |  0.89 | [ -2.99,   0.49] |   -1.40 | 0.160
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_rsp6, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_ELS"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-36.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Interoception Hypothesis 2A: RSP_Amplitude_Max -> HCT/MAIA}
\NormalTok{model_rsp7 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(RSP_Amplitude_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{HCT_Accuracy }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df3)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_rsp7)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                           | Coefficient |     SE |            95% CI | t(1054) |     p
## ------------------------------------------------------------------------------------------------
## (Intercept)                         |      128.58 | 133.18 | [-132.46, 389.61] |    0.97 | 0.334
## ConditionSP [social]                |      -82.66 |  97.94 | [-274.61, 109.29] |   -0.84 | 0.399
## HCT_Accuracy                        |      -34.61 | 143.82 | [-316.50, 247.28] |   -0.24 | 0.810
## ConditionSP [social] * HCT_Accuracy |       67.52 | 105.79 | [-139.84, 274.87] |    0.64 | 0.523
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_rsp7, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"HCT_Accuracy"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-37.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_rsp8 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(RSP_Amplitude_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{MAIA_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df3)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_rsp8)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |    SE |            95% CI | t(1054) |     p
## ---------------------------------------------------------------------------------------------
## (Intercept)                       |       66.92 | 43.72 | [ -18.77, 152.60] |    1.53 | 0.126
## ConditionSP [social]              |      -36.44 | 32.79 | [-100.71,  27.82] |   -1.11 | 0.266
## MAIA_Total                        |        1.38 |  1.99 | [  -2.52,   5.27] |    0.69 | 0.489
## ConditionSP [social] * MAIA_Total |        0.75 |  1.49 | [  -2.17,   3.67] |    0.50 | 0.615
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_rsp8, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"MAIA_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-38.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_rsp9 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(RSP_Amplitude_Max }\OperatorTok{~}\StringTok{ }\NormalTok{(ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{HCT_Accuracy) }\OperatorTok{+}\StringTok{ }\NormalTok{HCT_Confidence }\OperatorTok{+}\StringTok{ }\NormalTok{MAIA_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df3)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_rsp9)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                           | Coefficient |     SE |            95% CI | t(1052) |     p
## ------------------------------------------------------------------------------------------------
## (Intercept)                         |      116.25 | 137.99 | [-154.19, 386.70] |    0.84 | 0.400
## ConditionSP [social]                |      -83.47 |  97.94 | [-275.43, 108.49] |   -0.85 | 0.394
## HCT_Accuracy                        |      -51.98 | 146.34 | [-338.80, 234.84] |   -0.36 | 0.722
## HCT_Confidence                      |       24.61 |  35.10 | [ -44.18,  93.39] |    0.70 | 0.483
## MAIA_Total                          |        0.80 |   2.37 | [  -3.85,   5.44] |    0.34 | 0.736
## ConditionSP [social] * HCT_Accuracy |       68.40 | 105.80 | [-138.96, 275.76] |    0.65 | 0.518
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_rsp9, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"HCT_Accuracy"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-39.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Interoception Hypothesis 2C: RSP_Amplitude_Max -> SRP3_PRI}
\NormalTok{model_rsp10 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(RSP_Amplitude_Max }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_PRI }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df3)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_rsp10)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                       | Coefficient |    SE |            95% CI | t(1054) |     p
## -------------------------------------------------------------------------------------------
## (Intercept)                     |      118.83 | 43.81 | [  32.96, 204.69] |    2.71 | 0.007
## ConditionSP [social]            |      -65.16 | 32.19 | [-128.25,  -2.07] |   -2.02 | 0.043
## SRP3_PRI                        |       -0.28 |  0.54 | [  -1.34,   0.78] |   -0.52 | 0.604
## ConditionSP [social] * SRP3_PRI |        0.57 |  0.40 | [  -0.21,   1.35] |    1.42 | 0.155
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_rsp10, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_PRI"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-40.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{  df4 <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{participant =} \KeywordTok{as.factor}\NormalTok{(participant),}
         \DataTypeTok{ConditionSP =} \KeywordTok{as.factor}\NormalTok{(ConditionSP)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(truthfulness }\OperatorTok{==}\StringTok{ "LIE"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(Inclusion2 }\OperatorTok{!=}\StringTok{ "0"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(participant }\OperatorTok{!=}\StringTok{ "22"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(participant }\OperatorTok{!=}\StringTok{ "4"}\NormalTok{,}
\NormalTok{         participant }\OperatorTok{!=}\StringTok{ "5"}\NormalTok{,}
\NormalTok{         participant }\OperatorTok{!=}\StringTok{ "10"}\NormalTok{,}
\NormalTok{         participant }\OperatorTok{!=}\StringTok{ "12"}\NormalTok{,}
\NormalTok{         participant }\OperatorTok{!=}\StringTok{ "16"}\NormalTok{,}
\NormalTok{         participant }\OperatorTok{!=}\StringTok{ "23"}\NormalTok{,}
\NormalTok{         participant }\OperatorTok{!=}\StringTok{ "27"}\NormalTok{,}
\NormalTok{         participant }\OperatorTok{!=}\StringTok{ "29"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(Condition }\OperatorTok{==}\StringTok{ "C"}\NormalTok{)}

\CommentTok{#  filter(participant != "23") %>% }
\CommentTok{#  filter(participant != "30") %>% }

\CommentTok{#EDA_SCR}
\CommentTok{#TOM Hypothesis 1A: EDA_SCR -> YONI/BES}
\NormalTok{model_eda1 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(EDA_SCR }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df4)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_eda1)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |       SE |        95% CI | t(766) |     p
## -------------------------------------------------------------------------------------------
## (Intercept)                       |       -0.29 |     0.65 | [-1.56, 0.97] |  -0.45 | 0.651
## ConditionSP [social]              |        0.65 |     0.36 | [-0.06, 1.37] |   1.79 | 0.074
## yoni_total                        |    6.42e-03 | 7.54e-03 | [-0.01, 0.02] |   0.85 | 0.394
## ConditionSP [social] * yoni_total |   -4.31e-03 | 4.26e-03 | [-0.01, 0.00] |  -1.01 | 0.312
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_eda1, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-41.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_eda2 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(EDA_SCR }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_affective }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df4)  }\CommentTok{#explorative}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_eda2)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                             | Coefficient |       SE |        95% CI | t(766) |     p
## -----------------------------------------------------------------------------------------------
## (Intercept)                           |       -0.33 |     0.57 | [-1.44, 0.79] |  -0.58 | 0.562
## ConditionSP [social]                  |        0.89 |     0.32 | [ 0.27, 1.51] |   2.79 | 0.005
## yoni_affective                        |        0.01 |     0.01 | [-0.01, 0.04] |   1.03 | 0.301
## ConditionSP [social] * yoni_affective |       -0.01 | 7.57e-03 | [-0.03, 0.00] |  -1.91 | 0.056
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_eda2, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_affective"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-42.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_eda3 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(EDA_SCR }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{BES_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df4)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_eda3)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                        | Coefficient |       SE |        95% CI | t(766) |     p
## ------------------------------------------------------------------------------------------
## (Intercept)                      |        0.35 |     0.42 | [-0.47, 1.16] |   0.83 | 0.406
## ConditionSP [social]             |        0.05 |     0.23 | [-0.41, 0.51] |   0.22 | 0.823
## BES_Total                        |   -1.20e-03 | 5.51e-03 | [-0.01, 0.01] |  -0.22 | 0.827
## ConditionSP [social] * BES_Total |    3.12e-03 | 3.11e-03 | [ 0.00, 0.01] |   1.00 | 0.316
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_eda3, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"BES_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-43.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_eda4 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(EDA_SCR }\OperatorTok{~}\StringTok{ }\NormalTok{(ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{yoni_total) }\OperatorTok{+}\StringTok{ }\NormalTok{BES_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df4)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_eda4)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |       SE |        95% CI | t(765) |     p
## -------------------------------------------------------------------------------------------
## (Intercept)                       |       -0.29 |     0.73 | [-1.71, 1.14] |  -0.39 | 0.694
## ConditionSP [social]              |        0.65 |     0.36 | [-0.06, 1.37] |   1.79 | 0.074
## yoni_total                        |    6.45e-03 | 7.84e-03 | [-0.01, 0.02] |   0.82 | 0.410
## BES_Total                         |   -1.32e-04 | 5.44e-03 | [-0.01, 0.01] |  -0.02 | 0.981
## ConditionSP [social] * yoni_total |   -4.31e-03 | 4.26e-03 | [-0.01, 0.00] |  -1.01 | 0.312
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_eda4, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"yoni_total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{, }\StringTok{"BES_Total"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-44.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#TOM Hypothesis 1C: EDA_SCR -> SRP3}
\NormalTok{model_eda5 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(EDA_SCR }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df4)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_eda5)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |       SE |        95% CI | t(766) |     p
## -------------------------------------------------------------------------------------------
## (Intercept)                       |        0.09 |     0.31 | [-0.51, 0.69] |   0.28 | 0.776
## ConditionSP [social]              |        0.26 |     0.17 | [-0.08, 0.60] |   1.52 | 0.128
## SRP3_Total                        |    1.22e-03 | 2.18e-03 | [ 0.00, 0.01] |   0.56 | 0.576
## ConditionSP [social] * SRP3_Total |    1.65e-04 | 1.23e-03 | [ 0.00, 0.00] |   0.13 | 0.893
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_eda5, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-45.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_eda6 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(EDA_SCR }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_ELS }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df4)  }\CommentTok{#explorative}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_eda6)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                       | Coefficient |       SE |        95% CI | t(766) |     p
## -----------------------------------------------------------------------------------------
## (Intercept)                     |        0.37 |     0.29 | [-0.20, 0.94] |   1.26 | 0.206
## ConditionSP [social]            |        0.17 |     0.16 | [-0.15, 0.49] |   1.05 | 0.293
## SRP3_ELS                        |   -2.90e-03 | 7.28e-03 | [-0.02, 0.01] |  -0.40 | 0.690
## ConditionSP [social] * SRP3_ELS |    2.89e-03 | 4.07e-03 | [-0.01, 0.01] |   0.71 | 0.477
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_eda6, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_ELS"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-46.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Interoception Hypothesis 2A: EDA_SCR -> HCT/MAIA}
\NormalTok{model_eda7 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(EDA_SCR }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{HCT_Accuracy }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df4)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_eda7)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                           | Coefficient |   SE |         95% CI | t(766) |      p
## -------------------------------------------------------------------------------------------
## (Intercept)                         |       -0.06 | 0.83 | [-1.70,  1.57] |  -0.07 | 0.942 
## ConditionSP [social]                |        1.78 | 0.47 | [ 0.86,  2.71] |   3.78 | < .001
## HCT_Accuracy                        |        0.34 | 0.90 | [-1.43,  2.11] |   0.38 | 0.705 
## ConditionSP [social] * HCT_Accuracy |       -1.63 | 0.51 | [-2.63, -0.63] |  -3.18 | 0.001
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_eda7, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"HCT_Accuracy"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-47.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_eda8 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(EDA_SCR }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{MAIA_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df4)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_eda8)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                         | Coefficient |       SE |         95% CI | t(766) |      p
## ---------------------------------------------------------------------------------------------
## (Intercept)                       |       -0.04 |     0.25 | [-0.53,  0.45] |  -0.14 | 0.885 
## ConditionSP [social]              |        0.64 |     0.14 | [ 0.36,  0.91] |   4.48 | < .001
## MAIA_Total                        |        0.01 |     0.01 | [-0.01,  0.04] |   1.20 | 0.232 
## ConditionSP [social] * MAIA_Total |       -0.02 | 6.58e-03 | [-0.03,  0.00] |  -2.53 | 0.011
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_eda8, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"MAIA_Total"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-48.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_eda9 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(EDA_SCR }\OperatorTok{~}\StringTok{ }\NormalTok{(ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{HCT_Accuracy) }\OperatorTok{+}\StringTok{ }\NormalTok{HCT_Confidence }\OperatorTok{+}\StringTok{ }\NormalTok{MAIA_Total }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df4)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_eda9)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                           | Coefficient |   SE |         95% CI | t(764) |      p
## -------------------------------------------------------------------------------------------
## (Intercept)                         |       -0.21 | 0.89 | [-1.96,  1.53] |  -0.24 | 0.810 
## ConditionSP [social]                |        1.78 | 0.47 | [ 0.86,  2.71] |   3.78 | < .001
## HCT_Accuracy                        |        0.42 | 0.95 | [-1.44,  2.27] |   0.44 | 0.660 
## HCT_Confidence                      |        0.15 | 0.23 | [-0.29,  0.59] |   0.67 | 0.504 
## MAIA_Total                          |    1.09e-03 | 0.01 | [-0.03,  0.03] |   0.08 | 0.935 
## ConditionSP [social] * HCT_Accuracy |       -1.62 | 0.51 | [-2.62, -0.62] |  -3.18 | 0.001
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_eda9, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"HCT_Accuracy"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-49.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Interoception Hypothesis 2C: EDA_SCR -> SRP3_PRI}
\NormalTok{model_eda10 <-}\StringTok{ }\NormalTok{lme4}\OperatorTok{::}\KeywordTok{lmer}\NormalTok{(EDA_SCR }\OperatorTok{~}\StringTok{ }\NormalTok{ConditionSP }\OperatorTok{*}\StringTok{ }\NormalTok{SRP3_PRI }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{participant), }\DataTypeTok{data =}\NormalTok{ df4)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_eda10)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter                       | Coefficient |       SE |        95% CI | t(766) |     p
## -----------------------------------------------------------------------------------------
## (Intercept)                     |       -0.03 |     0.27 | [-0.56, 0.50] |  -0.10 | 0.923
## ConditionSP [social]            |        0.31 |     0.15 | [ 0.00, 0.61] |   1.99 | 0.047
## SRP3_PRI                        |    3.64e-03 | 3.43e-03 | [ 0.00, 0.01] |   1.06 | 0.287
## ConditionSP [social] * SRP3_PRI |   -2.85e-04 | 1.96e-03 | [ 0.00, 0.00] |  -0.15 | 0.884
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_eda10, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{terms =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3_PRI"}\NormalTok{, }\StringTok{"ConditionSP"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-50.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df5 <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }
\KeywordTok{group_by}\NormalTok{(participant) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{summarise_all}\NormalTok{(mean)}

\NormalTok{model_H1 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(yoni_affective }\OperatorTok{~}\StringTok{  }\NormalTok{SRP3_Total, }\DataTypeTok{data =}\NormalTok{ df5)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_H1)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter   | Coefficient |   SE |         95% CI | t(28) |      p
## ------------------------------------------------------------------
## (Intercept) |       42.21 | 4.23 | [33.54, 50.89] |  9.97 | < .001
## SRP3_Total  |   -2.65e-03 | 0.03 | [-0.06,  0.06] | -0.09 | 0.928
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_H1, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3 Inventory"}\NormalTok{, }\StringTok{"Yoni Task (Affective)"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Relationship Between Yoni Task (Affective) and SRP3"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## $SRP3_Total
\end{verbatim}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-51.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_H1a <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(BES_Affective }\OperatorTok{~}\StringTok{  }\NormalTok{SRP3_Total, }\DataTypeTok{data =}\NormalTok{ df5)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_H1a)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter   | Coefficient |   SE |         95% CI | t(28) |      p
## ------------------------------------------------------------------
## (Intercept) |       59.07 | 6.22 | [46.33, 71.81] |  9.50 | < .001
## SRP3_Total  |       -0.15 | 0.04 | [-0.23, -0.06] | -3.44 | 0.002
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_H1a, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3 Inventory"}\NormalTok{, }\StringTok{"BES (Affective)"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Relationship Between BES (Affective) Score and SRP3"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## $SRP3_Total
\end{verbatim}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-52.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_H2 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(HCT_Accuracy }\OperatorTok{~}\StringTok{  }\NormalTok{SRP3_PRI, }\DataTypeTok{data =}\NormalTok{ df5)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_H2)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter   | Coefficient |       SE |        95% CI | t(28) |      p
## ---------------------------------------------------------------------
## (Intercept) |        0.86 |     0.06 | [ 0.74, 0.97] | 15.56 | < .001
## SRP3_PRI    |    8.60e-04 | 6.72e-04 | [ 0.00, 0.00] |  1.28 | 0.211
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_H2, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3 (PRI) Inventory"}\NormalTok{, }\StringTok{"HCT Accuracy"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Relationship Between HCT Accuracy and SRP3 (PRI)"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## $SRP3_PRI
\end{verbatim}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-53.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model_H2 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(MAIA_Total }\OperatorTok{~}\StringTok{  }\NormalTok{SRP3_PRI, }\DataTypeTok{data =}\NormalTok{ df5)}
\NormalTok{parameters}\OperatorTok{::}\KeywordTok{parameters}\NormalTok{(model_H2)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Parameter   | Coefficient |   SE |         95% CI | t(28) |      p
## ------------------------------------------------------------------
## (Intercept) |       25.40 | 3.96 | [17.29, 33.51] |  6.42 | < .001
## SRP3_PRI    |       -0.05 | 0.05 | [-0.15,  0.05] | -0.96 | 0.343
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_model}\NormalTok{(model_H2, }\DataTypeTok{type =} \StringTok{"pred"}\NormalTok{, }\DataTypeTok{axis.title =} \KeywordTok{c}\NormalTok{(}\StringTok{"SRP3 (PRI) Inventory"}\NormalTok{, }\StringTok{"MAIA2"}\NormalTok{), }\DataTypeTok{title =} \StringTok{"Relationship Between MAIA2 and SRP3 (PRI)"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## $SRP3_PRI
\end{verbatim}

\includegraphics{analysis_files/figure-latex/unnamed-chunk-7-54.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{correlation}\OperatorTok{::}\KeywordTok{correlation}\NormalTok{(}\KeywordTok{select}\NormalTok{(df5,}
\NormalTok{         MAIA_Total,}
\NormalTok{         SRP3_PRI),}
  \DataTypeTok{multilevel =}\NormalTok{ F, }\DataTypeTok{p_adjust =} \StringTok{"none"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # Correlation table (pearson-method)
## 
## Parameter1 | Parameter2 |     r |        95% CI | t(28) |     p
## ---------------------------------------------------------------
## MAIA_Total |   SRP3_PRI | -0.18 | [-0.51, 0.19] | -0.96 | 0.343
## 
## p-value adjustment method: none
## Observations: 30
\end{verbatim}

An interaction is present when the effects of one IV on DV change at the
different levels of the second IV. the +ve effect of the HCT\_Accuracy
on the subjective response varies on the different level of the
ConditionSP. The rate of change of HCT\_Accuracy on the subjective
response in the polygraph condition is larger than the rate of change of
HCT\_Accuracy on the subjective response in the social condition.

Interaction EXPLANATION - ConditionSP - differences between social and
poly condition when HCTACCuracy is 0 - HCTAccuracy (poly condition as 0)
- only in polygraph condition, there is a positive effect of
HCT\_Accuracy on sub resp but not significant - interaction -
participants who have a better HCTAccur (interoceptive ability) have
better confidence on their lies in the poly condition compared to social
condition

\#1a: DV: Subjective rating, IV: TOM

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Hone.a4 <- lme4::lmer(subresp ~  yoni_total * BES_Total + (1|participant), data = df3)}
\CommentTok{# parameters::parameters(Hone.a4)}
\CommentTok{# plot_model(Hone.a4, type = "pred", terms = c("yoni_total", "BES_Total"))}
\CommentTok{# }
\CommentTok{# Hone.b4 <- lme4::lmer(subresp ~ yoni_cognitive + yoni_affective + yoni_physical + (1|participant), data = df3)}
\CommentTok{# parameters::parameters(Hone.b4)}
\CommentTok{# plot_model(Hone.b4, type = "pred", terms = c("yoni_cognitive"  + "yoni_affective", "yoni_physical"))}
\CommentTok{# }
\CommentTok{# Hone.c4 <- lme4::lmer(subresp ~  BES_Affective + BES_Cognitive + (1|participant), data = df3)}
\CommentTok{# parameters::parameters(Hone.c4)}
\CommentTok{# plot_model(Hone.c4, type = "pred")}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Hypothesis 1b  }
\CommentTok{# Hone.d <- lm(yoni_physical ~  SRP3_Total, data = des_stat)}
\CommentTok{# parameters::parameters(Hone.d)}
\CommentTok{# plot_model(Hone.d, type = "pred")}
\CommentTok{# }
\CommentTok{# Hone.da <- lm::lmer(BES_Affective ~  SRP3_Total + (1|participant), data = df3)}
\CommentTok{# parameters::parameters(Hone.da)}
\CommentTok{# plot_model(Hone.da, type = "pred")}
\end{Highlighting}
\end{Shaded}

\#Hypothesis 2 ECG\_Rate\_Max, ECG\_Rate\_Min, RSP\_Amplitude\_Max,
EDA\_SCR

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# #Hypothesis 2b  }
\CommentTok{# Htwo.d <- lme4::lmer(HCT_Accuracy ~  SRP3_PRI + (1|participant), data = df3)}
\CommentTok{# parameters::parameters(Htwo.d)}
\CommentTok{# plot_model(Htwo.d, type = "pred")}
\CommentTok{# }
\CommentTok{# Htwo.d <- lm(HCT_Accuracy ~  SRP3_PRI, data = des_stat)}
\CommentTok{# parameters::parameters(Htwo.d)}
\CommentTok{# plot_model(Htwo.d, type = "pred")}
\CommentTok{# }
\CommentTok{# Htwo.da <- lme4::lmer(MAIA3 ~  SRP3_PRI + (1|participant), data = df3)}
\CommentTok{# parameters::parameters(Htwo.da)}
\CommentTok{# plot_model(Htwo.da, type = "pred")}
\end{Highlighting}
\end{Shaded}

\hypertarget{other-analysis}{%
\section{Other Analysis}\label{other-analysis}}

\end{document}

### 2022-10-04 paper/manuscript.Rmd
update

--- 2022-09-19 paper/manuscript_v0.Rmd
@@
 ---
-title: '**The Role of Interoception and Theory of Mind in Deception**'
+title: '**The Heart Lies: The Role of Interoception and Theory of Mind in Deception**'
 shorttitle        : "TITLE"
@@
 
-The data analysis was carried out using R.... [CITE STUFF]. The full reproducible analysis script is available [INSERT LINK].
+The manipulation checks consist of testing whether there is an effect of question phrasing (direct vs.
+indirect), and condition (polygraph *vs.* interrogation), on our 3 outcome variables: the participants' ratings of confidence that their answers (lies *vs.* truths) were convincing, the response time (RT), and the heart rate change associated with the response.
+This analysis was performed using mixed models with the participants and questions both entered as random factors.
+Marginal contrasts analysis was also performed to clarify the differences between conditions.
+To allow for a better quantification of the uncertainty associated with the effects, as well increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework [**ref makowski2019existence**], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).
 
-We implimented a linear mixed-effect model where
+To further counterbalance the low number of participants and maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, theory of mind and interoception).
+We used factor analysis (using the method agreement procedure to estimate the optimal number of dimensions, **REF PARAMETERS PKG**), rather PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained.
+Then, we modelled the relationship between these inter-individual composite scores (the analysis for all the variables is included in Supplementary Materials) and the 3 outcome variables in interaction with the condition (polygraph *vs.* interrogation).
+Finally, we also investigated the relationship between the deception scale traits, and the theory of mind and interoception scores using Bayesian correlations.
 
-From the deception task, there were three dependent variables: confidence, reaction time and heart rate.
-For each dependent variable, we investigated its relationship with theory of mind and interoception abilities as measured by the tests on the previous slide.
-Participant and the specific question asked were added in as random effects, as they are not independent factors.
-For example, certain participants may be more confident in lying unrelated to their theory of mind or interoception abilities, or certain questions may have a longer reaction time
-
-To further build on the model, trials for lies and truths were separated using an embedded model and the interaction between the dependent variable and condition was probed.
-This reveals instances where the effect is greater in one condition, for example a higher total Yoni Task score is correlated with decreased lie confidence, but only in the polygraph condition.
-
-### Data Pre-Processing and Analyses
+The data analysis was carried out using R, the *brms* package [*REF*] and the *easystats* ecosystem **[REFS]**.
+As the full reproducible analysis script and statistical results are available at **[INSERT LINK]**, we will only focus on significant results in the manuscript.
 
@@
 
-INSERT VERY FANCY, VERY PRETTY GRAPHS
+## Manipulation Check
 
-Implicit relationship between dependent variables. Inter-Measure Correlation:
+Compared to truth, lies were rated with less confidence ($\beta=-1.09,~95\%~CI~[-0.94, -1.25],~pd = 100\%$).
+Moreover, lies told in the polygraph condition were rated with less confidence ($\delta=-0.24,~95\%~CI~[-0.10, -0.39],~pd > 99\%$).
+The RT did not differ between truth and lies, but was significantly slower in the polygraph condition ($\beta=0.14,~95\%~CI~[0.03, 0.25],~pd > 99\%$) for both conditions.
+The heart rate was significantly more elevated during lies as compared to truth ($\beta=1.31,~95\%~CI~[2.14, 0.50],~pd > 99.9\%$), and during interrogation as compared to the polygraph condition ($\beta=4.99	,~95\%~CI~[5.82, 4.19],~pd = 100\%$).
 
--   (confident and reaction time) When lying, the faster they answer, the more confident they are.
+The indirect phrasing of the question only had a significant effect on RT ($\beta=0.34,~95\%~CI~[0.23, 0.44],~pd = 100\%$), leading to slower answers, regardless of whether they were lies or truths.
 
--   less confident in lies than truths (expected) Condition interaction, greater effect in polygraph (relying on interoception) likely less intuitive feedback cues??
-Slower in polygraph makes sense if less intuitive
+## Feature Reduction
 
--   (HR and RT) no relationship
+The 3 YONI-task dimensions and the 2 BES traits were combined into a unique factor, labelled *Theory of Mind* (explaining 35.76\% of variance).
+It was loaded by the cognitive (.89), affective (.77), physical (.45) YONI dimension, and the affective (.41) and cognitive (.17) traits of the BES.
 
-TOM correlated with trials in polygraph (interoception), not expected(!) because expected it to correlate with Interrogation
+The 8 MAIA dimensions and the 3 HCT components were reduced to 4 factors (explaining 65.17\% of variance).
+The first factor, labelled *Interoception - Meta* (23.59\%), was loaded primarily by Attention Regulation (.97), Self-regulation (.63), Emotional awareness (.60), and noticing (.49) dimensions of the MAIA and the HCT confidence score (.40).
+The second factor, labelled *Interoception - Listening* (18.54\%), was primarily loaded by the body listening (.92) and trusting (.53) MAIA dimensions, and the awareness (-.60) and confidence (.46) HCT scores.
+The third factor, labelled *Interoception - Focus* (12.07\%), was primarily loaded by MAIA not-distracting (.87), emotional awareness (-.40) and HCT accuracy (.33).
+The fourth factor, labelled *Interoception - Regulation* (10.97\%), was primarily loaded by MAIA not-worrying (.71), HCT accuracy (.61) and MAIA trusting (.40).
+However, due to the interpretation difficulty, we will refer to these dimensions with their main correlates in **Figure 1**.
 
-higher HCT accuracy and MAIA positively correlated with lie confidence in polygraph condition
+## Theory of Mind
 
-No effect for reaction time
+The composite *ToM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67%\%$), specifically in the polygraph condition.
+No significant effect was found heart rate, and no correlation with the deception scale traits.
 
-BES positively correlated with HR,
+## Interoception
 
-HCT accuracy negatively correlated with HR
+The *Meta* interoception score was significantly associated with an increased confidence in lies, specifically in the polygraph condition ($\beta=0.20,~95\%~CI~[0.03, 0.35],~pd = 98.98\%$).
+It was also associated with faster answers for both lies ($\beta=-0.54,~95\%~CI~[-0.93, -0.15],~pd = 99.67\%$) and truths ($\beta=-0.29,~95\%~CI~[-0.63, 0.03],~pd = 96.10%\%$), specifically in the polygraph condition.
+No significant association was found with heart rate.
+
+The *Listening* interoception score was significantly associated with an increased confidence in lies, in the polygraph ($\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%$) and interrogation condition ($\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%$).
+It was also associated with faster answers, particilarly for lies ($\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%$) and truths ($\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%$) in the polygraph condition.
+No significant association was found with heart rate.
+This score also correlated with the deception *Contextuality* trait ($r = 0.50,~95\%~CI~[0.04, 0.64],~BF_{10} = 3.48\%$).
+
+The *Focus* interoception score was significantly associated with an increased confidence in truthful responses in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$) and interrogation condition ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76%\%$).
+No significant association was found with RT or heart rate, but the score correlated with the deception *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$).
+
+The *Regulation* interoception score was significantly associated with an increased confidence in lies in the polygraph ($\beta=0.32,~95\%~CI~[0.14, 0.51],~pd = 99.99\%$) and the interrogation conditions ($\beta=0.18,~95\%~CI~[0.00, 0.36],~pd = 97.42\%$), and with a decreased confidence in truth only in the polygraph condition ($\beta=-0.1,~95\%~CI~[-0.36, 0.01],~pd = 97.16\%$).
+No significant association was found with RT or heart rate.
 

### 2022-10-04 old/questionnaire_BES/BES Code.R

@@ -1,0 +1,250 @@
+#### HP3804 EFA in RStudio =====================================  (stats generated factors)
+# install the following 4 packages before you can run the commands below:
+#foreign is for reading spss
+#psych is for efa
+#gpa rotation is for factor rotation
+#hmisc is for some factor analysis
+install.packages("foreign")
+install.packages("psych")
+install.packages("GPArotation")
+install.packages("Hmisc")
+install.packages("tidyverse")
+install.packages("ggplot2")
+install.packages("bayestestR")
+install.packages("see")
+
+# Load required packages
+library(foreign)
+library(psych)
+library(GPArotation)
+library(Hmisc)
+library(tidyverse)
+library(ggplot2)
+library(bayestestR)
+library(see)
+
+# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
+setwd("  ")
+setwd("~/Desktop/R Testing")
+setwd("C:/Users/gen_3/Desktop/R Testing")
+
+
+#*****BES CODE PROCESSING****
+# read SPSS fa_eg.sav
+# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
+setwd("~/Dropbox/FYP_Jia Rong/R Processing/R Code for BES")
+library(tidyverse)
+mydata <- read.csv('BES_30.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)] 
+
+data <- mydata %>% 
+  as.data.frame() %>%  
+  rename(Q1 = Q3_1,
+       Q2 = Q3_2,
+       Q3 = Q3_3,
+       Q4 = Q3_4,
+       Q5 = Q3_5,
+       Q6 = Q3_6,
+       Q7 = Q3_7,
+       Q8 = Q3_8,
+       Q9 = Q3_9,
+       Q10 = Q3_10,
+       Q11 = Q3_11,
+       Q12 = Q3_12,
+       Q13 = Q3_13,
+       Q14 = Q3_14,
+       Q15 = Q3_15,
+       Q16 = Q3_16,
+       Q17 = Q3_17,
+       Q18 = Q3_18,
+       Q19 = Q3_19,
+       Q20 = Q3_20,
+       ID = Q2) %>% 
[…]

### 2022-10-04 old/questionnaire_LIE/Lie Profiler Code.R

@@ -1,0 +1,301 @@
+#### HP3804 EFA in RStudio =====================================  (stats generated factors)
+# install the following 4 packages before you can run the commands below:
+#foreign is for reading spss
+#psych is for efa
+#gpa rotation is for factor rotation
+#hmisc is for some factor analysis
+install.packages("foreign")
+install.packages("psych")
+install.packages("GPArotation")
+install.packages("Hmisc")
+install.packages("tidyverse")
+install.packages("ggplot2")
+install.packages("bayestestR")
+install.packages("see")
+install.packages("lavaan")
+
+# Load required packages
+library(foreign)
+library(psych)
+library(GPArotation)
+library(Hmisc)
+library(tidyverse)
+library(ggplot2)
+library(bayestestR)
+library(see)
+library(lavaan)
+
+# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
+setwd("  ")
+setwd("~/Desktop/R Testing")
+setwd("C:/Users/gen_3/Desktop/R Testing")
+
+#************LIE Profiler Code Processing***********************************
+# read SPSS fa_eg.sav
+# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
+setwd("~/Dropbox/FYP_Jia Rong/R Processing/R Code for LIE Profiler")
+library(tidyverse)
+mydata <- read.csv('LIE_30.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)] 
+
+data <- mydata %>% 
+  as.data.frame() %>%  
+  rename(LIE_10 = Q1_4,
+         LIE_9 = Q2_4, 
+         LIE_14 = Q3_4,
+         LIE_18 = Q4_4,  
+         LIE_4 = Q5_4, 
+         LIE_5 = Q6_4, 
+         LIE_23 = Q7_4, 
+         LIE_1 = Q8_4, 
+         LIE_41 = Q9_4, 
+         LIE_25 = Q10_1, 
+         LIE_44 = Q11_1, 
+         LIE_34 = Q12_4, 
+         LIE_43 = Q13_4, 
+         LIE_33 = Q14_4, 
+         LIE_42 = Q15_4, 
+         LIE_39 = Q16_4, 
+       LieDay = Q17,
+       LieWeek = Q18)
+
[…]

### 2022-10-04 old/questionnaire_MAIA/MAIA Code.R

@@ -1,0 +1,286 @@
+#### HP3804 EFA in RStudio =====================================  (stats generated factors)
+# install the following 4 packages before you can run the commands below:
+#foreign is for reading spss
+#psych is for efa
+#gpa rotation is for factor rotation
+#hmisc is for some factor analysis
+install.packages("foreign")
+install.packages("psych")
+install.packages("GPArotation")
+install.packages("Hmisc")
+install.packages("tidyverse")
+install.packages("ggplot2")
+install.packages("bayestestR")
+install.packages("see")
+
+# Load required packages
+library(foreign)
+library(psych)
+library(GPArotation)
+library(Hmisc)
+library(tidyverse)
+library(ggplot2)
+library(bayestestR)
+library(see)
+
+# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
+setwd("  ")
+setwd("~/Desktop/R Testing")
+setwd("C:/Users/gen_3/Desktop/R Testing")
+
+
+
+#******MAIA2 CODE PROCESSING**************
+# read SPSS fa_eg.sav
+# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
+setwd("~/Dropbox/FYP_Jia Rong/R Processing/R Code for MAIA2")
+library(tidyverse)
+mydata <- read.csv('MAIA2_30.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)] 
+
+data <- mydata %>% 
+  as.data.frame() %>%  
+  rename(Q1 = Q3_1,
+       Q2 = Q3_2,
+       Q3 = Q3_3,
+       Q4 = Q3_4,
+       Q5 = Q3_5,
+       Q6 = Q3_6,
+       Q7 = Q3_7,
+       Q8 = Q3_8,
+       Q9 = Q3_9,
+       Q10 = Q3_10,
+       Q11 = Q3_11,
+       Q12 = Q3_12,
+       Q13 = Q3_13,
+       Q14 = Q3_14,
+       Q15 = Q3_15,
+       Q16 = Q3_16,
+       Q17 = Q3_17,
+       Q18 = Q3_18,
+       Q19 = Q3_19,
+       Q20 = Q3_20,
+       Q21 = Q4_1,
+       Q22 = Q4_2,
[…]

### 2022-10-04 old/questionnaire_SRP/SRP3 Code.R

@@ -1,0 +1,331 @@
+#### HP3804 EFA in RStudio =====================================  (stats generated factors)
+# install the following 4 packages before you can run the commands below:
+#foreign is for reading spss
+#psych is for efa
+#gpa rotation is for factor rotation
+#hmisc is for some factor analysis
+install.packages("foreign")
+install.packages("psych")
+install.packages("GPArotation")
+install.packages("Hmisc")
+install.packages("tidyverse")
+install.packages("ggplot2")
+install.packages("bayestestR")
+install.packages("see")
+
+# Load required packages
+library(foreign)
+library(psych)
+library(GPArotation)
+library(Hmisc)
+library(tidyverse)
+library(ggplot2)
+library(bayestestR)
+library(see)
+
+# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
+setwd("  ")
+setwd("~/Desktop/R Testing")
+setwd("C:/Users/gen_3/Desktop/R Testing")
+
+
+#********SRP3 CODE PROCESSING*************
+# read SPSS fa_eg.sav
+# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
+setwd("~/Dropbox/FYP_Jia Rong/R Processing/R Code for SRP3")
+library(tidyverse)
+mydata <- read.csv('SRP3_30.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)] 
+
+data <- mydata %>% 
+  as.data.frame() %>%  
+  rename(Q1 = Q3_1,
+       Q2 = Q3_2,
+       Q3 = Q3_3,
+       Q4 = Q3_4,
+       Q5 = Q3_5,
+       Q6 = Q3_6,
+       Q7 = Q3_7,
+       Q8 = Q3_8,
+       Q9 = Q3_9,
+       Q10 = Q3_10,
+       Q11 = Q3_11,
+       Q12 = Q3_12,
+       Q13 = Q3_13,
+       Q14 = Q3_14,
+       Q15 = Q3_15,
+       Q16 = Q3_16,
+       Q17 = Q3_17,
+       Q18 = Q3_18,
+       Q19 = Q3_19,
+       Q20 = Q3_20,
+       Q21 = Q3_21,
+       Q22 = Q3_22,
+       Q23 = Q3_23,
[…]

### 2022-10-04 scripts (old)/questionnaire_SRP/SRP3 Code.R

@@ -1,331 +1,0 @@
-#### HP3804 EFA in RStudio =====================================  (stats generated factors)
-# install the following 4 packages before you can run the commands below:
-#foreign is for reading spss
-#psych is for efa
-#gpa rotation is for factor rotation
-#hmisc is for some factor analysis
-install.packages("foreign")
-install.packages("psych")
-install.packages("GPArotation")
-install.packages("Hmisc")
-install.packages("tidyverse")
-install.packages("ggplot2")
-install.packages("bayestestR")
-install.packages("see")
-
-# Load required packages
-library(foreign)
-library(psych)
-library(GPArotation)
-library(Hmisc)
-library(tidyverse)
-library(ggplot2)
-library(bayestestR)
-library(see)
-
-# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
-setwd("  ")
-setwd("~/Desktop/R Testing")
-setwd("C:/Users/gen_3/Desktop/R Testing")
-
-
-#********SRP3 CODE PROCESSING*************
-# read SPSS fa_eg.sav
-# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
-setwd("~/Dropbox/FYP_Jia Rong/R Processing/R Code for SRP3")
-library(tidyverse)
-mydata <- read.csv('SRP3_30.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)] 
-
-data <- mydata %>% 
-  as.data.frame() %>%  
-  rename(Q1 = Q3_1,
-       Q2 = Q3_2,
-       Q3 = Q3_3,
-       Q4 = Q3_4,
-       Q5 = Q3_5,
-       Q6 = Q3_6,
-       Q7 = Q3_7,
-       Q8 = Q3_8,
-       Q9 = Q3_9,
-       Q10 = Q3_10,
-       Q11 = Q3_11,
-       Q12 = Q3_12,
-       Q13 = Q3_13,
-       Q14 = Q3_14,
-       Q15 = Q3_15,
-       Q16 = Q3_16,
-       Q17 = Q3_17,
-       Q18 = Q3_18,
-       Q19 = Q3_19,
-       Q20 = Q3_20,
-       Q21 = Q3_21,
-       Q22 = Q3_22,
-       Q23 = Q3_23,
[…]

### 2022-10-04 scripts (old)/yoni/Yoni task Response Code.R

@@ -1,217 +1,0 @@
-#### HP3804 EFA in RStudio =====================================  (stats generated factors)
-# install the following 4 packages before you can run the commands below:
-#foreign is for reading spss
-#psych is for efa
-#gpa rotation is for factor rotation
-#hmisc is for some factor analysis
-install.packages("foreign")
-install.packages("psych")
-install.packages("GPArotation")
-install.packages("Hmisc")
-install.packages("tidyverse")
-install.packages("ggplot2")
-install.packages("bayestestR")
-install.packages("see")
-
-# Load required packages
-library(foreign)
-library(psych)
-library(GPArotation)
-library(Hmisc)
-library(tidyverse)
-library(ggplot2)
-library(bayestestR)
-library(see)
-
-# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
-setwd("  ")
-setwd("~/Desktop/R Testing")
-
-
-
-#**********YONI TASK Code Processing************************************
-# read SPSS fa_eg.sav
-# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
-setwd("~/Dropbox/FYP_Jia Rong/R Processing/Yoni task processing in R")
-library(tidyverse)
-
-mydata <- data.frame()
-for (participant in list.files("../../data/")) {
-  df_sub <- read.csv(paste0("../../data/", participant, "/yoni/", participant, "_untitled.csv"))[-c(1:3,28,61, 104), -c(4,5, 7:38, 42:47 )]
-    mydata <- rbind(mydata, df_sub)
-}
-
-results <- mydata %>% 
-  rename(response = mouse_2.clicked_name,
-         responsetime = mouse_2.time) %>% 
-  mutate(answer = ifelse(correct == response, 1, 0))
-
-total_score <- results %>% 
-  group_by(participant, condition) %>% 
-  summarise(total = sum(answer)) %>% 
-  pivot_wider(names_from = condition, values_from = total) %>% 
-  mutate(yoni_total = affect+cognitive+physical) %>% 
-  rename(yoni_affective = affect,
[…]

### 2022-10-04 utils/config.R

@@ -1,48 +1,0 @@
-installed <- rownames(installed.packages())
-
-# Install packages
-for(pkg in c("knitr", "magrittr", "insight", "bayestestR", "parameters", "effectsize", "performance", "correlation", "modelbased", "see", "remotes", "ggplot2")){
-  if (!pkg %in% installed){
-    install.packages(pkg, repos = "http://cran.us.r-project.org")
-  }
-}
-# Because report and easystats are not on CRAN
-if (!"report" %in% installed) remotes::install_github("easystats/report")
-# if (!"easystats" %in% installed) remotes::install_github("easystats/easystats")
-
-
-
-
-# Load packages silently
-for(pkg in c("tidyverse", "ggplot2", "easystats")){
-  if (pkg %in% installed && !require(pkg, character.only=TRUE)) {
-    suppressWarnings(suppressPackageStartupMessages(library(pkg, character.only=TRUE)))
-  }
-}
-
-# Install Python
-# py_install(packages = c('numpy', 'pandas', 'scipy', 'seaborn', 'matplotlib'))
-
-
-# Options relative to figure size
-figheight <- 6
-figwidth <- 6 * see::golden_ratio()
-
-# General options
-options(knitr.kable.NA = "",
-        digits = 2,
-        tidyverse.quiet = TRUE)
-
-# Chunk options (see https://yihui.org/knitr/options/#chunk_options)
-knitr::opts_chunk$set(
-  comment = ">",  # The prefix to be added before each line of the text output.
-  dpi = 600,
-  fig.path = "figures/",
-  fig.height=figheight,
-  fig.width=figwidth
-  # fig.align = "center"
-)
-
-
-# Set seed for reproducible results
-set.seed(333)

### 2022-10-04 utils/render.R

@@ -1,18 +1,0 @@
-suppressWarnings(library(rmarkdown))
-
-# Try to find the correct working dir
-if(!file.exists("index.Rmd") && file.exists("../index.Rmd")) {
-  setwd("../")
-}
-
-# Render as README
-rmarkdown::render('index.Rmd', output_format = rmarkdown::md_document(variant = "markdown_github"), output_file = "README")
-
-# Render HTML
-rmarkdown::render('index.Rmd', output_format = "html_document", output_dir = "docs/", output_file = "index")
-
-# Render Word
-rmarkdown::render('index.Rmd', output_format = "word_document", output_dir = "word_and_pdf/", output_file = "SupplementaryMaterials")
-
-# Render PDF
-rmarkdown::render('index.Rmd', output_format = "pdf_document", output_dir = "word_and_pdf/", output_file = "SupplementaryMaterials")

### 2022-10-10 index.Rmd
fig 2

@@
 
+# Deception Trait {.tabset}
+
+## Confidence
+
+```{r message=FALSE, warning=FALSE}
+results <- list()
+for (var in c("LIE_Ability", "LIE_Frequency", "LIE_Contextuality", "LIE_Negativity")) {
+  model <- brms::brm(as.formula(paste0(
+    "Confidence ~ Answer / (Condition / ",
+    var,
+    ") + (1|Participant) + (1|Item)"
+  )),
+  data = df, family = "beta", refresh = 0, seed=3, iter = 4000,
+  prior = set_prior("student_t(1, 0, 1)", class = "b")
+  )
+
+  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
+      as.data.frame() |> 
+      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+      mutate(
+        Answer = str_remove(Answer, "b_Answer"),
+        Condition = str_remove(Condition, "Condition")
+      )
+}
+
+display(format_table(results$LIE_Ability, stars = TRUE))
+display(format_table(results$LIE_Frequency, stars = TRUE))
+display(format_table(results$LIE_Contextuality, stars = TRUE))
+display(format_table(results$LIE_Negativity, stars = TRUE))
+```
+
+## RT
+
+```{r message=FALSE, warning=FALSE}
+results <- list()
+for (var in c("LIE_Ability", "LIE_Frequency", "LIE_Contextuality", "LIE_Negativity")) {
+  model <- brms::brm(as.formula(paste0(
+    "RT ~ Answer / (Condition / ",
+    var,
+    ") + (1|Participant) + (1|Item)"
+  )),
+  data = df, refresh = 0, seed=3, iter = 4000,
+  prior = set_prior("student_t(1, 0, 3)", class = "b")
+  )
+
+  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
+      as.data.frame() |> 
+      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+      mutate(
+        Answer = str_remove(Answer, "b_Answer"),
+        Condition = str_remove(Condition, "Condition")
+      )
+}
+
+display(format_table(results$LIE_Ability, stars = TRUE))
+display(format_table(results$LIE_Frequency, stars = TRUE))
+display(format_table(results$LIE_Contextuality, stars = TRUE))
+display(format_table(results$LIE_Negativity, stars = TRUE))
+```
+
+## Heart Rate
+
+```{r message=FALSE, warning=FALSE}
+results <- list()
+for (var in c("LIE_Ability", "LIE_Frequency", "LIE_Contextuality", "LIE_Negativity")) {
+  model <- brms::brm(as.formula(paste0(
+    "HeartRate ~ Answer / (Condition / ",
+    var,
+    ") + (1|Participant) + (1|Item)"
+  )),
+  data = df, refresh = 0, seed=3, iter = 4000,
+  prior = set_prior("student_t(1, 0, 8)", class = "b")
+  )
+
+  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
+      as.data.frame() |> 
+      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
+      mutate(
+        Answer = str_remove(Answer, "b_Answer"),
+        Condition = str_remove(Condition, "Condition")
+      )
+}
+
+display(format_table(results$LIE_Ability, stars = TRUE))
+display(format_table(results$LIE_Frequency, stars = TRUE))
+display(format_table(results$LIE_Contextuality, stars = TRUE))
+display(format_table(results$LIE_Negativity, stars = TRUE))
+```
+
 # Figure

### 2022-10-25 paper/manuscript.Rmd
update manu

@@
 
+interoceptive deception detection etc
+
+**EXPAND**
+
 <!-- ToM-->
@@
 Much of the current research investigating the process and mechanisms involved in lying has considered capabilities such as Theory of Mind (ToM), the ability to understand and make inferences about other people's mental states and predict their behaviours [@el2017deception; @lee2021lying].
-ToM is a critical component of deception, since the liar in question must be able to use their inferences to predict whether the individual accepted as true the false information presented to them [@stewart2019deception].
-Children begin using deception during the same period of development in which executive function and ToM develops [@sai2021theory], and children trained in ToM saw an increase in lying behaviour [@ding2015theory].
+ToM is a critical component of deception, since the liar in question must be able to use their inferences to predict whether their target has accepted as true the false information presented to them [@stewart2019deception].
+Children begin using deception during the same period of development in which executive function and ToM develops [@sai2021theory], and youth who have been trained in ToM saw an increase in lying behaviour [@ding2015theory].
 However, there is a growing link between other cognitive and physiological mechanisms that may play a role in both deception detection, and fabricating successful lies
 
-<!-- Intero in deception research-->
+<!-- Define Intero and connect to deception -->
 
-Interoceptive awareness (IA) is the ability to monitor, interpret, integrate, and regulate the sensations and state of one's internal organs, and is closely tied to emotional and cognitive processes [@chen2021emerging; @garfinkel2015knowing].
-Greater is IA associated with greater self-regulation [@weiss2014interaction], especially mindfulness practitioners who tend to have greater interoceptive awareness and greater ability to regulate stress and associated physiological indicators [@ardi2021effects; @mcmahon2021mindful].
+**Interoceptive sensibility? \< check if should use this term**
 
-The growing literature examining the relationship between interoception and deception is rapidly growing area of inquiry.
-Some research has examined how higher interoceptive accuracy, measured through heart beat detection, has been associated with vasoconstriction when faced with a liar, indicating that IA may aid in discriminating high stakes emotional lies and truths [@gunderson2021body].
-It is clear that interoception may indicate on an implicit level that one is being lied to [@ten2019different; @van2014registered], however, there is limited research investigating how interoception may work the other way around, in favour of a liar in regulating their own physiological state that may betray their deception.
+Interoceptive ability (IA) refers to a cluster of skills involved in monitoring, interpreting, integrating, and regulating one's visceral states[@chen2021emerging; @garfinkel2015knowing; @weiss2014interaction], and is closely tied to emotional and cognitive processes [@barrett2015interoceptive].
+Much of the existing literature examining the link between interoceptive abilities has focused on how it may implicitly flag that one is being lied to through an elevated cardiac response [@gunderson2021body], and skin temperature [@van2014registered], or play a role in increasing body ownership.
+While research indicates that attending to ones interoceptive cues improves success in unmasking detection[@ten2019different], there is limited information how IA function the other way around, in the case of the liar.
 
-Attending to interoceptive cues has been associated with greater willingness to engage in cheating [@williams2016valjean], risk-taking behaviours [@ditto2006visceral; @lenggenhager2013listening].
-The findings by @vabba2022interoceptive indicate that high cardiac interoceptive participants were more likely to be dishonest, and to tell higher egoistic lies.
-There is limited research examining whether individuals with high interoceptive accuracy may be more confident in managing physiological tells associated with emotions like guilt or anxiety that the lie may be discovered through suppression or reappraisal [@fustos2013embodiment; @megias2019emotionally].
+<!-- Define Intero and and moral behaviour -->
+
+Attending to interoceptive cues has been associated with greater willingness to engage in cheating [@williams2016valjean], risk-taking behaviours [@ditto2006visceral; @lenggenhager2013listening], and deception [@scattolin2021morality].
+The work by @vabba2022interoceptive indicates that higher cardiac interoception is positively associated with the tendency to be dishonest, and tell higher egoistic lies.
+While this phenomena has been attributed to an increased sense of bodily ownership which accompanies focused awareness of one's viscera, other factors at play have also yet to be examined.
+
+Given that the success of a lie depends more on the qualities of the deceiver versus the lie-detector [@verigin2019lie], fully understanding the link between IA and deception and other risk taking behaviours
+
+It has been well established that some individuals, such as mindfulness practitioners with particularly high IA may be more confident in down-regulation of stress and associated physiological responses [@ardi2021effects; @fustos2013embodiment; @mcmahon2021mindful].
+Since many of these cues, such as cardiac arousal and skin conductance are socially recognized as 'tells' that one is lying, and are used as primary indicators during the polygraph test, could those who are better at managing such responses lie more confidently?
+
+<!-- Intero/and/or/metacognition -->
 
@@
 Of particular interest is how liars might utilize their interoceptive ability to self regulate in towards a more successful deception, and how this ability may compare or interact with other mechanisms at play such as theory of mind.
-We hypothesize that participants with greater theory of mind ability will show higher lie confidence, shorter reaction time, and lower physiological arousal in the interrogation condition, while participants in the polygraph condition will demonstrate lower lie confidence, lower reaction time and higher physiological arousal during the polygraph prediction.
+We hypothesize that participants with greater theory of mind ability will show higher lie confidence, shorter reaction time, and lower physiological arousal in the interrogation condition, while participants in the polygraph condition will demonstrate lower lie confidence, lower reaction time and higher physiological arousal.
 
@@
 
-The plan for this study was preregistered (OSF?). The raw data and analysis script can be found at (GITHUB?).
+Along with open science standards, the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) for this research is available at: **[LINK].**
+
+The plan for this study was preregistered **(OSF?)**.
 
@@
 
-*26* participants (65.4% Females, M~*age*~ = 20.9, *SD* = 2.0) were
-
-recruited VIA HOW
-
-for HUAT
-
--exclusion criteria
-
-This research was approved by the Institutional Review Board (Reference Number: IRB-) of Nanyang Technological University (NTU).
-
-volunteered for [duration of study] for [compensation provided].
+*26* participants (65.4% Females, M~*age*~ = 20.9, *SD* = 2.0) were recruited advertising using univerisy mailing lists and posters.
+Participants were awarded with academic credit for their participation.
+This research was approved by the **Institutional Review Board (Reference Number: IRB-)** of Nanyang Technological University (NTU).
 
@@
 
-Additionally, we implemented the Heartbeat Tracking Task (HTT), in which participants - tap one
+Additionally, we implemented the Heartbeat Tracking Task (HTT) this is where they tap - **but not mentioned in the results??**
 
@@
 
+### Demographic Information
+
+The demographic information we collected was age, ethnicity, nationality, dominant hand (for application of EDA electrodes), education level (determined by highest qualification received, or in the midst of achieving), religion and duration lived in Singapore.
+
+## Procedure
+
+Each subject was briefed on the experimental procedure and study aims, and signed an informed consent document prior to the study commencing.
+During the first phase of the experiment, demographic measures were taken, followed by measures of Theory of Mind and interoceptive abilities, as described above.
+Participants were then connected to an electrocardiogram before proceeding with the deception task.
+
 #### Deception Task
 
-Participants were randomly allocated(??) between two conditions where they underwent 40 trials of a directed lying task.
-During the task, participants would be instructed to lie for 20 of the trials to questions such as, "What secondary school did you go to?".
-Prior to beginning the experiment, researchers collected the answers via questionnaire.
-In each condition, participants received false feedback through different mediums according to the condition that they were assigned, intended to examine the relationship between theory of mind or interoception and the dependent variables (see fig.
-X?).
-Participants were randomized between two conditions which we titled the Interrogation Condition and the Polygraph Condition.
+During the task, participants underwent 40 trails of a directed lying task (20 per condition), where they were asked questions such as, "What secondary school did you go to?".
+Participants provided their answer verbally and pressed a button when they were finished, at which point they would be connected for 10 seconds to the condition-unique stimulus.
 
@@
 
-During the interrogation condition, participants were exposed to video feedback of an examiner following each question.
-They were informed that the examiner was live and monitoring their physiological signals remotely to determine the honesty of their answers, however this was false, and the same sequence of videos was show to each participant.
-
-### Demographic Information
-
-The demographic information we collected was age, ethnicity, nationality, dominant hand (for application of EDA electrodes), education level (determined by highest qualification received, or in the midst of achieving), religion and duration lived in Singapore.
-
-## Procedure
-
-Each subject was briefed on the experimental procedure and study aims and signed an informed consent document prior to the study commencing.
-
-questionnaire to obtain truthful answers to directed lying task,
-
-when were the measures like yoni etc taken?
-
-sound attenuated room
-
-Physio recording devices (equipment by huat and who)
-
-Where/how did they provide their answer during directed lying task
-
-Deception task
-
-During the experiment, all participants were connected to an electrocardiogram to monitor their heart would be asked a question, [HOW WAS ANSWER GIVEN?] and then connected for 10 seconds to the condition-unique stimulus.
-Following the exposure to the stimulus, they would be asked to rate their confidence on a sliding scale before repeating the trial 40 times.
-
-Debriefing was provided following the study.
+Debriefing was provided following the study. At this time the truthful answers to the directed lie questions were collected via questionnaire.
 
@@
 We used factor analysis (using the method agreement procedure to estimate the optimal number of dimensions, **REF PARAMETERS PKG**), rather PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained.
-Then, we modelled the relationship between these inter-individual composite scores (the analysis for all the variables is included in Supplementary Materials) and the 3 outcome variables in interaction with the condition (polygraph *vs.* interrogation).
+Then, we modeled the relationship between these inter-individual composite scores (the analysis for all the variables is included in Supplementary Materials) and the 3 outcome variables in interaction with the condition (polygraph *vs.* interrogation).
 Finally, we also investigated the relationship between the deception scale traits, and the theory of mind and interoception scores using Bayesian correlations.
@@
 
-The 3 YONI-task dimensions and the 2 BES traits were combined into a unique factor, labelled *Theory of Mind* (explaining 35.76\% of variance).
+The 3 YONI-task dimensions and the 2 BES traits were combined into a unique factor, labelled *Theory of Mind* (explaining 35.76% of variance).
 It was loaded by the cognitive (.89), affective (.77), physical (.45) YONI dimension, and the affective (.41) and cognitive (.17) traits of the BES.
 
-The 8 MAIA dimensions and the 3 HCT components were reduced to 4 factors (explaining 65.17\% of variance).
-The first factor, labelled *Interoception - Meta* (23.59\%), was loaded primarily by Attention Regulation (.97), Self-regulation (.63), Emotional awareness (.60), and noticing (.49) dimensions of the MAIA and the HCT confidence score (.40).
-The second factor, labelled *Interoception - Listening* (18.54\%), was primarily loaded by the body listening (.92) and trusting (.53) MAIA dimensions, and the awareness (-.60) and confidence (.46) HCT scores.
-The third factor, labelled *Interoception - Focus* (12.07\%), was primarily loaded by MAIA not-distracting (.87), emotional awareness (-.40) and HCT accuracy (.33).
-The fourth factor, labelled *Interoception - Regulation* (10.97\%), was primarily loaded by MAIA not-worrying (.71), HCT accuracy (.61) and MAIA trusting (.40).
+The 8 MAIA dimensions and the 3 HCT components were reduced to 4 factors (explaining 65.17% of variance).
+The first factor, labelled *Interoception - Meta* (23.59%), was loaded primarily by Attention Regulation (.97), Self-regulation (.63), Emotional awareness (.60), and noticing (.49) dimensions of the MAIA and the HCT confidence score (.40).
+The second factor, labelled *Interoception - Listening* (18.54%), was primarily loaded by the body listening (.92) and trusting (.53) MAIA dimensions, and the awareness (-.60) and confidence (.46) HCT scores.
+The third factor, labelled *Interoception - Focus* (12.07%), was primarily loaded by MAIA not-distracting (.87), emotional awareness (-.40) and HCT accuracy (.33).
+The fourth factor, labelled *Interoception - Regulation* (10.97%), was primarily loaded by MAIA not-worrying (.71), HCT accuracy (.61) and MAIA trusting (.40).
 However, due to the interpretation difficulty, we will refer to these dimensions with their main correlates in **Figure 1**.
@@
 The *Listening* interoception score was significantly associated with an increased confidence in lies, in the polygraph ($\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%$) and interrogation condition ($\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%$).
-It was also associated with faster answers, particilarly for lies ($\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%$) and truths ($\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%$) in the polygraph condition.
+It was also associated with faster answers, particularly for lies ($\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%$) and truths ($\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%$) in the polygraph condition.
 No significant association was found with heart rate.
@@
 This study aimed to examine the relationship between Theory of Mind and interoception on lie confidence, reaction time and physiological arousal during deception.
-This was achieved through a directed lying task in which participants were randomized between two two conditions of false feedback where they were intended to rely on either interoceptive or ToM abilities.
-Across both conditions, the scores show a larger effect on confidence in the polygraph condition, which was both expected and unexpected.
-This may be due to the polygraph condition may be harder due to the less intuitive feedback cues.
-Those better at interoception or perceiving their internal signals would hence be more confident in their lies, as we expected.
-On the other hand, those with better theory of mind become less confident in the absence of another person from which to obtain feedback cues.
+This was achieved through a directed lying task in which participants underwent two conditions of false feedback where they were intended to rely on either interoceptive or ToM abilities.
+Our most notable result is the link between interoception and lying ability,
 
-There was no significant relationship between reaction time and heart rate, however lie confidence is negatively correlated with reaction time, which is expected.
-Generally, participants were less confident in lies than truth, however is effect was greater in the polygraph condition, which is possibly due to less intuitive feedback cues.
-This effect carries over into reaction time, where participants were also slower to respond in the polygraph condition, which is consistent with less intuitive cues.
+That the relationship was found largely in the polygraph condition indicates that our manipulation was successful, and further indicates a potential metacognitive element to this link.
 
-To our knowledge, this is the first study that has found a significant correlation between interoceptive awareness and lie confidence.
-Both interoceptive measures, HCT and MAIA, were strongly correlated.
-Participants with greater IA, also had greater lie confidence and lower truth confidence in the polygraph condition.
-The three sub-scales of MAIA which had a significant interaction were *Noticing, Body Listening* and *Attention Regulation*.
-Since participants were made aware of their cardiac activation through false feedback, we anticipated that those with greater accuracy would demonstrate greater lie confidence.
-Since research has shown deception is more likely when individuals judge a lower risk of confrontation or being caught [@sip2012if; @sip2013pinocchio], these results may offer support to the literature that implicates IA with immoral behaviour.
-Thus our research may be in support of the findings from @vabba2022interoceptive, where IA was found to be a significant moderator in participant's propensity toward deception and high egoist lies.
-Similar findings have also linked increased bodily awareness was linked to a greater likelihood of engaging in immoral behavior such as cheating [@williams2016valjean], and risk-taking behaviours [@ditto2006visceral; @lenggenhager2013listening].
-However, more research is required to examine this potential link.
+<!-- Confidence-->
 
-A greater HCT score was associated with decreased lie confidence in the polygraph condition.
-Since HCT awareness is understood to be the correlation between HCT accuracy and HCT confidence, there are two potential explanations for this.
-First, a low level of awareness could mean that the participant accurately counted their heartbeats, but were not confidence; or vice versa, where they were inaccurate counting but expressed high confidence.
-The dual interpretations of this data may indicate its lack of reliability.
-More research is needed to understand the relationship between lie confidence, interoception and potential implications on lying behaviour.
+See the relationship in confidence ratings - subjective nature/variables and noise/reliability
 
-HCT accuracy is negatively correlated with heart rate, but only in the interrogation condition.
-While it is expected that those with greater interoceptive ability would be better at perceiving and regulating physiological arousal [@megias2019emotionally], we expected to see this result in the polygraph condition which emphasizes interoceptive abilities.
+Regarding interoception and confidence, all factors show a significant effect in the polygraph condition, however, the individual interoceptive factors showed unique associations.
+
+Meta Interoception associated with increased confidence in lies in polygraph
+
+<!-- Reaction Time-->
+
+Meta associated with faster answers for lies and truths in polygraph
+
+Listening interoception faster lies and truths in poly
+
+Focus and regulation no RT
+
+<!-- Heart Rate-->
+
+Since we expected heart rate to be associated with theory of mind abilities and condition, our finding of no such relationship was unexpected.
+
+Manipulation checks show elevated cardiac response in lie conditions, so indicative of TOM or Interoception
+
 A potential explanation for this is that the presence of another person, whom they believe is observing them is understood to increase an individual's interoceptive accuracy [@hazem2017know; @isomura2020direct], which may in turn, cause the participant to attempt to regulate their cardiac response.
@@
 
-We anticipated that ToM measures would negatively correlate with physiological arousal, however while the Yoni Task had no association with heart rate, we found that BES scores were positively correlated with heart rate for both lies and truths, with a larger effect in the interrogation condition.
-Although initially unexpected, this finding is makes sense when interpreted in line with past research which finds a close positive correlation between empathy and increased cardiac response [@jauniaux2020emotion; @lischke2018inter].
-The lack of correlation between heart rate and the Yoni task, indicates that the elevated cardiac response may be due exclusively to empathy, and attributable to ToM.
+<!-- (mostly irrelevant) Scraps -->
+
+Since research has shown deception is more likely when individuals judge a lower risk of confrontation or being caught [@sip2012if; @sip2013pinocchio], these results may offer support to the literature that implicates IA with immoral behaviour.
+Thus our research may be in support of the findings from @vabba2022interoceptive, where IA was found to be a significant moderator in participant's propensity toward deception and high egoist lies.
+Similar findings have also linked increased bodily awareness was linked to a greater likelihood of engaging in immoral behavior such as cheating [@williams2016valjean], and risk-taking behaviours [@ditto2006visceral; @lenggenhager2013listening].
+However, more research is required to examine this potential link.
+
+Focus interoception associated with increase confidence in truthful response in both conditions
+
+Regulation Interoception associated with increased confidence in lies in both conditions and decreased confidence in truth in the polygraph only
+
+those with greater interoceptive ability would be better at perceiving and regulating physiological arousal [@megias2019emotionally], we expected to see this result in the polygraph condition which emphasizes interoceptive abilities.
 
@@
 
-Potential limitations worth noting in this research is that the interrogation and polygraph conditions may not bring out Theory of Mind and interoceptive abilities to the greatest degree.
-This must be considered as a potential limitation since the participants were still connected to the ECG in the interrogation condition, which may amplify their interoceptive awareness beyond what they may normally experience during a real-world act of deception.
-Furthermore, it is possible that there could be an interplay between Theory of Mind and interoception.
-More research is needed to investigate this relationship in the context of deception.
+future research see if interoceptive better at fabricating false emotions
+
+-   limitation that the lying task is very subjective, and the quality of the lie was not measured
 

### 2022-10-26 paper/manuscript.Rmd
mini manu update

@@
 
-interoceptive deception detection etc
+Interoception refers to a cluster of skills involved in monitoring, interpreting, integrating, and regulating one's visceral states[@chen2021emerging; @garfinkel2015knowing; @weiss2014interaction], and is closely tied to emotional and cognitive processes [@barrett2015interoceptive; @petzschner2021computational].
 
-**EXPAND**
+<!-- levels of intero (awareness, sensibility ) [@garfinkel2015knowing] -->
 
-<!-- ToM-->
+<!--features of intero picking up on emotional states etc of others [Konvalinkaa et al 2011] [Gu autism] -->
 
-Much of the current research investigating the process and mechanisms involved in lying has considered capabilities such as Theory of Mind (ToM), the ability to understand and make inferences about other people's mental states and predict their behaviours [@el2017deception; @lee2021lying].
-ToM is a critical component of deception, since the liar in question must be able to use their inferences to predict whether their target has accepted as true the false information presented to them [@stewart2019deception].
-Children begin using deception during the same period of development in which executive function and ToM develops [@sai2021theory], and youth who have been trained in ToM saw an increase in lying behaviour [@ding2015theory].
-However, there is a growing link between other cognitive and physiological mechanisms that may play a role in both deception detection, and fabricating successful lies
+<!-- Intero in Deception research -->
 
-<!-- Define Intero and connect to deception -->
+Much of the existing literature examining the link between interoceptive abilities has focused on how it may implicitly flag that one is being lied to through an elevated cardiac response [@gunderson2021body], and skin temperature [@van2014registered], or play a role in increasing body ownership.
+While research indicates that attending to ones interoceptive cues improves success in unmasking detection[@ten2019different], there is limited information how interoceptive skills may function the other way around, in the case of the liar.
 
-**Interoceptive sensibility? \< check if should use this term**
+under developed area in general in intero is propensity to use, and how it is used [@murphy2022propensity]
 
-Interoceptive ability (IA) refers to a cluster of skills involved in monitoring, interpreting, integrating, and regulating one's visceral states[@chen2021emerging; @garfinkel2015knowing; @weiss2014interaction], and is closely tied to emotional and cognitive processes [@barrett2015interoceptive].
-Much of the existing literature examining the link between interoceptive abilities has focused on how it may implicitly flag that one is being lied to through an elevated cardiac response [@gunderson2021body], and skin temperature [@van2014registered], or play a role in increasing body ownership.
-While research indicates that attending to ones interoceptive cues improves success in unmasking detection[@ten2019different], there is limited information how IA function the other way around, in the case of the liar.
-
-<!-- Define Intero and and moral behaviour -->
-
-Attending to interoceptive cues has been associated with greater willingness to engage in cheating [@williams2016valjean], risk-taking behaviours [@ditto2006visceral; @lenggenhager2013listening], and deception [@scattolin2021morality].
-The work by @vabba2022interoceptive indicates that higher cardiac interoception is positively associated with the tendency to be dishonest, and tell higher egoistic lies.
-While this phenomena has been attributed to an increased sense of bodily ownership which accompanies focused awareness of one's viscera, other factors at play have also yet to be examined.
-
-Given that the success of a lie depends more on the qualities of the deceiver versus the lie-detector [@verigin2019lie], fully understanding the link between IA and deception and other risk taking behaviours
-
-It has been well established that some individuals, such as mindfulness practitioners with particularly high IA may be more confident in down-regulation of stress and associated physiological responses [@ardi2021effects; @fustos2013embodiment; @mcmahon2021mindful].
-Since many of these cues, such as cardiac arousal and skin conductance are socially recognized as 'tells' that one is lying, and are used as primary indicators during the polygraph test, could those who are better at managing such responses lie more confidently?
-
-<!-- Intero/and/or/metacognition -->
+this research is about to be very useful, and very important
 
@@
 
-Additionally, we implemented the Heartbeat Tracking Task (HTT) this is where they tap - **but not mentioned in the results??**
-
 ### Deception
@@
 
-During the task, participants underwent 40 trails of a directed lying task (20 per condition), where they were asked questions such as, "What secondary school did you go to?".
+During the task, participants underwent 40 trails of a directed lying task, where they were asked questions such as, "What secondary school did you go to?".
 Participants provided their answer verbally and pressed a button when they were finished, at which point they would be connected for 10 seconds to the condition-unique stimulus.
+Participants would undergo two conditions of 20 trails each, beginning with the *interrogation* *conditon*, and followed by the second, *polygraph condition*.
+The purpose of these conditions was to draw out the interoceptive or theory of mind abilities by providing feedback cues that would cause the participants to focus their attention on either the feedback from other people, or their own cardiac response.
 
-In the Interrogation condition, participants were instructed that following their lie, a live examiner over video feed would appear briefly to judge whether they were truthful or not.
+In the *interrogation condition*, participants were instructed that following their lie, a live examiner over video feed would appear briefly to judge whether they were truthful or not.
 In actuality, the video of the examiner shown was pre-recorded and the same for all participants.
 We hypothesized that participants would will rely on theory of mind abilities to predict whether their lie to the examiner was successfully accepted as true.
+We hypothesized that in this condition, participants would rely on their theory of mind abilities to discern the facial feedback cues from the examiner to ascertain whether their lie was successful.
 
-The Polygraph Condition followed the same routine, however instead of a receiving feedback from an interrogator, following the lie, a video of physiological signals was shown.
-We hypothesized when made acutely aware of such signals through false feedback, that participants would rely on interoceptive abilities to be more mindful or intentional about modulating the signals that may give them away.
+The *polygraph condition* followed the same routine, however instead of a receiving feedback from an interrogator, following the lie, a video of physiological signals was shown.
+We hypothesised that when participants were made acutely aware of such signals through false feedback, they would rely on interoceptive abilities to be more mindful or intentional about modulating the signals that may give them away.
 The physiological signals in this condition are also false feedback, and pre-recorded and identical for all participants.
@@
 
-This study aimed to examine the relationship between Theory of Mind and interoception on lie confidence, reaction time and physiological arousal during deception.
-This was achieved through a directed lying task in which participants underwent two conditions of false feedback where they were intended to rely on either interoceptive or ToM abilities.
-Our most notable result is the link between interoception and lying ability,
+This study aimed to examine the relationship between theory of mind and interoception on lie confidence, reaction time and physiological arousal during deception.
+This was achieved through a directed lying task in which participants underwent two conditions of false feedback where they were intended to rely on either interoceptive or theory of mind abilities.
+To our knowledge, this is the first study which has shown a clear link between interoceptive abilities and cardiac regulation during the act of deception.
+As this relationship was largely found in the polygraph condition that was designed to draw out the interoceptive abilities within the individual, we can conclude that our manipulation was successful.
+This taken with high confidence ratings in participant's lying abilities, also indicates other potential factors at play.
 
-That the relationship was found largely in the polygraph condition indicates that our manipulation was successful, and further indicates a potential metacognitive element to this link.
+<!-- Participants relied on interoception -->
 
-<!-- Confidence-->
+Our results show that participants who were telling the truth had a slower reaction time, and rated themselves as less confident in the polygraph condition, however, their heart rate averaged lower as compared to the interrogation condition.
+This suggests that despite the participant's lack of confidence, they were very in-tune with their interoceptive feedback in the polygraph condition, and successfully able to decrease their heart rate.
+Given that interoceptive accuracy is enhanced by focusing on it during a time of stress [@schulz2013cold], such as attempting to conceal deception combined with false physiological feedback delivered during the polygraph condition, this conclusion is in line with our hypothesis.
 
-See the relationship in confidence ratings - subjective nature/variables and noise/reliability
+<!-- Metacognition and Interoception -->
 
-Regarding interoception and confidence, all factors show a significant effect in the polygraph condition, however, the individual interoceptive factors showed unique associations.
+This also reflects a broader theme in our results, which indicates that all interoceptive factors are associated with an increased confidence in deceptive abilities, and faster reaction time for lies in the polygraph condition.
+It logical that confidence in deception would be accompanied by faster reaction time.
+(**find smt useful to say about reaction time**)
 
-Meta Interoception associated with increased confidence in lies in polygraph
+However, since confidence was a subjective measure, it does not necessarily reflect competence [@khalsa2008interoceptive].
+While the data indicates that participants were able to self-regulate using interoceptive abilities, this still highlights an important caveat, which is the potential metacognitive element at play.
 
-<!-- Reaction Time-->
+the relationship between the objective accuracy and subjective report of their interoceptive accuracy [@garfinkel2015knowing].
+In this case, participants demonstrated a high level of metacognition, where they were confident in the quality of their physiological control.
 
-Meta associated with faster answers for lies and truths in polygraph
+metacognitive beliefs about competence in physiological regulation may influence the cognitive processes and development physiological responses (so their appraisal is just as important) [@petzschner2021computational]
 
-Listening interoception faster lies and truths in poly
+While this research has demonstrated that interoceptive abilities may be used to regulate and conceal deception, the individual's confidence in their lying abilities, is subjective, and may not offer a full-picture of their true success.
 
-Focus and regulation no RT
+<!-- Future Research -->
 
-<!-- Heart Rate-->
-
-Since we expected heart rate to be associated with theory of mind abilities and condition, our finding of no such relationship was unexpected.
-
-Manipulation checks show elevated cardiac response in lie conditions, so indicative of TOM or Interoception
-
-A potential explanation for this is that the presence of another person, whom they believe is observing them is understood to increase an individual's interoceptive accuracy [@hazem2017know; @isomura2020direct], which may in turn, cause the participant to attempt to regulate their cardiac response.
-
-Greater ToM abilities negatively correlated with lie confidence, and saw an increase in truth confidence, but only in the polygraph condition.
-In the Yoni Task, this effect is driven by the cognitive and physical domains.
-BES saw the effect driven by both the cognitive and affective domain for lie confidence, meanwhile, truth confidence is only driven by the affective domain.
-
-<!-- (mostly irrelevant) Scraps -->
-
-Since research has shown deception is more likely when individuals judge a lower risk of confrontation or being caught [@sip2012if; @sip2013pinocchio], these results may offer support to the literature that implicates IA with immoral behaviour.
-Thus our research may be in support of the findings from @vabba2022interoceptive, where IA was found to be a significant moderator in participant's propensity toward deception and high egoist lies.
-Similar findings have also linked increased bodily awareness was linked to a greater likelihood of engaging in immoral behavior such as cheating [@williams2016valjean], and risk-taking behaviours [@ditto2006visceral; @lenggenhager2013listening].
-However, more research is required to examine this potential link.
-
-Focus interoception associated with increase confidence in truthful response in both conditions
-
-Regulation Interoception associated with increased confidence in lies in both conditions and decreased confidence in truth in the polygraph only
-
-those with greater interoceptive ability would be better at perceiving and regulating physiological arousal [@megias2019emotionally], we expected to see this result in the polygraph condition which emphasizes interoceptive abilities.
-
-## Limitations and Future Research
-
-future research see if interoceptive better at fabricating false emotions
-
--   limitation that the lying task is very subjective, and the quality of the lie was not measured
+Future research should continue to unpack this relationship, examining how confidence and interoceptive regulation is reflected in the actual success of a lie, as well as how individuals confidence in their interoceptive abilities may correspond to decision bias [@garfinkel2015knowing], and propensity to engage in deception [@sip2012if].
+Furthermore, linking and expanding recent research [@pearson2022two] on interindividual traits correlate with interoceptive abilities, in addition to the beliefs about those abilities as they relate to deception.
 

### 2022-10-27 paper/manuscript.Rmd
update manuscript

@@
 
-The fabrication and delivery of false information is a sophisticated, and cognitively taxing activity [@abe2007deceiving; @leal2008time ], resulting in physiological arousal [@eskritt2021did] which may require effortful self-regulation to conceal[@krokoszinski2016emotion].
+The fabrication and delivery of false information is a sophisticated, and cognitively taxing activity [@abe2007deceiving], resulting in physiological arousal [@eskritt2021did] which may require effortful self-regulation to conceal [@krokoszinski2016emotion].
+While much of deception research has focused on topics such as theory of mind, other mechanisms underlying the regulation of physiological responses, such as increased cardiac arousal, respiration and sweating, which are often relied on during lie detection have been under researched.
 
-Interoception refers to a cluster of skills involved in monitoring, interpreting, integrating, and regulating one's visceral states[@chen2021emerging; @garfinkel2015knowing; @weiss2014interaction], and is closely tied to emotional and cognitive processes [@barrett2015interoceptive; @petzschner2021computational].
+<!-- Defining interoceptive processes -->
 
-<!-- levels of intero (awareness, sensibility ) [@garfinkel2015knowing] -->
-
-<!--features of intero picking up on emotional states etc of others [Konvalinkaa et al 2011] [Gu autism] -->
+Interoception refers to a cluster of skills involved in monitoring, interpreting, integrating, and regulating one's visceral states [@chen2021emerging; @weiss2014interaction], and is closely tied to emotional and cognitive processes [@barrett2015interoceptive; @petzschner2021computational].
+@garfinkel2015knowing consolidated the facets of interoception into three distinct processes: *interoceptive accuracy*, as an objective measure of one's ability to monitor viscera; *interoceptive sensibility*, as the subjective measure of accuracy; and *interoceptive awareness*, describing the metacognition underlying the perception of interoceptive accuracy.
+While interoceptive sensibility may be an important component, the corrospondence between the confidence and accuracy, or interoceptive awareness appears to be associated with the downregulation of emotional responses and their associated physiological symptoms [@fustos2013embodiment; @critchley2017interoception; @critchley2018influence].
 
@@
 
-Much of the existing literature examining the link between interoceptive abilities has focused on how it may implicitly flag that one is being lied to through an elevated cardiac response [@gunderson2021body], and skin temperature [@van2014registered], or play a role in increasing body ownership.
-While research indicates that attending to ones interoceptive cues improves success in unmasking detection[@ten2019different], there is limited information how interoceptive skills may function the other way around, in the case of the liar.
+Interoceptive processes are not only a key component of forming your own emotions, but may also facilitate being in tune with the emotional states of others [@konvalinka2011synchronized; @garfinkel2016discrepancies].
+This corresponds to situations involving deception, since much of the existing literature examining the link between interoceptive abilities has focused on how it may implicitly flag that one is being lied to through an elevated cardiac response [@gunderson2021body], and skin temperature [@van2014registered].
+While research indicates that attending to ones interoceptive cues improves success in unmasking detection [@ten2019different], there is limited information how interoceptive skills may function the other way around, in the case of the liar.
 
-under developed area in general in intero is propensity to use, and how it is used [@murphy2022propensity]
-
-this research is about to be very useful, and very important
+As identified by @murphy2022propensity, the propensity to use interoceptive information, and in what manner remains an underdeveloped area in research, and may illuminate the mechanisms underlying physiological and emotional control exhibited by successful liars [@krokoszinski2016emotion; @wielgopolan2021can].
 
@@
 
-The act of lying is often accompanied by physiological responses such as increased heart rate, increased respiration and sweating.
-Since fluctuations in key physiological indicators as a means to determine whether the individual is lying is a key principle behind the polygraph test and other lie detection techniques, there is a need for more research examining the relationship between IA, theory of mind, and deception.
-This research attempts to isolate the effects of theory of mind and interoception, and examine how they interact with deception.
+This research attempts to isolate the effects of theory of mind and interoception to examine how participants may rely on these abilities to evade lie detection.
 Of particular interest is how liars might utilize their interoceptive ability to self regulate in towards a more successful deception, and how this ability may compare or interact with other mechanisms at play such as theory of mind.
@@
 
-*26* participants (65.4% Females, M~*age*~ = 20.9, *SD* = 2.0) were recruited advertising using univerisy mailing lists and posters.
+*26* participants (65.4% Females, M~*age*~ = 20.9, *SD* = 2.0) were recruited advertising using university mailing lists and posters.
 Participants were awarded with academic credit for their participation.
@@
 
-### Theory of Mind and Empathy
+### Theory of Mind
 
-Since Theory of Mind and empathy are closely related, *The Basic Empathy Scale (BES)* [@jolliffe2006development] was used as a subjective measure for theory of mind.
+Since theory of mind and empathy are closely related, *The Basic Empathy Scale (BES)* [@jolliffe2006development] was used as a subjective measure for theory of mind.
 *BES* uses a 40-item Likert scale to rate statements such as, "I can usually work out when people are cheerful" from 1-5.
@@
 
-### Interoceptive Ability
+### Interoceptive Abilities
 
@@
 At the same time their true heart rate is recorded and the scores are compared to determine the individual's accuracy.
-They also completed the *MAIA questionnaire* [@mehling2012multidimensional], where they rated 32 statements such as "I can use my breath to reduce tension" on a 1-5 Likert scale.
+They also completed the *MAIA questionnaire* [@mehling2012multidimensional], that featured 32 statements such as "I can use my breath to reduce tension" on a 1-5 Likert scale.
 
@@
 During the first phase of the experiment, demographic measures were taken, followed by measures of Theory of Mind and interoceptive abilities, as described above.
-Participants were then connected to an electrocardiogram before proceeding with the deception task.
+Participants were then connected to an ECG before proceeding with the deception task on a computer.
 
@@
 
-During the task, participants underwent 40 trails of a directed lying task, where they were asked questions such as, "What secondary school did you go to?".
-Participants provided their answer verbally and pressed a button when they were finished, at which point they would be connected for 10 seconds to the condition-unique stimulus.
-Participants would undergo two conditions of 20 trails each, beginning with the *interrogation* *conditon*, and followed by the second, *polygraph condition*.
-The purpose of these conditions was to draw out the interoceptive or theory of mind abilities by providing feedback cues that would cause the participants to focus their attention on either the feedback from other people, or their own cardiac response.
+Participants underwent 40 trails of a directed lying task, where they were asked questions such as, "What secondary school did you go to?".
+Answers were provided verbally and participant pressed a button when they were finished, at which point they would be connected for 10 seconds to the condition-unique stimulus.
+There were two conditions of 20 trails each, beginning with the *interrogation* *condition*, and followed by the second, *polygraph condition*.
+The purpose of these conditions was to draw out the interoceptive or theory of mind abilities by providing feedback cues that would cause them to focus their attention on either the visual feedback cues from other people, or their own cardiac response.
 
@@
 The *polygraph condition* followed the same routine, however instead of a receiving feedback from an interrogator, following the lie, a video of physiological signals was shown.
-We hypothesised that when participants were made acutely aware of such signals through false feedback, they would rely on interoceptive abilities to be more mindful or intentional about modulating the signals that may give them away.
+We hypothesized that when participants were made acutely aware of such signals through false feedback, they would rely on interoceptive abilities to be more mindful or intentional about modulating the signals that may give them away.
 The physiological signals in this condition are also false feedback, and pre-recorded and identical for all participants.
 
-During each trial, the time it took for participants to answer is recorded, and their heart rates are measured using an electrocardiogram.
+During each trial, the time it took for participants to answer was recorded, and their heart rates are measured using an ECG.
 Following the trial, participants gave a confidence rating for how successful they believe their lie or truth was.
-
-Debriefing was provided following the study. At this time the truthful answers to the directed lie questions were collected via questionnaire.
+Debriefing was provided following the study.
+At this time the truthful answers to the directed lie questions were collected via questionnaire.
 
@@
 The 8 MAIA dimensions and the 3 HCT components were reduced to 4 factors (explaining 65.17% of variance).
-The first factor, labelled *Interoception - Meta* (23.59%), was loaded primarily by Attention Regulation (.97), Self-regulation (.63), Emotional awareness (.60), and noticing (.49) dimensions of the MAIA and the HCT confidence score (.40).
-The second factor, labelled *Interoception - Listening* (18.54%), was primarily loaded by the body listening (.92) and trusting (.53) MAIA dimensions, and the awareness (-.60) and confidence (.46) HCT scores.
-The third factor, labelled *Interoception - Focus* (12.07%), was primarily loaded by MAIA not-distracting (.87), emotional awareness (-.40) and HCT accuracy (.33).
-The fourth factor, labelled *Interoception - Regulation* (10.97%), was primarily loaded by MAIA not-worrying (.71), HCT accuracy (.61) and MAIA trusting (.40).
+The first factor, labelled *Interoception - Meta* (23.59%), was loaded primarily by Attention Regulation (.97), Self-regulation (.63), Emotional awareness (.60), and Noticing (.49) dimensions of the MAIA and the HCT confidence score (.40).
+The second factor, labelled *Interoception - Listening* (18.54%), was primarily loaded by the Body Listening (.92) and Trusting (.53) MAIA dimensions, and the Awareness (-.60) and Confidence (.46) HCT scores.
+The third factor, labelled *Interoception - Focus* (12.07%), was primarily loaded by MAIA Not-Distracting (.87), Emotional Awareness (-.40) and HCT Accuracy (.33).
+The fourth factor, labelled *Interoception - Regulation* (10.97%), was primarily loaded by MAIA not-worrying (.71), HCT Accuracy (.61) and MAIA Trusting (.40).
 However, due to the interpretation difficulty, we will refer to these dimensions with their main correlates in **Figure 1**.
@@
 Our results show that participants who were telling the truth had a slower reaction time, and rated themselves as less confident in the polygraph condition, however, their heart rate averaged lower as compared to the interrogation condition.
-This suggests that despite the participant's lack of confidence, they were very in-tune with their interoceptive feedback in the polygraph condition, and successfully able to decrease their heart rate.
+This suggests that despite the participant's lack of confidence, they were very in-tune with their physiological response in the polygraph condition, and successfully able to decrease their heart rate.
 Given that interoceptive accuracy is enhanced by focusing on it during a time of stress [@schulz2013cold], such as attempting to conceal deception combined with false physiological feedback delivered during the polygraph condition, this conclusion is in line with our hypothesis.
+
+As the relationship between interoception and emotion is well established [@barrett2015interoceptive; @dobrushina2020interaction; @ohira2020predictive], our work is consistent with @wielgopolan2021can, who found that groups with higher emotional awareness made better liars and were more successful at regulating their emotional and physiological responses, as well as fabricating new ones.
 
@@
 
-This also reflects a broader theme in our results, which indicates that all interoceptive factors are associated with an increased confidence in deceptive abilities, and faster reaction time for lies in the polygraph condition.
+Although participants were not explicitly directed to attend to their physiological signals as a means of evading deception detection, they were aware these signals were recorded and informed that their lies would be detected through their analysis.
+Additionally, the presence of the ECG likely made them aware, and these measures remained connected during the interrogation.
+This indicates that there was likely an explicit attentional component to the control exerted, which is further reflected by a broader theme in our results.
+Our results indicate that all interoceptive factors (*Meta, Listening, Focus and Regulation*) are associated with an increased confidence in deceptive abilities, and faster reaction time for lies in the polygraph condition.
 It logical that confidence in deception would be accompanied by faster reaction time.
-(**find smt useful to say about reaction time**)
+However, since confidence was a subjective measure, it does not necessarily reflect competence [@khalsa2008interoceptive].
+While our data indicates that participants were able to self-regulate using interoceptive abilities, this still highlights an important caveat, which is the potential metacognitive awareness at play [@garfinkel2015knowing].
 
-However, since confidence was a subjective measure, it does not necessarily reflect competence [@khalsa2008interoceptive].
-While the data indicates that participants were able to self-regulate using interoceptive abilities, this still highlights an important caveat, which is the potential metacognitive element at play.
+Metacognitive beliefs, or interoceptive awareness about competence in the quality of physiological regulation may influence the cognitive processes and development physiological responses.
+That is to say, that the appraisal is just as important to the process of deception by informing their true ability [@stephan2016allostatic; @harrison2021filter; @petzschner2021computational].
 
-the relationship between the objective accuracy and subjective report of their interoceptive accuracy [@garfinkel2015knowing].
-In this case, participants demonstrated a high level of metacognition, where they were confident in the quality of their physiological control.
+<!-- Interoceptive sensibility and risk-taking -->
 
-metacognitive beliefs about competence in physiological regulation may influence the cognitive processes and development physiological responses (so their appraisal is just as important) [@petzschner2021computational]
-
-While this research has demonstrated that interoceptive abilities may be used to regulate and conceal deception, the individual's confidence in their lying abilities, is subjective, and may not offer a full-picture of their true success.
+High interoceptive sensibility regardless of true competence may also directly shape behaviour through the reduced perception of risk associated with being caught.
+Past research indicates the likelihood of deception increases when individuals judge a lower risk of being caught, based on situation-specific variables and their own qualities [@sip2012if; @sip2013pinocchio].
+These results may offer support to findings such as @vabba2022interoceptive where interoceptive abilities were found to be a significant moderator in the willingness to engage in riskier forms of deception, and offer insight into other risk behaviours linked with interoceptive ability such as cheating [@williams2016valjean] and risk-taking [@ditto2006visceral; @lenggenhager2013listening].
 
@@
 
+While this research has demonstrated that interoceptive abilities may be used to regulate and conceal deception, the individual's confidence in their lying abilities, is subjective, and may not offer a full-picture of their objective success.
 Future research should continue to unpack this relationship, examining how confidence and interoceptive regulation is reflected in the actual success of a lie, as well as how individuals confidence in their interoceptive abilities may correspond to decision bias [@garfinkel2015knowing], and propensity to engage in deception [@sip2012if].
-Furthermore, linking and expanding recent research [@pearson2022two] on interindividual traits correlate with interoceptive abilities, in addition to the beliefs about those abilities as they relate to deception.
+Furthermore, future research should expand recent findings on how individual traits correlate with true interoceptive abilities [@pearson2022two], to understand how they may factor into deceptive behaviour.
 

### 2022-11-01 paper/manuscript.Rmd
manu

@@
 
-The fabrication and delivery of false information is a sophisticated, and cognitively taxing activity [@abe2007deceiving], resulting in physiological arousal [@eskritt2021did] which may require effortful self-regulation to conceal [@krokoszinski2016emotion].
-While much of deception research has focused on topics such as theory of mind, other mechanisms underlying the regulation of physiological responses, such as increased cardiac arousal, respiration and sweating, which are often relied on during lie detection have been under researched.
+In our current post-truth era, deception has become increasingly prevalent in our everyday lives [@lewandowsky2017beyond].
+Although the act of deceiving is complex and cognitively taxing [@abe2007deceiving], often requiring effortful self-regulation to conceal [@krokoszinski2016emotion], research shows that people tend to under-estimate their ability to successfully deceive others [@elaad2003effects].
+Moreover, meta-analytic findings suggest that the ability of the liar plays a more significant role than the lie detector in deceptive interactions [@verigin2019lie; @bond2008individual; @levine2011sender].
+However, relative to the abundant literature regarding deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], surprisingly little attention has been conferred to investigating the inter-individual differences in people's ability to successfully lie.
+
+<!-- TOM  -->
+
+As deception requires the liar to intentionally manipulate the beliefs of others [@burgoon1994interpersonal; @sip2012if], most research on lying capability has been focused on higher order cognitive processes, particularly in theory of mind (TOM).
+TOM refers to the ability to infer that others have mental states, such as beliefs, emotions and intentions, distinct from ourselves [@lee2021lying; @wellman2001meta; @baron1997mindblindness].
+Indeed, the capacity to tell lies, as well as the complexity of lies told, have previously been found to be associated with higher TOM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role].
+Furthermore, the deceptive capabilities of children has often been used as a measure of their TOM abilities.
+However, given that the development of TOM abilities has often been viewed as the building blocks of other higher order cognitive processes [@ketelaars2010dynamics; @isaksson2021s], studies investigating the links between TOM and lying ability have largely been conducted with children and individuals with neurocognitive deficits [@beaudoin2020systematic; @bora2017meta; @roheger2022progression].
+As such, little is known with regards to the role TOM plays in the lying ability of neurotypical adults.
 
@@
 
-Interoception refers to a cluster of skills involved in monitoring, interpreting, integrating, and regulating one's visceral states [@chen2021emerging; @weiss2014interaction], and is closely tied to emotional and cognitive processes [@barrett2015interoceptive; @petzschner2021computational].
-@garfinkel2015knowing consolidated the facets of interoception into three distinct processes: *interoceptive accuracy*, as an objective measure of one's ability to monitor viscera; *interoceptive sensibility*, as the subjective measure of accuracy; and *interoceptive awareness*, describing the metacognition underlying the perception of interoceptive accuracy.
-While interoceptive sensibility may be an important component, the corrospondence between the confidence and accuracy, or interoceptive awareness appears to be associated with the downregulation of emotional responses and their associated physiological symptoms [@fustos2013embodiment; @critchley2017interoception; @critchley2018influence].
+Alternatively, the variability observed in interoception, broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].
+Following @garfinkel2015knowing's three-dimensional framework, interoception is comprised of distinct facets, namely - *interoceptive accuracy*, the objective ability to monitor internal bodily signals; *interoceptive sensibility*, the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness*, the metacognitive awareness of one's interoceptive accuracy (i.e., accuracy-confidence correspondence).
+
+<!-- While interoceptive sensibility may be an important component, the correspondence between the confidence and accuracy, or interoceptive awareness appears to be associated with the downregulation of emotional responses and their associated physiological symptoms [@fustos2013embodiment; @critchley2017interoception; @critchley2018influence].
+-->
 
@@
 
-Interoceptive processes are not only a key component of forming your own emotions, but may also facilitate being in tune with the emotional states of others [@konvalinka2011synchronized; @garfinkel2016discrepancies].
+Given the influence of interoceptive abilities on higher order cognition, particularly with regards to emotional processing  [@barrett2015interoceptive; @petzschner2021computational; @vabba2022interoceptive], it is possible that interoception bears an effect on people's capacity to tell lies.
+Although there has been little research investigating the links between interoception and deceptive ability *per se*, some studies have found heightened self-focus towards internal bodily signals to result in an increased demonstration of apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening].
+In line with these findings, @vabba2022interoceptive reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high (relative to low), whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
+
+In contrast, however, the somatic marker hypothesis posits higher interoception to be linked to a propensity towards making rational decisions [@damasio1996somatic].
+Indeed, previous research has shown a negative correlation between interoceptive awareness and the likelihood to make risky decisions [@dunn2010listening; @furman2013interoceptive].
+Taking these mixed findings in perspective with the relative lack of deception research associated with the multidimensional construct of interoception, more studies are warranted to investigate the relationship between the interoceptive and deceptive ability.
+
+<!-- Interoceptive processes are not only a key component of forming your own emotions, but may also facilitate being in tune with the emotional states of others [@konvalinka2011synchronized; @garfinkel2016discrepancies].
 This corresponds to situations involving deception, since much of the existing literature examining the link between interoceptive abilities has focused on how it may implicitly flag that one is being lied to through an elevated cardiac response [@gunderson2021body], and skin temperature [@van2014registered].
 While research indicates that attending to ones interoceptive cues improves success in unmasking detection [@ten2019different], there is limited information how interoceptive skills may function the other way around, in the case of the liar.
+-->
 
-As identified by @murphy2022propensity, the propensity to use interoceptive information, and in what manner remains an underdeveloped area in research, and may illuminate the mechanisms underlying physiological and emotional control exhibited by successful liars [@krokoszinski2016emotion; @wielgopolan2021can].
+<!-- As identified by @murphy2022propensity, the propensity to use interoceptive information, and in what manner remains an underdeveloped area in research, and may illuminate the mechanisms underlying physiological and emotional control exhibited by successful liars [@krokoszinski2016emotion; @wielgopolan2021can].
+-->
 
@@
 
-This research attempts to isolate the effects of theory of mind and interoception to examine how participants may rely on these abilities to evade lie detection.
+This study aims at exploring the relationship between TOM and interoception with deceptive ability.
+Despite the criticism surrounding the somatic marker hypothesis [@dunn2006somatic; @maia2004reexamination], interoception has been shown to be associated with goal-directed behaviours and positively influence rational decision-making in ambiguous situations [@poppa2018somatic; @naqvi2014insula; @avery2017brain].
+As such, we expect individuals higher in interoception to exhibit better lying ability, as indicated by higher lie confidence, lower physiological arousal and shorter response time in the polygraph condition.
+In the interrogation condition, we expect people with higher TOM abilities to exhibit be better at lying, as indicated by higher low confidence, lower physiological arousal and shorter response time.
+
+<!-- This research attempts to isolate the effects of theory of mind and interoception to examine how participants may rely on these abilities to evade lie detection.
 Of particular interest is how liars might utilize their interoceptive ability to self regulate in towards a more successful deception, and how this ability may compare or interact with other mechanisms at play such as theory of mind.
 We hypothesize that participants with greater theory of mind ability will show higher lie confidence, shorter reaction time, and lower physiological arousal in the interrogation condition, while participants in the polygraph condition will demonstrate lower lie confidence, lower reaction time and higher physiological arousal.
+-->
 
@@
 Answers were provided verbally and participant pressed a button when they were finished, at which point they would be connected for 10 seconds to the condition-unique stimulus.
-There were two conditions of 20 trails each, beginning with the *interrogation* *condition*, and followed by the second, *polygraph condition*.
+There were two conditions of 20 trails each, beginning with the *interrogation condition*, and followed by the second, *polygraph condition*.
 The purpose of these conditions was to draw out the interoceptive or theory of mind abilities by providing feedback cues that would cause them to focus their attention on either the visual feedback cues from other people, or their own cardiac response.

### 2022-11-04 paper/manuscript.Rmd
update manuuuu

@@
 
-In our current post-truth era, deception has become increasingly prevalent in our everyday lives [@lewandowsky2017beyond].
+In this post-truth era, deception has become increasingly prevalent in our everyday lives [@lewandowsky2017beyond].
 Although the act of deceiving is complex and cognitively taxing [@abe2007deceiving], often requiring effortful self-regulation to conceal [@krokoszinski2016emotion], research shows that people tend to under-estimate their ability to successfully deceive others [@elaad2003effects].
@@
 Indeed, the capacity to tell lies, as well as the complexity of lies told, have previously been found to be associated with higher TOM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role].
-Furthermore, the deceptive capabilities of children has often been used as a measure of their TOM abilities.
-However, given that the development of TOM abilities has often been viewed as the building blocks of other higher order cognitive processes [@ketelaars2010dynamics; @isaksson2021s], studies investigating the links between TOM and lying ability have largely been conducted with children and individuals with neurocognitive deficits [@beaudoin2020systematic; @bora2017meta; @roheger2022progression].
+Furthermore, the deceptive capabilities of children is often used as a measure of their TOM abilities.
+However, given the view that development of TOM abilities serve as the building blocks of other higher order cognitive processes [@ketelaars2010dynamics; @isaksson2021s], studies investigating the links between TOM and lying ability have predominantly been focused on children and individuals with neurocognitive deficits [@beaudoin2020systematic; @bora2017meta; @roheger2022progression].
 As such, little is known with regards to the role TOM plays in the lying ability of neurotypical adults.
@@
 
-In contrast, however, the somatic marker hypothesis posits higher interoception to be linked to a propensity towards making rational decisions [@damasio1996somatic].
+In contrast, however, the somatic marker hypothesis posits higher interoception to be associated with a propensity towards making rational decisions [@damasio1996somatic].
 Indeed, previous research has shown a negative correlation between interoceptive awareness and the likelihood to make risky decisions [@dunn2010listening; @furman2013interoceptive].
-Taking these mixed findings in perspective with the relative lack of deception research associated with the multidimensional construct of interoception, more studies are warranted to investigate the relationship between the interoceptive and deceptive ability.
+Taking these mixed findings to perspective with the lack of consideration for the multidimensional nature of interoception in past studies, as well as the paucity in research linking deceptive ability with interoception, more studies are warranted to examine the relationship between interoception and deception.
 
@@
 
-<!-- This research attempts to isolate the effects of theory of mind and interoception to examine how participants may rely on these abilities to evade lie detection.
-Of particular interest is how liars might utilize their interoceptive ability to self regulate in towards a more successful deception, and how this ability may compare or interact with other mechanisms at play such as theory of mind.
-We hypothesize that participants with greater theory of mind ability will show higher lie confidence, shorter reaction time, and lower physiological arousal in the interrogation condition, while participants in the polygraph condition will demonstrate lower lie confidence, lower reaction time and higher physiological arousal.
--->
-
 # Methods
 
-Along with open science standards, the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) for this research is available at: **[LINK].**
+Along with open science standards, the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) for this research is available at [**https://github.com/DominiqueMakowski/DeceptionInteroTom**](https://github.com/DominiqueMakowski/DeceptionInteroTom){uri.}.
 
@@
 
-*26* participants (65.4% Females, M~*age*~ = 20.9, *SD* = 2.0) were recruited advertising using university mailing lists and posters.
-Participants were awarded with academic credit for their participation.
-This research was approved by the **Institutional Review Board (Reference Number: IRB-)** of Nanyang Technological University (NTU).
+30 participants were recruited through  posters, flyers, and online social media platforms.
+Inclusion criteria included residing in Singapore, and an absence of current or history of neurological, psychiatric, or cardiovascular disorders.
+4 participants were excluded as a result of a technical error that led to their data not being recorded.
+The final sample consists 26 participants (Mean age = 20.9, SD = 2.0, range:[18, 25], Sex: 65.4% women, 34.6% men, 0.00% non-binary).
+The heart rate of one participant and response time of one participant were excluded from analysis due to extreme outlying values [**PLEASE HELP ME CONFIRM**].
+
+This study was approved by the NTU Institutional Review Board (NTU IRB-2018-10-029)(**TBC**) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
+All participants provided their informed consent prior to participation and were awarded with academic credit upon completion of the study.
 
@@
 
-Since theory of mind and empathy are closely related, *The Basic Empathy Scale (BES)* [@jolliffe2006development] was used as a subjective measure for theory of mind.
-*BES* uses a 40-item Likert scale to rate statements such as, "I can usually work out when people are cheerful" from 1-5.
-We also implemented the *Yoni Task,* which assesses the ability to judge mental states based on verbal cues, eye gaze and facial expression [@shamay2007dissociable].
+The *Basic Empathy Scale (BES)* is a 20-item, 5-point Likert scale (Strongly Disagree - Stongly Agree) that measures cognitive and affective empathy [@jolliffe2006development].
+Although TOM and empathy are regarded as distinct psychological constructs, abundant evidence points to them being closely related [@gallant2020developing; @sebastian2012neural], with empathy thought to be integrated in the affective dimension of TOM (i.e., the ability to infer what someone else is feeling) [@shamay2010role].
+The *Yoni Task*, which comprises 3 dimensions, namely cognitive, physical and affective, was also administered to assess participants' objective TOM ability [@shamay2007dissociable].
 
@@
 
-To measure interoception, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart], where participants count their heart beats without taking their pulse, as well as provide a confidence rating for their estimate.
-At the same time their true heart rate is recorded and the scores are compared to determine the individual's accuracy.
-They also completed the *MAIA questionnaire* [@mehling2012multidimensional], that featured 32 statements such as "I can use my breath to reduce tension" on a 1-5 Likert scale.
+To measure interoceptive accuracy, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart] while having their heart beats recorded.
+During the HCT task, participants were instructed to count the number of heart beats they felt over 5 varying time periods (20s, 25s, 30s, 35s, 40s) administered in a randomized order.
+After each time period, interoceptive sensibility was assessed by having participants respond how confident they were of their counting accuracy using a visual analog scale.
+Furthermore, participants also completed the *MAIA-2 questionnaire* [@mehling2012multidimensional], a 32-item scale that measures 8 dimensions of interoception (Noticing, Not-Distracting, Not-Worrying, Attention, Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust) using a 5-point Likert scale(Never-Always).
 
-### Deception
+### Lie Profile
 
-We used the *LIE Scale*, which is a 44-item questionnaire examining deception as a dispositional trait, and measures the participant propensity towards lie frequency, ability, contextuality and negativity [@makowski2021structure].
+We used the *LIE Scale*, a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency) on a visual analog scale (Disagree-Agree) [@makowski2021structure].
 
@@
 
-The demographic information we collected was age, ethnicity, nationality, dominant hand (for application of EDA electrodes), education level (determined by highest qualification received, or in the midst of achieving), religion and duration lived in Singapore.
+We further collected demographic information including age, ethnicity, nationality, handedness (for application of EDA electrodes), religion, duration lived in Singapore as well as highest education qualification achieved (or in the midst of achieving).
+
+### Deception Task Paradigm
+
+A novel and computerized directed-lying experimental paradigm was designed to assess participants' lying ability in different scenarios.
+Each *Deception Task* trial is comprised of a question presented on a computer screen with an accompanying instruction that either asked participants to verbally lie or tell the truth.
+The instructions for each trial were displayed briefly, for a maximum of 10 seconds, or until the participants responded accordingly.
+Notably, these questions were either phrased directly (*"What is your favourite sport?*) or indirectly (*"Is your favourite sport Hockey?"*).
+The *Deception Task* paradigm consists of 2 conditions - namely, the *Interrogation Condition* and the *Polygraph Condition*.
+
+In the **Interrogation Condition**, social feedback in the form of a video stream with an examiner was presented to participants during each trial.
+Participants were informed that the examiner would be evaluating the truthfulness of their responses by observing through the live video feed, when in actuality, the video was a pre-recorded video clip of a confederate.
+This was done to heighten the salience of social cues so as to facilitate participants' TOM abilities.
+
+In the *Polygraph condition*, cardiac feedback in the form of an electrocardiogram (ECG) was presented to participants during each trial Participants were informed that they were being shown live feedback of their own physiological signals when in fact, the displayed ECG was of a prerecorded video clip.
+This was done in order to heighten the salience of interoceptive cues and facilitate participants' interoceptive abilities.
+
+Following each response, participants were asked to rate their confidence in the success of their truth or lie-telling before progressing to the next trial.
 
@@
 
-Each subject was briefed on the experimental procedure and study aims, and signed an informed consent document prior to the study commencing.
-During the first phase of the experiment, demographic measures were taken, followed by measures of Theory of Mind and interoceptive abilities, as described above.
-Participants were then connected to an ECG before proceeding with the deception task on a computer.
+In the first phase of the study, participants answered a brief demographic survey before being administered a battery of questionnaires (*BES*, *MAIA-2*, *Lie Scale*) and cognitive-behavioural tasks (*HCT*, *Yoni Task*).
+This series of tasks and questionnaires were administered in a randomized order [**TBC**] in order to ensure there were no order effects.
+In the second phase of the study, the *Deception Task* paradigm was presented to participants.
+Similar to the first phase, the order sequence of the 2 conditions (*polygraph* vs *interrogation*) was randomized [**TBC**], with each condition comprising 20 trials.
+In total, each participant underwent 40 *Deception Task* trials, of which they had to respond with either lies or truths depending on the given instruction.
 
-#### Deception Task
-
-Participants underwent 40 trails of a directed lying task, where they were asked questions such as, "What secondary school did you go to?".
-Answers were provided verbally and participant pressed a button when they were finished, at which point they would be connected for 10 seconds to the condition-unique stimulus.
-There were two conditions of 20 trails each, beginning with the *interrogation condition*, and followed by the second, *polygraph condition*.
-The purpose of these conditions was to draw out the interoceptive or theory of mind abilities by providing feedback cues that would cause them to focus their attention on either the visual feedback cues from other people, or their own cardiac response.
-
-In the *interrogation condition*, participants were instructed that following their lie, a live examiner over video feed would appear briefly to judge whether they were truthful or not.
-In actuality, the video of the examiner shown was pre-recorded and the same for all participants.
-We hypothesized that participants would will rely on theory of mind abilities to predict whether their lie to the examiner was successfully accepted as true.
-We hypothesized that in this condition, participants would rely on their theory of mind abilities to discern the facial feedback cues from the examiner to ascertain whether their lie was successful.
-
-The *polygraph condition* followed the same routine, however instead of a receiving feedback from an interrogator, following the lie, a video of physiological signals was shown.
-We hypothesized that when participants were made acutely aware of such signals through false feedback, they would rely on interoceptive abilities to be more mindful or intentional about modulating the signals that may give them away.
-The physiological signals in this condition are also false feedback, and pre-recorded and identical for all participants.
-
-During each trial, the time it took for participants to answer was recorded, and their heart rates are measured using an ECG.
-Following the trial, participants gave a confidence rating for how successful they believe their lie or truth was.
-Debriefing was provided following the study.
-At this time the truthful answers to the directed lie questions were collected via questionnaire.
+Physiological recording devices were prepared prior to beginning the experimental paradigm.
+Using three ECG electrodes placed according to a modified Lead II configuration [@takuma1995alternative], cardiovascular activity was recorded via the BioPac MP160 system (BioPac Systems Inc., USA) and the AcqKnowledge 5.0 software.
+Events were marked by a photosensor attached to the screen.
 
@@
 Marginal contrasts analysis was also performed to clarify the differences between conditions.
-To allow for a better quantification of the uncertainty associated with the effects, as well increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework [**ref makowski2019existence**], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).
+To allow for a better quantification of the uncertainty associated with the effects, as well increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework [@makowski2019bayestestr], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).
 
@@
 
-The data analysis was carried out using R, the *brms* package [*REF*] and the *easystats* ecosystem **[REFS]**.
-As the full reproducible analysis script and statistical results are available at **[INSERT LINK]**, we will only focus on significant results in the manuscript.
+The data analysis was carried out using*R 4.2* [@RCoreTeam2022], *brms* [@Burkner2017], and the *easystats* collection of packages [@bayestestRArticle; @correlationArticle; @performanceArticle; @insightArticle].
+As the full reproducible analysis script and statistical results are available at [**https://github.com/DominiqueMakowski/DeceptionInteroTom**](https://github.com/DominiqueMakowski/DeceptionInteroTom){.uri}, we will only focus on significant results in the manuscript.
 
@@
 
-The 3 YONI-task dimensions and the 2 BES traits were combined into a unique factor, labelled *Theory of Mind* (explaining 35.76% of variance).
+The 3 YONI-task dimensions and the 2 BES traits were combined into a unique factor, labelled *TOM* (explaining 35.76% of variance).
 It was loaded by the cognitive (.89), affective (.77), physical (.45) YONI dimension, and the affective (.41) and cognitive (.17) traits of the BES.
@@
 
-The composite *ToM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67%\%$), specifically in the polygraph condition.
+The composite *TOM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67%\%$), specifically in the polygraph condition.
 No significant effect was found heart rate, and no correlation with the deception scale traits.

### 2022-11-04 paper/manuscript.Rmd
manu

@@
 
-A novel and computerized directed-lying experimental paradigm was designed to assess participants' lying ability in different scenarios.
+We designed a computerized directed-lying experimental paradigm (the *Deception Task*) to assess participants' lying ability in different scenarios.
 Each *Deception Task* trial is comprised of a question presented on a computer screen with an accompanying instruction that either asked participants to verbally lie or tell the truth.
-The instructions for each trial were displayed briefly, for a maximum of 10 seconds, or until the participants responded accordingly.
+The instructions for each trial were displayed for a maximum of 10 seconds, or until the participants responded.
 Notably, these questions were either phrased directly (*"What is your favourite sport?*) or indirectly (*"Is your favourite sport Hockey?"*).
@@
 
-This study aimed to examine the relationship between theory of mind and interoception on lie confidence, reaction time and physiological arousal during deception.
-This was achieved through a directed lying task in which participants underwent two conditions of false feedback where they were intended to rely on either interoceptive or theory of mind abilities.
-To our knowledge, this is the first study which has shown a clear link between interoceptive abilities and cardiac regulation during the act of deception.
-As this relationship was largely found in the polygraph condition that was designed to draw out the interoceptive abilities within the individual, we can conclude that our manipulation was successful.
-This taken with high confidence ratings in participant's lying abilities, also indicates other potential factors at play.
+This study aimed to examine the relationship between TOM and interoception on deceptive ability.
+Whereas there lies an abundance of deception literature associated with social cognition and emotion regulation, most of the research had been focused on deception detection, leaving a paucity in the studies pertaining to lying ability.
+Through our bimodal feedback *Deception Task* paradigm, our results found a significant positive correlation between interoception and confidence in one's own lies.
+This is not only in line with @murphy2019classifying's findings on interoceptive awareness and interoceptive sensibility, but also extends their influence to other high order cognitve processes such as lying
 

### 2022-11-07 paper/manuscript.Rmd
manu updates

@@
 In this post-truth era, deception has become increasingly prevalent in our everyday lives [@lewandowsky2017beyond].
-Although the act of deceiving is complex and cognitively taxing [@abe2007deceiving], often requiring effortful self-regulation to conceal [@krokoszinski2016emotion], research shows that people tend to under-estimate their ability to successfully deceive others [@elaad2003effects].
-Moreover, meta-analytic findings suggest that the ability of the liar plays a more significant role than the lie detector in deceptive interactions [@verigin2019lie; @bond2008individual; @levine2011sender].
-However, relative to the abundant literature regarding deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], surprisingly little attention has been conferred to investigating the inter-individual differences in people's ability to successfully lie.
+Although the act of deceiving is regarded as complex and often requires effortful self-regulation to conceal [@abe2007deceiving; @krokoszinski2016emotion], research shows that people tend to under-estimate their ability to successfully lie [@elaad2003effects].
+However, relative to the abundant literature regarding deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], surprisingly little attention has been conferred to investigating the inter-individual differences in people's ability to lie.
+Given meta-analytic findings wherein the deceptive ability of the liar is suggested to be more important than the lie detector in deceptive interactions [@verigin2019lie; @bond2008individual; @levine2011sender], it is perhaps more pertinent to investigate what makes someone a better liar.
 
@@
 TOM refers to the ability to infer that others have mental states, such as beliefs, emotions and intentions, distinct from ourselves [@lee2021lying; @wellman2001meta; @baron1997mindblindness].
-Indeed, the capacity to tell lies, as well as the complexity of lies told, have previously been found to be associated with higher TOM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role].
+Indeed, the capacity to tell lies, as well as the complexity of lies told, have previously been found to be related to higher TOM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role].
 Furthermore, the deceptive capabilities of children is often used as a measure of their TOM abilities.
-However, given the view that development of TOM abilities serve as the building blocks of other higher order cognitive processes [@ketelaars2010dynamics; @isaksson2021s], studies investigating the links between TOM and lying ability have predominantly been focused on children and individuals with neurocognitive deficits [@beaudoin2020systematic; @bora2017meta; @roheger2022progression].
-As such, little is known with regards to the role TOM plays in the lying ability of neurotypical adults.
-
-<!-- Defining interoceptive processes -->
-
-Alternatively, the variability observed in interoception, broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].
-Following @garfinkel2015knowing's three-dimensional framework, interoception is comprised of distinct facets, namely - *interoceptive accuracy*, the objective ability to monitor internal bodily signals; *interoceptive sensibility*, the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness*, the metacognitive awareness of one's interoceptive accuracy (i.e., accuracy-confidence correspondence).
-
-<!-- While interoceptive sensibility may be an important component, the correspondence between the confidence and accuracy, or interoceptive awareness appears to be associated with the downregulation of emotional responses and their associated physiological symptoms [@fustos2013embodiment; @critchley2017interoception; @critchley2018influence].
--->
+However, studies investigating the links between TOM and lying ability have predominantly been focused on children and individuals with neurocognitive deficits [@beaudoin2020systematic; @bora2017meta; @roheger2022progression]; likely a result of the view of TOM as the foundation of other higher order cognitive processes [@ketelaars2010dynamics; @isaksson2021s].
+As such, little is known regarding the role TOM plays in the lying ability of healthy adults.
 
@@
 
-Given the influence of interoceptive abilities on higher order cognition, particularly with regards to emotional processing  [@barrett2015interoceptive; @petzschner2021computational; @vabba2022interoceptive], it is possible that interoception bears an effect on people's capacity to tell lies.
-Although there has been little research investigating the links between interoception and deceptive ability *per se*, some studies have found heightened self-focus towards internal bodily signals to result in an increased demonstration of apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening].
-In line with these findings, @vabba2022interoceptive reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high (relative to low), whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
+Alternatively, differences in interoception could also be a factor worthy of consideration.
+Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].
 
-In contrast, however, the somatic marker hypothesis posits higher interoception to be associated with a propensity towards making rational decisions [@damasio1996somatic].
-Indeed, previous research has shown a negative correlation between interoceptive awareness and the likelihood to make risky decisions [@dunn2010listening; @furman2013interoceptive].
-Taking these mixed findings to perspective with the lack of consideration for the multidimensional nature of interoception in past studies, as well as the paucity in research linking deceptive ability with interoception, more studies are warranted to examine the relationship between interoception and deception.
+Given the established link between interoceptive abilities and emotional processing [@barrett2015interoceptive; @petzschner2021computational; @vabba2022interoceptive], it is possible that interoception bears influence on people's capacity to tell lies.
+Although there has been little research investigating the relationship between interoception and deceptive ability *per se*, some studies have found heightened self-focus towards internal bodily signals to be associated with an increased demonstration of apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening].
+In line with these findings, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high (relative to low), whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
+
+In contrast, previous decision-making studies have shown a negative correlation between interoceptive awareness and one's likelihood of making risky decisions [@dunn2010listening; @furman2013interoceptive].
+In fact, this is consistent with the somatic marker hypothesis, which posits interoception to be associated with a propensity towards making rational decisions [@damasio1996somatic].
+While the literature pertaining to interoception seems contradictory, it is possible that these mixed findings are a result of a failure to take into consideration interoception's multidimensionality.
+According to @garfinkel2015knowing's three-dimensional framework, interoception is comprised of three distinct facets, namely - *interoceptive accuracy*, the objective ability to monitor internal bodily signals; *interoceptive sensibility*, the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness*, the metacognitive awareness of one's interoceptive accuracy (i.e., accuracy-confidence correspondence).
+However, previous interoception research has largely been focused on interoceptive accuracy [@wallman2021physical].
+Taking this to perspective with the paucity in studies linking deceptive ability with interoception, more studies are warranted to comprehensively examine the relationship between interoception and deception.
 
@@
 
-This study aims at exploring the relationship between TOM and interoception with deceptive ability.
-Despite the criticism surrounding the somatic marker hypothesis [@dunn2006somatic; @maia2004reexamination], interoception has been shown to be associated with goal-directed behaviours and positively influence rational decision-making in ambiguous situations [@poppa2018somatic; @naqvi2014insula; @avery2017brain].
-As such, we expect individuals higher in interoception to exhibit better lying ability, as indicated by higher lie confidence, lower physiological arousal and shorter response time in the polygraph condition.
-In the interrogation condition, we expect people with higher TOM abilities to exhibit be better at lying, as indicated by higher low confidence, lower physiological arousal and shorter response time.
+The aim of the present study was to explore the interplay effects of TOM and interoception on individuals' deceptive ability, as indicated by their lie confidence, physiological arousal and response time.
+To this end, we designed a directed-lying bi-modal feedback paradigm comprising 2 conditions ( *Interrogation* vs *Polygraph*) with distinct feedback cues.
+In particular, salient social feedback cues were conferred during the *Interrogation condition*, whereas physiological feedback cues were given during the *Polygraph condition*.
+We expected interoception to positively predict lying ability in the *Polygraph condition*, and have no significant effect on one's ability to lie in the *Interrogation condition*.
+Similarly, we hypothesized that TOM would positively predict individuals' capability in lying in the *Interrogation condition* and exhibit non-significant effects in the *Polygraph condition*.
 
@@
 Along with open science standards, the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) for this research is available at [**https://github.com/DominiqueMakowski/DeceptionInteroTom**](https://github.com/DominiqueMakowski/DeceptionInteroTom){uri.}.
-
-The plan for this study was preregistered **(OSF?)**.
 
@@
 The final sample consists 26 participants (Mean age = 20.9, SD = 2.0, range:[18, 25], Sex: 65.4% women, 34.6% men, 0.00% non-binary).
-The heart rate of one participant and response time of one participant were excluded from analysis due to extreme outlying values [**PLEASE HELP ME CONFIRM**].
+The heart rate of one participant and response time of one participant were excluded from further analysis due to extreme outlying values [**PLEASE HELP ME CONFIRM**].
 
@@
 
-The *Basic Empathy Scale (BES)* is a 20-item, 5-point Likert scale (Strongly Disagree - Stongly Agree) that measures cognitive and affective empathy [@jolliffe2006development].
-Although TOM and empathy are regarded as distinct psychological constructs, abundant evidence points to them being closely related [@gallant2020developing; @sebastian2012neural], with empathy thought to be integrated in the affective dimension of TOM (i.e., the ability to infer what someone else is feeling) [@shamay2010role].
+The *Basic Empathy Scale (BES)* is a 20-item, 5-point Likert scale (Strongly Disagree - Strongly Agree) that measures cognitive and affective empathy [@jolliffe2006development].
+Although TOM and empathy are regarded as distinct psychological constructs, previous research findings point to them being closely related [@gallant2020developing; @sebastian2012neural].
+Specifically, empathy is often thought to be an integral component in the affective dimension of TOM (i.e., the ability to infer what someone else is feeling) [@shamay2010role].
 The *Yoni Task*, which comprises 3 dimensions, namely cognitive, physical and affective, was also administered to assess participants' objective TOM ability [@shamay2007dissociable].
@@
 
-To measure interoceptive accuracy, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart] while having their heart beats recorded.
-During the HCT task, participants were instructed to count the number of heart beats they felt over 5 varying time periods (20s, 25s, 30s, 35s, 40s) administered in a randomized order.
-After each time period, interoceptive sensibility was assessed by having participants respond how confident they were of their counting accuracy using a visual analog scale.
-Furthermore, participants also completed the *MAIA-2 questionnaire* [@mehling2012multidimensional], a 32-item scale that measures 8 dimensions of interoception (Noticing, Not-Distracting, Not-Worrying, Attention, Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust) using a 5-point Likert scale(Never-Always).
+To assess particpants' interoceptive ability, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart] while having their actual heartbeats recorded.
+During the HCT task, participants were instructed to count the number of heartbeats they felt over 5 trials with varying time intervals (20s, 25s, 30s, 35s, 40s), the sequence of which was randomized.
+Interoceptive accuracy (*HCT Accuracy*) was then computed based on the absolute difference between the actual number of heartbeats and the number of heartbeats counted during each trial.
+To assess their interoceptive sensibility (*HCT Confidence*), participants were asked to indicate, on a visual analog, how confident they were of their heartbeat counting accuracy at the end of each trial.
+
+The *MAIA-2* [@mehling2012multidimensional], a 32-item questionnaire which measures 8 dimensions of interoception (Noticing, Not-Distracting, Not-Worrying, Attention, Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust) using a 5-point Likert scale (Never-Always) was also administered.
 
@@
 
-We used the *LIE Scale*, a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency) on a visual analog scale (Disagree-Agree) [@makowski2021structure].
+To evaluate participants' tendency to lie in their everyday lives, we used the *LIE Scale*, a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency) on a visual analog scale (Disagree-Agree) [@makowski2021structure].
 
@@
 
-We designed a computerized directed-lying experimental paradigm (the *Deception Task*) to assess participants' lying ability in different scenarios.
-Each *Deception Task* trial is comprised of a question presented on a computer screen with an accompanying instruction that either asked participants to verbally lie or tell the truth.
-The instructions for each trial were displayed for a maximum of 10 seconds, or until the participants responded.
-Notably, these questions were either phrased directly (*"What is your favourite sport?*) or indirectly (*"Is your favourite sport Hockey?"*).
-The *Deception Task* paradigm consists of 2 conditions - namely, the *Interrogation Condition* and the *Polygraph Condition*.
+We designed a computerized directed-lying experimental paradigm (the *Deception Task*) consisting of 2 conditions (the *Interrogation Condition* and the *Polygraph Condition*) to assess participants' lying ability.
 
-In the **Interrogation Condition**, social feedback in the form of a video stream with an examiner was presented to participants during each trial.
-Participants were informed that the examiner would be evaluating the truthfulness of their responses by observing through the live video feed, when in actuality, the video was a pre-recorded video clip of a confederate.
-This was done to heighten the salience of social cues so as to facilitate participants' TOM abilities.
+In the **Interrogation Condition**, participants' response to each trial was followed by social feedback in the form of a video stream with an examiner.
+Notably, participants were informed that the examiner would be evaluating the truthfulness of their responses by observing them through the live video feed.
+In actuality, the video was a pre-recorded video clip of a confederate, and the same video-clip was presented to all participants.
 
-In the *Polygraph condition*, cardiac feedback in the form of an electrocardiogram (ECG) was presented to participants during each trial Participants were informed that they were being shown live feedback of their own physiological signals when in fact, the displayed ECG was of a prerecorded video clip.
-This was done in order to heighten the salience of interoceptive cues and facilitate participants' interoceptive abilities.
+In the *Polygraph condition*, participants' response to each trial was followed by physiological feedback in the form of an electrocardiogram (ECG) instead.
+Specifically, participants were informed that they were being shown live feedback of their own physiological signals when in fact, the displayed ECG was that of a pre-recorded video clip.
+Similar to the *Interrogation Condition*, all participants were shown the same pre-recorded video clip of an electrocardiogram.
 
-Following each response, participants were asked to rate their confidence in the success of their truth or lie-telling before progressing to the next trial.
+Regardless of the task condition, participants were presented with a question, either phrased directly (*"What is your favourite sport?*), or indirectly (*"Is your favourite sport Hockey?"*), on a computer screen with accompanying instructions that either asked participants to verbally lie or tell the truth following each *Deception Task* trial.
+These instructions were displayed for a maximum of 10 seconds, or until the participants responded.
+Following each response, participants were then asked to rate their confidence in how convincing their answer was, before progressing to the next trial.
 
@@
 In the first phase of the study, participants answered a brief demographic survey before being administered a battery of questionnaires (*BES*, *MAIA-2*, *Lie Scale*) and cognitive-behavioural tasks (*HCT*, *Yoni Task*).
-This series of tasks and questionnaires were administered in a randomized order [**TBC**] in order to ensure there were no order effects.
+This series of tasks and questionnaires were administered in a randomized order [**TBC**] in order to control for order effects.
 In the second phase of the study, the *Deception Task* paradigm was presented to participants.
-Similar to the first phase, the order sequence of the 2 conditions (*polygraph* vs *interrogation*) was randomized [**TBC**], with each condition comprising 20 trials.
-In total, each participant underwent 40 *Deception Task* trials, of which they had to respond with either lies or truths depending on the given instruction.
+Similar to the first phase, the order sequence of the 2 conditions (*polygraph* vs *interrogation*) was randomized [**TBC**], with each condition comprising 40 trials.
+Within each condition, participants were instructed to lie in half of the trials (20 truth trials; 20 lie trials).
+In total, each participant underwent 80 *Deception Task* trials, of which they had to respond with either lies or truths depending on the given instruction.
 
 Physiological recording devices were prepared prior to beginning the experimental paradigm.
-Using three ECG electrodes placed according to a modified Lead II configuration [@takuma1995alternative], cardiovascular activity was recorded via the BioPac MP160 system (BioPac Systems Inc., USA) and the AcqKnowledge 5.0 software.
+Using three ECG electrodes placed according to a modified Lead II configuration [@takuma1995alternative], cardiovascular activity, sampled at 1000Hz (**TBC**) was recorded via the BioPac MP160 system (BioPac Systems Inc., USA) and the AcqKnowledge 5.0 software.
 Events were marked by a photosensor attached to the screen.
@@
 The manipulation checks consist of testing whether there is an effect of question phrasing (direct vs.
-indirect), and condition (polygraph *vs.* interrogation), on our 3 outcome variables: the participants' ratings of confidence that their answers (lies *vs.* truths) were convincing, the response time (RT), and the heart rate change associated with the response.
+indirect), and condition (polygraph *vs.* interrogation), on our 3 outcome variables: the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT), and the heart rate change associated with the response.
 This analysis was performed using mixed models with the participants and questions both entered as random factors.
 Marginal contrasts analysis was also performed to clarify the differences between conditions.
-To allow for a better quantification of the uncertainty associated with the effects, as well increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework [@makowski2019bayestestr], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).
+To allow for a better quantification of the uncertainty associated with the effects, as well as increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework [@makowski2019bayestestr], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).
 
-To further counterbalance the low number of participants and maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, theory of mind and interoception).
-We used factor analysis (using the method agreement procedure to estimate the optimal number of dimensions, **REF PARAMETERS PKG**), rather PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained.
+To further counterbalance the low number of participants and maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, TOM and interoception).
+We favoured the use of factor analysis (using the method agreement procedure to estimate the optimal number of dimensions, @parametersArticle), over PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained.
 Then, we modeled the relationship between these inter-individual composite scores (the analysis for all the variables is included in Supplementary Materials) and the 3 outcome variables in interaction with the condition (polygraph *vs.* interrogation).
@@
 The composite *TOM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67%\%$), specifically in the polygraph condition.
-No significant effect was found heart rate, and no correlation with the deception scale traits.
+No significant effect was found with regards to heart rate, and no correlation was observed with dispositional lying traits.
 
@@
 No significant association was found with heart rate.
-This score also correlated with the deception *Contextuality* trait ($r = 0.50,~95\%~CI~[0.04, 0.64],~BF_{10} = 3.48\%$).
+This score also correlated with the dispositional lying *Contextuality* trait ($r = 0.50,~95\%~CI~[0.04, 0.64],~BF_{10} = 3.48\%$).
 
 The *Focus* interoception score was significantly associated with an increased confidence in truthful responses in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$) and interrogation condition ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76%\%$).
-No significant association was found with RT or heart rate, but the score correlated with the deception *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$).
+No significant association was found with RT or heart rate, but the score correlated with the dispositional lying *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$).
 
@@
 
-This study aimed to examine the relationship between TOM and interoception on deceptive ability.
-Whereas there lies an abundance of deception literature associated with social cognition and emotion regulation, most of the research had been focused on deception detection, leaving a paucity in the studies pertaining to lying ability.
-Through our bimodal feedback *Deception Task* paradigm, our results found a significant positive correlation between interoception and confidence in one's own lies.
-This is not only in line with @murphy2019classifying's findings on interoceptive awareness and interoceptive sensibility, but also extends their influence to other high order cognitve processes such as lying
+While there is extensive literature associating deception with social cognition and emotion regulation, most of such research had been focused on deception detection, leaving a paucity in the studies pertaining to lying ability.
+This study hence seeks to address this research gap, further aiming to examine the interplay effect of TOM and interoception on deceptive ability.
+Using a bi-modal feedback deception task paradigm, participants were found to report significantly lower lie confidence in the *Polygraph condition*, relative to the *Interrogation condiiton*.
+Notably, we also found a significant association between several facets of interoception with individuals' lie confidence and response time in the polygraph condition.
+Taken together, this could be suggestive of people's greater reliance on social feedback cues when telling lies
 

### 2022-11-09 paper/manuscript.Rmd
discussion

@@
 Indeed, the capacity to tell lies, as well as the complexity of lies told, have previously been found to be related to higher TOM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role].
-Furthermore, the deceptive capabilities of children is often used as a measure of their TOM abilities.
+Furthermore, the deceptive capabilities of children is often used as a measure of their skills in TOM.
 However, studies investigating the links between TOM and lying ability have predominantly been focused on children and individuals with neurocognitive deficits [@beaudoin2020systematic; @bora2017meta; @roheger2022progression]; likely a result of the view of TOM as the foundation of other higher order cognitive processes [@ketelaars2010dynamics; @isaksson2021s].
@@
 
-Alternatively, differences in interoception could also be a factor worthy of consideration.
-Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].
+Alternatively, interoceptive abilities could also influence inter-individual differences in lying.
+Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing's conceptualizes interoception as a three-dimensional framework comprising three distinct facets, namely - *interoceptive accuracy*, the objective ability to monitor internal bodily signals; *interoceptive sensibility*, the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness*, the metacognitive awareness of one's interoceptive accuracy (i.e., accuracy-confidence correspondence).
+Interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].
+Although little research interest has been conferred to investigating the relationship between interoception and deceptive ability *per se*, previous decision-making studies have demonstrated a negative correlation between interoceptive awareness, a metacognitive dimension of interoception, and one's likelihood to make risky decisions [@dunn2010listening; @furman2013interoceptive].
+In fact, this is consistent with the somatic marker hypothesis, which posits interoception is associated with a propensity towards making rational decisions [@damasio1996somatic].
 
-Given the established link between interoceptive abilities and emotional processing [@barrett2015interoceptive; @petzschner2021computational; @vabba2022interoceptive], it is possible that interoception bears influence on people's capacity to tell lies.
-Although there has been little research investigating the relationship between interoception and deceptive ability *per se*, some studies have found heightened self-focus towards internal bodily signals to be associated with an increased demonstration of apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening].
-In line with these findings, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high (relative to low), whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
+In contrast, some studies have instead found heightened interoceptive attention, one's self-focus towards internal bodily signals, to predict apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening].
+Extending these findings to social cognition, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high (relative to low), whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
 
-In contrast, previous decision-making studies have shown a negative correlation between interoceptive awareness and one's likelihood of making risky decisions [@dunn2010listening; @furman2013interoceptive].
-In fact, this is consistent with the somatic marker hypothesis, which posits interoception to be associated with a propensity towards making rational decisions [@damasio1996somatic].
 While the literature pertaining to interoception seems contradictory, it is possible that these mixed findings are a result of a failure to take into consideration interoception's multidimensionality.
-According to @garfinkel2015knowing's three-dimensional framework, interoception is comprised of three distinct facets, namely - *interoceptive accuracy*, the objective ability to monitor internal bodily signals; *interoceptive sensibility*, the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness*, the metacognitive awareness of one's interoceptive accuracy (i.e., accuracy-confidence correspondence).
-However, previous interoception research has largely been focused on interoceptive accuracy [@wallman2021physical].
+Indeed, previous interoception research has largely been focused on examining interoceptive accuracy [@wallman2021physical].
 Taking this to perspective with the paucity in studies linking deceptive ability with interoception, more studies are warranted to comprehensively examine the relationship between interoception and deception.
-
-<!-- Interoceptive processes are not only a key component of forming your own emotions, but may also facilitate being in tune with the emotional states of others [@konvalinka2011synchronized; @garfinkel2016discrepancies].
-This corresponds to situations involving deception, since much of the existing literature examining the link between interoceptive abilities has focused on how it may implicitly flag that one is being lied to through an elevated cardiac response [@gunderson2021body], and skin temperature [@van2014registered].
-While research indicates that attending to ones interoceptive cues improves success in unmasking detection [@ten2019different], there is limited information how interoceptive skills may function the other way around, in the case of the liar.
--->
-
-<!-- As identified by @murphy2022propensity, the propensity to use interoceptive information, and in what manner remains an underdeveloped area in research, and may illuminate the mechanisms underlying physiological and emotional control exhibited by successful liars [@krokoszinski2016emotion; @wielgopolan2021can].
--->
 
@@
 To this end, we designed a directed-lying bi-modal feedback paradigm comprising 2 conditions ( *Interrogation* vs *Polygraph*) with distinct feedback cues.
-In particular, salient social feedback cues were conferred during the *Interrogation condition*, whereas physiological feedback cues were given during the *Polygraph condition*.
-We expected interoception to positively predict lying ability in the *Polygraph condition*, and have no significant effect on one's ability to lie in the *Interrogation condition*.
-Similarly, we hypothesized that TOM would positively predict individuals' capability in lying in the *Interrogation condition* and exhibit non-significant effects in the *Polygraph condition*.
+In particular, salient social feedback cues were conferred during the *Interrogation condition*, whereas visual biofeedback cues were given during the *Polygraph condition*.
+We expected interoception to positively predict lying ability in the *Polygraph condition*; participants with better interoception would exhibit higher lie confidence, shorter response time and lower physiological arousal.
+Alternatively, we hypothesized TOM would positively predict individuals' capability in lying in the *Interrogation condition*.
 
@@
 
-This study was approved by the NTU Institutional Review Board (NTU IRB-2018-10-029)(**TBC**) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
+This pre-registered study (**OSF?**) was approved by the NTU Institutional Review Board (NTU IRB-2018-10-029)(**TBC**) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
 All participants provided their informed consent prior to participation and were awarded with academic credit upon completion of the study.
@@
 
-The *Basic Empathy Scale (BES)* is a 20-item, 5-point Likert scale (Strongly Disagree - Strongly Agree) that measures cognitive and affective empathy [@jolliffe2006development].
+The *Basic Empathy Scale (BES)*, a 20-item, 5-point Likert scale (Strongly Disagree - Strongly Agree) that measures cognitive and affective empathy [@jolliffe2006development] was administered.
 Although TOM and empathy are regarded as distinct psychological constructs, previous research findings point to them being closely related [@gallant2020developing; @sebastian2012neural].
 Specifically, empathy is often thought to be an integral component in the affective dimension of TOM (i.e., the ability to infer what someone else is feeling) [@shamay2010role].
-The *Yoni Task*, which comprises 3 dimensions, namely cognitive, physical and affective, was also administered to assess participants' objective TOM ability [@shamay2007dissociable].
+The *Yoni Task*, which comprises 3 dimensions, namely cognitive, physical and affective TOM, was also administered to assess participants' objective TOM ability [@shamay2007dissociable].
 
@@
 
-To assess particpants' interoceptive ability, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart] while having their actual heartbeats recorded.
+To assess participants' interoceptive ability, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart] while having their actual heartbeats recorded.
 During the HCT task, participants were instructed to count the number of heartbeats they felt over 5 trials with varying time intervals (20s, 25s, 30s, 35s, 40s), the sequence of which was randomized.
 Interoceptive accuracy (*HCT Accuracy*) was then computed based on the absolute difference between the actual number of heartbeats and the number of heartbeats counted during each trial.
-To assess their interoceptive sensibility (*HCT Confidence*), participants were asked to indicate, on a visual analog, how confident they were of their heartbeat counting accuracy at the end of each trial.
+To assess their interoceptive sensibility (*HCT Confidence*), participants were asked to rate, on a visual analog, how confident they were of their heartbeat counting accuracy at the end of each interval.
 
@@
 
-We designed a computerized directed-lying experimental paradigm (the *Deception Task*) consisting of 2 conditions (the *Interrogation Condition* and the *Polygraph Condition*) to assess participants' lying ability.
+We designed a directed-lying bi-modal feedback task (the *Deception Task*) consisting 2 conditions - namely, the *Interrogation* condition and the *Polygraph* condition.
 
-In the **Interrogation Condition**, participants' response to each trial was followed by social feedback in the form of a video stream with an examiner.
+In the *Interrogation* condition, participants were given social feedback in the form of a video stream with an examiner.
 Notably, participants were informed that the examiner would be evaluating the truthfulness of their responses by observing them through the live video feed.
@@
 
-In the *Polygraph condition*, participants' response to each trial was followed by physiological feedback in the form of an electrocardiogram (ECG) instead.
-Specifically, participants were informed that they were being shown live feedback of their own physiological signals when in fact, the displayed ECG was that of a pre-recorded video clip.
-Similar to the *Interrogation Condition*, all participants were shown the same pre-recorded video clip of an electrocardiogram.
+In the *Polygraph* condition, participants were given biofeedback in the form of an electrocardiogram (ECG) displayed onscreen instead.
+Specifically, participants were informed that they were being shown live feedback of their own heartbeats when in fact, the displayed ECG was that of a pre-recorded video clip.
+Similar to the *Interrogation* condition, all participants were shown the same pre-recorded video clip of the ECG.
 
-Regardless of the task condition, participants were presented with a question, either phrased directly (*"What is your favourite sport?*), or indirectly (*"Is your favourite sport Hockey?"*), on a computer screen with accompanying instructions that either asked participants to verbally lie or tell the truth following each *Deception Task* trial.
-These instructions were displayed for a maximum of 10 seconds, or until the participants responded.
-Following each response, participants were then asked to rate their confidence in how convincing their answer was, before progressing to the next trial.
+The sequence of each task trial was the same for both conditions.
+Using a computer, participants were first shown a question, either phrased directly (*"What is your favourite sport?*), or indirectly (*"Is your favourite sport Hockey?"*), with accompanying instructions below that either asked participants to verbally lie or tell the truth.
+Following a connecting screen (0.7 - 1.5s), participants were presented with either social (*Interrogation* condition) or biofeedback (*Polygraph* condition) that was displayed for a maximum of 10s or until they made their accorded response.
+A disconnecting screen was then displayed (1.5-2.5s), following which participants were asked to rate their confidence in how convincing they perceived their answer to be.
 
@@
 This series of tasks and questionnaires were administered in a randomized order [**TBC**] in order to control for order effects.
-In the second phase of the study, the *Deception Task* paradigm was presented to participants.
-Similar to the first phase, the order sequence of the 2 conditions (*polygraph* vs *interrogation*) was randomized [**TBC**], with each condition comprising 40 trials.
-Within each condition, participants were instructed to lie in half of the trials (20 truth trials; 20 lie trials).
-In total, each participant underwent 80 *Deception Task* trials, of which they had to respond with either lies or truths depending on the given instruction.
+In the second phase of the study, the *Deception Task* was conducted using PsychoPy [**REF**].
+Each participant was conferred both conditions of the *Deception Task*, the order sequence of which was randomized.
+Each task condition comprised 40 trials, of which participants were instructed to lie in half of the trials (20 **Truth** trials; 20 **Lie** trials).
+In total, each participant underwent 80 *Deception Task* trials.
 
@@
 Using three ECG electrodes placed according to a modified Lead II configuration [@takuma1995alternative], cardiovascular activity, sampled at 1000Hz (**TBC**) was recorded via the BioPac MP160 system (BioPac Systems Inc., USA) and the AcqKnowledge 5.0 software.
-Events were marked by a photosensor attached to the screen.
 
@@
 The fourth factor, labelled *Interoception - Regulation* (10.97%), was primarily loaded by MAIA not-worrying (.71), HCT Accuracy (.61) and MAIA Trusting (.40).
-However, due to the interpretation difficulty, we will refer to these dimensions with their main correlates in **Figure 1**.
+However, due to the interpretation difficulty, we will refer to these dimensions with their main correlates in **Figure 1** [**Note to fix caption for Figure 1 from HCT Trusting to MAIA trusting**].
 
@@
 
-While there is extensive literature associating deception with social cognition and emotion regulation, most of such research had been focused on deception detection, leaving a paucity in the studies pertaining to lying ability.
-This study hence seeks to address this research gap, further aiming to examine the interplay effect of TOM and interoception on deceptive ability.
-Using a bi-modal feedback deception task paradigm, participants were found to report significantly lower lie confidence in the *Polygraph condition*, relative to the *Interrogation condiiton*.
-Notably, we also found a significant association between several facets of interoception with individuals' lie confidence and response time in the polygraph condition.
-Taken together, this could be suggestive of people's greater reliance on social feedback cues when telling lies
+While there is an extensive body of literature associating deception with social cognition and emotion regulation, most research had been focused on their roles in deception detection, leaving a paucity in studies pertaining to their influence on lying ability.
+The present study hence seeks to address this research gap, further aiming to examine the interplay effect of TOM and interoception on our ability to lie convincingly.
+Notably, we found a significant difference in participants' lying ability (as measured by response time, heart rate and confidence ratings) between the *Polygraph* and *Interrogation* conditions.
+This hence confers support for the manipulation used in our experimental paradigm, demonstrating that increasing the attentional focus towards external (visual) interoceptive cues can enhance interoceptive sensitivity, therefore improving the precision of internal signals perceived.
+Extending the growing body of literature pertaining to the application of interoceptive training to improve emotion regulation [@sugawara2020effects; @quadt2021interoceptive; @wu2022enhanced], our study thus provides evidence that interoceptive sensitivity can be manipulated and thereby modified to guide our emotional responses.
 
-<!-- Participants relied on interoception -->
+<!-- Interoceptive vs Social Cues -->
+Using a bi-modal feedback deception task, we found partial support for our hypothesis.
+Specifically, participants reported lower lie confidence and took a longer time to respond, but were less physiologically aroused in the *Polygraph* condition, relative to the *Interrogation* condition.
+While this mixed finding is challenging to interpret, it is possible that one's interoceptive sensitivity, enhanced by the perceived interoceptive cues, interacted with the stress experienced in such deceptive interactions and led to a depletion of cognitive resources [@ten2015physically; @porter2012secrets].
+Indeed, the experience of excessive stress has been shown to impair interoceptive accuracy, leading to a hyper-focus on internal bodily signals [@schulz2015interoception].
+Furthermore, this is also in line with the established attentional switching hypothesis, which posits that an increase in attention towards internal signals and managing one's emotional reaction would confer less cognitive resources available for the actual act of telling a lie, thereby resulting in individuals taking a longer time to respond, and rating their lies with less confidence [@arnold2019interoception; @hanania2010selective].
+This interplay of interoception and maladaptive stress response, and their effect on lying ability hence underscores the complexity underlying successful deceptive behaviour.
 
-Our results show that participants who were telling the truth had a slower reaction time, and rated themselves as less confident in the polygraph condition, however, their heart rate averaged lower as compared to the interrogation condition.
-This suggests that despite the participant's lack of confidence, they were very in-tune with their physiological response in the polygraph condition, and successfully able to decrease their heart rate.
-Given that interoceptive accuracy is enhanced by focusing on it during a time of stress [@schulz2013cold], such as attempting to conceal deception combined with false physiological feedback delivered during the polygraph condition, this conclusion is in line with our hypothesis.
+<!-- Meta-Interoception, Emotion Regulation and Lying -->
+Consistent with our hypothesis, a significant positive association was predominantly found between metacognitive dimensions of interoception (*Meta* and *Regulation* interoception) and individuals' lie confidence when their physiological cues were salient.
+In contrast to previous studies [@pinna2020systematic; @fustos2013embodiment; @owens2018investigating; @pollatos2007heart], we did not find any significant relationship between individuals' interoception scores and objective heart rate.
+Taken together, these findings suggest that interoceptive awareness, in and of itself, is insufficient for adaptive emotion regulation.
+Indeed, some researchers have found positive links between interoceptive awareness and individuals' use of maladaptive strategies such as rumination [@tan2023interoceptive].
+Furthermore, hypervigilance to bodily signals is also positively related to somatization and psychopathological disorders such as anxiety [@wang2020intrinsic; @dunn2010can; @pollatos2007interoceptive].
+As such, further studies are necessary to examine what factors modulate the relationship between the metacognitve facets of interoception and emotion regulation.
 
-As the relationship between interoception and emotion is well established [@barrett2015interoceptive; @dobrushina2020interaction; @ohira2020predictive], our work is consistent with @wielgopolan2021can, who found that groups with higher emotional awareness made better liars and were more successful at regulating their emotional and physiological responses, as well as fabricating new ones.
+<!-- TOM -->
+Our results show a significant association between individuals' composite TOM score with lower lie confidence and longer response times when interoceptive cues were highly salient.
+Recent studies linking interoceptive abilities and social cognition with one's experience of self posit that an accurate sense of internal bodily signals is integral for individuals to maintain a distinction between self and other, while correctly inferring the mental states of others [@shah2017heart; @palmer2018going].
+Taking this to perspective with the predictive coding framework [@friston2010free], when interoceptive cues are highly salient, the resulting increase in interoceptive awareness will be conflicted against higher (more precise) exteroceptive TOM.
+To attenuate this conflict so as to maintain balance between our interoceptive and exteroceptive states, it is hence possible that individuals experienced a re-direction of their attentional resources from external to internally-focused signals to update higher order beliefs.
+Consistent with the attentional shift hypothesis [@arnold2019interoception; @hanania2010selective], this re-direction of cognitive resources away from that needed to convincingly tell a lie could thus have led to lower lie confidence and a longer response time.
 
-<!-- Metacognition and Interoception -->
+<!-- Potential Implications  -->
 
-Although participants were not explicitly directed to attend to their physiological signals as a means of evading deception detection, they were aware these signals were recorded and informed that their lies would be detected through their analysis.
-Additionally, the presence of the ECG likely made them aware, and these measures remained connected during the interrogation.
-This indicates that there was likely an explicit attentional component to the control exerted, which is further reflected by a broader theme in our results.
-Our results indicate that all interoceptive factors (*Meta, Listening, Focus and Regulation*) are associated with an increased confidence in deceptive abilities, and faster reaction time for lies in the polygraph condition.
-It logical that confidence in deception would be accompanied by faster reaction time.
-However, since confidence was a subjective measure, it does not necessarily reflect competence [@khalsa2008interoceptive].
-While our data indicates that participants were able to self-regulate using interoceptive abilities, this still highlights an important caveat, which is the potential metacognitive awareness at play [@garfinkel2015knowing].
-
-Metacognitive beliefs, or interoceptive awareness about competence in the quality of physiological regulation may influence the cognitive processes and development physiological responses.
-That is to say, that the appraisal is just as important to the process of deception by informing their true ability [@stephan2016allostatic; @harrison2021filter; @petzschner2021computational].
-
-<!-- Interoceptive sensibility and risk-taking -->
-
-High interoceptive sensibility regardless of true competence may also directly shape behaviour through the reduced perception of risk associated with being caught.
-Past research indicates the likelihood of deception increases when individuals judge a lower risk of being caught, based on situation-specific variables and their own qualities [@sip2012if; @sip2013pinocchio].
-These results may offer support to findings such as @vabba2022interoceptive where interoceptive abilities were found to be a significant moderator in the willingness to engage in riskier forms of deception, and offer insight into other risk behaviours linked with interoceptive ability such as cheating [@williams2016valjean] and risk-taking [@ditto2006visceral; @lenggenhager2013listening].
-
-<!-- Future Research -->
+<!-- Limitations and Future Research -->
+- NOTE: no significant correlation between HCT accuracy and MAIA dimensions (only HCT confidence sig correlates with MAIA dimensions of awarenss and regulation)
 

### 2022-11-10 paper/manuscript.Rmd
manu

@@
 Although the act of deceiving is regarded as complex and often requires effortful self-regulation to conceal [@abe2007deceiving; @krokoszinski2016emotion], research shows that people tend to under-estimate their ability to successfully lie [@elaad2003effects].
-However, relative to the abundant literature regarding deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], surprisingly little attention has been conferred to investigating the inter-individual differences in people's ability to lie.
-Given meta-analytic findings wherein the deceptive ability of the liar is suggested to be more important than the lie detector in deceptive interactions [@verigin2019lie; @bond2008individual; @levine2011sender], it is perhaps more pertinent to investigate what makes someone a better liar.
+However, relative to the abundant literature regarding deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], surprisingly little attention has been conferred to investigating the inter-individual differences in people's lying ability.
+Given meta-analytic findings wherein the deceptive ability of the liar is suggested to be more important than the lie detector in deceptive interactions [@verigin2019lie; @bond2008individual; @levine2011sender], it is perhaps more pertinent to investigate what makes someone a more convincing liar.
 
@@
 Alternatively, interoceptive abilities could also influence inter-individual differences in lying.
-Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing's conceptualizes interoception as a three-dimensional framework comprising three distinct facets, namely - *interoceptive accuracy*, the objective ability to monitor internal bodily signals; *interoceptive sensibility*, the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness*, the metacognitive awareness of one's interoceptive accuracy (i.e., accuracy-confidence correspondence).
+Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing's conceptualizes interoception as a three-dimensional framework comprising three distinct facets, namely - *interoceptive accuracy*, the objective ability to monitor internal bodily signals; *interoceptive sensibility*, the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness*, one's ability to identify and appropriately respond to their perceived interoceptive states.
 Interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].
@@
 Extending these findings to social cognition, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high (relative to low), whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
-
-While the literature pertaining to interoception seems contradictory, it is possible that these mixed findings are a result of a failure to take into consideration interoception's multidimensionality.
-Indeed, previous interoception research has largely been focused on examining interoceptive accuracy [@wallman2021physical].
-Taking this to perspective with the paucity in studies linking deceptive ability with interoception, more studies are warranted to comprehensively examine the relationship between interoception and deception.
+Taking these mixed findings to perspective with the paucity in research linking deceptive ability with interoception, more studies are warranted to comprehensively examine the relationship between interoception and deception.
 
@@
 During the HCT task, participants were instructed to count the number of heartbeats they felt over 5 trials with varying time intervals (20s, 25s, 30s, 35s, 40s), the sequence of which was randomized.
-Interoceptive accuracy (*HCT Accuracy*) was then computed based on the absolute difference between the actual number of heartbeats and the number of heartbeats counted during each trial.
-To assess their interoceptive sensibility (*HCT Confidence*), participants were asked to rate, on a visual analog, how confident they were of their heartbeat counting accuracy at the end of each interval.
+Objective interoceptive accuracy (*HCT Accuracy*) was then computed based on the following formula ($\HCT_{Acc} = 1-|actual-count|/(actual + count)/2)$) [**lol pls help me write this in proper syntax**).
+To assess their interoceptive sensibility (*HCT Confidence*), participants were asked to rate, on a visual analog scale, how confident they were of their heartbeat counting accuracy at the end of each interval.
+Interoceptive awareness (*HCT Awareness*) was indexed by the correspondence between one's objective interoceptive accuracy and their confidence ratings.
 
@@
 This series of tasks and questionnaires were administered in a randomized order [**TBC**] in order to control for order effects.
-In the second phase of the study, the *Deception Task* was conducted using PsychoPy [**REF**].
-Each participant was conferred both conditions of the *Deception Task*, the order sequence of which was randomized.
+In the second phase of the study, the *Deception Task* was conducted using PsychoPy [@peirce2019psychopy2].
+Each participant was administered both conditions of the *Deception Task*, the order sequence of which was randomized.
 Each task condition comprised 40 trials, of which participants were instructed to lie in half of the trials (20 **Truth** trials; 20 **Lie** trials).
@@
 Notably, we found a significant difference in participants' lying ability (as measured by response time, heart rate and confidence ratings) between the *Polygraph* and *Interrogation* conditions.
-This hence confers support for the manipulation used in our experimental paradigm, demonstrating that increasing the attentional focus towards external (visual) interoceptive cues can enhance interoceptive sensitivity, therefore improving the precision of internal signals perceived.
-Extending the growing body of literature pertaining to the application of interoceptive training to improve emotion regulation [@sugawara2020effects; @quadt2021interoceptive; @wu2022enhanced], our study thus provides evidence that interoceptive sensitivity can be manipulated and thereby modified to guide our emotional responses.
+This hence confers support for the manipulation used in our experimental paradigm, demonstrating that increasing the attentional focus towards visual interoceptive cues, even if they are fake, can elicit interoceptive awareness and enhance the precision of internal signals if such external cues of interoceptive signals are perceived to be real.
+Extending previous research pertaining to the application of interoceptive training for improving emotion regulation [@sugawara2020effects; @quadt2021interoceptive; @wu2022enhanced], our study thus provides evidence that interoceptive awareness can be manipulated and thereby modified to guide our emotional responses.
 
@@
 <!-- TOM -->
-Our results show a significant association between individuals' composite TOM score with lower lie confidence and longer response times when interoceptive cues were highly salient.
-Recent studies linking interoceptive abilities and social cognition with one's experience of self posit that an accurate sense of internal bodily signals is integral for individuals to maintain a distinction between self and other, while correctly inferring the mental states of others [@shah2017heart; @palmer2018going].
-Taking this to perspective with the predictive coding framework [@friston2010free], when interoceptive cues are highly salient, the resulting increase in interoceptive awareness will be conflicted against higher (more precise) exteroceptive TOM.
-To attenuate this conflict so as to maintain balance between our interoceptive and exteroceptive states, it is hence possible that individuals experienced a re-direction of their attentional resources from external to internally-focused signals to update higher order beliefs.
-Consistent with the attentional shift hypothesis [@arnold2019interoception; @hanania2010selective], this re-direction of cognitive resources away from that needed to convincingly tell a lie could thus have led to lower lie confidence and a longer response time.
-
-<!-- Potential Implications  -->
+Our results show a significant association between individuals' composite TOM score with lower lie confidence and longer response time when interoceptive cues were highly salient.
+Under the free energy principle [@friston2010free], interoception is regarded as integral in TOM [@shah2017heart; @palmer2018going; @ondobaka2017role].
+Specifically, during social inference, interoceptive signals are integrated with exteroceptive (e.g., visual and auditory) and proprioceptive information (i.e., motor) to guide one's social behaviour [@ondobaka2017role].
+Given recent work in which TOM is associated with one having more precise interoceptive states [@tsakiris2017multisensory; @palmer2018going; @arnold2019interoception], it is possible that individuals with greater TOM abilities have higher interoceptive awareness, more stable self-other representations and less malleable percepts of self [@tsakiris2017multisensory; @arnold2019interoception].
+As such, external cues of their interoceptive signals may be perceived as incongruent, hence generating a sense of uncertainty in their responses and leading to their lower lie confidence and longer response times.
 
 <!-- Limitations and Future Research -->
-- NOTE: no significant correlation between HCT accuracy and MAIA dimensions (only HCT confidence sig correlates with MAIA dimensions of awarenss and regulation)
-
-While this research has demonstrated that interoceptive abilities may be used to regulate and conceal deception, the individual's confidence in their lying abilities, is subjective, and may not offer a full-picture of their objective success.
-Future research should continue to unpack this relationship, examining how confidence and interoceptive regulation is reflected in the actual success of a lie, as well as how individuals confidence in their interoceptive abilities may correspond to decision bias [@garfinkel2015knowing], and propensity to engage in deception [@sip2012if].
-Furthermore, future research should expand recent findings on how individual traits correlate with true interoceptive abilities [@pearson2022two], to understand how they may factor into deceptive behaviour.
+Despite longstanding research interest in deception, little attention has been conferred to understanding the inter-individual differences in lying ability.
+In this study, we found a significant effect of interoception, particularly pertaining to its metacognitive dimensions, on one's ability to lie convincingly.
+However, future research is needed to address a few limitations.
+Namely, objective interoceptive accuracy was only assessed using the HCT.
+While the HCT is one of the most commonly used measure of objective interoceptive accuracy [@desmedt2022does], concerns regarding its validity has been highlighted in several studies [@desmedt2018heartbeat; @desmedt2022does; @brener2016towards; @legrand2022heart].
+Given increasing research efforts invested in the development of novel interoception tasks [@plans2021measuring; @legrand2022heart; @ponzo2021measuring], future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.
+Additionally, in order to account for the small sample size, we used factor analysis to reduce the number of dimensions assessing our variables of interest, which could have over-simplified the effect of interoception observed.
+Taking into perspective that the various facets of interoception are widely regarded as dissociable [@suksasilp2022towards; @mehling2012multidimensional], future studies could thus investigate their effects separately, to better delineate how interoceptive processes influence lying ability.
 

### 2022-11-14 paper/manuscript.Rmd
intro

@@
 ---
-title: '**The Heart Lies: The Role of Interoception and Theory of Mind in Deception**'
+title: '**Does the Heart Lies: The Role of Interoception and Theory of Mind in Deception**'
 shorttitle        : "TITLE"
 author:
+
   - name          : "Dominique Makowski"
-    affiliation   : " 1, *"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
     address       : "HSS 04-18, 48 Nanyang Avenue, Singapore"
-    email         : "dmakowski@ntu.edu.sg"
+    email         : "dom.makowski@gmail.com"
+    orcid         : 0000-0001-5375-9967
+    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+      - "Conceptualization"
+      - "Data curation"
+      - "Formal Analysis"
+      - "Funding acquisition"
+      - "Investigation"
+      - "Methodology"
+      - "Project administration"
+      - "Resources"
+      - "Software"
+      - "Supervision"
+      - "Validation"
+      - "Visualization"
+      - "Writing – original draft"
   - name          : "Zen J. Lau"
@@
     affiliation   : " 1"
+  - name          : "An Shu Te"
+    affiliation   : "1"
+    orcid         : 0000-0001-8008-2824
+    role:
+      - "Project administration"
+      - "Resources"
+      - "Investigation"
+      - "Writing – original draft"
+  - name          : "Stephanie Kirk"
+    affiliation   : "1"
+    orcid         : 0000-0002-9312-5552
+    role:
+      - "Project administration"
+      - "Resources"
+      - "Writing – original draft"
+  - name          : "Ngoi Zi Liang"
+    affiliation   : "1"
+    role:
+      - "Project administration"
+      - "Resources"
+      - "Writing – review & editing"
   - name          : "S.H. Annabel Chen"
-    affiliation   : " 1, 2, 3, 4"
-    corresponding : yes    # Define only one corresponding author
-    address       : "HSS 04-19, 48 Nanyang Avenue, Singapore"
-    email         : "annabelchen@ntu.edu.sg"
+    affiliation   : "1, 2, 3, 4"
+    orcid         : 0000-0002-1540-5516
+    role:
+      - "Project administration"
+      - "Supervision"
+      - "Writing – review & editing"
+
 affiliation:
@@
 
-```{=html}
 <!-- 
@@
 -->
-```
-# Introduction
 
@@
 
-In this post-truth era, deception has become increasingly prevalent in our everyday lives [@lewandowsky2017beyond].
-Although the act of deceiving is regarded as complex and often requires effortful self-regulation to conceal [@abe2007deceiving; @krokoszinski2016emotion], research shows that people tend to under-estimate their ability to successfully lie [@elaad2003effects].
-However, relative to the abundant literature regarding deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], surprisingly little attention has been conferred to investigating the inter-individual differences in people's lying ability.
-Given meta-analytic findings wherein the deceptive ability of the liar is suggested to be more important than the lie detector in deceptive interactions [@verigin2019lie; @bond2008individual; @levine2011sender], it is perhaps more pertinent to investigate what makes someone a more convincing liar.
+Lying - the intentional attempt at ...
+[**Insert definition**] - is a prevalent phenomenon carrying potentially important consequences.
+Interestingly, evidence suggests that the successful detection of a lying attempt depends more on the ability of the liar, than on the performance of the lie detector [@verigin2019lie; @bond2008individual; @levine2011sender].
+However, the factors contributing to one's deception abilities remain unclear, most of the deception literature focusing instead on deception detection [@viji2022history; @sternglanz2019review; @masip2017deception].
+
+<!-- research shows that people tend to under-estimate their ability to successfully lie [@elaad2003effects] -->
 
@@
 
-As deception requires the liar to intentionally manipulate the beliefs of others [@burgoon1994interpersonal; @sip2012if], most research on lying capability has been focused on higher order cognitive processes, particularly in theory of mind (TOM).
-TOM refers to the ability to infer that others have mental states, such as beliefs, emotions and intentions, distinct from ourselves [@lee2021lying; @wellman2001meta; @baron1997mindblindness].
-Indeed, the capacity to tell lies, as well as the complexity of lies told, have previously been found to be related to higher TOM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role].
-Furthermore, the deceptive capabilities of children is often used as a measure of their skills in TOM.
-However, studies investigating the links between TOM and lying ability have predominantly been focused on children and individuals with neurocognitive deficits [@beaudoin2020systematic; @bora2017meta; @roheger2022progression]; likely a result of the view of TOM as the foundation of other higher order cognitive processes [@ketelaars2010dynamics; @isaksson2021s].
-As such, little is known regarding the role TOM plays in the lying ability of healthy adults.
+As deception requires the liar to intentionally manipulate the beliefs of others [@burgoon1994interpersonal; @sip2012if], a significant line of research has been focused on the role of theory of mind (ToM) in lying ability.
+ToM refers to the ability to infer that others have mental states, such as beliefs, emotions and intentions, distinct from ourselves [@lee2021lying; @wellman2001meta; @baron1997mindblindness].
+The ability to tell lies, as well as their complexity, have previously been found to be related to higher TOM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role].
+However, studies investigating the link between ToM and deception have predominantly been focused on children and neuroatypical individuals [@beaudoin2020systematic; @bora2017meta; @roheger2022progression], and its importance in healthy adults remains to be clarified.
 
@@
 
-Alternatively, interoceptive abilities could also influence inter-individual differences in lying.
-Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing's conceptualizes interoception as a three-dimensional framework comprising three distinct facets, namely - *interoceptive accuracy*, the objective ability to monitor internal bodily signals; *interoceptive sensibility*, the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness*, one's ability to identify and appropriately respond to their perceived interoceptive states.
+Besides paying to attention to the person we lie to, trying to gauge whether they believe us, it is also possible that some attention is directed inwards: monitoring our own body and its reactions (e.g., cardiac activity and its related changes such as blushing), susceptible to be used as cues to infer our real intent.
+This begs the question of the potential role of interoceptive abilities in deception ability.
+Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing's conceptualizes interoception as a three-dimensional framework comprising three distinct facets, namely, *interoceptive accuracy* - the objective ability to monitor internal bodily signals; *interoceptive sensibility* - the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness* - one's ability to identify and appropriately respond to their perceived interoceptive states.
 Interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].
 Although little research interest has been conferred to investigating the relationship between interoception and deceptive ability *per se*, previous decision-making studies have demonstrated a negative correlation between interoceptive awareness, a metacognitive dimension of interoception, and one's likelihood to make risky decisions [@dunn2010listening; @furman2013interoceptive].
-In fact, this is consistent with the somatic marker hypothesis, which posits interoception is associated with a propensity towards making rational decisions [@damasio1996somatic].
+In fact, this is consistent with the somatic marker hypothesis, which posits an association between interoception and a propensity towards making rational decisions [@damasio1996somatic].
 
 In contrast, some studies have instead found heightened interoceptive attention, one's self-focus towards internal bodily signals, to predict apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening].
-Extending these findings to social cognition, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high (relative to low), whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
-Taking these mixed findings to perspective with the paucity in research linking deceptive ability with interoception, more studies are warranted to comprehensively examine the relationship between interoception and deception.
+Extending these findings to social cognition, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high, whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
+In a context of scarce research on interoception and deception, more studies are needed to clarify these these mixed findings.
 
@@
 
-The aim of the present study was to explore the interplay effects of TOM and interoception on individuals' deceptive ability, as indicated by their lie confidence, physiological arousal and response time.
-To this end, we designed a directed-lying bi-modal feedback paradigm comprising 2 conditions ( *Interrogation* vs *Polygraph*) with distinct feedback cues.
-In particular, salient social feedback cues were conferred during the *Interrogation condition*, whereas visual biofeedback cues were given during the *Polygraph condition*.
-We expected interoception to positively predict lying ability in the *Polygraph condition*; participants with better interoception would exhibit higher lie confidence, shorter response time and lower physiological arousal.
-Alternatively, we hypothesized TOM would positively predict individuals' capability in lying in the *Interrogation condition*.
+The aim of the present study was to explore the contribution of ToM and interoception abilities on individuals' deceptive skills, as indicated by their lying confidence, physiological arousal and response time.
+To this end, we designed a directed-lying paradigm with 2 conditions differing in the nature of their feedback cues.
+The *Interrogation* condition was designed to emphasize (and preferentially mobilize) ToM-related mechanims, whereas the *Polygraph* condition was designed to emphasize interoceptive mechanisms.
+We expected ToM and interoception to positively predict lying ability (i.e., higher lie confidence, shorter response time and lower physiological arousal), in particular in the *Polygraph* and the *Interrogation* condition, respectively.
 
 # Methods
-
-Along with open science standards, the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) for this research is available at [**https://github.com/DominiqueMakowski/DeceptionInteroTom**](https://github.com/DominiqueMakowski/DeceptionInteroTom){uri.}.
 
@@
 
+# Data Availability
+
+The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) for this research is available at [**https://github.com/DominiqueMakowski/DeceptionInteroTom**](https://github.com/DominiqueMakowski/DeceptionInteroTom){uri.}.
+
 # Funding

### 2022-11-15 paper/manuscript.Rmd
measures

@@
 ---
-title: '**Does the Heart Lies: The Role of Interoception and Theory of Mind in Deception**'
-shorttitle        : "TITLE"
+title: '**The Heart can Lie: The Role of Interoception and Theory of Mind in Deception**'
+shorttitle        : "Deception, Interoception, and ToM"
 author:
@@
 This begs the question of the potential role of interoceptive abilities in deception ability.
-Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing's conceptualizes interoception as a three-dimensional framework comprising three distinct facets, namely, *interoceptive accuracy* - the objective ability to monitor internal bodily signals; *interoceptive sensibility* - the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness* - one's ability to identify and appropriately respond to their perceived interoceptive states.
+Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing's conceptualizes interoception as a three-dimensional framework comprising three distinct facets, namely, interoceptive accuracy - the objective ability to monitor internal bodily signals; interoceptive sensibility - the subjective confidence in one's interoceptive accuracy; and interoceptive awareness - one's ability to identify and appropriately respond to their perceived interoceptive states.
 Interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].
@@
 To this end, we designed a directed-lying paradigm with 2 conditions differing in the nature of their feedback cues.
-The *Interrogation* condition was designed to emphasize (and preferentially mobilize) ToM-related mechanims, whereas the *Polygraph* condition was designed to emphasize interoceptive mechanisms.
+The *Interrogation* condition was designed to emphasize (and preferentially mobilize) ToM-related mechanisms, whereas the *Polygraph* condition was designed to emphasize interoceptive mechanisms.
 We expected ToM and interoception to positively predict lying ability (i.e., higher lie confidence, shorter response time and lower physiological arousal), in particular in the *Polygraph* and the *Interrogation* condition, respectively.
@@
 
-30 participants were recruited through  posters, flyers, and online social media platforms.
+30 university students were recruited through posters, flyers, and online social media platforms.
 Inclusion criteria included residing in Singapore, and an absence of current or history of neurological, psychiatric, or cardiovascular disorders.
-4 participants were excluded as a result of a technical error that led to their data not being recorded.
-The final sample consists 26 participants (Mean age = 20.9, SD = 2.0, range:[18, 25], Sex: 65.4% women, 34.6% men, 0.00% non-binary).
-The heart rate of one participant and response time of one participant were excluded from further analysis due to extreme outlying values [**PLEASE HELP ME CONFIRM**].
+Four participants were excluded as their data was not recorded due to technical issues.
+The final sample consists 26 participants (Mean age = 20.9, SD = 2.0, range:[18, 25], Sex: 65.4% women, 34.6% men).
+The heart rate of one participant and response time of one participant were excluded from further analysis due to extreme outlying values.
 
-This pre-registered study (**OSF?**) was approved by the NTU Institutional Review Board (NTU IRB-2018-10-029)(**TBC**) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
-All participants provided their informed consent prior to participation and were awarded with academic credit upon completion of the study.
+This pre-registered study (**OSF?** **Dom: I think so but not sure were to find the prereg**) was approved by the NTU Institutional Review Board (NTU IRB-2018-10-029)(**TBC**) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
+All participants provided their informed consent prior to participation and were awarded with academic credits upon completion of the study.
 
@@
 
-The *Basic Empathy Scale (BES)*, a 20-item, 5-point Likert scale (Strongly Disagree - Strongly Agree) that measures cognitive and affective empathy [@jolliffe2006development] was administered.
-Although TOM and empathy are regarded as distinct psychological constructs, previous research findings point to them being closely related [@gallant2020developing; @sebastian2012neural].
-Specifically, empathy is often thought to be an integral component in the affective dimension of TOM (i.e., the ability to infer what someone else is feeling) [@shamay2010role].
-The *Yoni Task*, which comprises 3 dimensions, namely cognitive, physical and affective TOM, was also administered to assess participants' objective TOM ability [@shamay2007dissociable].
+Two measures of ToM and related constructs were administered.
+The Yoni Task **[REF]** is a behavioral task in which participants have to **INSERT SHORT DESCRIPTION**.
+It captures 3 ToM dimensions, namely cognitive, physical and affective ToM abilities [@shamay2007dissociable].
 
-### Interoceptive Abilities
+The Basic Empathy Scale [BES, @jolliffe2006development], a 20-item questionnaire measuring two dimensions of empathy (cognitive and affective) using 5-point Likert scales was administered.
+Although ToM and empathy are regarded as distinct psychological constructs, previous research findings point to them being closely related [@gallant2020developing; @sebastian2012neural].
+<!-- Specifically, empathy is often thought to be an integral component in the affective dimension of ToM (i.e., the ability to infer what someone else is feeling) [@shamay2010role].  -->
 
-To assess participants' interoceptive ability, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart] while having their actual heartbeats recorded.
-During the HCT task, participants were instructed to count the number of heartbeats they felt over 5 trials with varying time intervals (20s, 25s, 30s, 35s, 40s), the sequence of which was randomized.
-Objective interoceptive accuracy (*HCT Accuracy*) was then computed based on the following formula ($\HCT_{Acc} = 1-|actual-count|/(actual + count)/2)$) [**lol pls help me write this in proper syntax**).
-To assess their interoceptive sensibility (*HCT Confidence*), participants were asked to rate, on a visual analog scale, how confident they were of their heartbeat counting accuracy at the end of each interval.
-Interoceptive awareness (*HCT Awareness*) was indexed by the correspondence between one's objective interoceptive accuracy and their confidence ratings.
+### Interoception
 
-The *MAIA-2* [@mehling2012multidimensional], a 32-item questionnaire which measures 8 dimensions of interoception (Noticing, Not-Distracting, Not-Worrying, Attention, Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust) using a 5-point Likert scale (Never-Always) was also administered.
+To assess participants' interoceptive ability, participants completed a Heartbeat Counting Task [HCT, @schandry1981heart] while having their actual heartbeats recorded.
+During the HCT task, participants were instructed to count the number of heartbeats over 5 trials with varying time intervals (20s, 25s, 30s, 35s, 40s, randomized order).
+Interoceptive accuracy was computed from the difference between the estimated number and the real number of heart beats.
+Interoceptive sensibility was estimated as the average of the confidence ratings presented at the end of each trial.
+Interoceptive awareness was indexed by the correlation between the objective accuracy and the subjective confidence.
 
-### Lie Profile
+The MAIA-2 [@mehling2012multidimensional], a 32-item questionnaire which measures 8 dimensions of interoception (Noticing, Not-Distracting, Not-Worrying, Attention, Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust) using 5-point Likert scales, was also administered.
 
-To evaluate participants' tendency to lie in their everyday lives, we used the *LIE Scale*, a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency) on a visual analog scale (Disagree-Agree) [@makowski2021structure].
+### Deception
 
-### Demographic Information
+**TODO: create a procedure figure**
 
-We further collected demographic information including age, ethnicity, nationality, handedness (for application of EDA electrodes), religion, duration lived in Singapore as well as highest education qualification achieved (or in the midst of achieving).
+We designed and implemented in PsychoPy [@peirce2019psychopy2] a directed-lying task in which the participants were instructed that they would have to answer 80 questions by either lying or telling the truth (depending on whether they see "lie" or "truth" written on the screen).
+Importantly, they were told that for half of the trials, they would have to convince another participant, located in another room, that would see them through a webcam connection (*Interrogation* condition).
+For the remaining trials, they would have to convince a "lie detection machine" that would be based on their physiological signals *Polygraph* condition.
+The two conditions were presented in a counter-balanced order, and each comprised of 40 trials.
 
-### Deception Task Paradigm
+The sequence of each trial was the same for both conditions.
+A question was shown on a computer screen, either phrased directly (e.g., "What is your favourite sport?"), or indirectly (e.g., "Is your favourite sport Hockey?"), with accompanying instructions below that either asked participants to verbally lie or tell the truth (half of  the trials in each condition, i.e., n = 20, were directed lies).
+Following a short interval (0.7 - 1.5s) for response preparation (during which was written "Connecting..." on the screen), participants were presented with either a social-feedback or biofeedback cue (for the *Interrogation* and *Polygraph* conditions, respectively), displayed for a maximum of 10s.
+Participants had to provide their answer to the question verbally (out loud) and press the space key to mark the end of their response.
+After another short interval (1.5 - 2.5s) during which was written "Disconnecting..." on the screen, participants were asked to rate n an analog scale  their confidence on how convincing (i.e., likely to get judged as truthful) they perceived their response to be.
 
-We designed a directed-lying bi-modal feedback task (the *Deception Task*) consisting 2 conditions - namely, the *Interrogation* condition and the *Polygraph* condition.
+In the *Interrogation* condition, participants had to answer each trial while receiving social feedback in the form of a video stream of an examiner, and were informed that the examiner would be evaluating the truthfulness of their responses by observing them through the live video feed.
+In actuality, the video was a pre-recorded video clips of a confederate's face (staying still with minimal reactions, and with a medical mask, as the experiment was run during COVID restrictions), and the same video-clips were used with all participants.
+Note that after debriefing, all participants reported believing that the stream was real and that the examiner was really there.
 
-In the *Interrogation* condition, participants were given social feedback in the form of a video stream with an examiner.
-Notably, participants were informed that the examiner would be evaluating the truthfulness of their responses by observing them through the live video feed.
-In actuality, the video was a pre-recorded video clip of a confederate, and the same video-clip was presented to all participants.
+In the *Polygraph* condition, participants had to answer each trial while receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded.
+Participants were informed that they were being shown live feedback of their own physiological activity.
+In actuality, we displayed pre-recorded video clips of a confederate's signals.
+Note that after debriefing, all participants reported believing that it was indeed their own signals being shown.
 
-In the *Polygraph* condition, participants were given biofeedback in the form of an electrocardiogram (ECG) displayed onscreen instead.
-Specifically, participants were informed that they were being shown live feedback of their own heartbeats when in fact, the displayed ECG was that of a pre-recorded video clip.
-Similar to the *Interrogation* condition, all participants were shown the same pre-recorded video clip of the ECG.
+Finally, on top of the deception task, we also measured the self-reported tendency to lie in their everyday life using the *Lie Scale* [@makowski2021structure], a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency) with visual analog scales.
 
-The sequence of each task trial was the same for both conditions.
-Using a computer, participants were first shown a question, either phrased directly (*"What is your favourite sport?*), or indirectly (*"Is your favourite sport Hockey?"*), with accompanying instructions below that either asked participants to verbally lie or tell the truth.
-Following a connecting screen (0.7 - 1.5s), participants were presented with either social (*Interrogation* condition) or biofeedback (*Polygraph* condition) that was displayed for a maximum of 10s or until they made their accorded response.
-A disconnecting screen was then displayed (1.5-2.5s), following which participants were asked to rate their confidence in how convincing they perceived their answer to be.
+<!-- ### Demographic Information -->
+
+<!-- We further collected demographic information including age, ethnicity, nationality, handedness (for application of EDA electrodes), religion, duration lived in Singapore as well as highest education qualification achieved (or in the midst of achieving).
+-->
 
@@
 In the first phase of the study, participants answered a brief demographic survey before being administered a battery of questionnaires (*BES*, *MAIA-2*, *Lie Scale*) and cognitive-behavioural tasks (*HCT*, *Yoni Task*).
-This series of tasks and questionnaires were administered in a randomized order [**TBC**] in order to control for order effects.
-In the second phase of the study, the *Deception Task* was conducted using PsychoPy [@peirce2019psychopy2].
-Each participant was administered both conditions of the *Deception Task*, the order sequence of which was randomized.
-Each task condition comprised 40 trials, of which participants were instructed to lie in half of the trials (20 **Truth** trials; 20 **Lie** trials).
-In total, each participant underwent 80 *Deception Task* trials.
+This series of tasks and questionnaires were administered in a randomized order in order to control for order effects.
+In the second phase of the study, the *Deception Task* was administered.
 
 Physiological recording devices were prepared prior to beginning the experimental paradigm.
-Using three ECG electrodes placed according to a modified Lead II configuration [@takuma1995alternative], cardiovascular activity, sampled at 1000Hz (**TBC**) was recorded via the BioPac MP160 system (BioPac Systems Inc., USA) and the AcqKnowledge 5.0 software.
+Using three ECG electrodes placed according to a modified Lead II configuration [@takuma1995alternative], cardiovascular activity, sampled at 1000 Hz, was recorded via the BioPac MP160 system (BioPac Systems Inc., USA).
 

### 2022-11-20 paper/manuscript.Rmd
starting discussion

@@
 
-Finally, on top of the deception task, we also measured the self-reported tendency to lie in their everyday life using the *Lie Scale* [@makowski2021structure], a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency) with visual analog scales.
+Finally, on top of the deception task, we also measured the self-reported tendency to lie in their everyday life using the *Lie Scale* [@makowski2021structure], a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency).
 
@@
 
-In the first phase of the study, participants answered a brief demographic survey before being administered a battery of questionnaires (*BES*, *MAIA-2*, *Lie Scale*) and cognitive-behavioural tasks (*HCT*, *Yoni Task*).
-This series of tasks and questionnaires were administered in a randomized order in order to control for order effects.
-In the second phase of the study, the *Deception Task* was administered.
-
-Physiological recording devices were prepared prior to beginning the experimental paradigm.
-Using three ECG electrodes placed according to a modified Lead II configuration [@takuma1995alternative], cardiovascular activity, sampled at 1000 Hz, was recorded via the BioPac MP160 system (BioPac Systems Inc., USA).
+In the first phase of the study, participants answered a brief demographic survey before being administered the questionnaires and cognitive-behavioural tasks in a randomized order.
+Then, the physiological recording devices were set up.
+Cardiac activity (ECG) was recorded with 3 electrodes placed according to a modified Lead II configuration [@takuma1995alternative], electrodermal activity (EDA) and respiration (using a respiration belt) were also recorded, but not analyzed for the study (unfortunately, most participants did not yield any skin conductance responses - which we believe was partly caused by the strong air-conditioning of the experimental room).
+All signals were recorded at 1000 Hz via the BioPac MP160 system (BioPac Systems Inc., USA).
+The deception task was finally run, followed by a debriefing.
+Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of **4 sec** [TO-CHECK]).
 
@@
 
-The manipulation checks consist of testing whether there is an effect of question phrasing (direct vs.
-indirect), and condition (polygraph *vs.* interrogation), on our 3 outcome variables: the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT), and the heart rate change associated with the response.
+To ensure that our outcome variables were sensitive to the experimental manipulations, we first tested the effect of the question phrasing (direct *vs.* indirect) and condition (polygraph *vs.* interrogation) on the outcome variables.
 This analysis was performed using mixed models with the participants and questions both entered as random factors.
@@
 
-To further counterbalance the low number of participants and maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, TOM and interoception).
-We favoured the use of factor analysis (using the method agreement procedure to estimate the optimal number of dimensions, @parametersArticle), over PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained.
-Then, we modeled the relationship between these inter-individual composite scores (the analysis for all the variables is included in Supplementary Materials) and the 3 outcome variables in interaction with the condition (polygraph *vs.* interrogation).
-Finally, we also investigated the relationship between the deception scale traits, and the theory of mind and interoception scores using Bayesian correlations.
+To further counterbalance the low number of participants and maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, ToM and interoception) using factor analysis over PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained.
+Then, we modelled the relationship between these inter-individual composite scores (note that the analysis for all individual variables is nonetheless included in the analysis report) and the 3 outcome variables in interaction with the condition (polygraph *vs.* interrogation).
+Finally, we investigated the relationship between the deception scale traits, and the theory of mind and interoception scores using Bayesian correlations.
 
 The data analysis was carried out using*R 4.2* [@RCoreTeam2022], *brms* [@Burkner2017], and the *easystats* collection of packages [@bayestestRArticle; @correlationArticle; @performanceArticle; @insightArticle].
-As the full reproducible analysis script and statistical results are available at [**https://github.com/DominiqueMakowski/DeceptionInteroTom**](https://github.com/DominiqueMakowski/DeceptionInteroTom){.uri}, we will only focus on significant results in the manuscript.
+As the full reproducible analysis script and statistical results report are available at [**https://github.com/DominiqueMakowski/DeceptionInteroTom**](https://github.com/DominiqueMakowski/DeceptionInteroTom){.uri}, we will only focus on significant results in the manuscript.
 
@@
 
-While there is an extensive body of literature associating deception with social cognition and emotion regulation, most research had been focused on their roles in deception detection, leaving a paucity in studies pertaining to their influence on lying ability.
-The present study hence seeks to address this research gap, further aiming to examine the interplay effect of TOM and interoception on our ability to lie convincingly.
-Notably, we found a significant difference in participants' lying ability (as measured by response time, heart rate and confidence ratings) between the *Polygraph* and *Interrogation* conditions.
+<!-- While there is an extensive body of literature associating deception with social cognition and emotion regulation, most research had been focused on their roles in deception detection, leaving a paucity in studies pertaining to their influence on lying ability.
+-->
+
+The present study examined the contribution of ToM and interoception on our ability to lie using a directed lie paradigm with two conditions ("Polygraph" and "Interrogation") hypothesizingly enhancing each of the two mechanisms.
+Interestingly, we found a significant difference in participants' lying ability (as measured by response time, heart rate and confidence ratings) between the *Polygraph* and *Interrogation* conditions.
 This hence confers support for the manipulation used in our experimental paradigm, demonstrating that increasing the attentional focus towards visual interoceptive cues, even if they are fake, can elicit interoceptive awareness and enhance the precision of internal signals if such external cues of interoceptive signals are perceived to be real.
@@
 
-# Author Contributions
+**no funding**
 
@@
 
+The authors declare no conflict of interest.
+
 # Acknowledgements
+
+We would like to thank Jia Rong **what's his full name?** for his help in data collection and **...** for data analysis.
 

### 2022-11-21 2_ManipulationChecks.Rmd
anonimize data and revise ms

@@
 modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
+modelbased::estimate_contrasts(model, contrast = "Answer")
 modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
@@
 modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
+modelbased::estimate_contrasts(model, contrast = "Condition")
 ```
@@
 modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
+modelbased::estimate_contrasts(model, contrast = "Answer")
 modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
+modelbased::estimate_contrasts(model, contrast = "Condition")
 ```

### 2022-11-21 index.Rmd
anonimize data and revise ms

@@
 ```{r warning=FALSE, message=TRUE, results='asis'}
-df <- read.csv("data/data_combined.csv") %>% 
-  mutate(Participant = factor(paste0("S", Participant), levels = paste0("S", 1:30)),
-         Condition = as.factor(Condition),
-         Item = as.factor(Item),
-         Phrasing = as.factor(Phrasing),
-         Answer = as.factor(Answer)) |> 
-  dplyr::filter(!Participant %in% c("S3", "S15", "S19", "S23"))  # No data
+df <- read.csv("data/data.csv")
 
@@
   labs(y = "Confidence",
-       x = "Theory of Mind") +
+       x = expression(Theory~of~Mind~"'Composite'"["  (.89 YONI Cognitive, .77 YONI Affective, .45 YONI Physical)"])) +
   scale_y_continuous(labels = scales::percent) + 
@@
   labs(y = "Confidence",
-       x = expression(Interoception["  (.97 MAIA Attention regulation, .63 MAIA Self-regulation, .60 MAIA Emotional Awareness)"])) +
+       x = expression(Interoception~"'Meta'"["  (.97 MAIA Attention regulation, .63 MAIA Self-regulation, .60 MAIA Emotional Awareness)"])) +
   scale_y_continuous(labels = scales::percent) + 
@@
   labs(y = "Confidence",
-       x = expression(Interoception["  (.92 MAIA Body listening, -.60 HCT Awareness, .53 HCT Trusting)"])) +
+       x = expression(Interoception~"'Listening'"["  (.92 MAIA Body listening, -.60 HCT Awareness, .53 HCT Trusting)"])) +
   scale_y_continuous(labels = scales::percent) + 
@@
   labs(y = "Confidence",
-       x = expression(Interoception["  (.87 MAIA Not-distracting, -.40 MAIA Emotional Awareness, .33 HCT Accuracy)"])) +
+       x = expression(Interoception~"'Focus'"["  (.87 MAIA Not-distracting, -.40 MAIA Emotional Awareness, .33 HCT Accuracy)"])) +
   scale_y_continuous(labels = scales::percent) + 
@@
   labs(y = "Confidence",
-       x = expression(Interoception["  (.71 MAIA Not-worrying, .61 HCT Accuracy, .40 MAIA Trusting)"])) +
+       x = expression(Interoception~"'Regulation'"["  (.71 MAIA Not-worrying, .61 HCT Accuracy, .40 MAIA Trusting)"])) +
   scale_y_continuous(labels = scales::percent) + 

### 2022-11-21 paper/manuscript.Rmd
anonimize data and revise ms

@@
 This analysis was performed using mixed models with the participants and questions both entered as random factors.
-Marginal contrasts analysis was also performed to clarify the differences between conditions.
+Marginal contrasts analysis (denoted by $\Delta$) was also performed to clarify the differences between conditions.
 To allow for a better quantification of the uncertainty associated with the effects, as well as increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework [@makowski2019bayestestr], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).
@@
 
-Compared to truth, lies were rated with less confidence ($\beta=-1.09,~95\%~CI~[-0.94, -1.25],~pd = 100\%$).
-Moreover, lies told in the polygraph condition were rated with less confidence ($\delta=-0.24,~95\%~CI~[-0.10, -0.39],~pd > 99\%$).
-The RT did not differ between truth and lies, but was significantly slower in the polygraph condition ($\beta=0.14,~95\%~CI~[0.03, 0.25],~pd > 99\%$) for both conditions.
-The heart rate was significantly more elevated during lies as compared to truth ($\beta=1.31,~95\%~CI~[2.14, 0.50],~pd > 99.9\%$), and during interrogation as compared to the polygraph condition ($\beta=4.99 ,~95\%~CI~[5.82, 4.19],~pd = 100\%$).
+Compared to truth, lies were rated with less confidence ($\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%$), but no difference between the conditions was found.
+On the other hand, the RT did not differ between truth and lies, but was significantly slower in the polygraph condition for both conditions ($\Delta=0.25,~95\%~CI~[0.62, 0.41],~pd = 100\%$).
+The heart rate was significantly more elevated during lies as compared to truth ($\Delta=1.16,~95\%~CI~[0.57, 1.73],~pd = 100\%$), and during interrogation as compared to the polygraph condition ($\Delta=4.84 ,~95\%~CI~[4.23, 5.44],~pd = 100\%$).
 
-The indirect phrasing of the question only had a significant effect on RT ($\beta=0.34,~95\%~CI~[0.23, 0.44],~pd = 100\%$), leading to slower answers, regardless of whether they were lies or truths.
+The indirect phrasing of the question only had a significant effect on RT ($\beta=0.36,~95\%~CI~[0.21, 0.51],~pd = 100\%$), leading to slower answers, regardless of whether they were lies or truths.
 
@@
 The fourth factor, labelled *Interoception - Regulation* (10.97%), was primarily loaded by MAIA not-worrying (.71), HCT Accuracy (.61) and MAIA Trusting (.40).
-However, due to the interpretation difficulty, we will refer to these dimensions with their main correlates in **Figure 1** [**Note to fix caption for Figure 1 from HCT Trusting to MAIA trusting**].
+<!-- However, due to the interpretation difficulty, we will refer to these dimensions with their main correlates in **Figure 1** [**Note to fix caption for Figure 1 from HCT Trusting to MAIA trusting**].
+-->
 
@@
 The composite *TOM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67%\%$), specifically in the polygraph condition.
-No significant effect was found with regards to heart rate, and no correlation was observed with dispositional lying traits.
+No significant effect was found with regards to heart rate, and no correlation was observed with dispositional lying traits (**Figure 1**).
+
+```{r message=FALSE, warning=FALSE, out.width="100%", fig.cap="TODO: Caption."}
+knitr::include_graphics("../figures/figure1.png")
+```
 
@@
 The *Regulation* interoception score was significantly associated with an increased confidence in lies in the polygraph ($\beta=0.32,~95\%~CI~[0.14, 0.51],~pd = 99.99\%$) and the interrogation conditions ($\beta=0.18,~95\%~CI~[0.00, 0.36],~pd = 97.42\%$), and with a decreased confidence in truth only in the polygraph condition ($\beta=-0.1,~95\%~CI~[-0.36, 0.01],~pd = 97.16\%$).
-No significant association was found with RT or heart rate.
+No significant association was found with RT or heart rate (**Figure 2**).
+
+```{r message=FALSE, warning=FALSE, out.width="100%", fig.cap="TODO: Caption."}
+knitr::include_graphics("../figures/figure2.png")
+```
 
@@
 
-The present study examined the contribution of ToM and interoception on our ability to lie using a directed lie paradigm with two conditions ("Polygraph" and "Interrogation") hypothesizingly enhancing each of the two mechanisms.
-Interestingly, we found a significant difference in participants' lying ability (as measured by response time, heart rate and confidence ratings) between the *Polygraph* and *Interrogation* conditions.
-This hence confers support for the manipulation used in our experimental paradigm, demonstrating that increasing the attentional focus towards visual interoceptive cues, even if they are fake, can elicit interoceptive awareness and enhance the precision of internal signals if such external cues of interoceptive signals are perceived to be real.
+The present study examined the contribution of ToM and interoception on our ability to lie using a directed lie paradigm with two conditions ("Interrogation" and "Polygraph") designed to enhance each of the two mechanisms.
+Interestingly, we found that when participants were displayed a (fake) physiological feedback (the polygraph condition), instead of a face of a person they had to lie to (the interrogation condition), their response time for both lies and truths was increased, as well as their heart rate.
+Although the condition did not impact the subjective confidence that participants had in their answers, it suggests that believing to be submitted to a lying detection machine that supposedly reads physiological signals is a harder and/or more stressful condition than answering to a person.
+
+<!-- This hence confers support for the manipulation used in our experimental paradigm, demonstrating that increasing the attentional focus towards visual interoceptive cues, even if they are fake, can elicit interoceptive awareness and enhance the precision of internal signals if such external cues of interoceptive signals are perceived to be real.
 Extending previous research pertaining to the application of interoceptive training for improving emotion regulation [@sugawara2020effects; @quadt2021interoceptive; @wu2022enhanced], our study thus provides evidence that interoceptive awareness can be manipulated and thereby modified to guide our emotional responses.
+-->
 
 <!-- Interoceptive vs Social Cues -->
-Using a bi-modal feedback deception task, we found partial support for our hypothesis.
+<!-- Using a bi-modal feedback deception task, we found partial support for our hypothesis.
 Specifically, participants reported lower lie confidence and took a longer time to respond, but were less physiologically aroused in the *Polygraph* condition, relative to the *Interrogation* condition.
@@
 This interplay of interoception and maladaptive stress response, and their effect on lying ability hence underscores the complexity underlying successful deceptive behaviour.
+-->
+
+<!-- TOM -->
+Our results suggest that higher ToM abilities were related to a slower and less confident lies, but only in the polygraph condition.
+One possible interpretation is that people with stronger ToM abilities rely by default more on it when lying (i.e., they focus on - and try to read - the other person).
+When that mechanism is cut off (i.e., when there is no person to lie to - but in our case a "machine"), their lying ability decreases.
+
+<!-- Interoception -->
+We also showed that interoceptive abilities are correlated with a higher confidence in one's lies in the polygraph condition, a condition in which the attention towards internal reactions is fostered.
+However, in contrast to previous studies [@pinna2020systematic; @fustos2013embodiment; @owens2018investigating; @pollatos2007heart], we did not find any significant relationship between individuals' interoception scores and the heart rate changes during their answers.
+This points toward a predominantly meta-cognitive effect without necessarily an actual bodily regulation (i.e., participants with good interoception feel that their lies are more convincing, but do not actively attenuate their bodily reactions).
+
+<!-- Our results show a significant association between individuals' composite TOM score with lower lie confidence and longer response time when interoceptive cues were highly salient.
+Under the free energy principle [@friston2010free], interoception is regarded as integral in TOM [@shah2017heart; @palmer2018going; @ondobaka2017role].
+Specifically, during social inference, interoceptive signals are integrated with exteroceptive (e.g., visual and auditory) and proprioceptive information (i.e., motor) to guide one's social behaviour [@ondobaka2017role].
+Given recent work in which TOM is associated with one having more precise interoceptive states [@tsakiris2017multisensory; @palmer2018going; @arnold2019interoception], it is possible that individuals with greater TOM abilities have higher interoceptive awareness, more stable self-other representations and less malleable percepts of self [@tsakiris2017multisensory; @arnold2019interoception].
+As such, external cues of their interoceptive signals may be perceived as incongruent, hence generating a sense of uncertainty in their responses and leading to their lower lie confidence and longer response times.
+-->
 
 <!-- Meta-Interoception, Emotion Regulation and Lying -->
-Consistent with our hypothesis, a significant positive association was predominantly found between metacognitive dimensions of interoception (*Meta* and *Regulation* interoception) and individuals' lie confidence when their physiological cues were salient.
+<!-- Consistent with our hypothesis, a significant positive association was predominantly found between metacognitive dimensions of interoception (*Meta* and *Regulation* interoception) and individuals' lie confidence when their physiological cues were salient.
 In contrast to previous studies [@pinna2020systematic; @fustos2013embodiment; @owens2018investigating; @pollatos2007heart], we did not find any significant relationship between individuals' interoception scores and objective heart rate.
@@
 As such, further studies are necessary to examine what factors modulate the relationship between the metacognitve facets of interoception and emotion regulation.
-
-<!-- TOM -->
-Our results show a significant association between individuals' composite TOM score with lower lie confidence and longer response time when interoceptive cues were highly salient.
-Under the free energy principle [@friston2010free], interoception is regarded as integral in TOM [@shah2017heart; @palmer2018going; @ondobaka2017role].
-Specifically, during social inference, interoceptive signals are integrated with exteroceptive (e.g., visual and auditory) and proprioceptive information (i.e., motor) to guide one's social behaviour [@ondobaka2017role].
-Given recent work in which TOM is associated with one having more precise interoceptive states [@tsakiris2017multisensory; @palmer2018going; @arnold2019interoception], it is possible that individuals with greater TOM abilities have higher interoceptive awareness, more stable self-other representations and less malleable percepts of self [@tsakiris2017multisensory; @arnold2019interoception].
-As such, external cues of their interoceptive signals may be perceived as incongruent, hence generating a sense of uncertainty in their responses and leading to their lower lie confidence and longer response times.
+-->
 
 <!-- Limitations and Future Research -->
-Despite longstanding research interest in deception, little attention has been conferred to understanding the inter-individual differences in lying ability.
-In this study, we found a significant effect of interoception, particularly pertaining to its metacognitive dimensions, on one's ability to lie convincingly.
-However, future research is needed to address a few limitations.
-Namely, objective interoceptive accuracy was only assessed using the HCT.
-While the HCT is one of the most commonly used measure of objective interoceptive accuracy [@desmedt2022does], concerns regarding its validity has been highlighted in several studies [@desmedt2018heartbeat; @desmedt2022does; @brener2016towards; @legrand2022heart].
+Although yielding promising results, this exploratory study is limited by the sample size.
+Although we tried to mitigate it by 1) extracting more robust variables (by combining multiple ones by means of feature reduction) and 2) using a suited analysis approach (Bayesian statistics with informative priors), future replication studies with larger samples are warranted to confirm this first investigation.
+Nonetheless, we believe our results to be credible as we find consistent patterns across various facets and measures (for instance, all interoceptive dimensions, although distinct, share a similar trend) in line with theoretical expectations.
+The statistical power could also explain the overall lack of results with heart rate, which has a higher signal-to-noise ratio as compared to subjective reports (such as confidence scales).
+
+Another aspect to note is the strong reliance on self-reported measures as outcome variables of lie ability (in particular, the measure of answer confidence, but also the auto-questionnaires).
+This might conflate meta-cognitive abilities as well as dishonest answers.
+Although we tried to include more objective measures, such as RT (although it too was tied to the participants' conscious decision to press a key) and heart rate, future studies should attempt at measuring objectively the answer (lie or truth) quality, for instance by means of external examiners.
+Note that this is not limitation *per se*, as it answers a slightly different question  - what are the correlates of *objective* lying skills - than deception self-confidence.
+
+Additionally to limitations pertaining to the measure of lying ability, care has to be given to the measure of the predictor constructs, namely ToM and interoception.
+While we tried to include an behavioral task as well as a subjective questionnaire for each, it has to be underlined that they are notoriously difficult concepts to measure.
+In particular, objective interoceptive accuracy was assessed using the Heartbeat Counting Task.
+While the HCT used to be considered as a gold standard and is one of the most commonly used measure [@desmedt2022does], concerns regarding its validity has been highlighted in several studies [@desmedt2018heartbeat; @desmedt2022does; @brener2016towards; @legrand2022heart].
 Given increasing research efforts invested in the development of novel interoception tasks [@plans2021measuring; @legrand2022heart; @ponzo2021measuring], future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.
-Additionally, in order to account for the small sample size, we used factor analysis to reduce the number of dimensions assessing our variables of interest, which could have over-simplified the effect of interoception observed.
-Taking into perspective that the various facets of interoception are widely regarded as dissociable [@suksasilp2022towards; @mehling2012multidimensional], future studies could thus investigate their effects separately, to better delineate how interoceptive processes influence lying ability.
+Additionally, our application of feature reduction as a noise-elimination measure could have over-simplified the data.
+A more complex pattern of relationships, with different contributions of various subdimensions of ToM and interoception, could emerge provided a sufficient statistical power and valid measures.
+
+<!-- Taking into perspective that the various facets of interoception are widely regarded as dissociable [@suksasilp2022towards; @mehling2012multidimensional], future studies could thus investigate their effects separately, to better delineate how interoceptive processes influence lying ability.
+-->
+
+In conclusion, this study study is a first step towards assessing the contribution of ToM and interoception abilities in deception in one's ability to lie convincingly.
+We introduced a new paradigm that is able to modulate the contribution of these mechanisms while remaining relevant to applied fields of lie detection and criminology (in which the experimental conditions find echoing practices).
+Our results provide princeps evidence that interoception could be a key - and overlooked - mechanism in deception.
 
@@
 
-We would like to thank Jia Rong **what's his full name?** for his help in data collection and **...** for data analysis.
+We would like to thank Jia Rong **what's his full name?**, Max (**full name**, partial RA) for his help in data collection and **...** for data analysis.
 

### 2023-01-03 paper/manuscript.Rmd
update

@@
 
-Lying - the intentional attempt at ...
-[**Insert definition**] - is a prevalent phenomenon carrying potentially important consequences.
+Lying - the intentional attempt at instilling a false belief in others [@sip2012if] - is a prevalent phenomenon carrying potentially important consequences.
 Interestingly, evidence suggests that the successful detection of a lying attempt depends more on the ability of the liar, than on the performance of the lie detector [@verigin2019lie; @bond2008individual; @levine2011sender].
-However, the factors contributing to one's deception abilities remain unclear, most of the deception literature focusing instead on deception detection [@viji2022history; @sternglanz2019review; @masip2017deception].
+However, with most of the deception literature focused on deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], the factors contributing to one's deception abilities remain unclear.
 
@@
 
-Besides paying to attention to the person we lie to, trying to gauge whether they believe us, it is also possible that some attention is directed inwards: monitoring our own body and its reactions (e.g., cardiac activity and its related changes such as blushing), susceptible to be used as cues to infer our real intent.
+Besides paying attention to the person we lie to, trying to gauge whether they believe us, it is also possible that some attention is directed inwards: monitoring our own body and its reactions (e.g., cardiac activity and its related changes such as blushing), preventing them from being used as cues to infer our real intent.
 This begs the question of the potential role of interoceptive abilities in deception ability.
@@
 Extending these findings to social cognition, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high, whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
-In a context of scarce research on interoception and deception, more studies are needed to clarify these these mixed findings.
+Given the scarce research on interoception and deception, more studies are herein needed to clarify these mixed findings.
 
@@
 
-This pre-registered study (**OSF?** **Dom: I think so but not sure were to find the prereg**) was approved by the NTU Institutional Review Board (NTU IRB-2018-10-029)(**TBC**) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
+This pre-registered study (**OSF?** **Dom: I think so but not sure were to find the prereg**) was approved by the NTU Institutional Review Board (NTU-IRB-2020-09-007) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
 All participants provided their informed consent prior to participation and were awarded with academic credits upon completion of the study.
@@
 Two measures of ToM and related constructs were administered.
-The Yoni Task **[REF]** is a behavioral task in which participants have to **INSERT SHORT DESCRIPTION**.
-It captures 3 ToM dimensions, namely cognitive, physical and affective ToM abilities [@shamay2007dissociable].
+The Yoni Task [@shamay2007dissociable] is a behavioral task in which participants are presented with the face of a character named "Yoni", surrounded by 4 colored pictures of objects or faces.
+In total, each participant completed 101 trials - 49 trials assessing their affective TOM abilities, 37 trials assessing their cognitive TOM abilities and 15 control trial.
+During each trial, participants were shown a question and asked to make responses based on specific cues such as directions of eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical TOM).
 
-The Basic Empathy Scale [BES, @jolliffe2006development], a 20-item questionnaire measuring two dimensions of empathy (cognitive and affective) using 5-point Likert scales was administered.
+The Basic Empathy Scale [BES, @jolliffe2006development], a 20-item questionnaire measuring two dimensions of empathy (cognitive and affective) using a 5-point Likert scale was administered.
 Although ToM and empathy are regarded as distinct psychological constructs, previous research findings point to them being closely related [@gallant2020developing; @sebastian2012neural].
@@
 To assess participants' interoceptive ability, participants completed a Heartbeat Counting Task [HCT, @schandry1981heart] while having their actual heartbeats recorded.
-During the HCT task, participants were instructed to count the number of heartbeats over 5 trials with varying time intervals (20s, 25s, 30s, 35s, 40s, randomized order).
+During the HCT task, participants were instructed to count the number of heartbeats over 5 trials with varying time intervals (20s, 25s, 30s, 35s, 40s), the  order of which was randomized.
 Interoceptive accuracy was computed from the difference between the estimated number and the real number of heart beats.
@@
 
-We designed and implemented in PsychoPy [@peirce2019psychopy2] a directed-lying task in which the participants were instructed that they would have to answer 80 questions by either lying or telling the truth (depending on whether they see "lie" or "truth" written on the screen).
-Importantly, they were told that for half of the trials, they would have to convince another participant, located in another room, that would see them through a webcam connection (*Interrogation* condition).
-For the remaining trials, they would have to convince a "lie detection machine" that would be based on their physiological signals *Polygraph* condition.
-The two conditions were presented in a counter-balanced order, and each comprised of 40 trials.
+We designed and implemented in PsychoPy [@peirce2019psychopy2] a directed-lying task in which participants were instructed to answer 80 questions by either lying or telling the truth (depending on whether they see "lie" or "truth" written on the screen).
+Importantly, they were told that for half of the trials, they would have to convince another participant that would be observing them form a separate room via a webcam connection (*Interrogation* condition).
+For the remaining trials, participants were tasked to convince a "lie detection machine" that would be assessing their behaviour through their physiological signals (*Polygraph* condition).
+The two conditions were presented in a counter-balanced order, and each comprised of 40 trials (20 truth; 20 lies).
 
@@
 A question was shown on a computer screen, either phrased directly (e.g., "What is your favourite sport?"), or indirectly (e.g., "Is your favourite sport Hockey?"), with accompanying instructions below that either asked participants to verbally lie or tell the truth (half of  the trials in each condition, i.e., n = 20, were directed lies).
-Following a short interval (0.7 - 1.5s) for response preparation (during which was written "Connecting..." on the screen), participants were presented with either a social-feedback or biofeedback cue (for the *Interrogation* and *Polygraph* conditions, respectively), displayed for a maximum of 10s.
-Participants had to provide their answer to the question verbally (out loud) and press the space key to mark the end of their response.
-After another short interval (1.5 - 2.5s) during which was written "Disconnecting..." on the screen, participants were asked to rate n an analog scale  their confidence on how convincing (i.e., likely to get judged as truthful) they perceived their response to be.
+Following a short interval (0.7 - 1.5s) for response preparation (during which "Connecting..." was displayed on the screen), participants were presented with either a social-feedback or biofeedback cue (for the *Interrogation* and *Polygraph* conditions, respectively), displayed for a maximum of 10s.
+After the feedback cue, participants had to provide their answer to the question verbally (out loud) and press the 'space' key to mark the end of their response.
+Following another short interval (1.5 - 2.5s) during which was written "Disconnecting..." on the screen, participants were asked to rate, using an analog scale, their confidence in how convincing (i.e., likely to get judged as truthful) they perceived their response to be.
 
@@
 Then, the physiological recording devices were set up.
-Cardiac activity (ECG) was recorded with 3 electrodes placed according to a modified Lead II configuration [@takuma1995alternative], electrodermal activity (EDA) and respiration (using a respiration belt) were also recorded, but not analyzed for the study (unfortunately, most participants did not yield any skin conductance responses - which we believe was partly caused by the strong air-conditioning of the experimental room).
+Cardiac activity (ECG) was recorded with 3 electrodes placed according to a modified Lead II configuration [@takuma1995alternative], electrodermal activity (EDA) and respiration (using a respiration belt) were also recorded, but not analyzed for the study (unfortunately, most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (22 degrees Celsius) of the experimental room).
 All signals were recorded at 1000 Hz via the BioPac MP160 system (BioPac Systems Inc., USA).
@@
 The present study examined the contribution of ToM and interoception on our ability to lie using a directed lie paradigm with two conditions ("Interrogation" and "Polygraph") designed to enhance each of the two mechanisms.
-Interestingly, we found that when participants were displayed a (fake) physiological feedback (the polygraph condition), instead of a face of a person they had to lie to (the interrogation condition), their response time for both lies and truths was increased, as well as their heart rate.
-Although the condition did not impact the subjective confidence that participants had in their answers, it suggests that believing to be submitted to a lying detection machine that supposedly reads physiological signals is a harder and/or more stressful condition than answering to a person.
+Interestingly, we found that when participants were presented with (fake) physiological feedback (the polygraph condition), instead of a face of a person they had to lie to (the interrogation condition), their response time for both lies and truths increased, as did their heart rate.
+Although the condition did not impact the subjective confidence that participants had in their answers, it suggests that believing oneself to be submitted to a machine that is supposedly able to detect deception by interpreting physiological signals is a harder and/or more stressful condition than lying to a person.
+While research linking interoception and deception is limited, our results are in line with studies that show an association between interoceptive awareness and anxiety [@yoris2015roles; @garfinkel2013interoception; @domschke2010interoceptive].
+Specifically, enhancing one's attention towards their internal bodily signals could have resulted in a hyper-vigilance towards physiological sensations that is perceived negatively.
+Additionally, our study also extends past deception research and further confirms the validity concerns in solely relying on physiological measures as an indicator of deception [@rosky2013f; @oviatt2018handbook].
 
@@
 This points toward a predominantly meta-cognitive effect without necessarily an actual bodily regulation (i.e., participants with good interoception feel that their lies are more convincing, but do not actively attenuate their bodily reactions).
+[**also consistent with research demonstrating distinctions between interoceptive awareness and accuracy; extends pevious research in which individuals with greater interoceptive sensibility and accuracy were not better at detecting lies.**]
 
@@
 Note that this is not limitation *per se*, as it answers a slightly different question  - what are the correlates of *objective* lying skills - than deception self-confidence.
+[**look for lit linking to what are commonly considered cues for lying**]
 

### 2023-01-08 paper/manuscript.Rmd
update

@@
       - "Writing – original draft"
-  - name          : "Ngoi Zi Liang"
+  - name          : "Claudia Liauw"
     affiliation   : "1"
     role:
-      - "Project administration"
-      - "Resources"
-      - "Writing – review & editing"
+      - "Data curation"
+      - "Formal Analysis"
   - name          : "S.H. Annabel Chen"
@@
 output:
-  papaja::apa6_word:
-    keep_tex: yes
-  pdf_document: default
   papaja::apa6_pdf:
     keep_tex: yes
-keywords: ""
-wordcount: ''
+keywords: "Deception, Interoception, Theory of Mind, Poygraph"
+wordcount: '3526'
 bibliography: ["references.bib"]
@@
 ToM refers to the ability to infer that others have mental states, such as beliefs, emotions and intentions, distinct from ourselves [@lee2021lying; @wellman2001meta; @baron1997mindblindness].
-The ability to tell lies, as well as their complexity, have previously been found to be related to higher TOM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role].
+The ability to tell lies, as well as their complexity, have previously been found to be related to higher ToM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role].
 However, studies investigating the link between ToM and deception have predominantly been focused on children and neuroatypical individuals [@beaudoin2020systematic; @bora2017meta; @roheger2022progression], and its importance in healthy adults remains to be clarified.
@@
 
-Besides paying attention to the person we lie to, trying to gauge whether they believe us, it is also possible that some attention is directed inwards: monitoring our own body and its reactions (e.g., cardiac activity and its related changes such as blushing), preventing them from being used as cues to infer our real intent.
+Besides paying attention to the person we lie to, to try to gauge whether they believe us, some attention is also directed inwards: monitoring our own body and its reactions (e.g., cardiac activity and its related changes such as blushing), which could be used as cues to infer our real intent.
 This begs the question of the potential role of interoceptive abilities in deception ability.
-Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing's conceptualizes interoception as a three-dimensional framework comprising three distinct facets, namely, interoceptive accuracy - the objective ability to monitor internal bodily signals; interoceptive sensibility - the subjective confidence in one's interoceptive accuracy; and interoceptive awareness - one's ability to identify and appropriately respond to their perceived interoceptive states.
-Interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].
-Although little research interest has been conferred to investigating the relationship between interoception and deceptive ability *per se*, previous decision-making studies have demonstrated a negative correlation between interoceptive awareness, a metacognitive dimension of interoception, and one's likelihood to make risky decisions [@dunn2010listening; @furman2013interoceptive].
+Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing's conceptualizes interoception as a three-dimensional construct comprising three distinct facets, namely, interoceptive accuracy - the objective ability to monitor internal bodily signals; interoceptive sensibility - the subjective confidence in one's interoceptive accuracy; and interoceptive awareness - one's ability to identify and appropriately respond to their perceived interoceptive states.
+Interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing, and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].
+Although few studies exist that investigate the relationship between interoception and deceptive ability *per se*, previous decision-making studies have demonstrated a negative correlation between interoceptive awareness, a metacognitive dimension of interoception, and one's likelihood to make risky decisions [@dunn2010listening; @furman2013interoceptive].
 In fact, this is consistent with the somatic marker hypothesis, which posits an association between interoception and a propensity towards making rational decisions [@damasio1996somatic].
 
-In contrast, some studies have instead found heightened interoceptive attention, one's self-focus towards internal bodily signals, to predict apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening].
+In contrast, however, some studies have instead found heightened interoceptive attention (one's self-focus towards internal bodily signals), to predict apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening].
 Extending these findings to social cognition, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high, whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
@@
 
-The aim of the present study was to explore the contribution of ToM and interoception abilities on individuals' deceptive skills, as indicated by their lying confidence, physiological arousal and response time.
+The aim of the present study was to explore the contribution of ToM and interoception abilities on individuals' deception skills, as indicated by their lying confidence, physiological arousal and response time.
 To this end, we designed a directed-lying paradigm with 2 conditions differing in the nature of their feedback cues.
@@
 
-30 university students were recruited through posters, flyers, and online social media platforms.
-Inclusion criteria included residing in Singapore, and an absence of current or history of neurological, psychiatric, or cardiovascular disorders.
+30 university students from Singapore were recruited through posters, flyers, and online social media platforms. 
+<!-- Inclusion criteria included residing in Singapore, and an absence of current or history of neurological, psychiatric, or cardiovascular disorders.  -->
 Four participants were excluded as their data was not recorded due to technical issues.
@@
 
-This pre-registered study (**OSF?** **Dom: I think so but not sure were to find the prereg**) was approved by the NTU Institutional Review Board (NTU-IRB-2020-09-007) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
+This study was approved by the NTU Institutional Review Board (NTU-IRB-2020-09-007).
 All participants provided their informed consent prior to participation and were awarded with academic credits upon completion of the study.
@@
 
-**TODO: create a procedure figure**
+<!-- **TODO: create a procedure figure** -->
 
-We designed and implemented in PsychoPy [@peirce2019psychopy2] a directed-lying task in which participants were instructed to answer 80 questions by either lying or telling the truth (depending on whether they see "lie" or "truth" written on the screen).
+Using PsychoPy [@peirce2019psychopy2], we implemented a directed-lying task in which participants were instructed to answer 80 questions by either lying or telling the truth (depending on whether they see "lie" or "truth" written on the screen).
 Importantly, they were told that for half of the trials, they would have to convince another participant that would be observing them form a separate room via a webcam connection (*Interrogation* condition).
@@
 The deception task was finally run, followed by a debriefing.
-Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of **4 sec** [TO-CHECK]).
+Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of 3.5 sec).
 
@@
 
-The data analysis was carried out using*R 4.2* [@RCoreTeam2022], *brms* [@Burkner2017], and the *easystats* collection of packages [@bayestestRArticle; @correlationArticle; @performanceArticle; @insightArticle].
-As the full reproducible analysis script and statistical results report are available at [**https://github.com/DominiqueMakowski/DeceptionInteroTom**](https://github.com/DominiqueMakowski/DeceptionInteroTom){.uri}, we will only focus on significant results in the manuscript.
+The data analysis was carried out using *R 4.2* [@RCoreTeam2022], *brms* [@Burkner2017], and the *easystats* collection of packages [@makowski2019bayestestr; @correlationArticle; @performanceArticle; @insightArticle], and the physiological signal processing was done using the default routines avaialble in *NeuroKit2* [@makowski2021neurokit2].
+As the full reproducible analysis script and statistical results report are available at
+https://github.com/DominiqueMakowski/DeceptionInteroTom
+, we will only focus on significant results in the manuscript.
 
@@
 
-The composite *TOM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67%\%$), specifically in the polygraph condition.
+The composite *TOM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67\%$), specifically in the polygraph condition.
 No significant effect was found with regards to heart rate, and no correlation was observed with dispositional lying traits (**Figure 1**).
 
-```{r message=FALSE, warning=FALSE, out.width="100%", fig.cap="TODO: Caption."}
+```{r message=FALSE, warning=FALSE, out.width="100%", fig.cap="Interindividual corrrelates of lying confidence.
+Shows the correlation between the participants' interoceptive and theory of mind composite scores and their average lying confidence, withing the two experimental conditions."}
 knitr::include_graphics("../figures/figure1.png")
@@
 The *Meta* interoception score was significantly associated with an increased confidence in lies, specifically in the polygraph condition ($\beta=0.20,~95\%~CI~[0.03, 0.35],~pd = 98.98\%$).
-It was also associated with faster answers for both lies ($\beta=-0.54,~95\%~CI~[-0.93, -0.15],~pd = 99.67\%$) and truths ($\beta=-0.29,~95\%~CI~[-0.63, 0.03],~pd = 96.10%\%$), specifically in the polygraph condition.
+It was also associated with faster answers for both lies ($\beta=-0.54,~95\%~CI~[-0.93, -0.15],~pd = 99.67\%$) and truths ($\beta=-0.29,~95\%~CI~[-0.63, 0.03],~pd = 96.10\%$), specifically in the polygraph condition.
 No significant association was found with heart rate.
@@
 
-The *Focus* interoception score was significantly associated with an increased confidence in truthful responses in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$) and interrogation condition ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76%\%$).
+The *Focus* interoception score was significantly associated with an increased confidence in truthful responses in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$) and interrogation condition ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%$).
 No significant association was found with RT or heart rate, but the score correlated with the dispositional lying *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$).
@@
 
-```{r message=FALSE, warning=FALSE, out.width="100%", fig.cap="TODO: Caption."}
+```{r message=FALSE, warning=FALSE, out.width="100%", fig.cap="Summary of findings showing the positive (green) and negative (red) associations between interoception and theory of mind abilities and deception skills, depending on the experimental condition."}
 knitr::include_graphics("../figures/figure2.png")
@@
 This points toward a predominantly meta-cognitive effect without necessarily an actual bodily regulation (i.e., participants with good interoception feel that their lies are more convincing, but do not actively attenuate their bodily reactions).
-[**also consistent with research demonstrating distinctions between interoceptive awareness and accuracy; extends pevious research in which individuals with greater interoceptive sensibility and accuracy were not better at detecting lies.**]
+<!-- [**also consistent with research demonstrating distinctions between interoceptive awareness and accuracy; extends pevious research in which individuals with greater interoceptive sensibility and accuracy were not better at detecting lies.**] -->
 
@@
 Note that this is not limitation *per se*, as it answers a slightly different question - what are the correlates of *objective* lying skills - than deception self-confidence.
-[**look for lit linking to what are commonly considered cues for lying**]
+<!-- [**look for lit linking to what are commonly considered cues for lying**] -->
 
@@
 While we tried to include an behavioral task as well as a subjective questionnaire for each, it has to be underlined that they are notoriously difficult concepts to measure.
-In particular, objective interoceptive accuracy was assessed using the Heartbeat Counting Task.
+In particular, objective interoceptive accuracy was assessed using the Heartbeat Counting Task (HCT).
 While the HCT used to be considered as a gold standard and is one of the most commonly used measure [@desmedt2022does], concerns regarding its validity has been highlighted in several studies [@desmedt2018heartbeat; @desmedt2022does; @brener2016towards; @legrand2022heart].
@@
 
-The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) for this research is available at [**https://github.com/DominiqueMakowski/DeceptionInteroTom**](https://github.com/DominiqueMakowski/DeceptionInteroTom){uri.}.
+The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) for this research is available at **https://github.com/DominiqueMakowski/DeceptionInteroTom**.
 
-# Funding
+<!-- # Funding -->
 
-**no funding**
+<!-- **no funding** -->
 
@@
 
-We would like to thank Jia Rong **what's his full name?**, Max (**full name**, partial RA) for his help in data collection and **...** for data analysis.
+We would like to thank Jia Rong Low and Maximilian Yong for his help in data collection.
 

### 2023-01-08 paper/manuscript.tex
update

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Deception, Interoception, Theory of Mind, Poygraph\newline\indent Word count: 3526}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage[labelfont=bf, font={color=gray,small}]{caption}
\usepackage{float}
\usepackage[document]{ragged2e}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The Heart can Lie: The Role of Interoception and Theory of Mind in Deception},
  pdfauthor={Dominique Makowski1, Zen J. Lau1, Tam Pham1, An Shu Te1, Stephanie Kirk1, Claudia Liauw1, \& S.H. Annabel Chen1, 2, 3, 4},
  pdflang={en-EN},
  pdfkeywords={Deception, Interoception, Theory of Mind, Poygraph},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{\textbf{The Heart can Lie: The Role of Interoception and Theory of Mind in Deception}}
\author{Dominique Makowski\textsuperscript{1}, Zen J. Lau\textsuperscript{1}, Tam Pham\textsuperscript{1}, An Shu Te\textsuperscript{1}, Stephanie Kirk\textsuperscript{1}, Claudia Liauw\textsuperscript{1}, \& S.H. Annabel Chen\textsuperscript{1, 2, 3, 4}}
\date{}

\shorttitle{Deception, Interoception, and ToM}

\authornote{

The authors made the following contributions. Dominique Makowski: Conceptualization, Data curation, Formal Analysis, Funding acquisition, Investigation, Methodology, Project administration, Resources, Software, Supervision, Validation, Visualization, Writing -- original draft; An Shu Te: Project administration, Resources, Investigation, Writing -- original draft; Stephanie Kirk: Project administration, Resources, Writing -- original draft; Claudia Liauw: Data curation, Formal Analysis; S.H. Annabel Chen: Project administration, Supervision, Writing -- review \& editing.

Correspondence concerning this article should be addressed to Dominique Makowski, HSS 04-18, 48 Nanyang Avenue, Singapore. E-mail: \href{mailto:dom.makowski@gmail.com}{\nolinkurl{dom.makowski@gmail.com}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Social Sciences, Nanyang Technological University, Singapore\\\textsuperscript{2} Centre for Research and Development in Learning, Nanyang Technological University, Singapore\\\textsuperscript{3} Lee Kong Chian School of Medicine, Nanyang Technological University, Singapore\\\textsuperscript{4} National Institute of Education, Nanyang Technological University, Singapore}

\begin{document}
\maketitle

\justify

Lying - the intentional attempt at instilling a false belief in others (Sip et al., 2012) - is a prevalent phenomenon carrying potentially important consequences. Interestingly, evidence suggests that the successful detection of a lying attempt depends more on the ability of the liar, than on the performance of the lie detector (Bond Jr \& DePaulo, 2008; Levine et al., 2011; Verigin et al., 2019). However, with most of the deception literature focused on deception detection (Masip, 2017; Sternglanz et al., 2019; Viji et al., 2022), the factors contributing to one's deception abilities remain unclear.

As deception requires the liar to intentionally manipulate the beliefs of others (Burgoon \& Buller, 1994; Sip et al., 2012), a significant line of research has been focused on the role of theory of mind (ToM) in lying ability. ToM refers to the ability to infer that others have mental states, such as beliefs, emotions and intentions, distinct from ourselves (Baron-Cohen, 1997; Lee \& Imuta, 2021; Wellman et al., 2001). The ability to tell lies, as well as their complexity, have previously been found to be related to higher ToM abilities (Evans \& Lee, 2011; Talwar et al., 2007, 2017). However, studies investigating the link between ToM and deception have predominantly been focused on children and neuroatypical individuals (Beaudoin et al., 2020; Bora \& Yener, 2017; Roheger et al., 2022), and its importance in healthy adults remains to be clarified.

Besides paying attention to the person we lie to, to try to gauge whether they believe us, some attention is also directed inwards: monitoring our own body and its reactions (e.g., cardiac activity and its related changes such as blushing), which could be used as cues to infer our real intent. This begs the question of the potential role of interoceptive abilities in deception ability. Broadly defined as one's sensitivity to their own internal signals and bodily states (Chen et al., 2021; Murphy et al., 2019; Weiss et al., 2014), Garfinkel et al. (2015)'s conceptualizes interoception as a three-dimensional construct comprising three distinct facets, namely, interoceptive accuracy - the objective ability to monitor internal bodily signals; interoceptive sensibility - the subjective confidence in one's interoceptive accuracy; and interoceptive awareness - one's ability to identify and appropriately respond to their perceived interoceptive states. Interoception has increasingly been tied to subjective perceptual experiences (Connell et al., 2018; Seth et al., 2012), as well as individual differences in executive functions, emotional processing, and decision-making (Barrett \& Simmons, 2015; Murphy et al., 2019; Petzschner et al., 2021). Although few studies exist that investigate the relationship between interoception and deceptive ability \emph{per se}, previous decision-making studies have demonstrated a negative correlation between interoceptive awareness, a metacognitive dimension of interoception, and one's likelihood to make risky decisions (Dunn et al., 2010; Furman et al., 2013). In fact, this is consistent with the somatic marker hypothesis, which posits an association between interoception and a propensity towards making rational decisions (Damasio, 1996).

In contrast, however, some studies have instead found heightened interoceptive attention (one's self-focus towards internal bodily signals), to predict apathetic, immoral behaviour, such as cheating (Ditto et al., 2006; Lenggenhager et al., 2013; Williams et al., 2016). Extending these findings to social cognition, Vabba et al. (2022) further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high, whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told. Given the scarce research on interoception and deception, more studies are herein needed to clarify these mixed findings.

The aim of the present study was to explore the contribution of ToM and interoception abilities on individuals' deception skills, as indicated by their lying confidence, physiological arousal and response time. To this end, we designed a directed-lying paradigm with 2 conditions differing in the nature of their feedback cues. The \emph{Interrogation} condition was designed to emphasize (and preferentially mobilize) ToM-related mechanisms, whereas the \emph{Polygraph} condition was designed to emphasize interoceptive mechanisms. We expected ToM and interoception to positively predict lying ability (i.e., higher lie confidence, shorter response time and lower physiological arousal), in particular in the \emph{Polygraph} and the \emph{Interrogation} condition, respectively.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

30 university students from Singapore were recruited through posters, flyers, and online social media platforms.
Four participants were excluded as their data was not recorded due to technical issues. The final sample consists 26 participants (Mean age = 20.9, SD = 2.0, range:{[}18, 25{]}, Sex: 65.4\% women, 34.6\% men). The heart rate of one participant and response time of one participant were excluded from further analysis due to extreme outlying values.

This study was approved by the NTU Institutional Review Board (NTU-IRB-2020-09-007). All participants provided their informed consent prior to participation and were awarded with academic credits upon completion of the study.

\hypertarget{measures}{%
\subsection{Measures}\label{measures}}

\hypertarget{theory-of-mind}{%
\subsubsection{Theory of Mind}\label{theory-of-mind}}

Two measures of ToM and related constructs were administered. The Yoni Task (Shamay-Tsoory \& Aharon-Peretz, 2007) is a behavioral task in which participants are presented with the face of a character named ``Yoni'', surrounded by 4 colored pictures of objects or faces. In total, each participant completed 101 trials - 49 trials assessing their affective TOM abilities, 37 trials assessing their cognitive TOM abilities and 15 control trial. During each trial, participants were shown a question and asked to make responses based on specific cues such as directions of eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical TOM).

The Basic Empathy Scale (BES, Jolliffe \& Farrington, 2006), a 20-item questionnaire measuring two dimensions of empathy (cognitive and affective) using a 5-point Likert scale was administered. Although ToM and empathy are regarded as distinct psychological constructs, previous research findings point to them being closely related (Gallant et al., 2020; Sebastian et al., 2012).

\hypertarget{interoception}{%
\subsubsection{Interoception}\label{interoception}}

To assess participants' interoceptive ability, participants completed a Heartbeat Counting Task (HCT, Schandry, 1981) while having their actual heartbeats recorded. During the HCT task, participants were instructed to count the number of heartbeats over 5 trials with varying time intervals (20s, 25s, 30s, 35s, 40s), the order of which was randomized. Interoceptive accuracy was computed from the difference between the estimated number and the real number of heart beats. Interoceptive sensibility was estimated as the average of the confidence ratings presented at the end of each trial. Interoceptive awareness was indexed by the correlation between the objective accuracy and the subjective confidence.

The MAIA-2 (Mehling et al., 2012), a 32-item questionnaire which measures 8 dimensions of interoception (Noticing, Not-Distracting, Not-Worrying, Attention, Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust) using 5-point Likert scales, was also administered.

\hypertarget{deception}{%
\subsubsection{Deception}\label{deception}}

\textbf{TODO: create a procedure figure}

Using PsychoPy (Peirce et al., 2019), we implemented a directed-lying task in which participants were instructed to answer 80 questions by either lying or telling the truth (depending on whether they see ``lie'' or ``truth'' written on the screen). Importantly, they were told that for half of the trials, they would have to convince another participant that would be observing them form a separate room via a webcam connection (\emph{Interrogation} condition). For the remaining trials, participants were tasked to convince a ``lie detection machine'' that would be assessing their behaviour through their physiological signals (\emph{Polygraph} condition). The two conditions were presented in a counter-balanced order, and each comprised of 40 trials (20 truth; 20 lies).

The sequence of each trial was the same for both conditions. A question was shown on a computer screen, either phrased directly (e.g., ``What is your favourite sport?''), or indirectly (e.g., ``Is your favourite sport Hockey?''), with accompanying instructions below that either asked participants to verbally lie or tell the truth (half of the trials in each condition, i.e., n = 20, were directed lies). Following a short interval (0.7 - 1.5s) for response preparation (during which ``Connecting\ldots{}'' was displayed on the screen), participants were presented with either a social-feedback or biofeedback cue (for the \emph{Interrogation} and \emph{Polygraph} conditions, respectively), displayed for a maximum of 10s. After the feedback cue, participants had to provide their answer to the question verbally (out loud) and press the `space' key to mark the end of their response. Following another short interval (1.5 - 2.5s) during which was written ``Disconnecting\ldots{}'' on the screen, participants were asked to rate, using an analog scale, their confidence in how convincing (i.e., likely to get judged as truthful) they perceived their response to be.

In the \emph{Interrogation} condition, participants had to answer each trial while receiving social feedback in the form of a video stream of an examiner, and were informed that the examiner would be evaluating the truthfulness of their responses by observing them through the live video feed. In actuality, the video was a pre-recorded video clips of a confederate's face (staying still with minimal reactions, and with a medical mask, as the experiment was run during COVID restrictions), and the same video-clips were used with all participants. Note that after debriefing, all participants reported believing that the stream was real and that the examiner was really there.

In the \emph{Polygraph} condition, participants had to answer each trial while receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded. Participants were informed that they were being shown live feedback of their own physiological activity. In actuality, we displayed pre-recorded video clips of a confederate's signals. Note that after debriefing, all participants reported believing that it was indeed their own signals being shown.

Finally, on top of the deception task, we also measured the self-reported tendency to lie in their everyday life using the \emph{Lie Scale} (Makowski, Pham, Lau, Raine, et al., 2021), a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency).

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

In the first phase of the study, participants answered a brief demographic survey before being administered the questionnaires and cognitive-behavioural tasks in a randomized order. Then, the physiological recording devices were set up. Cardiac activity (ECG) was recorded with 3 electrodes placed according to a modified Lead II configuration (Takuma et al., 1995), electrodermal activity (EDA) and respiration (using a respiration belt) were also recorded, but not analyzed for the study (unfortunately, most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (22 degrees Celsius) of the experimental room). All signals were recorded at 1000 Hz via the BioPac MP160 system (BioPac Systems Inc., USA). The deception task was finally run, followed by a debriefing. Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies \emph{vs.} truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of 3.5 sec).

\hypertarget{data-analysis}{%
\subsection{Data Analysis}\label{data-analysis}}

To ensure that our outcome variables were sensitive to the experimental manipulations, we first tested the effect of the question phrasing (direct \emph{vs.} indirect) and condition (polygraph \emph{vs.} interrogation) on the outcome variables. This analysis was performed using mixed models with the participants and questions both entered as random factors. Marginal contrasts analysis (denoted by \(\Delta\)) was also performed to clarify the differences between conditions. To allow for a better quantification of the uncertainty associated with the effects, as well as increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework (Makowski et al., 2019), using informative priors centred around 0 (\(t_{Confidence}(1, 0, 1)\), \(t_{RT}(1, 0, 3)\), \(t_{Heartrate}(1, 0, 8)\)).

To further counterbalance the low number of participants and maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, ToM and interoception) using factor analysis over PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained. Then, we modelled the relationship between these inter-individual composite scores (note that the analysis for all individual variables is nonetheless included in the analysis report) and the 3 outcome variables in interaction with the condition (polygraph \emph{vs.} interrogation). Finally, we investigated the relationship between the deception scale traits, and the theory of mind and interoception scores using Bayesian correlations.

The data analysis was carried out using \emph{R 4.2} (R Core Team, 2022), \emph{brms} (Bürkner, 2017), and the \emph{easystats} collection of packages (Lüdecke et al., 2021, 2019; Makowski et al., 2020, 2019), and the physiological signal processing was done using the default routines avaialble in \emph{NeuroKit2} (Makowski, Pham, Lau, Brammer, et al., 2021). As the full reproducible analysis script and statistical results report are available at
\url{https://github.com/DominiqueMakowski/DeceptionInteroTom}
, we will only focus on significant results in the manuscript.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{manipulation-check}{%
\subsection{Manipulation Check}\label{manipulation-check}}

Compared to truth, lies were rated with less confidence (\(\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%\)), but no difference between the conditions was found. On the other hand, the RT did not differ between truth and lies, but was significantly slower in the polygraph condition for both conditions (\(\Delta=0.25,~95\%~CI~[0.62, 0.41],~pd = 100\%\)). The heart rate was significantly more elevated during lies as compared to truth (\(\Delta=1.16,~95\%~CI~[0.57, 1.73],~pd = 100\%\)), and during interrogation as compared to the polygraph condition (\(\Delta=4.84 ,~95\%~CI~[4.23, 5.44],~pd = 100\%\)).

The indirect phrasing of the question only had a significant effect on RT (\(\beta=0.36,~95\%~CI~[0.21, 0.51],~pd = 100\%\)), leading to slower answers, regardless of whether they were lies or truths.

\hypertarget{feature-reduction}{%
\subsection{Feature Reduction}\label{feature-reduction}}

The 3 YONI-task dimensions and the 2 BES traits were combined into a unique factor, labelled \emph{TOM} (explaining 35.76\% of variance). It was loaded by the cognitive (.89), affective (.77), physical (.45) YONI dimension, and the affective (.41) and cognitive (.17) traits of the BES.

The 8 MAIA dimensions and the 3 HCT components were reduced to 4 factors (explaining 65.17\% of variance). The first factor, labelled \emph{Interoception - Meta} (23.59\%), was loaded primarily by Attention Regulation (.97), Self-regulation (.63), Emotional awareness (.60), and Noticing (.49) dimensions of the MAIA and the HCT confidence score (.40). The second factor, labelled \emph{Interoception - Listening} (18.54\%), was primarily loaded by the Body Listening (.92) and Trusting (.53) MAIA dimensions, and the Awareness (-.60) and Confidence (.46) HCT scores. The third factor, labelled \emph{Interoception - Focus} (12.07\%), was primarily loaded by MAIA Not-Distracting (.87), Emotional Awareness (-.40) and HCT Accuracy (.33). The fourth factor, labelled \emph{Interoception - Regulation} (10.97\%), was primarily loaded by MAIA not-worrying (.71), HCT Accuracy (.61) and MAIA Trusting (.40).

\hypertarget{theory-of-mind-1}{%
\subsection{Theory of Mind}\label{theory-of-mind-1}}

The composite \emph{TOM} score was significantly associated with less confident (\(\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%\)) and slower lies (\(\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67\%\)), specifically in the polygraph condition. No significant effect was found with regards to heart rate, and no correlation was observed with dispositional lying traits (\textbf{Figure 1}).

\begin{figure}
\includegraphics[width=1\linewidth]{../figures/figure1} \caption{Interindividual corrrelates of lying confidence. Shows the correlation between the participants' interoceptive and theory of mind composite scores and their average lying confidence, withing the two experimental conditions.}\label{fig:unnamed-chunk-1}
\end{figure}

\hypertarget{interoception-1}{%
\subsection{Interoception}\label{interoception-1}}

The \emph{Meta} interoception score was significantly associated with an increased confidence in lies, specifically in the polygraph condition (\(\beta=0.20,~95\%~CI~[0.03, 0.35],~pd = 98.98\%\)). It was also associated with faster answers for both lies (\(\beta=-0.54,~95\%~CI~[-0.93, -0.15],~pd = 99.67\%\)) and truths (\(\beta=-0.29,~95\%~CI~[-0.63, 0.03],~pd = 96.10\%\)), specifically in the polygraph condition. No significant association was found with heart rate.

The \emph{Listening} interoception score was significantly associated with an increased confidence in lies, in the polygraph (\(\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%\)) and interrogation condition (\(\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%\)). It was also associated with faster answers, particularly for lies (\(\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%\)) and truths (\(\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%\)) in the polygraph condition. No significant association was found with heart rate. This score also correlated with the dispositional lying \emph{Contextuality} trait (\(r = 0.50,~95\%~CI~[0.04, 0.64],~BF_{10} = 3.48\%\)).

The \emph{Focus} interoception score was significantly associated with an increased confidence in truthful responses in the polygraph (\(\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%\)) and interrogation condition (\(\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%\)). No significant association was found with RT or heart rate, but the score correlated with the dispositional lying \emph{Ability} trait (\(r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%\)).

The \emph{Regulation} interoception score was significantly associated with an increased confidence in lies in the polygraph (\(\beta=0.32,~95\%~CI~[0.14, 0.51],~pd = 99.99\%\)) and the interrogation conditions (\(\beta=0.18,~95\%~CI~[0.00, 0.36],~pd = 97.42\%\)), and with a decreased confidence in truth only in the polygraph condition (\(\beta=-0.1,~95\%~CI~[-0.36, 0.01],~pd = 97.16\%\)). No significant association was found with RT or heart rate (\textbf{Figure 2}).

\begin{figure}
\includegraphics[width=1\linewidth]{../figures/figure2} \caption{Summary of findings showing the positive (green) and negative (red) associations between interoception and theory of mind abilities and deception skills, depending on the experimental condition.}\label{fig:unnamed-chunk-2}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The present study examined the contribution of ToM and interoception on our ability to lie using a directed lie paradigm with two conditions (``Interrogation'' and ``Polygraph'') designed to enhance each of the two mechanisms. Interestingly, we found that when participants were presented with (fake) physiological feedback (the polygraph condition), instead of a face of a person they had to lie to (the interrogation condition), their response time for both lies and truths increased, as did their heart rate. Although the condition did not impact the subjective confidence that participants had in their answers, it suggests that believing oneself to be submitted to a machine that is supposedly able to detect deception by interpreting physiological signals is a harder and/or more stressful condition than lying to a person. While research linking interoception and deception is limited, our results are in line with studies that show an association between interoceptive awareness and anxiety (Domschke et al., 2010; Garfinkel \& Critchley, 2013; Yoris et al., 2015). Specifically, enhancing one's attention towards their internal bodily signals could have resulted in a hyper-vigilance towards physiological sensations that is perceived negatively. Additionally, our study also extends past deception research and further confirms the validity concerns in solely relying on physiological measures as an indicator of deception (Oviatt et al., 2018; Rosky, 2013).

Our results suggest that higher ToM abilities were related to a slower and less confident lies, but only in the polygraph condition. One possible interpretation is that people with stronger ToM abilities rely by default more on it when lying (i.e., they focus on - and try to read - the other person). When that mechanism is cut off (i.e., when there is no person to lie to - but in our case a ``machine''), their lying ability decreases.

We also showed that interoceptive abilities are correlated with a higher confidence in one's lies in the polygraph condition, a condition in which the attention towards internal reactions is fostered. However, in contrast to previous studies (Füstös et al., 2013; Owens et al., 2018; Pinna \& Edwards, 2020; Pollatos et al., 2007), we did not find any significant relationship between individuals' interoception scores and the heart rate changes during their answers. This points toward a predominantly meta-cognitive effect without necessarily an actual bodily regulation (i.e., participants with good interoception feel that their lies are more convincing, but do not actively attenuate their bodily reactions).

Although yielding promising results, this exploratory study is limited by the sample size. Although we tried to mitigate it by 1) extracting more robust variables (by combining multiple ones by means of feature reduction) and 2) using a suited analysis approach (Bayesian statistics with informative priors), future replication studies with larger samples are warranted to confirm this first investigation. Nonetheless, we believe our results to be credible as we find consistent patterns across various facets and measures (for instance, all interoceptive dimensions, although distinct, share a similar trend) in line with theoretical expectations. The statistical power could also explain the overall lack of results with heart rate, which has a higher signal-to-noise ratio as compared to subjective reports (such as confidence scales).

Another aspect to note is the strong reliance on self-reported measures as outcome variables of lie ability (in particular, the measure of answer confidence, but also the auto-questionnaires). This might conflate meta-cognitive abilities as well as dishonest answers. Although we tried to include more objective measures, such as RT (although it too was tied to the participants' conscious decision to press a key) and heart rate, future studies should attempt at measuring objectively the answer (lie or truth) quality, for instance by means of external examiners. Note that this is not limitation \emph{per se}, as it answers a slightly different question - what are the correlates of \emph{objective} lying skills - than deception self-confidence.

Additionally to limitations pertaining to the measure of lying ability, care has to be given to the measure of the predictor constructs, namely ToM and interoception. While we tried to include an behavioral task as well as a subjective questionnaire for each, it has to be underlined that they are notoriously difficult concepts to measure. In particular, objective interoceptive accuracy was assessed using the Heartbeat Counting Task (HCT). While the HCT used to be considered as a gold standard and is one of the most commonly used measure (Desmedt et al., 2022), concerns regarding its validity has been highlighted in several studies (Brener \& Ring, 2016; Desmedt et al., 2018, 2022; Legrand et al., 2022). Given increasing research efforts invested in the development of novel interoception tasks (Legrand et al., 2022; Plans et al., 2021; Ponzo et al., 2021), future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties. Additionally, our application of feature reduction as a noise-elimination measure could have over-simplified the data. A more complex pattern of relationships, with different contributions of various subdimensions of ToM and interoception, could emerge provided a sufficient statistical power and valid measures.

In conclusion, this study study is a first step towards assessing the contribution of ToM and interoception abilities in deception in one's ability to lie convincingly. We introduced a new paradigm that is able to modulate the contribution of these mechanisms while remaining relevant to applied fields of lie detection and criminology (in which the experimental conditions find echoing practices). Our results provide princeps evidence that interoception could be a key - and overlooked - mechanism in deception.

\hypertarget{data-availability}{%
\section{Data Availability}\label{data-availability}}

The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) for this research is available at \textbf{\url{https://github.com/DominiqueMakowski/DeceptionInteroTom}}.

\hypertarget{conflict-of-interest-statement}{%
\section{Conflict of Interest Statement}\label{conflict-of-interest-statement}}

The authors declare no conflict of interest.

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

We would like to thank Jia Rong Low and Maximilian Yong for his help in data collection.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begin{verbatim}
## Warning in readLines(file): incomplete final line found on 'references.bib'
\end{verbatim}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-baron1997mindblindness}{}}%
Baron-Cohen, S. (1997). \emph{Mindblindness: An essay on autism and theory of mind}. MIT press.

\leavevmode\vadjust pre{\hypertarget{ref-barrett2015interoceptive}{}}%
Barrett, L. F., \& Simmons, W. K. (2015). Interoceptive predictions in the brain. \emph{Nature Reviews Neuroscience}, \emph{16}(7), 419--429.

\leavevmode\vadjust pre{\hypertarget{ref-beaudoin2020systematic}{}}%
Beaudoin, C., Leblanc, É., Gagner, C., \& Beauchamp, M. H. (2020). Systematic review and inventory of theory of mind measures for young children. \emph{Frontiers in Psychology}, \emph{10}, 2905.

\leavevmode\vadjust pre{\hypertarget{ref-bond2008individual}{}}%
Bond Jr, C. F., \& DePaulo, B. M. (2008). Individual differences in judging deception: Accuracy and bias. \emph{Psychological Bulletin}, \emph{134}(4), 477.

\leavevmode\vadjust pre{\hypertarget{ref-bora2017meta}{}}%
Bora, E., \& Yener, G. G. (2017). Meta-analysis of social cognition in mild cognitive impairment. \emph{Journal of Geriatric Psychiatry and Neurology}, \emph{30}(4), 206--213.

\leavevmode\vadjust pre{\hypertarget{ref-brener2016towards}{}}%
Brener, J., \& Ring, C. (2016). Towards a psychophysics of interoceptive processes: The measurement of heartbeat detection. \emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{371}(1708), 20160015.

\leavevmode\vadjust pre{\hypertarget{ref-burgoon1994interpersonal}{}}%
Burgoon, J. K., \& Buller, D. B. (1994). Interpersonal deception: III. Effects of deceit on perceived communication and nonverbal behavior dynamics. \emph{Journal of Nonverbal Behavior}, \emph{18}(2), 155--184.

\leavevmode\vadjust pre{\hypertarget{ref-Burkner2017}{}}%
Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}

\leavevmode\vadjust pre{\hypertarget{ref-chen2021emerging}{}}%
Chen, W. G., Schloesser, D., Arensdorf, A. M., Simmons, J. M., Cui, C., Valentino, R., Gnadt, J. W., Nielsen, L., Hillaire-Clarke, C. S., Spruance, V., et al. (2021). The emerging science of interoception: Sensing, integrating, interpreting, and regulating signals within the self. \emph{Trends in Neurosciences}, \emph{44}(1), 3--16.

\leavevmode\vadjust pre{\hypertarget{ref-connell2018interoception}{}}%
Connell, L., Lynott, D., \& Banks, B. (2018). Interoception: The forgotten modality in perceptual grounding of abstract and concrete concepts. \emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{373}(1752), 20170143.

\leavevmode\vadjust pre{\hypertarget{ref-damasio1996somatic}{}}%
Damasio, A. R. (1996). The somatic marker hypothesis and the possible functions of the prefrontal cortex. \emph{Philosophical Transactions of the Royal Society of London. Series B: Biological Sciences}, \emph{351}(1346), 1413--1420.

\leavevmode\vadjust pre{\hypertarget{ref-desmedt2018heartbeat}{}}%
Desmedt, O., Luminet, O., \& Corneille, O. (2018). The heartbeat counting task largely involves non-interoceptive processes: Evidence from both the original and an adapted counting task. \emph{Biological Psychology}, \emph{138}, 185--188.

\leavevmode\vadjust pre{\hypertarget{ref-desmedt2022does}{}}%
Desmedt, O., Van Den Houte, M., Walentynowicz, M., Dekeyser, S., Luminet, O., \& Corneille, O. (2022). How does heartbeat counting task performance relate to theoretically-relevant mental health outcomes? A meta-analysis. \emph{Collabra: Psychology}, \emph{8}(1), 33271.

\leavevmode\vadjust pre{\hypertarget{ref-ditto2006visceral}{}}%
Ditto, P. H., Pizarro, D. A., Epstein, E. B., Jacobson, J. A., \& MacDonald, T. K. (2006). Visceral influences on risk-taking behavior. \emph{Journal of Behavioral Decision Making}, \emph{19}(2), 99--113.

\leavevmode\vadjust pre{\hypertarget{ref-domschke2010interoceptive}{}}%
Domschke, K., Stevens, S., Pfleiderer, B., \& Gerlach, A. L. (2010). Interoceptive sensitivity in anxiety and anxiety disorders: An overview and integration of neurobiological findings. \emph{Clinical Psychology Review}, \emph{30}(1), 1--11.

\leavevmode\vadjust pre{\hypertarget{ref-dunn2010listening}{}}%
Dunn, B. D., Galton, H. C., Morgan, R., Evans, D., Oliver, C., Meyer, M., Cusack, R., Lawrence, A. D., \& Dalgleish, T. (2010). Listening to your heart: How interoception shapes emotion experience and intuitive decision making. \emph{Psychological Science}, \emph{21}(12), 1835--1844.

\leavevmode\vadjust pre{\hypertarget{ref-evans2011verbal}{}}%
Evans, A. D., \& Lee, K. (2011). Verbal deception from late childhood to middle adolescence and its relation to executive functioning skills. \emph{Developmental Psychology}, \emph{47}(4), 1108.

\leavevmode\vadjust pre{\hypertarget{ref-furman2013interoceptive}{}}%
Furman, D. J., Waugh, C. E., Bhattacharjee, K., Thompson, R. J., \& Gotlib, I. H. (2013). Interoceptive awareness, positive affect, and decision making in major depressive disorder. \emph{Journal of Affective Disorders}, \emph{151}(2), 780--785.

\leavevmode\vadjust pre{\hypertarget{ref-fustos2013embodiment}{}}%
Füstös, J., Gramann, K., Herbert, B. M., \& Pollatos, O. (2013). On the embodiment of emotion regulation: Interoceptive awareness facilitates reappraisal. \emph{Social Cognitive and Affective Neuroscience}, \emph{8}(8), 911--917.

\leavevmode\vadjust pre{\hypertarget{ref-gallant2020developing}{}}%
Gallant, C. M., Lavis, L., \& Mahy, C. E. (2020). Developing an understanding of others' emotional states: Relations among affective theory of mind and empathy measures in early childhood. \emph{British Journal of Developmental Psychology}, \emph{38}(2), 151--166.

\leavevmode\vadjust pre{\hypertarget{ref-garfinkel2013interoception}{}}%
Garfinkel, S. N., \& Critchley, H. D. (2013). Interoception, emotion and brain: New insights link internal physiology to social behaviour. Commentary on: {``Anterior insular cortex mediates bodily sensibility and social anxiety''} by terasawa et al.(2012). \emph{Social Cognitive and Affective Neuroscience}, \emph{8}(3), 231--234.

\leavevmode\vadjust pre{\hypertarget{ref-garfinkel2015knowing}{}}%
Garfinkel, S. N., Seth, A. K., Barrett, A. B., Suzuki, K., \& Critchley, H. D. (2015). Knowing your own heart: Distinguishing interoceptive accuracy from interoceptive awareness. \emph{Biological Psychology}, \emph{104}, 65--74.

\leavevmode\vadjust pre{\hypertarget{ref-jolliffe2006development}{}}%
Jolliffe, D., \& Farrington, D. P. (2006). Development and validation of the basic empathy scale. \emph{Journal of Adolescence}, \emph{29}(4), 589--611.

\leavevmode\vadjust pre{\hypertarget{ref-lee2021lying}{}}%
Lee, J. Y. S., \& Imuta, K. (2021). Lying and theory of mind: A meta-analysis. \emph{Child Development}, \emph{92}(2), 536--553.

\leavevmode\vadjust pre{\hypertarget{ref-legrand2022heart}{}}%
Legrand, N., Nikolova, N., Correa, C., Brændholt, M., Stuckert, A., Kildahl, N., Vejlø, M., Fardo, F., \& Allen, M. (2022). The heart rate discrimination task: A psychophysical method to estimate the accuracy and precision of interoceptive beliefs. \emph{Biological Psychology}, \emph{168}, 108239.

\leavevmode\vadjust pre{\hypertarget{ref-lenggenhager2013listening}{}}%
Lenggenhager, B., Azevedo, R. T., Mancini, A., \& Aglioti, S. M. (2013). Listening to your heart and feeling yourself: Effects of exposure to interoceptive signals during the ultimatum game. \emph{Experimental Brain Research}, \emph{230}(2), 233--241.

\leavevmode\vadjust pre{\hypertarget{ref-levine2011sender}{}}%
Levine, T. R., Serota, K. B., Shulman, H., Clare, D. D., Park, H. S., Shaw, A. S., Shim, J. C., \& Lee, J. H. (2011). Sender demeanor: Individual differences in sender believability have a powerful impact on deception detection judgments. \emph{Human Communication Research}, \emph{37}(3), 377--403.

\leavevmode\vadjust pre{\hypertarget{ref-performanceArticle}{}}%
Lüdecke, D., Ben-Shachar, M., Patil, I., Waggoner, P., \& Makowski, D. (2021). {performance}: An {R} package for assessment, comparison and testing of statistical models. \emph{Journal of Open Source Software}, \emph{6}(60), 3139. \url{https://doi.org/10.21105/joss.03139}

\leavevmode\vadjust pre{\hypertarget{ref-insightArticle}{}}%
Lüdecke, D., Waggoner, P., \& Makowski, D. (2019). Insight: A unified interface to access information from model objects in {R}. \emph{Journal of Open Source Software}, \emph{4}(38), 1412. \url{https://doi.org/10.21105/joss.01412}

\leavevmode\vadjust pre{\hypertarget{ref-makowski2019bayestestr}{}}%
Makowski, D., Ben-Shachar, M. S., \& Lüdecke, D. (2019). bayestestR: Describing effects and their uncertainty, existence and significance within the bayesian framework. \emph{Journal of Open Source Software}, \emph{4}(40), 1541.

\leavevmode\vadjust pre{\hypertarget{ref-correlationArticle}{}}%
Makowski, D., Ben-Shachar, M., Patil, I., \& Lüdecke, D. (2020). Methods and algorithms for correlation analysis in {R}. \emph{Journal of Open Source Software}, \emph{5}(51), 2306. \url{https://doi.org/10.21105/joss.02306}

\leavevmode\vadjust pre{\hypertarget{ref-makowski2021neurokit2}{}}%
Makowski, D., Pham, T., Lau, Z. J., Brammer, J. C., Lespinasse, F., Pham, H., Schölzel, C., \& Chen, S. (2021). NeuroKit2: A python toolbox for neurophysiological signal processing. \emph{Behavior Research Methods}, \emph{53}(4), 1689--1696.

\leavevmode\vadjust pre{\hypertarget{ref-makowski2021structure}{}}%
Makowski, D., Pham, T., Lau, Z. J., Raine, A., \& Chen, S. (2021). The structure of deception: Validation of the lying profile questionnaire. \emph{Current Psychology}, 1--16.

\leavevmode\vadjust pre{\hypertarget{ref-masip2017deception}{}}%
Masip, J. (2017). Deception detection: State of the art and future prospects. \emph{Psicothema}, \emph{29}(2), 149--159.

\leavevmode\vadjust pre{\hypertarget{ref-mehling2012multidimensional}{}}%
Mehling, W. E., Price, C., Daubenmier, J. J., Acree, M., Bartmess, E., \& Stewart, A. (2012). The multidimensional assessment of interoceptive awareness (MAIA). \emph{PloS One}, \emph{7}(11), e48230.

\leavevmode\vadjust pre{\hypertarget{ref-murphy2019classifying}{}}%
Murphy, J., Catmur, C., \& Bird, G. (2019). Classifying individual differences in interoception: Implications for the measurement of interoceptive awareness. \emph{Psychonomic Bulletin \& Review}, \emph{26}(5), 1467--1471.

\leavevmode\vadjust pre{\hypertarget{ref-oviatt2018handbook}{}}%
Oviatt, S., Schuller, B., Cohen, P. R., Sonntag, D., Potamianos, G., \& Krüger, A. (2018). \emph{The handbook of multimodal-multisensor interfaces: Signal processing, architectures, and detection of emotion and cognition-volume 2}. Association for Computing Machinery; Morgan \& Claypool.

\leavevmode\vadjust pre{\hypertarget{ref-owens2018investigating}{}}%
Owens, A. P., Friston, K. J., Low, D. A., Mathias, C. J., \& Critchley, H. D. (2018). Investigating the relationship between cardiac interoception and autonomic cardiac control using a predictive coding framework. \emph{Autonomic Neuroscience}, \emph{210}, 65--71.

\leavevmode\vadjust pre{\hypertarget{ref-peirce2019psychopy2}{}}%
Peirce, J., Gray, J. R., Simpson, S., MacAskill, M., Höchenberger, R., Sogo, H., Kastman, E., \& Lindeløv, J. K. (2019). PsychoPy2: Experiments in behavior made easy. \emph{Behavior Research Methods}, \emph{51}(1), 195--203.

\leavevmode\vadjust pre{\hypertarget{ref-petzschner2021computational}{}}%
Petzschner, F. H., Garfinkel, S. N., Paulus, M. P., Koch, C., \& Khalsa, S. S. (2021). Computational models of interoception and body regulation. \emph{Trends in Neurosciences}, \emph{44}(1), 63--76.

\leavevmode\vadjust pre{\hypertarget{ref-pinna2020systematic}{}}%
Pinna, T., \& Edwards, D. J. (2020). A systematic review of associations between interoception, vagal tone, and emotional regulation: Potential applications for mental health, wellbeing, psychological flexibility, and chronic conditions. \emph{Frontiers in Psychology}, \emph{11}, 1792.

\leavevmode\vadjust pre{\hypertarget{ref-plans2021measuring}{}}%
Plans, D., Ponzo, S., Morelli, D., Cairo, M., Ring, C., Keating, C. T., Cunningham, A., Catmur, C., Murphy, J., \& Bird, G. (2021). Measuring interoception: The phase adjustment task. \emph{Biological Psychology}, \emph{165}, 108171.

\leavevmode\vadjust pre{\hypertarget{ref-pollatos2007heart}{}}%
Pollatos, O., Herbert, B. M., Matthias, E., \& Schandry, R. (2007). Heart rate response after emotional picture presentation is modulated by interoceptive awareness. \emph{International Journal of Psychophysiology}, \emph{63}(1), 117--124.

\leavevmode\vadjust pre{\hypertarget{ref-ponzo2021measuring}{}}%
Ponzo, S., Morelli, D., Suksasilp, C., Cairo, M., \& Plans, D. (2021). Measuring interoception: The CARdiac elevation detection task. \emph{Frontiers in Psychology}, \emph{12}.

\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}

\leavevmode\vadjust pre{\hypertarget{ref-roheger2022progression}{}}%
Roheger, M., Brenning, J., Riemann, S., Martin, A. K., Flöel, A., \& Meinzer, M. (2022). Progression of socio-cognitive impairment from healthy aging to alzheimer's dementia: A systematic review and meta-analysis. \emph{Neuroscience \& Biobehavioral Reviews}, 104796.

\leavevmode\vadjust pre{\hypertarget{ref-rosky2013f}{}}%
Rosky, J. W. (2013). The (f) utility of post-conviction polygraph testing. \emph{Sexual Abuse}, \emph{25}(3), 259--281.

\leavevmode\vadjust pre{\hypertarget{ref-schandry1981heart}{}}%
Schandry, R. (1981). Heart beat perception and emotional experience. \emph{Psychophysiology}, \emph{18}(4), 483--488.

\leavevmode\vadjust pre{\hypertarget{ref-sebastian2012neural}{}}%
Sebastian, C. L., Fontaine, N. M., Bird, G., Blakemore, S.-J., De Brito, S. A., McCrory, E. J., \& Viding, E. (2012). Neural processing associated with cognitive and affective theory of mind in adolescents and adults. \emph{Social Cognitive and Affective Neuroscience}, \emph{7}(1), 53--63.

\leavevmode\vadjust pre{\hypertarget{ref-seth2012interoceptive}{}}%
Seth, A. K., Suzuki, K., \& Critchley, H. D. (2012). An interoceptive predictive coding model of conscious presence. \emph{Frontiers in Psychology}, \emph{2}, 395.

\leavevmode\vadjust pre{\hypertarget{ref-shamay2007dissociable}{}}%
Shamay-Tsoory, S. G., \& Aharon-Peretz, J. (2007). Dissociable prefrontal networks for cognitive and affective theory of mind: A lesion study. \emph{Neuropsychologia}, \emph{45}(13), 3054--3067.

\leavevmode\vadjust pre{\hypertarget{ref-sip2012if}{}}%
Sip, K. E., Skewes, J. C., Marchant, J. L., McGregor, W. B., Roepstorff, A., \& Frith, C. D. (2012). What if i get busted? Deception, choice, and decision-making in social interaction. \emph{Frontiers in Neuroscience}, \emph{6}, 58.

\leavevmode\vadjust pre{\hypertarget{ref-sternglanz2019review}{}}%
Sternglanz, R. W., Morris, W. L., Morrow, M., \& Braverman, J. (2019). A review of meta-analyses about deception detection. \emph{The Palgrave Handbook of Deceptive Communication}, 303--326.

\leavevmode\vadjust pre{\hypertarget{ref-takuma1995alternative}{}}%
Takuma, K., Hori, S., Sasaki, J., Shinozawa, Y., Yoshikawa, T., Handa, S., Horikawa, M., \& Aikawa, N. (1995). An alternative limb lead system for electrocardiographs in emergency patients. \emph{The American Journal of Emergency Medicine}, \emph{13}(5), 514--517. \url{https://doi.org/10.1016/0735-6757(95)90160-4}

\leavevmode\vadjust pre{\hypertarget{ref-talwar2017role}{}}%
Talwar, V., Crossman, A., \& Wyman, J. (2017). The role of executive functioning and theory of mind in children's lies for another and for themselves. \emph{Early Childhood Research Quarterly}, \emph{41}, 126--135.

\leavevmode\vadjust pre{\hypertarget{ref-talwar2007lying}{}}%
Talwar, V., Gordon, H. M., \& Lee, K. (2007). Lying in the elementary school years: Verbal deception and its relation to second-order belief understanding. \emph{Developmental Psychology}, \emph{43}(3), 804.

\leavevmode\vadjust pre{\hypertarget{ref-vabba2022interoceptive}{}}%
Vabba, A., Porciello, G., Panasiti, M. S., \& Aglioti, S. M. (2022). Interoceptive influences on the production of self-serving lies in reputation risk conditions. \emph{International Journal of Psychophysiology}, \emph{177}, 34--42.

\leavevmode\vadjust pre{\hypertarget{ref-verigin2019lie}{}}%
Verigin, B. L., Meijer, E. H., Bogaard, G., \& Vrij, A. (2019). Lie prevalence, lie characteristics and strategies of self-reported good liars. \emph{PloS One}, \emph{14}(12), e0225566.

\leavevmode\vadjust pre{\hypertarget{ref-viji2022history}{}}%
Viji, D., Gupta, N., \& Parekh, K. H. (2022). History of deception detection techniques. \emph{Proceedings of International Conference on Deep Learning, Computing and Intelligence}, 373--387.

\leavevmode\vadjust pre{\hypertarget{ref-weiss2014interaction}{}}%
Weiss, S., Sack, M., Henningsen, P., \& Pollatos, O. (2014). On the interaction of self-regulation, interoception and pain perception. \emph{Psychopathology}, \emph{47}(6), 377--382.

\leavevmode\vadjust pre{\hypertarget{ref-wellman2001meta}{}}%
Wellman, H. M., Cross, D., \& Watson, J. (2001). Meta-analysis of theory-of-mind development: The truth about false belief. \emph{Child Development}, \emph{72}(3), 655--684.

\leavevmode\vadjust pre{\hypertarget{ref-williams2016valjean}{}}%
Williams, E. F., Pizarro, D., Ariely, D., \& Weinberg, J. D. (2016). The valjean effect: Visceral states and cheating. \emph{Emotion}, \emph{16}(6), 897.

\leavevmode\vadjust pre{\hypertarget{ref-yoris2015roles}{}}%
Yoris, A., Esteves, S., Couto, B., Melloni, M., Kichic, R., Cetkovich, M., Favaloro, R., Moser, J., Manes, F., Ibanez, A., et al. (2015). The roles of interoceptive sensitivity and metacognitive interoception in panic. \emph{Behavioral and Brain Functions}, \emph{11}(1), 1--6.

\end{CSLReferences}

\endgroup

\end{document}

### 2023-01-08 paper/manuscript.Rmd
update more

@@
 Interestingly, evidence suggests that the successful detection of a lying attempt depends more on the ability of the liar, than on the performance of the lie detector [@verigin2019lie; @bond2008individual; @levine2011sender].
-However, with most of the deception literature focused on deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], the factors contributing to one's deception abilities remain unclear.
+However, with most of the deception literature focused on deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], the factors contributing to one's ability to successfully lie remain unclear.
 
@@
 
-Besides paying attention to the person we lie to, to try to gauge whether they believe us, some attention is also directed inwards: monitoring our own body and its reactions (e.g., cardiac activity and its related changes such as blushing), which could be used as cues to infer our real intent.
+Besides paying attention to the person we lie to, gauging whether they believe us, some attention is also directed inwards: monitoring our own body and its reactions (e.g., cardiac activity and its related changes such as blushing), which could be used as cues to infer our real intent.
 This begs the question of the potential role of interoceptive abilities in deception ability.
@@
 
-This study was approved by the NTU Institutional Review Board (NTU-IRB-2020-09-007).
+This study was in accordance with the Declaration of Helsinki and was approved by the NTU Institutional Review Board (NTU-IRB-2020-09-007).
 All participants provided their informed consent prior to participation and were awarded with academic credits upon completion of the study.
@@
 
-Two measures of ToM and related constructs were administered.
+Two measures of ToM and its related constructs were administered.
 The Yoni Task [@shamay2007dissociable] is a behavioral task in which participants are presented with the face of a character named "Yoni", surrounded by 4 colored pictures of objects or faces.
-In total, each participant completed 101 trials - 49 trials assessing their affective TOM abilities, 37 trials assessing their cognitive TOM abilities and 15 control trial.
-During each trial, participants were shown a question and asked to make responses based on specific cues such as directions of eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical TOM).
+In total, each participant completed 101 trials - 49 trials assessing their affective TOM abilities, 37 trials assessing their cognitive TOM abilities and 15 control trials.
+During each trial, participants were shown a question and asked to make responses based on specific cues such as directions of Yoni's eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical TOM).
 
@@
 Using PsychoPy [@peirce2019psychopy2], we implemented a directed-lying task in which participants were instructed to answer 80 questions by either lying or telling the truth (depending on whether they see "lie" or "truth" written on the screen).
-Importantly, they were told that for half of the trials, they would have to convince another participant that would be observing them form a separate room via a webcam connection (*Interrogation* condition).
+Importantly, they were told that for half of the trials, they would have to convince another participant that would be observing them from a separate room via a webcam connection (*Interrogation* condition).
 For the remaining trials, participants were tasked to convince a "lie detection machine" that would be assessing their behaviour through their physiological signals (*Polygraph* condition).
@@
 Following a short interval (0.7 - 1.5s) for response preparation (during which "Connecting..." was displayed on the screen), participants were presented with either a social-feedback or biofeedback cue (for the *Interrogation* and *Polygraph* conditions, respectively), displayed for a maximum of 10s.
-After the feedback cue, participants had to provide their answer to the question verbally (out loud) and press the 'space' key to mark the end of their response.
+After the feedback cue, participants had to provide their answer to the question (verbally) aloud and press the 'space' key to mark the end of their response.
 Following another short interval (1.5 - 2.5s) during which was written "Disconnecting..." on the screen, participants were asked to rate, using an analog scale, their confidence in how convincing (i.e., likely to get judged as truthful) they perceived their response to be.
 
-In the *Interrogation* condition, participants had to answer each trial while receiving social feedback in the form of a video stream of an examiner, and were informed that the examiner would be evaluating the truthfulness of their responses by observing them through the live video feed.
-In actuality, the video was a pre-recorded video clips of a confederate's face (staying still with minimal reactions, and with a medical mask, as the experiment was run during COVID restrictions), and the same video-clips were used with all participants.
+In the *Interrogation* condition, participants had to provide their answer for each trial after receiving social feedback in the form of a video stream of an examiner, and were informed that the examiner would be evaluating the truthfulness of their responses based on their observations of them through the live video feed.
+In actuality, the displayed video feed was pre-recorded video clips of a confederate's face (staying still with minimal reactions, and wearing a medical mask, as the experiment was administered in the face of COVID restrictions), and the same video-clips were used with all participants.
 Note that after debriefing, all participants reported believing that the stream was real and that the examiner was really there.
 
-In the *Polygraph* condition, participants had to answer each trial while receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded.
-Participants were informed that they were being shown live feedback of their own physiological activity.
-In actuality, we displayed pre-recorded video clips of a confederate's signals.
+In the *Polygraph* condition, participants had to provide their answer for each trial after receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded.
+Specifically, participants were informed that they were being shown live feedback of their own physiological activity.
+In actuality, we displayed pre-recorded video clips of a confederate's physiological signals.
 Note that after debriefing, all participants reported believing that it was indeed their own signals being shown.
 
-Finally, on top of the deception task, we also measured the self-reported tendency to lie in their everyday life using the *Lie Scale* [@makowski2021structure], a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency).
+Finally, on top of the deception task, we also measured participants' self-reported tendency to lie in their everyday life using the *Lie Scale* [@makowski2021structure], a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency).
 
@@
 In the first phase of the study, participants answered a brief demographic survey before being administered the questionnaires and cognitive-behavioural tasks in a randomized order.
-Then, the physiological recording devices were set up.
-Cardiac activity (ECG) was recorded with 3 electrodes placed according to a modified Lead II configuration [@takuma1995alternative], electrodermal activity (EDA) and respiration (using a respiration belt) were also recorded, but not analyzed for the study (unfortunately, most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (22 degrees Celsius) of the experimental room).
+Then, the physiological recording devices were set up as follows: Cardiac activity (ECG) was recorded with 3 electrodes placed according to a modified Lead II configuration [@takuma1995alternative]; electrodermal activity (EDA) and respiration (using a respiration belt) were also recorded, but not analyzed for the study (unfortunately, most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (22 degrees Celsius) of the experimental room).
 All signals were recorded at 1000 Hz via the BioPac MP160 system (BioPac Systems Inc., USA).
 The deception task was finally run, followed by a debriefing.
-Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of 3.5 sec).
+Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of 3.5s).
 
@@
 Marginal contrasts analysis (denoted by $\Delta$) was also performed to clarify the differences between conditions.
-To allow for a better quantification of the uncertainty associated with the effects, as well as increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework [@makowski2019bayestestr], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).
+To allow for a better quantification of the uncertainty associated with the effects, as well as to increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework [@makowski2019bayestestr], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).
 
@@
 Then, we modelled the relationship between these inter-individual composite scores (note that the analysis for all individual variables is nonetheless included in the analysis report) and the 3 outcome variables in interaction with the condition (polygraph *vs.* interrogation).
-Finally, we investigated the relationship between the deception scale traits, and the theory of mind and interoception scores using Bayesian correlations.
+Finally, we investigated the relationship between the deception scale traits, and the ToM and interoception scores using Bayesian correlations.
 
@@
 
-Compared to truth, lies were rated with less confidence ($\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%$), but no difference between the conditions was found.
+Compared to truth, lies were rated with less confidence ($\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%$), but no significant difference between the conditions was found.
 On the other hand, the RT did not differ between truth and lies, but was significantly slower in the polygraph condition for both conditions ($\Delta=0.25,~95\%~CI~[0.62, 0.41],~pd = 100\%$).
@@
 The 3 YONI-task dimensions and the 2 BES traits were combined into a unique factor, labelled *TOM* (explaining 35.76% of variance).
-It was loaded by the cognitive (.89), affective (.77), physical (.45) YONI dimension, and the affective (.41) and cognitive (.17) traits of the BES.
+It was loaded by the cognitive (.89), affective (.77), physical (.45) YONI dimensions, and the affective (.41) and cognitive (.17) facets of the BES.
 
@@
 
-The *Listening* interoception score was significantly associated with an increased confidence in lies, in the polygraph ($\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%$) and interrogation condition ($\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%$).
+The *Listening* interoception score was significantly associated with an increased confidence in lies, in both the polygraph ($\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%$) and interrogation condition ($\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%$).
 It was also associated with faster answers, particularly for lies ($\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%$) and truths ($\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%$) in the polygraph condition.
@@
 
-The *Focus* interoception score was significantly associated with an increased confidence in truthful responses in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$) and interrogation condition ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%$).
+The *Focus* interoception score was significantly associated with an increased confidence in truthful responses in both the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$) and interrogation condition ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%$).
 No significant association was found with RT or heart rate, but the score correlated with the dispositional lying *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$).
 
-The *Regulation* interoception score was significantly associated with an increased confidence in lies in the polygraph ($\beta=0.32,~95\%~CI~[0.14, 0.51],~pd = 99.99\%$) and the interrogation conditions ($\beta=0.18,~95\%~CI~[0.00, 0.36],~pd = 97.42\%$), and with a decreased confidence in truth only in the polygraph condition ($\beta=-0.1,~95\%~CI~[-0.36, 0.01],~pd = 97.16\%$).
+The *Regulation* interoception score was significantly associated with an increased confidence in lies in both the polygraph ($\beta=0.32,~95\%~CI~[0.14, 0.51],~pd = 99.99\%$) and the interrogation conditions ($\beta=0.18,~95\%~CI~[0.00, 0.36],~pd = 97.42\%$), and with a decreased confidence in truth only in the polygraph condition ($\beta=-0.1,~95\%~CI~[-0.36, 0.01],~pd = 97.16\%$).
 No significant association was found with RT or heart rate (**Figure 2**).
@@
 Specifically, enhancing one's attention towards their internal bodily signals could have resulted in a hyper-vigilance towards physiological sensations that is perceived negatively.
+This is consistent with previous deception detection studies, in which participants' spontaneous lying behaviour only decreased when they were given feedback by a polygraph machine, but not when no feedback was given [@peleg2019lie].
 Additionally, our study also extends past deception research and further confirms the validity concerns in solely relying on physiological measures as an indicator of deception [@rosky2013f; @oviatt2018handbook].
@@
 <!-- TOM -->
-Our results suggest that higher ToM abilities were related to a slower and less confident lies, but only in the polygraph condition.
-One possible interpretation is that people with stronger ToM abilities rely by default more on it when lying (i.e., they focus on - and try to read - the other person).
-When that mechanism is cut off (i.e., when there is no person to lie to - but in our case a "machine"), their lying ability decreases.
+Our results suggest that higher ToM abilities were related to slower and less confident lies, but only in the polygraph condition.
+One possible interpretation of our findings is that people with stronger ToM abilities by default rely more on their social skills and altercentric inference when lying (i.e., they focus on - and try to read - the other person).
+When that mechanism is rendered dispensable (i.e., when there is no person to lie to - but a "machine" in our case), their corresponding lying ability decreases.
+Our result expands current mixed findings relating interoception and ToM [@shah2017heart; @gao2019bodyl; @canino2022embodiment; @miller2015connections].
+Future studies are therein necessary to elucidate the relationship between interoception and theory of mind in different social contexts.
 
@@
 We also showed that interoceptive abilities are correlated with a higher confidence in one's lies in the polygraph condition, a condition in which the attention towards internal reactions is fostered.
-However, in contrast to previous studies [@pinna2020systematic; @fustos2013embodiment; @owens2018investigating; @pollatos2007heart], we did not find any significant relationship between individuals' interoception scores and the heart rate changes during their answers.
+However, in contrast to previous studies [@pinna2020systematic; @fustos2013embodiment; @owens2018investigating; @pollatos2007heart], we did not find any significant relationship between individuals' interoception scores and their heart rate changes during their answers.
 This points toward a predominantly meta-cognitive effect without necessarily an actual bodily regulation (i.e., participants with good interoception feel that their lies are more convincing, but do not actively attenuate their bodily reactions).
@@
 Nonetheless, we believe our results to be credible as we find consistent patterns across various facets and measures (for instance, all interoceptive dimensions, although distinct, share a similar trend) in line with theoretical expectations.
-The statistical power could also explain the overall lack of results with heart rate, which has a higher signal-to-noise ratio as compared to subjective reports (such as confidence scales).
+The statistical power could also explain the overall lack of results found in relation to heart rate, which has a higher signal-to-noise ratio as compared to subjective reports (such as confidence scales).
 
@@
 Although we tried to include more objective measures, such as RT (although it too was tied to the participants' conscious decision to press a key) and heart rate, future studies should attempt at measuring objectively the answer (lie or truth) quality, for instance by means of external examiners.
-Note that this is not limitation *per se*, as it answers a slightly different question - what are the correlates of *objective* lying skills - than deception self-confidence.
+Note that this is not a limitation *per se*, as it answers a slightly different question - what are the correlates of *objective* lying skills - than deception self-confidence.
 <!-- [**look for lit linking to what are commonly considered cues for lying**] -->
 
-Additionally to limitations pertaining to the measure of lying ability, care has to be given to the measure of the predictor constructs, namely ToM and interoception.
-While we tried to include an behavioral task as well as a subjective questionnaire for each, it has to be underlined that they are notoriously difficult concepts to measure.
+Additionally, pertaining to the limitations with regards to the measure of lying ability, care has to be given to the measure of the predictor constructs, namely ToM and interoception.
+While we tried to include a behavioral task as well as a subjective questionnaire for each, it has to be underlined that they are notoriously difficult concepts to measure.
 In particular, objective interoceptive accuracy was assessed using the Heartbeat Counting Task (HCT).
-While the HCT used to be considered as a gold standard and is one of the most commonly used measure [@desmedt2022does], concerns regarding its validity has been highlighted in several studies [@desmedt2018heartbeat; @desmedt2022does; @brener2016towards; @legrand2022heart].
+While the HCT used to be considered as a gold standard and remains one of the most commonly used measures [@desmedt2022does], concerns regarding its validity has been highlighted in several studies [@desmedt2018heartbeat; @desmedt2022does; @brener2016towards; @legrand2022heart].
 Given increasing research efforts invested in the development of novel interoception tasks [@plans2021measuring; @legrand2022heart; @ponzo2021measuring], future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.
@@
 
-In conclusion, this study study is a first step towards assessing the contribution of ToM and interoception abilities in deception in one's ability to lie convincingly.
-We introduced a new paradigm that is able to modulate the contribution of these mechanisms while remaining relevant to applied fields of lie detection and criminology (in which the experimental conditions find echoing practices).
-Our results provide princeps evidence that interoception could be a key - and overlooked - mechanism in deception.
+In conclusion, this study is a first step towards assessing the contribution of ToM and interoception abilities in deception, particularly in one's ability to lie convincingly.
+To this end, we introduced a new paradigm that is able to modulate the contribution of these mechanisms while remaining relevant to applied fields of lie detection and criminology (in which the experimental conditions find echoing practices).
+Notably, our results provide princeps evidence that interoception could be a key - and overlooked - mechanism in deception.
 

### 2023-01-08 paper/manuscript.Rmd
reknit

@@
 keywords: "Deception, Interoception, Theory of Mind, Poygraph"
-wordcount: '3526'
+wordcount: '3629'
 bibliography: ["references.bib"]
@@
 Interestingly, evidence suggests that the successful detection of a lying attempt depends more on the ability of the liar, than on the performance of the lie detector [@verigin2019lie; @bond2008individual; @levine2011sender].
-However, with most of the deception literature focused on deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], the factors contributing to one's ability to successfully lie remain unclear.
+However, with most of the deception literature focused on deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], the factors contributing to one's ability to lie remain unclear.
 
@@
 
-This study was in accordance with the Declaration of Helsinki and was approved by the NTU Institutional Review Board (NTU-IRB-2020-09-007).
+This study was approved by the NTU Institutional Review Board (NTU-IRB-2020-09-007).
 All participants provided their informed consent prior to participation and were awarded with academic credits upon completion of the study.
@@
 
-In the *Interrogation* condition, participants had to provide their answer for each trial after receiving social feedback in the form of a video stream of an examiner, and were informed that the examiner would be evaluating the truthfulness of their responses based on their observations of them through the live video feed.
-In actuality, the displayed video feed was pre-recorded video clips of a confederate's face (staying still with minimal reactions, and wearing a medical mask, as the experiment was administered in the face of COVID restrictions), and the same video-clips were used with all participants.
+In the *Interrogation* condition, participants had to provide their answer each trial while receiving social feedback in the form of a video stream of an examiner, and were informed that the examiner would be evaluating the truthfulness of their responses after observing them through the live video feed.
+In actuality, the displayed video feed was pre-recorded video clips of a confederate's face (staying still with minimal reactions, and with a medical mask, as the experiment was run during COVID restrictions), and the same video-clips were used with all participants.
 Note that after debriefing, all participants reported believing that the stream was real and that the examiner was really there.
 
-In the *Polygraph* condition, participants had to provide their answer for each trial after receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded.
-Specifically, participants were informed that they were being shown live feedback of their own physiological activity.
+In the *Polygraph* condition, participants had to provide their answer answer each trial while receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded.
+Participants were informed that they were being shown live feedback of their own physiological activity.
 In actuality, we displayed pre-recorded video clips of a confederate's physiological signals.
@@
 The deception task was finally run, followed by a debriefing.
-Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of 3.5s).
+Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of 3.5 s).
 
@@
 One possible interpretation of our findings is that people with stronger ToM abilities by default rely more on their social skills and altercentric inference when lying (i.e., they focus on - and try to read - the other person).
-When that mechanism is rendered dispensable (i.e., when there is no person to lie to - but a "machine" in our case), their corresponding lying ability decreases.
-Our result expands current mixed findings relating interoception and ToM [@shah2017heart; @gao2019bodyl; @canino2022embodiment; @miller2015connections].
-Future studies are therein necessary to elucidate the relationship between interoception and theory of mind in different social contexts.
+When that mechanism is unavailable or unsuited (e.g., when there is no person to lie to - but a "machine" in our case), their corresponding lying ability decreases.
+In light of the current field of mixed findings relating interoception and ToM [@shah2017heart; @gao2019bodyl; @canino2022embodiment; @miller2015connections], future studies are necessary to investigate the interaction of these mechanisms in different social contexts.
 

### 2023-01-08 paper/manuscript.tex
reknit

@@
 {}{\PatchFailed}
-\keywords{Deception, Interoception, Theory of Mind, Poygraph\newline\indent Word count: 3526}
+\keywords{Deception, Interoception, Theory of Mind, Poygraph\newline\indent Word count: 3629}
 \usepackage{lineno}
@@
 Interestingly, evidence suggests that the successful detection of a lying attempt depends more on the ability of the liar, than on the performance of the lie detector (Bond Jr \& DePaulo, 2008; Levine et al., 2011; Verigin et al., 2019).
-However, with most of the deception literature focused on deception detection (Masip, 2017; Sternglanz et al., 2019; Viji et al., 2022), the factors contributing to one's deception abilities remain unclear.
+However, with most of the deception literature focused on deception detection (Masip, 2017; Sternglanz et al., 2019; Viji et al., 2022), the factors contributing to one's ability to lie remain unclear.
 
@@
 
-Two measures of ToM and related constructs were administered.
+Two measures of ToM and its related constructs were administered.
 The Yoni Task (Shamay-Tsoory \& Aharon-Peretz, 2007) is a behavioral task in which participants are presented with the face of a character named ``Yoni'', surrounded by 4 colored pictures of objects or faces.
-In total, each participant completed 101 trials - 49 trials assessing their affective TOM abilities, 37 trials assessing their cognitive TOM abilities and 15 control trial.
-During each trial, participants were shown a question and asked to make responses based on specific cues such as directions of eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical TOM).
+In total, each participant completed 101 trials - 49 trials assessing their affective TOM abilities, 37 trials assessing their cognitive TOM abilities and 15 control trials.
+During each trial, participants were shown a question and asked to make responses based on specific cues such as directions of Yoni's eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical TOM).
 
@@
 
-\textbf{TODO: create a procedure figure}
-
 Using PsychoPy (Peirce et al., 2019), we implemented a directed-lying task in which participants were instructed to answer 80 questions by either lying or telling the truth (depending on whether they see ``lie'' or ``truth'' written on the screen).
-Importantly, they were told that for half of the trials, they would have to convince another participant that would be observing them form a separate room via a webcam connection (\emph{Interrogation} condition).
+Importantly, they were told that for half of the trials, they would have to convince another participant that would be observing them from a separate room via a webcam connection (\emph{Interrogation} condition).
 For the remaining trials, participants were tasked to convince a ``lie detection machine'' that would be assessing their behaviour through their physiological signals (\emph{Polygraph} condition).
@@
 Following a short interval (0.7 - 1.5s) for response preparation (during which ``Connecting\ldots{}'' was displayed on the screen), participants were presented with either a social-feedback or biofeedback cue (for the \emph{Interrogation} and \emph{Polygraph} conditions, respectively), displayed for a maximum of 10s.
-After the feedback cue, participants had to provide their answer to the question verbally (out loud) and press the `space' key to mark the end of their response.
+After the feedback cue, participants had to provide their answer to the question (verbally) aloud and press the `space' key to mark the end of their response.
 Following another short interval (1.5 - 2.5s) during which was written ``Disconnecting\ldots{}'' on the screen, participants were asked to rate, using an analog scale, their confidence in how convincing (i.e., likely to get judged as truthful) they perceived their response to be.
 
-In the \emph{Interrogation} condition, participants had to answer each trial while receiving social feedback in the form of a video stream of an examiner, and were informed that the examiner would be evaluating the truthfulness of their responses by observing them through the live video feed.
-In actuality, the video was a pre-recorded video clips of a confederate's face (staying still with minimal reactions, and with a medical mask, as the experiment was run during COVID restrictions), and the same video-clips were used with all participants.
+In the \emph{Interrogation} condition, participants had to provide their answer each trial while receiving social feedback in the form of a video stream of an examiner, and were informed that the examiner would be evaluating the truthfulness of their responses after observing them through the live video feed.
+In actuality, the displayed video feed was pre-recorded video clips of a confederate's face (staying still with minimal reactions, and with a medical mask, as the experiment was run during COVID restrictions), and the same video-clips were used with all participants.
 Note that after debriefing, all participants reported believing that the stream was real and that the examiner was really there.
 
-In the \emph{Polygraph} condition, participants had to answer each trial while receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded.
+In the \emph{Polygraph} condition, participants had to provide their answer answer each trial while receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded.
 Participants were informed that they were being shown live feedback of their own physiological activity.
-In actuality, we displayed pre-recorded video clips of a confederate's signals.
+In actuality, we displayed pre-recorded video clips of a confederate's physiological signals.
 Note that after debriefing, all participants reported believing that it was indeed their own signals being shown.
 
-Finally, on top of the deception task, we also measured the self-reported tendency to lie in their everyday life using the \emph{Lie Scale} (Makowski, Pham, Lau, Raine, et al., 2021), a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency).
+Finally, on top of the deception task, we also measured participants' self-reported tendency to lie in their everyday life using the \emph{Lie Scale} (Makowski, Pham, Lau, Raine, et al., 2021), a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency).
 
@@
 In the first phase of the study, participants answered a brief demographic survey before being administered the questionnaires and cognitive-behavioural tasks in a randomized order.
-Then, the physiological recording devices were set up.
-Cardiac activity (ECG) was recorded with 3 electrodes placed according to a modified Lead II configuration (Takuma et al., 1995), electrodermal activity (EDA) and respiration (using a respiration belt) were also recorded, but not analyzed for the study (unfortunately, most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (22 degrees Celsius) of the experimental room).
+Then, the physiological recording devices were set up as follows: Cardiac activity (ECG) was recorded with 3 electrodes placed according to a modified Lead II configuration (Takuma et al., 1995); electrodermal activity (EDA) and respiration (using a respiration belt) were also recorded, but not analyzed for the study (unfortunately, most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (22 degrees Celsius) of the experimental room).
 All signals were recorded at 1000 Hz via the BioPac MP160 system (BioPac Systems Inc., USA).
 The deception task was finally run, followed by a debriefing.
-Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies \emph{vs.} truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of 3.5 sec).
+Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies \emph{vs.} truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of 3.5 s).
 
@@
 Marginal contrasts analysis (denoted by \(\Delta\)) was also performed to clarify the differences between conditions.
-To allow for a better quantification of the uncertainty associated with the effects, as well as increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework (Makowski et al., 2019), using informative priors centred around 0 (\(t_{Confidence}(1, 0, 1)\), \(t_{RT}(1, 0, 3)\), \(t_{Heartrate}(1, 0, 8)\)).
+To allow for a better quantification of the uncertainty associated with the effects, as well as to increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework (Makowski et al., 2019), using informative priors centred around 0 (\(t_{Confidence}(1, 0, 1)\), \(t_{RT}(1, 0, 3)\), \(t_{Heartrate}(1, 0, 8)\)).
 
@@
 Then, we modelled the relationship between these inter-individual composite scores (note that the analysis for all individual variables is nonetheless included in the analysis report) and the 3 outcome variables in interaction with the condition (polygraph \emph{vs.} interrogation).
-Finally, we investigated the relationship between the deception scale traits, and the theory of mind and interoception scores using Bayesian correlations.
+Finally, we investigated the relationship between the deception scale traits, and the ToM and interoception scores using Bayesian correlations.
 
@@
 
-Compared to truth, lies were rated with less confidence (\(\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%\)), but no difference between the conditions was found.
+Compared to truth, lies were rated with less confidence (\(\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%\)), but no significant difference between the conditions was found.
 On the other hand, the RT did not differ between truth and lies, but was significantly slower in the polygraph condition for both conditions (\(\Delta=0.25,~95\%~CI~[0.62, 0.41],~pd = 100\%\)).
@@
 The 3 YONI-task dimensions and the 2 BES traits were combined into a unique factor, labelled \emph{TOM} (explaining 35.76\% of variance).
-It was loaded by the cognitive (.89), affective (.77), physical (.45) YONI dimension, and the affective (.41) and cognitive (.17) traits of the BES.
+It was loaded by the cognitive (.89), affective (.77), physical (.45) YONI dimensions, and the affective (.41) and cognitive (.17) facets of the BES.
 
@@
 
-The \emph{Listening} interoception score was significantly associated with an increased confidence in lies, in the polygraph (\(\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%\)) and interrogation condition (\(\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%\)).
+The \emph{Listening} interoception score was significantly associated with an increased confidence in lies, in both the polygraph (\(\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%\)) and interrogation condition (\(\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%\)).
 It was also associated with faster answers, particularly for lies (\(\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%\)) and truths (\(\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%\)) in the polygraph condition.
@@
 
-The \emph{Focus} interoception score was significantly associated with an increased confidence in truthful responses in the polygraph (\(\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%\)) and interrogation condition (\(\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%\)).
+The \emph{Focus} interoception score was significantly associated with an increased confidence in truthful responses in both the polygraph (\(\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%\)) and interrogation condition (\(\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%\)).
 No significant association was found with RT or heart rate, but the score correlated with the dispositional lying \emph{Ability} trait (\(r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%\)).
 
-The \emph{Regulation} interoception score was significantly associated with an increased confidence in lies in the polygraph (\(\beta=0.32,~95\%~CI~[0.14, 0.51],~pd = 99.99\%\)) and the interrogation conditions (\(\beta=0.18,~95\%~CI~[0.00, 0.36],~pd = 97.42\%\)), and with a decreased confidence in truth only in the polygraph condition (\(\beta=-0.1,~95\%~CI~[-0.36, 0.01],~pd = 97.16\%\)).
+The \emph{Regulation} interoception score was significantly associated with an increased confidence in lies in both the polygraph (\(\beta=0.32,~95\%~CI~[0.14, 0.51],~pd = 99.99\%\)) and the interrogation conditions (\(\beta=0.18,~95\%~CI~[0.00, 0.36],~pd = 97.42\%\)), and with a decreased confidence in truth only in the polygraph condition (\(\beta=-0.1,~95\%~CI~[-0.36, 0.01],~pd = 97.16\%\)).
 No significant association was found with RT or heart rate (\textbf{Figure 2}).
@@
 Specifically, enhancing one's attention towards their internal bodily signals could have resulted in a hyper-vigilance towards physiological sensations that is perceived negatively.
+This is consistent with previous deception detection studies, in which participants' spontaneous lying behaviour only decreased when they were given feedback by a polygraph machine, but not when no feedback was given (Peleg et al., 2019).
 Additionally, our study also extends past deception research and further confirms the validity concerns in solely relying on physiological measures as an indicator of deception (Oviatt et al., 2018; Rosky, 2013).
 
-Our results suggest that higher ToM abilities were related to a slower and less confident lies, but only in the polygraph condition.
-One possible interpretation is that people with stronger ToM abilities rely by default more on it when lying (i.e., they focus on - and try to read - the other person).
-When that mechanism is cut off (i.e., when there is no person to lie to - but in our case a ``machine''), their lying ability decreases.
+Our results suggest that higher ToM abilities were related to slower and less confident lies, but only in the polygraph condition.
+One possible interpretation of our findings is that people with stronger ToM abilities by default rely more on their social skills and altercentric inference when lying (i.e., they focus on - and try to read - the other person).
+When that mechanism is unavailable or unsuited (e.g., when there is no person to lie to - but a ``machine'' in our case), their corresponding lying ability decreases.
+In light of the current field of mixed findings relating interoception and ToM (Canino et al., 2022; Miller, 2015; Shah et al., 2017; \textbf{gao2019bodyl?}), future studies are necessary to investigate the interaction of these mechanisms in different social contexts.
 
 We also showed that interoceptive abilities are correlated with a higher confidence in one's lies in the polygraph condition, a condition in which the attention towards internal reactions is fostered.
-However, in contrast to previous studies (Füstös et al., 2013; Owens et al., 2018; Pinna \& Edwards, 2020; Pollatos et al., 2007), we did not find any significant relationship between individuals' interoception scores and the heart rate changes during their answers.
+However, in contrast to previous studies (Füstös et al., 2013; Owens et al., 2018; Pinna \& Edwards, 2020; Pollatos et al., 2007), we did not find any significant relationship between individuals' interoception scores and their heart rate changes during their answers.
 This points toward a predominantly meta-cognitive effect without necessarily an actual bodily regulation (i.e., participants with good interoception feel that their lies are more convincing, but do not actively attenuate their bodily reactions).
@@
 Although we tried to include more objective measures, such as RT (although it too was tied to the participants' conscious decision to press a key) and heart rate, future studies should attempt at measuring objectively the answer (lie or truth) quality, for instance by means of external examiners.
-Note that this is not limitation \emph{per se}, as it answers a slightly different question - what are the correlates of \emph{objective} lying skills - than deception self-confidence.
+Note that this is not a limitation \emph{per se}, as it answers a slightly different question - what are the correlates of \emph{objective} lying skills - than deception self-confidence.
 
-Additionally to limitations pertaining to the measure of lying ability, care has to be given to the measure of the predictor constructs, namely ToM and interoception.
-While we tried to include an behavioral task as well as a subjective questionnaire for each, it has to be underlined that they are notoriously difficult concepts to measure.
+Additionally, pertaining to the limitations with regards to the measure of lying ability, care has to be given to the measure of the predictor constructs, namely ToM and interoception.
+While we tried to include a behavioral task as well as a subjective questionnaire for each, it has to be underlined that they are notoriously difficult concepts to measure.
 In particular, objective interoceptive accuracy was assessed using the Heartbeat Counting Task (HCT).
-While the HCT used to be considered as a gold standard and is one of the most commonly used measure (Desmedt et al., 2022), concerns regarding its validity has been highlighted in several studies (Brener \& Ring, 2016; Desmedt et al., 2018, 2022; Legrand et al., 2022).
+While the HCT used to be considered as a gold standard and remains one of the most commonly used measures (Desmedt et al., 2022), concerns regarding its validity has been highlighted in several studies (Brener \& Ring, 2016; Desmedt et al., 2018, 2022; Legrand et al., 2022).
 Given increasing research efforts invested in the development of novel interoception tasks (Legrand et al., 2022; Plans et al., 2021; Ponzo et al., 2021), future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.
@@
 Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
+
+\leavevmode\vadjust pre{\hypertarget{ref-canino2022embodiment}{}}%
+Canino, S., Raimo, S., Boccia, M., Di Vita, A., \& Palermo, L.
+(2022).
+On the embodiment of social cognition skills: The inner and outer body processing differently contributes to the affective and cognitive theory of mind.
+\emph{Brain Sciences}, \emph{12}(11), 1423.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-miller2015connections}{}}%
+Miller, J. E. (2015). \emph{The connections between self-monitoring and theory of mind}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-murphy2019classifying}{}}%
@@
 \emph{Behavior Research Methods}, \emph{51}(1), 195--203.
+
+\leavevmode\vadjust pre{\hypertarget{ref-peleg2019lie}{}}%
+Peleg, D., Ayal, S., Ariely, D., \& Hochman, G. (2019). The lie deflator-the effect of polygraph test feedback on subsequent (dis) honesty. \emph{Judgment \& Decision Making}, \emph{16}(6).
 
@@
 Seth, A. K., Suzuki, K., \& Critchley, H. D. (2012). An interoceptive predictive coding model of conscious presence. \emph{Frontiers in Psychology}, \emph{2}, 395.
+
+\leavevmode\vadjust pre{\hypertarget{ref-shah2017heart}{}}%
+Shah, P., Catmur, C., \& Bird, G.
+(2017).
+From heart to mind: Linking interoception, emotion, and theory of mind.
+\emph{Cortex; a Journal Devoted to the Study of the Nervous System and Behavior}, \emph{93}, 220.
 

### 2023-01-23 paper/manuscript.Rmd
edit manu method and procedures

@@
 The sequence of each trial was the same for both conditions.
-A question was shown on a computer screen, either phrased directly (e.g., "What is your favourite sport?"), or indirectly (e.g., "Is your favourite sport Hockey?"), with accompanying instructions below that either asked participants to verbally lie or tell the truth (half of the trials in each condition, i.e., n = 20, were directed lies).
-Following a short interval (0.7 - 1.5s) for response preparation (during which "Connecting..." was displayed on the screen), participants were presented with either a social-feedback or biofeedback cue (for the *Interrogation* and *Polygraph* conditions, respectively), displayed for a maximum of 10s.
-After the feedback cue, participants had to provide their answer to the question (verbally) aloud and press the 'space' key to mark the end of their response.
-Following another short interval (1.5 - 2.5s) during which was written "Disconnecting..." on the screen, participants were asked to rate, using an analog scale, their confidence in how convincing (i.e., likely to get judged as truthful) they perceived their response to be.
+Participants were instructed to respond to a question shown on a computer screen, phrased either directly (e.g., "What is your favourite sport?"), or indirectly (e.g., "Is your favourite sport Hockey?"), by verbally lying or telling the truth (for half of the trials in each condition, i.e., n = 20).
+Following a short interval (0.7 - 1.5s) for response preparation, during which "Connecting..." was shown on the screen, a social or bio-feedback cue (for *Interrogation* and *Polygraph* conditions respectively) was displayed for a maximum of 10s.
+Participants then had to provide their answers verbally, and pressed the space key to signify the end of their response.
+After another short interval (1.5-2.5s), during which "Disconnecting" was written on the screen, participants were asked to rate their confidence in how convincing (i.e., likely to get judged as truthful) they perceived their response to be on a visual analog scale.
 
-In the *Interrogation* condition, participants had to provide their answer each trial while receiving social feedback in the form of a video stream of an examiner, and were informed that the examiner would be evaluating the truthfulness of their responses after observing them through the live video feed.
-In actuality, the displayed video feed was pre-recorded video clips of a confederate's face (staying still with minimal reactions, and with a medical mask, as the experiment was run during COVID restrictions), and the same video-clips were used with all participants.
-Note that after debriefing, all participants reported believing that the stream was real and that the examiner was really there.
+In the *Interrogation* condition, participants had to provide their answer while receiving social feedback in the form of a video stream of an examiner, and were informed that the examiner would be evaluating the truthfulness of their responses after observing them through the live video feed.
+In actuality, the displayed video feed were pre-recorded video clips of a confederate's face (staying still with minimal reactions, and with a medical mask, as the experiment was run during COVID restrictions), and the same video-clips were used with all participants.
+All participants reported believing that the stream was real and that the examiner was really there during the debriefing.
 
-In the *Polygraph* condition, participants had to provide their answer answer each trial while receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded.
+In the *Polygraph* condition, participants had to provide their answer while receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded.
 Participants were informed that they were being shown live feedback of their own physiological activity.
 In actuality, we displayed pre-recorded video clips of a confederate's physiological signals.
-Note that after debriefing, all participants reported believing that it was indeed their own signals being shown.
+All participants reported believing that it was indeed their own signals being shown during the debriefing.
 
@@
 
-In the first phase of the study, participants answered a brief demographic survey before being administered the questionnaires and cognitive-behavioural tasks in a randomized order.
-Then, the physiological recording devices were set up as follows: Cardiac activity (ECG) was recorded with 3 electrodes placed according to a modified Lead II configuration [@takuma1995alternative]; electrodermal activity (EDA) and respiration (using a respiration belt) were also recorded, but not analyzed for the study (unfortunately, most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (22 degrees Celsius) of the experimental room).
-All signals were recorded at 1000 Hz via the BioPac MP160 system (BioPac Systems Inc., USA).
-The deception task was finally run, followed by a debriefing.
+This study is comprised of 2 sessions.
+During session 1, participants answered a brief demographic survey before the questionnaires, which were presented in a randomized order.
+During session 2, cognitive-behavioural tasks were administered to participants while their physiological signals (including cardiac activity (ECG), respiration (RSP) and electrodermal activity (EDA)) were being recorded.
+The physiological recording devices were set up as follows: ECG was recorded with 3 electrodes placed according to a modified Lead II configuration [@takuma1995alternative], and respiration was measured using a respiration belt.
+All signals were recorded at 1000Hz via the BioPac MP160 system (BioPac Systems Inc., USA).
+For all participants, session 2 began with the deception task, followed by the YONI task and the HCT, with the latter two presented in a randomized order.
 Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of 3.5 s).
@@
 ## Data Analysis
+
+EDA was not further analyzed for the study because most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (22 degrees Celsius) of the experimental room.
 

### 2023-04-22 paper/manuscript.Rmd
rephrase

@@
   - name          : "Dominique Makowski"
-    affiliation   : "1"
+    affiliation   : "1, 2"
     corresponding : yes    # Define only one corresponding author
-    address       : "HSS 04-18, 48 Nanyang Avenue, Singapore"
-    email         : "dom.makowski@gmail.com"
+    address       : "Pevensey 1, University of Sussex, Brighton, UK"
+    email         : "D.Makowski@sussex.ac.uk"
     orcid         : 0000-0001-5375-9967
@@
   - name          : "Zen J. Lau"
-    affiliation   : " 1"
+    affiliation   : " 2"
   - name          : "Tam Pham"
-    affiliation   : " 1"
+    affiliation   : " 2"
   - name          : "An Shu Te"
-    affiliation   : "1"
+    affiliation   : "2"
     orcid         : 0000-0001-8008-2824
@@
   - name          : "Stephanie Kirk"
-    affiliation   : "1"
+    affiliation   : "2"
     orcid         : 0000-0002-9312-5552
@@
   - name          : "Claudia Liauw"
-    affiliation   : "1"
+    affiliation   : "2"
     role:
@@
   - name          : "S.H. Annabel Chen"
-    affiliation   : "1, 2, 3, 4"
+    affiliation   : "2, 3, 4, 5"
     orcid         : 0000-0002-1540-5516
@@
   - id            : "1"
+    institution   : "School of Psychology, University of Sussex, UK"
+  - id            : "2"
     institution   : "School of Social Sciences, Nanyang Technological University, Singapore"
-  - id            : "2"
+  - id            : "3"
     institution   : "Centre for Research and Development in Learning, Nanyang Technological University, Singapore"
-  - id            : "3"
+  - id            : "4"
     institution   : "Lee Kong Chian School of Medicine, Nanyang Technological University, Singapore"
-  - id            : "4"
+  - id            : "5"
     institution   : "National Institute of Education, Nanyang Technological University, Singapore"
@@
     keep_tex: yes
-keywords: "Deception, Interoception, Theory of Mind, Poygraph"
-wordcount: '3629'
+keywords: "Deception, Interoception, Theory of Mind, Poygraph, Lying Ability"
+wordcount: '3720'
 bibliography: ["references.bib"]
@@
 
-EDA was not further analyzed for the study because most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (22 degrees Celsius) of the experimental room.
+Aware of the low number of participants, we tried to take every steps to 1) maximize power by using all available data (from individual trials) with appropriate statistical tools and 2) ensure the robustness of results by cross-validating the findings accross different measures and approaches.
 
-To ensure that our outcome variables were sensitive to the experimental manipulations, we first tested the effect of the question phrasing (direct *vs.* indirect) and condition (polygraph *vs.* interrogation) on the outcome variables.
+Firstly, a manipulation check was carried out to ensure that our outcome variables were sensitive to the experimental manipulations, by testing the effect of the question phrasing (direct *vs.* indirect) and condition (polygraph *vs.* interrogation) on the outcome variables.
 This analysis was performed using mixed models with the participants and questions both entered as random factors.
 Marginal contrasts analysis (denoted by $\Delta$) was also performed to clarify the differences between conditions.
-To allow for a better quantification of the uncertainty associated with the effects, as well as to increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework [@makowski2019bayestestr], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).
+To allow for a better quantification of the uncertainty associated with the effects, as well as to increase the robustness to outliers and artefactual findings, all statistics were undertaken under the Bayesian framework [@makowski2019bayestestr], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).
 
-To further counterbalance the low number of participants and maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, ToM and interoception) using factor analysis over PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained.
+To maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, ToM and interoception) using factor analysis over PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained.
 Then, we modelled the relationship between these inter-individual composite scores (note that the analysis for all individual variables is nonetheless included in the analysis report) and the 3 outcome variables in interaction with the condition (polygraph *vs.* interrogation).
 Finally, we investigated the relationship between the deception scale traits, and the ToM and interoception scores using Bayesian correlations.
+As all the analyses and data has been made available, we will in the manuscript focus on significant, i.e., - in this context - statistically reliable and in our opinion theoretically relevant.
 
 The data analysis was carried out using *R 4.2* [@RCoreTeam2022], *brms* [@Burkner2017], and the *easystats* collection of packages [@makowski2019bayestestr; @correlationArticle; @performanceArticle; @insightArticle], and the physiological signal processing was done using the default routines avaialble in *NeuroKit2* [@makowski2021neurokit2].
-As the full reproducible analysis script and statistical results report are available at
+Note that EDA was not further analyzed as most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (with dry air-con air) of the experimental room.
+
+The analysis was not pre-registered (stemming out from a student's project), but the full reproducible analysis script, statistical results report, and data, are available at 
 https://github.com/DominiqueMakowski/DeceptionInteroTom
-, we will only focus on significant results in the manuscript.
 
@@
 When that mechanism is unavailable or unsuited (e.g., when there is no person to lie to - but a "machine" in our case), their corresponding lying ability decreases.
-In light of the current field of mixed findings relating interoception and ToM [@shah2017heart; @gao2019bodyl; @canino2022embodiment; @miller2015connections], future studies are necessary to investigate the interaction of these mechanisms in different social contexts.
+In light of the current field of mixed findings relating interoception and ToM [@shah2017heart; @gao2019body; @canino2022embodiment; @miller2015connections], future studies are necessary to investigate the interaction of these mechanisms in different social contexts.
 
@@
 
-The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) for this research is available at **https://github.com/DominiqueMakowski/DeceptionInteroTom**.
+The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, etc.) for this research is available at **https://github.com/DominiqueMakowski/DeceptionInteroTom**.
 
@@
 
-We would like to thank Jia Rong Low and Maximilian Yong for his help in data collection.
+We would like to thank Jia Rong Low and Maximilian Yong for their help in data collection.
 

### 2023-04-22 paper/manuscript.tex
rephrase

@@
 {}{\PatchFailed}
-\keywords{Deception, Interoception, Theory of Mind, Poygraph\newline\indent Word count: 3629}
+\keywords{Deception, Interoception, Theory of Mind, Poygraph, Lying Ability\newline\indent Word count: 3720}
 \usepackage{lineno}
@@
   pdftitle={The Heart can Lie: The Role of Interoception and Theory of Mind in Deception},
-  pdfauthor={Dominique Makowski1, Zen J. Lau1, Tam Pham1, An Shu Te1, Stephanie Kirk1, Claudia Liauw1, \& S.H. Annabel Chen1, 2, 3, 4},
+  pdfauthor={Dominique Makowski1, 2, Zen J. Lau2, Tam Pham2, An Shu Te2, Stephanie Kirk2, Claudia Liauw2, \& S.H. Annabel Chen2, 3, 4, 5},
   pdflang={en-EN},
-  pdfkeywords={Deception, Interoception, Theory of Mind, Poygraph},
+  pdfkeywords={Deception, Interoception, Theory of Mind, Poygraph, Lying Ability},
   hidelinks,
@@
 \title{\textbf{The Heart can Lie: The Role of Interoception and Theory of Mind in Deception}}
-\author{Dominique Makowski\textsuperscript{1}, Zen J.
-Lau\textsuperscript{1}, Tam Pham\textsuperscript{1}, An Shu Te\textsuperscript{1}, Stephanie Kirk\textsuperscript{1}, Claudia Liauw\textsuperscript{1}, \& S.H.
-Annabel Chen\textsuperscript{1, 2, 3, 4}}
+\author{Dominique Makowski\textsuperscript{1, 2}, Zen J.
+Lau\textsuperscript{2}, Tam Pham\textsuperscript{2}, An Shu Te\textsuperscript{2}, Stephanie Kirk\textsuperscript{2}, Claudia Liauw\textsuperscript{2}, \& S.H.
+Annabel Chen\textsuperscript{2, 3, 4, 5}}
 \date{}
@@
 
-Correspondence concerning this article should be addressed to Dominique Makowski, HSS 04-18, 48 Nanyang Avenue, Singapore.
-E-mail: \href{mailto:dom.makowski@gmail.com}{\nolinkurl{dom.makowski@gmail.com}}
+Correspondence concerning this article should be addressed to Dominique Makowski, Pevensey 1, University of Sussex, Brighton, UK.
+E-mail: \href{mailto:D.Makowski@sussex.ac.uk}{\nolinkurl{D.Makowski@sussex.ac.uk}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Social Sciences, Nanyang Technological University, Singapore\\\textsuperscript{2} Centre for Research and Development in Learning, Nanyang Technological University, Singapore\\\textsuperscript{3} Lee Kong Chian School of Medicine, Nanyang Technological University, Singapore\\\textsuperscript{4} National Institute of Education, Nanyang Technological University, Singapore}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Psychology, University of Sussex, UK\\\textsuperscript{2} School of Social Sciences, Nanyang Technological University, Singapore\\\textsuperscript{3} Centre for Research and Development in Learning, Nanyang Technological University, Singapore\\\textsuperscript{4} Lee Kong Chian School of Medicine, Nanyang Technological University, Singapore\\\textsuperscript{5} National Institute of Education, Nanyang Technological University, Singapore}
 
@@
 The sequence of each trial was the same for both conditions.
-A question was shown on a computer screen, either phrased directly (e.g., ``What is your favourite sport?''), or indirectly (e.g., ``Is your favourite sport Hockey?''), with accompanying instructions below that either asked participants to verbally lie or tell the truth (half of the trials in each condition, i.e., n = 20, were directed lies).
-Following a short interval (0.7 - 1.5s) for response preparation (during which ``Connecting\ldots{}'' was displayed on the screen), participants were presented with either a social-feedback or biofeedback cue (for the \emph{Interrogation} and \emph{Polygraph} conditions, respectively), displayed for a maximum of 10s.
-After the feedback cue, participants had to provide their answer to the question (verbally) aloud and press the `space' key to mark the end of their response.
-Following another short interval (1.5 - 2.5s) during which was written ``Disconnecting\ldots{}'' on the screen, participants were asked to rate, using an analog scale, their confidence in how convincing (i.e., likely to get judged as truthful) they perceived their response to be.
+Participants were instructed to respond to a question shown on a computer screen, phrased either directly (e.g., ``What is your favourite sport?''), or indirectly (e.g., ``Is your favourite sport Hockey?''), by verbally lying or telling the truth (for half of the trials in each condition, i.e., n = 20).
+Following a short interval (0.7 - 1.5s) for response preparation, during which ``Connecting\ldots{}'' was shown on the screen, a social or bio-feedback cue (for \emph{Interrogation} and \emph{Polygraph} conditions respectively) was displayed for a maximum of 10s.
+Participants then had to provide their answers verbally, and pressed the space key to signify the end of their response.
+After another short interval (1.5-2.5s), during which ``Disconnecting'' was written on the screen, participants were asked to rate their confidence in how convincing (i.e., likely to get judged as truthful) they perceived their response to be on a visual analog scale.
 
-In the \emph{Interrogation} condition, participants had to provide their answer each trial while receiving social feedback in the form of a video stream of an examiner, and were informed that the examiner would be evaluating the truthfulness of their responses after observing them through the live video feed.
-In actuality, the displayed video feed was pre-recorded video clips of a confederate's face (staying still with minimal reactions, and with a medical mask, as the experiment was run during COVID restrictions), and the same video-clips were used with all participants.
-Note that after debriefing, all participants reported believing that the stream was real and that the examiner was really there.
+In the \emph{Interrogation} condition, participants had to provide their answer while receiving social feedback in the form of a video stream of an examiner, and were informed that the examiner would be evaluating the truthfulness of their responses after observing them through the live video feed.
+In actuality, the displayed video feed were pre-recorded video clips of a confederate's face (staying still with minimal reactions, and with a medical mask, as the experiment was run during COVID restrictions), and the same video-clips were used with all participants.
+All participants reported believing that the stream was real and that the examiner was really there during the debriefing.
 
-In the \emph{Polygraph} condition, participants had to provide their answer answer each trial while receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded.
+In the \emph{Polygraph} condition, participants had to provide their answer while receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded.
 Participants were informed that they were being shown live feedback of their own physiological activity.
 In actuality, we displayed pre-recorded video clips of a confederate's physiological signals.
-Note that after debriefing, all participants reported believing that it was indeed their own signals being shown.
+All participants reported believing that it was indeed their own signals being shown during the debriefing.
 
@@
 
-In the first phase of the study, participants answered a brief demographic survey before being administered the questionnaires and cognitive-behavioural tasks in a randomized order.
-Then, the physiological recording devices were set up as follows: Cardiac activity (ECG) was recorded with 3 electrodes placed according to a modified Lead II configuration (Takuma et al., 1995); electrodermal activity (EDA) and respiration (using a respiration belt) were also recorded, but not analyzed for the study (unfortunately, most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (22 degrees Celsius) of the experimental room).
-All signals were recorded at 1000 Hz via the BioPac MP160 system (BioPac Systems Inc., USA).
-The deception task was finally run, followed by a debriefing.
+This study is comprised of 2 sessions.
+During session 1, participants answered a brief demographic survey before the questionnaires, which were presented in a randomized order.
+During session 2, cognitive-behavioural tasks were administered to participants while their physiological signals (including cardiac activity (ECG), respiration (RSP) and electrodermal activity (EDA)) were being recorded.
+The physiological recording devices were set up as follows: ECG was recorded with 3 electrodes placed according to a modified Lead II configuration (Takuma et al., 1995), and respiration was measured using a respiration belt.
+All signals were recorded at 1000Hz via the BioPac MP160 system (BioPac Systems Inc., USA).
+For all participants, session 2 began with the deception task, followed by the YONI task and the HCT, with the latter two presented in a randomized order.
 Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies \emph{vs.} truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of 3.5 s).
@@
 
-To ensure that our outcome variables were sensitive to the experimental manipulations, we first tested the effect of the question phrasing (direct \emph{vs.} indirect) and condition (polygraph \emph{vs.} interrogation) on the outcome variables.
+Aware of the low number of participants, we tried to take every steps to 1) maximize power by using all available data (from individual trials) with appropriate statistical tools and 2) ensure the robustness of results by cross-validating the findings accross different measures and approaches.
+
+Firstly, a manipulation check was carried out to ensure that our outcome variables were sensitive to the experimental manipulations, by testing the effect of the question phrasing (direct \emph{vs.} indirect) and condition (polygraph \emph{vs.} interrogation) on the outcome variables.
 This analysis was performed using mixed models with the participants and questions both entered as random factors.
 Marginal contrasts analysis (denoted by \(\Delta\)) was also performed to clarify the differences between conditions.
-To allow for a better quantification of the uncertainty associated with the effects, as well as to increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework (Makowski et al., 2019), using informative priors centred around 0 (\(t_{Confidence}(1, 0, 1)\), \(t_{RT}(1, 0, 3)\), \(t_{Heartrate}(1, 0, 8)\)).
+To allow for a better quantification of the uncertainty associated with the effects, as well as to increase the robustness to outliers and artefactual findings, all statistics were undertaken under the Bayesian framework (Makowski et al., 2019), using informative priors centred around 0 (\(t_{Confidence}(1, 0, 1)\), \(t_{RT}(1, 0, 3)\), \(t_{Heartrate}(1, 0, 8)\)).
 
-To further counterbalance the low number of participants and maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, ToM and interoception) using factor analysis over PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained.
+To maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, ToM and interoception) using factor analysis over PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained.
 Then, we modelled the relationship between these inter-individual composite scores (note that the analysis for all individual variables is nonetheless included in the analysis report) and the 3 outcome variables in interaction with the condition (polygraph \emph{vs.} interrogation).
 Finally, we investigated the relationship between the deception scale traits, and the ToM and interoception scores using Bayesian correlations.
+As all the analyses and data has been made available, we will in the manuscript focus on significant, i.e., - in this context - statistically reliable and in our opinion theoretically relevant.
 
 The data analysis was carried out using \emph{R 4.2} (R Core Team, 2022), \emph{brms} (Bürkner, 2017), and the \emph{easystats} collection of packages (Lüdecke et al., 2021, 2019; Makowski et al., 2020, 2019), and the physiological signal processing was done using the default routines avaialble in \emph{NeuroKit2} (Makowski, Pham, Lau, Brammer, et al., 2021).
-As the full reproducible analysis script and statistical results report are available at
+Note that EDA was not further analyzed as most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (with dry air-con air) of the experimental room.
+
+The analysis was not pre-registered (stemming out from a student's project), but the full reproducible analysis script, statistical results report, and data, are available at
 \url{https://github.com/DominiqueMakowski/DeceptionInteroTom}
-, we will only focus on significant results in the manuscript.
 
@@
 When that mechanism is unavailable or unsuited (e.g., when there is no person to lie to - but a ``machine'' in our case), their corresponding lying ability decreases.
-In light of the current field of mixed findings relating interoception and ToM (Canino et al., 2022; Miller, 2015; Shah et al., 2017; \textbf{gao2019bodyl?}), future studies are necessary to investigate the interaction of these mechanisms in different social contexts.
+In light of the current field of mixed findings relating interoception and ToM (Canino et al., 2022; Gao et al., 2019; Miller, 2015; Shah et al., 2017), future studies are necessary to investigate the interaction of these mechanisms in different social contexts.
 
@@
 
-The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) for this research is available at \textbf{\url{https://github.com/DominiqueMakowski/DeceptionInteroTom}}.
+The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, etc.) for this research is available at \textbf{\url{https://github.com/DominiqueMakowski/DeceptionInteroTom}}.
 
@@
 \emph{British Journal of Developmental Psychology}, \emph{38}(2), 151--166.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gao2019body}{}}%
+Gao, Q., Ping, X., \& Chen, W. (2019). Body influences on social cognition through interoception. \emph{Frontiers in Psychology}, \emph{10}, 2066.
 

### 2023-04-22 index.Rmd
more

@@
   geom_text(data=data.frame(ToM = -0.3, Predicted = 0.45, Condition = "Polygraph", Answer = "Lie"),
-            label = "***",
+            label = format_pd(0.9767, stars_only = TRUE),
             color = "#FF5722",
@@
   geom_text(data=data.frame(Intero_Meta = -0.15, Predicted = 0.25, Condition = "Polygraph", Answer = "Lie"),
-            label = "***",
+            label = format_pd(0.9898, stars_only = TRUE),
             color = "#FF5722",
@@
   geom_text(data=data.frame(Intero_Listening = 0.2, Predicted = 0.45, Condition = "Polygraph", Answer = "Lie"),
-            label = "***",
+            label = format_pd(1, stars_only = TRUE),
             color = "#FF5722",
+            size = 10, show.legend = FALSE, fontface = "bold") +
+  geom_text(data=data.frame(Intero_Listening = 0.2, Predicted = 0.27, Condition = "Polygraph", Answer = "Lie"),
+            label = format_pd(0.9804, stars_only = TRUE),
+            color = "#2196F3",
             size = 10, show.legend = FALSE, fontface = "bold") +
@@
                             Answer = c("Truth", "Truth")),
-            label = c("*", "*"),
+            label = format_pd(c(0.9716, 0.9576), stars_only = TRUE),
             color = c("#2196F3", "#FF5722"),
@@
                             Answer = c("Lie", "Lie", "Truth")),
-            label = c("***", "*", "*"),
+            label = format_pd(c(0.9999, 0.9742, 0.9716), stars_only = TRUE),
             color = c("#FF5722", "#2196F3", "#FF5722"),

### 2023-04-22 paper/manuscript.Rmd
more

@@
 ```{r message=FALSE, warning=FALSE, out.width="100%", fig.cap="Interindividual corrrelates of lying confidence.
-Shows the correlation between the participants' interoceptive and theory of mind composite scores and their average lying confidence, withing the two experimental conditions."}
+The lines shows the relationship (with 95% CI uncertainty), assessed via Bayesian mixed models (**pd > 97%, **pd > 99%, ***pd > 99.9%), between the participants' interoceptive and theory of mind composite scores and the confidence ratings of their lies and truthful asnwers.
+Their average lying confidence (+/- 1 SD), withing the two experimental conditions, is displayed as points for descriptive purposes (as the models were ran on individual trials)."}
 knitr::include_graphics("../figures/figure1.png")
@@
 
-```{r message=FALSE, warning=FALSE, out.width="100%", fig.cap="Summary of findings showing the positive (green) and negative (red) associations between interoception and theory of mind abilities and deception skills, depending on the experimental condition."}
+```{r message=FALSE, warning=FALSE, out.width="100%", fig.cap="Summary of findings showing the positive (green) and negative (red) associations between interoception and theory of mind abilities and deception skills, depending on the experimental condition.
+It highlights that ToM was related to less confident and slower lies in the polygraph condition, and that specific interoceptive dimensions were related to more confident lies."}
 knitr::include_graphics("../figures/figure2.png")

### 2023-04-22 paper/manuscript.tex
more

@@
 
-\begin{figure}
-\includegraphics[width=1\linewidth]{../figures/figure1} \caption{Interindividual corrrelates of lying confidence.
-Shows the correlation between the participants' interoceptive and theory of mind composite scores and their average lying confidence, withing the two experimental conditions.}\label{fig:unnamed-chunk-1}
-\end{figure}
+\textbackslash begin\{figure\}
+\includegraphics[width=1\linewidth]{../figures/figure1} \textbackslash caption\{Interindividual corrrelates of lying confidence.
+The lines shows the relationship (with 95\% CI uncertainty), assessed via Bayesian mixed models (\textbf{pd \textgreater{} 97\%, }pd \textgreater{} 99\%, ***pd \textgreater{} 99.9\%), between the participants' interoceptive and theory of mind composite scores and the confidence ratings of their lies and truthful asnwers.
+Their average lying confidence (+/- 1 SD), withing the two experimental conditions, is displayed as points for descriptive purposes (as the models were ran on individual trials).\}\label{fig:unnamed-chunk-1}
+\textbackslash end\{figure\}
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{../figures/figure2} \caption{Summary of findings showing the positive (green) and negative (red) associations between interoception and theory of mind abilities and deception skills, depending on the experimental condition.}\label{fig:unnamed-chunk-2}
+\includegraphics[width=1\linewidth]{../figures/figure2} \caption{Summary of findings showing the positive (green) and negative (red) associations between interoception and theory of mind abilities and deception skills, depending on the experimental condition.
+It highlights that ToM was related to less confident and slower lies in the polygraph condition, and that specific interoceptive dimensions were related to more confident lies.}\label{fig:unnamed-chunk-2}
 \end{figure}

### 2023-04-23 paper/manuscript.Rmd
fix fig caption

@@
 ```{r message=FALSE, warning=FALSE, out.width="100%", fig.cap="Interindividual corrrelates of lying confidence.
-The lines shows the relationship (with 95% CI uncertainty), assessed via Bayesian mixed models (**pd > 97%, **pd > 99%, ***pd > 99.9%), between the participants' interoceptive and theory of mind composite scores and the confidence ratings of their lies and truthful asnwers.
-Their average lying confidence (+/- 1 SD), withing the two experimental conditions, is displayed as points for descriptive purposes (as the models were ran on individual trials)."}
+The lines shows the relationship (with 95\\% CI uncertainty), assessed via Bayesian mixed models (\\***pd > 97\\%, \\***pd > 99\\%, \\****pd > 99.9\\%), between the participants' interoceptive and TOM composite scores and the confidence ratings of their responses.
+Average lying confidence (+/- 1 SD) within the two experimental conditions is displayed as points for descriptive purposes as the models were ran on individual trials."}
 knitr::include_graphics("../figures/figure1.png")

### 2023-04-23 paper/manuscript.tex
fix fig caption

@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={The Heart can Lie: The Role of Interoception and Theory of Mind in Deception},
+  pdfauthor={Dominique Makowski1, 2, Zen J. Lau2, Tam Pham2, An Shu Te2, Stephanie Kirk2, Claudia Liauw2, \& S.H. Annabel Chen2, 3, 4, 5},
+  pdflang={en-EN},
+  pdfkeywords={Deception, Interoception, Theory of Mind, Poygraph, Lying Ability},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={The Heart can Lie: The Role of Interoception and Theory of Mind in Deception},
-  pdfauthor={Dominique Makowski1, 2, Zen J. Lau2, Tam Pham2, An Shu Te2, Stephanie Kirk2, Claudia Liauw2, \& S.H. Annabel Chen2, 3, 4, 5},
-  pdflang={en-EN},
-  pdfkeywords={Deception, Interoception, Theory of Mind, Poygraph, Lying Ability},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
@@
 
-\textbackslash begin\{figure\}
-\includegraphics[width=1\linewidth]{../figures/figure1} \textbackslash caption\{Interindividual corrrelates of lying confidence.
-The lines shows the relationship (with 95\% CI uncertainty), assessed via Bayesian mixed models (\textbf{pd \textgreater{} 97\%, }pd \textgreater{} 99\%, ***pd \textgreater{} 99.9\%), between the participants' interoceptive and theory of mind composite scores and the confidence ratings of their lies and truthful asnwers.
-Their average lying confidence (+/- 1 SD), withing the two experimental conditions, is displayed as points for descriptive purposes (as the models were ran on individual trials).\}\label{fig:unnamed-chunk-1}
-\textbackslash end\{figure\}
+\begin{figure}
+\includegraphics[width=1\linewidth]{../figures/figure1} \caption{Interindividual corrrelates of lying confidence.
+The lines shows the relationship (with 95\% CI uncertainty), assessed via Bayesian mixed models (\***pd > 97\%, \***pd > 99\%, \****pd > 99.9\%), between the participants' interoceptive and TOM composite scores and the confidence ratings of their responses.
+Average lying confidence (+/- 1 SD) within the two experimental conditions is displayed as points for descriptive purposes as the models were ran on individual trials.}\label{fig:unnamed-chunk-1}
+\end{figure}
 
@@
 W., Nielsen, L., Hillaire-Clarke, C.
-S., Spruance, V., et al.
+S., Spruance, V.others.
 (2021).
@@
 \leavevmode\vadjust pre{\hypertarget{ref-yoris2015roles}{}}%
-Yoris, A., Esteves, S., Couto, B., Melloni, M., Kichic, R., Cetkovich, M., Favaloro, R., Moser, J., Manes, F., Ibanez, A., et al.
+Yoris, A., Esteves, S., Couto, B., Melloni, M., Kichic, R., Cetkovich, M., Favaloro, R., Moser, J., Manes, F., Ibanez, A.others.
 (2015).

### 2023-04-23 paper/manuscript.Rmd
minor fig and readme

@@
 ```{r message=FALSE, warning=FALSE, out.width="100%", fig.cap="Interindividual corrrelates of lying confidence.
-The lines shows the relationship (with 95\\% CI uncertainty), assessed via Bayesian mixed models (\\***pd > 97\\%, \\***pd > 99\\%, \\****pd > 99.9\\%), between the participants' interoceptive and TOM composite scores and the confidence ratings of their responses.
+The lines shows the relationship (with 95\\% CI uncertainty), assessed via Bayesian mixed models (\\***pd > 97\\%, \\***pd > 99\\%, \\****pd > 99.9\\%), between the participants' interoceptive and ToM composite scores and the confidence ratings of their responses.
 Average lying confidence (+/- 1 SD) within the two experimental conditions is displayed as points for descriptive purposes as the models were ran on individual trials."}

### 2023-04-23 paper/manuscript.tex
minor fig and readme

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={The Heart can Lie: The Role of Interoception and Theory of Mind in Deception},
-  pdfauthor={Dominique Makowski1, 2, Zen J. Lau2, Tam Pham2, An Shu Te2, Stephanie Kirk2, Claudia Liauw2, \& S.H. Annabel Chen2, 3, 4, 5},
-  pdflang={en-EN},
-  pdfkeywords={Deception, Interoception, Theory of Mind, Poygraph, Lying Ability},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={The Heart can Lie: The Role of Interoception and Theory of Mind in Deception},
+  pdfauthor={Dominique Makowski1, 2, Zen J. Lau2, Tam Pham2, An Shu Te2, Stephanie Kirk2, Claudia Liauw2, \& S.H. Annabel Chen2, 3, 4, 5},
+  pdflang={en-EN},
+  pdfkeywords={Deception, Interoception, Theory of Mind, Poygraph, Lying Ability},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 \includegraphics[width=1\linewidth]{../figures/figure1} \caption{Interindividual corrrelates of lying confidence.
-The lines shows the relationship (with 95\% CI uncertainty), assessed via Bayesian mixed models (\***pd > 97\%, \***pd > 99\%, \****pd > 99.9\%), between the participants' interoceptive and TOM composite scores and the confidence ratings of their responses.
+The lines shows the relationship (with 95\% CI uncertainty), assessed via Bayesian mixed models (\***pd > 97\%, \***pd > 99\%, \****pd > 99.9\%), between the participants' interoceptive and ToM composite scores and the confidence ratings of their responses.
 Average lying confidence (+/- 1 SD) within the two experimental conditions is displayed as points for descriptive purposes as the models were ran on individual trials.}\label{fig:unnamed-chunk-1}
@@
 W., Nielsen, L., Hillaire-Clarke, C.
-S., Spruance, V.others.
+S., Spruance, V., et al.
 (2021).
@@
 \leavevmode\vadjust pre{\hypertarget{ref-yoris2015roles}{}}%
-Yoris, A., Esteves, S., Couto, B., Melloni, M., Kichic, R., Cetkovich, M., Favaloro, R., Moser, J., Manes, F., Ibanez, A.others.
+Yoris, A., Esteves, S., Couto, B., Melloni, M., Kichic, R., Cetkovich, M., Favaloro, R., Moser, J., Manes, F., Ibanez, A., et al.
 (2015).

### 2023-04-23 old/final_processing/Analysis/Analysis Code.R
add preprint link to README

@@ -1,88 +1,0 @@
-#### HP3804 EFA in RStudio =====================================  (stats generated factors)
-# install the following 4 packages before you can run the commands below:
-#foreign is for reading spss
-#psych is for efa
-#gpa rotation is for factor rotation
-#hmisc is for some factor analysis
-install.packages("foreign")
-install.packages("psych")
-install.packages("GPArotation")
-install.packages("Hmisc")
-install.packages("tidyverse")
-install.packages("ggplot2")
-install.packages("bayestestR")
-install.packages("see")
-install.packages("psycho")
-install.packages("lme4")
-install.packages("rstatix")
-install.packages("glmer")
-
-# Load required packages
-library(foreign)
-library(psych)
-library(GPArotation)
-library(Hmisc)
-library(tidyverse)
-library(ggplot2)
-library(bayestestR)
-library(see)
-
-# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
-setwd("  ")
-setwd("~/Desktop/R Testing")
-
-
-
-#**********YONI TASK Code Processing************************************
-# read SPSS fa_eg.sav
-# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
-setwd("~/Dropbox/FYP_Jia Rong/R Processing/FINAL PROCESSING")
-library(tidyverse)
-library(lme4)
-#library(rstatix)
-
-#LOAD DATA
-Behav <- read.csv('Behaviouraldata.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1)] %>% 
-  rename(participant = ID) %>% 
-  mutate(Trial = rep(1:80, 30))
-
-Phy <- read.csv('DT.csv', stringsAsFactors = FALSE, header = TRUE) [-c(1),] %>% 
-  rename(participant = Participant.number) %>% 
-  mutate(Trial = rep(1:80, each = 4, times = 30))
-
-#Phy <- Phy[!(Phy$Participant == 1 & Phy$Label == 3),]
-
-data <- merge(Behav, Phy, by = c("participant" ,"Trial"), all = TRUE) %>% 
-  arrange(participant,Trial)
-
-#REMOVE ERROR TRIALS IN PARTICIPANTS
-
-
[…]

### 2023-04-23 old/final_processing/Analysis/Old Codes.R

@@ -1,608 +1,0 @@
-
-#Regression models
-##Subjective Response Comparison
-df <- data %>% 
-  mutate(participant = as.factor(participant),
-         ConditionSP = as.factor(ConditionSP)) %>% 
-  filter(truthfulness == "LIE") %>% 
-  filter(participant != "3",
-         participant != "15",
-         participant != "19",
-         participant != "23")
-
-#report(model)
-#summary(model)
-
-#subresp = ConditionSP(X1) + Yoni_Task(X2) + HCT_Accuracy(X3) (3-way interaction)
-model_sub1 <- lme4::lmer(subresp ~ ConditionSP * yoni_total * HCT_Accuracy + (1|participant), data = df)
-parameters::parameters(model_sub1)
-plot_model(model_sub1, type = "pred", terms = c("HCT_Accuracy", "yoni_total", "ConditionSP"))
-
-#subresp = ConditionSP(X1) + Yoni_Task(X2) + HCT_Accuracy(X3) (3-way interaction)
-model_sub2 <- lme4::lmer(subresp ~ ConditionSP * (yoni_total + HCT_Accuracy) + (1|participant), data = df)
-parameters::parameters(model_sub2)
-plot_model(model_sub2, type = "pred", terms = c("yoni_total", "HCT_Accuracy", "ConditionSP"))
-
-#Interoception (HCT)
-#subresp = ConditionSP(X1) + HCT_Accuracy(X2) (Interaction)
-model_sub3 <- lme4::lmer(subresp ~ ConditionSP * HCT_Accuracy + (1|participant), data = df)
-parameters::parameters(model_sub3)
-plot_model(model_sub3, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"))
-
-model_sub4 <- lme4::lmer(subresp ~ ConditionSP * MAIA_Total + (1|participant), data = df)
-parameters::parameters(model_sub4)
-plot_model(model_sub4, type = "pred", terms = c("MAIA_Total", "ConditionSP"))
-
-model_sub5 <- lme4::lmer(subresp ~ (ConditionSP * HCT_Accuracy) + HCT_Confidence + HCT_Awareness + MAIA_Total + (1|participant), data = df)
-parameters::parameters(model_sub5)
-plot_model(model_sub5, type = "pred", terms = c("HCT_Accuracy", "ConditionSP"))
-
[…]

### 2023-04-23 old/final_processing/FInal Code.R

@@ -1,333 +1,0 @@
-#### HP3804 EFA in RStudio =====================================  (stats generated factors)
-# install the following 4 packages before you can run the commands below:
-#foreign is for reading spss
-#psych is for efa
-#gpa rotation is for factor rotation
-#hmisc is for some factor analysis
-install.packages("foreign")
-install.packages("psych")
-install.packages("GPArotation")
-install.packages("Hmisc")
-install.packages("tidyverse")
-install.packages("ggplot2")
-install.packages("bayestestR")
-install.packages("see")
-install.packages("psycho")
-install.packages("lme4")
-install.packages("rstatix")
-install.packages("glmer")
-
-# Load required packages
-library(foreign)
-library(psych)
-library(GPArotation)
-library(Hmisc)
-library(tidyverse)
-library(ggplot2)
-library(bayestestR)
-library(see)
-
-# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
-setwd("  ")
-setwd("~/Desktop/R Testing")
-
-
-
-#**********YONI TASK Code Processing************************************
-# read SPSS fa_eg.sav
-# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
-setwd("~/Dropbox/FYP_Jia Rong/R Processing/FINAL PROCESSING")
-library(tidyverse)
-library(lme4)
-library(rstatix)
-
-BES <- read.csv('BES_30processed.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1)]
-LIE <- read.csv('lieprofiler_30.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1,2)]
-MAIA <- read.csv('MAIA2_30processed.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1,2)]
-SRP3 <- read.csv('SRP3_30processed.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1,2)]
-YONI <- read.csv('yonitask_30processed.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1,2)]
-HCT <- read.csv('HCTdata.csv', stringsAsFactors = FALSE, header = TRUE)[-c(1,2)]
[…]

### 2023-04-23 old/heartbeat/HCT Code.R

@@ -1,342 +1,0 @@
-#### HP3804 EFA in RStudio =====================================  (stats generated factors)
-# install the following 4 packages before you can run the commands below:
-#foreign is for reading spss
-#psych is for efa
-#gpa rotation is for factor rotation
-#hmisc is for some factor analysis
-install.packages("foreign")
-install.packages("psych")
-install.packages("GPArotation")
-install.packages("Hmisc")
-install.packages("tidyverse")
-install.packages("ggplot2")
-install.packages("bayestestR")
-install.packages("see")
-install.packages("stringr")
-
-# Load required packages
-library(foreign)
-library(psych)
-library(GPArotation)
-library(Hmisc)
-library(tidyverse)
-library(ggplot2)
-library(bayestestR)
-library(see)
-library(stringr)
-
-# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
-setwd("  ")
-setwd("~/Desktop/R Testing")
-
-
-
-#**********YONI TASK Code Processing************************************
-# read SPSS fa_eg.sav
-# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
-setwd("~/Dropbox/FYP_Jia Rong/R Processing/heartbeat task processing in R")
-library(tidyverse)
-library(stringr)
-
-
-
-mydata <- data.frame()
-for (participant in list.files("../../data/")) {
-  df_sub <- read.csv(paste0("../../data/", participant, "/heartbeat/", participant, "_heartbeat.csv"))[-c(6:9), -c(1, 3:8, 12:31, 33:38)]  
-    mydata <- rbind(mydata, df_sub)
-}
-
-
-mydata <- mydata %>% 
-rename(hbcount = heartbeatresponse.text,
-       confidence = confidenceslider.response,
-       confidenceRT = confidenceslider.rt)
-      # guess = key_guess.keys,
-      # guessRT = key_guess.rt,
-      # noguess = key_noguess.keys,
-     #  noguessRT = key_noguess.rt,
-     #  onebreath = key_noguess_perturbed.keys,
[…]

### 2023-04-23 old/questionnaire_BES/BES Code.R

@@ -1,250 +1,0 @@
-#### HP3804 EFA in RStudio =====================================  (stats generated factors)
-# install the following 4 packages before you can run the commands below:
-#foreign is for reading spss
-#psych is for efa
-#gpa rotation is for factor rotation
-#hmisc is for some factor analysis
-install.packages("foreign")
-install.packages("psych")
-install.packages("GPArotation")
-install.packages("Hmisc")
-install.packages("tidyverse")
-install.packages("ggplot2")
-install.packages("bayestestR")
-install.packages("see")
-
-# Load required packages
-library(foreign)
-library(psych)
-library(GPArotation)
-library(Hmisc)
-library(tidyverse)
-library(ggplot2)
-library(bayestestR)
-library(see)
-
-# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
-setwd("  ")
-setwd("~/Desktop/R Testing")
-setwd("C:/Users/gen_3/Desktop/R Testing")
-
-
-#*****BES CODE PROCESSING****
-# read SPSS fa_eg.sav
-# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
-setwd("~/Dropbox/FYP_Jia Rong/R Processing/R Code for BES")
-library(tidyverse)
-mydata <- read.csv('BES_30.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)] 
-
-data <- mydata %>% 
-  as.data.frame() %>%  
-  rename(Q1 = Q3_1,
-       Q2 = Q3_2,
-       Q3 = Q3_3,
-       Q4 = Q3_4,
-       Q5 = Q3_5,
-       Q6 = Q3_6,
-       Q7 = Q3_7,
-       Q8 = Q3_8,
-       Q9 = Q3_9,
-       Q10 = Q3_10,
-       Q11 = Q3_11,
-       Q12 = Q3_12,
-       Q13 = Q3_13,
-       Q14 = Q3_14,
-       Q15 = Q3_15,
-       Q16 = Q3_16,
-       Q17 = Q3_17,
-       Q18 = Q3_18,
-       Q19 = Q3_19,
-       Q20 = Q3_20,
-       ID = Q2) %>% 
[…]

### 2023-04-23 old/questionnaire_LIE/Lie Profiler Code.R

@@ -1,301 +1,0 @@
-#### HP3804 EFA in RStudio =====================================  (stats generated factors)
-# install the following 4 packages before you can run the commands below:
-#foreign is for reading spss
-#psych is for efa
-#gpa rotation is for factor rotation
-#hmisc is for some factor analysis
-install.packages("foreign")
-install.packages("psych")
-install.packages("GPArotation")
-install.packages("Hmisc")
-install.packages("tidyverse")
-install.packages("ggplot2")
-install.packages("bayestestR")
-install.packages("see")
-install.packages("lavaan")
-
-# Load required packages
-library(foreign)
-library(psych)
-library(GPArotation)
-library(Hmisc)
-library(tidyverse)
-library(ggplot2)
-library(bayestestR)
-library(see)
-library(lavaan)
-
-# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
-setwd("  ")
-setwd("~/Desktop/R Testing")
-setwd("C:/Users/gen_3/Desktop/R Testing")
-
-#************LIE Profiler Code Processing***********************************
-# read SPSS fa_eg.sav
-# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
-setwd("~/Dropbox/FYP_Jia Rong/R Processing/R Code for LIE Profiler")
-library(tidyverse)
-mydata <- read.csv('LIE_30.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)] 
-
-data <- mydata %>% 
-  as.data.frame() %>%  
-  rename(LIE_10 = Q1_4,
-         LIE_9 = Q2_4, 
-         LIE_14 = Q3_4,
-         LIE_18 = Q4_4,  
-         LIE_4 = Q5_4, 
-         LIE_5 = Q6_4, 
-         LIE_23 = Q7_4, 
-         LIE_1 = Q8_4, 
-         LIE_41 = Q9_4, 
-         LIE_25 = Q10_1, 
-         LIE_44 = Q11_1, 
-         LIE_34 = Q12_4, 
-         LIE_43 = Q13_4, 
-         LIE_33 = Q14_4, 
-         LIE_42 = Q15_4, 
-         LIE_39 = Q16_4, 
-       LieDay = Q17,
-       LieWeek = Q18)
-
[…]

### 2023-04-23 old/questionnaire_MAIA/MAIA Code.R

@@ -1,286 +1,0 @@
-#### HP3804 EFA in RStudio =====================================  (stats generated factors)
-# install the following 4 packages before you can run the commands below:
-#foreign is for reading spss
-#psych is for efa
-#gpa rotation is for factor rotation
-#hmisc is for some factor analysis
-install.packages("foreign")
-install.packages("psych")
-install.packages("GPArotation")
-install.packages("Hmisc")
-install.packages("tidyverse")
-install.packages("ggplot2")
-install.packages("bayestestR")
-install.packages("see")
-
-# Load required packages
-library(foreign)
-library(psych)
-library(GPArotation)
-library(Hmisc)
-library(tidyverse)
-library(ggplot2)
-library(bayestestR)
-library(see)
-
-# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
-setwd("  ")
-setwd("~/Desktop/R Testing")
-setwd("C:/Users/gen_3/Desktop/R Testing")
-
-
-
-#******MAIA2 CODE PROCESSING**************
-# read SPSS fa_eg.sav
-# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
-setwd("~/Dropbox/FYP_Jia Rong/R Processing/R Code for MAIA2")
-library(tidyverse)
-mydata <- read.csv('MAIA2_30.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)] 
-
-data <- mydata %>% 
-  as.data.frame() %>%  
-  rename(Q1 = Q3_1,
-       Q2 = Q3_2,
-       Q3 = Q3_3,
-       Q4 = Q3_4,
-       Q5 = Q3_5,
-       Q6 = Q3_6,
-       Q7 = Q3_7,
-       Q8 = Q3_8,
-       Q9 = Q3_9,
-       Q10 = Q3_10,
-       Q11 = Q3_11,
-       Q12 = Q3_12,
-       Q13 = Q3_13,
-       Q14 = Q3_14,
-       Q15 = Q3_15,
-       Q16 = Q3_16,
-       Q17 = Q3_17,
-       Q18 = Q3_18,
-       Q19 = Q3_19,
-       Q20 = Q3_20,
-       Q21 = Q4_1,
-       Q22 = Q4_2,
[…]

### 2023-04-23 old/questionnaire_demogaphics/Demo Code.R

@@ -1,295 +1,0 @@
-#### HP3804 EFA in RStudio =====================================  (stats generated factors)
-# install the following 4 packages before you can run the commands below:
-#foreign is for reading spss
-#psych is for efa
-#gpa rotation is for factor rotation
-#hmisc is for some factor analysis
-install.packages("foreign")
-install.packages("psych")
-install.packages("GPArotation")
-install.packages("Hmisc")
-install.packages("tidyverse")
-install.packages("ggplot2")
-install.packages("bayestestR")
-install.packages("see")
-install.packages("stringr")
-
-# Load required packages
-library(foreign)
-library(psych)
-library(GPArotation)
-library(Hmisc)
-library(tidyverse)
-library(ggplot2)
-library(bayestestR)
-library(see)
-library(stringr)
-
-# Remember to first set your working directory from pull down menu or use the command below by inserting the directory path
-setwd("  ")
-setwd("~/Desktop/R Testing")
-
-
-
-#**********YONI TASK Code Processing************************************
-# read SPSS fa_eg.sav
-# mydata <- read.spss('fa_eg.sav', to.data.frame = T)
-setwd("~/Dropbox/FYP_Jia Rong/R Processing/Demogaphics")
-library(tidyverse)
-library(stringr)
-
-
-
-mydata <- read.csv('demo.csv', stringsAsFactors = FALSE)[-c(1:2), -c(1:17, 30, 32, 34,36)] 
-
-mydata <- mydata %>% 
-  rename(Name = Q2,
-         ID = Q3,
-         Matric = Q4,
-         HP = Q5,
-         Email = Q6,
-         Gender = Q7,
-         Age = Q8,
-         Birthday = Q9,
-         handedness = Q10,
-         School = Q11,
-         Course = Q12,
-         Polyjc = Q13,
-         Ethnicity = Q14,
-         Religion = Q15,
-         Nationality = Q16,
-         RaisedinSG = Q17,
-         LivedinSG = Q18) %>% 
-  mutate(ID = as.numeric(ID)) %>% 
-  arrange(ID)
-
-write.csv(mydata, file = "demo_30.csv")
-
[…]

### 2023-04-23 paper/manuscript.Rmd
add abstract

@@
 abstract: |
+  While a large part of the deception literature focuses on lying detection, the factors contributing to one's ability to lie remain unclear.
+The present study examined the contribution of Theory of Mind (ToM) and interoception on our ability to lie using a directed lie paradigm with two conditions ("Interrogation" and "Polygraph"), designed to enhance each of the two mechanisms.
+Using a mixed-design Bayesian analysis, we show that various facets of interoceptive abilities are positively related to the self-rated confidence in one's own lies, especially when under the belief that bodily signals are being monitored (i.e., in the "Polygraph" condition).
+Beyond providing evidence for the role of the body in lying and raising interesting questions for deception science, these results carry practical implications for criminology and lie detection protocols.
 output:
@@
 The analysis was not pre-registered (stemming out from a student's project), but the full reproducible analysis script, statistical results report, and data, are available at 
-https://github.com/DominiqueMakowski/DeceptionInteroTom
+<!-- **[masked for blinding]** -->
+**https://github.com/DominiqueMakowski/DeceptionInteroTom**
 
@@
 
-The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, etc.) for this research is available at **https://github.com/DominiqueMakowski/DeceptionInteroTom**.
-
-<!-- # Funding -->
-
-<!-- **no funding** -->
+The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, etc.) for this research is available at 
+**https://github.com/DominiqueMakowski/DeceptionInteroTom**.
+<!-- **[masked for blinding]**. -->
 
@@
 
+<!-- **[masked for blinding]** -->
 We would like to thank Jia Rong Low and Maximilian Yong for their help in data collection.

### 2023-04-23 paper/manuscript.tex
add abstract

@@
 
+\abstract{%
+While a large part of the deception literature focuses on lying detection, the factors contributing to one's ability to lie remain unclear.
+The present study examined the contribution of Theory of Mind (ToM) and interoception on our ability to lie using a directed lie paradigm with two conditions (``Interrogation'' and ``Polygraph''), designed to enhance each of the two mechanisms.
+Using a mixed-design Bayesian analysis, we show that various facets of interoceptive abilities are positively related to the self-rated confidence in one's own lies, especially when under the belief that bodily signals are being monitored (i.e., in the ``Polygraph'' condition).
+Beyond providing evidence for the role of the body in lying and raising interesting questions for deception science, these results carry practical implications for criminology and lie detection protocols.
+}
+
 \begin{document}
@@
 The analysis was not pre-registered (stemming out from a student's project), but the full reproducible analysis script, statistical results report, and data, are available at
-\url{https://github.com/DominiqueMakowski/DeceptionInteroTom}
+\textbf{\url{https://github.com/DominiqueMakowski/DeceptionInteroTom}}
 
@@
 
-The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, etc.) for this research is available at \textbf{\url{https://github.com/DominiqueMakowski/DeceptionInteroTom}}.
+The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, etc.) for this research is available at
+\textbf{\url{https://github.com/DominiqueMakowski/DeceptionInteroTom}}.
 

### 2023-04-23 paper/manuscript.Rmd
blind

@@
       - "Writing – original draft"
-  - name          : "Zen J. Lau"
+  - name          : "Zen J. Lau"  # lauzenjuen@gmail.com
     affiliation   : " 2"
-  - name          : "Tam Pham"
+  - name          : "Tam Pham"  # phamttam17@gmail.com
     affiliation   : " 2"
-  - name          : "An Shu Te"
+  - name          : "An Shu Te" # anshu.te@ntu.edu.sg
     affiliation   : "2"
@@
       - "Writing – original draft"
-  - name          : "Stephanie Kirk"
+  - name          : "Stephanie Kirk"  # stephanie.morgank@gmail.com
     affiliation   : "2"
@@
       - "Writing – original draft"
-  - name          : "Claudia Liauw"
+  - name          : "Claudia Liauw"  # YLIAUW001@e.ntu.edu.sg
     affiliation   : "2"
@@
       - "Formal Analysis"
-  - name          : "S.H. Annabel Chen"
+  - name          : "S.H. Annabel Chen"  # AnnabelChen@ntu.edu.sg
     affiliation   : "2, 3, 4, 5"
@@
     keep_tex: yes
-keywords: "Deception, Interoception, Theory of Mind, Poygraph, Lying Ability"
+keywords: "Deception; Interoception; Theory of Mind; Poygraph; Lying Ability"
 wordcount: '3720'
@@
 linenumbers: yes
-mask: no
+mask: yes
 draft: no
@@
 The analysis was not pre-registered (stemming out from a student's project), but the full reproducible analysis script, statistical results report, and data, are available at 
-<!-- **[masked for blinding]** -->
-**https://github.com/DominiqueMakowski/DeceptionInteroTom**
+**[masked for blinding]**
+<!-- **https://github.com/DominiqueMakowski/DeceptionInteroTom** -->
 
@@
 The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, etc.) for this research is available at 
-**https://github.com/DominiqueMakowski/DeceptionInteroTom**.
-<!-- **[masked for blinding]**. -->
+<!-- **https://github.com/DominiqueMakowski/DeceptionInteroTom**. -->
+**[masked for blinding]**.
 
@@
 
-<!-- **[masked for blinding]** -->
-We would like to thank Jia Rong Low and Maximilian Yong for their help in data collection.
+**[masked for blinding]**
+<!-- We would like to thank Jia Rong Low and Maximilian Yong for their help in data collection. -->
 

### 2023-04-23 paper/manuscript.tex
blind

@@
 \documentclass[
-  man,floatsintext]{apa6}
+  man,mask,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
   pdftitle={The Heart can Lie: The Role of Interoception and Theory of Mind in Deception},
-  pdfauthor={Dominique Makowski1, 2, Zen J. Lau2, Tam Pham2, An Shu Te2, Stephanie Kirk2, Claudia Liauw2, \& S.H. Annabel Chen2, 3, 4, 5},
   pdflang={en-EN},
@@
 The analysis was not pre-registered (stemming out from a student's project), but the full reproducible analysis script, statistical results report, and data, are available at
-\textbf{\url{https://github.com/DominiqueMakowski/DeceptionInteroTom}}
+\textbf{{[}masked for blinding{]}}
 
@@
 The material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, etc.) for this research is available at
-\textbf{\url{https://github.com/DominiqueMakowski/DeceptionInteroTom}}.
+\textbf{{[}masked for blinding{]}}.
 
@@
 
-We would like to thank Jia Rong Low and Maximilian Yong for their help in data collection.
+\textbf{{[}masked for blinding{]}}
 

### 2023-06-05 paper/manuscript.Rmd
minor

@@
     affiliation   : " 2"
+    role:
+      - "Data curation"
+      - "Project administration"
+      - "Resources"
+      - "Investigation"
   - name          : "Tam Pham"  # phamttam17@gmail.com
     affiliation   : " 2"
+    role:
+      - "Data curation"
+      - "Project administration"
+      - "Resources"
+      - "Investigation"
   - name          : "An Shu Te" # anshu.te@ntu.edu.sg
@@
 output:
-  papaja::apa6_pdf:
+  papaja::apa6_word:
     keep_tex: yes

### 2023-06-22 paper/manuscript.Rmd
R1 update

@@
 ---
-title: '**The Heart can Lie: The Role of Interoception and Theory of Mind in Deception**'
+title: '**The Heart can Lie: A Preliminary Analysis of the Role of Interoception and Theory of Mind in Deception**'
 shorttitle        : "Deception, Interoception, and ToM"
@@
   While a large part of the deception literature focuses on lying detection, the factors contributing to one's ability to lie remain unclear.
-The present study examined the contribution of Theory of Mind (ToM) and interoception on our ability to lie using a directed lie paradigm with two conditions ("Interrogation" and "Polygraph"), designed to enhance each of the two mechanisms.
+The present study (n=26) examined the contribution of Theory of Mind (ToM) and interoception on our ability to lie using a directed lie paradigm with two conditions ("Interrogation" and "Polygraph"), designed to enhance each of the two mechanisms.
+In view of the relatively small sample size, we performed a feature reduction on the measures used to assess our two groups of predictor variables using factor analysis and extracted a unique factor of ToM as well as 4 components of interoception (*Metacognition*, *Listening*, *Focus* and *Regulation*).
 Using a mixed-design Bayesian analysis, we show that various facets of interoceptive abilities are positively related to the self-rated confidence in one's own lies, especially when under the belief that bodily signals are being monitored (i.e., in the "Polygraph" condition).
@@
 keywords: "Deception; Interoception; Theory of Mind; Poygraph; Lying Ability"
-wordcount: '3720'
+wordcount: '5004'
 bibliography: ["references.bib"]
@@
 However, with most of the deception literature focused on deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], the factors contributing to one's ability to lie remain unclear.
+Nevertheless, some findings suggest a relationship between the propensity to tell lies, and traits that characterize the socially malevolent profile known as the Dark Triad [@paulhus2002dark], such as narcissism [@zvi2018correlates] and psychopathy [@rassin2023psychopathy].
+While often conceptualized to be immoral and unconscionable, lying is ubiquitous in everyday life, and being able to lie skillfully can sometimes facilitate interpersonal relationships, helping us avoid conflict or causing emotional harm to others [@levine2022prosocial].
+In fact, recent research shows that certain forms of deception, such as prosocial lies (i.e., false statements told to benefit others; @levine2022prosocial), can increase trust [@levine2015prosocial].
+Moreover, individuals who told altruistic lies were perceived as more benevolent than those who were honest [@levine2014liars].
 
@@
 
-<!-- TOM  -->
+<!-- ToM  -->
 
@@
 This begs the question of the potential role of interoceptive abilities in deception ability.
-Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing's conceptualizes interoception as a three-dimensional construct comprising three distinct facets, namely, interoceptive accuracy - the objective ability to monitor internal bodily signals; interoceptive sensibility - the subjective confidence in one's interoceptive accuracy; and interoceptive awareness - one's ability to identify and appropriately respond to their perceived interoceptive states.
+Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing conceptualize interoception as a three-dimensional construct comprising three distinct facets, namely, interoceptive accuracy - the objective ability to monitor internal bodily signals; interoceptive sensibility - the subjective confidence in one's interoceptive accuracy; and interoceptive awareness (also referred to as interoceptive insight; @khalsa2018interoception) - one's ability to correctly evaluate their interoceptive ability.
 Interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing, and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].
+In particular, neuroscientific findings investigating the correlates of interoception have underlined the potential role of the anterior cingulate cortex (ACC) and anterior insula (AI) [@wang2019anterior; @craig2009you; @critchley2004neural; @khalsa2009pathways], both of which are often thought to be activated during deception [@abe2011brain; @sip2008detecting; @baumgartner2013honest], and have been implicated in cognitive processes associated with deception (e.g., cognitive control [@molnar2022anterior], conflict detection [@kerns2004anterior]).
+
 Although few studies exist that investigate the relationship between interoception and deceptive ability *per se*, previous decision-making studies have demonstrated a negative correlation between interoceptive awareness, a metacognitive dimension of interoception, and one's likelihood to make risky decisions [@dunn2010listening; @furman2013interoceptive].
-In fact, this is consistent with the somatic marker hypothesis, which posits an association between interoception and a propensity towards making rational decisions [@damasio1996somatic].
-
-In contrast, however, some studies have instead found heightened interoceptive attention (one's self-focus towards internal bodily signals), to predict apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening].
+This is in line with the somatic marker hypothesis, which posits that an accurate evaluation of one's bodily signals facilitates the use of such interoceptive feedback to guide rational decision making [@damasio1996somatic].
+Indeed, @sugawara2020effects further reports that individuals who received interoceptive training were more likely to show higher interoceptive accuracy and make reasoned decisions.
+Given that deciding to lie generally involves a consideration of the potential costs of getting caught, and hence could also be perceived as risky behavior [@kireev2013possible], interoception could be construed to be negatively related to lying ability.
+However, some studies have instead found heightened interoceptive attention (one's self-focus towards internal bodily signals), to predict apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening].
 Extending these findings to social cognition, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high, whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
@@
 The *Interrogation* condition was designed to emphasize (and preferentially mobilize) ToM-related mechanisms, whereas the *Polygraph* condition was designed to emphasize interoceptive mechanisms.
-We expected ToM and interoception to positively predict lying ability (i.e., higher lie confidence, shorter response time and lower physiological arousal), in particular in the *Polygraph* and the *Interrogation* condition, respectively.
+In particular, we expected lying ability (i.e., higher lie confidence, shorter response time and lower physiological arousal), to be positively predicted by individuals' interoceptive abilities in the *Polygraph* condition, and by ToM skills in the *Interrogation* condition.
+Consistent with the cognitive load approach outlined in several theories of deception (such as the Four-Factor Theory [@riggio1987verbal] and Activation-Decision-Construction Model [@walczyk2014social]), as well as previous findings which suggest response time as a reliable cue to deception [@walczyk2009cognitive; @gonzalez2019can], we regarded shorter response times as a proxy of better lying ability.
 
@@
 Four participants were excluded as their data was not recorded due to technical issues.
-The final sample consists 26 participants (Mean age = 20.9, SD = 2.0, range:[18, 25], Sex: 65.4% women, 34.6% men).
+The final sample consists of 26 participants (Mean age = 20.9, SD = 2.0, range:[18, 25], Sex: 65.4% women, 34.6% men).
 The heart rate of one participant and response time of one participant were excluded from further analysis due to extreme outlying values.
+To maximize statistical power, the problematic data from these 2 participants were only excluded from analyses involving those measures; all other data were retained for analyses.
 
@@
 
-### Theory of Mind
+### Theory of Mind (ToM)
 
 Two measures of ToM and its related constructs were administered.
-The Yoni Task [@shamay2007dissociable] is a behavioral task in which participants are presented with the face of a character named "Yoni", surrounded by 4 colored pictures of objects or faces.
-In total, each participant completed 101 trials - 49 trials assessing their affective TOM abilities, 37 trials assessing their cognitive TOM abilities and 15 control trials.
-During each trial, participants were shown a question and asked to make responses based on specific cues such as directions of Yoni's eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical TOM).
+The Yoni Task [@shamay2007dissociable] is a behavioral task which assesses first and second-order ToM abilities in both cognitive and affective domains.
+Participants were presented with the face of a character named "Yoni", surrounded by 4 colored pictures of objects or faces, one in each corner of the screen.
+In total, each participant completed 101 trials - 49 trials assessing their affective ToM abilities, 37 trials assessing their cognitive ToM abilities and 15 control trials.
+During each trial, participants were shown a question pertaining the item Yoni is referring to, and asked to make responses based on specific corresponding cues such as the directions of Yoni's eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical ToM).
+More specifically, in first-order trials, participants were instructed to make inferences about Yoni's mental state with regards to the objects surrounding it (e.g., "Yoni is thinking of...").
+In more complex second-order trials, participants had to correctly infer the interaction between Yoni and others' mental states (e.g., Yoni is thinking of the fruit that ...
+wants").
 
-The Basic Empathy Scale [BES, @jolliffe2006development], a 20-item questionnaire measuring two dimensions of empathy (cognitive and affective) using a 5-point Likert scale was administered.
+The Basic Empathy Scale [BES, @jolliffe2006development], a 20-item self-report questionnaire measuring two dimensions of empathy (cognitive and affective) using a 5-point Likert scale was administered.
 Although ToM and empathy are regarded as distinct psychological constructs, previous research findings point to them being closely related [@gallant2020developing; @sebastian2012neural].
-<!-- Specifically, empathy is often thought to be an integral component in the affective dimension of ToM (i.e., the ability to infer what someone else is feeling) [@shamay2010role].  -->
+Specifically, empathy is often thought to be an integral component in the affective dimension of ToM (i.e., the ability to infer what someone else is feeling) [@shamay2010role].
+<!-- Interestingly, some studies suggest that people's performance on interpersonal ToM tasks can be disassociated from that of interpersonal ToM [@dvash2014theory; @tine2012unique].  -->
 
@@
 
-The MAIA-2 [@mehling2012multidimensional], a 32-item questionnaire which measures 8 dimensions of interoception (Noticing, Not-Distracting, Not-Worrying, Attention, Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust) using 5-point Likert scales, was also administered.
+Given its multidimensional nature, the MAIA-2 [@mehling2012multidimensional], a 37-item questionnaire which measures 8 distinct facets of interoception including Noticing (**I notice when I am uncomfortable in my body**), Not-Distracting (**I try to ignore pain**), Not-Worrying (**I can stay calm and not worry when I have feelings of discomfort or pain**), Attention Regulation (**I can refocus my attention from thinking to sensing my body**), Emotional Awareness (**I notice how my body changes when I am angry**), Self-Regulation (**I can use my breath to reduce tension**), Body Listening (**I listen to information from my body about my emotional state**), and Trust (**I trust my body sensations**), using 5-point Likert scales, was also administered.
 
@@
 
-Using PsychoPy [@peirce2019psychopy2], we implemented a directed-lying task in which participants were instructed to answer 80 questions by either lying or telling the truth (depending on whether they see "lie" or "truth" written on the screen).
+Using PsychoPy [@peirce2019psychopy2], we implemented a directed-lying task in which participants were instructed to answer 80 questions pertaining to their personal preferences and subjective experiences, by either lying or telling the truth (depending on whether they see "lie" or "truth" written on the screen).
 Importantly, they were told that for half of the trials, they would have to convince another participant that would be observing them from a separate room via a webcam connection (*Interrogation* condition).
@@
 The sequence of each trial was the same for both conditions.
-Participants were instructed to respond to a question shown on a computer screen, phrased either directly (e.g., "What is your favourite sport?"), or indirectly (e.g., "Is your favourite sport Hockey?"), by verbally lying or telling the truth (for half of the trials in each condition, i.e., n = 20).
-Following a short interval (0.7 - 1.5s) for response preparation, during which "Connecting..." was shown on the screen, a social or bio-feedback cue (for *Interrogation* and *Polygraph* conditions respectively) was displayed for a maximum of 10s.
-Participants then had to provide their answers verbally, and pressed the space key to signify the end of their response.
-After another short interval (1.5-2.5s), during which "Disconnecting" was written on the screen, participants were asked to rate their confidence in how convincing (i.e., likely to get judged as truthful) they perceived their response to be on a visual analog scale.
+Participants were first instructed to respond to a question shown on a computer screen by verbally lying or telling the truth (for half of the trials in each condition, i.e., n = 20).
+In addition, as past studies have found associations between lying behaviour and type of question phrasing [@walczyk2022err], each question was phrased either directly (e.g., "What is your favourite sport?"), or indirectly (e.g., "Is your favourite sport Hockey?") to reduce possible confounding effects.
+Following a short interval (0.7 - 1.5s) to allow time for response preparation, during which "Connecting..." was shown on the screen, a social or bio-feedback cue (for *Interrogation* and *Polygraph* conditions respectively) was displayed for a maximum of 10s or until a response was given.
+Specifically, participants had to provide their answers verbally, and pressed the space key to signify the end of their response.
+After another short interval (1.5-2.5s), during which "Disconnecting..." was presented on the screen, participants were asked to rate their confidence in how convincing (i.e., likely to get judged as truthful) they perceived their response to be on a visual analog scale.
+<!-- individuals experience heightened physiological arousal when the items are embedded with concealed information known to them (i.e., indirect questions) regardless of the truthfulness of their response [@verschuere2006psychopathy] -->
 
@@
 
-In the *Polygraph* condition, participants had to provide their answer while receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded.
-Participants were informed that they were being shown live feedback of their own physiological activity.
+In the *Polygraph* condition, participants had to provide their answer while receiving bio-feedback in the form of physiological signals (ECG, EDA and Respiration), of which they were informed was live feedback of their own physiological activity.
 In actuality, we displayed pre-recorded video clips of a confederate's physiological signals.
-All participants reported believing that it was indeed their own signals being shown during the debriefing.
+All participants reported believing that their own signals were shown during the debriefing.
 
@@
 
-This study is comprised of 2 sessions.
-During session 1, participants answered a brief demographic survey before the questionnaires, which were presented in a randomized order.
-During session 2, cognitive-behavioural tasks were administered to participants while their physiological signals (including cardiac activity (ECG), respiration (RSP) and electrodermal activity (EDA)) were being recorded.
+A within-subjects design was used in the present study, which is comprised of 2 sessions, to investigate the roles interoception and ToM play in lying ability.
+During session 1, participants answered a brief demographic survey as well as a questionnaire regarding their personal preferences and subjective experiences (Autobiographical Memory Questionnaire, AMQ), followed by a series of psychological scales (i.e., BES, MAIA and Lie scale), which were randomly displayed.
+During session 2, cognitive-behavioural tasks (i.e., the deception task, HCT and the Yoni task) were administered to participants while their physiological signals (including cardiac activity (ECG), respiration (RSP) and electrodermal activity (EDA)) were being recorded.
 The physiological recording devices were set up as follows: ECG was recorded with 3 electrodes placed according to a modified Lead II configuration [@takuma1995alternative], and respiration was measured using a respiration belt.
 All signals were recorded at 1000Hz via the BioPac MP160 system (BioPac Systems Inc., USA).
-For all participants, session 2 began with the deception task, followed by the YONI task and the HCT, with the latter two presented in a randomized order.
-Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of 3.5 s).
+For all participants, session 2 began with the deception task, followed by the Yoni task and the HCT, with the latter two presented in a randomized order.
+In the directed-lying task, items in the AMQ were presented as stimuli, with participants' recorded responses (in session 1) used to establish the ground truth.
+Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the change in heart rate associated with the response (within a window of 3.5 s).
 
@@
 
-Aware of the low number of participants, we tried to take every steps to 1) maximize power by using all available data (from individual trials) with appropriate statistical tools and 2) ensure the robustness of results by cross-validating the findings accross different measures and approaches.
+Aware of the low number of participants, we tried to take every step to 1) maximize power by using all available data (from individual trials) with appropriate statistical tools and 2) ensure the robustness of results by cross-validating the findings across different measures and approaches.
 
@@
 Finally, we investigated the relationship between the deception scale traits, and the ToM and interoception scores using Bayesian correlations.
-As all the analyses and data has been made available, we will in the manuscript focus on significant, i.e., - in this context - statistically reliable and in our opinion theoretically relevant.
+As all the analyses and data have been made available, we will in the manuscript focus on significant, i.e., - in this context - statistically reliable and in our opinion theoretically relevant.
 
@@
 
-The analysis was not pre-registered (stemming out from a student's project), but the full reproducible analysis script, statistical results report, and data, are available at 
+The analysis was not pre-registered (stemming out from an undergraduate's final year project), but the full reproducible analysis script, statistical results report, and data, are available at 
 **[masked for blinding]**
@@
 
-The 3 YONI-task dimensions and the 2 BES traits were combined into a unique factor, labelled *TOM* (explaining 35.76% of variance).
-It was loaded by the cognitive (.89), affective (.77), physical (.45) YONI dimensions, and the affective (.41) and cognitive (.17) facets of the BES.
+The 3 Yoni-task dimensions and the 2 BES traits were combined into a unique factor, labelled *ToM* (explaining 35.76% of variance).
+It was loaded by the cognitive (.89), affective (.77), physical (.45) Yoni dimensions, and the affective (.41) and cognitive (.17) facets of the BES.
 
@@
 
-The composite *TOM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67\%$), specifically in the polygraph condition.
+The composite *ToM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67\%$), specifically in the polygraph condition.
 No significant effect was found with regards to heart rate, and no correlation was observed with dispositional lying traits (**Figure 1**).
@@
 This is consistent with previous deception detection studies, in which participants' spontaneous lying behaviour only decreased when they were given feedback by a polygraph machine, but not when no feedback was given [@peleg2019lie].
-Additionally, our study also extends past deception research and further confirms the validity concerns in solely relying on physiological measures as an indicator of deception [@rosky2013f; @oviatt2018handbook].
+By extension, our study adds to the controversial discourse surrounding the use of physiological measures in past deception research, further questioning its validity as an indicator of deception [@rosky2013f; @oviatt2018handbook].
 
@@
 
-<!-- TOM -->
+<!-- ToM -->
 Our results suggest that higher ToM abilities were related to slower and less confident lies, but only in the polygraph condition.
+While previous bodies of work have reported mixed findings regarding the association between interoception and ToM [@scaffidi2016self; @gendolla2009self; @wundrack2023mindful; @chiou2013enactment], our results suggest the two are negatively linked.
 One possible interpretation of our findings is that people with stronger ToM abilities by default rely more on their social skills and altercentric inference when lying (i.e., they focus on - and try to read - the other person).
 When that mechanism is unavailable or unsuited (e.g., when there is no person to lie to - but a "machine" in our case), their corresponding lying ability decreases.
-In light of the current field of mixed findings relating interoception and ToM [@shah2017heart; @gao2019body; @canino2022embodiment; @miller2015connections], future studies are necessary to investigate the interaction of these mechanisms in different social contexts.
+However, in light of the current field of mixed findings relating interoception and ToM [@shah2017heart; @gao2019body; @canino2022embodiment; @miller2015connections], future studies are necessary to investigate the interaction of these mechanisms in different social contexts.
+
+<!-- ionship between ToM and deception in contexts where interoceptive abilities are emphasized, the observed effects are in line with studies that suggest negative links associating ToM with interoceptive sensibility (i.e., the self-perceived tendency to monitor internal signals) [@canino2022embodiment].
+-->
 
 <!-- Interoception -->
-We also showed that interoceptive abilities are correlated with a higher confidence in one's lies in the polygraph condition, a condition in which the attention towards internal reactions is fostered.
+We also showed that interoceptive abilities (as indicated by the composite interoception scores) are correlated with a higher confidence in one's lies in the polygraph condition, a condition in which the attention towards internal reactions is fostered.
+Indeed, this is in line with previous studies that found individuals with low interoception were more averse to risk when reputational stakes were high, telling fewer egoistical lies [@vabba2022interoceptive].
+In fact, @vabba2022interoceptive further reports that people with high interoception abilities were less likely to differ in risk-taking tendencies, telling the same number of lies regardless of the social stakes.
+Consistent with our results, @von2023social further reports that individuals with high interoceptive accuracy were more likely to make egocentric decisions.
 However, in contrast to previous studies [@pinna2020systematic; @fustos2013embodiment; @owens2018investigating; @pollatos2007heart], we did not find any significant relationship between individuals' interoception scores and their heart rate changes during their answers.
@@
 
-<!-- Our results show a significant association between individuals' composite TOM score with lower lie confidence and longer response time when interoceptive cues were highly salient.
-Under the free energy principle [@friston2010free], interoception is regarded as integral in TOM [@shah2017heart; @palmer2018going; @ondobaka2017role].
+<!-- Our results show a significant association between individuals' composite ToM score with lower lie confidence and longer response time when interoceptive cues were highly salient.
+Under the free energy principle [@friston2010free], interoception is regarded as integral in ToM [@shah2017heart; @palmer2018going; @ondobaka2017role].
 Specifically, during social inference, interoceptive signals are integrated with exteroceptive (e.g., visual and auditory) and proprioceptive information (i.e., motor) to guide one's social behaviour [@ondobaka2017role].
-Given recent work in which TOM is associated with one having more precise interoceptive states [@tsakiris2017multisensory; @palmer2018going; @arnold2019interoception], it is possible that individuals with greater TOM abilities have higher interoceptive awareness, more stable self-other representations and less malleable percepts of self [@tsakiris2017multisensory; @arnold2019interoception].
+Given recent work in which ToM is associated with one having more precise interoceptive states [@tsakiris2017multisensory; @palmer2018going; @arnold2019interoception], it is possible that individuals with greater ToM abilities have higher interoceptive awareness, more stable self-other representations and less malleable percepts of self [@tsakiris2017multisensory; @arnold2019interoception].
 As such, external cues of their interoceptive signals may be perceived as incongruent, hence generating a sense of uncertainty in their responses and leading to their lower lie confidence and longer response times.
@@
 Given increasing research efforts invested in the development of novel interoception tasks [@plans2021measuring; @legrand2022heart; @ponzo2021measuring], future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.
-Additionally, our application of feature reduction as a noise-elimination measure could have over-simplified the data.
+
+Moreover, although the cognitive and affective components of ToM and empathy share overlaps in the current literature, and there is no consensus regarding how the two concepts should be delineated, recent evidence nonetheless suggests ToM and empathy are necessarily distinct constructs with separable underlying mechanisms [@kanske2015dissecting].
+As such, future studies are warranted to further investigate the associations between ToM and lying ability using validated instruments sensitive to measuring ToM (such as the Theory of Mind Inventory:Self-Report, @hutchins2021development).
+Furthermore, our application of feature reduction as a noise-elimination measure could have over-simplified the data.
 A more complex pattern of relationships, with different contributions of various subdimensions of ToM and interoception, could emerge provided a sufficient statistical power and valid measures.
@@
 Notably, our results provide princeps evidence that interoception could be a key - and overlooked - mechanism in deception.
+Furthermore, our findings extend and offer an alternate perspective to the debatable use of polygraphs, suggesting that its utility for lie detection is not only questionable, but could potentially enhance the deceptive ability of people with better interoception.
 

### 2023-10-02 1_Measures.Rmd
update

@@
 ```{r message=FALSE}
-df %>% 
-  group_by(Participant) %>% 
+
+bes_items <- read.csv("preprocessing/BES_processed.csv")
+bes_items |>   # Cognitive
+  select(Q3,Q6,Q9,Q10,Q12,Q14,Q16,Q19,Q20) |> 
+  cronbachs_alpha()
+bes_items |> 
+  select(Q1,Q2,Q4,Q5,Q7,Q8,Q11,Q13,Q15,Q17,Q18) |> 
+  cronbachs_alpha()
+```
+
+```{r message=FALSE}
+df |> 
+  group_by(Participant) |> 
   select(starts_with("BES_")) |> 
@@
 ```{r message=FALSE}
+items <- read.csv("preprocessing/MAIA2_processed.csv")
+# Noticing
+items |>  
+  select(Q1,Q2,Q3,Q4) |> 
+  performance::cronbachs_alpha()
+# Not-distracting
+items |>  
+  select(Q5,Q6,Q7,Q8,Q9,Q10) |> 
+  performance::cronbachs_alpha()
+# Not-worrying
+items |>  
+  select(Q11,Q12,Q13,Q14,Q15) |> 
+  performance::cronbachs_alpha()
+# AttentionRegulation
+items |>  
+  select(Q16,Q17,Q18,Q19,Q20,Q21,Q22) |> 
+  performance::cronbachs_alpha()
+# EmotionalAwareness
+items |>  
+  select(Q23,Q24,Q25,Q26,Q27) |> 
+  performance::cronbachs_alpha()
+# SelfRegulation
+items |>  
+  select(Q28,Q29,Q30,Q31) |> 
+  performance::cronbachs_alpha()
+# BodyListening
+items |>  
+  select(Q32,Q33,Q34) |> 
+  performance::cronbachs_alpha()
+# Trusting
+items |>  
+  select(Q35,Q36,Q37) |> 
+  performance::cronbachs_alpha()
+```
+
+```{r message=FALSE}
 df %>% 
@@
 ### LIE Scale
+
+```{r message=FALSE}
+items <- read.csv("preprocessing/LIE_processed.csv")
+# Ability
+items |>  
+  select(Q4,Q5,Q6,Q7) |> 
+  performance::cronbachs_alpha()
+# Frequency
+items |>  
+  select(Q1,Q2,Q3,Q8) |> 
+  performance::cronbachs_alpha()
+# Negativity
+items |>  
+  select(Q9,Q11,Q13,Q16) |> 
+  performance::cronbachs_alpha()
+# AContextuality
+items |>  
+  select(Q10,Q12,Q14,Q15) |> 
+  performance::cronbachs_alpha()
+```
 

### 2023-10-02 paper/manuscript.Rmd
update

@@
 ---
-title: '**The Heart can Lie: A Preliminary Analysis of the Role of Interoception and Theory of Mind in Deception**'
+title: '**The Heart can Lie: A Preliminary Investigation of the Role of Interoception and Theory of Mind in Deception**'
 shorttitle        : "Deception, Interoception, and ToM"
@@
   While a large part of the deception literature focuses on lying detection, the factors contributing to one's ability to lie remain unclear.
-The present study (n=26) examined the contribution of Theory of Mind (ToM) and interoception on our ability to lie using a directed lie paradigm with two conditions ("Interrogation" and "Polygraph"), designed to enhance each of the two mechanisms.
-In view of the relatively small sample size, we performed a feature reduction on the measures used to assess our two groups of predictor variables using factor analysis and extracted a unique factor of ToM as well as 4 components of interoception (*Metacognition*, *Listening*, *Focus* and *Regulation*).
-Using a mixed-design Bayesian analysis, we show that various facets of interoceptive abilities are positively related to the self-rated confidence in one's own lies, especially when under the belief that bodily signals are being monitored (i.e., in the "Polygraph" condition).
+The present study examined the contribution of Theory of Mind (ToM) and interoception on our ability to lie using a directed lie paradigm with two conditions ("Interrogation" and "Polygraph"), designed to enhance each of the two mechanisms.
+Given the relatively small sample size (n = 26 x 40 trials), special steps were taken to avoid false positives.
+Our results suggest that various facets of interoceptive abilities are positively related to the self-rated confidence in one's own lies, especially when under the belief that bodily signals are being monitored (i.e., in the "Polygraph" condition).
 Beyond providing evidence for the role of the body in lying and raising interesting questions for deception science, these results carry practical implications for criminology and lie detection protocols.
 output:
-  papaja::apa6_word:
+  papaja::apa6_pdf:
     keep_tex: yes
@@
 This begs the question of the potential role of interoceptive abilities in deception ability.
-Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing conceptualize interoception as a three-dimensional construct comprising three distinct facets, namely, interoceptive accuracy - the objective ability to monitor internal bodily signals; interoceptive sensibility - the subjective confidence in one's interoceptive accuracy; and interoceptive awareness (also referred to as interoceptive insight; @khalsa2018interoception) - one's ability to correctly evaluate their interoceptive ability.
+Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing conceptualize interoception as a three-dimensional construct comprising three distinct facets, namely, interoceptive accuracy - the objective ability to monitor internal bodily signals; interoceptive sensibility - the subjective confidence in one's interoceptive accuracy; and interoceptive awareness - the metacognitive ability to correctly evaluate one's interoceptive ability.
 Interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing, and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].
-In particular, neuroscientific findings investigating the correlates of interoception have underlined the potential role of the anterior cingulate cortex (ACC) and anterior insula (AI) [@wang2019anterior; @craig2009you; @critchley2004neural; @khalsa2009pathways], both of which are often thought to be activated during deception [@abe2011brain; @sip2008detecting; @baumgartner2013honest], and have been implicated in cognitive processes associated with deception (e.g., cognitive control [@molnar2022anterior], conflict detection [@kerns2004anterior]).
 
@@
 Given that deciding to lie generally involves a consideration of the potential costs of getting caught, and hence could also be perceived as risky behavior [@kireev2013possible], interoception could be construed to be negatively related to lying ability.
-However, some studies have instead found heightened interoceptive attention (one's self-focus towards internal bodily signals), to predict apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening].
+However, some studies have instead found heightened interoceptive attention (one's self-focus towards internal bodily signals), to predict immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening].
 Extending these findings to social cognition, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high, whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
@@
 
-30 university students from Singapore were recruited through posters, flyers, and online social media platforms. 
+30 university students from Singapore were recruited through posters, flyers, and online social media platforms, and rewarded with study credits for their time.
 <!-- Inclusion criteria included residing in Singapore, and an absence of current or history of neurological, psychiatric, or cardiovascular disorders.  -->
@@
 
-The Basic Empathy Scale [BES, @jolliffe2006development], a 20-item self-report questionnaire measuring two dimensions of empathy (cognitive and affective) using a 5-point Likert scale was administered.
+The Basic Empathy Scale [BES, @jolliffe2006development], a 20-item self-report questionnaire measuring two dimensions of empathy, namely Cognitive ($\alpha = 0.83$) and Affective ($\alpha = 0.82$) using a 5-point Likert scale was administered.
 Although ToM and empathy are regarded as distinct psychological constructs, previous research findings point to them being closely related [@gallant2020developing; @sebastian2012neural].
@@
 
-Given its multidimensional nature, the MAIA-2 [@mehling2012multidimensional], a 37-item questionnaire which measures 8 distinct facets of interoception including Noticing (**I notice when I am uncomfortable in my body**), Not-Distracting (**I try to ignore pain**), Not-Worrying (**I can stay calm and not worry when I have feelings of discomfort or pain**), Attention Regulation (**I can refocus my attention from thinking to sensing my body**), Emotional Awareness (**I notice how my body changes when I am angry**), Self-Regulation (**I can use my breath to reduce tension**), Body Listening (**I listen to information from my body about my emotional state**), and Trust (**I trust my body sensations**), using 5-point Likert scales, was also administered.
+Given its multidimensional nature, the MAIA-2 [@mehling2012multidimensional], a 37-item questionnaire which measures 8 distinct facets of interoception including Noticing (e.g., *I notice when I am uncomfortable in my body*; $\alpha = 0.70$), Not-Distracting (e.g., *I try to ignore pain*; $\alpha = 0.87$), Not-Worrying (e.g., *I can stay calm and not worry when I have feelings of discomfort or pain*; $\alpha = 0.68$), Attention Regulation (e.g., *I can refocus my attention from thinking to sensing my body*; $\alpha = 0.85$), Emotional Awareness (e.g., *I notice how my body changes when I am angry*; $\alpha = 0.75$), Self-Regulation (e.g., *I can use my breath to reduce tension*; $\alpha = 0.62$), Body Listening (e.g., *I listen to information from my body about my emotional state*; $\alpha = 0.88$), and Trust (e.g., *I trust my body sensations*; $\alpha = 0.89$), using 5-point Likert scales, was also administered.
 
@@
 
-Using PsychoPy [@peirce2019psychopy2], we implemented a directed-lying task in which participants were instructed to answer 80 questions pertaining to their personal preferences and subjective experiences, by either lying or telling the truth (depending on whether they see "lie" or "truth" written on the screen).
-Importantly, they were told that for half of the trials, they would have to convince another participant that would be observing them from a separate room via a webcam connection (*Interrogation* condition).
+Using PsychoPy [@peirce2019psychopy2], we implemented a directed-lying task in which participants were instructed to briefly answer 80 questions [taken from the Autobiographical Memory Questionnaire - AMQ, @rubin2003belief] pertaining to their personal preferences and subjective experiences, by either lying or telling the truth (depending on whether they see "lie" or "truth" written on the screen).
+Their goal was to make convincing answers, so that truths would be judged as truths by the receiver, and lies as lies.
+The nature of the receiver was different depending on the condition: participants were told that for half of the trials, they would have to convince another participant that would be observing them from a separate room (COVID regulations were used as a justification) via a webcam connection (*Interrogation* condition).
 For the remaining trials, participants were tasked to convince a "lie detection machine" that would be assessing their behaviour through their physiological signals (*Polygraph* condition).
+In reality, there was no real "receiver" and their answers were not judged externally (the study focused on their subjective ratings and reactions).
 The two conditions were presented in a counter-balanced order, and each comprised of 40 trials (20 truth; 20 lies).
@@
 
-Finally, on top of the deception task, we also measured participants' self-reported tendency to lie in their everyday life using the *Lie Scale* [@makowski2021structure], a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency).
+Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies or truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the change in heart rate associated with the response (within a window of 3.5 s).
+
+Finally, on top of the deception task, we also measured participants' self-reported tendency to lie in their everyday life using the *Lie Scale* [@makowski2021structure], a 16-item questionnaire that assesses 4 dispositional lying dimensions - Ability ($\alpha = 0.92$), Frequency ($\alpha = 0.66$), Negativity ($\alpha = 0.66$), and Contextuality ($\alpha = 0.70$).
 
@@
 During session 1, participants answered a brief demographic survey as well as a questionnaire regarding their personal preferences and subjective experiences (Autobiographical Memory Questionnaire, AMQ), followed by a series of psychological scales (i.e., BES, MAIA and Lie scale), which were randomly displayed.
-During session 2, cognitive-behavioural tasks (i.e., the deception task, HCT and the Yoni task) were administered to participants while their physiological signals (including cardiac activity (ECG), respiration (RSP) and electrodermal activity (EDA)) were being recorded.
+
+During session 2, performed about one week later, the 3 cognitive-behavioural tasks (i.e., the deception task, HCT and the Yoni task) were administered to participants while their physiological signals (including cardiac activity - ECG, respiration -RSP, and electrodermal activity - EDA) were being recorded.
 The physiological recording devices were set up as follows: ECG was recorded with 3 electrodes placed according to a modified Lead II configuration [@takuma1995alternative], and respiration was measured using a respiration belt.
 All signals were recorded at 1000Hz via the BioPac MP160 system (BioPac Systems Inc., USA).
+
 For all participants, session 2 began with the deception task, followed by the Yoni task and the HCT, with the latter two presented in a randomized order.
-In the directed-lying task, items in the AMQ were presented as stimuli, with participants' recorded responses (in session 1) used to establish the ground truth.
-Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the change in heart rate associated with the response (within a window of 3.5 s).
+In the directed-lying task, items of the AMQ were presented as stimuli, with participants' recorded responses (in session 1) used to establish the ground truth.
 
@@
 
-The data analysis was carried out using *R 4.2* [@RCoreTeam2022], *brms* [@Burkner2017], and the *easystats* collection of packages [@makowski2019bayestestr; @correlationArticle; @performanceArticle; @insightArticle], and the physiological signal processing was done using the default routines avaialble in *NeuroKit2* [@makowski2021neurokit2].
+The data analysis was carried out using *R 4.2* [@RCoreTeam2022], *brms* [@Burkner2017], and the *easystats* collection of packages [@makowski2019bayestestr; @correlationArticle; @performanceArticle; @insightArticle], and the physiological signal processing was done using the default routines available in *NeuroKit2* [@makowski2021neurokit2].
 Note that EDA was not further analyzed as most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (with dry air-con air) of the experimental room.
@@
 Compared to truth, lies were rated with less confidence ($\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%$), but no significant difference between the conditions was found.
-On the other hand, the RT did not differ between truth and lies, but was significantly slower in the polygraph condition for both conditions ($\Delta=0.25,~95\%~CI~[0.62, 0.41],~pd = 100\%$).
-The heart rate was significantly more elevated during lies as compared to truth ($\Delta=1.16,~95\%~CI~[0.57, 1.73],~pd = 100\%$), and during interrogation as compared to the polygraph condition ($\Delta=4.84 ,~95\%~CI~[4.23, 5.44],~pd = 100\%$).
+On the other hand, the RT did not differ between truth and lies, but was significantly slower in the polygraph condition for both conditions ($\Delta=0.25$, 95\% CI [0.62, 0.41], pd = 100\%).
+The heart rate was significantly more elevated during lies as compared to truth ($\Delta=1.16$, 95\% CI [0.57, 1.73], pd = 100\%), and during interrogation as compared to the polygraph condition ($\Delta=4.84$, 95\% CI [4.23, 5.44], pd = 100\%).
 
-The indirect phrasing of the question only had a significant effect on RT ($\beta=0.36,~95\%~CI~[0.21, 0.51],~pd = 100\%$), leading to slower answers, regardless of whether they were lies or truths.
+The indirect phrasing of the question only had a significant effect on RT ($\beta=0.36$, 95\% CI [0.21, 0.51], pd = 100\%), leading to slower answers, regardless of whether they were lies or truths.
+Given this absence of interaction with the type of answers in any modality, this factor was not included in subsequent analysis.
 
@@
 
-The composite *ToM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67\%$), specifically in the polygraph condition.
+The composite *ToM* score was significantly associated with less confident ($\beta=-0.19$, 95\% CI [-0.36, -0.02], pd = 98.47\%) and slower lies ($\beta=0.42$, 95\% CI [0.01, 0.83], pd = 97.67\%), specifically in the polygraph condition.
 No significant effect was found with regards to heart rate, and no correlation was observed with dispositional lying traits (**Figure 1**).
@@
 This points toward a predominantly meta-cognitive effect without necessarily an actual bodily regulation (i.e., participants with good interoception feel that their lies are more convincing, but do not actively attenuate their bodily reactions).
+
+Another possibility that should be tested in the future is that of a mediating role of executive functions, given their positive association with interoception [@molnar2022anterior].
+For instance, neuroscientific findings investigating the correlates of interoception have underlined the potential role of the anterior cingulate cortex (ACC) and anterior insula (AI) [@wang2019anterior; @craig2009you; @critchley2004neural; @khalsa2009pathways], both of which are often thought to be activated during deception [@abe2011brain; @sip2008detecting; @baumgartner2013honest], and have been implicated in cognitive processes associated with deception [such as cognitive control, @molnar2022anterior; or conflict detection, @kerns2004anterior].
+It is thus possible that the positive relationship between interoceptive abilities and deception is at least partially mediated by cognitive control abilities.
+
 <!-- [**also consistent with research demonstrating distinctions between interoceptive awareness and accuracy; extends pevious research in which individuals with greater interoceptive sensibility and accuracy were not better at detecting lies.**] -->
@@
 <!-- Limitations and Future Research -->
-Although yielding promising results, this exploratory study is limited by the sample size.
+Although yielding promising results, the sample size of this exploratory study is a source of concern.
 Although we tried to mitigate it by 1) extracting more robust variables (by combining multiple ones by means of feature reduction) and 2) using a suited analysis approach (Bayesian statistics with informative priors), future replication studies with larger samples are warranted to confirm this first investigation.
@@
 The statistical power could also explain the overall lack of results found in relation to heart rate, which has a higher signal-to-noise ratio as compared to subjective reports (such as confidence scales).
+Additionally, one has to note that the participants did not have strong incentive for lying (there was no risk of losing the "reward" - i.e., student credits), which might have further decreased the potential effect sizes.
 
@@
 
-Additionally, pertaining to the limitations with regards to the measure of lying ability, care has to be given to the measure of the predictor constructs, namely ToM and interoception.
+Additionally to the limitations pertaining to the measure of lying ability, some also concern the measure of the predictor constructs, namely ToM and interoception.
 While we tried to include a behavioral task as well as a subjective questionnaire for each, it has to be underlined that they are notoriously difficult concepts to measure.
@@
 Moreover, although the cognitive and affective components of ToM and empathy share overlaps in the current literature, and there is no consensus regarding how the two concepts should be delineated, recent evidence nonetheless suggests ToM and empathy are necessarily distinct constructs with separable underlying mechanisms [@kanske2015dissecting].
-As such, future studies are warranted to further investigate the associations between ToM and lying ability using validated instruments sensitive to measuring ToM (such as the Theory of Mind Inventory:Self-Report, @hutchins2021development).
+As such, future studies are warranted to further investigate the associations between ToM and lying ability using validated instruments sensitive to measuring ToM [such as the Theory of Mind Inventory, @hutchins2021development].
 Furthermore, our application of feature reduction as a noise-elimination measure could have over-simplified the data.
@@
 In conclusion, this study is a first step towards assessing the contribution of ToM and interoception abilities in deception, particularly in one's ability to lie convincingly.
-To this end, we introduced a new paradigm that is able to modulate the contribution of these mechanisms while remaining relevant to applied fields of lie detection and criminology (in which the experimental conditions find echoing practices).
-Notably, our results provide princeps evidence that interoception could be a key - and overlooked - mechanism in deception.
-Furthermore, our findings extend and offer an alternate perspective to the debatable use of polygraphs, suggesting that its utility for lie detection is not only questionable, but could potentially enhance the deceptive ability of people with better interoception.
+To this end, we introduced a new paradigm to delineate the contribution of these mechanisms while remaining relevant to applied fields of lie detection and criminology (in which the experimental conditions find echoing practices).
+Notably, our results provide some evidence that interoception could be an important - and overlooked - process involved in deception.
+Furthermore, our findings extend and offer an alternate perspective to the debatable use of polygraphs, suggesting that its utility for lie detection is not only questionable, but could potentially selectively modulate deceptive skills depending on the cognitive and interoceptive profile of the participant.
 

### 2023-10-02 paper/manuscript.tex
update

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 {}{\PatchFailed}
-\keywords{Deception, Interoception, Theory of Mind, Poygraph, Lying Ability\newline\indent Word count: 3720}
+\keywords{Deception; Interoception; Theory of Mind; Poygraph; Lying Ability\newline\indent Word count: 5004}
 \usepackage{lineno}
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
-  pdftitle={The Heart can Lie: The Role of Interoception and Theory of Mind in Deception},
+  pdftitle={The Heart can Lie: A Preliminary Investigation of the Role of Interoception and Theory of Mind in Deception},
   pdflang={en-EN},
-  pdfkeywords={Deception, Interoception, Theory of Mind, Poygraph, Lying Ability},
+  pdfkeywords={Deception; Interoception; Theory of Mind; Poygraph; Lying Ability},
   hidelinks,
@@
 
-\title{\textbf{The Heart can Lie: The Role of Interoception and Theory of Mind in Deception}}
+\title{\textbf{The Heart can Lie: A Preliminary Investigation of the Role of Interoception and Theory of Mind in Deception}}
 \author{Dominique Makowski\textsuperscript{1, 2}, Zen J.
@@
 The authors made the following contributions.
-Dominique Makowski: Conceptualization, Data curation, Formal Analysis, Funding acquisition, Investigation, Methodology, Project administration, Resources, Software, Supervision, Validation, Visualization, Writing -- original draft; An Shu Te: Project administration, Resources, Investigation, Writing -- original draft; Stephanie Kirk: Project administration, Resources, Writing -- original draft; Claudia Liauw: Data curation, Formal Analysis; S.H.
+Dominique Makowski: Conceptualization, Data curation, Formal Analysis, Funding acquisition, Investigation, Methodology, Project administration, Resources, Software, Supervision, Validation, Visualization, Writing -- original draft; Zen J.
+Lau: Data curation, Project administration, Resources, Investigation; Tam Pham: Data curation, Project administration, Resources, Investigation; An Shu Te: Project administration, Resources, Investigation, Writing -- original draft; Stephanie Kirk: Project administration, Resources, Writing -- original draft; Claudia Liauw: Data curation, Formal Analysis; S.H.
 Annabel Chen: Project administration, Supervision, Writing -- review \& editing.
@@
 The present study examined the contribution of Theory of Mind (ToM) and interoception on our ability to lie using a directed lie paradigm with two conditions (``Interrogation'' and ``Polygraph''), designed to enhance each of the two mechanisms.
-Using a mixed-design Bayesian analysis, we show that various facets of interoceptive abilities are positively related to the self-rated confidence in one's own lies, especially when under the belief that bodily signals are being monitored (i.e., in the ``Polygraph'' condition).
+Given the relatively small sample size (n = 26 x 40 trials), special steps were taken to avoid false positives.
+Our results suggest that various facets of interoceptive abilities are positively related to the self-rated confidence in one's own lies, especially when under the belief that bodily signals are being monitored (i.e., in the ``Polygraph'' condition).
 Beyond providing evidence for the role of the body in lying and raising interesting questions for deception science, these results carry practical implications for criminology and lie detection protocols.
@@
 Lying - the intentional attempt at instilling a false belief in others (Sip et al., 2012) - is a prevalent phenomenon carrying potentially important consequences.
-Interestingly, evidence suggests that the successful detection of a lying attempt depends more on the ability of the liar, than on the performance of the lie detector (Bond Jr \& DePaulo, 2008; Levine et al., 2011; Verigin et al., 2019).
+Interestingly, evidence suggests that the successful detection of a lying attempt depends more on the ability of the liar, than on the performance of the lie detector (Bond Jr \& DePaulo, 2008; T.
+R.
+Levine et al., 2011; Verigin et al., 2019).
 However, with most of the deception literature focused on deception detection (Masip, 2017; Sternglanz et al., 2019; Viji et al., 2022), the factors contributing to one's ability to lie remain unclear.
+Nevertheless, some findings suggest a relationship between the propensity to tell lies, and traits that characterize the socially malevolent profile known as the Dark Triad (Paulhus \& Williams, 2002), such as narcissism (Zvi \& Elaad, 2018) and psychopathy (Rassin et al., 2023).
+While often conceptualized to be immoral and unconscionable, lying is ubiquitous in everyday life, and being able to lie skillfully can sometimes facilitate interpersonal relationships, helping us avoid conflict or causing emotional harm to others (E.
+E.
+Levine \& Lupoli, 2022).
+In fact, recent research shows that certain forms of deception, such as prosocial lies (i.e., false statements told to benefit others; E.
+E.
+Levine and Lupoli (2022)), can increase trust (E.
+E.
+Levine \& Schweitzer, 2015).
+Moreover, individuals who told altruistic lies were perceived as more benevolent than those who were honest (E.
+E.
+Levine \& Schweitzer, 2014).
 
@@
 Broadly defined as one's sensitivity to their own internal signals and bodily states (Chen et al., 2021; Murphy et al., 2019; Weiss et al., 2014), Garfinkel et al.
-(2015)'s conceptualizes interoception as a three-dimensional construct comprising three distinct facets, namely, interoceptive accuracy - the objective ability to monitor internal bodily signals; interoceptive sensibility - the subjective confidence in one's interoceptive accuracy; and interoceptive awareness - one's ability to identify and appropriately respond to their perceived interoceptive states.
+(2015) conceptualize interoception as a three-dimensional construct comprising three distinct facets, namely, interoceptive accuracy - the objective ability to monitor internal bodily signals; interoceptive sensibility - the subjective confidence in one's interoceptive accuracy; and interoceptive awareness - the metacognitive ability to correctly evaluate one's interoceptive ability.
 Interoception has increasingly been tied to subjective perceptual experiences (Connell et al., 2018; Seth et al., 2012), as well as individual differences in executive functions, emotional processing, and decision-making (Barrett \& Simmons, 2015; Murphy et al., 2019; Petzschner et al., 2021).
+
 Although few studies exist that investigate the relationship between interoception and deceptive ability \emph{per se}, previous decision-making studies have demonstrated a negative correlation between interoceptive awareness, a metacognitive dimension of interoception, and one's likelihood to make risky decisions (Dunn et al., 2010; Furman et al., 2013).
-In fact, this is consistent with the somatic marker hypothesis, which posits an association between interoception and a propensity towards making rational decisions (Damasio, 1996).
-
-In contrast, however, some studies have instead found heightened interoceptive attention (one's self-focus towards internal bodily signals), to predict apathetic, immoral behaviour, such as cheating (Ditto et al., 2006; Lenggenhager et al., 2013; Williams et al., 2016).
+This is in line with the somatic marker hypothesis, which posits that an accurate evaluation of one's bodily signals facilitates the use of such interoceptive feedback to guide rational decision making (Damasio, 1996).
+Indeed, Sugawara et al.
+(2020) further reports that individuals who received interoceptive training were more likely to show higher interoceptive accuracy and make reasoned decisions.
+Given that deciding to lie generally involves a consideration of the potential costs of getting caught, and hence could also be perceived as risky behavior (Kireev et al., 2013), interoception could be construed to be negatively related to lying ability.
+However, some studies have instead found heightened interoceptive attention (one's self-focus towards internal bodily signals), to predict immoral behaviour, such as cheating (Ditto et al., 2006; Lenggenhager et al., 2013; Williams et al., 2016).
 Extending these findings to social cognition, Vabba et al.
@@
 The \emph{Interrogation} condition was designed to emphasize (and preferentially mobilize) ToM-related mechanisms, whereas the \emph{Polygraph} condition was designed to emphasize interoceptive mechanisms.
-We expected ToM and interoception to positively predict lying ability (i.e., higher lie confidence, shorter response time and lower physiological arousal), in particular in the \emph{Polygraph} and the \emph{Interrogation} condition, respectively.
+In particular, we expected lying ability (i.e., higher lie confidence, shorter response time and lower physiological arousal), to be positively predicted by individuals' interoceptive abilities in the \emph{Polygraph} condition, and by ToM skills in the \emph{Interrogation} condition.
+Consistent with the cognitive load approach outlined in several theories of deception (such as the Four-Factor Theory (Riggio et al., 1987) and Activation-Decision-Construction Model (Walczyk et al., 2014)), as well as previous findings which suggest response time as a reliable cue to deception (Gonzalez-Billandon et al., 2019; Walczyk et al., 2009), we regarded shorter response times as a proxy of better lying ability.
 
@@
 
-30 university students from Singapore were recruited through posters, flyers, and online social media platforms.
+30 university students from Singapore were recruited through posters, flyers, and online social media platforms, and rewarded with study credits for their time.
 Four participants were excluded as their data was not recorded due to technical issues.
-The final sample consists 26 participants (Mean age = 20.9, SD = 2.0, range:{[}18, 25{]}, Sex: 65.4\% women, 34.6\% men).
+The final sample consists of 26 participants (Mean age = 20.9, SD = 2.0, range:{[}18, 25{]}, Sex: 65.4\% women, 34.6\% men).
 The heart rate of one participant and response time of one participant were excluded from further analysis due to extreme outlying values.
+To maximize statistical power, the problematic data from these 2 participants were only excluded from analyses involving those measures; all other data were retained for analyses.
 
@@
 
-\hypertarget{theory-of-mind}{%
-\subsubsection{Theory of Mind}\label{theory-of-mind}}
+\hypertarget{theory-of-mind-tom}{%
+\subsubsection{Theory of Mind (ToM)}\label{theory-of-mind-tom}}
 
 Two measures of ToM and its related constructs were administered.
-The Yoni Task (Shamay-Tsoory \& Aharon-Peretz, 2007) is a behavioral task in which participants are presented with the face of a character named ``Yoni'', surrounded by 4 colored pictures of objects or faces.
-In total, each participant completed 101 trials - 49 trials assessing their affective TOM abilities, 37 trials assessing their cognitive TOM abilities and 15 control trials.
-During each trial, participants were shown a question and asked to make responses based on specific cues such as directions of Yoni's eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical TOM).
+The Yoni Task (Shamay-Tsoory \& Aharon-Peretz, 2007) is a behavioral task which assesses first and second-order ToM abilities in both cognitive and affective domains.
+Participants were presented with the face of a character named ``Yoni'', surrounded by 4 colored pictures of objects or faces, one in each corner of the screen.
+In total, each participant completed 101 trials - 49 trials assessing their affective ToM abilities, 37 trials assessing their cognitive ToM abilities and 15 control trials.
+During each trial, participants were shown a question pertaining the item Yoni is referring to, and asked to make responses based on specific corresponding cues such as the directions of Yoni's eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical ToM).
+More specifically, in first-order trials, participants were instructed to make inferences about Yoni's mental state with regards to the objects surrounding it (e.g., ``Yoni is thinking of\ldots{}'').
+In more complex second-order trials, participants had to correctly infer the interaction between Yoni and others' mental states (e.g., Yoni is thinking of the fruit that \ldots{} wants'').
 
-The Basic Empathy Scale (BES, Jolliffe \& Farrington, 2006), a 20-item questionnaire measuring two dimensions of empathy (cognitive and affective) using a 5-point Likert scale was administered.
+The Basic Empathy Scale (BES, Jolliffe \& Farrington, 2006), a 20-item self-report questionnaire measuring two dimensions of empathy, namely Cognitive (\(\alpha = 0.83\)) and Affective (\(\alpha = 0.82\)) using a 5-point Likert scale was administered.
 Although ToM and empathy are regarded as distinct psychological constructs, previous research findings point to them being closely related (Gallant et al., 2020; Sebastian et al., 2012).
+Specifically, empathy is often thought to be an integral component in the affective dimension of ToM (i.e., the ability to infer what someone else is feeling) (Shamay-Tsoory et al., 2010).
 
@@
 
-The MAIA-2 (Mehling et al., 2012), a 32-item questionnaire which measures 8 dimensions of interoception (Noticing, Not-Distracting, Not-Worrying, Attention, Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust) using 5-point Likert scales, was also administered.
+Given its multidimensional nature, the MAIA-2 (Mehling et al., 2012), a 37-item questionnaire which measures 8 distinct facets of interoception including Noticing (e.g., \emph{I notice when I am uncomfortable in my body}; \(\alpha = 0.70\)), Not-Distracting (e.g., \emph{I try to ignore pain}; \(\alpha = 0.87\)), Not-Worrying (e.g., \emph{I can stay calm and not worry when I have feelings of discomfort or pain}; \(\alpha = 0.68\)), Attention Regulation (e.g., \emph{I can refocus my attention from thinking to sensing my body}; \(\alpha = 0.85\)), Emotional Awareness (e.g., \emph{I notice how my body changes when I am angry}; \(\alpha = 0.75\)), Self-Regulation (e.g., \emph{I can use my breath to reduce tension}; \(\alpha = 0.62\)), Body Listening (e.g., \emph{I listen to information from my body about my emotional state}; \(\alpha = 0.88\)), and Trust (e.g., \emph{I trust my body sensations}; \(\alpha = 0.89\)), using 5-point Likert scales, was also administered.
 
@@
 
-Using PsychoPy (Peirce et al., 2019), we implemented a directed-lying task in which participants were instructed to answer 80 questions by either lying or telling the truth (depending on whether they see ``lie'' or ``truth'' written on the screen).
-Importantly, they were told that for half of the trials, they would have to convince another participant that would be observing them from a separate room via a webcam connection (\emph{Interrogation} condition).
+Using PsychoPy (Peirce et al., 2019), we implemented a directed-lying task in which participants were instructed to briefly answer 80 questions (taken from the Autobiographical Memory Questionnaire - AMQ, Rubin et al., 2003) pertaining to their personal preferences and subjective experiences, by either lying or telling the truth (depending on whether they see ``lie'' or ``truth'' written on the screen).
+Their goal was to make convincing answers, so that truths would be judged as truths by the receiver, and lies as lies.
+The nature of the receiver was different depending on the condition: participants were told that for half of the trials, they would have to convince another participant that would be observing them from a separate room (COVID regulations were used as a justification) via a webcam connection (\emph{Interrogation} condition).
 For the remaining trials, participants were tasked to convince a ``lie detection machine'' that would be assessing their behaviour through their physiological signals (\emph{Polygraph} condition).
+In reality, there was no real ``receiver'' and their answers were not judged externally (the study focused on their subjective ratings and reactions).
 The two conditions were presented in a counter-balanced order, and each comprised of 40 trials (20 truth; 20 lies).
@@
 The sequence of each trial was the same for both conditions.
-Participants were instructed to respond to a question shown on a computer screen, phrased either directly (e.g., ``What is your favourite sport?''), or indirectly (e.g., ``Is your favourite sport Hockey?''), by verbally lying or telling the truth (for half of the trials in each condition, i.e., n = 20).
-Following a short interval (0.7 - 1.5s) for response preparation, during which ``Connecting\ldots{}'' was shown on the screen, a social or bio-feedback cue (for \emph{Interrogation} and \emph{Polygraph} conditions respectively) was displayed for a maximum of 10s.
-Participants then had to provide their answers verbally, and pressed the space key to signify the end of their response.
-After another short interval (1.5-2.5s), during which ``Disconnecting'' was written on the screen, participants were asked to rate their confidence in how convincing (i.e., likely to get judged as truthful) they perceived their response to be on a visual analog scale.
+Participants were first instructed to respond to a question shown on a computer screen by verbally lying or telling the truth (for half of the trials in each condition, i.e., n = 20).
+In addition, as past studies have found associations between lying behaviour and type of question phrasing (Walczyk \& Cockrell, 2022), each question was phrased either directly (e.g., ``What is your favourite sport?''), or indirectly (e.g., ``Is your favourite sport Hockey?'') to reduce possible confounding effects.
+Following a short interval (0.7 - 1.5s) to allow time for response preparation, during which ``Connecting\ldots{}'' was shown on the screen, a social or bio-feedback cue (for \emph{Interrogation} and \emph{Polygraph} conditions respectively) was displayed for a maximum of 10s or until a response was given.
+Specifically, participants had to provide their answers verbally, and pressed the space key to signify the end of their response.
+After another short interval (1.5-2.5s), during which ``Disconnecting\ldots{}'' was presented on the screen, participants were asked to rate their confidence in how convincing (i.e., likely to get judged as truthful) they perceived their response to be on a visual analog scale.
 
@@
 
-In the \emph{Polygraph} condition, participants had to provide their answer while receiving biofeedback in the form of physiological signals (ECG, EDA and Respiration) being recorded.
-Participants were informed that they were being shown live feedback of their own physiological activity.
+In the \emph{Polygraph} condition, participants had to provide their answer while receiving bio-feedback in the form of physiological signals (ECG, EDA and Respiration), of which they were informed was live feedback of their own physiological activity.
 In actuality, we displayed pre-recorded video clips of a confederate's physiological signals.
-All participants reported believing that it was indeed their own signals being shown during the debriefing.
+All participants reported believing that their own signals were shown during the debriefing.
 
-Finally, on top of the deception task, we also measured participants' self-reported tendency to lie in their everyday life using the \emph{Lie Scale} (Makowski, Pham, Lau, Raine, et al., 2021), a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency).
+Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies or truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the change in heart rate associated with the response (within a window of 3.5 s).
+
+Finally, on top of the deception task, we also measured participants' self-reported tendency to lie in their everyday life using the \emph{Lie Scale} (Makowski, Pham, Lau, Raine, et al., 2021), a 16-item questionnaire that assesses 4 dispositional lying dimensions - Ability (\(\alpha = 0.92\)), Frequency (\(\alpha = 0.66\)), Negativity (\(\alpha = 0.66\)), and Contextuality (\(\alpha = 0.70\)).
 
@@
 
-This study is comprised of 2 sessions.
-During session 1, participants answered a brief demographic survey before the questionnaires, which were presented in a randomized order.
-During session 2, cognitive-behavioural tasks were administered to participants while their physiological signals (including cardiac activity (ECG), respiration (RSP) and electrodermal activity (EDA)) were being recorded.
+A within-subjects design was used in the present study, which is comprised of 2 sessions, to investigate the roles interoception and ToM play in lying ability.
+During session 1, participants answered a brief demographic survey as well as a questionnaire regarding their personal preferences and subjective experiences (Autobiographical Memory Questionnaire, AMQ), followed by a series of psychological scales (i.e., BES, MAIA and Lie scale), which were randomly displayed.
+
+During session 2, performed about one week later, the 3 cognitive-behavioural tasks (i.e., the deception task, HCT and the Yoni task) were administered to participants while their physiological signals (including cardiac activity - ECG, respiration -RSP, and electrodermal activity - EDA) were being recorded.
 The physiological recording devices were set up as follows: ECG was recorded with 3 electrodes placed according to a modified Lead II configuration (Takuma et al., 1995), and respiration was measured using a respiration belt.
 All signals were recorded at 1000Hz via the BioPac MP160 system (BioPac Systems Inc., USA).
-For all participants, session 2 began with the deception task, followed by the YONI task and the HCT, with the latter two presented in a randomized order.
-Three outcome variables were recorded for each trial of the deception task, namely the participants' confidence ratings that their answers (lies \emph{vs.} truths) were convincing, the response time (RT) between the question onset and the participant's key press (indicating the end of their verbal answer), and the heart rate change associated with the response (within a window of 3.5 s).
+
+For all participants, session 2 began with the deception task, followed by the Yoni task and the HCT, with the latter two presented in a randomized order.
+In the directed-lying task, items of the AMQ were presented as stimuli, with participants' recorded responses (in session 1) used to establish the ground truth.
 
@@
 Finally, we investigated the relationship between the deception scale traits, and the ToM and interoception scores using Bayesian correlations.
-As all the analyses and data has been made available, we will in the manuscript focus on significant, i.e., - in this context - statistically reliable and in our opinion theoretically relevant.
+As all the analyses and data have been made available, we will in the manuscript focus on significant, i.e., - in this context - statistically reliable and in our opinion theoretically relevant.
 
-The data analysis was carried out using \emph{R 4.2} (R Core Team, 2022), \emph{brms} (Bürkner, 2017), and the \emph{easystats} collection of packages (Lüdecke et al., 2021, 2019; Makowski et al., 2020, 2019), and the physiological signal processing was done using the default routines avaialble in \emph{NeuroKit2} (Makowski, Pham, Lau, Brammer, et al., 2021).
+The data analysis was carried out using \emph{R 4.2} (R Core Team, 2022), \emph{brms} (Bürkner, 2017), and the \emph{easystats} collection of packages (Lüdecke et al., 2019, 2021; Makowski et al., 2019, 2020), and the physiological signal processing was done using the default routines available in \emph{NeuroKit2} (Makowski, Pham, Lau, Brammer, et al., 2021).
 Note that EDA was not further analyzed as most participants did not yield any skin conductance responses - which we believe was partly caused by the low temperature (with dry air-con air) of the experimental room.
 
-The analysis was not pre-registered (stemming out from a student's project), but the full reproducible analysis script, statistical results report, and data, are available at
+The analysis was not pre-registered (stemming out from an undergraduate's final year project), but the full reproducible analysis script, statistical results report, and data, are available at
 \textbf{{[}masked for blinding{]}}
@@
 Compared to truth, lies were rated with less confidence (\(\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%\)), but no significant difference between the conditions was found.
-On the other hand, the RT did not differ between truth and lies, but was significantly slower in the polygraph condition for both conditions (\(\Delta=0.25,~95\%~CI~[0.62, 0.41],~pd = 100\%\)).
-The heart rate was significantly more elevated during lies as compared to truth (\(\Delta=1.16,~95\%~CI~[0.57, 1.73],~pd = 100\%\)), and during interrogation as compared to the polygraph condition (\(\Delta=4.84 ,~95\%~CI~[4.23, 5.44],~pd = 100\%\)).
+On the other hand, the RT did not differ between truth and lies, but was significantly slower in the polygraph condition for both conditions (\(\Delta=0.25\), 95\% CI {[}0.62, 0.41{]}, pd = 100\%).
+The heart rate was significantly more elevated during lies as compared to truth (\(\Delta=1.16\), 95\% CI {[}0.57, 1.73{]}, pd = 100\%), and during interrogation as compared to the polygraph condition (\(\Delta=4.84\), 95\% CI {[}4.23, 5.44{]}, pd = 100\%).
 
-The indirect phrasing of the question only had a significant effect on RT (\(\beta=0.36,~95\%~CI~[0.21, 0.51],~pd = 100\%\)), leading to slower answers, regardless of whether they were lies or truths.
+The indirect phrasing of the question only had a significant effect on RT (\(\beta=0.36\), 95\% CI {[}0.21, 0.51{]}, pd = 100\%), leading to slower answers, regardless of whether they were lies or truths.
+Given this absence of interaction with the type of answers in any modality, this factor was not included in subsequent analysis.
 
@@
 
-The 3 YONI-task dimensions and the 2 BES traits were combined into a unique factor, labelled \emph{TOM} (explaining 35.76\% of variance).
-It was loaded by the cognitive (.89), affective (.77), physical (.45) YONI dimensions, and the affective (.41) and cognitive (.17) facets of the BES.
+The 3 Yoni-task dimensions and the 2 BES traits were combined into a unique factor, labelled \emph{ToM} (explaining 35.76\% of variance).
+It was loaded by the cognitive (.89), affective (.77), physical (.45) Yoni dimensions, and the affective (.41) and cognitive (.17) facets of the BES.
 
@@
 
-\hypertarget{theory-of-mind-1}{%
-\subsection{Theory of Mind}\label{theory-of-mind-1}}
+\hypertarget{theory-of-mind}{%
+\subsection{Theory of Mind}\label{theory-of-mind}}
 
-The composite \emph{TOM} score was significantly associated with less confident (\(\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%\)) and slower lies (\(\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67\%\)), specifically in the polygraph condition.
+The composite \emph{ToM} score was significantly associated with less confident (\(\beta=-0.19\), 95\% CI {[}-0.36, -0.02{]}, pd = 98.47\%) and slower lies (\(\beta=0.42\), 95\% CI {[}0.01, 0.83{]}, pd = 97.67\%), specifically in the polygraph condition.
 No significant effect was found with regards to heart rate, and no correlation was observed with dispositional lying traits (\textbf{Figure 1}).
@@
 This is consistent with previous deception detection studies, in which participants' spontaneous lying behaviour only decreased when they were given feedback by a polygraph machine, but not when no feedback was given (Peleg et al., 2019).
-Additionally, our study also extends past deception research and further confirms the validity concerns in solely relying on physiological measures as an indicator of deception (Oviatt et al., 2018; Rosky, 2013).
+By extension, our study adds to the controversial discourse surrounding the use of physiological measures in past deception research, further questioning its validity as an indicator of deception (Oviatt et al., 2018; Rosky, 2013).
 
 Our results suggest that higher ToM abilities were related to slower and less confident lies, but only in the polygraph condition.
+While previous bodies of work have reported mixed findings regarding the association between interoception and ToM (Chiou \& Lee, 2013; Gendolla \& Wicklund, 2009; Scaffidi Abbate et al., 2016; Wundrack \& Specht, 2023), our results suggest the two are negatively linked.
 One possible interpretation of our findings is that people with stronger ToM abilities by default rely more on their social skills and altercentric inference when lying (i.e., they focus on - and try to read - the other person).
 When that mechanism is unavailable or unsuited (e.g., when there is no person to lie to - but a ``machine'' in our case), their corresponding lying ability decreases.
-In light of the current field of mixed findings relating interoception and ToM (Canino et al., 2022; Gao et al., 2019; Miller, 2015; Shah et al., 2017), future studies are necessary to investigate the interaction of these mechanisms in different social contexts.
+However, in light of the current field of mixed findings relating interoception and ToM (Canino et al., 2022; Gao et al., 2019; Miller, 2015; Shah et al., 2017), future studies are necessary to investigate the interaction of these mechanisms in different social contexts.
 
-We also showed that interoceptive abilities are correlated with a higher confidence in one's lies in the polygraph condition, a condition in which the attention towards internal reactions is fostered.
+We also showed that interoceptive abilities (as indicated by the composite interoception scores) are correlated with a higher confidence in one's lies in the polygraph condition, a condition in which the attention towards internal reactions is fostered.
+Indeed, this is in line with previous studies that found individuals with low interoception were more averse to risk when reputational stakes were high, telling fewer egoistical lies (Vabba et al., 2022).
+In fact, Vabba et al.
+(2022) further reports that people with high interoception abilities were less likely to differ in risk-taking tendencies, telling the same number of lies regardless of the social stakes.
+Consistent with our results, Mohr et al.
+(2023) further reports that individuals with high interoceptive accuracy were more likely to make egocentric decisions.
 However, in contrast to previous studies (Füstös et al., 2013; Owens et al., 2018; Pinna \& Edwards, 2020; Pollatos et al., 2007), we did not find any significant relationship between individuals' interoception scores and their heart rate changes during their answers.
@@
 
-Although yielding promising results, this exploratory study is limited by the sample size.
+Another possibility that should be tested in the future is that of a mediating role of executive functions, given their positive association with interoception (Molnar-Szakacs \& Uddin, 2022).
+For instance, neuroscientific findings investigating the correlates of interoception have underlined the potential role of the anterior cingulate cortex (ACC) and anterior insula (AI) (Craig, 2009; Critchley et al., 2004; Khalsa et al., 2009; Wang et al., 2019), both of which are often thought to be activated during deception (Abe, 2011; Baumgartner et al., 2013; Sip et al., 2008), and have been implicated in cognitive processes associated with deception (such as cognitive control, Molnar-Szakacs \& Uddin, 2022; or conflict detection, Kerns et al., 2004).
+It is thus possible that the positive relationship between interoceptive abilities and deception is at least partially mediated by cognitive control abilities.
+
+Although yielding promising results, the sample size of this exploratory study is a source of concern.
 Although we tried to mitigate it by 1) extracting more robust variables (by combining multiple ones by means of feature reduction) and 2) using a suited analysis approach (Bayesian statistics with informative priors), future replication studies with larger samples are warranted to confirm this first investigation.
@@
 The statistical power could also explain the overall lack of results found in relation to heart rate, which has a higher signal-to-noise ratio as compared to subjective reports (such as confidence scales).
+Additionally, one has to note that the participants did not have strong incentive for lying (there was no risk of losing the ``reward'' - i.e., student credits), which might have further decreased the potential effect sizes.
 
@@
 Given increasing research efforts invested in the development of novel interoception tasks (Legrand et al., 2022; Plans et al., 2021; Ponzo et al., 2021), future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.
-Additionally, our application of feature reduction as a noise-elimination measure could have over-simplified the data.
+
+Moreover, although the cognitive and affective components of ToM and empathy share overlaps in the current literature, and there is no consensus regarding how the two concepts should be delineated, recent evidence nonetheless suggests ToM and empathy are necessarily distinct constructs with separable underlying mechanisms (Kanske et al., 2015).
+As such, future studies are warranted to further investigate the associations between ToM and lying ability using validated instruments sensitive to measuring ToM (such as the Theory of Mind Inventory, Hutchins et al., 2021).
+Furthermore, our application of feature reduction as a noise-elimination measure could have over-simplified the data.
 A more complex pattern of relationships, with different contributions of various subdimensions of ToM and interoception, could emerge provided a sufficient statistical power and valid measures.
@@
 In conclusion, this study is a first step towards assessing the contribution of ToM and interoception abilities in deception, particularly in one's ability to lie convincingly.
-To this end, we introduced a new paradigm that is able to modulate the contribution of these mechanisms while remaining relevant to applied fields of lie detection and criminology (in which the experimental conditions find echoing practices).
-Notably, our results provide princeps evidence that interoception could be a key - and overlooked - mechanism in deception.
+To this end, we introduced a new paradigm to delineate the contribution of these mechanisms while remaining relevant to applied fields of lie detection and criminology (in which the experimental conditions find echoing practices).
+Notably, our results provide some evidence that interoception could be an important - and overlooked - process involved in deception.
+Furthermore, our findings extend and offer an alternate perspective to the debatable use of polygraphs, suggesting that its utility for lie detection is not only questionable, but could potentially selectively modulate deceptive skills depending on the cognitive and interoceptive profile of the participant.
 
@@
 
-\begin{verbatim}
-## Warning in readLines(file): incomplete final line found on 'references.bib'
-\end{verbatim}
-
 \begingroup
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-abe2011brain}{}}%
+Abe, N. (2011). How the brain shapes deception: An integrated review of the literature. \emph{The Neuroscientist}, \emph{17}(5), 560--574.
+
 \leavevmode\vadjust pre{\hypertarget{ref-baron1997mindblindness}{}}%
@@
 Barrett, L. F., \& Simmons, W. K. (2015). Interoceptive predictions in the brain. \emph{Nature Reviews Neuroscience}, \emph{16}(7), 419--429.
+
+\leavevmode\vadjust pre{\hypertarget{ref-baumgartner2013honest}{}}%
+Baumgartner, T., Gianotti, L.
+R., \& Knoch, D.
+(2013).
+Who is honest and why: Baseline activation in anterior insula predicts inter-individual differences in deceptive behavior.
+\emph{Biological Psychology}, \emph{94}(1), 192--197.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-chiou2013enactment}{}}%
+Chiou, W.-B., \& Lee, C.-C.
+(2013).
+Enactment of one-to-many communication may induce self-focused attention that leads to diminished perspective taking: The case of facebook.
+\emph{Judgment and Decision Making}, \emph{8}(3), 372--380.
+
 \leavevmode\vadjust pre{\hypertarget{ref-connell2018interoception}{}}%
@@
 \emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{373}(1752), 20170143.
+
+\leavevmode\vadjust pre{\hypertarget{ref-craig2009you}{}}%
+Craig, A. D. (2009). How do you feel---now? The anterior insula and human awareness. \emph{Nature Reviews Neuroscience}, \emph{10}(1), 59--70.
+
+\leavevmode\vadjust pre{\hypertarget{ref-critchley2004neural}{}}%
+Critchley, H. D., Wiens, S., Rotshtein, P., Öhman, A., \& Dolan, R. J. (2004). Neural systems supporting interoceptive awareness. \emph{Nature Neuroscience}, \emph{7}(2), 189--195.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-gendolla2009self}{}}%
+Gendolla, G. H., \& Wicklund, R. A. (2009). Self-focused attention, perspective-taking, and false consensus. \emph{Social Psychology}, \emph{40}(2), 66--72.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gonzalez2019can}{}}%
+Gonzalez-Billandon, J., Aroyo, A.
+M., Tonelli, A., Pasquali, D., Sciutti, A., Gori, M., Sandini, G., \& Rea, F.
+(2019).
+Can a robot catch you lying?
+A machine learning system to detect lies during interactions.
+\emph{Frontiers in Robotics and AI}, \emph{6}, 64.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hutchins2021development}{}}%
+Hutchins, T.
+L., Lewis, L., Prelock, P.
+A., \& Brien, A.
+(2021).
+The development and preliminary psychometric evaluation of the theory of mind inventory: Self report---adult (ToMI: SR-adult).
+\emph{Journal of Autism and Developmental Disorders}, \emph{51}, 1839--1851.
+
 \leavevmode\vadjust pre{\hypertarget{ref-jolliffe2006development}{}}%
 Jolliffe, D., \& Farrington, D. P. (2006). Development and validation of the basic empathy scale. \emph{Journal of Adolescence}, \emph{29}(4), 589--611.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kanske2015dissecting}{}}%
+Kanske, P., Böckler, A., Trautwein, F.-M., \& Singer, T.
+(2015).
+Dissecting the social brain: Introducing the EmpaToM to reveal distinct neural networks and brain--behavior relations for empathy and theory of mind.
+\emph{NeuroImage}, \emph{122}, 6--19.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kerns2004anterior}{}}%
+Kerns, J.
+G., Cohen, J.
+D., MacDonald III, A.
+W., Cho, R.
+Y., Stenger, V.
+A., \& Carter, C.
+S.
+(2004).
+Anterior cingulate conflict monitoring and adjustments in control.
+\emph{Science}, \emph{303}(5660), 1023--1026.
+
+\leavevmode\vadjust pre{\hypertarget{ref-khalsa2009pathways}{}}%
+Khalsa, S. S., Rudrauf, D., Feinstein, J. S., \& Tranel, D. (2009). The pathways of interoceptive awareness. \emph{Nature Neuroscience}, \emph{12}(12), 1494--1496.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kireev2013possible}{}}%
+Kireev, M., Korotkov, A., Medvedeva, N., \& Medvedev, S.
+(2013).
+Possible role of an error detection mechanism in brain processing of deception: PET-fMRI study.
+\emph{International Journal of Psychophysiology}, \emph{90}(3), 291--299.
 
@@
 \emph{Experimental Brain Research}, \emph{230}(2), 233--241.
+
+\leavevmode\vadjust pre{\hypertarget{ref-levine2022prosocial}{}}%
+Levine, E. E., \& Lupoli, M. J. (2022). Prosocial lies: Causes and consequences. \emph{Current Opinion in Psychology}, \emph{43}, 335--340.
+
+\leavevmode\vadjust pre{\hypertarget{ref-levine2014liars}{}}%
+Levine, E. E., \& Schweitzer, M. E. (2014). Are liars ethical? On the tension between benevolence and honesty. \emph{Journal of Experimental Social Psychology}, \emph{53}, 107--117.
+
+\leavevmode\vadjust pre{\hypertarget{ref-levine2015prosocial}{}}%
+Levine, E. E., \& Schweitzer, M. E. (2015). Prosocial lies: When deception breeds trust. \emph{Organizational Behavior and Human Decision Processes}, \emph{126}, 88--106.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-von2023social}{}}%
+Mohr, M.
+von, Finotti, G., Esposito, G., Bahrami, B., \& Tsakiris, M.
+(2023).
+Social interoception: Perceiving events during cardiac afferent activity makes people more suggestible to other people's influence.
+\emph{Cognition}, \emph{238}, 105502.
+
+\leavevmode\vadjust pre{\hypertarget{ref-molnar2022anterior}{}}%
+Molnar-Szakacs, I., \& Uddin, L. Q. (2022). Anterior insula as a gatekeeper of executive control. \emph{Neuroscience \& Biobehavioral Reviews}, 104736.
+
 \leavevmode\vadjust pre{\hypertarget{ref-murphy2019classifying}{}}%
@@
 \emph{Autonomic Neuroscience}, \emph{210}, 65--71.
+
+\leavevmode\vadjust pre{\hypertarget{ref-paulhus2002dark}{}}%
+Paulhus, D. L., \& Williams, K. M. (2002). The dark triad of personality: Narcissism, machiavellianism, and psychopathy. \emph{Journal of Research in Personality}, \emph{36}(6), 556--563.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-rassin2023psychopathy}{}}%
+Rassin, E., Sergiou, C., Linden, D. van der, \& Dongen, J. van. (2023). Psychopathy as a predisposition to lie hedonistically. \emph{Psychology, Crime \& Law}, 1--8.
+
+\leavevmode\vadjust pre{\hypertarget{ref-riggio1987verbal}{}}%
+Riggio, R. E., Tucker, J., \& Widaman, K. F. (1987). Verbal and nonverbal cues as mediators of deception ability. \emph{Journal of Nonverbal Behavior}, \emph{11}, 126--145.
+
 \leavevmode\vadjust pre{\hypertarget{ref-roheger2022progression}{}}%
@@
 Rosky, J. W. (2013). The (f) utility of post-conviction polygraph testing. \emph{Sexual Abuse}, \emph{25}(3), 259--281.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rubin2003belief}{}}%
+Rubin, D. C., Schrauf, R. W., \& Greenberg, D. L. (2003). Belief and recollection of autobiographical memories. \emph{Memory \& Cognition}, \emph{31}, 887--901.
+
+\leavevmode\vadjust pre{\hypertarget{ref-scaffidi2016self}{}}%
+Scaffidi Abbate, C., Boca, S., \& Gendolla, G. H. (2016). Self-awareness, perspective-taking, and egocentrism. \emph{Self and Identity}, \emph{15}(4), 371--380.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-shamay2010role}{}}%
+Shamay-Tsoory, S.
+G., Harari, H., Aharon-Peretz, J., \& Levkovitz, Y.
+(2010).
+The role of the orbitofrontal cortex in affective theory of mind deficits in criminal offenders with psychopathic tendencies.
+\emph{Cortex}, \emph{46}(5), 668--677.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sip2008detecting}{}}%
+Sip, K. E., Roepstorff, A., McGregor, W., \& Frith, C. D. (2008). Detecting deception: The scope and limits. \emph{Trends in Cognitive Sciences}, \emph{12}(2), 48--53.
+
 \leavevmode\vadjust pre{\hypertarget{ref-sip2012if}{}}%
@@
 Sternglanz, R. W., Morris, W. L., Morrow, M., \& Braverman, J. (2019). A review of meta-analyses about deception detection. \emph{The Palgrave Handbook of Deceptive Communication}, 303--326.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sugawara2020effects}{}}%
+Sugawara, A., Terasawa, Y., Katsunuma, R., \& Sekiguchi, A.
+(2020).
+Effects of interoceptive training on decision making, anxiety, and somatic symptoms.
+\emph{BioPsychoSocial Medicine}, \emph{14}, 1--8.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-walczyk2022err}{}}%
+Walczyk, J. J., \& Cockrell, N. F. (2022). To err is human but not deceptive. \emph{Memory \& Cognition}, \emph{50}(1), 232--244.
+
+\leavevmode\vadjust pre{\hypertarget{ref-walczyk2014social}{}}%
+Walczyk, J.
+J., Harris, L.
+L., Duck, T.
+K., \& Mulay, D.
+(2014).
+A social-cognitive framework for understanding serious lies: Activation-decision-construction-action theory.
+\emph{New Ideas in Psychology}, \emph{34}, 22--36.
+
+\leavevmode\vadjust pre{\hypertarget{ref-walczyk2009cognitive}{}}%
+Walczyk, J.
+J., Mahoney, K.
+T., Doverspike, D., \& Griffith-Ross, D.
+A.
+(2009).
+Cognitive lie detection: Response time and consistency of answers as cues to deception.
+\emph{Journal of Business and Psychology}, \emph{24}, 33--49.
+
+\leavevmode\vadjust pre{\hypertarget{ref-wang2019anterior}{}}%
+Wang, X., Wu, Q., Egan, L., Gu, X., Liu, P., Gu, H., Yang, Y., Luo, J., Wu, Y., Gao, Z., et al.
+(2019).
+Anterior insular cortex plays a critical role in interoceptive attention.
+\emph{Elife}, \emph{8}, e42265.
+
 \leavevmode\vadjust pre{\hypertarget{ref-weiss2014interaction}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wundrack2023mindful}{}}%
+Wundrack, R., \& Specht, J. (2023). Mindful self-focus--an interaction affecting theory of mind? \emph{Plos One}, \emph{18}(2), e0279544.
+
 \leavevmode\vadjust pre{\hypertarget{ref-yoris2015roles}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-zvi2018correlates}{}}%
+Zvi, L., \& Elaad, E.
+(2018).
+Correlates of narcissism, self-reported lies, and self-assessed abilities to tell and detect lies, tell truths, and believe others.
+\emph{Journal of Investigative Psychology and Offender Profiling}, \emph{15}(3), 271--286.
+
 \end{CSLReferences}

### 2023-10-05 paper/manuscript.Rmd
Revision

@@
     keep_tex: yes
-keywords: "Deception; Interoception; Theory of Mind; Poygraph; Lying Ability"
+keywords: "Deception; Interoception; Theory of Mind; Polygraph; Lying Ability"
 wordcount: '5004'

### 2024-01-11 paper/manuscript.tex
update tex

@@
 
-% \usepackage{etoolbox}
 \makeatletter
-\patchcmd{\HyOrg@maketitle}
+\usepackage{etoolbox}
+\patchcmd{\maketitle}
   {\section{\normalfont\normalsize\abstractname}}
@@
   {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
+\patchcmd{\maketitle}
   {\section{\protect\normalfont{\@title}}}
@@
 {}{\PatchFailed}
-\keywords{Deception; Interoception; Theory of Mind; Poygraph; Lying Ability\newline\indent Word count: 5004}
+\keywords{Deception; Interoception; Theory of Mind; Polygraph; Lying Ability\newline\indent Word count: 5004}
 \usepackage{lineno}
@@
   pdflang={en-EN},
-  pdfkeywords={Deception; Interoception; Theory of Mind; Poygraph; Lying Ability},
+  pdfkeywords={Deception; Interoception; Theory of Mind; Polygraph; Lying Ability},
   hidelinks,

### 2024-06-11 paper/manuscript.Rmd
update

--- 2023-10-02 paper/manuscript.Rmd
@@
       - "Writing – review & editing"
-
 affiliation:
@@
     keep_tex: yes
-keywords: "Deception; Interoception; Theory of Mind; Poygraph; Lying Ability"
+  papaja::apa6_word:
+    keep_tex: yes
+keywords: "Deception; Interoception; Theory of Mind; Polygraph; Lying Ability"
 wordcount: '5004'
@@
 
-Although few studies exist that investigate the relationship between interoception and deceptive ability *per se*, previous decision-making studies have demonstrated a negative correlation between interoceptive awareness, a metacognitive dimension of interoception, and one's likelihood to make risky decisions [@dunn2010listening; @furman2013interoceptive].
+Although few studies exist that investigate the relationship between interoception and deceptive ability *per se*, previous decision-making studies have demonstrated a negative correlation between interoceptive awareness and one's likelihood to make risky decisions [@dunn2010listening; @furman2013interoceptive].
 This is in line with the somatic marker hypothesis, which posits that an accurate evaluation of one's bodily signals facilitates the use of such interoceptive feedback to guide rational decision making [@damasio1996somatic].
-Indeed, @sugawara2020effects further reports that individuals who received interoceptive training were more likely to show higher interoceptive accuracy and make reasoned decisions.
+Indeed, @sugawara2020effects further reported that individuals who received interoceptive training were more likely to show higher interoceptive accuracy and make reasoned decisions.
 Given that deciding to lie generally involves a consideration of the potential costs of getting caught, and hence could also be perceived as risky behavior [@kireev2013possible], interoception could be construed to be negatively related to lying ability.
@@
 The aim of the present study was to explore the contribution of ToM and interoception abilities on individuals' deception skills, as indicated by their lying confidence, physiological arousal and response time.
-To this end, we designed a directed-lying paradigm with 2 conditions differing in the nature of their feedback cues.
+To this end, we designed a directed-lying paradigm with two conditions differing in the nature of their feedback cues.
 The *Interrogation* condition was designed to emphasize (and preferentially mobilize) ToM-related mechanisms, whereas the *Polygraph* condition was designed to emphasize interoceptive mechanisms.
@@
 
-30 university students from Singapore were recruited through posters, flyers, and online social media platforms, and rewarded with study credits for their time.
+Thirty university students from Singapore were recruited through posters, flyers, and online social media platforms, and rewarded with study credits for their time.
 <!-- Inclusion criteria included residing in Singapore, and an absence of current or history of neurological, psychiatric, or cardiovascular disorders.  -->
@@
 The Yoni Task [@shamay2007dissociable] is a behavioral task which assesses first and second-order ToM abilities in both cognitive and affective domains.
-Participants were presented with the face of a character named "Yoni", surrounded by 4 colored pictures of objects or faces, one in each corner of the screen.
+Participants were presented with the face of a character named "Yoni", surrounded by four colored pictures of objects or faces, one in each corner of the screen.
 In total, each participant completed 101 trials - 49 trials assessing their affective ToM abilities, 37 trials assessing their cognitive ToM abilities and 15 control trials.
-During each trial, participants were shown a question pertaining the item Yoni is referring to, and asked to make responses based on specific corresponding cues such as the directions of Yoni's eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical ToM).
+During each trial, participants were instructed to respond based on specific corresponding cues such as the directions of Yoni's eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical ToM).
 More specifically, in first-order trials, participants were instructed to make inferences about Yoni's mental state with regards to the objects surrounding it (e.g., "Yoni is thinking of...").
@@
 
-Given its multidimensional nature, the MAIA-2 [@mehling2012multidimensional], a 37-item questionnaire which measures 8 distinct facets of interoception including Noticing (e.g., *I notice when I am uncomfortable in my body*; $\alpha = 0.70$), Not-Distracting (e.g., *I try to ignore pain*; $\alpha = 0.87$), Not-Worrying (e.g., *I can stay calm and not worry when I have feelings of discomfort or pain*; $\alpha = 0.68$), Attention Regulation (e.g., *I can refocus my attention from thinking to sensing my body*; $\alpha = 0.85$), Emotional Awareness (e.g., *I notice how my body changes when I am angry*; $\alpha = 0.75$), Self-Regulation (e.g., *I can use my breath to reduce tension*; $\alpha = 0.62$), Body Listening (e.g., *I listen to information from my body about my emotional state*; $\alpha = 0.88$), and Trust (e.g., *I trust my body sensations*; $\alpha = 0.89$), using 5-point Likert scales, was also administered.
+Given its multidimensional nature, the MAIA-2 [@mehling2012multidimensional], a 37-item questionnaire using 5-point Likert scales was also administered.
+It measures eight distinct facets of interoception including Noticing (e.g., *I notice when I am uncomfortable in my body*; $\alpha = 0.70$), Not-Distracting (e.g., *I try to ignore pain*; $\alpha = 0.87$), Not-Worrying (e.g., *I can stay calm and not worry when I have feelings of discomfort or pain*; $\alpha = 0.68$), Attention Regulation (e.g., *I can refocus my attention from thinking to sensing my body*; $\alpha = 0.85$), Emotional Awareness (e.g., *I notice how my body changes when I am angry*; $\alpha = 0.75$), Self-Regulation (e.g., *I can use my breath to reduce tension*; $\alpha = 0.62$), Body Listening (e.g., *I listen to information from my body about my emotional state*; $\alpha = 0.88$), and Trust (e.g., *I trust my body sensations*; $\alpha = 0.89$).
 
@@
 
-Using PsychoPy [@peirce2019psychopy2], we implemented a directed-lying task in which participants were instructed to briefly answer 80 questions [taken from the Autobiographical Memory Questionnaire - AMQ, @rubin2003belief] pertaining to their personal preferences and subjective experiences, by either lying or telling the truth (depending on whether they see "lie" or "truth" written on the screen).
+Using PsychoPy [@peirce2019psychopy2], we implemented a directed-lying task in which participants were instructed to briefly answer 80 questions [taken from their previously taken Autobiographical Memory Questionnaire - AMQ, @rubin2003belief] pertaining to their personal preferences and subjective experiences, by either lying or telling the truth (depending on whether they see "lie" or "truth" written on the screen).
 Their goal was to make convincing answers, so that truths would be judged as truths by the receiver, and lies as lies.
@@
 
-In the *Polygraph* condition, participants had to provide their answer while receiving bio-feedback in the form of physiological signals (ECG, EDA and Respiration), of which they were informed was live feedback of their own physiological activity.
+In the *Polygraph* condition, participants had to provide their answer while receiving bio-feedback in the form of physiological signals (including cardiac activity - ECG, respiration - RSP, and electrodermal activity - EDA), of which they were informed was live feedback of their own physiological activity.
 In actuality, we displayed pre-recorded video clips of a confederate's physiological signals.
@@
 A within-subjects design was used in the present study, which is comprised of 2 sessions, to investigate the roles interoception and ToM play in lying ability.
-During session 1, participants answered a brief demographic survey as well as a questionnaire regarding their personal preferences and subjective experiences (Autobiographical Memory Questionnaire, AMQ), followed by a series of psychological scales (i.e., BES, MAIA and Lie scale), which were randomly displayed.
+During session 1, participants answered a brief demographic survey as well as a questionnaire regarding their personal preferences and subjective experiences (the AMQ), followed by a series of psychological scales (i.e., BES, MAIA and Lie scale), which were randomly displayed.
 
-During session 2, performed about one week later, the 3 cognitive-behavioural tasks (i.e., the deception task, HCT and the Yoni task) were administered to participants while their physiological signals (including cardiac activity - ECG, respiration -RSP, and electrodermal activity - EDA) were being recorded.
-The physiological recording devices were set up as follows: ECG was recorded with 3 electrodes placed according to a modified Lead II configuration [@takuma1995alternative], and respiration was measured using a respiration belt.
+During session 2, performed about one week later, the three cognitive-behavioural tasks (i.e., the deception task, HCT and the Yoni task) were administered to participants while their physiological signals (ECG, RSP, and EDA) were being recorded.
+The physiological recording devices were set up as follows: ECG was recorded with three electrodes placed according to a modified Lead II configuration [@takuma1995alternative], and respiration was measured using a respiration belt.
 All signals were recorded at 1000Hz via the BioPac MP160 system (BioPac Systems Inc., USA).
@@
 To maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, ToM and interoception) using factor analysis over PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained.
-Then, we modelled the relationship between these inter-individual composite scores (note that the analysis for all individual variables is nonetheless included in the analysis report) and the 3 outcome variables in interaction with the condition (polygraph *vs.* interrogation).
+Then, we modelled the relationship between these inter-individual composite scores (note that the analysis for all individual variables is nonetheless included in the analysis report) and the three outcome variables in interaction with the condition (polygraph *vs.* interrogation).
 Finally, we investigated the relationship between the deception scale traits, and the ToM and interoception scores using Bayesian correlations.
@@
 
-The analysis was not pre-registered (stemming out from an undergraduate's final year project), but the full reproducible analysis script, statistical results report, and data, are available at 
+The analysis was not pre-registered (stemming from an undergraduate's final year project), but the full reproducible analysis script, statistical results report, and data, are available at 
 **[masked for blinding]**
@@
 
-Compared to truth, lies were rated with less confidence ($\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%$), but no significant difference between the conditions was found.
-On the other hand, the RT did not differ between truth and lies, but was significantly slower in the polygraph condition for both conditions ($\Delta=0.25$, 95\% CI [0.62, 0.41], pd = 100\%).
-The heart rate was significantly more elevated during lies as compared to truth ($\Delta=1.16$, 95\% CI [0.57, 1.73], pd = 100\%), and during interrogation as compared to the polygraph condition ($\Delta=4.84$, 95\% CI [4.23, 5.44], pd = 100\%).
+Compared to truths, lies were rated with less confidence ($\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%$), but no significant difference between the conditions was found.
+On the other hand, the RT did not differ between truths and lies, but was significantly slower in the polygraph condition for both conditions ($\Delta=0.25$, 95\% CI [0.62, 0.41], pd = 100\%).
+The heart rate was significantly more elevated during lies as compared to truths ($\Delta=1.16$, 95\% CI [0.57, 1.73], pd = 100\%), and during interrogation as compared to the polygraph condition ($\Delta=4.84$, 95\% CI [4.23, 5.44], pd = 100\%).
 
@@
 
-The 3 Yoni-task dimensions and the 2 BES traits were combined into a unique factor, labelled *ToM* (explaining 35.76% of variance).
+The three Yoni-task dimensions and the two BES traits were combined into a unique factor, labelled *ToM* (explaining 35.76% of variance).
 It was loaded by the cognitive (.89), affective (.77), physical (.45) Yoni dimensions, and the affective (.41) and cognitive (.17) facets of the BES.
 
-The 8 MAIA dimensions and the 3 HCT components were reduced to 4 factors (explaining 65.17% of variance).
+The eight MAIA dimensions and the three HCT components were reduced to 4 factors (explaining 65.17% of variance).
 The first factor, labelled *Interoception - Meta* (23.59%), was loaded primarily by Attention Regulation (.97), Self-regulation (.63), Emotional awareness (.60), and Noticing (.49) dimensions of the MAIA and the HCT confidence score (.40).
@@
 Indeed, this is in line with previous studies that found individuals with low interoception were more averse to risk when reputational stakes were high, telling fewer egoistical lies [@vabba2022interoceptive].
-In fact, @vabba2022interoceptive further reports that people with high interoception abilities were less likely to differ in risk-taking tendencies, telling the same number of lies regardless of the social stakes.
-Consistent with our results, @von2023social further reports that individuals with high interoceptive accuracy were more likely to make egocentric decisions.
+In fact, @vabba2022interoceptive further reported that people with high interoception abilities were less likely to differ in risk-taking tendencies, telling the same number of lies regardless of the social stakes.
+Consistent with our results, @von2023social found that individuals with high interoceptive accuracy were more likely to make egocentric decisions.
 However, in contrast to previous studies [@pinna2020systematic; @fustos2013embodiment; @owens2018investigating; @pollatos2007heart], we did not find any significant relationship between individuals' interoception scores and their heart rate changes during their answers.
@@
 Although we tried to include more objective measures, such as RT (although it too was tied to the participants' conscious decision to press a key) and heart rate, future studies should attempt at measuring objectively the answer (lie or truth) quality, for instance by means of external examiners.
-Note that this is not a limitation *per se*, as it answers a slightly different question - what are the correlates of *objective* lying skills - than deception self-confidence.
+Note that this is not a limitation *per se*, as it answers a slightly different question - what are the correlates of *objective* lying skills - rather than of deception self-confidence.
 <!-- [**look for lit linking to what are commonly considered cues for lying**] -->
@@
 In particular, objective interoceptive accuracy was assessed using the Heartbeat Counting Task (HCT).
-While the HCT used to be considered as a gold standard and remains one of the most commonly used measures [@desmedt2022does], concerns regarding its validity has been highlighted in several studies [@desmedt2018heartbeat; @desmedt2022does; @brener2016towards; @legrand2022heart].
+While the HCT used to be considered as a gold standard and remains one of the most commonly used measures [@desmedt2022does], concerns regarding its validity have been highlighted in several studies [@desmedt2018heartbeat; @desmedt2022does; @brener2016towards; @legrand2022heart].
 Given increasing research efforts invested in the development of novel interoception tasks [@plans2021measuring; @legrand2022heart; @ponzo2021measuring], future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.
@@
 Furthermore, our application of feature reduction as a noise-elimination measure could have over-simplified the data.
-A more complex pattern of relationships, with different contributions of various subdimensions of ToM and interoception, could emerge provided a sufficient statistical power and valid measures.
+A more complex pattern of relationships, with different contributions of various subdimensions of ToM and interoception, could emerge with sufficient statistical power and valid measures.
 

### 2024-06-14 paper/manuscript.Rmd
address some R2 comments
@DominiqueMakowski to update Figure 1 to reflect the significance between Focus interocept with confidence for truths

@@
   - name          : "Tam Pham"  # phamttam17@gmail.com
-    affiliation   : " 2"
+    affiliation   : " 3"
     role:
@@
   - name          : "S.H. Annabel Chen"  # AnnabelChen@ntu.edu.sg
-    affiliation   : "2, 3, 4, 5"
+    affiliation   : "2, 4, 5, 6"
     orcid         : 0000-0002-1540-5516
@@
   - id            : "3"
+    institution   : "School of Psychological Sciences, Macquarie University, Australia"
+  - id            : "4"
     institution   : "Centre for Research and Development in Learning, Nanyang Technological University, Singapore"
-  - id            : "4"
+  - id            : "5"
     institution   : "Lee Kong Chian School of Medicine, Nanyang Technological University, Singapore"
-  - id            : "5"
+  - id            : "6"
     institution   : "National Institute of Education, Nanyang Technological University, Singapore"
@@
 During each trial, participants were instructed to respond based on specific corresponding cues such as the directions of Yoni's eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical ToM).
-More specifically, in first-order trials, participants were instructed to make inferences about Yoni's mental state with regards to the objects surrounding it (e.g., "Yoni is thinking of...").
-In more complex second-order trials, participants had to correctly infer the interaction between Yoni and others' mental states (e.g., Yoni is thinking of the fruit that ...
-wants").
+More specifically, in first-order trials, participants were instructed to make inferences about Yoni's mental state with regards to the objects surrounding it (e.g., "Yoni is thinking of..." for cognitive ToM trials or "Yoni likes..." for affective ToM trials).
+In more complex second-order trials, participants had to correctly infer the interaction between Yoni and others' mental states (e.g., "Yoni is thinking of the fruit that ...
+wants" for cognitive ToM trials or "Yoni likes the fruit that ...
+likes" for affective ToM trials).
 
@@
 
-The composite *ToM* score was significantly associated with less confident ($\beta=-0.19$, 95\% CI [-0.36, -0.02], pd = 98.47\%) and slower lies ($\beta=0.42$, 95\% CI [0.01, 0.83], pd = 97.67\%), specifically in the polygraph condition.
-No significant effect was found with regards to heart rate, and no correlation was observed with dispositional lying traits (**Figure 1**).
+The higher composite *ToM* score was significantly associated with a decreased confidence in lies ($\beta=-0.19$, 95\% CI [-0.36, -0.02], pd = 98.47\%), specifically in the polygraph condition.
+**Figure 1** illustrates the interindividual correlates of lying confidence.
+The higher composite *ToM* score was also associated with slower answers for lies ($\beta=0.42$, 95\% CI [0.01, 0.83], pd = 97.67\%), specifically in the polygraph condition.
+No significant effect was found with regards to dispositional lying traits, heart rate, and RT for truths in both polygraph and interrogation conditions.
 
@@
 
-The *Meta* interoception score was significantly associated with an increased confidence in lies, specifically in the polygraph condition ($\beta=0.20,~95\%~CI~[0.03, 0.35],~pd = 98.98\%$).
+The higher *Meta* interoception score was significantly associated with an increased confidence in lies, specifically in the polygraph condition ($\beta=0.20,~95\%~CI~[0.03, 0.35],~pd = 98.98\%$).
 It was also associated with faster answers for both lies ($\beta=-0.54,~95\%~CI~[-0.93, -0.15],~pd = 99.67\%$) and truths ($\beta=-0.29,~95\%~CI~[-0.63, 0.03],~pd = 96.10\%$), specifically in the polygraph condition.
-No significant association was found with heart rate.
+No significant association was found with regards to dispositional lying traits and heart rate in both conditions.
 
-The *Listening* interoception score was significantly associated with an increased confidence in lies, in both the polygraph ($\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%$) and interrogation condition ($\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%$).
-It was also associated with faster answers, particularly for lies ($\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%$) and truths ($\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%$) in the polygraph condition.
-No significant association was found with heart rate.
-This score also correlated with the dispositional lying *Contextuality* trait ($r = 0.50,~95\%~CI~[0.04, 0.64],~BF_{10} = 3.48\%$).
+The higher *Listening* interoception score was significantly associated with an increased confidence in lies, in both the polygraph ($\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%$) and interrogation conditions ($\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%$).
+It was also associated with faster answers for both lies ($\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%$) and truths ($\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%$), specifically in the polygraph condition.
+The *Listening* interoception score was also positively correlated with the dispositional lying *Contextuality* trait ($r = 0.50,~95\%~CI~[0.04, 0.64],~BF_{10} = 3.48\%$).
+No significant association was found with heart rate in both conditions.
 
-The *Focus* interoception score was significantly associated with an increased confidence in truthful responses in both the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$) and interrogation condition ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%$).
-No significant association was found with RT or heart rate, but the score correlated with the dispositional lying *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$).
+The higher *Focus* interoception score was significantly associated with an increased confidence in truths in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$); a consistent pattern, although non-significant, was found for confidence in truth in the interrogation conditions ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%$).
+The *Focus* interoception score was also positively correlated with the dispositional lying *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$).
+No significant association was found with RT for lies and heart rate in both conditions
 
-The *Regulation* interoception score was significantly associated with an increased confidence in lies in both the polygraph ($\beta=0.32,~95\%~CI~[0.14, 0.51],~pd = 99.99\%$) and the interrogation conditions ($\beta=0.18,~95\%~CI~[0.00, 0.36],~pd = 97.42\%$), and with a decreased confidence in truth only in the polygraph condition ($\beta=-0.1,~95\%~CI~[-0.36, 0.01],~pd = 97.16\%$).
-No significant association was found with RT or heart rate (**Figure 2**).
+The higher *Regulation* interoception score was significantly associated with an increased confidence in lies in both the polygraph ($\beta=0.32,~95\%~CI~[0.14, 0.51],~pd = 99.99\%$) and the interrogation conditions ($\beta=0.18,~95\%~CI~[0.00, 0.36],~pd = 97.42\%$), and with a decreased confidence in truth only in the polygraph condition ($\beta=-0.1,~95\%~CI~[-0.36, 0.01],~pd = 97.16\%$).
+No significant association was found with RT and heart rate in both conditions (**Figure 2**).
 
@@
 
-Another possibility that should be tested in the future is that of a mediating role of executive functions, given their positive association with interoception [@molnar2022anterior].
+Another possibility that should be tested in the future is that of a mediating role of executive functions, given their association with lying [e.g., @battista2021role; @abe2007deceiving] and interoception [@molnar2022anterior].
 For instance, neuroscientific findings investigating the correlates of interoception have underlined the potential role of the anterior cingulate cortex (ACC) and anterior insula (AI) [@wang2019anterior; @craig2009you; @critchley2004neural; @khalsa2009pathways], both of which are often thought to be activated during deception [@abe2011brain; @sip2008detecting; @baumgartner2013honest], and have been implicated in cognitive processes associated with deception [such as cognitive control, @molnar2022anterior; or conflict detection, @kerns2004anterior].
@@
 
+<!-- the concepts of interoception and TOM work together, that is could it be that they influence the ability to lie simultaneously and not in a separate way  -->
+
+Finally, there has been some research in the extant literature linking individual differences in ToM and interoception, as well as their neurophysiological underpinnings [@shah2017heart; @gao2019body; @ondobaka2017role].
+As such, it remains a possibility that the two constructs interact in influencing lying ability.
+However, much of this research seems focused on emotion processing, which only constitutes one of the hosts of cognitive processes required to engage in deceptive behaviour [e.g., @shah2017heart].
+Furthermore, given the overlaps in the literature surrounding ToM and empathy, it remains unclear whether interoception works with ToM or empathy (specifically affectivce empathy) in the processing of emotions.
+Considering the current gaps in literature, the present study investigates the influence of individual differences in ToM and interoception on lying ability separately; this could be a useful first approach to delineate potential "main effects" of these processes.
+Nevertheless, future studies (with a different design and a larger sample) could investigate the interaction (and possible mediation effects) between interoception and ToM by means of, for instance, structural equation modelling.
+
 <!-- Taking into perspective that the various facets of interoception are widely regarded as dissociable [@suksasilp2022towards; @mehling2012multidimensional], future studies could thus investigate their effects separately, to better delineate how interoceptive processes influence lying ability.

### 2024-06-14 paper/manuscript.tex
address some R2 comments
@DominiqueMakowski to update Figure 1 to reflect the significance between Focus interocept with confidence for truths

@@
 \author{Dominique Makowski\textsuperscript{1, 2}, Zen J.
-Lau\textsuperscript{2}, Tam Pham\textsuperscript{2}, An Shu Te\textsuperscript{2}, Stephanie Kirk\textsuperscript{2}, Claudia Liauw\textsuperscript{2}, \& S.H.
-Annabel Chen\textsuperscript{2, 3, 4, 5}}
+Lau\textsuperscript{2}, Tam Pham\textsuperscript{3}, An Shu Te\textsuperscript{2}, Stephanie Kirk\textsuperscript{2}, Claudia Liauw\textsuperscript{2}, \& S.H.
+Annabel Chen\textsuperscript{2, 4, 5, 6}}
 \date{}
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Psychology, University of Sussex, UK\\\textsuperscript{2} School of Social Sciences, Nanyang Technological University, Singapore\\\textsuperscript{3} Centre for Research and Development in Learning, Nanyang Technological University, Singapore\\\textsuperscript{4} Lee Kong Chian School of Medicine, Nanyang Technological University, Singapore\\\textsuperscript{5} National Institute of Education, Nanyang Technological University, Singapore}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Psychology, University of Sussex, UK\\\textsuperscript{2} School of Social Sciences, Nanyang Technological University, Singapore\\\textsuperscript{3} School of Psychological Sciences, Macquarie University, Australia\\\textsuperscript{4} Centre for Research and Development in Learning, Nanyang Technological University, Singapore\\\textsuperscript{5} Lee Kong Chian School of Medicine, Nanyang Technological University, Singapore\\\textsuperscript{6} National Institute of Education, Nanyang Technological University, Singapore}
 
@@
 
-Although few studies exist that investigate the relationship between interoception and deceptive ability \emph{per se}, previous decision-making studies have demonstrated a negative correlation between interoceptive awareness, a metacognitive dimension of interoception, and one's likelihood to make risky decisions (Dunn et al., 2010; Furman et al., 2013).
+Although few studies exist that investigate the relationship between interoception and deceptive ability \emph{per se}, previous decision-making studies have demonstrated a negative correlation between interoceptive awareness and one's likelihood to make risky decisions (Dunn et al., 2010; Furman et al., 2013).
 This is in line with the somatic marker hypothesis, which posits that an accurate evaluation of one's bodily signals facilitates the use of such interoceptive feedback to guide rational decision making (Damasio, 1996).
 Indeed, Sugawara et al.
-(2020) further reports that individuals who received interoceptive training were more likely to show higher interoceptive accuracy and make reasoned decisions.
+(2020) further reported that individuals who received interoceptive training were more likely to show higher interoceptive accuracy and make reasoned decisions.
 Given that deciding to lie generally involves a consideration of the potential costs of getting caught, and hence could also be perceived as risky behavior (Kireev et al., 2013), interoception could be construed to be negatively related to lying ability.
@@
 The aim of the present study was to explore the contribution of ToM and interoception abilities on individuals' deception skills, as indicated by their lying confidence, physiological arousal and response time.
-To this end, we designed a directed-lying paradigm with 2 conditions differing in the nature of their feedback cues.
+To this end, we designed a directed-lying paradigm with two conditions differing in the nature of their feedback cues.
 The \emph{Interrogation} condition was designed to emphasize (and preferentially mobilize) ToM-related mechanisms, whereas the \emph{Polygraph} condition was designed to emphasize interoceptive mechanisms.
@@
 
-30 university students from Singapore were recruited through posters, flyers, and online social media platforms, and rewarded with study credits for their time.
+Thirty university students from Singapore were recruited through posters, flyers, and online social media platforms, and rewarded with study credits for their time.
 Four participants were excluded as their data was not recorded due to technical issues.
@@
 The Yoni Task (Shamay-Tsoory \& Aharon-Peretz, 2007) is a behavioral task which assesses first and second-order ToM abilities in both cognitive and affective domains.
-Participants were presented with the face of a character named ``Yoni'', surrounded by 4 colored pictures of objects or faces, one in each corner of the screen.
+Participants were presented with the face of a character named ``Yoni'', surrounded by four colored pictures of objects or faces, one in each corner of the screen.
 In total, each participant completed 101 trials - 49 trials assessing their affective ToM abilities, 37 trials assessing their cognitive ToM abilities and 15 control trials.
-During each trial, participants were shown a question pertaining the item Yoni is referring to, and asked to make responses based on specific corresponding cues such as the directions of Yoni's eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical ToM).
-More specifically, in first-order trials, participants were instructed to make inferences about Yoni's mental state with regards to the objects surrounding it (e.g., ``Yoni is thinking of\ldots{}'').
-In more complex second-order trials, participants had to correctly infer the interaction between Yoni and others' mental states (e.g., Yoni is thinking of the fruit that \ldots{} wants'').
+During each trial, participants were instructed to respond based on specific corresponding cues such as the directions of Yoni's eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical ToM).
+More specifically, in first-order trials, participants were instructed to make inferences about Yoni's mental state with regards to the objects surrounding it (e.g., ``Yoni is thinking of\ldots{}'' for cognitive ToM trials or ``Yoni likes\ldots{}'' for affective ToM trials).
+In more complex second-order trials, participants had to correctly infer the interaction between Yoni and others' mental states (e.g., ``Yoni is thinking of the fruit that \ldots{} wants'' for cognitive ToM trials or ``Yoni likes the fruit that \ldots{} likes'' for affective ToM trials).
 
@@
 
-Given its multidimensional nature, the MAIA-2 (Mehling et al., 2012), a 37-item questionnaire which measures 8 distinct facets of interoception including Noticing (e.g., \emph{I notice when I am uncomfortable in my body}; \(\alpha = 0.70\)), Not-Distracting (e.g., \emph{I try to ignore pain}; \(\alpha = 0.87\)), Not-Worrying (e.g., \emph{I can stay calm and not worry when I have feelings of discomfort or pain}; \(\alpha = 0.68\)), Attention Regulation (e.g., \emph{I can refocus my attention from thinking to sensing my body}; \(\alpha = 0.85\)), Emotional Awareness (e.g., \emph{I notice how my body changes when I am angry}; \(\alpha = 0.75\)), Self-Regulation (e.g., \emph{I can use my breath to reduce tension}; \(\alpha = 0.62\)), Body Listening (e.g., \emph{I listen to information from my body about my emotional state}; \(\alpha = 0.88\)), and Trust (e.g., \emph{I trust my body sensations}; \(\alpha = 0.89\)), using 5-point Likert scales, was also administered.
+Given its multidimensional nature, the MAIA-2 (Mehling et al., 2012), a 37-item questionnaire using 5-point Likert scales was also administered.
+It measures eight distinct facets of interoception including Noticing (e.g., \emph{I notice when I am uncomfortable in my body}; \(\alpha = 0.70\)), Not-Distracting (e.g., \emph{I try to ignore pain}; \(\alpha = 0.87\)), Not-Worrying (e.g., \emph{I can stay calm and not worry when I have feelings of discomfort or pain}; \(\alpha = 0.68\)), Attention Regulation (e.g., \emph{I can refocus my attention from thinking to sensing my body}; \(\alpha = 0.85\)), Emotional Awareness (e.g., \emph{I notice how my body changes when I am angry}; \(\alpha = 0.75\)), Self-Regulation (e.g., \emph{I can use my breath to reduce tension}; \(\alpha = 0.62\)), Body Listening (e.g., \emph{I listen to information from my body about my emotional state}; \(\alpha = 0.88\)), and Trust (e.g., \emph{I trust my body sensations}; \(\alpha = 0.89\)).
 
@@
 
-Using PsychoPy (Peirce et al., 2019), we implemented a directed-lying task in which participants were instructed to briefly answer 80 questions (taken from the Autobiographical Memory Questionnaire - AMQ, Rubin et al., 2003) pertaining to their personal preferences and subjective experiences, by either lying or telling the truth (depending on whether they see ``lie'' or ``truth'' written on the screen).
+Using PsychoPy (Peirce et al., 2019), we implemented a directed-lying task in which participants were instructed to briefly answer 80 questions (taken from their previously taken Autobiographical Memory Questionnaire - AMQ, Rubin et al., 2003) pertaining to their personal preferences and subjective experiences, by either lying or telling the truth (depending on whether they see ``lie'' or ``truth'' written on the screen).
 Their goal was to make convincing answers, so that truths would be judged as truths by the receiver, and lies as lies.
@@
 
-In the \emph{Polygraph} condition, participants had to provide their answer while receiving bio-feedback in the form of physiological signals (ECG, EDA and Respiration), of which they were informed was live feedback of their own physiological activity.
+In the \emph{Polygraph} condition, participants had to provide their answer while receiving bio-feedback in the form of physiological signals (including cardiac activity - ECG, respiration - RSP, and electrodermal activity - EDA), of which they were informed was live feedback of their own physiological activity.
 In actuality, we displayed pre-recorded video clips of a confederate's physiological signals.
@@
 A within-subjects design was used in the present study, which is comprised of 2 sessions, to investigate the roles interoception and ToM play in lying ability.
-During session 1, participants answered a brief demographic survey as well as a questionnaire regarding their personal preferences and subjective experiences (Autobiographical Memory Questionnaire, AMQ), followed by a series of psychological scales (i.e., BES, MAIA and Lie scale), which were randomly displayed.
-
-During session 2, performed about one week later, the 3 cognitive-behavioural tasks (i.e., the deception task, HCT and the Yoni task) were administered to participants while their physiological signals (including cardiac activity - ECG, respiration -RSP, and electrodermal activity - EDA) were being recorded.
-The physiological recording devices were set up as follows: ECG was recorded with 3 electrodes placed according to a modified Lead II configuration (Takuma et al., 1995), and respiration was measured using a respiration belt.
+During session 1, participants answered a brief demographic survey as well as a questionnaire regarding their personal preferences and subjective experiences (the AMQ), followed by a series of psychological scales (i.e., BES, MAIA and Lie scale), which were randomly displayed.
+
+During session 2, performed about one week later, the three cognitive-behavioural tasks (i.e., the deception task, HCT and the Yoni task) were administered to participants while their physiological signals (ECG, RSP, and EDA) were being recorded.
+The physiological recording devices were set up as follows: ECG was recorded with three electrodes placed according to a modified Lead II configuration (Takuma et al., 1995), and respiration was measured using a respiration belt.
 All signals were recorded at 1000Hz via the BioPac MP160 system (BioPac Systems Inc., USA).
@@
 To maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, ToM and interoception) using factor analysis over PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained.
-Then, we modelled the relationship between these inter-individual composite scores (note that the analysis for all individual variables is nonetheless included in the analysis report) and the 3 outcome variables in interaction with the condition (polygraph \emph{vs.} interrogation).
+Then, we modelled the relationship between these inter-individual composite scores (note that the analysis for all individual variables is nonetheless included in the analysis report) and the three outcome variables in interaction with the condition (polygraph \emph{vs.} interrogation).
 Finally, we investigated the relationship between the deception scale traits, and the ToM and interoception scores using Bayesian correlations.
@@
 
-The analysis was not pre-registered (stemming out from an undergraduate's final year project), but the full reproducible analysis script, statistical results report, and data, are available at
+The analysis was not pre-registered (stemming from an undergraduate's final year project), but the full reproducible analysis script, statistical results report, and data, are available at
 \textbf{{[}masked for blinding{]}}
@@
 
-Compared to truth, lies were rated with less confidence (\(\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%\)), but no significant difference between the conditions was found.
-On the other hand, the RT did not differ between truth and lies, but was significantly slower in the polygraph condition for both conditions (\(\Delta=0.25\), 95\% CI {[}0.62, 0.41{]}, pd = 100\%).
-The heart rate was significantly more elevated during lies as compared to truth (\(\Delta=1.16\), 95\% CI {[}0.57, 1.73{]}, pd = 100\%), and during interrogation as compared to the polygraph condition (\(\Delta=4.84\), 95\% CI {[}4.23, 5.44{]}, pd = 100\%).
+Compared to truths, lies were rated with less confidence (\(\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%\)), but no significant difference between the conditions was found.
+On the other hand, the RT did not differ between truths and lies, but was significantly slower in the polygraph condition for both conditions (\(\Delta=0.25\), 95\% CI {[}0.62, 0.41{]}, pd = 100\%).
+The heart rate was significantly more elevated during lies as compared to truths (\(\Delta=1.16\), 95\% CI {[}0.57, 1.73{]}, pd = 100\%), and during interrogation as compared to the polygraph condition (\(\Delta=4.84\), 95\% CI {[}4.23, 5.44{]}, pd = 100\%).
 
@@
 
-The 3 Yoni-task dimensions and the 2 BES traits were combined into a unique factor, labelled \emph{ToM} (explaining 35.76\% of variance).
+The three Yoni-task dimensions and the two BES traits were combined into a unique factor, labelled \emph{ToM} (explaining 35.76\% of variance).
 It was loaded by the cognitive (.89), affective (.77), physical (.45) Yoni dimensions, and the affective (.41) and cognitive (.17) facets of the BES.
 
-The 8 MAIA dimensions and the 3 HCT components were reduced to 4 factors (explaining 65.17\% of variance).
+The eight MAIA dimensions and the three HCT components were reduced to 4 factors (explaining 65.17\% of variance).
 The first factor, labelled \emph{Interoception - Meta} (23.59\%), was loaded primarily by Attention Regulation (.97), Self-regulation (.63), Emotional awareness (.60), and Noticing (.49) dimensions of the MAIA and the HCT confidence score (.40).
@@
 
-The composite \emph{ToM} score was significantly associated with less confident (\(\beta=-0.19\), 95\% CI {[}-0.36, -0.02{]}, pd = 98.47\%) and slower lies (\(\beta=0.42\), 95\% CI {[}0.01, 0.83{]}, pd = 97.67\%), specifically in the polygraph condition.
-No significant effect was found with regards to heart rate, and no correlation was observed with dispositional lying traits (\textbf{Figure 1}).
+The higher composite \emph{ToM} score was significantly associated with a decreased confidence in lies (\(\beta=-0.19\), 95\% CI {[}-0.36, -0.02{]}, pd = 98.47\%), specifically in the polygraph condition.
+\textbf{Figure 1} illustrates the interindividual correlates of lying confidence.
+The higher composite \emph{ToM} score was also associated with slower answers for lies (\(\beta=0.42\), 95\% CI {[}0.01, 0.83{]}, pd = 97.67\%), specifically in the polygraph condition.
+No significant effect was found with regards to dispositional lying traits, heart rate, and RT for truths in both polygraph and interrogation conditions.
 
@@
 
-The \emph{Meta} interoception score was significantly associated with an increased confidence in lies, specifically in the polygraph condition (\(\beta=0.20,~95\%~CI~[0.03, 0.35],~pd = 98.98\%\)).
+The higher \emph{Meta} interoception score was significantly associated with an increased confidence in lies, specifically in the polygraph condition (\(\beta=0.20,~95\%~CI~[0.03, 0.35],~pd = 98.98\%\)).
 It was also associated with faster answers for both lies (\(\beta=-0.54,~95\%~CI~[-0.93, -0.15],~pd = 99.67\%\)) and truths (\(\beta=-0.29,~95\%~CI~[-0.63, 0.03],~pd = 96.10\%\)), specifically in the polygraph condition.
-No significant association was found with heart rate.
-
-The \emph{Listening} interoception score was significantly associated with an increased confidence in lies, in both the polygraph (\(\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%\)) and interrogation condition (\(\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%\)).
-It was also associated with faster answers, particularly for lies (\(\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%\)) and truths (\(\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%\)) in the polygraph condition.
-No significant association was found with heart rate.
-This score also correlated with the dispositional lying \emph{Contextuality} trait (\(r = 0.50,~95\%~CI~[0.04, 0.64],~BF_{10} = 3.48\%\)).
-
-The \emph{Focus} interoception score was significantly associated with an increased confidence in truthful responses in both the polygraph (\(\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%\)) and interrogation condition (\(\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%\)).
-No significant association was found with RT or heart rate, but the score correlated with the dispositional lying \emph{Ability} trait (\(r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%\)).
-
-The \emph{Regulation} interoception score was significantly associated with an increased confidence in lies in both the polygraph (\(\beta=0.32,~95\%~CI~[0.14, 0.51],~pd = 99.99\%\)) and the interrogation conditions (\(\beta=0.18,~95\%~CI~[0.00, 0.36],~pd = 97.42\%\)), and with a decreased confidence in truth only in the polygraph condition (\(\beta=-0.1,~95\%~CI~[-0.36, 0.01],~pd = 97.16\%\)).
-No significant association was found with RT or heart rate (\textbf{Figure 2}).
+No significant association was found with regards to dispositional lying traits and heart rate in both conditions.
+
+The higher \emph{Listening} interoception score was significantly associated with an increased confidence in lies, in both the polygraph (\(\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%\)) and interrogation conditions (\(\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%\)).
+It was also associated with faster answers for both lies (\(\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%\)) and truths (\(\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%\)), specifically in the polygraph condition.
+The \emph{Listening} interoception score was also positively correlated with the dispositional lying \emph{Contextuality} trait (\(r = 0.50,~95\%~CI~[0.04, 0.64],~BF_{10} = 3.48\%\)).
+No significant association was found with heart rate in both conditions.
+
+The higher \emph{Focus} interoception score was significantly associated with an increased confidence in truths in the polygraph (\(\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%\)); a consistent pattern, although non-significant, was found for confidence in truth in the interrogation conditions (\(\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%\)).
+The \emph{Focus} interoception score was also positively correlated with the dispositional lying \emph{Ability} trait (\(r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%\)).
+No significant association was found with RT for lies and heart rate in both conditions
+
+The higher \emph{Regulation} interoception score was significantly associated with an increased confidence in lies in both the polygraph (\(\beta=0.32,~95\%~CI~[0.14, 0.51],~pd = 99.99\%\)) and the interrogation conditions (\(\beta=0.18,~95\%~CI~[0.00, 0.36],~pd = 97.42\%\)), and with a decreased confidence in truth only in the polygraph condition (\(\beta=-0.1,~95\%~CI~[-0.36, 0.01],~pd = 97.16\%\)).
+No significant association was found with RT and heart rate in both conditions (\textbf{Figure 2}).
 
@@
 In fact, Vabba et al.
-(2022) further reports that people with high interoception abilities were less likely to differ in risk-taking tendencies, telling the same number of lies regardless of the social stakes.
+(2022) further reported that people with high interoception abilities were less likely to differ in risk-taking tendencies, telling the same number of lies regardless of the social stakes.
 Consistent with our results, Mohr et al.
-(2023) further reports that individuals with high interoceptive accuracy were more likely to make egocentric decisions.
+(2023) found that individuals with high interoceptive accuracy were more likely to make egocentric decisions.
 However, in contrast to previous studies (Füstös et al., 2013; Owens et al., 2018; Pinna \& Edwards, 2020; Pollatos et al., 2007), we did not find any significant relationship between individuals' interoception scores and their heart rate changes during their answers.
@@
 
-Another possibility that should be tested in the future is that of a mediating role of executive functions, given their positive association with interoception (Molnar-Szakacs \& Uddin, 2022).
+Another possibility that should be tested in the future is that of a mediating role of executive functions, given their association with lying (Abe et al., 2007; e.g., Battista et al., 2021) and interoception (Molnar-Szakacs \& Uddin, 2022).
 For instance, neuroscientific findings investigating the correlates of interoception have underlined the potential role of the anterior cingulate cortex (ACC) and anterior insula (AI) (Craig, 2009; Critchley et al., 2004; Khalsa et al., 2009; Wang et al., 2019), both of which are often thought to be activated during deception (Abe, 2011; Baumgartner et al., 2013; Sip et al., 2008), and have been implicated in cognitive processes associated with deception (such as cognitive control, Molnar-Szakacs \& Uddin, 2022; or conflict detection, Kerns et al., 2004).
@@
 Although we tried to include more objective measures, such as RT (although it too was tied to the participants' conscious decision to press a key) and heart rate, future studies should attempt at measuring objectively the answer (lie or truth) quality, for instance by means of external examiners.
-Note that this is not a limitation \emph{per se}, as it answers a slightly different question - what are the correlates of \emph{objective} lying skills - than deception self-confidence.
+Note that this is not a limitation \emph{per se}, as it answers a slightly different question - what are the correlates of \emph{objective} lying skills - rather than of deception self-confidence.
 
@@
 In particular, objective interoceptive accuracy was assessed using the Heartbeat Counting Task (HCT).
-While the HCT used to be considered as a gold standard and remains one of the most commonly used measures (Desmedt et al., 2022), concerns regarding its validity has been highlighted in several studies (Brener \& Ring, 2016; Desmedt et al., 2018, 2022; Legrand et al., 2022).
+While the HCT used to be considered as a gold standard and remains one of the most commonly used measures (Desmedt et al., 2022), concerns regarding its validity have been highlighted in several studies (Brener \& Ring, 2016; Desmedt et al., 2018, 2022; Legrand et al., 2022).
 Given increasing research efforts invested in the development of novel interoception tasks (Legrand et al., 2022; Plans et al., 2021; Ponzo et al., 2021), future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.
@@
 Furthermore, our application of feature reduction as a noise-elimination measure could have over-simplified the data.
-A more complex pattern of relationships, with different contributions of various subdimensions of ToM and interoception, could emerge provided a sufficient statistical power and valid measures.
+A more complex pattern of relationships, with different contributions of various subdimensions of ToM and interoception, could emerge with sufficient statistical power and valid measures.
+
+Finally, there has been some research in the extant literature linking individual differences in ToM and interoception, as well as their neurophysiological underpinnings (Gao et al., 2019; Ondobaka et al., 2017; Shah et al., 2017).
+As such, it remains a possibility that the two constructs interact in influencing lying ability.
+However, much of this research seems focused on emotion processing, which only constitutes one of the hosts of cognitive processes required to engage in deceptive behaviour (e.g., Shah et al., 2017).
+Furthermore, given the overlaps in the literature surrounding ToM and empathy, it remains unclear whether interoception works with ToM or empathy (specifically affectivce empathy) in the processing of emotions.
+Considering the current gaps in literature, the present study investigates the influence of individual differences in ToM and interoception on lying ability separately; this could be a useful first approach to delineate potential ``main effects'' of these processes.
+Nevertheless, future studies (with a different design and a larger sample) could investigate the interaction (and possible mediation effects) between interoception and ToM by means of, for instance, structural equation modelling.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-abe2007deceiving}{}}%
+Abe, N., Suzuki, M., Mori, E., Itoh, M., \& Fujii, T.
+(2007).
+Deceiving others: Distinct neural responses of the prefrontal cortex and amygdala in simple fabrication and deception with social interactions.
+\emph{Journal of Cognitive Neuroscience}, \emph{19}(2), 287--295.
+
 \leavevmode\vadjust pre{\hypertarget{ref-baron1997mindblindness}{}}%
@@
 Barrett, L. F., \& Simmons, W. K. (2015). Interoceptive predictions in the brain. \emph{Nature Reviews Neuroscience}, \emph{16}(7), 419--429.
+
+\leavevmode\vadjust pre{\hypertarget{ref-battista2021role}{}}%
+Battista, F., Otgaar, H., Mangiulli, I., \& Curci, A. (2021). The role of executive functions in the effects of lying on memory. \emph{Acta Psychologica}, \emph{215}, 103295.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ondobaka2017role}{}}%
+Ondobaka, S., Kilner, J., \& Friston, K. (2017). The role of interoceptive inference in theory of mind. \emph{Brain and Cognition}, \emph{112}, 64--68.
+
 \leavevmode\vadjust pre{\hypertarget{ref-oviatt2018handbook}{}}%

### 2024-06-19 index.Rmd
edit figure

@@
 # Remove outlier trials
-df <- df |>
-  group_by(Participant) |>
-  mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore", threshold = qnorm(0.99999))),
-         Outliers_Physio = as.logical(performance::check_outliers(HeartRate, method = "zscore", threshold = qnorm(0.99999)))) |>
-  ungroup()
+# df <- df |>
+#   group_by(Participant) |>
+#   mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore", threshold = qnorm(0.99999))),
+#          Outliers_Physio = as.logical(performance::check_outliers(HeartRate, method = "zscore", threshold = qnorm(0.99999)))) |>
+#   ungroup()
 
@@
 
-model <- glmmTMB(Confidence ~ Answer / Condition / ToM + (1|Participant) + (1|Item), 
-                 data = df, 
-                 family = beta_family())
+# model <- glmmTMB(Confidence ~ Answer / Condition / ToM + (1|Participant) + (1|Item), 
+#                  data = df, 
+#                  family = beta_family())
 
@@
   geom_line(aes(color = Condition), size=1) +
-  geom_text(data=data.frame(Intero_Focus = -0.2,
+  geom_text(data=data.frame(Intero_Focus = -0.25,
                             Predicted = c(0.55, 0.75),
@@
                             Answer = c("Truth", "Truth")),
-            label = format_pd(c(0.9716, 0.9576), stars_only = TRUE),
+            label = format_pd(c(0.9576, 0.9716), stars_only = TRUE),
             color = c("#2196F3", "#FF5722"),

### 2024-06-19 index.Rmd
R2 update
@zen-juen @Tam-Pham back to you for halp

@@
 
-p <- (p1 / p2 / p3 / p4 / p5) + plot_layout(guides = "collect") + plot_annotation(title = "Interindividual correlates of the confidence\nthat one tells a convincing lie", theme = list(plot.title = element_text(face = "bold", hjust = 0.5)))
+p <- (p1 / p2 / p3 / p4 / p5) + plot_layout(guides = "collect") + plot_annotation(title = "Interindividual correlates of the confidence\nthat one tells a convincing response", theme = list(plot.title = element_text(face = "bold", hjust = 0.5)))
 p

### 2024-06-25 paper/manuscript.Rmd
footnote on title page + move citation in discussion
sorry i cannot knit no more T_T

@@
 In particular, objective interoceptive accuracy was assessed using the Heartbeat Counting Task (HCT).
-While the HCT used to be considered as a gold standard and remains one of the most commonly used measures [@desmedt2022does], concerns regarding its validity have been highlighted in several studies [@desmedt2018heartbeat; @desmedt2022does; @brener2016towards; @legrand2022heart].
-Given increasing research efforts invested in the development of novel interoception tasks [@plans2021measuring; @legrand2022heart; @ponzo2021measuring], future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.
+While the HCT used to be considered as a gold standard and remains one of the most commonly used measures [@desmedt2022does], concerns regarding its validity have been increasingly highlighted in several studies as more research efforts are invested into developing novel interoception tasks [@desmedt2018heartbeat; @desmedt2022does; @brener2016towards; @legrand2022heart; @plans2021measuring; @ponzo2021measuring].
+Future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.
 

### 2024-06-26 paper/manuscript.Rmd
edit ms to align discussion with results

@@
 The present study examined the contribution of ToM and interoception on our ability to lie using a directed lie paradigm with two conditions ("Interrogation" and "Polygraph") designed to enhance each of the two mechanisms.
-Interestingly, we found that when participants were presented with (fake) physiological feedback (the polygraph condition), instead of a face of a person they had to lie to (the interrogation condition), their response time for both lies and truths increased, as did their heart rate.
-Although the condition did not impact the subjective confidence that participants had in their answers, it suggests that believing oneself to be submitted to a machine that is supposedly able to detect deception by interpreting physiological signals is a harder and/or more stressful condition than lying to a person.
-While research linking interoception and deception is limited, our results are in line with studies that show an association between interoceptive awareness and anxiety [@yoris2015roles; @garfinkel2013interoception; @domschke2010interoceptive].
+Interestingly, we found that when participants' responses were perceived to be evaluated by a person (the interrogation condition), instead of (fake) lie detection machine (the polygraph condition), their response time for both lies and truths were faster, and their heart rate was elevated.
+Although the condition did not impact the subjective confidence that participants had in their answers, the pattern of results suggests that believing one's response is being evaluated by a person, instead of a machine, could induce more fear, consequently speeding up the response and increasing the physiological arousal [@aylward2017impact].
+Alternatively, the slower response in the polygraph condition could be explained by the established attentional switching hypothesis, which posits that an increase in attention towards internal signals and managing one's emotional reaction would confer less cognitive resources available, thereby resulting in individuals taking a longer time to respond [@arnold2019interoception; @hanania2010selective].
+Individual differences in their interoceptive and ToM abilities further modulated the reported confidence, response time and physiological arousal in each condition.
+
+<!-- While research linking interoception and deception is limited, our results are in line with studies that show an association between interoceptive awareness and anxiety [@yoris2015roles; @garfinkel2013interoception; @domschke2010interoceptive].
 Specifically, enhancing one's attention towards their internal bodily signals could have resulted in a hyper-vigilance towards physiological sensations that is perceived negatively.
@@
 By extension, our study adds to the controversial discourse surrounding the use of physiological measures in past deception research, further questioning its validity as an indicator of deception [@rosky2013f; @oviatt2018handbook].
+-->
 
@@
 <!-- Interoception -->
-We also showed that interoceptive abilities (as indicated by the composite interoception scores) are correlated with a higher confidence in one's lies in the polygraph condition, a condition in which the attention towards internal reactions is fostered.
+We also found that interoceptive abilities (as indicated by the composite interoception scores) are correlated with a higher confidence in one's lies in the polygraph condition, a condition in which the attention towards internal reactions is fostered.
 Indeed, this is in line with previous studies that found individuals with low interoception were more averse to risk when reputational stakes were high, telling fewer egoistical lies [@vabba2022interoceptive].

### 2024-07-02 paper/manuscript.Rmd
finalize R2

@@
 Alternatively, the slower response in the polygraph condition could be explained by the established attentional switching hypothesis, which posits that an increase in attention towards internal signals and managing one's emotional reaction would confer less cognitive resources available, thereby resulting in individuals taking a longer time to respond [@arnold2019interoception; @hanania2010selective].
-Individual differences in their interoceptive and ToM abilities further modulated the reported confidence, response time and physiological arousal in each condition.
+While the impacts of external settings on individuals' responses warrant further investigation, the results highlight how physiological responses can be easily confounded by other factors (e.g., presence or absence of a stimuli), independent of whether one is lying or telling the truth.
+By extension, our study concurs with the controversial discourse surrounding the use of physiological measures in deception research [@rosky2013f; @oviatt2018handbook].
 
@@
 <!-- ToM -->
-Our results suggest that higher ToM abilities were related to slower and less confident lies, but only in the polygraph condition.
+Furthermore, our results suggest that higher ToM abilities were related to slower and less confident lies, but only in the polygraph condition.
 While previous bodies of work have reported mixed findings regarding the association between interoception and ToM [@scaffidi2016self; @gendolla2009self; @wundrack2023mindful; @chiou2013enactment], our results suggest the two are negatively linked.

### 2024-07-02 paper/manuscript.tex
finalize R2

@@
 \fi
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\section{Methods}\label{methods}
+
+\subsection{Participants}\label{participants}
 
@@
 
-\hypertarget{measures}{%
-\subsection{Measures}\label{measures}}
-
-\hypertarget{theory-of-mind-tom}{%
-\subsubsection{Theory of Mind (ToM)}\label{theory-of-mind-tom}}
+\subsection{Measures}\label{measures}
+
+\subsubsection{Theory of Mind (ToM)}\label{theory-of-mind-tom}
 
@@
 
-\hypertarget{interoception}{%
-\subsubsection{Interoception}\label{interoception}}
+\subsubsection{Interoception}\label{interoception}
 
@@
 
-\hypertarget{deception}{%
-\subsubsection{Deception}\label{deception}}
+\subsubsection{Deception}\label{deception}
 
@@
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\subsection{Procedure}\label{procedure}
 
@@
 
-\hypertarget{data-analysis}{%
-\subsection{Data Analysis}\label{data-analysis}}
+\subsection{Data Analysis}\label{data-analysis}
 
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{manipulation-check}{%
-\subsection{Manipulation Check}\label{manipulation-check}}
+\section{Results}\label{results}
+
+\subsection{Manipulation Check}\label{manipulation-check}
 
@@
 
-\hypertarget{feature-reduction}{%
-\subsection{Feature Reduction}\label{feature-reduction}}
+\subsection{Feature Reduction}\label{feature-reduction}
 
@@
 
-\hypertarget{theory-of-mind}{%
-\subsection{Theory of Mind}\label{theory-of-mind}}
+\subsection{Theory of Mind}\label{theory-of-mind}
 
@@
 
-\hypertarget{interoception-1}{%
-\subsection{Interoception}\label{interoception-1}}
+\subsection{Interoception}\label{interoception-1}
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\section{Discussion}\label{discussion}
 
 The present study examined the contribution of ToM and interoception on our ability to lie using a directed lie paradigm with two conditions (``Interrogation'' and ``Polygraph'') designed to enhance each of the two mechanisms.
-Interestingly, we found that when participants were presented with (fake) physiological feedback (the polygraph condition), instead of a face of a person they had to lie to (the interrogation condition), their response time for both lies and truths increased, as did their heart rate.
-Although the condition did not impact the subjective confidence that participants had in their answers, it suggests that believing oneself to be submitted to a machine that is supposedly able to detect deception by interpreting physiological signals is a harder and/or more stressful condition than lying to a person.
-While research linking interoception and deception is limited, our results are in line with studies that show an association between interoceptive awareness and anxiety (Domschke et al., 2010; Garfinkel \& Critchley, 2013; Yoris et al., 2015).
-Specifically, enhancing one's attention towards their internal bodily signals could have resulted in a hyper-vigilance towards physiological sensations that is perceived negatively.
-This is consistent with previous deception detection studies, in which participants' spontaneous lying behaviour only decreased when they were given feedback by a polygraph machine, but not when no feedback was given (Peleg et al., 2019).
-By extension, our study adds to the controversial discourse surrounding the use of physiological measures in past deception research, further questioning its validity as an indicator of deception (Oviatt et al., 2018; Rosky, 2013).
-
-Our results suggest that higher ToM abilities were related to slower and less confident lies, but only in the polygraph condition.
+Interestingly, we found that when participants' responses were perceived to be evaluated by a person (the interrogation condition), instead of (fake) lie detection machine (the polygraph condition), their response time for both lies and truths were faster, and their heart rate was elevated.
+Although the condition did not impact the subjective confidence that participants had in their answers, the pattern of results suggests that believing one's response is being evaluated by a person, instead of a machine, could induce more fear, consequently speeding up the response and increasing the physiological arousal (Aylward et al., 2017).
+Alternatively, the slower response in the polygraph condition could be explained by the established attentional switching hypothesis, which posits that an increase in attention towards internal signals and managing one's emotional reaction would confer less cognitive resources available, thereby resulting in individuals taking a longer time to respond (Arnold et al., 2019; Hanania \& Smith, 2010).
+While the impacts of external settings on individuals' responses warrant further investigation, the results highlight how physiological responses can be easily confounded by other factors (e.g., presence or absence of a stimuli), independent of whether one is lying or telling the truth.
+By extension, our study concurs with the controversial discourse surrounding the use of physiological measures in deception research (Oviatt et al., 2018; Rosky, 2013).
+
+Furthermore, our results suggest that higher ToM abilities were related to slower and less confident lies, but only in the polygraph condition.
 While previous bodies of work have reported mixed findings regarding the association between interoception and ToM (Chiou \& Lee, 2013; Gendolla \& Wicklund, 2009; Scaffidi Abbate et al., 2016; Wundrack \& Specht, 2023), our results suggest the two are negatively linked.
@@
 
-We also showed that interoceptive abilities (as indicated by the composite interoception scores) are correlated with a higher confidence in one's lies in the polygraph condition, a condition in which the attention towards internal reactions is fostered.
+We also found that interoceptive abilities (as indicated by the composite interoception scores) are correlated with a higher confidence in one's lies in the polygraph condition, a condition in which the attention towards internal reactions is fostered.
 Indeed, this is in line with previous studies that found individuals with low interoception were more averse to risk when reputational stakes were high, telling fewer egoistical lies (Vabba et al., 2022).
@@
 In particular, objective interoceptive accuracy was assessed using the Heartbeat Counting Task (HCT).
-While the HCT used to be considered as a gold standard and remains one of the most commonly used measures (Desmedt et al., 2022), concerns regarding its validity have been highlighted in several studies (Brener \& Ring, 2016; Desmedt et al., 2018, 2022; Legrand et al., 2022).
-Given increasing research efforts invested in the development of novel interoception tasks (Legrand et al., 2022; Plans et al., 2021; Ponzo et al., 2021), future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.
+While the HCT used to be considered as a gold standard and remains one of the most commonly used measures (Desmedt et al., 2022), concerns regarding its validity have been increasingly highlighted in several studies as more research efforts are invested into developing novel interoception tasks (Brener \& Ring, 2016; Desmedt et al., 2018, 2022; Legrand et al., 2022; Plans et al., 2021; Ponzo et al., 2021).
+Future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.
 
@@
 
-\hypertarget{data-availability}{%
-\section{Data Availability}\label{data-availability}}
+\section{Data Availability}\label{data-availability}
 
@@
 
-\hypertarget{conflict-of-interest-statement}{%
-\section{Conflict of Interest Statement}\label{conflict-of-interest-statement}}
+\section{Conflict of Interest Statement}\label{conflict-of-interest-statement}
 
@@
 
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
+\section{Acknowledgements}\label{acknowledgements}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{References}\label{references}
 
@@
 
-\hypertarget{refs}{}
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abe2011brain}{}}%
+\bibitem[\citeproctext]{ref-abe2011brain}
 Abe, N. (2011). How the brain shapes deception: An integrated review of the literature. \emph{The Neuroscientist}, \emph{17}(5), 560--574.
 
-\leavevmode\vadjust pre{\hypertarget{ref-abe2007deceiving}{}}%
+\bibitem[\citeproctext]{ref-abe2007deceiving}
 Abe, N., Suzuki, M., Mori, E., Itoh, M., \& Fujii, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-baron1997mindblindness}{}}%
+\bibitem[\citeproctext]{ref-arnold2019interoception}
+Arnold, A. J., Winkielman, P., \& Dobkins, K. (2019). Interoception and social connection. \emph{Frontiers in Psychology}, \emph{10}, 2589.
+
+\bibitem[\citeproctext]{ref-aylward2017impact}
+Aylward, J., Valton, V., Goer, F., Mkrtchian, A., Lally, N., Peters, S., Limbachya, T., \& Robinson, O.
+J.
+(2017).
+The impact of induced anxiety on affective response inhibition.
+\emph{Royal Society Open Science}, \emph{4}(6), 170084.
+
+\bibitem[\citeproctext]{ref-baron1997mindblindness}
 Baron-Cohen, S. (1997). \emph{Mindblindness: An essay on autism and theory of mind}. MIT press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-barrett2015interoceptive}{}}%
+\bibitem[\citeproctext]{ref-barrett2015interoceptive}
 Barrett, L. F., \& Simmons, W. K. (2015). Interoceptive predictions in the brain. \emph{Nature Reviews Neuroscience}, \emph{16}(7), 419--429.
 
-\leavevmode\vadjust pre{\hypertarget{ref-battista2021role}{}}%
+\bibitem[\citeproctext]{ref-battista2021role}
 Battista, F., Otgaar, H., Mangiulli, I., \& Curci, A. (2021). The role of executive functions in the effects of lying on memory. \emph{Acta Psychologica}, \emph{215}, 103295.
 
-\leavevmode\vadjust pre{\hypertarget{ref-baumgartner2013honest}{}}%
+\bibitem[\citeproctext]{ref-baumgartner2013honest}
 Baumgartner, T., Gianotti, L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-beaudoin2020systematic}{}}%
+\bibitem[\citeproctext]{ref-beaudoin2020systematic}
 Beaudoin, C., Leblanc, É., Gagner, C., \& Beauchamp, M. H. (2020). Systematic review and inventory of theory of mind measures for young children. \emph{Frontiers in Psychology}, \emph{10}, 2905.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bond2008individual}{}}%
+\bibitem[\citeproctext]{ref-bond2008individual}
 Bond Jr, C. F., \& DePaulo, B. M. (2008). Individual differences in judging deception: Accuracy and bias. \emph{Psychological Bulletin}, \emph{134}(4), 477.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bora2017meta}{}}%
+\bibitem[\citeproctext]{ref-bora2017meta}
 Bora, E., \& Yener, G. G. (2017). Meta-analysis of social cognition in mild cognitive impairment. \emph{Journal of Geriatric Psychiatry and Neurology}, \emph{30}(4), 206--213.
 
-\leavevmode\vadjust pre{\hypertarget{ref-brener2016towards}{}}%
+\bibitem[\citeproctext]{ref-brener2016towards}
 Brener, J., \& Ring, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-burgoon1994interpersonal}{}}%
+\bibitem[\citeproctext]{ref-burgoon1994interpersonal}
 Burgoon, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Burkner2017}{}}%
+\bibitem[\citeproctext]{ref-Burkner2017}
 Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
 
-\leavevmode\vadjust pre{\hypertarget{ref-canino2022embodiment}{}}%
+\bibitem[\citeproctext]{ref-canino2022embodiment}
 Canino, S., Raimo, S., Boccia, M., Di Vita, A., \& Palermo, L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chen2021emerging}{}}%
+\bibitem[\citeproctext]{ref-chen2021emerging}
 Chen, W.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chiou2013enactment}{}}%
+\bibitem[\citeproctext]{ref-chiou2013enactment}
 Chiou, W.-B., \& Lee, C.-C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-connell2018interoception}{}}%
+\bibitem[\citeproctext]{ref-connell2018interoception}
 Connell, L., Lynott, D., \& Banks, B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-craig2009you}{}}%
+\bibitem[\citeproctext]{ref-craig2009you}
 Craig, A. D. (2009). How do you feel---now? The anterior insula and human awareness. \emph{Nature Reviews Neuroscience}, \emph{10}(1), 59--70.
 
-\leavevmode\vadjust pre{\hypertarget{ref-critchley2004neural}{}}%
+\bibitem[\citeproctext]{ref-critchley2004neural}
 Critchley, H. D., Wiens, S., Rotshtein, P., Öhman, A., \& Dolan, R. J. (2004). Neural systems supporting interoceptive awareness. \emph{Nature Neuroscience}, \emph{7}(2), 189--195.
 
-\leavevmode\vadjust pre{\hypertarget{ref-damasio1996somatic}{}}%
+\bibitem[\citeproctext]{ref-damasio1996somatic}
 Damasio, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-desmedt2018heartbeat}{}}%
+\bibitem[\citeproctext]{ref-desmedt2018heartbeat}
 Desmedt, O., Luminet, O., \& Corneille, O.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-desmedt2022does}{}}%
+\bibitem[\citeproctext]{ref-desmedt2022does}
 Desmedt, O., Van Den Houte, M., Walentynowicz, M., Dekeyser, S., Luminet, O., \& Corneille, O.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ditto2006visceral}{}}%
+\bibitem[\citeproctext]{ref-ditto2006visceral}
 Ditto, P.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-domschke2010interoceptive}{}}%
-Domschke, K., Stevens, S., Pfleiderer, B., \& Gerlach, A.
-L.
-(2010).
-Interoceptive sensitivity in anxiety and anxiety disorders: An overview and integration of neurobiological findings.
-\emph{Clinical Psychology Review}, \emph{30}(1), 1--11.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dunn2010listening}{}}%
+\bibitem[\citeproctext]{ref-dunn2010listening}
 Dunn, B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-evans2011verbal}{}}%
+\bibitem[\citeproctext]{ref-evans2011verbal}
 Evans, A. D., \& Lee, K. (2011). Verbal deception from late childhood to middle adolescence and its relation to executive functioning skills. \emph{Developmental Psychology}, \emph{47}(4), 1108.
 
-\leavevmode\vadjust pre{\hypertarget{ref-furman2013interoceptive}{}}%
+\bibitem[\citeproctext]{ref-furman2013interoceptive}
 Furman, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-fustos2013embodiment}{}}%
+\bibitem[\citeproctext]{ref-fustos2013embodiment}
 Füstös, J., Gramann, K., Herbert, B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-gallant2020developing}{}}%
+\bibitem[\citeproctext]{ref-gallant2020developing}
 Gallant, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-gao2019body}{}}%
+\bibitem[\citeproctext]{ref-gao2019body}
 Gao, Q., Ping, X., \& Chen, W. (2019). Body influences on social cognition through interoception. \emph{Frontiers in Psychology}, \emph{10}, 2066.
 
-\leavevmode\vadjust pre{\hypertarget{ref-garfinkel2013interoception}{}}%
-Garfinkel, S.
-N., \& Critchley, H.
-D.
-(2013).
-Interoception, emotion and brain: New insights link internal physiology to social behaviour.
-Commentary on: {``Anterior insular cortex mediates bodily sensibility and social anxiety''} by terasawa et al.(2012).
-\emph{Social Cognitive and Affective Neuroscience}, \emph{8}(3), 231--234.
-
-\leavevmode\vadjust pre{\hypertarget{ref-garfinkel2015knowing}{}}%
+\bibitem[\citeproctext]{ref-garfinkel2015knowing}
 Garfinkel, S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-gendolla2009self}{}}%
+\bibitem[\citeproctext]{ref-gendolla2009self}
 Gendolla, G. H., \& Wicklund, R. A. (2009). Self-focused attention, perspective-taking, and false consensus. \emph{Social Psychology}, \emph{40}(2), 66--72.
 
-\leavevmode\vadjust pre{\hypertarget{ref-gonzalez2019can}{}}%
+\bibitem[\citeproctext]{ref-gonzalez2019can}
 Gonzalez-Billandon, J., Aroyo, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-hutchins2021development}{}}%
+\bibitem[\citeproctext]{ref-hanania2010selective}
+Hanania, R., \& Smith, L. B. (2010). Selective attention and attention switching: Towards a unified developmental approach. \emph{Developmental Science}, \emph{13}(4), 622--635.
+
+\bibitem[\citeproctext]{ref-hutchins2021development}
 Hutchins, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-jolliffe2006development}{}}%
+\bibitem[\citeproctext]{ref-jolliffe2006development}
 Jolliffe, D., \& Farrington, D. P. (2006). Development and validation of the basic empathy scale. \emph{Journal of Adolescence}, \emph{29}(4), 589--611.
 
-\leavevmode\vadjust pre{\hypertarget{ref-kanske2015dissecting}{}}%
+\bibitem[\citeproctext]{ref-kanske2015dissecting}
 Kanske, P., Böckler, A., Trautwein, F.-M., \& Singer, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kerns2004anterior}{}}%
+\bibitem[\citeproctext]{ref-kerns2004anterior}
 Kerns, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-khalsa2009pathways}{}}%
+\bibitem[\citeproctext]{ref-khalsa2009pathways}
 Khalsa, S. S., Rudrauf, D., Feinstein, J. S., \& Tranel, D. (2009). The pathways of interoceptive awareness. \emph{Nature Neuroscience}, \emph{12}(12), 1494--1496.
 
-\leavevmode\vadjust pre{\hypertarget{ref-kireev2013possible}{}}%
+\bibitem[\citeproctext]{ref-kireev2013possible}
 Kireev, M., Korotkov, A., Medvedeva, N., \& Medvedev, S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lee2021lying}{}}%
+\bibitem[\citeproctext]{ref-lee2021lying}
 Lee, J. Y. S., \& Imuta, K. (2021). Lying and theory of mind: A meta-analysis. \emph{Child Development}, \emph{92}(2), 536--553.
 
-\leavevmode\vadjust pre{\hypertarget{ref-legrand2022heart}{}}%
+\bibitem[\citeproctext]{ref-legrand2022heart}
 Legrand, N., Nikolova, N., Correa, C., Brændholt, M., Stuckert, A., Kildahl, N., Vejlø, M., Fardo, F., \& Allen, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lenggenhager2013listening}{}}%
+\bibitem[\citeproctext]{ref-lenggenhager2013listening}
 Lenggenhager, B., Azevedo, R.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-levine2022prosocial}{}}%
+\bibitem[\citeproctext]{ref-levine2022prosocial}
 Levine, E. E., \& Lupoli, M. J. (2022). Prosocial lies: Causes and consequences. \emph{Current Opinion in Psychology}, \emph{43}, 335--340.
 
-\leavevmode\vadjust pre{\hypertarget{ref-levine2014liars}{}}%
+\bibitem[\citeproctext]{ref-levine2014liars}
 Levine, E. E., \& Schweitzer, M. E. (2014). Are liars ethical? On the tension between benevolence and honesty. \emph{Journal of Experimental Social Psychology}, \emph{53}, 107--117.
 
-\leavevmode\vadjust pre{\hypertarget{ref-levine2015prosocial}{}}%
+\bibitem[\citeproctext]{ref-levine2015prosocial}
 Levine, E. E., \& Schweitzer, M. E. (2015). Prosocial lies: When deception breeds trust. \emph{Organizational Behavior and Human Decision Processes}, \emph{126}, 88--106.
 
-\leavevmode\vadjust pre{\hypertarget{ref-levine2011sender}{}}%
+\bibitem[\citeproctext]{ref-levine2011sender}
 Levine, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-performanceArticle}{}}%
+\bibitem[\citeproctext]{ref-performanceArticle}
 Lüdecke, D., Ben-Shachar, M., Patil, I., Waggoner, P., \& Makowski, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-insightArticle}{}}%
+\bibitem[\citeproctext]{ref-insightArticle}
 Lüdecke, D., Waggoner, P., \& Makowski, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2019bayestestr}{}}%
+\bibitem[\citeproctext]{ref-makowski2019bayestestr}
 Makowski, D., Ben-Shachar, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-correlationArticle}{}}%
+\bibitem[\citeproctext]{ref-correlationArticle}
 Makowski, D., Ben-Shachar, M., Patil, I., \& Lüdecke, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2021neurokit2}{}}%
+\bibitem[\citeproctext]{ref-makowski2021neurokit2}
 Makowski, D., Pham, T., Lau, Z.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2021structure}{}}%
+\bibitem[\citeproctext]{ref-makowski2021structure}
 Makowski, D., Pham, T., Lau, Z. J., Raine, A., \& Chen, S. (2021). The structure of deception: Validation of the lying profile questionnaire. \emph{Current Psychology}, 1--16.
 
-\leavevmode\vadjust pre{\hypertarget{ref-masip2017deception}{}}%
+\bibitem[\citeproctext]{ref-masip2017deception}
 Masip, J. (2017). Deception detection: State of the art and future prospects. \emph{Psicothema}, \emph{29}(2), 149--159.
 
-\leavevmode\vadjust pre{\hypertarget{ref-mehling2012multidimensional}{}}%
+\bibitem[\citeproctext]{ref-mehling2012multidimensional}
 Mehling, W. E., Price, C., Daubenmier, J. J., Acree, M., Bartmess, E., \& Stewart, A. (2012). The multidimensional assessment of interoceptive awareness (MAIA). \emph{PloS One}, \emph{7}(11), e48230.
 
-\leavevmode\vadjust pre{\hypertarget{ref-miller2015connections}{}}%
+\bibitem[\citeproctext]{ref-miller2015connections}
 Miller, J. E. (2015). \emph{The connections between self-monitoring and theory of mind}.
 
-\leavevmode\vadjust pre{\hypertarget{ref-von2023social}{}}%
+\bibitem[\citeproctext]{ref-von2023social}
 Mohr, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-molnar2022anterior}{}}%
+\bibitem[\citeproctext]{ref-molnar2022anterior}
 Molnar-Szakacs, I., \& Uddin, L. Q. (2022). Anterior insula as a gatekeeper of executive control. \emph{Neuroscience \& Biobehavioral Reviews}, 104736.
 
-\leavevmode\vadjust pre{\hypertarget{ref-murphy2019classifying}{}}%
+\bibitem[\citeproctext]{ref-murphy2019classifying}
 Murphy, J., Catmur, C., \& Bird, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ondobaka2017role}{}}%
+\bibitem[\citeproctext]{ref-ondobaka2017role}
 Ondobaka, S., Kilner, J., \& Friston, K. (2017). The role of interoceptive inference in theory of mind. \emph{Brain and Cognition}, \emph{112}, 64--68.
 
-\leavevmode\vadjust pre{\hypertarget{ref-oviatt2018handbook}{}}%
+\bibitem[\citeproctext]{ref-oviatt2018handbook}
 Oviatt, S., Schuller, B., Cohen, P.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-owens2018investigating}{}}%
+\bibitem[\citeproctext]{ref-owens2018investigating}
 Owens, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-paulhus2002dark}{}}%
+\bibitem[\citeproctext]{ref-paulhus2002dark}
 Paulhus, D. L., \& Williams, K. M. (2002). The dark triad of personality: Narcissism, machiavellianism, and psychopathy. \emph{Journal of Research in Personality}, \emph{36}(6), 556--563.
 
-\leavevmode\vadjust pre{\hypertarget{ref-peirce2019psychopy2}{}}%
+\bibitem[\citeproctext]{ref-peirce2019psychopy2}
 Peirce, J., Gray, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-peleg2019lie}{}}%
-Peleg, D., Ayal, S., Ariely, D., \& Hochman, G. (2019). The lie deflator-the effect of polygraph test feedback on subsequent (dis) honesty. \emph{Judgment \& Decision Making}, \emph{16}(6).
-
-\leavevmode\vadjust pre{\hypertarget{ref-petzschner2021computational}{}}%
+\bibitem[\citeproctext]{ref-petzschner2021computational}
 Petzschner, F. H., Garfinkel, S. N., Paulus, M. P., Koch, C., \& Khalsa, S. S. (2021). Computational models of interoception and body regulation. \emph{Trends in Neurosciences}, \emph{44}(1), 63--76.
 
-\leavevmode\vadjust pre{\hypertarget{ref-pinna2020systematic}{}}%
+\bibitem[\citeproctext]{ref-pinna2020systematic}
 Pinna, T., \& Edwards, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-plans2021measuring}{}}%
+\bibitem[\citeproctext]{ref-plans2021measuring}
 Plans, D., Ponzo, S., Morelli, D., Cairo, M., Ring, C., Keating, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-pollatos2007heart}{}}%
+\bibitem[\citeproctext]{ref-pollatos2007heart}
 Pollatos, O., Herbert, B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ponzo2021measuring}{}}%
+\bibitem[\citeproctext]{ref-ponzo2021measuring}
 Ponzo, S., Morelli, D., Suksasilp, C., Cairo, M., \& Plans, D. (2021). Measuring interoception: The CARdiac elevation detection task. \emph{Frontiers in Psychology}, \emph{12}.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
+\bibitem[\citeproctext]{ref-RCoreTeam2022}
 R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
 
-\leavevmode\vadjust pre{\hypertarget{ref-rassin2023psychopathy}{}}%
+\bibitem[\citeproctext]{ref-rassin2023psychopathy}
 Rassin, E., Sergiou, C., Linden, D. van der, \& Dongen, J. van. (2023). Psychopathy as a predisposition to lie hedonistically. \emph{Psychology, Crime \& Law}, 1--8.
 
-\leavevmode\vadjust pre{\hypertarget{ref-riggio1987verbal}{}}%
+\bibitem[\citeproctext]{ref-riggio1987verbal}
 Riggio, R. E., Tucker, J., \& Widaman, K. F. (1987). Verbal and nonverbal cues as mediators of deception ability. \emph{Journal of Nonverbal Behavior}, \emph{11}, 126--145.
 
-\leavevmode\vadjust pre{\hypertarget{ref-roheger2022progression}{}}%
+\bibitem[\citeproctext]{ref-roheger2022progression}
 Roheger, M., Brenning, J., Riemann, S., Martin, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-rosky2013f}{}}%
+\bibitem[\citeproctext]{ref-rosky2013f}
 Rosky, J. W. (2013). The (f) utility of post-conviction polygraph testing. \emph{Sexual Abuse}, \emph{25}(3), 259--281.
 
-\leavevmode\vadjust pre{\hypertarget{ref-rubin2003belief}{}}%
+\bibitem[\citeproctext]{ref-rubin2003belief}
 Rubin, D. C., Schrauf, R. W., \& Greenberg, D. L. (2003). Belief and recollection of autobiographical memories. \emph{Memory \& Cognition}, \emph{31}, 887--901.
 
-\leavevmode\vadjust pre{\hypertarget{ref-scaffidi2016self}{}}%
+\bibitem[\citeproctext]{ref-scaffidi2016self}
 Scaffidi Abbate, C., Boca, S., \& Gendolla, G. H. (2016). Self-awareness, perspective-taking, and egocentrism. \emph{Self and Identity}, \emph{15}(4), 371--380.
 
-\leavevmode\vadjust pre{\hypertarget{ref-schandry1981heart}{}}%
+\bibitem[\citeproctext]{ref-schandry1981heart}
 Schandry, R. (1981). Heart beat perception and emotional experience. \emph{Psychophysiology}, \emph{18}(4), 483--488.
 
-\leavevmode\vadjust pre{\hypertarget{ref-sebastian2012neural}{}}%
+\bibitem[\citeproctext]{ref-sebastian2012neural}
 Sebastian, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-seth2012interoceptive}{}}%
+\bibitem[\citeproctext]{ref-seth2012interoceptive}
 Seth, A. K., Suzuki, K., \& Critchley, H. D. (2012). An interoceptive predictive coding model of conscious presence. \emph{Frontiers in Psychology}, \emph{2}, 395.
 
-\leavevmode\vadjust pre{\hypertarget{ref-shah2017heart}{}}%
+\bibitem[\citeproctext]{ref-shah2017heart}
 Shah, P., Catmur, C., \& Bird, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-shamay2007dissociable}{}}%
+\bibitem[\citeproctext]{ref-shamay2007dissociable}
 Shamay-Tsoory, S. G., \& Aharon-Peretz, J. (2007). Dissociable prefrontal networks for cognitive and affective theory of mind: A lesion study. \emph{Neuropsychologia}, \emph{45}(13), 3054--3067.
 
-\leavevmode\vadjust pre{\hypertarget{ref-shamay2010role}{}}%
+\bibitem[\citeproctext]{ref-shamay2010role}
 Shamay-Tsoory, S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-sip2008detecting}{}}%
+\bibitem[\citeproctext]{ref-sip2008detecting}
 Sip, K. E., Roepstorff, A., McGregor, W., \& Frith, C. D. (2008). Detecting deception: The scope and limits. \emph{Trends in Cognitive Sciences}, \emph{12}(2), 48--53.
 
-\leavevmode\vadjust pre{\hypertarget{ref-sip2012if}{}}%
+\bibitem[\citeproctext]{ref-sip2012if}
 Sip, K.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-sternglanz2019review}{}}%
+\bibitem[\citeproctext]{ref-sternglanz2019review}
 Sternglanz, R. W., Morris, W. L., Morrow, M., \& Braverman, J. (2019). A review of meta-analyses about deception detection. \emph{The Palgrave Handbook of Deceptive Communication}, 303--326.
 
-\leavevmode\vadjust pre{\hypertarget{ref-sugawara2020effects}{}}%
+\bibitem[\citeproctext]{ref-sugawara2020effects}
 Sugawara, A., Terasawa, Y., Katsunuma, R., \& Sekiguchi, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-takuma1995alternative}{}}%
+\bibitem[\citeproctext]{ref-takuma1995alternative}
 Takuma, K., Hori, S., Sasaki, J., Shinozawa, Y., Yoshikawa, T., Handa, S., Horikawa, M., \& Aikawa, N.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-talwar2017role}{}}%
+\bibitem[\citeproctext]{ref-talwar2017role}
 Talwar, V., Crossman, A., \& Wyman, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-talwar2007lying}{}}%
+\bibitem[\citeproctext]{ref-talwar2007lying}
 Talwar, V., Gordon, H.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-vabba2022interoceptive}{}}%
+\bibitem[\citeproctext]{ref-vabba2022interoceptive}
 Vabba, A., Porciello, G., Panasiti, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-verigin2019lie}{}}%
+\bibitem[\citeproctext]{ref-verigin2019lie}
 Verigin, B. L., Meijer, E. H., Bogaard, G., \& Vrij, A. (2019). Lie prevalence, lie characteristics and strategies of self-reported good liars. \emph{PloS One}, \emph{14}(12), e0225566.
 
-\leavevmode\vadjust pre{\hypertarget{ref-viji2022history}{}}%
+\bibitem[\citeproctext]{ref-viji2022history}
 Viji, D., Gupta, N., \& Parekh, K. H. (2022). History of deception detection techniques. \emph{Proceedings of International Conference on Deep Learning, Computing and Intelligence}, 373--387.
 
-\leavevmode\vadjust pre{\hypertarget{ref-walczyk2022err}{}}%
+\bibitem[\citeproctext]{ref-walczyk2022err}
 Walczyk, J. J., \& Cockrell, N. F. (2022). To err is human but not deceptive. \emph{Memory \& Cognition}, \emph{50}(1), 232--244.
 
-\leavevmode\vadjust pre{\hypertarget{ref-walczyk2014social}{}}%
+\bibitem[\citeproctext]{ref-walczyk2014social}
 Walczyk, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-walczyk2009cognitive}{}}%
+\bibitem[\citeproctext]{ref-walczyk2009cognitive}
 Walczyk, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-wang2019anterior}{}}%
+\bibitem[\citeproctext]{ref-wang2019anterior}
 Wang, X., Wu, Q., Egan, L., Gu, X., Liu, P., Gu, H., Yang, Y., Luo, J., Wu, Y., Gao, Z., et al.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-weiss2014interaction}{}}%
+\bibitem[\citeproctext]{ref-weiss2014interaction}
 Weiss, S., Sack, M., Henningsen, P., \& Pollatos, O. (2014). On the interaction of self-regulation, interoception and pain perception. \emph{Psychopathology}, \emph{47}(6), 377--382.
 
-\leavevmode\vadjust pre{\hypertarget{ref-wellman2001meta}{}}%
+\bibitem[\citeproctext]{ref-wellman2001meta}
 Wellman, H. M., Cross, D., \& Watson, J. (2001). Meta-analysis of theory-of-mind development: The truth about false belief. \emph{Child Development}, \emph{72}(3), 655--684.
 
-\leavevmode\vadjust pre{\hypertarget{ref-williams2016valjean}{}}%
+\bibitem[\citeproctext]{ref-williams2016valjean}
 Williams, E. F., Pizarro, D., Ariely, D., \& Weinberg, J. D. (2016). The valjean effect: Visceral states and cheating. \emph{Emotion}, \emph{16}(6), 897.
 
-\leavevmode\vadjust pre{\hypertarget{ref-wundrack2023mindful}{}}%
+\bibitem[\citeproctext]{ref-wundrack2023mindful}
 Wundrack, R., \& Specht, J. (2023). Mindful self-focus--an interaction affecting theory of mind? \emph{Plos One}, \emph{18}(2), e0279544.
 
-\leavevmode\vadjust pre{\hypertarget{ref-yoris2015roles}{}}%
-Yoris, A., Esteves, S., Couto, B., Melloni, M., Kichic, R., Cetkovich, M., Favaloro, R., Moser, J., Manes, F., Ibanez, A., et al.
-(2015).
-The roles of interoceptive sensitivity and metacognitive interoception in panic.
-\emph{Behavioral and Brain Functions}, \emph{11}(1), 1--6.
-
-\leavevmode\vadjust pre{\hypertarget{ref-zvi2018correlates}{}}%
+\bibitem[\citeproctext]{ref-zvi2018correlates}
 Zvi, L., \& Elaad, E.

### 2024-07-04 paper/manuscript.tex
knitted pdf

--- 2024-06-14 paper/manuscript.tex
@@
 The present study examined the contribution of ToM and interoception on our ability to lie using a directed lie paradigm with two conditions (``Interrogation'' and ``Polygraph'') designed to enhance each of the two mechanisms.
-Interestingly, we found that when participants were presented with (fake) physiological feedback (the polygraph condition), instead of a face of a person they had to lie to (the interrogation condition), their response time for both lies and truths increased, as did their heart rate.
-Although the condition did not impact the subjective confidence that participants had in their answers, it suggests that believing oneself to be submitted to a machine that is supposedly able to detect deception by interpreting physiological signals is a harder and/or more stressful condition than lying to a person.
-While research linking interoception and deception is limited, our results are in line with studies that show an association between interoceptive awareness and anxiety (Domschke et al., 2010; Garfinkel \& Critchley, 2013; Yoris et al., 2015).
-Specifically, enhancing one's attention towards their internal bodily signals could have resulted in a hyper-vigilance towards physiological sensations that is perceived negatively.
-This is consistent with previous deception detection studies, in which participants' spontaneous lying behaviour only decreased when they were given feedback by a polygraph machine, but not when no feedback was given (Peleg et al., 2019).
-By extension, our study adds to the controversial discourse surrounding the use of physiological measures in past deception research, further questioning its validity as an indicator of deception (Oviatt et al., 2018; Rosky, 2013).
-
-Our results suggest that higher ToM abilities were related to slower and less confident lies, but only in the polygraph condition.
+Interestingly, we found that when participants' responses were perceived to be evaluated by a person (the interrogation condition), instead of (fake) lie detection machine (the polygraph condition), their response time for both lies and truths were faster, and their heart rate was elevated.
+Although the condition did not impact the subjective confidence that participants had in their answers, the pattern of results suggests that believing one's response is being evaluated by a person, instead of a machine, could induce more fear, consequently speeding up the response and increasing the physiological arousal (Aylward et al., 2017).
+Alternatively, the slower response in the polygraph condition could be explained by the established attentional switching hypothesis, which posits that an increase in attention towards internal signals and managing one's emotional reaction would confer less cognitive resources available, thereby resulting in individuals taking a longer time to respond (Arnold et al., 2019; Hanania \& Smith, 2010).
+While the impacts of external settings on individuals' responses warrant further investigation, the results highlight how physiological responses can be easily confounded by other factors (e.g., presence or absence of a stimuli), independent of whether one is lying or telling the truth.
+By extension, our study concurs with the controversial discourse surrounding the use of physiological measures in deception research (Oviatt et al., 2018; Rosky, 2013).
+
+Furthermore, our results suggest that higher ToM abilities were related to slower and less confident lies, but only in the polygraph condition.
 While previous bodies of work have reported mixed findings regarding the association between interoception and ToM (Chiou \& Lee, 2013; Gendolla \& Wicklund, 2009; Scaffidi Abbate et al., 2016; Wundrack \& Specht, 2023), our results suggest the two are negatively linked.
@@
 \emph{Journal of Cognitive Neuroscience}, \emph{19}(2), 287--295.
+
+\leavevmode\vadjust pre{\hypertarget{ref-arnold2019interoception}{}}%
+Arnold, A. J., Winkielman, P., \& Dobkins, K. (2019). Interoception and social connection. \emph{Frontiers in Psychology}, \emph{10}, 2589.
+
+\leavevmode\vadjust pre{\hypertarget{ref-aylward2017impact}{}}%
+Aylward, J., Valton, V., Goer, F., Mkrtchian, A., Lally, N., Peters, S., Limbachya, T., \& Robinson, O.
+J.
+(2017).
+The impact of induced anxiety on affective response inhibition.
+\emph{Royal Society Open Science}, \emph{4}(6), 170084.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-domschke2010interoceptive}{}}%
-Domschke, K., Stevens, S., Pfleiderer, B., \& Gerlach, A.
-L.
-(2010).
-Interoceptive sensitivity in anxiety and anxiety disorders: An overview and integration of neurobiological findings.
-\emph{Clinical Psychology Review}, \emph{30}(1), 1--11.
-
 \leavevmode\vadjust pre{\hypertarget{ref-dunn2010listening}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-garfinkel2013interoception}{}}%
-Garfinkel, S.
-N., \& Critchley, H.
-D.
-(2013).
-Interoception, emotion and brain: New insights link internal physiology to social behaviour.
-Commentary on: {``Anterior insular cortex mediates bodily sensibility and social anxiety''} by terasawa et al.(2012).
-\emph{Social Cognitive and Affective Neuroscience}, \emph{8}(3), 231--234.
-
 \leavevmode\vadjust pre{\hypertarget{ref-garfinkel2015knowing}{}}%
@@
 \emph{Frontiers in Robotics and AI}, \emph{6}, 64.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hanania2010selective}{}}%
+Hanania, R., \& Smith, L. B. (2010). Selective attention and attention switching: Towards a unified developmental approach. \emph{Developmental Science}, \emph{13}(4), 622--635.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-peleg2019lie}{}}%
-Peleg, D., Ayal, S., Ariely, D., \& Hochman, G. (2019). The lie deflator-the effect of polygraph test feedback on subsequent (dis) honesty. \emph{Judgment \& Decision Making}, \emph{16}(6).
-
 \leavevmode\vadjust pre{\hypertarget{ref-petzschner2021computational}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-yoris2015roles}{}}%
-Yoris, A., Esteves, S., Couto, B., Melloni, M., Kichic, R., Cetkovich, M., Favaloro, R., Moser, J., Manes, F., Ibanez, A., et al.
-(2015).
-The roles of interoceptive sensitivity and metacognitive interoception in panic.
-\emph{Behavioral and Brain Functions}, \emph{11}(1), 1--6.
-
 \leavevmode\vadjust pre{\hypertarget{ref-zvi2018correlates}{}}%

### 2024-07-10 paper/manuscript.Rmd
R2

@@
 While often conceptualized to be immoral and unconscionable, lying is ubiquitous in everyday life, and being able to lie skillfully can sometimes facilitate interpersonal relationships, helping us avoid conflict or causing emotional harm to others [@levine2022prosocial].
-In fact, recent research shows that certain forms of deception, such as prosocial lies (i.e., false statements told to benefit others; @levine2022prosocial), can increase trust [@levine2015prosocial].
+In fact, recent research shows that certain forms of deception, such as prosocial lies [i.e., false statements told to benefit others, @levine2022prosocial], can increase trust [@levine2015prosocial].
 Moreover, individuals who told altruistic lies were perceived as more benevolent than those who were honest [@levine2014liars].
@@
 The present study examined the contribution of ToM and interoception on our ability to lie using a directed lie paradigm with two conditions ("Interrogation" and "Polygraph") designed to enhance each of the two mechanisms.
-Interestingly, we found that when participants' responses were perceived to be evaluated by a person (the interrogation condition), instead of (fake) lie detection machine (the polygraph condition), their response time for both lies and truths were faster, and their heart rate was elevated.
+Interestingly, we found that when participants' responses were perceived to be evaluated by a person (the interrogation condition), instead of the lie detection machine (the polygraph condition), their response time for both lies and truths were faster, and their heart rate was elevated.
 Although the condition did not impact the subjective confidence that participants had in their answers, the pattern of results suggests that believing one's response is being evaluated by a person, instead of a machine, could induce more fear, consequently speeding up the response and increasing the physiological arousal [@aylward2017impact].
 Alternatively, the slower response in the polygraph condition could be explained by the established attentional switching hypothesis, which posits that an increase in attention towards internal signals and managing one's emotional reaction would confer less cognitive resources available, thereby resulting in individuals taking a longer time to respond [@arnold2019interoception; @hanania2010selective].
-While the impacts of external settings on individuals' responses warrant further investigation, the results highlight how physiological responses can be easily confounded by other factors (e.g., presence or absence of a stimuli), independent of whether one is lying or telling the truth.
+While the impacts of external settings on individuals' responses warrant further investigation, the results highlight how physiological responses can be easily confounded by other factors, independent of whether one is lying or telling the truth.
+For instance, the presence or absence of the "interrogator", or the saliency of the moral nature of the task [e.g.
+@peleg2019lie, argues that the polygraph test alone also acts as a "moral reminder", framing the possibility that physiological arousal in a polygraph context might be partially a reflection of individuals’ attention directed to their own moral standards].
 By extension, our study concurs with the controversial discourse surrounding the use of physiological measures in deception research [@rosky2013f; @oviatt2018handbook].

### 2024-07-10 paper/manuscript.tex
R2

@@
 Levine \& Lupoli, 2022).
-In fact, recent research shows that certain forms of deception, such as prosocial lies (i.e., false statements told to benefit others; E.
+In fact, recent research shows that certain forms of deception, such as prosocial lies (i.e., false statements told to benefit others, E.
 E.
-Levine and Lupoli (2022)), can increase trust (E.
+Levine \& Lupoli, 2022), can increase trust (E.
 E.
@@
 The present study examined the contribution of ToM and interoception on our ability to lie using a directed lie paradigm with two conditions (``Interrogation'' and ``Polygraph'') designed to enhance each of the two mechanisms.
-Interestingly, we found that when participants' responses were perceived to be evaluated by a person (the interrogation condition), instead of (fake) lie detection machine (the polygraph condition), their response time for both lies and truths were faster, and their heart rate was elevated.
+Interestingly, we found that when participants' responses were perceived to be evaluated by a person (the interrogation condition), instead of the lie detection machine (the polygraph condition), their response time for both lies and truths were faster, and their heart rate was elevated.
 Although the condition did not impact the subjective confidence that participants had in their answers, the pattern of results suggests that believing one's response is being evaluated by a person, instead of a machine, could induce more fear, consequently speeding up the response and increasing the physiological arousal (Aylward et al., 2017).
 Alternatively, the slower response in the polygraph condition could be explained by the established attentional switching hypothesis, which posits that an increase in attention towards internal signals and managing one's emotional reaction would confer less cognitive resources available, thereby resulting in individuals taking a longer time to respond (Arnold et al., 2019; Hanania \& Smith, 2010).
-While the impacts of external settings on individuals' responses warrant further investigation, the results highlight how physiological responses can be easily confounded by other factors (e.g., presence or absence of a stimuli), independent of whether one is lying or telling the truth.
+While the impacts of external settings on individuals' responses warrant further investigation, the results highlight how physiological responses can be easily confounded by other factors, independent of whether one is lying or telling the truth.
+For instance, the presence or absence of the ``interrogator'', or the saliency of the moral nature of the task (e.g.
+Peleg et al., 2019, argues that the polygraph test alone also acts as a ``moral reminder,'' framing the possibility that physiological arousal in a polygraph context might be partially a reflection of individuals' attention directed to their own moral standards).
 By extension, our study concurs with the controversial discourse surrounding the use of physiological measures in deception research (Oviatt et al., 2018; Rosky, 2013).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-peleg2019lie}{}}%
+Peleg, D., Ayal, S., Ariely, D., \& Hochman, G. (2019). The lie deflator-the effect of polygraph test feedback on subsequent (dis) honesty. \emph{Judgment \& Decision Making}, \emph{16}(6).
+
 \leavevmode\vadjust pre{\hypertarget{ref-petzschner2021computational}{}}%

### 2024-09-15 paper/manuscript.Rmd
minor
R3

@@
 output:
+  papaja::apa6_word:
+    keep_tex: yes
   papaja::apa6_pdf:
-    keep_tex: yes
-  papaja::apa6_word:
     keep_tex: yes
@@
 However, some studies have instead found heightened interoceptive attention (one's self-focus towards internal bodily signals), to predict immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening].
-Extending these findings to social cognition, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high, whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
+Extending these findings to social cognition, @vabba2022interoceptive further reports individuals with lower interoception told significantly fewer egoistic lies when the social reputational stakes were high, whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
 Given the scarce research on interoception and deception, more studies are herein needed to clarify these mixed findings.
@@
 Four participants were excluded as their data was not recorded due to technical issues.
-The final sample consists of 26 participants (Mean age = 20.9, SD = 2.0, range:[18, 25], Sex: 65.4% women, 34.6% men).
+The final sample consisted of 26 participants (Mean age = 20.9, SD = 2.0, range:[18, 25], Sex: 65.4% women, 34.6% men).
 The heart rate of one participant and response time of one participant were excluded from further analysis due to extreme outlying values.
-To maximize statistical power, the problematic data from these 2 participants were only excluded from analyses involving those measures; all other data were retained for analyses.
+To maximize statistical power, the problematic data from these two participants were only excluded from analyses involving those measures; all other data were retained for analyses.
 
@@
 The Yoni Task [@shamay2007dissociable] is a behavioral task which assesses first and second-order ToM abilities in both cognitive and affective domains.
-Participants were presented with the face of a character named "Yoni", surrounded by four colored pictures of objects or faces, one in each corner of the screen.
+Participants were presented with the face of a character named "Yoni", surrounded by four colored pictures of objects or faces - one in each corner of the screen.
 In total, each participant completed 101 trials - 49 trials assessing their affective ToM abilities, 37 trials assessing their cognitive ToM abilities and 15 control trials.
@@
 Their goal was to make convincing answers, so that truths would be judged as truths by the receiver, and lies as lies.
-The nature of the receiver was different depending on the condition: participants were told that for half of the trials, they would have to convince another participant that would be observing them from a separate room (COVID regulations were used as a justification) via a webcam connection (*Interrogation* condition).
+The nature of the receiver was different depending on the condition: participants were told that for half of the trials, they would have to convince another participant who would be observing them from a separate room (COVID regulations were used as a justification) via a webcam connection (*Interrogation* condition).
 For the remaining trials, participants were tasked to convince a "lie detection machine" that would be assessing their behaviour through their physiological signals (*Polygraph* condition).
@@
 
-Finally, on top of the deception task, we also measured participants' self-reported tendency to lie in their everyday life using the *Lie Scale* [@makowski2021structure], a 16-item questionnaire that assesses 4 dispositional lying dimensions - Ability ($\alpha = 0.92$), Frequency ($\alpha = 0.66$), Negativity ($\alpha = 0.66$), and Contextuality ($\alpha = 0.70$).
+Finally, on top of the deception task, we also measured participants' self-reported tendency to lie in their everyday life using the *Lie Scale* [@makowski2021structure], a 16-item questionnaire that assesses four dispositional lying dimensions - Ability ($\alpha = 0.92$), Frequency ($\alpha = 0.66$), Negativity ($\alpha = 0.66$), and Contextuality ($\alpha = 0.70$).
 
@@
 
-A within-subjects design was used in the present study, which is comprised of 2 sessions, to investigate the roles interoception and ToM play in lying ability.
+A within-subjects design was used in the present study, which is comprised of two sessions, to investigate the roles interoception and ToM play in lying ability.
 During session 1, participants answered a brief demographic survey as well as a questionnaire regarding their personal preferences and subjective experiences (the AMQ), followed by a series of psychological scales (i.e., BES, MAIA and Lie scale), which were randomly displayed.
@@
 Finally, we investigated the relationship between the deception scale traits, and the ToM and interoception scores using Bayesian correlations.
-As all the analyses and data have been made available, we will in the manuscript focus on significant, i.e., - in this context - statistically reliable and in our opinion theoretically relevant.
+All analyses and data have been made publicly available.
+Therefore, in this manuscript, we will focus on discussing significant findings, which - in this context - are statistically reliable and in our opinion theoretically relevant results.
 
@@
 Compared to truths, lies were rated with less confidence ($\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%$), but no significant difference between the conditions was found.
-On the other hand, the RT did not differ between truths and lies, but was significantly slower in the polygraph condition for both conditions ($\Delta=0.25$, 95\% CI [0.62, 0.41], pd = 100\%).
-The heart rate was significantly more elevated during lies as compared to truths ($\Delta=1.16$, 95\% CI [0.57, 1.73], pd = 100\%), and during interrogation as compared to the polygraph condition ($\Delta=4.84$, 95\% CI [4.23, 5.44], pd = 100\%).
+On the other hand, the RT did not differ between truths and lies, but was significantly slower in the polygraph condition for both conditions ($\Delta=0.25,~95\% CI [0.62, 0.41],~pd = 100\%$).
+The heart rate was significantly more elevated during lies as compared to truths ($\Delta=1.16,~95\% CI [0.57, 1.73],~pd = 100\%$), and during interrogation as compared to the polygraph condition ($\Delta=4.84,~95\% CI [4.23, 5.44],~pd = 100\%$).
 
-The indirect phrasing of the question only had a significant effect on RT ($\beta=0.36$, 95\% CI [0.21, 0.51], pd = 100\%), leading to slower answers, regardless of whether they were lies or truths.
+The indirect phrasing of the question only had a significant effect on RT ($\beta=0.36,~95\% CI [0.21, 0.51],~pd = 100\%$), leading to slower answers, regardless of whether they were lies or truths.
 Given this absence of interaction with the type of answers in any modality, this factor was not included in subsequent analysis.
@@
 
-The higher composite *ToM* score was significantly associated with a decreased confidence in lies ($\beta=-0.19$, 95\% CI [-0.36, -0.02], pd = 98.47\%), specifically in the polygraph condition.
+The higher composite *ToM* score was significantly associated with a decreased confidence in lies ($\beta=-0.19,~95\% CI [-0.36, -0.02],~pd = 98.47\%$), specifically in the polygraph condition.
 **Figure 1** illustrates the interindividual correlates of lying confidence.
-The higher composite *ToM* score was also associated with slower answers for lies ($\beta=0.42$, 95\% CI [0.01, 0.83], pd = 97.67\%), specifically in the polygraph condition.
+The higher composite *ToM* score was also associated with slower answers for lies ($\beta=0.42,~95\% CI [0.01, 0.83],~pd = 97.67\%$), specifically in the polygraph condition.
 No significant effect was found with regards to dispositional lying traits, heart rate, and RT for truths in both polygraph and interrogation conditions.

### 2024-09-15 paper/manuscript.Rmd
R3

@@
 
-The higher *Focus* interoception score was significantly associated with an increased confidence in truths in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$); a consistent pattern, although non-significant, was found for confidence in truth in the interrogation conditions ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%$).
+The higher *Focus* interoception score was significantly associated with an increased confidence in truths in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$); a consistent pattern, although non-significant, was found for confidence in truths in the interrogation condition ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%$).
 The *Focus* interoception score was also positively correlated with the dispositional lying *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$).
-No significant association was found with RT for lies and heart rate in both conditions
+No significant association was found with RT for lies and heart rate in both conditions.
 

### 2024-09-16 paper/manuscript.Rmd
R3

@@
 Participants were presented with the face of a character named "Yoni", surrounded by four colored pictures of objects or faces - one in each corner of the screen.
-In total, each participant completed 101 trials - 49 trials assessing their affective ToM abilities, 37 trials assessing their cognitive ToM abilities and 15 control trials.
-During each trial, participants were instructed to respond based on specific corresponding cues such as the directions of Yoni's eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical ToM).
-More specifically, in first-order trials, participants were instructed to make inferences about Yoni's mental state with regards to the objects surrounding it (e.g., "Yoni is thinking of..." for cognitive ToM trials or "Yoni likes..." for affective ToM trials).
-In more complex second-order trials, participants had to correctly infer the interaction between Yoni and others' mental states (e.g., "Yoni is thinking of the fruit that ...
+In total, each participant completed 101 trials - 49 trials assessing their affective ToM abilities, 37 trials assessing their cognitive ToM abilities and 15 control trials (physical TOM).
+During each trial, participants were given an instruction (e.g., "Yoni is thinking of ..." or "Yoni loves ...") and a specific cue (e.g., the directions of Yoni's eye gaze or Yoni's facial expressions) which they used to choose the correct answer among the four options presented.
+Participants were instructed to respond as quickly as possible using the corresponding keys on the given keyboard.
+In the control trials (physical TOM), the instruction (e.g., "Yoni is close to ...") and the cue (e.g., physical distance between Yoni and the options) required participants to respond based on Yoni's physical context.
+Additionally, the instructions were changed to assess the first and second-order abilities for cognitive and affective TOM.
+In first-order TOM trials, participants were instructed to make inferences about Yoni's mental state with regards to the objects surrounding it (e.g., "Yoni is thinking of..." for cognitive ToM trials or "Yoni likes..." for affective ToM trials).
+In more complex second-order TOM trials, participants had to correctly infer the interaction between Yoni and others' mental states (e.g., "Yoni is thinking of the fruit that ...
 wants" for cognitive ToM trials or "Yoni likes the fruit that ...

### 2024-10-04 paper/manuscript.tex
edits

@@
 Extending these findings to social cognition, Vabba et al.
-(2022) further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high, whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
+(2022) further reports individuals with lower interoception told significantly fewer egoistic lies when the social reputational stakes were high, whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.
 Given the scarce research on interoception and deception, more studies are herein needed to clarify these mixed findings.
@@
 Four participants were excluded as their data was not recorded due to technical issues.
-The final sample consists of 26 participants (Mean age = 20.9, SD = 2.0, range:{[}18, 25{]}, Sex: 65.4\% women, 34.6\% men).
+The final sample consisted of 26 participants (Mean age = 20.9, SD = 2.0, range:{[}18, 25{]}, Sex: 65.4\% women, 34.6\% men).
 The heart rate of one participant and response time of one participant were excluded from further analysis due to extreme outlying values.
-To maximize statistical power, the problematic data from these 2 participants were only excluded from analyses involving those measures; all other data were retained for analyses.
+To maximize statistical power, the problematic data from these two participants were only excluded from analyses involving those measures; all other data were retained for analyses.
 
@@
 The Yoni Task (Shamay-Tsoory \& Aharon-Peretz, 2007) is a behavioral task which assesses first and second-order ToM abilities in both cognitive and affective domains.
-Participants were presented with the face of a character named ``Yoni'', surrounded by four colored pictures of objects or faces, one in each corner of the screen.
-In total, each participant completed 101 trials - 49 trials assessing their affective ToM abilities, 37 trials assessing their cognitive ToM abilities and 15 control trials.
-During each trial, participants were instructed to respond based on specific corresponding cues such as the directions of Yoni's eye gaze, facial expressions etc., In the control trials, participants made judgements based on Yoni's physical context (physical ToM).
-More specifically, in first-order trials, participants were instructed to make inferences about Yoni's mental state with regards to the objects surrounding it (e.g., ``Yoni is thinking of\ldots{}'' for cognitive ToM trials or ``Yoni likes\ldots{}'' for affective ToM trials).
-In more complex second-order trials, participants had to correctly infer the interaction between Yoni and others' mental states (e.g., ``Yoni is thinking of the fruit that \ldots{} wants'' for cognitive ToM trials or ``Yoni likes the fruit that \ldots{} likes'' for affective ToM trials).
+Participants were presented with the face of a character named ``Yoni'', surrounded by four colored pictures of objects or faces - one in each corner of the screen.
+In total, each participant completed 101 trials - 49 trials assessing their affective ToM abilities, 37 trials assessing their cognitive ToM abilities and 15 control trials (physical TOM).
+During each trial, participants were given an instruction (e.g., ``Yoni is thinking of \ldots{}'' or ``Yoni loves \ldots{}'') and a specific cue (e.g., the directions of Yoni's eye gaze or Yoni's facial expressions) which they used to choose the correct answer among the four options presented.
+Participants were instructed to respond as quickly as possible using the corresponding keys on the given keyboard.
+In the control trials (physical TOM), the instruction (e.g., ``Yoni is close to \ldots{}'') and the cue (e.g., physical distance between Yoni and the options) required participants to respond based on Yoni's physical context.
+Additionally, the instructions were changed to assess the first and second-order abilities for cognitive and affective TOM.
+In first-order TOM trials, participants were instructed to make inferences about Yoni's mental state with regards to the objects surrounding it (e.g., ``Yoni is thinking of\ldots{}'' for cognitive ToM trials or ``Yoni likes\ldots{}'' for affective ToM trials).
+In more complex second-order TOM trials, participants had to correctly infer the interaction between Yoni and others' mental states (e.g., ``Yoni is thinking of the fruit that \ldots{} wants'' for cognitive ToM trials or ``Yoni likes the fruit that \ldots{} likes'' for affective ToM trials).
 
@@
 Their goal was to make convincing answers, so that truths would be judged as truths by the receiver, and lies as lies.
-The nature of the receiver was different depending on the condition: participants were told that for half of the trials, they would have to convince another participant that would be observing them from a separate room (COVID regulations were used as a justification) via a webcam connection (\emph{Interrogation} condition).
+The nature of the receiver was different depending on the condition: participants were told that for half of the trials, they would have to convince another participant who would be observing them from a separate room (COVID regulations were used as a justification) via a webcam connection (\emph{Interrogation} condition).
 For the remaining trials, participants were tasked to convince a ``lie detection machine'' that would be assessing their behaviour through their physiological signals (\emph{Polygraph} condition).
@@
 
-Finally, on top of the deception task, we also measured participants' self-reported tendency to lie in their everyday life using the \emph{Lie Scale} (Makowski, Pham, Lau, Raine, et al., 2021), a 16-item questionnaire that assesses 4 dispositional lying dimensions - Ability (\(\alpha = 0.92\)), Frequency (\(\alpha = 0.66\)), Negativity (\(\alpha = 0.66\)), and Contextuality (\(\alpha = 0.70\)).
+Finally, on top of the deception task, we also measured participants' self-reported tendency to lie in their everyday life using the \emph{Lie Scale} (Makowski, Pham, Lau, Raine, et al., 2021), a 16-item questionnaire that assesses four dispositional lying dimensions - Ability (\(\alpha = 0.92\)), Frequency (\(\alpha = 0.66\)), Negativity (\(\alpha = 0.66\)), and Contextuality (\(\alpha = 0.70\)).
 
@@
 Compared to truths, lies were rated with less confidence (\(\Delta=-1.35,~95\%~CI~[-1.46, -1.23],~pd = 100\%\)), but no significant difference between the conditions was found.
-On the other hand, the RT did not differ between truths and lies, but was significantly slower in the polygraph condition for both conditions (\(\Delta=0.25\), 95\% CI {[}0.62, 0.41{]}, pd = 100\%).
-The heart rate was significantly more elevated during lies as compared to truths (\(\Delta=1.16\), 95\% CI {[}0.57, 1.73{]}, pd = 100\%), and during interrogation as compared to the polygraph condition (\(\Delta=4.84\), 95\% CI {[}4.23, 5.44{]}, pd = 100\%).
-
-The indirect phrasing of the question only had a significant effect on RT (\(\beta=0.36\), 95\% CI {[}0.21, 0.51{]}, pd = 100\%), leading to slower answers, regardless of whether they were lies or truths.
+On the other hand, the RT did not differ between truths and lies, but was significantly slower in the polygraph condition for both conditions (\(\Delta=0.25,~95\% CI [0.62, 0.41],~pd = 100\%\)).
+The heart rate was significantly more elevated during lies as compared to truths (\(\Delta=1.16,~95\% CI [0.57, 1.73],~pd = 100\%\)), and during interrogation as compared to the polygraph condition (\(\Delta=4.84,~95\% CI [4.23, 5.44],~pd = 100\%\)).
+
+The indirect phrasing of the question only had a significant effect on RT (\(\beta=0.36,~95\% CI [0.21, 0.51],~pd = 100\%\)), leading to slower answers, regardless of whether they were lies or truths.
 Given this absence of interaction with the type of answers in any modality, this factor was not included in subsequent analysis.
@@
 
-The higher composite \emph{ToM} score was significantly associated with a decreased confidence in lies (\(\beta=-0.19\), 95\% CI {[}-0.36, -0.02{]}, pd = 98.47\%), specifically in the polygraph condition.
+The higher composite \emph{ToM} score was significantly associated with a decreased confidence in lies (\(\beta=-0.19,~95\% CI [-0.36, -0.02],~pd = 98.47\%\)), specifically in the polygraph condition.
 \textbf{Figure 1} illustrates the interindividual correlates of lying confidence.
-The higher composite \emph{ToM} score was also associated with slower answers for lies (\(\beta=0.42\), 95\% CI {[}0.01, 0.83{]}, pd = 97.67\%), specifically in the polygraph condition.
+The higher composite \emph{ToM} score was also associated with slower answers for lies (\(\beta=0.42,~95\% CI [0.01, 0.83],~pd = 97.67\%\)), specifically in the polygraph condition.
 No significant effect was found with regards to dispositional lying traits, heart rate, and RT for truths in both polygraph and interrogation conditions.
@@
 
-The higher \emph{Focus} interoception score was significantly associated with an increased confidence in truths in the polygraph (\(\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%\)); a consistent pattern, although non-significant, was found for confidence in truth in the interrogation conditions (\(\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%\)).
+The higher \emph{Focus} interoception score was significantly associated with an increased confidence in truths in the polygraph (\(\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%\)); a consistent pattern, although non-significant, was found for confidence in truths in the interrogation condition (\(\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%\)).
 The \emph{Focus} interoception score was also positively correlated with the dispositional lying \emph{Ability} trait (\(r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%\)).
-No significant association was found with RT for lies and heart rate in both conditions
+No significant association was found with RT for lies and heart rate in both conditions.
 
